### 2019-03-21 tex/appendix/ellipse_intersection.tex
Initial Overleaf Import

In this appendix the intersection of two ellipses with the same shape parameters $(a,b) \in \R^2_{>0}$ is described with more detail, as well as determining the functions $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ for two ellipses that intersect.

\section{Intersection}

Let $E_1$ and $E_2$ be two ellipses that the intersection will be determined here. Without loss of generality, let us assume that $E_1$ is at the origin and $E_2$ is located at the center $(h,k) \in \R^2$. Their equations are given by

\begin{align*}
    \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1 && (E_1)\\
    \frac{(x-h)^2}{a^2} + \frac{(y-k)^2}{b^2} = 1 && (E_2)
\end{align*}

As they are both equal to one we can get the following

\begin{align*}
    b^2x^2 + a^2y^2 = b^2(x-h)^2 + a^2(y-k)^2 \\
    b^2(-2xh + h^2) + a^2(-2yk + k^2) = 0\\
    x(2hb^2) = b^2h^2 + a^2(-2yk + k^2)\\
    x = y\frac{-2yka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2}
\end{align*}

Which can be rewritten as

\begin{align*}
    x = y\alpha + \beta
\end{align*}

with the constants $\alpha$ and $\beta$ being

\begin{align*}
    \alpha = \frac{-2yka^2}{2hb^2} \\
    \beta = \frac{b^2h^2 + a^2k^2}{2hb^2}
\end{align*}

Then replacing it back to the equation of $E_1$ we get

\begin{align*}
    \frac{(y\alpha + \beta)^2}{a^2} + \frac{y^2}{b^2} = 1\\
    b^2(y\alpha + \beta)^2 + y^2a^2 - a^2b^2 = 0\\
    y^2(b^2\alpha^2 + a^2) + y(2\beta\alpha b^2) + b^2\beta^2 -a^2b^2 = 0
\end{align*}

Which is a second degree polynomial, therefore, $E_1$ and $E_2$ intersect if, and only if the roots of the polynomial are real. The intersection points itself can be obtained by solving the polynomial for $y$ and applying its value onto the $x=y\alpha + \beta$ equation.

\subsection{Determining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$}

Let us assume that $E_1$ and $E_2$, each one with shape parameters $(a,b) \in \R^2_{>0}$, intersect at $p_1$ and $p_2$. Then, to determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the angles of intersection of $p_1$ and $p_2$ on $E_1$. For that, let us first define another way that ellipses can be represented

\begin{definicao}
Let $E(q)$ be an ellipse with shape parameters $(a,b)\in \R^2_{>0}$, centered at $q \in \R^2$. Then, $E(q)$ is the set of points that are the image of curve $\gamma : [0, 2\pi] \mapsto \R^2$ given by

\begin{equation}\label{eq:parametric_ellipse}
\gamma(t) = \left\{
\begin{array}{l}
x(t)= a\cos{t} + q_x\\
y(t)=b\sin{t} + q_y
\end{array}
\right.
\end{equation}

\end{definicao}

From \autoref{eq:parametric_ellipse}, we can get that

\begin{align*}
\dfrac{y-q_y}{x-q_x} = \dfrac{b}{a}\tan{t}\\
t=\arctan\left(\dfrac{a}{b} \dfrac{y-q_y}{x-q_x}\right)
\end{align*}

However, as the image of $\arctan$ is $[-\frac{\pi}{2}, \frac{\pi}{2}]$, we need to check the sign of $x-q_x$ to determine the angle in $[0, 2\pi]$. After that, we can get the two angles that represent the intersection points on $E_1$.

To find out which one of the angles are $\Gamma_+(1,2)$, we need to go further and determine the derivative of $\gamma(t)$ which is going to be used to determine the vectors tangent to the ellipses at the intersection points.

\begin{equation}\label{eq:der_parametric_ellipse}
\gamma'(t) = \left\{
\begin{array}{l}
x(t)= -a\sin{t}\\
y(t)=b\cos{t}
\end{array}
\right.
\end{equation}

Let $\gamma_1$ and $\gamma_2$ be the curves describing $E_1$ and $E_2$ respectively. Also, let $s_1$ be the angle, such that $\gamma_1(s_1)=p_1$, and $t_1$ be the angle, such that $\gamma_2(t_1)=p_1$.
Then, the tangent vectors to the $E_1$ and $E_2$ at $p_1$ are $\gamma_1'(s_1)$ and $\gamma_2'(t_1)$ respectively.

\begin{figure}[H]
\centering

    \caption{Determining $\Gamma_+(1,2)$}
    \input{tex/figures/ellipse_gamma.tex}
    \fautor
    \label{fig:ellipse_gamma}
\end{figure}

The following lemma states a relation between $s_1$ and $\Gamma_+(1,2)$

\begin{lema}\label{lema:lema_ellipse_angle}
	Let $\theta$ be the angle between $\gamma_1'(s_1)$ and $\gamma_2'(t_1)$ (counter-clockwise). Then, $\theta > \pi$ if, and only if $\Gamma_+(1,2)=s_1$.
\end{lema}

Instead of a formal proof of \autoref{lema:lema_ellipse_angle}, a graphical explanation using \autoref{fig:ellipse_gamma} is provided.

First, let us state some facts that can also be seen in \autoref{fig:ellipse_gamma}

\begin{itemize}
    \item $E_1 \cap E_2$ is convex and bounded by two arcs, one from each ellipse.
    \item Starting at any of the intersection points, one of the $E_1 \cap E_2$ arcs will be clockwise-oriented and the other counter-clockwise-oriented.
    \item The counter-clockwise-oriented arc starting at $\Gamma_+(1,2)$ is from $E_1$.
\end{itemize}

Let us assume that $p_1$ is the intersection point which is the opening angle $\Gamma_+(1,2)$. Then, the vectors $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ are tangent to the $E_1 \cap E_2$ area at point $p_1$. Because of the convexity of $E_1 \cap E_2$, the angle between $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ has to be less than or equal to $\pi$, therefore the angle between $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ has to be greater than $\pi$, which is what \autoref{lema:lema_ellipse_angle} says. It is easy to see that the converse is also true assuming that $p_1$ is the point which determines the angle $\Gamma_-(1,2)$.

Lastly, in \autoref{fig:ellipse_gamma}, it can be seen that if one point is classified as $\Gamma_+(1,2)$ the other will necessarily be classified as $\Gamma_-(1,2)$.
Computationally, this classification can be done taking the cross product of the two vectors and checking its signal, negative cross products imply an angle greater than $\pi$.

### 2019-03-21 tex/chapter/definicoes.tex
Initial Overleaf Import

Some definitions and results that are used throughout the text are given in this chapter.

\section{Disk}

A circle (or circumference) is a set of points in $\R^2$ that have constant euclidean distance, also known as radius, to another point, also referred to as the center of the circle. A unit circle is a circle with radius equal to $1$.
A disk is the set of points of a circle plus its interior

\begin{definicao}
Let $q \in \R^2$, a unit disk centered at $q$ is the set of points that satisfy \autoref{equation:disk_eq}

\begin{equation}\label{equation:disk_eq}
    (x-q_x)^2 + (y-q_y)^2 \le 1
\end{equation}
\end{definicao}

\section{Ellipse}
An ellipse is the set of all points which have the sum of the distances to two focal points constant. Several equations and parametrizations can be derived from this definition, here they are gonna separated in two cases, the axis parallel and the non axis parallel case.

The axis of an ellipse is the line that passes through its two focal points. An ellipse is considered axis parallel, if its axis is parallel to the $x$-axis.

\subsection{Axis parallel}

An axis parallel ellipse centered at $(0,0)$ can be described by two shape parameters: $a \in \R_{>0}$ the semi-major, $b \in \R_{>0}$ the semi-minor. Its equation is given by \ref{equation:pellipse}

\begin{equation}\label{equation:pellipse}
    \dfrac{x^2}{a^2} + \dfrac{y^2}{b^2} = 1
\end{equation}

\begin{figure}[H]
\centering

    \caption{View of the ellipses parameters}
    \input{tex/figures/ellipse_definition.tex}
    \fautor
    \label{fig:3ellipses_intersect}
\end{figure}

\begin{definicao}
An axis-parallel ellipse centered at $(c_x, c_y) \in \R^2$, with shape parameters $(a,b) \in \R^2_{>0}$ is said to cover a point $p=(p_x,p_y)$ if the \autoref{equation:cover_ellipse} is satisfied.

\begin{equation}\label{equation:cover_ellipse}
    \dfrac{(p_x-c_x)^2}{a^2} + \dfrac{(p_y-c_y)^2}{b^2} \le 1
\end{equation}
\end{definicao}

In other words, a point is considered covered by an ellipse if it lies inside, or in the border of the region determined by it.

No equivalent disk-circle wording exists for ellipses, this could be a source of ambiguity in the text, that is why a note for the reader was judged to be necessary. Throughout this work an ellipse will represent the set of points that satisfy \autoref{equation:pellipse}. In some places, though, with prior clarification, we will denote as an ellipse, the set of points that satisfy \autoref{equation:cover_ellipse}. For example, when we define $\Pp \cap E$ as the set of points in $\Pp$ that are covered by $E$, we are implicityly calling $E$ the set of points that satisfy \autoref{equation:cover_ellipse}.

### 2019-03-21 tex/chapter/ellipses.tex
Initial Overleaf Import

In this chapter, two versions of the planar maximal covering by ellipses problem will be introduced.
First, the axis-parallel variant will be defined and a method for it will be developed. Second, the version where there is no axis-parallel constraint and the ellipses can be freely rotated will be introduced.

\section{Axis-Parallel}
The maximal planar covering using axis-parallel ellipses was first introduced in \cite{canbolat} which proposed a mixed integer non-linear programming method for the problem. This first approach showed to be not that efficient as it could not find the optimal solution for some instances within a timeout defined by them. To obtain solutions, not necessarily optimal ones, for the instances which the exact method showed inefficiency, a heuristic technique called Simulated Annealing was used to develop another method. Comparisons were made, and the second approach was able to obtain good solutions, compared to the optimal ones found for some of the instances, within a good run-time.

The second work found in the literature was \cite{andreta} which developed a method that breaks the problem into smaller ones fixing the set of points an ellipse is going to cover. For each set of points fixed as the points an ellipse is going to cover, a small optimization problem is solved to find out if there is a location where the ellipse can be placed, so to cover the set of fixed points. To enumerate the possible solutions and then find the optimal one, the method defined a data structure that stores every set of points an ellipse can cover. This method showed better results and was able to find the optimal solutions for the instances that the first method could not get as well as for new created instances.

\subsection{Notation and definition of the problem}

Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}. Therefore, all it takes to describe one is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, also called the shape parameters, and a center point $q \in \R^2$.

Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$, is a pair of real numbers called the shape parameters of an ellipse. 
In the general case every point has weights, but without loss of generality (later explained), this detail will be ignored and the weights are assumed to be unitary.
The notation used here is similar to the one introduced on \autoref{chapter:pmclp}, the ellipse with an undefined center is referred to as $E$. To denote the ellipse with center set to be at point $q$, $E(q)$ is used. Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_ellipse}, in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$. Hence, the problem can be defined as follows

\begin{definicao}
Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by

\begin{equation}
    \max_q |\Pp \cap E(q)|
\end{equation}
\end{definicao}

\subsection{One Disk algorithm adaptation}

The adaptation of \autoref{algoritmo:mcd_1} is obtained by just replacing the function that finds the intersection points between two disks by a function that finds the intersection points between two ellipses.
It can be seen in \autoref{fig:3ellipses_intersect} that the intersection points and their correspondents $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ functions behave the same way as in the disks case.

The intersection of two ellipses as well as determining $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ is described thoroughly in \autoref{chapter:ellipses_intersection}.

\begin{figure}[H]
\centering

    \caption{Three ellipses and their intersection points}
    \input{tex/img.ellipses.1.tex}
    \fautor
    \label{fig:3ellipses_intersect}
\end{figure}

\subsection{Multiple ellipses}

The multiple ellipses case is handled using the same idea of the multiple disks case. The only difference is that an instance of the multiple ellipses may contain ellipses of different shapes, which does not happen for the disks case as every disk has the same radius. For this reason, a different pre-processing has to be done for every one of them.

An instance of the multiple ellipses case is denoted as $MCE(\Pp, \E)$, with $\Pp$ being a set of $n$ points and $\E = \{E_1, \dots, E_m\}$ being a set of $m$ ellipses, each one with shape parameters $(a_i, b_i) \in \R^2_{>0}, i = 1 \dots m$. Also, without loss of generality, the weight of every point is assumed to be unitary.

\begin{definicao}
Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by

\begin{equation}
    max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|}
\end{equation}
\end{definicao}

The \autoref{algoritmo:mce} describes the adapted version of the maximal disk covering algorithm for the ellipses case. The $MCE_1$ procedure returns every possible set of points that an ellipse with shape parameters $(a,b)$ can cover. With that, the procedure $MCE$ does the backtracking process, assigning every possible cover to every ellipse.

As stated in \autoref{lema:disk}, $MCE_1$ runs in $\bigO(n^2\log{n})$. The number of sets of points an ellipse can cover, however, is $\bigO(n^2)$, note that the $\log{n}$ is part of the complexity due to sorting the set $A$. If $MCE_1$ is called only in a pre-process phase storing its return for every ellipse, a $\bigO(n^{2m})$ run-time complexity can be achieved.

Also, it can be seen that the unitary weights assumption can be easily removed through replacing the way the answer is updated: 
the weights of the covered points should be added to the answer instead of the number of covered points, this could be done by keeping an extra variable along with every possible set of points an ellipse can cover that is returned by $MCE_1$.

It is worth noting that some easy improvements, which do not change the algorithm's overall complexity, can be made in the implementation. For example, if an ellipse covers two sets of points $X$ and $Y$, with $X \subset Y$, then set $X$ can be ignored by the algorithm because of the positive weights constraint.

\begin{algoritmo}[b]
\caption{Algorithm for $MCE(\Pp, \E)$ with unit weights}\label{algoritmo:mce}
\begin{algorithmic}[1]
\Procedure{$MCE_1$}{$\Pp, a, b$}\Comment{Returns every possible coverage.}
\State $Q \gets \{\}$

\ForAll{$p_i \in \Pp$}
\State Let $E_i$ be the ellipse with center at $p_i$ and parameters $(a,b)$

\State Let $I_i$ be the set of ellipses that intersect with $E_i$

\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$

\State $Q \gets Q \cup \{p_i\}$ 
\State $Cov \gets \{p_i\}$ \Comment{The set of active disks}

\For{$cnt=1..2$} \Comment{Do it twice}
\For{$a \in A$}\Comment{Assuming $A$ is sorted}
\State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
\If{$a$ is a starting angle}
\State $Cov \gets Cov \cup \{p_a\}$
\Else
\State $Cov \gets Cov \setminus \{p_a\}$
\EndIf
\State $Q \gets Q \cup Cov$
\EndFor
\EndFor
\EndFor

\State \Return $Q$
\EndProcedure

\Procedure{$MCE$}{$\Pp, \E, j=1$}\Comment{Returns an optimal solution of $MCE(\Pp, \E)$, $j$ is a backtracking parameter that says that $j$-th ellipse should be processed by this call.}
\If{$j = m+1$}
\State \Return $0$
\EndIf

\State $ans \gets 0$
\For{$E \in \E$}
\State Let $(a,b)$ be the shape parameters of $E$
\State $Q \gets MCE_1(\Pp, a, b)$
\For{$Cov \in Q$}
\State $ans \gets \max\{ans, |Cov| + MCE(\Pp \setminus Cov, \E, j+1 \}$ \Comment{Calls the procedure for the next ellipse}
\EndFor
\EndFor

\State \Return $ans$
\EndProcedure
\end{algorithmic}
\end{algoritmo}

### 2019-03-21 tex/chapter/future.tex
Initial Overleaf Import

In this work, we defined the problem of planar maximal covering by disks, we called it $MCD$, and proposed a method for it based on previous works that we found. This method established the basis of our work, as after defining the ellipses counterpart problem, we developed a method based on that algorithm which needed very little modification. To compare results with \cite{andreta}, a small change needs to be done in the algorithm because their version of the problem contains another constraint: out of the $m$ ellipses given, the solution can use exactly $k$ of them. This change as well as the comparison of results is left as future work.

The $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} is also a subject of future work and is set as the primary goal for this master's research. We want to develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

Also, in \cite{aronov:2008} a Monte Carlo approximation is presented for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse. An adaptation for the multiple ellipses case is left as a secondary goal for the final version of this work.

Finally, the version of the problem where every ellipse can be freely rotated is left as a subject of study for the future. In \cite{andreta}, the deterministic method developed by them could not obtain solutions for moderate-to-large instances within reasonable time. Because of that, a stochastic global optimization method was proposed, it performed well and was able to obtain an optimal solution for small cases. The goal we have in mind for the future is to develop an exact method that takes into consideration the algorithm we developed for the axis-parallel version of the problem and compare the results.

### 2019-03-21 tex/chapter/introducao.tex
Initial Overleaf Import

There are two main types of optimal covering problems found in the literature: the minimum cover problem, also known as just set cover, and the maximal covering problem \cite{karatas}.

One of the 21 Karp's NP-Hard problems \cite{karp}, the minimum cover is considered to be a classic and very well studied problem. On it, a demand set has to be covered, and the cost of doing it has to be minimized. One of its most famous example is the minimum vertex cover defined over graphs where the vertex set has to be covered by a subset of edges.

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \cite{church:1974}. In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities are used. Just like the minimum cover, \MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed for it.

In \cite{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced. This version of the problem was not defined on a network, instead the demand set and the facilities are located in $\R^2$, having the coverage area of a facility be defined by a distance function. PMCLP is said to have been studied under euclidean and rectilinear distance functions \cite{younies}. The euclidean norm PMCLP, which has a lot of results that are applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}. The version where only one disk is used is studied in \cite{chazelle:1986}, a $\bigO(n^2)$ algorithm is proposed, improving the $\bigO(n^2\log{n})$ algorithm that was created in \cite{drezner}. Furthermore, in \cite{aronov:2008} a lower bound result is stabilised, it proves that one disk maximal covering is a 3SUM-HARD problem, which means that it is as difficult as finding three real numbers that sum to zero among $n$ given real numbers. The version with $m$ unit disks was studied in \cite{cabello:2006} and a $\bigO(n^{2m-1}\log{n})$ deterministic algorithm is developed, also a $(1-\epsilon)$-approximation method, for any $\epsilon > 0$, that runs in $\bigO(n\log{n})$.

The difference between the regular PMCLP and the one studied in this work is that the shape of the coverage area of a facility is determined by an ellipse. The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal an elliptical PMCLP is better suited \cite{canbolat}. Only two articles have been found published in the literature that study this problem. In \cite{canbolat}, a mixed non-linear programming method was proposed as a first approach to the problem. For some instances the method took too long and did not find the optimal solution. For this reason a heuristic method was developed using a technique called Simulated Annealing, solutions for the instances that timed-out with the first method were then obtained. The problem was further explored in \cite{andreta} which proposed a deterministic method that showed better performance obtaining the optimal solutions for the instances which the first method could not. Also, in \cite{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find the optimal solutions for large instances, and a heuristic method were proposed for it.

### 2019-03-21 tex/chapter/pmclp.tex
Initial Overleaf Import

In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP. Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$ where $\Pp$ is a set of points and $m$ is the number of unit disks.

\section{One disk, $MCD(\Pp,1)$}

Two exact methods for the $MCD(\Pp, 1)$ have been found in the literature. A $\bigO(n^2)$ algorithm is proposed by \cite{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \cite{drezner}.
As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real number that sum to $0$, given $n$ real numbers). Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for $MCD(\Pp,1)$, which meant that no better time-complexity could be achieved. Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.

The $m=1$ version is treated here before the general case because it will be shown that, using the algorithm here proposed for $MCD(\Pp, 1)$, an optimal solution can be obtained for the $MCD(\Pp, m)$ as well as for the axis-parallel ellipse version of the problem.

\subsection{Notation and definition of the problem}

Initially, the input of the problem defines a unit disk with its center point undefined, a solution for the problem will then choose a point to be the center of the unit disk, in other words a solution places the disk somewhere in the plane.
We refer to the unit disk with undefined center as $D$. If it is placed at a center $q \in \R^2$, we call it $D(q)$.

\begin{definicao}
    Let $\Pp=\{p_1,\dots,p_n\}$ be a set of $n$ points in $\R^2$, and $w(p)>0, p \in \Pp$ the weight of every point in $\Pp$, we denote $w(A)$, with $A \subset \Pp$, as the sum of weights of every point in $A$. Finally, let $D$ be a unit disk, we define the optimal solution of $MCD(\Pp,1)$ as

    \begin{equation}\label{eq:max_one_disk}
        \max_q w(\Pp \cap D(q))
    \end{equation}

\end{definicao}

Therefore, an optimal solution for an instance of $MCD(\Pp,1)$ will be a point in which a unit disk located at it, covers points whose weights, when summed, is maximal.

In \cite{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal one.
The algorithm, for every point, sorts the other points with respect to the angle they form with the first one. After that, the first point is placed on the border of the disk and, going through the sorted list, the algorithm inserts and removes points from the disk coverage. Also, when inserting and removing a point from the coverage, it only checks the disk centers that make the entering/leaving point to be on the border. Because the algorithm only checks the centers that make the disk have two points on its border, the number of centers it goes through is bounded by the number of pairs of points, which is $\binom{n}{2} = \bigO(n^2)$.

In \cite{chazelle:1986, cabello:2006}, on the other hand, the authors instead of working directly with $MCD(P,1)$, introduced an equivalent problem called maximum weight clique. Both methods for this problem consist on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections. With the graph constructed, a traversal would be done to obtain the answer, thus the time complexity of $\bigO(n^2)$.
The algorithm that we later describe in this work also uses this equivalence. That is why it has been taken to be fundamental to introduce the maximum weight clique problem and discuss the equivalence.

\section{Maximum weight clique}

Let $\Pp=\{p_1,\dots,p_n\}$, with $p\in \R^2$ be a set of points, $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$. A clique, in this context, is a non-empty intersection area of a subset of disks. Note that this is different than the clique problem on a intersection graph (a graph where the vertices are the disks and an edge exists if there is an intersection between two disks). As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique), but the intersection of all the three together is empty. That is why the clique problem for unit disks is also referred to as the maximum geometric clique problem when the condition of common intersection exists and as the maximum graphical clique problem where there is only the pairwise intersection condition \cite{inplace:2014}. The graphical version of the problem was studied by \cite{graphical-clique} where a $\bigO(n^{4.5})$ algorithm was proposed. Also, in \cite{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm, which needs $\bigO(1)$ extra space, for arbitrary radii disks was proposed.

\begin{figure}[H]
\centering

    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection}
    \begin{tikzpicture}[domain=0:11]
    %\draw [help lines] (-5,-3) grid (5,3);
    \draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);

    %a^2-b^2=c^2 -> c^2=25-9=16 -> c=4

    \draw[fill] (0.9,1.6) circle [radius=.5pt];
	\draw[fill] (0,0) circle [radius=.5pt];
    \draw[fill] (-0.9,1.6) circle [radius=.5pt];

    \node[below] at (0,0) {$p_1$};
    \node[below] at (0.9, 1.6) {$p_2$};
    \node[below] at (-0.9, 1.6) {$p_3$};

    %\draw [-] (-5,0) -- (5,0);
     %\draw [-] (0,-3) -- (0,3);
     %\draw [|-|] (0.001,-0.1) -- (4.999,-0.1);
    \end{tikzpicture}
    \label{fig:three_disks_no_intersection}
    \fautor
\end{figure}

A solution for the maximum weight clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized. Even though, there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the maximum weight clique is enough. This will become clear when the equivalence is stated. With everything in hands, we can define the maximum weight clique problem as follows

\begin{definicao}\label{def:max_weight_clique}
    Let $\D$ be a set of unit disks and $\Pp$ be a set of points as defined before, an optimal solution for the maximum weight clique problem is given by

    \begin{equation}
        \max_q \sum_{D_k \cap q \neq \emptyset} w_k
    \end{equation}

\end{definicao}

As it has been proposed, with the equivalence of the two problems, the optimal solution of the maximum weight clique problem is also the optimal solution of the $MCD(\Pp,1)$, which means that a disk centered at $q$, defined in \autoref{def:max_weight_clique}, will have a maximal weight covering of the set $\Pp$.

Given an instance of $MCD(\Pp,1)$, the equivalent maximum weight clique problem is obtained by defining the set $\D$ to be the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$. A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$, this means that a intersection between some disks is an area where a disk could be placed to cover the corresponding points.

In \autoref{fig:three_disks_no_intersection}, it can be seen that there is no point where a disk could be placed such that it would cover $p_1, p_2$ and $p_3$, nonetheless anywhere, in any of the pairwise intersections, a disk could be placed to cover the two corresponding points.

Formally, in the maximum weight clique problem, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the $MCD(P,1)$ problem. Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the one disk maximal covering problem. It means that $q$ will lie inside the region $\bigcap_{k \in I} D_k$.

\subsection{An algorithm for the maximum weight clique problem}

The algorithm described here is based on the one in \cite{drezner}, also with some ideas from \cite{inplace:2014} and \cite{cabello:2006}. It has a run time complexity of $\bigO(n^2\log{n})$ and uses $\bigO(n)$ of extra space. It is worth noting, however, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \cite{bentley:1979} to find all the intersections among the $n$ circumferences.

Without loss of generality, the weights will be ignored, and the method will be described for the maximum clique problem, assuming that every disk has unit weight. Also, it will be assumed that no pair of disks are placed at the same center.

Let $\D$ be a set of $n$ unit disks, a non-empty intersection area of a subset of disks is convex and bounded by the arcs of the disks that are intersecting \cite{inplace:2014}.
This observation makes checking for every disk $\Cc$, every intersection area that is bounded by its arc sufficient in order to find the optimal solution.

\begin{definicao}\label{def:inter_arc}
    Let $D_i$ and $D_j$ be two unit disks that intersect (at least at one point). Also let $(\theta_1, \theta_2) \in [0,2\pi]^2$ be the two angles that the circumferences induced by $D_i$ and $D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$. If $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$. Then, We define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
\end{definicao}

\begin{figure}[H]
\centering

    \caption{Three disks and their intersection points}
    \input{tex/img2.tex}
    \fautor
    \label{fig:3disks_intersect}
\end{figure}

In \autoref{fig:3disks_intersect}, it is shown all the intersection points between $D_1$ with $D_2$ and $D_3$, also they are labeled according to \autoref{def:inter_arc}, note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).

With \autoref{def:inter_arc} in hands, we can establish the basis of the algorithm to find the maximum clique that a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$ in counter-clockwise order keeping a set of active disks, when an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$, see \autoref{fig:3disks_intersect}. If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it, if there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and the optimal solution could end up not being found. This can be worked around repeating the traversal once without resetting the active disks set, that way in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$.

\begin{algoritmo}
\caption{Algorithm for $MCD(\Pp, 1)$ with unit weights}\label{algoritmo:mcd_1}
\begin{algorithmic}[1]
\Procedure{$MCD_1$}{$\Pp$}\Comment{Returns the maximum number of disks that have a non-empty.}
\State $Q_{best} \gets \{\}$
\State $ans \gets$ center of $D_1$
\ForAll{$p_i \in \Pp$}
\State Let $D_i$ be the disk with center at $p_i$
\State Let $I_i$ be the set of disks that intersect with $D_i$
\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$

\State $Q \gets \{D_i\}$ \Comment{The set of active disks}
\For{$cnt=1..2$} \Comment{Do it twice}
\For{$a \in A$}\Comment{Assuming $A$ is sorted}
\State Let $D_a$ be the disk that intersects $D_i$ at angle $a$. 
\If{$a$ is a starting angle}
\State $Q \gets Q \cup \{D_a\}$
\Else
\State $Q \gets Q \setminus \{D_a\}$
\EndIf
\If{$|Q_{best}| < |Q|$}
\State $Q_{best} \gets Q$
\State $ans \gets $ point corresponding to the intersection angle $a$
\EndIf
\EndFor
\EndFor
\EndFor

\State \Return $ans$
\EndProcedure
\end{algorithmic}
\end{algoritmo}

\begin{lema}\label{lema:disk}
The \autoref{algoritmo:mcd_1} for the maximum clique has a $\bigO((n+K)\log{n})$ run time complexity where $K$ is the number of intersections of the $n$ disks.
\end{lema}

\begin{proof}
    Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \cite{bentley:1979}. 
    Because the traversal is made in counter-clockwise order, the intersection points have to be sorted by their intersection angles, so an additional $\bigO(K\log{K})$ pre-processing is needed. All the other operations can be done in constant time. Therefore, the final algorithm complexity is $\bigO((n+K)\log{n})$.
\end{proof}

If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.

\section{Multiple disks $MCD(\Pp, m)$}

For the case with $m>1$, a simple backtracking algorithm can be developed, considering every possible solution for every one of the $m$ unit disks. In any solution, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the maximum weight clique problem. The point $q$ is inside a intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by the algorithm as a candidate to be the optimal solution. Therefore, the \autoref{algoritmo:mcd_1} can be adapted to serve the backtracking that searches for an optimal solution of $MCD(\Pp, m)$. Then, as for every disk there are $\bigO(n^2)$ possible centers, the overall complexity of the backtracking algorithm is $\bigO(n^{2m})$.

### 2019-03-21 tex/figures/ellipse_definition.tex
Initial Overleaf Import

%\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Ellipse [id:dp1559950964552308] 
\draw   (100,180) .. controls (100,147.42) and (161.34,121) .. (237,121) .. controls (312.66,121) and (374,147.42) .. (374,180) .. controls (374,212.58) and (312.66,239) .. (237,239) .. controls (161.34,239) and (100,212.58) .. (100,180) -- cycle ;
%Straight Lines [id:da3716259356733107] 
\draw    (100,180) -- (374,180) ;

%Straight Lines [id:da9880464900454329] 
\draw    (237,121) -- (237,239) ;

%Shape: Brace [id:dp3973633345998604] 
\draw   (242,182) .. controls (242,186.67) and (244.33,189) .. (249,189) -- (293.5,189) .. controls (300.17,189) and (303.5,191.33) .. (303.5,196) .. controls (303.5,191.33) and (306.83,189) .. (313.5,189)(310.5,189) -- (358,189) .. controls (362.67,189) and (365,186.67) .. (365,182) ;
%Shape: Brace [id:dp94498526835576] 
\draw   (232,129) .. controls (227.34,128.79) and (224.9,131.01) .. (224.68,135.67) -- (224.47,140.23) .. controls (224.16,146.89) and (221.68,150.11) .. (217.01,149.9) .. controls (221.68,150.11) and (223.85,153.55) .. (223.54,160.21)(223.68,157.21) -- (223.33,164.68) .. controls (223.12,169.35) and (225.34,171.79) .. (230,172) ;
%Shape: Arc [id:dp3154280429415799] 
\draw  [draw opacity=0] (258.54,158.43) .. controls (260.37,158.96) and (262.06,159.82) .. (263.54,161.03) .. controls (268.5,165.07) and (270.12,172.1) .. (268.62,179.79) -- (244.51,184.38) -- cycle ; \draw   (258.54,158.43) .. controls (260.37,158.96) and (262.06,159.82) .. (263.54,161.03) .. controls (268.5,165.07) and (270.12,172.1) .. (268.62,179.79) ;
%Shape: Circle [id:dp8908034615999807] 
\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (289.08,125.57) .. controls (289.08,124.98) and (289.56,124.51) .. (290.14,124.51) .. controls (290.73,124.51) and (291.21,124.98) .. (291.21,125.57) .. controls (291.21,126.16) and (290.73,126.64) .. (290.14,126.64) .. controls (289.56,126.64) and (289.08,126.16) .. (289.08,125.57) -- cycle ;
%Straight Lines [id:da6323920079482996] 
\draw    (290.14,125.57) -- (237,180) ;

% Text Node
\draw (304,205) node   {$a$};
% Text Node
\draw (207,148.33) node   {$b$};
% Text Node
\draw (330,114.67) node [scale=0.5]  {$( x,y) \ =\ \left( a\cos^{2} t,\ b\sin^{2} t\right)$};
% Text Node
\draw (279.6,162) node [scale=0.7]  {$t$};

\end{tikzpicture}

### 2019-03-21 tex/figures/ellipse_gamma.tex
Initial Overleaf Import

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,193); %set diagram left start at 0, and has height of 193

%Shape: Ellipse [id:dp10634347053631776] 
\draw   (68.5,97.75) .. controls (68.5,67.24) and (115.62,42.5) .. (173.75,42.5) .. controls (231.88,42.5) and (279,67.24) .. (279,97.75) .. controls (279,128.26) and (231.88,153) .. (173.75,153) .. controls (115.62,153) and (68.5,128.26) .. (68.5,97.75) -- cycle ;
%Shape: Ellipse [id:dp7816950476685691] 
\draw  [color={rgb, 255:red, 163; green, 163; blue, 163 }  ,draw opacity=1 ] (167.5,103.75) .. controls (167.5,73.24) and (214.62,48.5) .. (272.75,48.5) .. controls (330.88,48.5) and (378,73.24) .. (378,103.75) .. controls (378,134.26) and (330.88,159) .. (272.75,159) .. controls (214.62,159) and (167.5,134.26) .. (167.5,103.75) -- cycle ;
%Straight Lines [id:da36505632658461096] 
\draw    (236,53) -- (185.87,33.72) ;
\draw [shift={(184,33)}, rotate = 381.03999999999996] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da357569598162492] 
\draw    (234,52) -- (182.95,63.56) ;
\draw [shift={(181,64)}, rotate = 347.24] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da9574900886541131] 
\draw    (212,149) -- (257.1,164.11) ;
\draw [shift={(259,164.75)}, rotate = 198.53] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Straight Lines [id:da5801314237314061] 
\draw    (212,149) -- (261.53,140.1) ;
\draw [shift={(263.5,139.75)}, rotate = 529.8199999999999] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Shape: Arc [id:dp33725313902395126] 
\draw  [draw opacity=0][line width=0.75]  (219.73,152.25) .. controls (218.31,154.08) and (215.71,155.31) .. (212.73,155.31) .. controls (208.24,155.31) and (204.6,152.51) .. (204.6,149.06) .. controls (204.6,145.61) and (208.24,142.81) .. (212.73,142.81) .. controls (216.16,142.81) and (219.09,144.44) .. (220.29,146.74) -- (212.73,149.06) -- cycle ; \draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=0.75]  (219.73,152.25) .. controls (218.31,154.08) and (215.71,155.31) .. (212.73,155.31) .. controls (208.24,155.31) and (204.6,152.51) .. (204.6,149.06) .. controls (204.6,145.61) and (208.24,142.81) .. (212.73,142.81) .. controls (216.16,142.81) and (219.09,144.44) .. (220.29,146.74) ;
%Shape: Arc [id:dp6533092564639917] 
\draw  [draw opacity=0] (216.22,56.17) .. controls (213.28,54.85) and (212,51.09) .. (213.38,47.64) .. controls (213.78,46.63) and (214.38,45.75) .. (215.09,45.04) -- (218.98,49.88) -- cycle ; \draw   (216.22,56.17) .. controls (213.28,54.85) and (212,51.09) .. (213.38,47.64) .. controls (213.78,46.63) and (214.38,45.75) .. (215.09,45.04) ;

% Text Node
\draw (216,26) node [scale=0.7]  {$\gamma _{1} '( s_{2})$};
% Text Node
\draw (164,70) node [scale=0.7]  {$\gamma _{2} '( t_{2})$};
% Text Node
\draw (202,50) node [scale=0.5]  {$\theta $};
% Text Node
\draw (284,143) node [scale=0.7]  {$\gamma _{1} '( s_{1})$};
% Text Node
\draw (286,170) node [scale=0.7]  {$\gamma _{2} '( t_{1})$};
% Text Node
\draw (206.67,136.67) node [scale=0.5]  {$\theta $};
% Text Node
\draw (214,163) node [scale=0.7]  {$p_{1}$};
% Text Node
\draw (237,41) node [scale=0.7]  {$p_{2}$};
% Text Node
\draw (56,93) node   {$E_{1}$};
% Text Node
\draw (390,97) node   {$E_{2}$};

\end{tikzpicture}

### 2019-03-22 tex/appendix/ellipse_intersection.tex
WIP

@@
 Then, to determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the angles of intersection of $p_1$ and $p_2$ on $E_1$.
-For that, let us first define another way that ellipses can be represented
+For that, we will use the curve defined in \autoref{eq:parametric_ellipse} because it is easier to work with angles here.
 
-\begin{definicao}
-Let $E(q)$ be an ellipse with shape parameters $(a,b)\in \R^2_{>0}$, centered at $q \in \R^2$. Then, $E(q)$ is the set of points that are the image of curve $\gamma : [0, 2\pi] \mapsto \R^2$ given by
-
-\begin{equation}\label{eq:parametric_ellipse}
-\gamma(t) = \left\{
-\begin{array}{l}
-x(t)= a\cos{t} + q_x\\
-y(t)=b\sin{t} + q_y
-\end{array}
-\right.
-\end{equation}
-
-\end{definicao}
-
-From \autoref{eq:parametric_ellipse}, we can get that
+Given a point $(x,y)$, to find the angle it makes with the major axis, from \autoref{eq:parametric_ellipse}, we can get that
 
@@
 
-However, as the image of $\arctan$ is $[-\frac{\pi}{2}, \frac{\pi}{2}]$, we need to check the sign of $x-q_x$ to determine the angle in $[0, 2\pi]$.
-After that, we can get the two angles that represent the intersection points on $E_1$.
+As the image of $\arctan$ is $[-\frac{\pi}{2}, \frac{\pi}{2}]$, we need to check the sign of $x-q_x$ to determine the angle in $[0, 2\pi]$.
+After that, we can get the two angles that represent the intersection points $p_1$ and $p_2$ on $E_1$.
 
@@
     \item $E_1 \cap E_2$ is convex and bounded by two arcs, one from each ellipse.
-    \item Starting at any of the intersection points, one of the $E_1 \cap E_2$ arcs will be clockwise-oriented and the other counter-clockwise-oriented.
-    \item The counter-clockwise-oriented arc starting at $\Gamma_+(1,2)$ is from $E_1$.
+    \item Starting at any of the intersection points, one of the $E_1 \cap E_2$ arcs will be clockwise-oriented and the other, counter-clockwise-oriented.
+    \item The counter-clockwise-oriented arc starting at $\Gamma_+(1,2)$ is from the ellipse $E_1$.
 \end{itemize}

### 2019-03-22 tex/chapter/definicoes.tex
WIP

@@
 Some definitions and results that are used throughout the text are given in this chapter.
+
+\section{Norm}
+
+Norms are used in this chapter to define disks and ellipses.
+
+\begin{definicao}
+Let $\xi : \R^2 \mapsto [0, \infty]$, $\xi$ is said to be a norm function of $\R^2$ if for any $p, q \in \R^2$ and $a \in \R$,
+
+\begin{enumerate}
+    \item $\xi(p + q) \le \xi(p) + \xi(q)$
+    \item $\xi(ap) = |a|\xi(p)$
+    \item if $\xi(p)=0$, then $p=0$
+\end{enumerate}
+
+\end{definicao}
+
+Probably the most known example of a norm function in $\R^2$ is the euclidean norm, described by \autoref{eq:norm2}.
+
+\begin{equation}\label{eq:norm2}
+||u||_2 = \sqrt{u^{T}u}
+\end{equation}
+
+A more general version of the euclidean norm is the here called elliptical norm which is defined as
+
+\begin{definicao}
+Let $Q$ be a $2$ by $2$ positive definite matrix, and $u \in \R^2$, then the elliptical norm is defined as
+
+\begin{equation}
+||u||_{elliptical} = \sqrt{u^{T}Qu}
+\end{equation}
+\end{definicao}
+
+It is easy to see that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the euclidean norm.
+
+Given a norm function, determining the distance between two points is done by calculating the norm of the vector defined by the difference between the two points.
+For example, the elliptical distance between the points $p,q \in \R^2$ is $||p-q||_{elliptical}$.
 
@@
 A unit circle is a circle with radius equal to $1$.
-A disk is the set of points of a circle plus its interior
+A disk is the set of points of a circle plus its interior, or in other words the set of points with euclidean distance to the center less than or equal the radius.
 
-\begin{definicao}
-Let $q \in \R^2$, a unit disk centered at $q$ is the set of points that satisfy \autoref{equation:disk_eq}
+\section{Ellipse}
 
-\begin{equation}\label{equation:disk_eq}
-    (x-q_x)^2 + (y-q_y)^2 \le 1
+The ellipse is categorized, along with the parabola and the hyperbola, as a conic section.
+As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}.
+From that definition, an equation that describes any conic section is given as follows
+
+\begin{equation}\label{equation:quadratic_form}
+Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0
 \end{equation}
+
+Any ellipse, rotated or axis-parallel, can be described by \autoref{equation:quadratic_form}.
+To distinguish an ellipse from the other conic sections the condition $4AC - B^2>0$ can be verified \cite{ayoub}.
+
+Then, assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
+
+\begin{equation}
+(p-c)^{T}Q(p-c) = 1
+\end{equation}
+
+with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
+
+\[
+Q=
+\left( {\begin{array}{cc}
+	A & \frac{B}{2} \\
+	\frac{B}{2} & C \\
+	\end{array} } \right).
+\]
+
+This makes us arrive at the following definition of the ellipse
+
+\begin{definicao}\label{def:ellipse}
+    Let $c\in \R^2$ be the center of an ellipse and $Q$ be a $2$ by $2$ positive definite matrix, an ellipse is the set of every point $p \in \R^2$ that have $||p-c||_{elliptical} = \sqrt{(p-c)^{T}Q(p-c)} = 1$.
+Also, a point $p$ is considered covered by an ellipse if $||p-c||_{elliptical} = \sqrt{(p-c)^{T}Q(p-c)} \le 1$.
 \end{definicao}
 
-\section{Ellipse}
-An ellipse is the set of all points which have the sum of the distances to two focal points constant.
-Several equations and parametrizations can be derived from this definition, here they are gonna separated in two cases, the axis parallel and the non axis parallel case.
-
-The axis of an ellipse is the line that passes through its two focal points. An ellipse is considered axis parallel, if its axis is parallel to the $x$-axis.
-
-\subsection{Axis parallel}
-
-An axis parallel ellipse centered at $(0,0)$ can be described by two shape parameters: $a \in \R_{>0}$ the semi-major, $b \in \R_{>0}$ the semi-minor. Its equation is given by \ref{equation:pellipse}
-
-\begin{equation}\label{equation:pellipse}
-    \dfrac{x^2}{a^2} + \dfrac{y^2}{b^2} = 1
-\end{equation}
+An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin the construction of the ellipse with two points called foci and a constant $R \in \R$, with $R$ being greater than the distance between the two foci points (see \autoref{fig:ellipse_with_foci}).
+The ellipse is, then, defined as the set of points whose distance to the foci is equal to $R$.
+In other words, let $f_1, f_2 \in \R^2$ be the two foci points, the ellipse is the set of every point $p \in \R^2$, such that $||p-f_1||_2 + ||p-f_2||_2 = R$.
+It can be shown that this definition is equivalent to \autoref{def:ellipse}.
 
@@
 
-    \caption{View of the ellipses parameters}
+    \caption{A non-axis-parallel ellipse and its foci points.}
+    \input{tex/figures/ellipse_with_foci.tex}
+    \fautor
+    \label{fig:ellipse_with_foci}
+\end{figure}
+
+Also, in \autoref{fig:ellipse_with_foci}, the distance $a = ||p_a - c||_2$ is called the semi-major, and the distance $b = ||p_b-c||_2$ is called the semi-minor.
+These two values are also referred to as the shape parameters of an ellipse.
+Let $d = ||c-f_1||_2$, then it is easy to see that $a = R - d$ and $b = \sqrt{\frac{R^2}{4} - d^2}$.
+
+Finally, an ellipse is said to be axis-parallel if its major-axis (see \autoref{fig:ellipse_with_foci}), which is the line that passes through its two foci points, is parallel to the $x$-axis.
+
+\subsection{Axis parallel}
+
+An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{the only non-zero terms are in the main diagonal}.
+This can be understood as a scaling transformation applied to the euclidean norm.
+Defining the matrix $Q$ as
+
+\[
+Q=
+\left( {\begin{array}{cc}
+    \frac{1}{a^2} & 0 \\
+    0 & \frac{1}{b^2} \\
+    \end{array} } \right)
+\]
+
+Then, starting from \autoref{def:ellipse}, we can obtain the following equation
+
+\begin{align*}
+        (p-c)^{T}Q(p-c) = 1\\
+    (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) = 1
+ \end{align*}
+ \begin{equation}
+  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} = 1
+ \end{equation}
+
+where $a$ and $b$ are the semi-major and semi-minor shape parameters respectively.
+
+Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve, function of the angle with its major-axis (see \autoref{fig:ellipse_params}).
+
+\begin{figure}[H]
+    \centering
+
+    \caption{The ellipse as a parametric curve}
     \input{tex/figures/ellipse_definition.tex}
     \fautor
-    \label{fig:3ellipses_intersect}
+    \label{fig:ellipse_params}
 \end{figure}
 
-\begin{definicao}
-An axis-parallel ellipse centered at $(c_x, c_y) \in \R^2$, with shape parameters $(a,b) \in \R^2_{>0}$ is said to cover a point $p=(p_x,p_y)$ if the \autoref{equation:cover_ellipse} is satisfied.
+Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
+Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse defined in \autoref{eq:parametric_ellipse}.
 
-\begin{equation}\label{equation:cover_ellipse}
-    \dfrac{(p_x-c_x)^2}{a^2} + \dfrac{(p_y-c_y)^2}{b^2} \le 1
+    \begin{equation}\label{eq:parametric_ellipse}
+    \gamma(t) = \left\{
+    \begin{array}{l}
+    x(t)= a\cos{t} + c_x\\
+    y(t)=b\sin{t} + c_y
+    \end{array}
+    \right.
     \end{equation}
-\end{definicao}
-
-In other words, a point is considered covered by an ellipse if it lies inside, or in the border of the region determined by it.
 
 No equivalent disk-circle wording exists for ellipses, this could be a source of ambiguity in the text, that is why a note for the reader was judged to be necessary.
-Throughout this work an ellipse will represent the set of points that satisfy \autoref{equation:pellipse}.
-In some places, though, with prior clarification, we will denote as an ellipse, the set of points that satisfy \autoref{equation:cover_ellipse}.
-For example, when we define $\Pp \cap E$ as the set of points in $\Pp$ that are covered by $E$, we are implicityly calling $E$ the set of points that satisfy \autoref{equation:cover_ellipse}.
+Throughout this work an ellipse will represent the set of points that satisfy \autoref{def:ellipse}.
+In some places, though, with prior clarification, we will denote as an ellipse, the set of points that are covered by the ellipse itself.
+For example, when we define $\Pp \cap E$ as the set of points in $\Pp$ that are covered by $E$, we are implicitly calling $E$ the set of points that are covered by the ellipse itself as it is defined by \autoref{def:ellipse}.

### 2019-03-23 tex/appendix/ellipse_intersection.tex
WIP

@@
 \begin{array}{l}
-x(t)= -a\sin{t}\\
-y(t)=b\cos{t}
+x'(t)= -a\sin{t}\\
+y'(t)=b\cos{t}
 \end{array}
@@
 \begin{lema}\label{lema:lema_ellipse_angle}
-	Let $\theta$ be the angle between $\gamma_1'(s_1)$ and $\gamma_2'(t_1)$ (counter-clockwise). Then, $\theta > \pi$ if, and only if $\Gamma_+(1,2)=s_1$.
+	Let $\theta$ be the angle between $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$. Then, $\theta \le \pi$ if, and only if $\Gamma_+(1,2)=s_1$.
 \end{lema}
@@
     \item Starting at any of the intersection points, one of the $E_1 \cap E_2$ arcs will be clockwise-oriented and the other, counter-clockwise-oriented.
+In \autoref{fig:ellipse_gamma}, for example, it is clear that only the $E_1$ arc starting at $p_1$, ending at $p_2$, is counter-clockwise-oriented.
+
     \item The counter-clockwise-oriented arc starting at $\Gamma_+(1,2)$ is from the ellipse $E_1$.
@@
 Then, the vectors $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ are tangent to the $E_1 \cap E_2$ area at point $p_1$.
-Because of the convexity of $E_1 \cap E_2$, the angle between $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ has to be less than or equal to $\pi$, therefore the angle between $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ has to be greater than $\pi$, which is what \autoref{lema:lema_ellipse_angle} says.
-It is easy to see that the converse is also true assuming that $p_1$ is the point which determines the angle $\Gamma_-(1,2)$.
+Because of the convexity of $E_1 \cap E_2$, the angle between $\gamma_1'(s_1)$ and $-\gamma_2'(t_1)$ has to be less than or equal to $\pi$ (see \autoref{fig:ellipse_gamma}), which is what \autoref{lema:lema_ellipse_angle} says.
+It is easy to prove the converse by proving the contra-positive assuming that $p_1$ is the point which determines the angle $\Gamma_-(1,2)$.
 
-Lastly, in \autoref{fig:ellipse_gamma}, it can be seen that if one point is classified as $\Gamma_+(1,2)$ the other will necessarily be classified as $\Gamma_-(1,2)$.
-Computationally, this classification can be done taking the cross product of the two vectors and checking its signal, negative cross products imply an angle greater than $\pi$.
+Lastly, in \autoref{fig:ellipse_gamma}, it can be seen that if one the intersection points is classified as $\Gamma_+(1,2)$ the other will necessarily be classified as $\Gamma_-(1,2)$.
+This gives us all we need to implement \autoref{algoritmo:mce}.
+
+It is worth noting that computationally, this classification can be done taking the cross product of the two vectors and checking its signal, negative cross products imply an angle greater than $\pi$.
+Also, determining the polar angle of a point in $\R^2$ can be done using the $atan2(x,y)$ function which is present in most of the math libraries of modern programming languages.

### 2019-03-23 tex/chapter/definicoes.tex
WIP

@@
 
-Norms are used in this chapter to define disks and ellipses.
+A norm is a function that maps every vector from a vector space onto a non-negative number satisfying some conditions. Here it is defined for the vector space $\R^2$ as follows
 
@@
 
-Probably the most known example of a norm function in $\R^2$ is the euclidean norm, described by \autoref{eq:norm2}.
+\subsection{Elliptical and euclidean norm functions}
+
+Let $u \in \R^2$ be a vector, the euclidean norm of $u$ is defined as
 
@@
 
-A more general version of the euclidean norm is the here called elliptical norm which is defined as
-
-\begin{definicao}
-Let $Q$ be a $2$ by $2$ positive definite matrix, and $u \in \R^2$, then the elliptical norm is defined as
+The elliptical norm takes a $2$ by $2$ positive definite matrix as its parameter.
+This matrix can be seen as a linear transformation of the euclidean norm.
+Let $u \in \R^2$ be a vector and $Q$ be a $2$ by $2$ positive definite matrix, the elliptical norm of $u$ is defined as
 
@@
 \end{equation}
-\end{definicao}
 
@@
 
-Given a norm function, determining the distance between two points is done by calculating the norm of the vector defined by the difference between the two points.
+Determining the distance between two points, given a norm function is done by calculating the norm of the vector defined by the difference between the two points.
 For example, the elliptical distance between the points $p,q \in \R^2$ is $||p-q||_{elliptical}$.
@@
 A unit circle is a circle with radius equal to $1$.
-A disk is the set of points of a circle plus its interior, or in other words the set of points with euclidean distance to the center less than or equal the radius.
+A disk is the set of points of a circle plus its interior, let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.
+
+\begin{equation}\label{eq:disk}
+||p-c||_2^2 \le 1
+\end{equation}
 
@@
 \begin{definicao}\label{def:ellipse}
-    Let $c\in \R^2$ be the center of an ellipse and $Q$ be a $2$ by $2$ positive definite matrix, an ellipse is the set of every point $p \in \R^2$ that have $||p-c||_{elliptical} = \sqrt{(p-c)^{T}Q(p-c)} = 1$.
-Also, a point $p$ is considered covered by an ellipse if $||p-c||_{elliptical} = \sqrt{(p-c)^{T}Q(p-c)} \le 1$.
+    Let $c\in \R^2$ be the center of an ellipse and $Q$ be a $2$ by $2$ positive definite matrix, an ellipse is the set of every point $p \in \R^2$ that have $||p-c||_{elliptical}^2 = (p-c)^{T}Q(p-c) = 1$.
+Also, a point $p$ is considered covered by an ellipse if $||p-c||_{elliptical}^2 = (p-c)^{T}Q(p-c) \le 1$.
 \end{definicao}
 
-An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin the construction of the ellipse with two points called foci and a constant $R \in \R$, with $R$ being greater than the distance between the two foci points (see \autoref{fig:ellipse_with_foci}).
+An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin its construction with two points called foci and a constant $R \in \R$, with $R$ being greater than the euclidean distance between the two foci points (see \autoref{fig:ellipse_with_foci}).
 The ellipse is, then, defined as the set of points whose distance to the foci is equal to $R$.
 In other words, let $f_1, f_2 \in \R^2$ be the two foci points, the ellipse is the set of every point $p \in \R^2$, such that $||p-f_1||_2 + ||p-f_2||_2 = R$.
-It can be shown that this definition is equivalent to \autoref{def:ellipse}.
+It can be shown that this definition is equivalent to \autoref{def:ellipse}, with the coverage of a point $p$ being equivalent to $||p-f_1||_2 + ||p-f_2||_2 \le R$.
 
@@
 
-\subsection{Axis parallel}
+\subsection{Axis-parallel}
 
@@
  \end{align*}
- \begin{equation}
+ \begin{equation}\label{equation:pellipse}
   \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} = 1
@@
 where $a$ and $b$ are the semi-major and semi-minor shape parameters respectively.
+
+Also, the coverage region is determined by just changing the equality to a inequality as follows
+
+\begin{equation}\label{equation:cover_pellipse}
+\frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} \le 1
+\end{equation}
 
@@
 Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
-Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse defined in \autoref{eq:parametric_ellipse}.
+Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
 

### 2019-03-23 tex/chapter/ellipses.tex
WIP

@@
 To denote the ellipse with center set to be at point $q$, $E(q)$ is used.
-Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_ellipse}, in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$.
+Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse}, in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$.
 Hence, the problem can be defined as follows
@@
 For example, if an ellipse covers two sets of points $X$ and $Y$, with $X \subset Y$, then set $X$ can be ignored by the algorithm because of the positive weights constraint.
+Also, if two ellipses have their centers with euclidean distance greater than their semi-major parameter, they for sure do not intersect.
+Depending on the input, this observation can make the algorithm not go through the whole list of ellipses every time it needs to determine the ellipses pairwise intersections.
 

### 2019-03-23 tex/chapter/introducao.tex
WIP

@@
 Furthermore, in \cite{aronov:2008} a lower bound result is stabilised, it proves that one disk maximal covering is a 3SUM-HARD problem, which means that it is as difficult as finding three real numbers that sum to zero among $n$ given real numbers.
-The version with $m$ unit disks was studied in \cite{cabello:2006} and a $\bigO(n^{2m-1}\log{n})$ deterministic algorithm is developed, also a $(1-\epsilon)$-approximation method, for any $\epsilon > 0$, that runs in $\bigO(n\log{n})$.
+The version with $m$ unit disks was studied in \cite{cabello:2006} which developed a $\bigO(n^{2m-1}\log{n})$ deterministic algorithm and a $(1-\epsilon)$-approximation method, for any $\epsilon > 0$, that runs in $\bigO(n\log{n})$.
 
 The difference between the regular PMCLP and the one studied in this work is that the shape of the coverage area of a facility is determined by an ellipse.
-The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal an elliptical PMCLP is better suited \cite{canbolat}.
+The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.
 Only two articles have been found published in the literature that study this problem.
@@
 Also, in \cite{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find the optimal solutions for large instances, and a heuristic method were proposed for it.
+
+This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximal covering by disks problem is studied and a $\bigO(n^{2m})$ is proposed; in \autoref{chapter:ellipses}, the maximal covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work.
+Also, the \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

### 2019-03-24 tex/chapter/definicoes.tex
WIP

@@
 Determining the distance between two points, given a norm function is done by calculating the norm of the vector defined by the difference between the two points.
-For example, the elliptical distance between the points $p,q \in \R^2$ is $||p-q||_{elliptical}$.
+For example, the elliptical distance between the points $p,q \in \R^2$ is given by $||p-q||_{elliptical}$.
 
@@
 
-The ellipse is categorized, along with the parabola and the hyperbola, as a conic section.
+The ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section.
 As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}.
@@
 Any ellipse, rotated or axis-parallel, can be described by \autoref{equation:quadratic_form}.
-To distinguish an ellipse from the other conic sections the condition $4AC - B^2>0$ can be verified \cite{ayoub}.
+To distinguish an ellipse from the other conic sections given an instance of \autoref{equation:quadratic_form}, the condition $4AC - B^2>0$ can be verified \cite{ayoub}.
 
-Then, assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
+Assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
 
@@
 
-An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{the only non-zero terms are in the main diagonal}.
+An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal}.
 This can be understood as a scaling transformation applied to the euclidean norm.

### 2019-03-24 tex/chapter/future.tex
WIP

@@
-In this work, we defined the problem of planar maximal covering by disks, we called it $MCD$, and proposed a method for it based on previous works that we found.
-This method established the basis of our work, as after defining the ellipses counterpart problem, we developed a method based on that algorithm which needed very little modification.
-To compare results with \cite{andreta}, a small change needs to be done in the algorithm because their version of the problem contains another constraint: out of the $m$ ellipses given, the solution can use exactly $k$ of them.
-This change as well as the comparison of results is left as future work.
+To take advantage of the great amount of works which were found in the literature,
+ we decided to first introduce the planar maximal covering by disks problem, develop a method for it, and just then adapt it for the ellipses case.
+It turned out that because of the similarities between the two problems, adapting was possible and actually very simple.
+This made the method developed by us have a very different approach than the ones in \cite{andreta} and \cite{canbolat}.
+The next step is to implement it and compare the results that \cite{andreta} obtained.
 
-The $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} is also a subject of future work and is set as the primary goal for this master's research.
-We want to develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
+As of future work, we intend to study $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
 
-Also, in \cite{aronov:2008} a Monte Carlo approximation is presented for the problem of finding the deepest point in a arrangement of regions.
-The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse.
-An adaptation for the multiple ellipses case is left as a secondary goal for the final version of this work.
-
-Finally, the version of the problem where every ellipse can be freely rotated is left as a subject of study for the future.
+Also, the version of the problem where every ellipse can be freely rotated is set as a primary goal for this master's research.
 In \cite{andreta}, the deterministic method developed by them could not obtain solutions for moderate-to-large instances within reasonable time.
@@
 The goal we have in mind for the future is to develop an exact method that takes into consideration the algorithm we developed for the axis-parallel version of the problem and compare the results.
+
+Finally, as a secondary goal, we want to develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
+The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse, the case with more than one is left as a challenge for us for the next steps of our research.

### 2019-03-24 tex/chapter/introducao.tex
WIP

@@
 
-This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximal covering by disks problem is studied and a $\bigO(n^{2m})$ is proposed; in \autoref{chapter:ellipses}, the maximal covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work.
-Also, the \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.
+This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximal covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximal covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work.
+Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

### 2019-03-25 tex/chapter/definicoes.tex
WIP

@@
 
-A norm is a function that maps every vector from a vector space onto a non-negative number satisfying some conditions. Here it is defined for the vector space $\R^2$ as follows
+A norm is a function that maps every vector from a vector space onto a non-negative real number satisfying some conditions. Here it is defined for the vector space $\R^2$ as follows
 
@@
 A unit circle is a circle with radius equal to $1$.
-A disk is the set of points of a circle plus its interior, let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.
+A disk is the set of points bounded by a circle, in other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.
 
@@
 As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}.
-From that definition, an equation that describes any conic section is given as follows
+From that definition, an equation which describes any conic section is given as follows
 
@@
 
-Any ellipse, rotated or axis-parallel, can be described by \autoref{equation:quadratic_form}.
 To distinguish an ellipse from the other conic sections given an instance of \autoref{equation:quadratic_form}, the condition $4AC - B^2>0$ can be verified \cite{ayoub}.
@@
 
-This makes us arrive at the following definition of the ellipse
+Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse
 

### 2019-03-25 tex/chapter/ellipses.tex
WIP

@@
 To obtain solutions, not necessarily optimal ones, for the instances which the exact method showed inefficiency, a heuristic technique called Simulated Annealing was used to develop another method.
-Comparisons were made, and the second approach was able to obtain good solutions, compared to the optimal ones found for some of the instances, within a good run-time.
+Comparisons were made which showed that the second approach was able to obtain good solutions, compared to the optimal ones found for some of the instances, within a good run-time.
 

### 2019-03-25 tex/chapter/future.tex
WIP

@@
-To take advantage of the great amount of works which were found in the literature,
+To take advantage of the great amount of work found in the literature,
  we decided to first introduce the planar maximal covering by disks problem, develop a method for it, and just then adapt it for the ellipses case.
@@
 
-As of future work, we intend to study $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
+As of future work, we intend to study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
 

### 2019-03-25 tex/chapter/introducao.tex
WIP

@@
-There are two main types of optimal covering problems found in the literature: the minimum cover problem, also known as just set cover, and the maximal covering problem \cite{karatas}.
+Two main types of optimal covering problems can be found in the literature: the minimum cover problem, also known as just set cover, and the maximal covering problem \cite{karatas}.
 
-One of the 21 Karp's NP-Hard problems \cite{karp}, the minimum cover is considered to be a classic and very well studied problem.
-On it, a demand set has to be covered, and the cost of doing it has to be minimized.
+One of the 21 Karp's NP-Complete problems\footnote{The decision version is NP-Complete, the optimization variant is NP-Hard.} \cite{karp}, the minimum cover is considered to be a classic and very well explored problem.
+On it, covering a demand set, also known as the universe set, has to be minimized whereas covering is accomplished by selecting some elements from a given collection of subsets of the demand set.
 One of its most famous example is the minimum vertex cover defined over graphs where the vertex set has to be covered by a subset of edges.
@@
 In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities are used.
-Just like the minimum cover, \MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed for it.
+Just like the minimum cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed for it.
 
 In \cite{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced.
-This version of the problem was not defined on a network, instead the demand set and the facilities are located in $\R^2$, having the coverage area of a facility be defined by a distance function.
+This version of the problem was not defined on a network, instead the demand set and the facilities are located in $\R^2$ having the coverage area of a facility be defined by a distance function.
 PMCLP is said to have been studied under euclidean and rectilinear distance functions \cite{younies}.
-The euclidean norm PMCLP, which has a lot of results that are applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
-The version where only one disk is used is studied in \cite{chazelle:1986}, a $\bigO(n^2)$ algorithm is proposed, improving the $\bigO(n^2\log{n})$ algorithm that was created in \cite{drezner}.
-Furthermore, in \cite{aronov:2008} a lower bound result is stabilised, it proves that one disk maximal covering is a 3SUM-HARD problem, which means that it is as difficult as finding three real numbers that sum to zero among $n$ given real numbers.
-The version with $m$ unit disks was studied in \cite{cabello:2006} which developed a $\bigO(n^{2m-1}\log{n})$ deterministic algorithm and a $(1-\epsilon)$-approximation method, for any $\epsilon > 0$, that runs in $\bigO(n\log{n})$.
+The euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
+Early works only tackled the one-disk version of the problem, in \cite{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed besting the prior $\bigO(n^2\log{n})$ algorithm created by \cite{drezner}.
+The $m$ unit disks maximal covering was studied in \cite{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
+To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
+Additionally, in \cite{aronov:2008} one-disk maximal covering is proven to be 3SUM-HARD.
+This means that maximizing the amount of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.
 
-The difference between the regular PMCLP and the one studied in this work is that the shape of the coverage area of a facility is determined by an ellipse.
+Planar maximal covering with ellipses differs from its disks counterpart only in the shape of the facility's coverage area.
 The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.
@@
 Also, in \cite{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find the optimal solutions for large instances, and a heuristic method were proposed for it.
+Despite the similarities, none of the works cited above base their development on the maximal covering with disks algorithms found in the literature.
 

### 2019-03-26 tex/chapter/definicoes.tex
WIP

@@
 
-\section{Norm}
+\section{Elliptical and euclidean norm functions}
 
-A norm is a function that maps every vector from a vector space onto a non-negative real number satisfying some conditions. Here it is defined for the vector space $\R^2$ as follows
-
-\begin{definicao}
-Let $\xi : \R^2 \mapsto [0, \infty]$, $\xi$ is said to be a norm function of $\R^2$ if for any $p, q \in \R^2$ and $a \in \R$,
-
-\begin{enumerate}
-    \item $\xi(p + q) \le \xi(p) + \xi(q)$
-    \item $\xi(ap) = |a|\xi(p)$
-    \item if $\xi(p)=0$, then $p=0$
-\end{enumerate}
-
-\end{definicao}
-
-\subsection{Elliptical and euclidean norm functions}
+A norm in $\R^2$ is a function that maps every vector onto a non-negative real number satisfying homogeneity and the triangle inequality.
 
@@
 \begin{equation}\label{eq:norm2}
-||u||_2 = \sqrt{u^{T}u}
+||u||_2 = \sqrt{u^{T}u},
 \end{equation}
 
-The elliptical norm takes a $2$ by $2$ positive definite matrix as its parameter.
+\noindent the elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
 This matrix can be seen as a linear transformation of the euclidean norm.
-Let $u \in \R^2$ be a vector and $Q$ be a $2$ by $2$ positive definite matrix, the elliptical norm of $u$ is defined as
+Let $u \in \R^2$ be a vector, the elliptical norm of $u$ is defined as
 
 \begin{equation}
-||u||_{elliptical} = \sqrt{u^{T}Qu}
+||u||_{Q} = \sqrt{u^{T}Qu},
 \end{equation}
+
+\noindent where $Q$ is a $2$ by $2$ positive definite matrix.
 
@@
 Determining the distance between two points, given a norm function is done by calculating the norm of the vector defined by the difference between the two points.
-For example, the elliptical distance between the points $p,q \in \R^2$ is given by $||p-q||_{elliptical}$.
+For example, the elliptical distance between the points $p,q \in \R^2$ is given by $||p-q||_{Q}$.
 
@@
 A unit circle is a circle with radius equal to $1$.
-A disk is the set of points bounded by a circle, in other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.
+
+A disk is the set of points bounded by a circle. In other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.
 
@@
 
-The ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section.
+An ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section.
 As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}.
@@
 \begin{equation}\label{equation:quadratic_form}
-Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0
+Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0,
 \end{equation}
 
-To distinguish an ellipse from the other conic sections given an instance of \autoref{equation:quadratic_form}, the condition $4AC - B^2>0$ can be verified \cite{ayoub}.
+\noindent where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$.
+
+To distinguish an ellipse from the other conic sections given an instance of \autoref{equation:quadratic_form}, the condition $4AC - B^2>0$ must be verified \cite{ayoub}.
 
@@
 \begin{equation}
-(p-c)^{T}Q(p-c) = 1
+(p-c)^{T}Q(p-c) = 1,
 \end{equation}
 
-with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
+\noindent with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
 
@@
 
-Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse
+Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse,
 
 \begin{definicao}\label{def:ellipse}
-    Let $c\in \R^2$ be the center of an ellipse and $Q$ be a $2$ by $2$ positive definite matrix, an ellipse is the set of every point $p \in \R^2$ that have $||p-c||_{elliptical}^2 = (p-c)^{T}Q(p-c) = 1$.
-Also, a point $p$ is considered covered by an ellipse if $||p-c||_{elliptical}^2 = (p-c)^{T}Q(p-c) \le 1$.
+    Let $c\in \R^2$ be the center of an ellipse and $Q$ be a $2$ by $2$ positive definite matrix.
+An ellipse is the set of every point $p \in \R^2$ that have $||p-c||_{Q}^2 = (p-c)^{T}Q(p-c) = 1$.
+Also, a point $p$ is considered covered by an ellipse if $||p-c||_{Q}^2 = (p-c)^{T}Q(p-c) \le 1$.
 \end{definicao}
@@
 
-Also, in \autoref{fig:ellipse_with_foci}, the distance $a = ||p_a - c||_2$ is called the semi-major, and the distance $b = ||p_b-c||_2$ is called the semi-minor.
+Also, in \autoref{fig:ellipse_with_foci}, the distance $a = ||p_a - c||_2$, where $p_a$ is one of the intersection points of the ellipse with the major axis, is called the semi-major, and the distance $b = ||p_b-c||_2$, where $p_b$ is one of the intersection points of the ellipse with the minor axis, is called the semi-minor.
 These two values are also referred to as the shape parameters of an ellipse.
@@
 
-An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal}.
+An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal.}.
 This can be understood as a scaling transformation applied to the euclidean norm.
+
 Defining the matrix $Q$ as
@@
     0 & \frac{1}{b^2} \\
-    \end{array} } \right)
+    \end{array} } \right),
 \]
 
-Then, starting from \autoref{def:ellipse}, we can obtain the following equation
+\noindent then, starting from \autoref{def:ellipse}, we can obtain the following equation
 
 \begin{align*}
-        (p-c)^{T}Q(p-c) = 1\\
-    (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) = 1
+        (p-c)^{T}Q(p-c) = 1 & \Rightarrow \\
+    (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) = 1 & \Rightarrow
  \end{align*}
  \begin{equation}\label{equation:pellipse}
-  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} = 1
+  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} = 1,
  \end{equation}
 
-where $a$ and $b$ are the semi-major and semi-minor shape parameters respectively.
+\noindent where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.
 
@@
 \begin{equation}\label{equation:cover_pellipse}
-\frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} \le 1
+\frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} \le 1.
 \end{equation}
@@
     \begin{array}{l}
-    x(t)= a\cos{t} + c_x\\
-    y(t)=b\sin{t} + c_y
+    x(t)= a\cos{t} + c_x,\\
+    y(t)=b\sin{t} + c_y.
     \end{array}
@@
 Throughout this work an ellipse will represent the set of points that satisfy \autoref{def:ellipse}.
-In some places, though, with prior clarification, we will denote as an ellipse, the set of points that are covered by the ellipse itself.
+In some places, though, with prior clarification, we will denote as an ellipse the set of points that are covered by the ellipse itself.
 For example, when we define $\Pp \cap E$ as the set of points in $\Pp$ that are covered by $E$, we are implicitly calling $E$ the set of points that are covered by the ellipse itself as it is defined by \autoref{def:ellipse}.

### 2019-03-26 tex/chapter/ellipses.tex
WIP

--- 2019-03-23 tex/chapter/ellipses.tex
@@
 In this chapter, two versions of the planar maximal covering by ellipses problem will be introduced.
-First, the axis-parallel variant will be defined and a method for it will be developed.
-Second, the version where there is no axis-parallel constraint and the ellipses can be freely rotated will be introduced.
+Firstly, the axis-parallel variant will be defined and a method for it will be developed.
+Secondly, the version where there is no axis-parallel constraint and the ellipses can be freely rotated will be introduced.
 
@@
 To obtain solutions, not necessarily optimal ones, for the instances which the exact method showed inefficiency, a heuristic technique called Simulated Annealing was used to develop another method.
-Comparisons were made, and the second approach was able to obtain good solutions, compared to the optimal ones found for some of the instances, within a good run-time.
+Comparisons were made, which showed that the second approach was able to obtain good solutions, compared to the optimal ones found for some of the instances, within a good run-time.
 
-The second work found in the literature was \cite{andreta} which developed a method that breaks the problem into smaller ones fixing the set of points an ellipse is going to cover.
+The second work found in the literature was \cite{andreta}, which developed a method that breaks the problem into smaller ones fixing the set of points an ellipse is going to cover.
 For each set of points fixed as the points an ellipse is going to cover, a small optimization problem is solved to find out if there is a location where the ellipse can be placed, so to cover the set of fixed points.
@@
 
-Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$, is a pair of real numbers called the shape parameters of an ellipse.
-In the general case every point has weights, but without loss of generality (later explained), this detail will be ignored and the weights are assumed to be unitary.
+Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$ is a pair of real numbers called the shape parameters of an ellipse.
+In the general case, every point has weights, but without loss of generality (later explained), this detail will be ignored and the weights are assumed to be unitary.
 The notation used here is similar to the one introduced on \autoref{chapter:pmclp}, the ellipse with an undefined center is referred to as $E$.
 To denote the ellipse with center set to be at point $q$, $E(q)$ is used.
-Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse}, in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$.
+Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse} (in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$).
 Hence, the problem can be defined as follows
@@
 \begin{equation}
-    \max_q |\Pp \cap E(q)|
+    \max_q |\Pp \cap E(q)|.
 \end{equation}
@@
 
-The adaptation of \autoref{algoritmo:mcd_1} is obtained by just replacing the function that finds the intersection points between two disks by a function that finds the intersection points between two ellipses.
+An adaptation of \autoref{algoritmo:mcd_1} is obtained by just replacing the function that finds the intersection points between two disks by a function that finds the intersection points between two ellipses $E_i$ and $E_j$.
 It can be seen in \autoref{fig:3ellipses_intersect} that the intersection points and their correspondents $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ functions behave the same way as in the disks case.
@@
 \begin{equation}
-    max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|}
+    \max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|}.
 \end{equation}
@@
 
-The \autoref{algoritmo:mce} describes the adapted version of the maximal disk covering algorithm for the ellipses case.
+\autoref{algoritmo:mce} describes the adapted version of the maximal disk covering algorithm for the ellipses case.
 The $MCE_1$ procedure returns every possible set of points that an ellipse with shape parameters $(a,b)$ can cover.
-With that, the procedure $MCE$ does the backtracking process, assigning every possible cover to every ellipse.
+With that, procedure $MCE$ does the backtracking process, assigning every possible cover to every ellipse.
 
-As stated in \autoref{lema:disk}, $MCE_1$ runs in $\bigO(n^2\log{n})$.
-The number of sets of points an ellipse can cover, however, is $\bigO(n^2)$, note that the $\log{n}$ is part of the complexity due to sorting the set $A$.
+As stated in \autoref{lema:disk}, $MCE_1$ runs in $\bigO(n^2\log{n})$, where $n$ is the number of points.
+The number of sets of points an ellipse can cover, however, is $\bigO(n^2)$.
+Note that the $\log{n}$ being part of the complexity is due to sorting the set $A$.
 If $MCE_1$ is called only in a pre-process phase storing its return for every ellipse, a $\bigO(n^{2m})$ run-time complexity can be achieved.
@@
 
-\begin{algoritmo}[b]
-\caption{Algorithm for $MCE(\Pp, \E)$ with unit weights}\label{algoritmo:mce}
+\floatname{algorithm}{Procedure}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+
+\begin{algoritmo}[H]
+\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
+%\KwIn{alskdjf}
+
 \begin{algorithmic}[1]
+\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and the shape parameters $(a, b)$ of an ellipse.}
+\Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}
 \Procedure{$MCE_1$}{$\Pp, a, b$}\Comment{Returns every possible coverage.}
-\State $Q \gets \{\}$
+\State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}
 
@@
 
-\State $Q \gets Q \cup \{p_i\}$ 
+\State $Z \gets Z \cup \{\{p_i\}\}$
 \State $Cov \gets \{p_i\}$ \Comment{The set of active disks}
@@
 \EndIf
-\State $Q \gets Q \cup Cov$
+\State $Z \gets Z \cup \{Cov\}$
 \EndFor
@@
 
-\State \Return $Q$
+\State \Return $Z$
 \EndProcedure
 
+\end{algorithmic}
+\end{algoritmo}
+
+\begin{algoritmo}[H]
+    \caption{Algorithm for $MCE(\Pp, \E)$ with unit weights}\label{algoritmo:mce}
+    \begin{algorithmic}[1]
+        \Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and a set of ellipses $\E = \{E_1, \dots, E_m\}$.}
+        \Ensure{The maximum number of points that can be covered by the set of ellipses $\E$.}
         \Procedure{$MCE$}{$\Pp, \E, j=1$}\Comment{Returns an optimal solution of $MCE(\Pp, \E)$, $j$ is a backtracking parameter that says that $j$-th ellipse should be processed by this call.}
@@
         \For{$Cov \in Q$}
-\State $ans \gets \max\{ans, |Cov| + MCE(\Pp \setminus Cov, \E, j+1 \}$ \Comment{Calls the procedure for the next ellipse}
+        \State $ans \gets \max\{ans, |Cov| + MCE(\Pp \setminus Cov, \E, j+1)\}$ \Comment{Calls the procedure for the next ellipse}
         \EndFor

### 2019-03-26 tex/chapter/future.tex
WIP

@@
 Finally, as a secondary goal, we want to develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
-The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse, the case with more than one is left as a challenge for us for the next steps of our research.
+The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse.
+The case with more than one ellipse is left as a challenge for us for the next steps of our research.

### 2019-03-26 tex/chapter/introducao.tex
WIP

@@
-Two main types of optimal covering problems can be found in the literature: the minimum cover problem, also known as just set cover, and the maximal covering problem \cite{karatas}.
+Two main types of optimal covering problems can be found in the literature: the Minimum Cover Problem, also known as just Set Cover Problem, and the Maximal Covering Problem \cite{karatas}.
 
-One of the 21 Karp's NP-Complete problems\footnote{The decision version is NP-Complete, the optimization variant is NP-Hard.} \cite{karp}, the minimum cover is considered to be a classic and very well explored problem.
-On it, covering a demand set, also known as the universe set, has to be minimized whereas covering is accomplished by selecting some elements from a given collection of subsets of the demand set.
-One of its most famous example is the minimum vertex cover defined over graphs where the vertex set has to be covered by a subset of edges.
+One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic.
+Given a demand set and collection of subsets of the demand set, the problem asks what is the minimum number of elements from the collection of subsets needed to cover the whole demand set.
+One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.
 
@@
 This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \cite{church:1974}.
-In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities are used.
-Just like the minimum cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed for it.
+In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used.
+Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, (using integer programming) \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed to solve it.
 
@@
 This version of the problem was not defined on a network, instead the demand set and the facilities are located in $\R^2$ having the coverage area of a facility be defined by a distance function.
-PMCLP is said to have been studied under euclidean and rectilinear distance functions \cite{younies}.
-The euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
+PMCLP is said to have been studied under Euclidean and rectilinear distance functions \cite{younies}.
+The Euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
 Early works only tackled the one-disk version of the problem, in \cite{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed besting the prior $\bigO(n^2\log{n})$ algorithm created by \cite{drezner}.

### 2019-03-27 tex/chapter/pmclp.tex
WIP

@@
     \begin{equation}\label{eq:max_one_disk}
-        \max_q w(\Pp \cap D(q))
+        \max_q w(\Pp \cap D(q)).
     \end{equation}
@@
     \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection}
-    \begin{tikzpicture}[domain=0:11]
+    \begin{tikzpicture}[scale=0.55]
     %\draw [help lines] (-5,-3) grid (5,3);
@@
 
-    \node[below] at (0,0) {$p_1$};
-    \node[below] at (0.9, 1.6) {$p_2$};
-    \node[below] at (-0.9, 1.6) {$p_3$};
+    \node[below] at (0,0) {\tiny $p_1$};
+    \node[below] at (0.9, 1.6) {\tiny $p_2$};
+    \node[below] at (-0.9, 1.6) {\tiny $p_3$};
 
@@
 A solution for the maximum weight clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized.
-Even though, there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the maximum weight clique is enough.
+Even though there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the maximum weight clique is enough.
 This will become clear when the equivalence is stated.
@@
     \begin{equation}
-        \max_q \sum_{D_k \cap q \neq \emptyset} w_k
+        \max_q \sum_{D_k \cap q \neq \emptyset} w_k.
     \end{equation}
@@
 With \autoref{def:inter_arc} in hands, we can establish the basis of the algorithm to find the maximum clique that a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$ in counter-clockwise order keeping a set of active disks, when an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
-This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$, see \autoref{fig:3disks_intersect}.
-If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it, if there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and the optimal solution could end up not being found.
+This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ (see \autoref{fig:3disks_intersect}).
+If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it.
+If there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and the optimal solution could end up not being found.
 This can be worked around repeating the traversal once without resetting the active disks set, that way in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$.
+This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal repetition (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
+It can be seen that without the repetition, the algorithm would find $2$ as the value of an optimal solution, which is wrong.
+
+\begin{figure}[H]
+    \centering
+
+    \caption{The intersections list of a disk with three other disks.}
+    \input{tex/figures/fig:array_disks.tex}
+    \fautor
+    \label{fig:array_disks}
+\end{figure}
 
@@
 \State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
-
 \State $Q \gets \{D_i\}$ \Comment{The set of active disks}
@@
 
-For the case with $m>1$, a simple backtracking algorithm can be developed, considering every possible solution for every one of the $m$ unit disks.
-In any solution, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the maximum weight clique problem.
-The point $q$ is inside a intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by the algorithm as a candidate to be the optimal solution.
-Therefore, the \autoref{algoritmo:mcd_1} can be adapted to serve the backtracking that searches for an optimal solution of $MCD(\Pp, m)$.
-Then, as for every disk there are $\bigO(n^2)$ possible centers, the overall complexity of the backtracking algorithm is $\bigO(n^{2m})$.
+In \cite{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD(\Pp, m)$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.
+Firstly, they solve the sub-problem $MCD(\Pp, 2)$ in $\bigO(n^3\log{n})$.
+Then for the rest of the points that are not in that solution, it uses the algorithm developed in \cite{chazelle:1986} for the one-disk case checking every possible solution for every one of the disks left.
+
+It can be seen that in any solution of $MCD(\Pp, m)$, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the maximum weight clique problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be the optimal solution.
+The number of points \autoref{algoritmo:mcd_1} goes through is $\bigO(n^2)$, then checking every possible center for every ellipse yields a $\bigO(n^{2m})$ run-time complexity.
+This algorithm is described in \autoref{chapter:ellipses} for the ellipses case.
+
+The choice of developing a different method for the problem, instead of using the one from \cite{cabello:2006}, is taken for the sake of simplicity considering both algorithms achieve similar bounds.

### 2019-03-27 tex/figures/fig:array_disks.tex
WIP

\usetikzlibrary{matrix}

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95

%Shape: Circle [id:dp37777408295388804] 
\draw   (21,59.5) .. controls (21,45.69) and (32.19,34.5) .. (46,34.5) .. controls (59.81,34.5) and (71,45.69) .. (71,59.5) .. controls (71,73.31) and (59.81,84.5) .. (46,84.5) .. controls (32.19,84.5) and (21,73.31) .. (21,59.5) -- cycle ;
%Shape: Circle [id:dp4562198988843913] 
\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) .. controls (47.5,33.14) and (58.69,21.94) .. (72.5,21.94) .. controls (86.31,21.94) and (97.5,33.14) .. (97.5,46.94) .. controls (97.5,60.75) and (86.31,71.94) .. (72.5,71.94) .. controls (58.69,71.94) and (47.5,60.75) .. (47.5,46.94) -- cycle ;
%Shape: Circle [id:dp8913971633985722] 
\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (33,53.5) .. controls (33,39.69) and (44.19,28.5) .. (58,28.5) .. controls (71.81,28.5) and (83,39.69) .. (83,53.5) .. controls (83,67.31) and (71.81,78.5) .. (58,78.5) .. controls (44.19,78.5) and (33,67.31) .. (33,53.5) -- cycle ;
%Shape: Circle [id:dp05970043129919356] 
\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) .. controls (57.81,18.66) and (69,7.47) .. (82.81,7.47) .. controls (96.62,7.47) and (107.81,18.66) .. (107.81,32.47) .. controls (107.81,46.27) and (96.62,57.47) .. (82.81,57.47) .. controls (69,57.47) and (57.81,46.27) .. (57.81,32.47) -- cycle ;
%Straight Lines [id:da04725899028195979] 
%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;

%Flowchart: Extract [id:dp5267407418119328] 
\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

% Text Node
\draw (20,35) node [scale=0.5]  {$E_{1}$};
\end{tikzpicture}

\begin{tikzpicture}

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

\node at (-4,-0.5) {$0$};
\node at (0,-0.5) {$2\pi$};
\end{tikzpicture}

### 2019-03-29 tex/chapter/ellipses.tex
WIP

@@
-In this chapter, two versions of the planar maximal covering by ellipses problem will be introduced.
+In this chapter, two versions of the Planar Maximal Covering by Ellipses Problem will be introduced.
 Firstly, the axis-parallel variant will be defined and a method for it will be developed.
@@
 The maximal planar covering using axis-parallel ellipses was first introduced in \cite{canbolat} which proposed a mixed integer non-linear programming method for the problem.
-This first approach showed to be not that efficient as it could not find the optimal solution for some instances within a timeout defined by them.
+This first approach showed to be not that efficient as it could not find an optimal solution for some instances within a timeout defined by them.
 To obtain solutions, not necessarily optimal ones, for the instances which the exact method showed inefficiency, a heuristic technique called Simulated Annealing was used to develop another method.
@@
 For each set of points fixed as the points an ellipse is going to cover, a small optimization problem is solved to find out if there is a location where the ellipse can be placed, so to cover the set of fixed points.
-To enumerate the possible solutions and then find the optimal one, the method defined a data structure that stores every set of points an ellipse can cover.
-This method showed better results and was able to find the optimal solutions for the instances that the first method could not get as well as for new created instances.
+To enumerate the possible solutions and then find an optimal one, the method defined a data structure that stores every set of points an ellipse can cover.
+This method showed better results and was able to find optimal solutions for the instances that the first method could not get as well as for new created instances.
 
@@
 Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse} (in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$).
-Hence, the problem can be defined as follows
+Hence, the problem can be defined as follows.
 
@@
 \autoref{algoritmo:mce} describes the adapted version of the maximal disk covering algorithm for the ellipses case.
-The $MCE_1$ procedure returns every possible set of points that an ellipse with shape parameters $(a,b)$ can cover.
+In \autoref{algoritmo:mce1}, the $MCE_1$ procedure returns every possible set of points that an ellipse with shape parameters $(a,b)$ can cover.
 With that, procedure $MCE$ does the backtracking process, assigning every possible cover to every ellipse.
@@
 For example, if an ellipse covers two sets of points $X$ and $Y$, with $X \subset Y$, then set $X$ can be ignored by the algorithm because of the positive weights constraint.
-Also, if two ellipses have their centers with euclidean distance greater than their semi-major parameter, they for sure do not intersect.
+Also, if two ellipses have their centers with Euclidean distance greater than their semi-major parameter, they for sure do not intersect.
 Depending on the input, this observation can make the algorithm not go through the whole list of ellipses every time it needs to determine the ellipses pairwise intersections.
 
-\floatname{algorithm}{Procedure}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-
-\begin{algoritmo}[H]
+\begin{algoritmo}
 \caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
@@
 \Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}
-\Procedure{$MCE_1$}{$\Pp, a, b$}\Comment{Returns every possible coverage.}
+
+\item[]
+\Procedure{$MCE_1$}{$\Pp, a, b$}
 \State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}
@@
 
-\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
+%\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $E_i$}
+
+\State $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$ \Comment{The multiset of intersection angles with $E_i$.}
+
+%\ForAll{$j \in I_i$}
+%\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
+%\EndFor
 
 \State $Z \gets Z \cup \{\{p_i\}\}$
-\State $Cov \gets \{p_i\}$ \Comment{The set of active disks}
+\State $Cov \gets \{p_i\}$ \Comment{The set of active disks.}
 
-\For{$cnt=1..2$} \Comment{Do it twice}
-\For{$a \in A$}\Comment{Assuming $A$ is sorted}
+\For{$cnt=1..2$} \Comment{Do it twice.}
+\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
 \State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
@@
 
-\begin{algoritmo}[H]
+\begin{algoritmo}
     \caption{Algorithm for $MCE(\Pp, \E)$ with unit weights}\label{algoritmo:mce}
@@
         \Ensure{The maximum number of points that can be covered by the set of ellipses $\E$.}
-        \Procedure{$MCE$}{$\Pp, \E, j=1$}\Comment{Returns an optimal solution of $MCE(\Pp, \E)$, $j$ is a backtracking parameter that says that $j$-th ellipse should be processed by this call.}
+
+        \item[]
+
+        \Procedure{$MCE$}{$\Pp, \E, j=1$}
         \If{$j = m+1$}
@@
         \For{$Cov \in Q$}
-        \State $ans \gets \max\{ans, |Cov| + MCE(\Pp \setminus Cov, \E, j+1)\}$ \Comment{Calls the procedure for the next ellipse}
+        \State $ans \gets \max\{ans, |Cov| + MCE(\Pp \setminus Cov, \E, j+1)\}$ \Comment{Calls the procedure for the next ellipse.}
         \EndFor

### 2019-04-23 tex/appendix/ellipse_intersection.tex
WIP

@@
 
-It is worth noting that computationally, this classification can be done taking the cross product of the two vectors and checking its signal, negative cross products imply an angle greater than $\pi$.
+%It is worth noting that computationally, this classification can be done taking the cross product of the two vectors and checking its signal, negative cross products imply an angle greater than $\pi$.
 Also, determining the polar angle of a point in $\R^2$ can be done using the $atan2(x,y)$ function which is present in most of the math libraries of modern programming languages.

### 2019-04-23 tex/chapter/introducao.tex
WIP

@@
 In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used.
-Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, (using integer programming) \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed to solve it.
+Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed to solve it.
 
@@
 The Euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
-Early works only tackled the one-disk version of the problem, in \cite{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed besting the prior $\bigO(n^2\log{n})$ algorithm created by \cite{drezner}.
+Early works only tackled the one-disk version of the problem, in \cite{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \cite{drezner}.
 The $m$ unit disks maximal covering was studied in \cite{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
@@
 In \cite{canbolat}, a mixed non-linear programming method was proposed as a first approach to the problem.
-For some instances the method took too long and did not find the optimal solution.
+For some instances the method took too long and did not find an optimal solution.
 For this reason a heuristic method was developed using a technique called Simulated Annealing, solutions for the instances that timed-out with the first method were then obtained.
-The problem was further explored in \cite{andreta} which proposed a deterministic method that showed better performance obtaining the optimal solutions for the instances which the first method could not.
-Also, in \cite{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find the optimal solutions for large instances, and a heuristic method were proposed for it.
+The problem was further explored in \cite{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances which the first method could not.
+Also, in \cite{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances, and a heuristic method were proposed for it.
 Despite the similarities, none of the works cited above base their development on the maximal covering with disks algorithms found in the literature.

### 2019-04-24 implementation/ellipses_intersection.jl
Add implementation

@@ -1,0 +1,61 @@
+using Printf
+
+struct Point
+	x::Real
+	y::Real
+end
+
+struct Ellipse
+    a::Real
+    b::Real
+    center::Point
+end
+
+function root2(a::Real, b::Real, c::Real)::Union{Bool, Tuple{Real,Real}}
+	Δ = b^2 - 4*a*c
+	if (Δ < 0)
+		return false
+	end
+
+	return (-b + √Δ) / 2*a, (-b-√Δ)/2*a
+end
+
+#Assumes that e_a.a === e_2.a
+function intersection(e_1::Ellipse, e_2::Ellipse)::Union{Bool,Tuple{Point,Point}}
+	h::Real = e_2.center.x - e_1.center.y
+	k::Real = e_2.center.y - e_1.center.y
+	a::Real = e_1.a
+	b::Real = e_1.b
+
+	α = (-2*k*a^2)/(2*h*b^2)
+	β = (b^2*h^2 + a^2*k^2) / (2*h*b^2)
+	
+	ro = root2(b^2*α^2+a^2, 2*β*α*b^2, b^2*β^2 - a^2*b^2)
+
+	if (ro === false)
+		return false
+	end
+	
+	y_1, y_2 = ro
+
+	x_1 = y_1*α + β
+	x_2 = y_2*α + β
+
+	return Point(x_1,y_1), Point(x_2,y_2)
+end
+
+function main()
+	ret = intersection(Ellipse(3, 2, Point(0,0)), Ellipse(3,2,Point(1,1)))
+
+	if (ret === false)
+		return
+	end
+
+	p1, p2 = ret
+
+	@printf("%.3f %.3f\n", p1.x, p1.y)
+
+	return ret
+end
+
+main()

### 2019-04-24 quali/quali.presentation/slides.tex
Refactoring

\documentclass{beamer}

\mode<presentation>{
\usetheme{Madrid}
%\usecolortheme{beaver}
}
\usepackage[utf8]{inputenc}
%\usepackage{default}
%\usepackage[portuguese]{babel}
%\usepackage{pgfplots}
%\pgfplotsset{/pgf/number format/use comma,compat=newest}
%\usepackage{color}
\usepackage{amsfonts}
\usepackage{mathrsfs}

%\usepackage{hyperref}
%\usepackage{tikz}

%MEUS COMANDOs
\newcommand{\R}{\mathbb{R}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}

\newcommand{\bigO}{\mathscr{O}}

\title[Qualificação de Mestrado]{Planar Maximal Covering with Ellipses}
\author[Tedeschi, D. F.]{Danilo F. Tedeschi}
\institute[ICMC]{Instituto de Ciências Matemáticas e Computação}
\date{\today}

\begin{document}

\begin{frame}
 \maketitle
\end{frame}

\begin{frame}
\frametitle{Sumário}
 \tableofcontents
\end{frame}

\section{Introdução}
\begin{frame}
\frametitle{Introdução}
\begin{itemize}
	\item Problemas de cobertura
	\begin{itemize}
		%\item Cobertura mínima
		\item Cobertura maximal
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item Um disco: algoritmos $\bigO(n^2)$ e $\bigO(n^2\log{n})$
	\item $m$ discos: algoritmo $\bigO(n^{2m-1}\log{n})$
	\end{itemize}
	\item Objetivos
	\begin{itemize}
		\item Desenvolver algoritmo $\bigO(n^2\log{n})$ para um disco
		\item Adaptar o algoritmo para o caso com $m$ ellipses
	\end{itemize}
\end{itemize}

\end{frame}

\section{Preliminares}

\begin{frame}
	\frametitle{Preliminares}
	\begin{block}{Norma Euclidiana}
		Seja $u \in \R^2$

		\begin{equation*}
		||u||_2 = \sqrt{u^Tu}
		\end{equation*}

	\end{block}

\begin{block}{Norma Elíptica}
	Seja $u \in \R^2$ e $Q$ uma matriz $2x2$ positiva definida

	\begin{equation*}
	||u||_{Q} = \sqrt{u^TQu}
	\end{equation*}
\end{block}
\end{frame}

\begin{frame}{Preliminares}
	\begin{block}{Disco}
		content...
	\end{block}

	\begin{block}{Ellipse}
		content...
	\end{block}
\end{frame}

\section{Cobertura Maximal por Discos}
\begin{frame}{Cobertura maximal por discos}{Um disco}
	content... trabalhos passados e motivacao
\end{frame}

\section{Cobertura Maximal por Discos}
\begin{frame}{Cobertura maximal por discos}{Um disco}
	content... meu algoritmo
\end{frame}

\section{Cobertura Maximal por Ellipses}

\begin{frame}{Cobertura Maximal por Ellipses}
	content... trabalhos passados
\end{frame}

\begin{frame}{Cobertura Maximal por Ellipses}{$m$ elipses}
	content... algoritmo
\end{frame}

\section{Trabalhos Futuros}

\begin{frame}{Trabalhos Futuros}

\end{frame}
\end{document}

### 2019-04-24 quali/tex/appendix/ellipse_intersection.tex
Refactoring

--- 2019-04-23 tex/appendix/ellipse_intersection.tex
@@
     x(2hb^2) = b^2h^2 + a^2(-2yk + k^2)\\
-    x = y\frac{-2yka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2}
+    x = y\frac{-2ka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2}
 \end{align*}
@@
 \begin{align*}
-    \alpha = \frac{-2yka^2}{2hb^2} \\
+    \alpha = \frac{-2ka^2}{2hb^2} \\
     \beta = \frac{b^2h^2 + a^2k^2}{2hb^2}

### 2019-04-24 quali/tex/chapter/definicoes.tex
Refactoring

--- 2019-03-26 tex/chapter/definicoes.tex
@@
 
-\section{Elliptical and euclidean norm functions}
+\section{Elliptical and Euclidean norm functions}
 
@@
 
-Let $u \in \R^2$ be a vector, the euclidean norm of $u$ is defined as
+Let $u \in \R^2$ be a vector, the Euclidean norm of $u$ is defined as
 
@@
 \noindent the elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
-This matrix can be seen as a linear transformation of the euclidean norm.
+This matrix can be seen as a linear transformation of the Euclidean norm.
 Let $u \in \R^2$ be a vector, the elliptical norm of $u$ is defined as
@@
 
-It is easy to see that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the euclidean norm.
+It is easy to see that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.
 
@@
 
-A circle (or circumference) is a set of points in $\R^2$ that have constant euclidean distance, also known as radius, to another point, also referred to as the center of the circle.
+A circle (or circumference) is a set of points in $\R^2$ that have constant Euclidean distance, also known as radius, to another point, also referred to as the center of the circle.
 A unit circle is a circle with radius equal to $1$.
 
-A disk is the set of points bounded by a circle. In other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy \autoref{eq:disk}.
+A disk is the set of points bounded by a circle. In other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy
 
 \begin{equation}\label{eq:disk}
-||p-c||_2^2 \le 1
+||p-c||_2^2 \le 1.
 \end{equation}
@@
 
-An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin its construction with two points called foci and a constant $R \in \R$, with $R$ being greater than the euclidean distance between the two foci points (see \autoref{fig:ellipse_with_foci}).
+An alternative way to define an ellipse, which can be seen as just a property derived from the definition above, is to begin its construction with two points called foci and a constant $R \in \R$, with $R$ being greater than the Euclidean distance between the two foci points (see \autoref{fig:ellipse_with_foci}).
 The ellipse is, then, defined as the set of points whose distance to the foci is equal to $R$.
@@
 An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal.}.
-This can be understood as a scaling transformation applied to the euclidean norm.
+This can be understood as a scaling transformation applied to the Euclidean norm.
 
@@
 
-    \caption{The ellipse as a parametric curve}
+    \caption{The ellipse as a parametric curve.}
     \input{tex/figures/ellipse_definition.tex}

### 2019-04-24 quali/tex/figures/ellipse_gamma.tex
Refactoring

--- 2019-03-21 tex/figures/ellipse_gamma.tex
@@
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+%\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
 
 \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,193); %set diagram left start at 0, and has height of 193
+every edge quotes/.append style = {anchor=south, sloped}
+
+%uncomment if require: \path (0,191); %set diagram left start at 0, and has height of 191
 
@@
 %Straight Lines [id:da36505632658461096] 
-\draw    (236,53) -- (185.87,33.72) ;
+\draw    (234,52) -- (185.87,33.72) ;
 \draw [shift={(184,33)}, rotate = 381.03999999999996] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
@@
 %Straight Lines [id:da357569598162492] 
-\draw    (234,52) -- (182.95,63.56) ;
-\draw [shift={(181,64)}, rotate = 347.24] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw    (234,52) -- (286.05,39.95) ;
+\draw [shift={(288,39.5)}, rotate = 526.97] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 %Straight Lines [id:da9574900886541131] 
-\draw    (212,149) -- (257.1,164.11) ;
-\draw [shift={(259,164.75)}, rotate = 198.53] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw    (212,149) -- (173.91,137.34) ;
+\draw [shift={(172,136.75)}, rotate = 377.03] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 
-%Shape: Arc [id:dp33725313902395126] 
-\draw  [draw opacity=0][line width=0.75]  (219.73,152.25) ..
-controls (218.31,154.08) and (215.71,155.31) ..
-(212.73,155.31) ..
-controls (208.24,155.31) and (204.6,152.51) ..
-(204.6,149.06) ..
-controls (204.6,145.61) and (208.24,142.81) ..
-(212.73,142.81) ..
-controls (216.16,142.81) and (219.09,144.44) ..
-(220.29,146.74) -- (212.73,149.06) -- cycle ; \draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=0.75]  (219.73,152.25) ..
-controls (218.31,154.08) and (215.71,155.31) ..
-(212.73,155.31) ..
-controls (208.24,155.31) and (204.6,152.51) ..
-(204.6,149.06) ..
-controls (204.6,145.61) and (208.24,142.81) ..
-(212.73,142.81) ..
-controls (216.16,142.81) and (219.09,144.44) ..
-(220.29,146.74) ;
-%Shape: Arc [id:dp6533092564639917] 
-\draw  [draw opacity=0] (216.22,56.17) ..
-controls (213.28,54.85) and (212,51.09) ..
-(213.38,47.64) ..
-controls (213.78,46.63) and (214.38,45.75) ..
-(215.09,45.04) -- (218.98,49.88) -- cycle ; \draw   (216.22,56.17) ..
-controls (213.28,54.85) and (212,51.09) ..
-(213.38,47.64) ..
-controls (213.78,46.63) and (214.38,45.75) ..
-(215.09,45.04) ;
-
 % Text Node
@@
 % Text Node
-\draw (164,70) node [scale=0.7]  {$\gamma _{2} '( t_{2})$};
-% Text Node
-\draw (202,50) node [scale=0.5]  {$\theta $};
+\draw (312.5,36.5) node [scale=0.7]  {$-\gamma _{2} '( t_{2})$};
 % Text Node
@@
 % Text Node
-\draw (286,170) node [scale=0.7]  {$\gamma _{2} '( t_{1})$};
-% Text Node
-\draw (206.67,136.67) node [scale=0.5]  {$\theta $};
+\draw (147,134) node [scale=0.7]  {$-\gamma _{2} '( t_{1})$};
 % Text Node
@@
 
+\coordinate (O) at (212,149) ;
+\coordinate (A) at (261.53,140.1) ;
+\coordinate (B) at (173.91,137.34) ;
+
+\coordinate (O2) at (234,52);
+\coordinate (A2) at (185.87,33.72);
+\coordinate (B2) at (286.05,39.95);
+
+\draw (214,130) node [scale=0.7]  {$\theta$};
+
+\draw pic[draw=black, -, angle eccentricity=1.2, angle radius=0.2cm]
+{angle=A--O--B};
+
+\draw pic[draw=black, -, angle eccentricity=1.2, angle radius=0.2cm]
+{angle=A2--O2--B2};
+
 \end{tikzpicture}

### 2019-04-24 implementation/GeometryBase.jl

@@ -1,0 +1,28 @@
+module GeometryBase 
+
+export Point, Ellipse
+
+struct Point
+	x::Real
+	y::Real
+end
+
+struct Ellipse
+    a::Real
+    b::Real
+    center::Point
+	fx::Function
+	fy::Function
+
+	Ellipse(a::Real, b::Real, cx::Real, cy::Real) = Ellipse(a,b,Point(cx,cy))
+
+	Ellipse(a::Real, b::Real, c::Point) = 
+	begin 
+		if (a<=0 || b<=0)
+			return error("Invalid ellipse parameters")
+		end
+
+		return new(a,b,c, t-> c.x + a * cos(t), t-> c.y + b * sin(t))
+	end
+end
+end

### 2019-04-24 implementation/ellipses_intersection.jl

@@ -1,39 +1,33 @@
-using Printf
+using GeometryBase
 
-struct Point
-	x::Real
-	y::Real
-end
-
-struct Ellipse
-    a::Real
-    b::Real
-    center::Point
-end
-
-function root2(a::Real, b::Real, c::Real)::Union{Bool, Tuple{Real,Real}}
+function root2(a::Real, b::Real, c::Real)::Union{Nothing, Tuple{Real,Real}}
 	Δ = b^2 - 4*a*c
+
 	if (Δ < 0)
-		return false
+		return nothing 
+	end
+
+	if (a==0)
+		return (-c / b, -c / b)
 	end
 
 	return (-b + √Δ) / 2*a, (-b-√Δ)/2*a
 end
 
 #Assumes that e_a.a === e_2.a
-function intersection(e_1::Ellipse, e_2::Ellipse)::Union{Bool,Tuple{Point,Point}}
+function intersection(e_1::Ellipse, e_2::Ellipse)::Union{Nothing,Tuple{Point,Point}}
 	h::Real = e_2.center.x - e_1.center.y
 	k::Real = e_2.center.y - e_1.center.y
 	a::Real = e_1.a
 	b::Real = e_1.b
 
-	α = (-2*k*a^2)/(2*h*b^2)
+	α = (-2k*a^2)/(2h*b^2)
 	β = (b^2*h^2 + a^2*k^2) / (2*h*b^2)
 	
 	ro = root2(b^2*α^2+a^2, 2*β*α*b^2, b^2*β^2 - a^2*b^2)
 
-	if (ro === false)
-		return false
+	if (ro === nothing)
+		return nothing 
 	end
 	
 	y_1, y_2 = ro
@@ -43,19 +37,3 @@ function intersection(e_1::Ellipse, e_2::Ellipse)::Union{Bool,Tuple{Point,Point}
 
 	return Point(x_1,y_1), Point(x_2,y_2)
 end
-
-function main()
-	ret = intersection(Ellipse(3, 2, Point(0,0)), Ellipse(3,2,Point(1,1)))
-
-	if (ret === false)
-		return
-	end
-
-	p1, p2 = ret
-
-	@printf("%.3f %.3f\n", p1.x, p1.y)
-
-	return ret
-end
-
-main()

### 2019-04-24 implementation/main.jl

@@ -1,0 +1,32 @@
+push!(LOAD_PATH, pwd())
+
+using Plots
+using Printf
+using GeometryBase
+
+include("ellipses_intersection.jl")
+
+function main()
+
+	e₁ = Ellipse(3,2,0,0)
+	e₂ = Ellipse(3,2,1,1)
+
+	ret = intersection(e₁, e₂)
+
+	if (ret === nothing)
+		return nothing
+	end
+
+	p₁, p₂ = ret
+
+	@printf("%.3f %.3f\n", p₁.x, p₁.y)
+
+	plt = plot(e₁.fx, e₁.fy, 0, 2π)
+	plot!(e₂.fx, e₂.fy, 0, 2π)
+	plot!([p₁.x, p₂.x], [p₁.y, p₂.y], seriestype=:scatter)
+	savefig(plt, "a.png")
+
+	return ret
+end
+
+main()

### 2019-04-24 implementation/ellipses_intersection.jl
WIP

@@ -21,16 +21,20 @@ function intersection(e_1::Ellipse, e_2::Ellipse)::Union{Nothing,Tuple{Point,Poi
 	a::Real = e_1.a
 	b::Real = e_1.b
 
-	α = (-2k*a^2)/(2h*b^2)
-	β = (b^2*h^2 + a^2*k^2) / (2*h*b^2)
+	α = (-2k*a²)/(2h*b²)
+	β = (b²h² + a²k²) / (2h*b²)
 	
-	ro = root2(b^2*α^2+a^2, 2*β*α*b^2, b^2*β^2 - a^2*b^2)
+	ro = root2(b²α²+a², 2β*α*b², b²*β² - a²*b²)
 
 	if (ro === nothing)
 		return nothing 
 	end
 	
 	y_1, y_2 = ro
+
+	@show(y_1, y_2)
+	@show(b²α²+a², 2β*α*b², b²*β² - a²*b²)
+
 
 	x_1 = y_1*α + β
 	x_2 = y_2*α + β

### 2019-04-25 quali/quali.presentation/slides.tex
WIP

@@
 %\usepackage{hyperref}
-%\usepackage{tikz}
+\usepackage{tikz}
+\usetikzlibrary{quotes, angles, intersections}
 
@@
 \begin{frame}
-\frametitle{Sumário}
+\frametitle{Contents}
  \tableofcontents
@@
 \begin{itemize}
-	\item Problemas de cobertura
+	\item Covering problems
 	\begin{itemize}
-		%\item Cobertura mínima
-		\item Cobertura maximal
+		\item Set Cover Problem
+		\item Maximal Covering Problem
 	\end{itemize}
@@
 	\begin{itemize}
-	\item Um disco: algoritmos $\bigO(n^2)$ e $\bigO(n^2\log{n})$
-	\item $m$ discos: algoritmo $\bigO(n^{2m-1}\log{n})$
+	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
+	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
 	\end{itemize}
-	\item Objetivos
+	\item Goals
 	\begin{itemize}
-		\item Desenvolver algoritmo $\bigO(n^2\log{n})$ para um disco
-		\item Adaptar o algoritmo para o caso com $m$ ellipses
+		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
+		\item Adapt it for the $m$ ellipses case
 	\end{itemize}
@@
 
-\section{Preliminares}
+\section{Preliminaries}
 
-\begin{frame}
-	\frametitle{Preliminares}
-	\begin{block}{Norma Euclidiana}
-		Seja $u \in \R^2$
+\begin{frame}{Preliminaries}
 
+	\begin{block}{Norms}
+		Let $u \in \R^2$ and $Q$ a $2$ by $2$ positive definite matrix
+		\begin{itemize}
+			\item Euclidean
 			\begin{equation*}
@@
 
-	\end{block}
-
-\begin{block}{Norma Elíptica}
-	Seja $u \in \R^2$ e $Q$ uma matriz $2x2$ positiva definida
-
+			\item Elliptical
 			\begin{equation*}
@@
 			\end{equation*}
+		\end{itemize}
 	\end{block}
+
 \end{frame}
 
-\begin{frame}{Preliminares}
-	\begin{block}{Disco}
-		content...
+\begin{frame}{Preliminaries}
+
+	\begin{block}{Ellipse}
+		Given a center $c \in \R^2$ and a p.d. matrix $Q$, an ellipse is the set of points that satisfy
+
+		\begin{equation*}
+		||u-c||_Q = 1
+		\end{equation*}
+
+		with $\le$ representing the set of covered points
 	\end{block}
 
-	\begin{block}{Ellipse}
-		content...
+	\begin{block}{Axis-parallel ellipse}
+		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by
+
+		\begin{equation*}
+		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1
+		\end{equation*}
 	\end{block}
+
 \end{frame}
 
-\section{Cobertura Maximal por Discos}
-\begin{frame}{Cobertura maximal por discos}{Um disco}
-	content... trabalhos passados e motivacao
+\begin{frame}{Preliminaries}
+	\begin{figure}[H]
+		\centering
+
+		\caption{Three curves representing the points that have distance equal to one.}
+		\input{figures/a.tex}
+		%\fautor
+		\label{fig:3ellipses_intersect}
+	\end{figure}
 \end{frame}
 
-\section{Cobertura Maximal por Discos}
-\begin{frame}{Cobertura maximal por discos}{Um disco}
-	content... meu algoritmo
+\section{Maximal Covering by Disks}
+\begin{frame}{Maximal Covering by Disks}{One disk}
+
+	$MCD(\Pp, 1)$ is the problem of placing one disk on the plane to cover a subset of a demand set $\Pp$ maximizing the weights of the covered points.
+
+	\begin{equation*}\label{eq:max_one_disk}
+		\max_q w(\Pp \cap D(q)),
+	\end{equation*}
+
+	\begin{itemize}
+		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
+		\item $w(A)$, with $A\subset \Pp$ is the sum of weights of the points in $A$
+		\item $D(q)$ is a disk with radius one with center at point $q$
+		\item We will introduce an equivalent problem...
+	\end{itemize}
+\end{frame}
+
+\subsection{Maximum Weight Clique Problem}
+\begin{frame}{Maximum Weight Clique Problem}
+	Let $\D=\{D_1,\dots,D_n\}$ be a set of $n$ unit disks with weights $w_i>0$. The maximum weight clique is defined as
+
+	\begin{equation*}
+	\max_q \sum_{D_k \cap q \neq \emptyset} w_k,
+	\end{equation*}
+
+	\begin{itemize}
+		\item The disks are fixed at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
+		\item A clique is a non-empty intersection area of a subset of disks
+		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
+	\end{itemize}
 \end{frame}

### 2019-04-25 implementation/ellipses_intersection.jl

@@ -11,33 +11,29 @@ function root2(a::Real, b::Real, c::Real)::Union{Nothing, Tuple{Real,Real}}
 		return (-c / b, -c / b)
 	end
 
-	return (-b + √Δ) / 2*a, (-b-√Δ)/2*a
+	return (-b + √Δ) / (2*a), (-b-√Δ)/(2*a)
 end
 
-#Assumes that e_a.a === e_2.a
-function intersection(e_1::Ellipse, e_2::Ellipse)::Union{Nothing,Tuple{Point,Point}}
-	h::Real = e_2.center.x - e_1.center.y
-	k::Real = e_2.center.y - e_1.center.y
-	a::Real = e_1.a
-	b::Real = e_1.b
+#Assumes that e_a.a === e₂.a
+function intersection(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,Point}}
+	h::Float64 = e₂.center.x - e₁.center.y
+	k::Float64 = e₂.center.y - e₁.center.y
+	a::Float64 = e₁.a
+	b::Float64 = e₁.b
 
-	α = (-2k*a²)/(2h*b²)
-	β = (b²h² + a²k²) / (2h*b²)
+	α = (-2k*a^2)/(2h*b^2)
+	β = (b^2*h^2 + a^2*k^2) / (2h*b^2)
 	
-	ro = root2(b²α²+a², 2β*α*b², b²*β² - a²*b²)
+	ro = root2(b^2*α^2+a^2, 2β*α*b^2, b^2*β^2 - a^2*b^2)
 
 	if (ro === nothing)
 		return nothing 
 	end
 	
-	y_1, y_2 = ro
+	y₁, y₂ = ro
 
-	@show(y_1, y_2)
-	@show(b²α²+a², 2β*α*b², b²*β² - a²*b²)
+	x_₁ = y₁*α + β
+	x_₂ = y₂*α + β
 
-
-	x_1 = y_1*α + β
-	x_2 = y_2*α + β
-
-	return Point(x_1,y_1), Point(x_2,y_2)
+	return Point(x_₁,y₁), Point(x_₂,y₂)
 end

### 2019-04-25 implementation/main.jl

@@ -1,3 +1,4 @@
+#Makes julia be able to see GeometryBase
 push!(LOAD_PATH, pwd())
 
 using Plots

### 2019-04-25 quali/quali.presentation/slides.tex
WIP

@@
 %\usepackage{hyperref}
+
+%MEUS COMANDOs
+
 \usepackage{tikz}
 \usetikzlibrary{quotes, angles, intersections}
-
-%MEUS COMANDOs
 \newcommand{\R}{\mathbb{R}}
@@
 \newcommand{\bigO}{\mathscr{O}}
+
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.4}
+%\usepgfplotslibrary{external}
+%\tikzexternalize
+
+%FIM MEUS COMANDOS
 
@@
 
-\section{Introdução}
+\section{Introduction}
 \begin{frame}
-\frametitle{Introdução}
+\frametitle{Introduction}
 \begin{itemize}
@@
 	\begin{block}{Norms}
-		Let $u \in \R^2$ and $Q$ a $2$ by $2$ positive definite matrix
+		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
 		\begin{itemize}
@@
 \begin{frame}{Preliminaries}
+	\begin{figure}[H]
+		\centering
+
+		\caption{The elliptical and euclidean norms.}
+		\input{figures/elliptical.and.euclidean.norms.tex}
+		%\fautor
+		\label{fig:3ellipses_intersect}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Preliminaries}
 
 	\begin{block}{Ellipse}
-		Given a center $c \in \R^2$ and a p.d. matrix $Q$, an ellipse is the set of points that satisfy
+		Given a center $c \in \R^2$ and a $2x2$ p.d. matrix $Q$, an ellipse is the set of points that satisfy
 
 		\begin{equation*}
-		||u-c||_Q = 1
+		||u-c||_Q = 1,
 		\end{equation*}
@@
 		\begin{equation*}
-		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1
+		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1,
 		\end{equation*}
+
+		where $(a,b)$ are the shape parameters and $c=(c_x,c_y)$ is the center.
 	\end{block}
 
-\end{frame}
-
-\begin{frame}{Preliminaries}
-	\begin{figure}[H]
-		\centering
-
-		\caption{Three curves representing the points that have distance equal to one.}
-		\input{figures/a.tex}
-		%\fautor
-		\label{fig:3ellipses_intersect}
-	\end{figure}
 \end{frame}
@@
 		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
-		\item $w(A)$, with $A\subset \Pp$ is the sum of weights of the points in $A$
-		\item $D(q)$ is a disk with radius one with center at point $q$
+		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
+		\item $D(q)$ is a unit disk with center at point $q$
 		\item We will introduce an equivalent problem...
@@
 	\begin{itemize}
-		\item The disks are fixed at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
-		\item A clique is a non-empty intersection area of a subset of disks
+		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
+		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.
 		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
 	\end{itemize}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
+		\begin{figure}[H]
+		\centering
+
+		\caption{An instance of $MCD(\Pp,1)$.}
+		%\input{figures/elliptical.and.euclidean.norms.tex}
+      \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
+		%\fautor
+		\label{fig:mcd_instance}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
+	\begin{figure}[H]
+		\centering
+
+		\caption{An instance of $MCD(\Pp,1)$.}
+		%\input{figures/elliptical.and.euclidean.norms.tex}
+		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
+		%\fautor
+		\label{fig:max_wieght_clique}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
+	\begin{figure}[H]
+		\centering
+
+		\caption{Three disks and their intersection points.}
+		\input{figures/img2.tex}
+		%\fautor
+		\label{fig:3disks_intersect}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.
+
+	\begin{itemize}
+		\item An intersection region of disks is bounded by arcs.
+
+		\item The arc $\Gamma_+(i,j),\Gamma_-(i,j)$ (counter-clockwise) determines a region where $i$ and $j$ intersect.
+
+		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. Work-around: repeat it.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+
+	The algorithm is described simply as:
+
+	For every disk, traverse the sorted list of intersection angles twice, keeping a set of active disks, and the current best solution.
+
+\begin{figure}[H]
+	\centering
+
+	\caption{The intersections list of a disk with three other disks.}
+	\input{figures/fig:array_disks.tex}
+%	\fautor
+	\label{fig:array_disks}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+
+	The run-time complexity of the algorithm is $\bigO(n^2\log{n})$.
+
+	\begin{itemize}
+		\item There are $\bigO(n^2)$ intersections among $n$ disks
+
+		\item Sorting takes $\bigO(n^2\log{n})$
+
+		\item The traversal takes $\bigO(n)$ for every disk.
+
+		\item Can be implemented in $K\log{n}$ where $K$ is the number of intersections. 
+	\end{itemize}
+
+\begin{block}{Multiple disks}
+	For every disk, try every possible assignment that the traversal goes through.
+\end{block}
+
 \end{frame}

### 2019-04-26 implementation/GeometryBase.jl
WIP

@@ -13,6 +13,8 @@ struct Ellipse
     center::Point
 	fx::Function
 	fy::Function
+	dfx::Function
+	dfy::Function
 
 	Ellipse(a::Real, b::Real, cx::Real, cy::Real) = Ellipse(a,b,Point(cx,cy))
 
@@ -22,7 +24,8 @@ struct Ellipse
 			return error("Invalid ellipse parameters")
 		end
 
-		return new(a,b,c, t-> c.x + a * cos(t), t-> c.y + b * sin(t))
+		return new(a,b,c, t-> c.x + a * cos(t), t-> c.y + b * sin(t), t->-a*sin(t), t-> b * cos(t))
 	end
 end
+
 end

### 2019-04-26 implementation/ellipses_intersection.jl

@@ -16,7 +16,7 @@ end
 
 #Assumes that e_a.a === e₂.a
 function intersection(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,Point}}
-	h::Float64 = e₂.center.x - e₁.center.y
+	h::Float64 = e₂.center.x - e₁.center.x
 	k::Float64 = e₂.center.y - e₁.center.y
 	a::Float64 = e₁.a
 	b::Float64 = e₁.b
@@ -35,5 +35,30 @@ function intersection(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,P
 	x_₁ = y₁*α + β
 	x_₂ = y₂*α + β
 
-	return Point(x_₁,y₁), Point(x_₂,y₂)
+	return Point(x_₁ + e₁.center.x,y₁ + e₁.center.y), Point(x_₂ + e₁.center.x,y₂ + e₁.center.x)
 end
+
+function angles(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Real,Real}}
+	ret = intersection(e₁, e₂)
+	if (ret === nothing)
+		return nothing
+	end
+
+	P::Point, Q::Point = ret
+	a::Real = e₁.a
+	b::Real = e₂.b
+
+	s1 = atan(a*(P.y-e₁.center.y), b*(P.x - e₁.center.x))
+	s2 = atan(a*(Q.y-e₁.center.y), b*(Q.x - e₁.center.x))
+	
+	t1 = atan(a*(P.y-e₂.center.y), b*(P.x - e₂.center.x))
+	t2 = atan(a*(Q.y-e₂.center.y), b*(Q.x - e₂.center.x))
+	
+	u = [e₁.dfx(s1), e₁.dfy(s1)]
+	v = -[e₂.dfx(t1), e₂.dfy(t1)]
+
+	@show (u[1] * v[2] - u[2]*v[1])
+
+	return u[1] * v[2] - u[2] * v[1] >= 0 ? (s1,s2) : (s2,s1)
+end
+

### 2019-04-26 implementation/main.jl

@@ -18,15 +18,37 @@ function main()
 		return nothing
 	end
 
-	p₁, p₂ = ret
+	a1, a2 = angles(e₁, e₂)
+	p₁, p₂ = (Point(e₁.fx(a1), e₁.fy(a1)),
+			  Point(e₁.fx(a2), e₁.fy(a2)))
 
-	@printf("%.3f %.3f\n", p₁.x, p₁.y)
+	@show(ret)
+	@show(a1,a2)
+	@show(p₁, p₂)
+
+	#@printf("%.3f %.3f\n", e₁.fx(a1), p₁.y)
 
 	plt = plot(e₁.fx, e₁.fy, 0, 2π)
 	plot!(e₂.fx, e₂.fy, 0, 2π)
-	plot!([p₁.x, p₂.x], [p₁.y, p₂.y], seriestype=:scatter)
-	savefig(plt, "a.png")
+	plot!([p₁.x, p₂.x], [p₁.y, p₂.y], seriestype=:scatter, series_annotations = ["+","-"])
 
+	b1, b2 = angles(e₂, e₁)
+
+	dfx1 = e₁.dfx(a1)	
+	dfy1 = e₁.dfy(a1)
+
+	dfx2 = -e₂.dfx(b2)
+	dfy2 = -e₂.dfy(b2)
+	quiver!([p₁.x, p₁.x], [p₁.y, p₁.y], quiver=([dfx1, dfx2],[dfy1, dfy2]))
+
+	dfx1 = e₁.dfx(a2)	
+	dfy1 = e₁.dfy(a2)
+
+	dfx2 = -e₂.dfx(b1)
+	dfy2 = -e₂.dfy(b1)
+	quiver!([p₂.x, p₂.x], [p₂.y, p₂.y], quiver=([dfx1, dfx2],[dfy1, dfy2]))
+
+	savefig(plt, "a.png")
 	return ret
 end
 

### 2019-04-27 quali/quali.presentation/slides.tex
WIP

@@
 
-		\item Can be implemented in $K\log{n}$ where $K$ is the number of intersections. 
+		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections. 
 	\end{itemize}
@@
 
-\section{Cobertura Maximal por Ellipses}
+\section{Maximal Covering by Ellipses}
 
-\begin{frame}{Cobertura Maximal por Ellipses}
-	content... trabalhos passados
+\begin{frame}{Maximal Covering by Ellipses}
+	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by
+
+	\begin{equation*}
+	\max_q |\Pp \cap (q)|,
+	\end{equation*}
+
+	\begin{itemize}
+		\item $E(q)$ is an axis-parallel ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
+		\item Assuming unit weights for now
+		\item Same algorithm for one disk
+	\end{itemize}
+
 \end{frame}

### 2019-04-27 implementation/Ellipses.jl

@@ -1,0 +1,83 @@
+module Ellipses
+
+include("Utils.jl")
+#import .Utils
+using .Utils
+
+#exports
+export Ellipse
+export ellipseinter
+export angles
+
+struct Ellipse
+    a::Real
+    b::Real
+    center::Point
+	fx::Function
+	fy::Function
+	dfx::Function
+	dfy::Function
+
+	Ellipse(a::Real, b::Real, cx::Real, cy::Real) = Ellipse(a,b,Point(cx,cy))
+
+	Ellipse(a::Real, b::Real, c::Point) = 
+	begin 
+		if (a<=0 || b<=0)
+			return error("Invalid ellipse parameters")
+		end
+
+		return new(a,b,c, t-> c.x + a * cos(t), t-> c.y + b * sin(t), t->-a*sin(t), t-> b * cos(t))
+	end
+end
+
+#functions
+
+function ellipseinter(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,Point}}
+	h::Float64 = e₂.center.x - e₁.center.x
+	k::Float64 = e₂.center.y - e₁.center.y
+	a::Float64 = e₁.a
+	b::Float64 = e₁.b
+
+	α = (-2k*a^2)/(2h*b^2)
+	β = (b^2*h^2 + a^2*k^2) / (2h*b^2)
+	
+	ro = root2(b^2*α^2+a^2, 2β*α*b^2, b^2*β^2 - a^2*b^2)
+
+	if (ro === nothing)
+		return nothing 
+	end
+	
+	y₁, y₂ = ro
+
+	x_₁ = y₁*α + β
+	x_₂ = y₂*α + β
+
+	return Point(x_₁ + e₁.center.x,y₁ + e₁.center.y), Point(x_₂ + e₁.center.x,y₂ + e₁.center.x)
+end
+
+function angles(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Real,Real}}
+	ret = ellipseinter(e₁, e₂)
+	if (ret === nothing)
+		return nothing
+	end
+
+	P::Point, Q::Point = ret
+	a::Real = e₁.a
+	b::Real = e₂.b
+
+	s1 = atan(a*(P.y-e₁.center.y), b*(P.x - e₁.center.x))
[…]

### 2019-04-27 implementation/GeometryBase.jl

@@ -1,31 +1,0 @@
-module GeometryBase 
-
-export Point, Ellipse
-
-struct Point
-	x::Real
-	y::Real
-end
-
-struct Ellipse
-    a::Real
-    b::Real
-    center::Point
-	fx::Function
-	fy::Function
-	dfx::Function
-	dfy::Function
-
-	Ellipse(a::Real, b::Real, cx::Real, cy::Real) = Ellipse(a,b,Point(cx,cy))
-
-	Ellipse(a::Real, b::Real, c::Point) = 
-	begin 
-		if (a<=0 || b<=0)
-			return error("Invalid ellipse parameters")
-		end
-
-		return new(a,b,c, t-> c.x + a * cos(t), t-> c.y + b * sin(t), t->-a*sin(t), t-> b * cos(t))
-	end
-end
-
-end

### 2019-04-27 implementation/Utils.jl

@@ -1,0 +1,24 @@
+module Utils 
+
+export Point, root2 
+
+struct Point
+	x::Real
+	y::Real
+end
+
+function root2(a::Real, b::Real, c::Real)::Union{Nothing, Tuple{Real,Real}}
+	Δ = b^2 - 4*a*c
+
+	if (Δ < 0)
+		return nothing 
+	end
+
+	if (a==0)
+		return (-c / b, -c / b)
+	end
+
+	return (-b + √Δ) / (2*a), (-b-√Δ)/(2*a)
+end
+
+end

### 2019-04-27 implementation/ellipses_intersection.jl

@@ -1,64 +1,8 @@
+module EllipseIntersection
+
 using GeometryBase
 
-function root2(a::Real, b::Real, c::Real)::Union{Nothing, Tuple{Real,Real}}
-	Δ = b^2 - 4*a*c
-
-	if (Δ < 0)
-		return nothing 
-	end
-
-	if (a==0)
-		return (-c / b, -c / b)
-	end
-
-	return (-b + √Δ) / (2*a), (-b-√Δ)/(2*a)
-end
+export intersection, angles
 
 #Assumes that e_a.a === e₂.a
-function intersection(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,Point}}
-	h::Float64 = e₂.center.x - e₁.center.x
-	k::Float64 = e₂.center.y - e₁.center.y
-	a::Float64 = e₁.a
-	b::Float64 = e₁.b
-
-	α = (-2k*a^2)/(2h*b^2)
-	β = (b^2*h^2 + a^2*k^2) / (2h*b^2)
-	
-	ro = root2(b^2*α^2+a^2, 2β*α*b^2, b^2*β^2 - a^2*b^2)
-
-	if (ro === nothing)
-		return nothing 
-	end
-	
-	y₁, y₂ = ro
-
-	x_₁ = y₁*α + β
-	x_₂ = y₂*α + β
-
-	return Point(x_₁ + e₁.center.x,y₁ + e₁.center.y), Point(x_₂ + e₁.center.x,y₂ + e₁.center.x)
 end
-
-function angles(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Real,Real}}
-	ret = intersection(e₁, e₂)
-	if (ret === nothing)
-		return nothing
-	end
-
-	P::Point, Q::Point = ret
-	a::Real = e₁.a
-	b::Real = e₂.b
-
-	s1 = atan(a*(P.y-e₁.center.y), b*(P.x - e₁.center.x))
-	s2 = atan(a*(Q.y-e₁.center.y), b*(Q.x - e₁.center.x))
-	
-	t1 = atan(a*(P.y-e₂.center.y), b*(P.x - e₂.center.x))
-	t2 = atan(a*(Q.y-e₂.center.y), b*(Q.x - e₂.center.x))
-	
-	u = [e₁.dfx(s1), e₁.dfy(s1)]
[…]

### 2019-04-27 implementation/main.jl

@@ -1,18 +1,29 @@
 #Makes julia be able to see GeometryBase
-push!(LOAD_PATH, pwd())
-
 using Plots
+using PGFPlots
 using Printf
-using GeometryBase
+using LaTeXStrings
 
-include("ellipses_intersection.jl")
+include("Ellipses.jl")
+include("Utils.jl")
+import .Utils
+#import .Ellipses
+using .Utils
+using .Ellipses
+
+function versor(A::AbstractArray)::AbstractArray{Real}
+	hh::Real = 0
+	hh = mapreduce(x->x^2, +, A)
+	return map(x -> x / hh, A)
+end
 
 function main()
 
 	e₁ = Ellipse(3,2,0,0)
 	e₂ = Ellipse(3,2,1,1)
+	pgfplots()  
 
-	ret = intersection(e₁, e₂)
+	ret = ellipseinter(e₁, e₂)
 
 	if (ret === nothing)
 		return nothing
@@ -28,27 +39,40 @@ function main()
 
 	#@printf("%.3f %.3f\n", e₁.fx(a1), p₁.y)
 
-	plt = plot(e₁.fx, e₁.fy, 0, 2π)
-	plot!(e₂.fx, e₂.fy, 0, 2π)
-	plot!([p₁.x, p₂.x], [p₁.y, p₂.y], seriestype=:scatter, series_annotations = ["+","-"])
+	plt = plot(e₁.fx, e₁.fy, 0, 2π, dpi=300, label=L"$E_1$")
+	plot!(e₂.fx, e₂.fy, 0, 2π,dpi=300, label=L"E_2")
+	plot!([p₁.x, p₂.x], [p₁.y, p₂.y], seriestype=:scatter,color=:black,lab="")
 
 	b1, b2 = angles(e₂, e₁)
+
 
 	dfx1 = e₁.dfx(a1)	
 	dfy1 = e₁.dfy(a1)
 
 	dfx2 = -e₂.dfx(b2)
 	dfy2 = -e₂.dfy(b2)
-	quiver!([p₁.x, p₁.x], [p₁.y, p₁.y], quiver=([dfx1, dfx2],[dfy1, dfy2]))
+
+	quiver!([p₁.x, p₁.x], [p₁.y, p₁.y], 
+			gradient=(
+					  versor([dfx1, dfx2]),
[…]

### 2019-04-27 implementation/ellipses_intersection.jl
remove unused

@@ -1,8 +1,0 @@
-module EllipseIntersection
-
-using GeometryBase
-
-export intersection, angles
-
-#Assumes that e_a.a === e₂.a
-end

### 2019-04-27 implementation/main.jl
WIP

@@ -1,29 +1,40 @@
 #Makes julia be able to see GeometryBase
 using Plots
-using PGFPlots
+#using PGFPlots
 using Printf
 using LaTeXStrings
 
 include("Ellipses.jl")
+include("plotting.jl")
 include("Utils.jl")
-import .Utils
+
+#import .Utils
 #import .Ellipses
 using .Utils
 using .Ellipses
 
-function versor(A::AbstractArray)::AbstractArray{Real}
-	hh::Real = 0
-	hh = mapreduce(x->x^2, +, A)
-	return map(x -> x / hh, A)
+pgfplots()
+
+function main2()
+	e₁ = Ellipse(3,2,0,0)
+	e₂ = Ellipse(3,2,first(randn(1)), first(randn(1)))
+	e₃ = Ellipse(3,2,first(randn(1)),first(randn(1)))
+	#e2 = Ellipse(3,2,1,1)
+
+	plt = plotellipses([e₁, e₂, e₃])
+	#plt = plotellipses([e₁, e2])
+
+	savefig(plt, "a.pdf")
 end
 
 function main()
 
 	e₁ = Ellipse(3,2,0,0)
 	e₂ = Ellipse(3,2,1,1)
+	e₃ = Ellipse(3,2,rand(1),rand(1))
 	pgfplots()  
 
-	ret = ellipseinter(e₁, e₂)
+	ret = ellipseinter(e₁, e₂, e₃)
 
 	if (ret === nothing)
 		return nothing
@@ -76,4 +87,4 @@ function main()
 	return ret
 end
 
-main()
+#main()

### 2019-04-27 implementation/plotting.jl

@@ -1,0 +1,72 @@
+include("Ellipses.jl")
+include("Utils.jl")
+using .Ellipses
+using .Utils
+using Plots
+#using PGFPlots
+using LaTeXStrings
+
+function versor(A::AbstractArray)::AbstractArray{Real}
+	hh::Real = 0
+	hh = mapreduce(x->x^2, +, A)
+	return map(x -> x / hh, A)
+end
+
+function plotellipses(E::AbstractArray{Ellipse})
+
+	e1 = E[1]
+
+	plt = plot(e1.fx, e1.fy, 0, 2π, dpi=300, label=L"E_1")
+
+	for i in 2:length(E)
+		ret = ellipseinter(e1, E[i])
+		if (ret == nothing) continue end
+		
+		a1, a2 = angles(e1, E[i])
+		p1, p2 = ret
+
+		e2 = E[i]
+
+		plot!(e2.fx, e2.fy, 0, 2π,dpi=300, label=latexstring("E_", "$i"))
+		plot!([p1.x, p2.x], [p1.y, p2.y], seriestype=:scatter,color=:black,lab="")
+
+		b1, b2 = angles(e2, e1)
+
+		dfx1 = e1.dfx(a1)	
+		dfy1 = e1.dfy(a1)
+
+		dfx1, dfy1 = versor([dfx1, dfy1])
+
+		dfx2 = -e2.dfx(b2)
+		dfy2 = -e2.dfy(b2)
+		dfx2, dfy2 = versor([dfx2, dfy2])
+
+
+		quiver!([p1.x, p1.x], [p1.y, p1.y], 
+				gradient=(
+						  versor([dfx1, dfx2]),
+						  versor([dfy1, dfy2]))
+		)
+
+		dfx1 = e1.dfx(a2)	
+		dfy1 = e1.dfy(a2)
+		dfx1, dfy1 = versor([dfx1, dfy1])
+
+		dfx2 = -e2.dfx(b1)
+		dfy2 = -e2.dfy(b1)
+		dfx2, dfy2 = versor([dfx2, dfy2])
+
+		quiver!([p2.x, p2.x], [p2.y, p2.y], 
+				quiver=(versor([dfx1, dfx2]),versor([dfy1, dfy2])),lab="")
+
+
+		annotate!([(p1.x+0.4,p1.y-0.1,
+					text(latexstring(L"\tiny\Gamma_+(1,", "$i)"), pointsize=8))])
+
[…]

### 2019-04-27 implementation/main.jl
WIP

@@ -1,17 +1,13 @@
-#Makes julia be able to see GeometryBase
+push!(LOAD_PATH, pwd())
+
 using Plots
-#using PGFPlots
 using Printf
 using LaTeXStrings
 
-include("Ellipses.jl")
 include("plotting.jl")
-include("Utils.jl")
 
-#import .Utils
-#import .Ellipses
-using .Utils
-using .Ellipses
+using Utils
+using Ellipses
 
 pgfplots()
 

### 2019-04-27 implementation/plotting.jl

@@ -1,29 +1,26 @@
-include("Ellipses.jl")
-include("Utils.jl")
-using .Ellipses
-using .Utils
+using Ellipses
+using Utils
 using Plots
-#using PGFPlots
 using LaTeXStrings
+using LinearAlgebra
 
 function versor(A::AbstractArray)::AbstractArray{Real}
 	hh::Real = 0
-	hh = mapreduce(x->x^2, +, A)
-	return map(x -> x / hh, A)
+	return map(x -> x / norm(A), A)
 end
 
 function plotellipses(E::AbstractArray{Ellipse})
 
 	e1 = E[1]
 
-	plt = plot(e1.fx, e1.fy, 0, 2π, dpi=300, label=L"E_1")
+	plt = plot(e1.fx, e1.fy, 0, 2π, dpi=300, label=L"E_1", xaxis=false,yaxis=false, color=:black)
 
 	for i in 2:length(E)
 		ret = ellipseinter(e1, E[i])
 		if (ret == nothing) continue end
 		
 		a1, a2 = angles(e1, E[i])
-		p1, p2 = ret
+		p1, p2 = Point(e1.fx(a1), e1.fy(a1)), Point(e1.fx(a2), e1.fy(a2)) 
 
 		e2 = E[i]
 
@@ -42,22 +39,20 @@ function plotellipses(E::AbstractArray{Ellipse})
 		dfx2, dfy2 = versor([dfx2, dfy2])
 
 
-		quiver!([p1.x, p1.x], [p1.y, p1.y], 
-				gradient=(
-						  versor([dfx1, dfx2]),
-						  versor([dfy1, dfy2]))
-		)
+		quiver!([p1.x], [p1.y], quiver=([dfx1], [dfy1]), color=:red)
+		quiver!([p1.x], [p1.y], quiver=([dfx2], [dfy2]), color=:blue)
 
-		dfx1 = e1.dfx(a2)	
+		dfx1 = e1.dfx(a2)
 		dfy1 = e1.dfy(a2)
 		dfx1, dfy1 = versor([dfx1, dfy1])
 
 		dfx2 = -e2.dfx(b1)
 		dfy2 = -e2.dfy(b1)
-		dfx2, dfy2 = versor([dfx2, dfy2])
+		#dfx2, dfy2 = versor([dfx2, dfy2])
 
-		quiver!([p2.x, p2.x], [p2.y, p2.y], 
[…]

### 2019-04-28 quali/quali.presentation/slides.tex
remove unused
WIP

@@
 \pgfplotsset{compat=1.4}
+\usepackage{algorithmicx}
+\usepackage{algorithm}
 %\usepgfplotslibrary{external}
@@
 		\item $D(q)$ is a unit disk with center at point $q$
+		\item \cite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
+		\item \cite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
 		\item We will introduce an equivalent problem...
@@
 
-		\caption{An instance of $MCD(\Pp,1)$.}
+		\caption{An instance of Maximum Weight Clique Problem.}
 		%\input{figures/elliptical.and.euclidean.norms.tex}
@@
 \begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
+	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles (with respect to $D_i$) of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
 	\begin{figure}[H]
@@
 \begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+\begin{figure}
+	%\centering
+
+	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
+	\input{figures/mcd_sim.tex}
+	%	\fautor
+	%\label{fig:array_disks}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
 
@@
 \begin{block}{Multiple disks}
-	For every disk, try every possible assignment that the traversal goes through.
+	For every disk, try every possible assignment that the traversal goes through. \cite{cabello:2006} proposed a $\bigO(n^{2m-1})$ algorithm.
 \end{block}
@@
 	\begin{itemize}
-		\item $E(q)$ is an axis-parallel ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
+		\item $E(q)$ is an axis-parallel ellipse with center point $q$
 		\item Assuming unit weights for now
@@
 
-\begin{frame}{Cobertura Maximal por Ellipses}{$m$ elipses}
-	content... algoritmo
+\begin{frame}{Maximal Covering by Ellipses}
+\begin{figure}[H]
+	\centering
+
+	\caption{Intersection points of $E_1$ with $E_2$ and $E_3$ along with opening and closing angles indicators.}
+	\input{figures/3ellipses_with_gammas.tex}
+	%	\fautor
+	\label{fig:3ellipses_with_gammas}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
+	Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by
+
+	\begin{equation*}
+	\max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|},
+	\end{equation*}
+
+	\begin{itemize}
+		\item $\E$ is a set of $m$ ellipses
+		\item \cite{andreta,canbolat} are the works found on the problem which the ellipses have costs
+		\item \cite{andreta} also developed a method for the non-axis-parallel case
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
+	\begin{algorithm}[H]
+	%	\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
+		%\KwIn{alskdjf}
+
+		\begin{algorithmic}[1]
+			\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and the shape parameters $(a, b)$ of an ellipse.}
+			%\Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}
+
+			%\item[]
+			%\Procedure{$MCE_1$}{$\Pp, a, b$}
+			%\State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}
+
+			%\ForAll{$p_i \in \Pp$}
+			%\State Let $E_i$ be the ellipse with center at $p_i$ and parameters $(a,b)$
+
+			%\State Let $I_i$ be the set of ellipses that intersect with $E_i$
+
+			%\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $E_i$}
+
+			%\State $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$ %\Comment{The multiset of intersection angles with $E_i$.}
+
+			%\ForAll{$j \in I_i$}
+			%\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
+			%\EndFor
+
+			%\State $Z \gets Z \cup \{\{p_i\}\}$
+			%\State $Cov \gets \{p_i\}$ \Comment{The set of active disks.}
+
+			%\For{$cnt=1..2$} \Comment{Do it twice.}
+			%\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
+			%\State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
+			%\If{$a$ is a starting angle}
+			%\State $Cov \gets Cov \cup \{p_a\}$
+			%\Else
+			%\State $Cov \gets Cov \setminus \{p_a\}$
+			%\EndIf
+			%\State $Z \gets Z \cup \{Cov\}$
+			%\EndFor
+			%\EndFor
+			%\EndFor
+
+			%\State \Return $Z$
+			%\EndProcedure
+
+		\end{algorithmic}
+	\end{algorithm}
 \end{frame}
@@
 \end{frame}
+
+\begin{frame}[allowframebreaks]
+	\frametitle{References}
+	\bibliographystyle{amsalpha}
+	\bibliography{../references.bib}
+\end{frame}
+
 \end{document}

### 2019-04-28 implementation/main.jl

@@ -21,6 +21,22 @@ function main2()
 	#plt = plotellipses([e₁, e2])
 
 	savefig(plt, "a.pdf")
+	savefig(plt, "a.tex")
+end
+
+function main3()
+
+	e₁ = Ellipse(3,2,0,0)
+	e₂ = Ellipse(3,2,first(randn(1)), first(randn(1)))
+	e₃ = Ellipse(3,2,first(randn(1)),first(randn(1)))
+	#e2 = Ellipse(3,2,1,1)
+
+	plt = plotwihtoutquiver([e₁, e₂, e₃])
+	#plt = plotellipses([e₁, e2])
+
+	savefig(plt, "a.pdf")
+	savefig(plt, "a.tex")
+
 end
 
 function main()

### 2019-04-28 implementation/plotting.jl

@@ -3,44 +3,83 @@ using Utils
 using Plots
 using LaTeXStrings
 using LinearAlgebra
+using ColorSchemes
 
 function versor(A::AbstractArray)::AbstractArray{Real}
-	hh::Real = 0
 	return map(x -> x / norm(A), A)
 end
 
-function plotellipses(E::AbstractArray{Ellipse})
+function plotwihtoutquiver(E::AbstractArray{Ellipse})
 
 	e1 = E[1]
+	colors = [:black, ColorSchemes.hsv.colors[10], ColorSchemes.hsv.colors[28]]
 
-	plt = plot(e1.fx, e1.fy, 0, 2π, dpi=300, label=L"E_1", xaxis=false,yaxis=false, color=:black)
+	plt = plot(e1.fx, e1.fy, 0, 2π, dpi=300, label=L"E_1", xaxis=false,yaxis=false, color=colors[1])
 
 	for i in 2:length(E)
 		ret = ellipseinter(e1, E[i])
 		if (ret == nothing) continue end
 		
-		a1, a2 = angles(e1, E[i])
-		p1, p2 = Point(e1.fx(a1), e1.fy(a1)), Point(e1.fx(a2), e1.fy(a2)) 
-
 		e2 = E[i]
 
-		plot!(e2.fx, e2.fy, 0, 2π,dpi=300, label=latexstring("E_", "$i"))
+		a1, a2 = angles(e1, e2)
+		b1, b2 = angles(e2, e1)
+
+		#p1, p2 = Point(e2.fx(b2), e2.fy(b2)), Point(e2.fx(b1), e2.fy(b1)) 
+		p1, p2 = ellipseinter(e2,e1)
+
+
+		plot!(e2.fx, e2.fy, 0, 2π,dpi=300, label=latexstring("E_", "$i"), color=colors[i])
 		plot!([p1.x, p2.x], [p1.y, p2.y], seriestype=:scatter,color=:black,lab="")
 
+		#annotate!([(p1.x+0.4,p1.y-0.1,
+		#			text(latexstring(L"\tiny\Gamma_+(1,", "$i)"), pointsize=8))])
+
+		#annotate!([(p2.x-0.4,p2.y+0.1,
+		#			text(latexstring(L"\tiny\Gamma_-(1,","$i)"),pointsize=8))])
+
+	end
+
+	return plt
+
+end
+
[…]

### 2019-04-29 quali/quali.presentation/figures/mcd_sim.tex

--- 2019-03-27 tex/figures/fig:array_disks.tex
@@
 %Shape: Circle [id:dp05970043129919356] 
+\draw  [color=green  ,draw opacity=1 ] (57.81,32.47) ..
+controls (57.81,18.66) and (69,7.47) ..
+(82.81,7.47) ..
+controls (96.62,7.47) and (107.81,18.66) ..
+(107.81,32.47) ..
+controls (107.81,46.27) and (96.62,57.47) ..
+(82.81,57.47) ..
+controls (69,57.47) and (57.81,46.27) ..
+(57.81,32.47) -- cycle ;
+%Straight Lines [id:da04725899028195979] 
+%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
+
+%Flowchart: Extract [id:dp5267407418119328] 
+\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
+
+\draw (60,73) node [scale=0.5]  {$+$};
+% Text Node
+\draw (65.22,66) node [scale=0.5]  {$+$};
+% Text Node
+\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
+% Text Node
+\draw (54.22,39.56) node [scale=0.5]  {$-$};
+% Text Node
+\draw (45.62,36.96) node [scale=0.5]  {$-$};
+% Text Node
+\draw (38.02,31.56) node [scale=0.5]  {$-$};
+
+% Text Node
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\end{tikzpicture}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
+
+%Shape: Circle [id:dp37777408295388804] 
+\draw   (21,59.5) ..
+controls (21,45.69) and (32.19,34.5) ..
+(46,34.5) ..
+controls (59.81,34.5) and (71,45.69) ..
+(71,59.5) ..
+controls (71,73.31) and (59.81,84.5) ..
+(46,84.5) ..
+controls (32.19,84.5) and (21,73.31) ..
+(21,59.5) -- cycle ;
+%Shape: Circle [id:dp4562198988843913] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) ..
+controls (47.5,33.14) and (58.69,21.94) ..
+(72.5,21.94) ..
+controls (86.31,21.94) and (97.5,33.14) ..
+(97.5,46.94) ..
+controls (97.5,60.75) and (86.31,71.94) ..
+(72.5,71.94) ..
+controls (58.69,71.94) and (47.5,60.75) ..
+(47.5,46.94) -- cycle ;
+%Shape: Circle [id:dp8913971633985722] 
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
+controls (33,39.69) and (44.19,28.5) ..
+(58,28.5) ..
+controls (71.81,28.5) and (83,39.69) ..
+(83,53.5) ..
+controls (83,67.31) and (71.81,78.5) ..
+(58,78.5) ..
+controls (44.19,78.5) and (33,67.31) ..
+(33,53.5) -- cycle ;
+%Shape: Circle [id:dp05970043129919356] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
+controls (57.81,18.66) and (69,7.47) ..
+(82.81,7.47) ..
+controls (96.62,7.47) and (107.81,18.66) ..
+(107.81,32.47) ..
+controls (107.81,46.27) and (96.62,57.47) ..
+(82.81,57.47) ..
+controls (69,57.47) and (57.81,46.27) ..
+(57.81,32.47) -- cycle ;
+%Straight Lines [id:da04725899028195979] 
+%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
+
+%Flowchart: Extract [id:dp5267407418119328] 
+\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
+
+\draw (60,73) node [scale=0.5,color=red]  {$+$};
+% Text Node
+\draw (65.22,66) node [scale=0.5]  {$+$};
+% Text Node
+\draw (74.22,50) node [scale=0.5]  {$+$};
+% Text Node
+\draw (54.22,39.56) node [scale=0.5]  {$-$};
+% Text Node
+\draw (45.62,36.96) node [scale=0.5]  {$-$};
+% Text Node
+\draw (38.02,31.56) node [scale=0.5]  {$-$};
+
+% Text Node
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\end{tikzpicture}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
+
+%Shape: Circle [id:dp37777408295388804] 
+\draw   (21,59.5) ..
+controls (21,45.69) and (32.19,34.5) ..
+(46,34.5) ..
+controls (59.81,34.5) and (71,45.69) ..
+(71,59.5) ..
+controls (71,73.31) and (59.81,84.5) ..
+(46,84.5) ..
+controls (32.19,84.5) and (21,73.31) ..
+(21,59.5) -- cycle ;
+
+%Shape: Circle [id:dp4562198988843913] 
+\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
+controls (47.5,33.14) and (58.69,21.94) ..
+(72.5,21.94) ..
+controls (86.31,21.94) and (97.5,33.14) ..
+(97.5,46.94) ..
+controls (97.5,60.75) and (86.31,71.94) ..
+(72.5,71.94) ..
+controls (58.69,71.94) and (47.5,60.75) ..
+(47.5,46.94) -- cycle ;
+
+%Shape: Circle [id:dp8913971633985722] 
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
+controls (33,39.69) and (44.19,28.5) ..
+(58,28.5) ..
+controls (71.81,28.5) and (83,39.69) ..
+(83,53.5) ..
+controls (83,67.31) and (71.81,78.5) ..
+(58,78.5) ..
+controls (44.19,78.5) and (33,67.31) ..
+(33,53.5) -- cycle ;
+
+%Shape: Circle [id:dp05970043129919356] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
+controls (57.81,18.66) and (69,7.47) ..
+(82.81,7.47) ..
+controls (96.62,7.47) and (107.81,18.66) ..
+(107.81,32.47) ..
+controls (107.81,46.27) and (96.62,57.47) ..
+(82.81,57.47) ..
+controls (69,57.47) and (57.81,46.27) ..
+(57.81,32.47) -- cycle ;
+%Straight Lines [id:da04725899028195979] 
+%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
+
+%Flowchart: Extract [id:dp5267407418119328] 
+\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
+
+\draw (60,73) node [scale=0.5]  {$+$};
+% Text Node
+\draw (65.22,66) node [scale=0.5,color=red]  {$+$};
+% Text Node
+\draw (74.22,50) node [scale=0.5]  {$+$};
+% Text Node
+\draw (54.22,39.56) node [scale=0.5]  {$-$};
+% Text Node
+\draw (45.62,36.96) node [scale=0.5]  {$-$};
+% Text Node
+\draw (38.02,31.56) node [scale=0.5]  {$-$};
+
+% Text Node
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\end{tikzpicture}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
+
+%Shape: Circle [id:dp37777408295388804] 
+\draw   (21,59.5) ..
+controls (21,45.69) and (32.19,34.5) ..
+(46,34.5) ..
+controls (59.81,34.5) and (71,45.69) ..
+(71,59.5) ..
+controls (71,73.31) and (59.81,84.5) ..
+(46,84.5) ..
+controls (32.19,84.5) and (21,73.31) ..
+(21,59.5) -- cycle ;
+
+%Shape: Circle [id:dp4562198988843913] 
+\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
+controls (47.5,33.14) and (58.69,21.94) ..
+(72.5,21.94) ..
+controls (86.31,21.94) and (97.5,33.14) ..
+(97.5,46.94) ..
+controls (97.5,60.75) and (86.31,71.94) ..
+(72.5,71.94) ..
+controls (58.69,71.94) and (47.5,60.75) ..
+(47.5,46.94) -- cycle ;
+
+%Shape: Circle [id:dp8913971633985722] 
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
+controls (33,39.69) and (44.19,28.5) ..
+(58,28.5) ..
+controls (71.81,28.5) and (83,39.69) ..
+(83,53.5) ..
+controls (83,67.31) and (71.81,78.5) ..
+(58,78.5) ..
+controls (44.19,78.5) and (33,67.31) ..
+(33,53.5) -- cycle ;
+
+%Shape: Circle [id:dp05970043129919356] 
+\draw  [color=green ,draw opacity=1 ] (57.81,32.47) ..
+controls (57.81,18.66) and (69,7.47) ..
+(82.81,7.47) ..
+controls (96.62,7.47) and (107.81,18.66) ..
+(107.81,32.47) ..
+controls (107.81,46.27) and (96.62,57.47) ..
+(82.81,57.47) ..
+controls (69,57.47) and (57.81,46.27) ..
+(57.81,32.47) -- cycle ;
+%Straight Lines [id:da04725899028195979] 
+%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
+
+%Flowchart: Extract [id:dp5267407418119328] 
+\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
+
+\draw (60,73) node [scale=0.5]  {$+$};
+% Text Node
+\draw (65.22,66) node [scale=0.5]  {$+$};
+% Text Node
+\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
+% Text Node
+\draw (54.22,39.56) node [scale=0.5]  {$-$};
+% Text Node
+\draw (45.62,36.96) node [scale=0.5]  {$-$};
+% Text Node
+\draw (38.02,31.56) node [scale=0.5]  {$-$};
+
+% Text Node
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\end{tikzpicture}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
+
+%Shape: Circle [id:dp37777408295388804] 
+\draw   (21,59.5) ..
+controls (21,45.69) and (32.19,34.5) ..
+(46,34.5) ..
+controls (59.81,34.5) and (71,45.69) ..
+(71,59.5) ..
+controls (71,73.31) and (59.81,84.5) ..
+(46,84.5) ..
+controls (32.19,84.5) and (21,73.31) ..
+(21,59.5) -- cycle ;
+
+%Shape: Circle [id:dp4562198988843913] 
+\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
+controls (47.5,33.14) and (58.69,21.94) ..
+(72.5,21.94) ..
+controls (86.31,21.94) and (97.5,33.14) ..
+(97.5,46.94) ..
+controls (97.5,60.75) and (86.31,71.94) ..
+(72.5,71.94) ..
+controls (58.69,71.94) and (47.5,60.75) ..
+(47.5,46.94) -- cycle ;
+
+%Shape: Circle [id:dp8913971633985722] 
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
+controls (33,39.69) and (44.19,28.5) ..
+(58,28.5) ..
+controls (71.81,28.5) and (83,39.69) ..
+(83,53.5) ..
+controls (83,67.31) and (71.81,78.5) ..
+(58,78.5) ..
+controls (44.19,78.5) and (33,67.31) ..
+(33,53.5) -- cycle ;
+
+%Shape: Circle [id:dp05970043129919356] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
+controls (57.81,18.66) and (69,7.47) ..
+(82.81,7.47) ..
+controls (96.62,7.47) and (107.81,18.66) ..
+(107.81,32.47) ..
+controls (107.81,46.27) and (96.62,57.47) ..
+(82.81,57.47) ..
+controls (69,57.47) and (57.81,46.27) ..
+(57.81,32.47) -- cycle ;
+%Straight Lines [id:da04725899028195979] 
+%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
+
+%Flowchart: Extract [id:dp5267407418119328] 
+\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
+
+\draw (60,73) node [scale=0.5]  {$+$};
+% Text Node
+\draw (65.22,66) node [scale=0.5]  {$+$};
+% Text Node
+\draw (74.22,50) node [scale=0.5]  {$+$};
+% Text Node
+\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
+% Text Node
+\draw (45.62,36.96) node [scale=0.5]  {$-$};
+% Text Node
+\draw (38.02,31.56) node [scale=0.5]  {$-$};
+
+% Text Node
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\end{tikzpicture}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
+
+%Shape: Circle [id:dp37777408295388804] 
+\draw   (21,59.5) ..
+controls (21,45.69) and (32.19,34.5) ..
+(46,34.5) ..
+controls (59.81,34.5) and (71,45.69) ..
+(71,59.5) ..
+controls (71,73.31) and (59.81,84.5) ..
+(46,84.5) ..
+controls (32.19,84.5) and (21,73.31) ..
+(21,59.5) -- cycle ;
+
+%Shape: Circle [id:dp4562198988843913] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 },draw opacity=1 ] (47.5,46.94) ..
+controls (47.5,33.14) and (58.69,21.94) ..
+(72.5,21.94) ..
+controls (86.31,21.94) and (97.5,33.14) ..
+(97.5,46.94) ..
+controls (97.5,60.75) and (86.31,71.94) ..
+(72.5,71.94) ..
+controls (58.69,71.94) and (47.5,60.75) ..
+(47.5,46.94) -- cycle ;
+
+%Shape: Circle [id:dp8913971633985722] 
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
+controls (33,39.69) and (44.19,28.5) ..
+(58,28.5) ..
+controls (71.81,28.5) and (83,39.69) ..
+(83,53.5) ..
+controls (83,67.31) and (71.81,78.5) ..
+(58,78.5) ..
+controls (44.19,78.5) and (33,67.31) ..
+(33,53.5) -- cycle ;
+
+%Shape: Circle [id:dp05970043129919356] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
+controls (57.81,18.66) and (69,7.47) ..
+(82.81,7.47) ..
+controls (96.62,7.47) and (107.81,18.66) ..
+(107.81,32.47) ..
+controls (107.81,46.27) and (96.62,57.47) ..
+(82.81,57.47) ..
+controls (69,57.47) and (57.81,46.27) ..
+(57.81,32.47) -- cycle ;
+%Straight Lines [id:da04725899028195979] 
+%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
+
+%Flowchart: Extract [id:dp5267407418119328] 
+\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
+
+\draw (60,73) node [scale=0.5]  {$+$};
+% Text Node
+\draw (65.22,66) node [scale=0.5]  {$+$};
+% Text Node
+\draw (74.22,50) node [scale=0.5]  {$+$};
+% Text Node
+\draw (54.22,39.56) node [scale=0.5]  {$-$};
+% Text Node
+\draw (45.62,36.96) node [scale=0.5,color=red]  {$-$};
+% Text Node
+\draw (38.02,31.56) node [scale=0.5]  {$-$};
+
+% Text Node
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\end{tikzpicture}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
+
+%Shape: Circle [id:dp37777408295388804] 
+\draw   (21,59.5) ..
+controls (21,45.69) and (32.19,34.5) ..
+(46,34.5) ..
+controls (59.81,34.5) and (71,45.69) ..
+(71,59.5) ..
+controls (71,73.31) and (59.81,84.5) ..
+(46,84.5) ..
+controls (32.19,84.5) and (21,73.31) ..
+(21,59.5) -- cycle ;
+
+%Shape: Circle [id:dp4562198988843913] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 },draw opacity=1 ] (47.5,46.94) ..
+controls (47.5,33.14) and (58.69,21.94) ..
+(72.5,21.94) ..
+controls (86.31,21.94) and (97.5,33.14) ..
+(97.5,46.94) ..
+controls (97.5,60.75) and (86.31,71.94) ..
+(72.5,71.94) ..
+controls (58.69,71.94) and (47.5,60.75) ..
+(47.5,46.94) -- cycle ;
+
+%Shape: Circle [id:dp8913971633985722] 
+\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 } ,draw opacity=1 ] (33,53.5) ..
+controls (33,39.69) and (44.19,28.5) ..
+(58,28.5) ..
+controls (71.81,28.5) and (83,39.69) ..
+(83,53.5) ..
+controls (83,67.31) and (71.81,78.5) ..
+(58,78.5) ..
+controls (44.19,78.5) and (33,67.31) ..
+(33,53.5) -- cycle ;
+
+%Shape: Circle [id:dp05970043129919356] 
 \draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
@@
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (38.02,31.56) node [scale=0.5,color=red]  {\textbf{$-$}};
 
 % Text Node
-\draw (20,35) node [scale=0.5]  {$E_{1}$};
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
 \end{tikzpicture}
-
-\begin{tikzpicture}
-
-\matrix [matrix of nodes,row sep=,row sep=0mm,
-column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
-column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
-column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
-column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
-column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
-column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
-] (O)
-{
-$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
-%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
-};
-
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
-\end{tikzpicture}

### 2019-04-30 quali/quali.presentation/slides.tex
WIP

@@
 \pgfplotsset{compat=1.4}
-\usepackage{algorithmicx}
-\usepackage{algorithm}
+\usepackage{algorithm2e}
+\usepackage{algorithmic}
+\usepackage{float}
+\usepackage{caption}
+\newcommand{\source}[1]{\caption*{Source: {#1}} }
+
 %\usepgfplotslibrary{external}
@@
 \title[Qualificação de Mestrado]{Planar Maximal Covering with Ellipses}
-\author[Tedeschi, D. F.]{Danilo F. Tedeschi}
+\author[Tedeschi, D. F.]{Danilo F. Tedeschi\\ \small Orientadora: Dra. Marina Andretta}
+
 \institute[ICMC]{Instituto de Ciências Matemáticas e Computação}
@@
  \maketitle
+
+\centering Thanks to CAPES
 \end{frame}
@@
 
-		\caption{The elliptical and euclidean norms.}
+		\caption{The elliptical and euclidean norms}
 		\input{figures/elliptical.and.euclidean.norms.tex}
-		%\fautor
+		\source{Elaborated by the author.}
 		\label{fig:3ellipses_intersect}
+
 	\end{figure}
@@
       \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
-		%\fautor
+		\source{Elaborated by the author.}
 		\label{fig:mcd_instance}
@@
 		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
-		%\fautor
+		\source{Elaborated by the author.}
 		\label{fig:max_wieght_clique}
@@
 		\input{figures/img2.tex}
-		%\fautor
+		\source{Elaborated by the author.}
 		\label{fig:3disks_intersect}
@@
 	\input{figures/fig:array_disks.tex}
-%	\fautor
+	\source{Elaborated by the author.}
 	\label{fig:array_disks}
@@
 	\input{figures/mcd_sim.tex}
-	%	\fautor
+		\source{Elaborated by the author.}
 	%\label{fig:array_disks}
@@
 
-\begin{block}{Multiple disks}
-	For every disk, try every possible assignment that the traversal goes through. \cite{cabello:2006} proposed a $\bigO(n^{2m-1})$ algorithm.
-\end{block}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Multiple disks}
+	\begin{itemize}
+		\item In \cite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.
+
+		\item In \cite{zhou} a heuristic method using an algorithm called mean-shift was developed.
+The mean-shift algorithm converges to a local density maxima of any probability distribution and it is used to find a smaller candidate list of centers for the disks.
+	\end{itemize}
 
@@
 
-\begin{frame}{Maximal Covering by Ellipses}
+\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
 	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by
@@
 
-\begin{frame}{Maximal Covering by Ellipses}
+\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
 \begin{figure}[H]
@@
 	\input{figures/3ellipses_with_gammas.tex}
-	%	\fautor
+	\source{Elaborated by the author.}
 	\label{fig:3ellipses_with_gammas}
@@
 		\item $\E$ is a set of $m$ ellipses
-		\item \cite{andreta,canbolat} are the works found on the problem which the ellipses have costs
-		\item \cite{andreta} also developed a method for the non-axis-parallel case
+		\item \cite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
+		\item \cite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
 	\end{itemize}
@@
 
-\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
+\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
 	\begin{algorithm}[H]
-	%	\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
-		%\KwIn{alskdjf}
+		%\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
+		\begin{algorithmic}[1]
+			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
+			\STATE $Z \gets \{\}$
 
-		\begin{algorithmic}[1]
-			\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and the shape parameters $(a, b)$ of an ellipse.}
-			%\Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}
-
-			%\item[]
-			%\Procedure{$MCE_1$}{$\Pp, a, b$}
-			%\State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}
-
-			%\ForAll{$p_i \in \Pp$}
-			%\State Let $E_i$ be the ellipse with center at $p_i$ and parameters $(a,b)$
-
-			%\State Let $I_i$ be the set of ellipses that intersect with $E_i$
-
-			%\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $E_i$}
-
-			%\State $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$ %\Comment{The multiset of intersection angles with $E_i$.}
-
-			%\ForAll{$j \in I_i$}
-			%\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
-			%\EndFor
-
-			%\State $Z \gets Z \cup \{\{p_i\}\}$
-			%\State $Cov \gets \{p_i\}$ \Comment{The set of active disks.}
-
-			%\For{$cnt=1..2$} \Comment{Do it twice.}
-			%\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
-			%\State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
-			%\If{$a$ is a starting angle}
-			%\State $Cov \gets Cov \cup \{p_a\}$
-			%\Else
-			%\State $Cov \gets Cov \setminus \{p_a\}$
-			%\EndIf
-			%\State $Z \gets Z \cup \{Cov\}$
-			%\EndFor
-			%\EndFor
-			%\EndFor
-
-			%\State \Return $Z$
-			%\EndProcedure
+			\FOR{$cnt=1..2$} 
+			\FOR{$a \in A$}
+			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
+			\IF{$a$ is a starting angle}
+			\STATE $Cov \gets Cov \cup \{p_a\}$
+			\ELSE
+			\STATE $Cov \gets Cov \setminus \{p_a\}$
+			\ENDIF
+			\STATE $Z \gets Z \cup \{Cov\}$
+			\ENDFOR
+			\ENDFOR
 
@@
 
-\section{Trabalhos Futuros}
+\begin{frame}{Maximal Covering by Ellipses}
 
-\begin{frame}{Trabalhos Futuros}
+	\begin{itemize}
+		\item The algorithm for $m$ ellipses tries every possible assignment of coverage for every one of the ellipses
+		\item Run-time complexity of $\bigO(n^2)^m = \bigO(n^{2m})$
 
+		\item Simpler than the $m$ disks algorithm proposed by \cite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).
+
+		\item Small improvements can be made in the pre-processing exhibited earlier in oder to reduce the size of the search space:
+		\begin{itemize}
+			\item Non-maximal coverage sets.
+			\item Ellipses that are too distant do not need to be checked.
+		\end{itemize}
+
+		\item The unit-weight assumption can be easily dropped
+	\end{itemize}
+
+\end{frame}
+
+\section{Future Work}
+
+\begin{frame}{Future Work}
+	Primary goals:
+\begin{itemize}
+	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
+
+	\item Develop an exact method for the version of the problem introduced in \cite{andreta} where the ellipses can be freely rotated.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Future Work}
+
+	Secondary goals:
+	\begin{itemize}
+
+	\item Develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
+The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse.
+The case with more than one ellipse is left as a challenge for us for the next steps of our research.
+
+	\item In \cite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity.
+We want to generalize this for the elliptical distance function and achieve a better run-time complexity.
+We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.
+
+		\end{itemize}
 \end{frame}

### 2019-04-30 implementation/solution.jl

@@ -1,0 +1,59 @@
+push!(LOAD_PATH, pwd())
+using Ellipses
+
+mutable struct PointW
+	id::Int
+	x::Real
+	y::Real
+	w::Real
+end
+
+function hash(p::PointW)::UInt64
+	return p.id
+end
+
+function sum(Z::Set{PointW})
+	return reduce(Z) do (pa,pb)
+		return pa.w + pb.w
+	end
+end
+
+function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Set{PointW}}
+	Z::AbstractArray{Set{PointW}} = []
+
+	n=length(P)
+
+	for i in 1:n 
+		e1 = Ellipse(E.a, E.b, P[i].x, P[i].y)
+		A::AbstractArray{Tuple{Real,PointW,Int}} = []
+		push!(Z, Set([P[i]]))
+
+		for j in 1:n
+			e2 = Ellipse(E.a, E.b, P[j].x, P[j].y)
+			ret = angles(e1, e2)
+			if (ret === nothing) continue end
+
+			a1, a2 = ret
+
+			push!(A, (a1, P[j], 1))
+			push!(A, (a2, P[j], -1))
+		end
+		
+		sort!(A)
+
+		Cov::Set{PointW} = Set{PointW}([P[i]])
+
+		for pa in A
+			if (pa[3]==-1)
+				push!(Z, Cov)
+				setdiff!(Cov, [pa[2]])
+			else
+				push!(Cov, pa[2])
+			end
+		end
+	end
+end
+
+function MCE(P::AbstractArray{PointW}, E::AbstractArray{Ellipse})
+
+end

### 2019-04-30 implementation/Ellipses.jl
WIP

@@ -18,8 +18,9 @@ struct Ellipse
 	dfx::Function
 	dfy::Function
 
+	# No use for the center
+	Ellipse(a::Real, b::Real) = Ellipse(a,b,Point(0,0))
 	Ellipse(a::Real, b::Real, cx::Real, cy::Real) = Ellipse(a,b,Point(cx,cy))
-
 	Ellipse(a::Real, b::Real, c::Point) = 
 	begin 
 		if (a<=0 || b<=0)
@@ -37,6 +38,10 @@ function ellipseinter(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,P
 	k::Float64 = e₂.center.y - e₁.center.y
 	a::Float64 = e₁.a
 	b::Float64 = e₁.b
+
+	if (h==0)
+		error("Try to find intersection of ellipses with the same center")
+	end
 
 	α = (-2k*a^2)/(2h*b^2)
 	β = (b^2*h^2 + a^2*k^2) / (2h*b^2)
@@ -74,7 +79,9 @@ function angles(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Real,Real}}
 	u = [e₁.dfx(s1), e₁.dfy(s1)]
 	v = -[e₂.dfx(t1), e₂.dfy(t1)]
 
-	@show (u[1] * v[2] - u[2]*v[1])
+	@show(ret)
+	@show(s1,s2,t1,t2)
+	#@show (u[1] * v[2] - u[2]*v[1])
 
 	return u[1] * v[2] - u[2] * v[1] >= 0 ? (s1,s2) : (s2,s1)
 end

### 2019-04-30 implementation/Utils.jl

@@ -15,7 +15,7 @@ function root2(a::Real, b::Real, c::Real)::Union{Nothing, Tuple{Real,Real}}
 	end
 
 	if (a==0)
-		return (-c / b, -c / b)
+		return (b!=0) ? (-c / b, -c / b) : nothing
 	end
 
 	return (-b + √Δ) / (2*a), (-b-√Δ)/(2*a)

### 2019-04-30 implementation/solution.jl

@@ -6,6 +6,18 @@ mutable struct PointW
 	x::Real
 	y::Real
 	w::Real
+
+	PointW(id::Int, x::Real, y::Real) = new(id,x,y,1)
+end
+
+mutable struct Solution
+	Cover::Set{PointW}
+	x::Real
+	y::Real
+end
+
+function Base.isless(lhs::PointW, rhs::PointW)
+	return (lhs.id != rhs.id) ? lhs.id < rhs.id : lhs.w < rhs.w
 end
 
 function hash(p::PointW)::UInt64
@@ -13,22 +25,25 @@ function hash(p::PointW)::UInt64
 end
 
 function sum(Z::Set{PointW})
-	return reduce(Z) do (pa,pb)
-		return pa.w + pb.w
+	ret = 0
+	for x in Z
+		ret += x.w
 	end
+	return ret
 end
 
-function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Set{PointW}}
-	Z::AbstractArray{Set{PointW}} = []
+function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Solution}
+	Z::AbstractArray{Solution} = []
 
 	n=length(P)
 
 	for i in 1:n 
 		e1 = Ellipse(E.a, E.b, P[i].x, P[i].y)
-		A::AbstractArray{Tuple{Real,PointW,Int}} = []
-		push!(Z, Set([P[i]]))
 
-		for j in 1:n
+		#angle, point, entering or leaving
+		A::AbstractArray{Tuple{Real,PointW,Int}} = [(0, P[1], 1), (2π, P[1], -1)]
+
+		for j in i+1:n
 			e2 = Ellipse(E.a, E.b, P[j].x, P[j].y)
 			ret = angles(e1, e2)
 			if (ret === nothing) continue end
@@ -45,15 +60,38 @@ function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Set{PointW}}
 
 		for pa in A
 			if (pa[3]==-1)
-				push!(Z, Cov)
+				push!(Z, Solution(copy(Cov), pa[2].x, pa[2].y))
 				setdiff!(Cov, [pa[2]])
 			else
 				push!(Cov, pa[2])
 			end
 		end
 	end
+
+	return Z
 end
 
[…]

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_1.tex
WIP

--- 2019-03-27 tex/figures/fig:array_disks.tex
@@
-\usetikzlibrary{matrix}
-
 \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
 
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\begin{tikzpicture}[x=1pt,y=1pt,yscale=-1.3,xscale=1.3]
 %uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
@@
 %Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
+\draw  [color=green  ,draw opacity=1 ] (57.81,32.47) ..
 controls (57.81,18.66) and (69,7.47) ..
@@
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
 % Text Node
@@
 % Text Node
-\draw (20,35) node [scale=0.5]  {$E_{1}$};
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
 \end{tikzpicture}
@@
 \matrix [matrix of nodes,row sep=,row sep=0mm,
-column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
 column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_2.tex
WIP

--- 2019-03-27 tex/figures/fig:array_disks.tex
@@
 % Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
+\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
 % Text Node
@@
 column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
 column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_2_5.tex
WIP

--- 2019-05-01 quali/quali.presentation/figures/mcd_sim_2.tex
@@
 %Shape: Circle [id:dp8913971633985722] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (33,53.5) ..
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
 controls (33,39.69) and (44.19,28.5) ..
@@
 column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 2/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
 column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
 column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
 column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_3.tex
WIP

--- 2019-05-01 quali/quali.presentation/figures/mcd_sim_2_5.tex
@@
 (21,59.5) -- cycle ;
+
 %Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) ..
+\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
 controls (47.5,33.14) and (58.69,21.94) ..
@@
 (47.5,46.94) -- cycle ;
+
 %Shape: Circle [id:dp8913971633985722] 
@@
 (33,53.5) -- cycle ;
+
 %Shape: Circle [id:dp05970043129919356] 
@@
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.5,color=red]  {$+$};
 % Text Node
@@
 % Text Node
-\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
+\draw (54.22,39.56) node [scale=0.5]  {$-$};
 % Text Node
@@
 column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 5/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
-column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 6/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
 column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_4.tex
WIP

--- 2019-05-01 quali/quali.presentation/figures/mcd_sim_1.tex
@@
 (47.5,46.94) -- cycle ;
+
 %Shape: Circle [id:dp8913971633985722] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (33,53.5) ..
+\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
 controls (33,39.69) and (44.19,28.5) ..
@@
 \matrix [matrix of nodes,row sep=,row sep=0mm,
-column 1/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
 column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
@@
 column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
 column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_5.tex
WIP

--- 2019-05-01 quali/quali.presentation/figures/mcd_sim_2_5.tex
@@
 \end{tikzpicture}
-
 \begin{tikzpicture}
@@
 column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 5/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
 column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
 column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
-column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
 column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_6.tex
WIP

--- 2019-04-29 quali/quali.presentation/figures/mcd_sim.tex
@@
-\usetikzlibrary{matrix}
-
 \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
 
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color=green  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color=green ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\begin{tikzpicture}[x=1pt,y=1pt,yscale=-1.3,xscale=1.3]
 %uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
@@
 \end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
 
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
+\begin{tikzpicture}
 
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 },draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
+\matrix [matrix of nodes,row sep=,row sep=0mm,
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
+column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
+] (O)
+{
+	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+};
 
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 } ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5,color=red]  {\textbf{$-$}};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\node at (-4,-0.5) {$0$};
+\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-01 quali/quali.presentation/figures/mcd_sim_7.tex
WIP

--- 2019-04-29 quali/quali.presentation/figures/mcd_sim.tex
@@
-\usetikzlibrary{matrix}
-
 \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
 
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color=green  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color=green ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color=green  ,draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
-
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
-
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 },draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
-
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color=green  ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5,color=red]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
-\end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\begin{tikzpicture}[x=1pt,y=1pt,yscale=-1.3,xscale=1.3]
 %uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
@@
 \end{tikzpicture}
+
+\begin{tikzpicture}
+
+\matrix [matrix of nodes,row sep=,row sep=0mm,
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
+column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
+] (O)
+{
+	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+};
+
+\node at (-4,-0.5) {$0$};
+\node at (0,-0.5) {$2\pi$};
+\end{tikzpicture}

### 2019-05-01 quali/quali.presentation/slides.tex
WIP

@@
 \newcommand{\bigO}{\mathscr{O}}
-
+\usetikzlibrary{matrix}
 \usepackage{pgfplots}
@@
 	\begin{itemize}
-		\item Set Cover Problem
+		\item Minimum Cover Problem
 		\item Maximal Covering Problem
@@
 		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
-		\item Adapt it for the $m$ ellipses case
+		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm
 	\end{itemize}
@@
 
+\end{frame}
+
+\begin{frame}
+	\begin{figure}
+		\only<1>{\caption{Maximal cover by two disks.}}
+		\only<2>{\caption{Minimum number of disks needed to cover the set of points.}}
+		\only<1>{\input{figures/intro_a.tex}}
+		\only<2>{\input{figures/intro_b.tex}}
+		\source{Elaborated by the author.}
+	\end{figure}
 \end{frame}
@@
 
-		\caption{The elliptical and euclidean norms}
+		\caption{The elliptical and euclidean norms.}
 		\input{figures/elliptical.and.euclidean.norms.tex}
@@
 
-		\caption{An instance of $MCD(\Pp,1)$.}
-		%\input{figures/elliptical.and.euclidean.norms.tex}
-      \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
+		\only<1>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
+
+		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
+
+		\only<1>{\input{figures/max_w_clique.tex}}
+		\only<2>{\input{figures/max_w_clique_b.tex}}
+      %\center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
 		\source{Elaborated by the author.}
@@
 
-\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+	Defining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$:
+
+	Let $D_i$ and $D_j$ be two unit disks that intersect at two points.
+
+	\begin{itemize}
+		\item Assume $D_i$ is at the origin
+		\item We can find the polar angle of the intersection points. Let's call them $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ with the following condition:
+		\begin{itemize}
+			\item The arc defined by $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ bounds the region $D_i \cap D_j$
+
+		\end{itemize}
+		\item Later it will be shown how to find which one is which algorithmically.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
 	\begin{figure}[H]
@@
 
-		\caption{An instance of Maximum Weight Clique Problem.}
-		%\input{figures/elliptical.and.euclidean.norms.tex}
-		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
-		\source{Elaborated by the author.}
-		\label{fig:max_wieght_clique}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles (with respect to $D_i$) of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
-	\begin{figure}[H]
-		\centering
-
-		\caption{Three disks and their intersection points.}
+		\caption{Three disks and their intersection points and angles.}
 		\input{figures/img2.tex}
@@
 
-		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. Work-around: repeat it.
+		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. The traversal is on a circle, where to start?
+
+		\item If the traversal reaches a opening angle, we mark the intersecting disk as active. If it reaches a closing angle we unmark it.
+
+		\item We want to find a point in the traversal with the most active disks.
 	\end{itemize}
@@
 
-	The algorithm is described simply as:
+	For every disk, traverse the sorted list of intersection angles twice, keeping a set of active disks, and the current best solution.
 
-	For every disk, traverse the sorted list of intersection angles twice, keeping a set of active disks, and the current best solution.
+	Doing the traversal twice solves the problem of deciding where to start.
 
@@
 
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-\begin{figure}
+%\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+%\begin{figure}
 	%\centering
 
+%	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
+%	\input{figures/mcd_sim.tex}
+%		\source{Elaborated by the author.}
+	%\label{fig:array_disks}
+%\end{figure}
+%\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+
+	\begin{figure}
 		\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
-	\input{figures/mcd_sim.tex}
+		\only<1>{\input{figures/mcd_sim_1.tex}}
+		\only<2>{\input{figures/mcd_sim_2.tex}}
+		\only<3>{\input{figures/mcd_sim_2_5.tex}}
+		\only<4>{\input{figures/mcd_sim_3.tex}}
+		\only<5>{\input{figures/mcd_sim_4.tex}}
+		\only<6>{\input{figures/mcd_sim_5.tex}}
+		\only<7>{\input{figures/mcd_sim_6.tex}}
+		\only<8>{\input{figures/mcd_sim_7.tex}}
 			\source{Elaborated by the author.}
-	%\label{fig:array_disks}
 	\end{figure}
@@
 
-\begin{frame}{Maximum Weight Clique Problem}{Multiple disks}
+\begin{frame}{Maximum Covering by Disks}{Multiple disks}
+
+	Works found in the literature:
+
 	\begin{itemize}
@@
 	\end{itemize}
+
+	Because of the similarities, we will discuss only the multiple ellipses algorithm later.
 

### 2019-05-01 implementation/Utils.jl
WIP

@@ -1,6 +1,15 @@
 module Utils 
 
-export Point, root2 
+export Point, PointW, root2 
+
+mutable struct PointW
+	id::Int
+	x::Real
+	y::Real
+	w::Real
+
+	PointW(id::Int, x::Real, y::Real) = new(id,x,y,1)
+end
 
 struct Point
 	x::Real

### 2019-05-01 implementation/main.jl

@@ -5,6 +5,7 @@ using Printf
 using LaTeXStrings
 
 include("plotting.jl")
+include("solution.jl")
 
 using Utils
 using Ellipses
@@ -41,61 +42,22 @@ end
 
 function main()
 
-	e₁ = Ellipse(3,2,0,0)
-	e₂ = Ellipse(3,2,1,1)
-	e₃ = Ellipse(3,2,rand(1),rand(1))
-	pgfplots()  
+	P::Array{PointW} = []
+	xmax = 5
+	ymax = 5
+	n = 20
 
-	ret = ellipseinter(e₁, e₂, e₃)
-
-	if (ret === nothing)
-		return nothing
+	for i in n
+		push!(P, PointW(i, rand() * xmax, rand() * ymax))
 	end
 
-	a1, a2 = angles(e₁, e₂)
-	p₁, p₂ = (Point(e₁.fx(a1), e₁.fy(a1)),
-			  Point(e₁.fx(a2), e₁.fy(a2)))
+	ret = ex1(P, 3, 2)
 
-	@show(ret)
-	@show(a1,a2)
-	@show(p₁, p₂)
+	plt = plotpointsellipse(map(p -> p.x, P), map(p -> p.y, P), ret)
 
-	#@printf("%.3f %.3f\n", e₁.fx(a1), p₁.y)
-
-	plt = plot(e₁.fx, e₁.fy, 0, 2π, dpi=300, label=L"$E_1$")
-	plot!(e₂.fx, e₂.fy, 0, 2π,dpi=300, label=L"E_2")
-	plot!([p₁.x, p₂.x], [p₁.y, p₂.y], seriestype=:scatter,color=:black,lab="")
-
-	b1, b2 = angles(e₂, e₁)
+	savefig(plt, "b.pdf")
 
 
-	dfx1 = e₁.dfx(a1)	
-	dfy1 = e₁.dfy(a1)
-
-	dfx2 = -e₂.dfx(b2)
-	dfy2 = -e₂.dfy(b2)
-
-	quiver!([p₁.x, p₁.x], [p₁.y, p₁.y], 
-			gradient=(
-					  versor([dfx1, dfx2]),
-					  versor([dfy1, dfy2]))
-			)
-
-	dfx1 = e₁.dfx(a2)	
-	dfy1 = e₁.dfy(a2)
-
-	dfx2 = -e₂.dfx(b1)
-	dfy2 = -e₂.dfy(b1)
[…]

### 2019-05-01 implementation/plotting.jl

@@ -9,6 +9,14 @@ function versor(A::AbstractArray)::AbstractArray{Real}
 	return map(x -> x / norm(A), A)
 end
 
+function plotpointsellipse(X::AbstractArray{Real}, Y::AbstractArray{Real}, E::Ellipse)
+	plt = plot(X, Y, seriestype=:scatter,color=:black,lab="")
+
+	plot!(E.fx, E.fy, 0, 2π, dpi=300, label=L"E_1", xaxis=false,yaxis=false, color=colors[1])
+
+	return plt
+end
+
 function plotwihtoutquiver(E::AbstractArray{Ellipse})
 
 	e1 = E[1]

### 2019-05-01 implementation/solution.jl

@@ -1,19 +1,12 @@
 push!(LOAD_PATH, pwd())
-using Ellipses
+using Ellipses 
+using Utils
 
-mutable struct PointW
-	id::Int
-	x::Real
-	y::Real
-	w::Real
-
-	PointW(id::Int, x::Real, y::Real) = new(id,x,y,1)
-end
-
-mutable struct Solution
+struct Solution
 	Cover::Set{PointW}
 	x::Real
 	y::Real
+	Solution() = new(Set{PointW}(), 0, 0)
 end
 
 function Base.isless(lhs::PointW, rhs::PointW)
@@ -60,8 +53,9 @@ function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Solution}
 
 		for pa in A
 			if (pa[3]==-1)
-				push!(Z, Solution(copy(Cov), pa[2].x, pa[2].y))
-				setdiff!(Cov, [pa[2]])
+				tmp::Solution = Solution(Cov, pa[2].x, pa[2].y)
+				push!(Z,tmp)
+				#setdiff!(Cov, [pa[2]])
 			else
 				push!(Cov, pa[2])
 			end
@@ -75,23 +69,27 @@ function MCE(P::AbstractArray{PointW}, E::AbstractArray{Ellipse})
 
 end
 
-function MCE1(P::AbstractArray{PointW}, a::Real, b::Real)
+function MCE1(P::AbstractArray{PointW}, a::Real, b::Real)::Solution
 	e::Ellipse = Ellipse(a,b)
 	Z = MCE1(P,e)
 
 	fopt = 0
+	optSolution = Solution()
 
 	for s in Z
 		zf = sum(s.Cover)
 		if (zf > fopt)
 			fopt = zf
+			optSolution = zf
 		end
 	end
 
-	return fopt
+	return optSolution 
 end
 
-function ex1()
-	@show(MCE1([PointW(1,0,0), PointW(2, 1, 1), PointW(3,2,2)], 3,2))
+function ex1(P::AbstractArray{PointW}, a::Real, b::Real)::Ellipse
+	so::Solution = MCE1(P, a,b)
+
+	return Ellipse(a, b, so.x, so.y)
 end
 

### 2019-05-02 implementation/Ellipses.jl
WIP

@@ -1,8 +1,8 @@
+push!(LOAD_PATH, pwd())
 module Ellipses
 
-include("Utils.jl")
 #import .Utils
-using .Utils
+using Utils
 
 #exports
 export Ellipse
@@ -78,10 +78,6 @@ function angles(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Real,Real}}
 	
 	u = [e₁.dfx(s1), e₁.dfy(s1)]
 	v = -[e₂.dfx(t1), e₂.dfy(t1)]
-
-	@show(ret)
-	@show(s1,s2,t1,t2)
-	#@show (u[1] * v[2] - u[2]*v[1])
 
 	return u[1] * v[2] - u[2] * v[1] >= 0 ? (s1,s2) : (s2,s1)
 end

### 2019-05-02 implementation/Utils.jl

@@ -2,19 +2,26 @@ module Utils
 
 export Point, PointW, root2 
 
-mutable struct PointW
+struct PointW{T<:Real}
 	id::Int
-	x::Real
-	y::Real
-	w::Real
+	x::T
+	y::T
+	w::T
 
-	PointW(id::Int, x::Real, y::Real) = new(id,x,y,1)
+	#PointW{T}(id::Int, x::T, y::T) where {T<:Real} = new(id,x,y,1.0)
 end
 
-struct Point
-	x::Real
-	y::Real
+struct Point{T<:Real}
+	x::T
+	y::T
+	Point{T}(x::T, y::T) where {T<:Real} = new(x,y)
 end
+
+#PointW(id::Int, x::T, y::T, w::T) where {T<:Real} = PointW{T}(id, x, y, w)
+PointW(id::Int, x::T, y::T) where {T<:Real} = PointW{T}(id, x, y, 1.0)
+PointW(id::Int, p::Point{T}, w::Float64) where {T<:Real} = PointW{T}(id, p.x, p.y, w)
+
+Point(x::T, y::T) where {T<:Real} = Point{T}(x,y)
 
 function root2(a::Real, b::Real, c::Real)::Union{Nothing, Tuple{Real,Real}}
 	Δ = b^2 - 4*a*c

### 2019-05-02 implementation/main.jl

@@ -42,23 +42,28 @@ end
 
 function main()
 
-	P::Array{PointW} = []
+	P::Vector{PointW} = []
 	xmax = 5
 	ymax = 5
 	n = 20
 
-	for i in n
+	for i in 1:n
 		push!(P, PointW(i, rand() * xmax, rand() * ymax))
 	end
 
-	ret = ex1(P, 3, 2)
-
-	plt = plotpointsellipse(map(p -> p.x, P), map(p -> p.y, P), ret)
-
-	savefig(plt, "b.pdf")
+	#ret = ex1(P, 1, 1)
+	#@show(length(ret.Cover))
+	#@show(ret.x, ret.y)
 
 
-	return ret
+
+
+
+	ret2 = ex2(P, Ellipse(1,1), Ellipse(1.4, 1))
+	plt = plotpointsellipse(map(p -> p.x, P), map(p -> p.y, P), [ret2...])
+	savefig(plt, "c.pdf")
+
+	#return ret
 end
 
 #main()

### 2019-05-02 implementation/plotting.jl

@@ -9,10 +9,19 @@ function versor(A::AbstractArray)::AbstractArray{Real}
 	return map(x -> x / norm(A), A)
 end
 
-function plotpointsellipse(X::AbstractArray{Real}, Y::AbstractArray{Real}, E::Ellipse)
-	plt = plot(X, Y, seriestype=:scatter,color=:black,lab="")
+function plotpointsellipse(X::AbstractVector{<:Real}, Y::AbstractVector{<:Real}, Es::AbstractVector{Ellipse})
+	plt = plot(X, Y, seriestype=:scatter,lab="", 
+			   markersize = 2.5, 
+			   markerstrokewidth=0.5,
+			   grid=false,
+			   aspect_ratio=:equal, xaxis=false,yaxis=false)
 
-	plot!(E.fx, E.fy, 0, 2π, dpi=300, label=L"E_1", xaxis=false,yaxis=false, color=colors[1])
+
+	i=1
+	for E in Es
+		plot!(E.fx, E.fy, 0, 2π, dpi=300, label=latexstring("E_", "$i"))
+		i+=1
+	end
 
 	return plt
 end

### 2019-05-02 implementation/solution.jl

@@ -4,17 +4,21 @@ using Utils
 
 struct Solution
 	Cover::Set{PointW}
-	x::Real
-	y::Real
-	Solution() = new(Set{PointW}(), 0, 0)
+	p::Point
+	Solution() = new(Set{PointW}(), Point(0.0, 0.0))
+	Solution(Cover::Set{PointW}, p::Point{T}) where {T<:Real} = new(Cover,p)
 end
 
 function Base.isless(lhs::PointW, rhs::PointW)
 	return (lhs.id != rhs.id) ? lhs.id < rhs.id : lhs.w < rhs.w
 end
 
-function hash(p::PointW)::UInt64
+function Base.hash(p::PointW)::UInt64
 	return p.id
+end
+
+function Base.isequal(x::PointW, y::PointW) 
+	return x.id==y.id
 end
 
 function sum(Z::Set{PointW})
@@ -34,7 +38,8 @@ function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Solution}
 		e1 = Ellipse(E.a, E.b, P[i].x, P[i].y)
 
 		#angle, point, entering or leaving
-		A::AbstractArray{Tuple{Real,PointW,Int}} = [(0, P[1], 1), (2π, P[1], -1)]
+		A::AbstractArray{Tuple{Real,PointW,Int}} = 
+		[(0, PointW(i,e1.center,P[i].w), 1), (2π, PointW(i,e1.center,P[i].w), -1)]
 
 		for j in i+1:n
 			e2 = Ellipse(E.a, E.b, P[j].x, P[j].y)
@@ -43,21 +48,33 @@ function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Solution}
 
 			a1, a2 = ret
 
-			push!(A, (a1, P[j], 1))
-			push!(A, (a2, P[j], -1))
+			p1 = PointW(j, e1.fx(a2), e1.fy(a2), P[j].w)
+			p2 = PointW(j, e1.fx(a2), e1.fy(a2), P[j].w)
+
+			push!(A, (a1, p1, 1))
+			push!(A, (a2, p2, -1))
 		end
 		
 		sort!(A)
 
-		Cov::Set{PointW} = Set{PointW}([P[i]])
+		Cov::Set{PointW} = Set{PointW}()
 
-		for pa in A
-			if (pa[3]==-1)
[…]

### 2019-05-04 quali/quali.presentation/figures/example_2_ellipses.tex
wip

\begin{tikzpicture}[scale=0.8]
\begin{axis}[height = {101.6mm}, axis equal = {true}, ylabel = {}, xmin = {-0.04304650080536887}, xmax = {5.015893955055976}, ymax = {4.953655933510717}, xlabel = {}, unbounded coords=jump,scaled x ticks = false,xlabel style = {font = {\fontsize{11 pt}{14.3 pt}\selectfont}, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0, rotate = 0.0},xmajorgrids = true,xtick = {0.0,1.0,2.0,3.0,4.0,5.0},xticklabels = {},xtick align = inside,xticklabel style = {font = {\fontsize{8 pt}{10.4 pt}\selectfont}, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0, rotate = 0.0},x grid style = {color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 0.1,
line width = 0.5,
solid},axis lines* = left,separate axis lines,x axis line style = {draw opacity = 0},scaled y ticks = false,ylabel style = {font = {\fontsize{11 pt}{14.3 pt}\selectfont}, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0, rotate = 0.0},ymajorgrids = true,ytick = {0.0,1.0,2.0,3.0,4.0},yticklabels = {},ytick align = inside,yticklabel style = {font = {\fontsize{8 pt}{10.4 pt}\selectfont}, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0, rotate = 0.0},y grid style = {color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 0.1,
line width = 0.5,
solid},axis lines* = left,separate axis lines,y axis line style = {draw opacity = 0},    xshift = 0.0mm,
    yshift = 0.0mm,
    axis background/.style={fill={rgb,1:red,1.00000000;green,1.00000000;blue,1.00000000}}
,legend style = {color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 1,
solid,fill = {rgb,1:red,1.00000000;green,1.00000000;blue,1.00000000},font = {\fontsize{8 pt}{10.4 pt}\selectfont}},colorbar style={title=}, ymin = {-0.025453315895344608}, width = {152.4mm}]\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.602918949315934, 0.1421191370308239)
};
\addplot+[draw=none, color = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.396020400537423, 2.2686705873010817)
};
\addplot+[draw=none, color = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(4.872716394984428, 3.773817627065047)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(3.202948490978642, 1.6235525016076402)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.848573275272137, 0.20375192853344104)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(1.8690841880778053, 1.6568512573232197)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.300100178756294, 4.05463630589837)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(1.6738171002119706, 3.3074971831952427)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.907448354814198, 4.598195661337079)
};
\addplot+[draw=none, color = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(0.1001310592661786, 3.3500841191834887)
};
\addplot+[draw=none, color = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(0.9130732329791647, 3.4401427131346485)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(3.4385814568108195, 4.065543992107185)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.354854569358288, 0.5753620833645212)
};
\addplot+[draw=none, color = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(4.393915159418624, 4.812737747206772)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(3.50505217637773, 0.20556942673409795)
};
\addplot+[draw=none, color = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,1.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(3.427160885660112, 2.538013336230315)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.1063177109467004, 4.409416548982065)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(2.3672535618848976, 1.8968192015410446)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(3.213442183570654, 2.9502323475574324)
};
\addplot+[draw=none, color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000},
draw opacity = 1.0,
line width = 0,
solid,mark = *,
mark size = 1.25,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, fill opacity = 1.0,
    line width = 0.5,
    rotate = 0,
    solid
},forget plot] coordinates {
(3.1034740796888682, 3.8975002907243397)
};
\addplot+ [color = {rgb,1:red,0.88887350;green,0.43564919;blue,0.27812294},
draw opacity = 1.0,
line width = 1,
solid,mark = none,
mark size = 2.0,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.88887350;green,0.43564919;blue,0.27812294}, fill opacity = 1.0,
    line width = 1,
    rotate = 0,
    solid
}]coordinates {
(3.5821391801246905, 3.725768625135797)
(3.581640769250864, 3.7573371749006075)
(3.5801460334561837, 3.7888742564484703)
(3.5776564627257965, 3.8203484329306416)
(3.574174538717948, 3.8517283302035143)
(3.5697037322902143, 3.8829826681030477)
(3.564248500039671, 3.9140802916255146)
(3.557814279860464, 3.9449902019834884)
(3.5504074855231975, 3.9756815875061053)
(3.5420355002815476, 4.006123854352811)
(3.532706669512473, 4.036286657009966)
(3.522430292397366, 4.06613992853991)
(3.511216612652421, 4.095653910552343)
(3.4990768083174792, 4.124799182868138)
(3.486022980613514, 4.153546692846007)
(3.4720681418798707, 4.1818677843428125)
(3.4572262026032843, 4.209734226278636)
(3.4415119575516027, 4.237118240778123)
(3.424941071026041, 4.263992530860086)
(3.407530061246667, 4.290330307647715)
(3.389296283886676, 4.316105317072325)
(3.3702579147718827, 4.341291866043976)
(3.3504339317626615, 4.365864848062904)
(3.3298440958363997, 4.389799768246228)
(3.30850893138933, 4.413072767744981)
(3.2864497057773625, 4.43566064752713)
(3.2636884081163244, 4.457540891502873)
(3.2402477273627284, 4.478691688969174)
(3.2161510296969293, 4.499091956351136)
(3.191422335231207, 4.518721358218576)
(3.166086294065997, 4.537560327556817)
(3.1401681617181305, 4.555590085271523)
(3.1136937739455917, 4.572792658908096)
(3.086689520993868, 4.58915090056702)
(3.05918232128958, 4.604648503997257)
(3.0311995946076107, 4.619270020850671)
(3.0027692347384747, 4.633000876081278)
(2.973919581683184, 4.645827382473971)
(2.944679393403315, 4.657736754288232)
(2.9150778171544514, 4.668717120003234)
(2.885144360431563, 4.678757534151636)
(2.8549088615552938, 4.68784798823026)
(2.8244014599284735, 4.6959794206767835)
(2.7936525659925096, 4.703143725902504)
(2.762692830913593, 4.709333762372166)
(2.7315531160289512, 4.7145433597228)
(2.7002644620835987, 4.718767324914467)
(2.6688580582882415, 4.722001447406804)
(2.6373652112291985, 4.724242503356176)
(2.6058173136613147, 4.725488258829275)
(2.574245813214977, 4.725737472029953)
(2.5426821810484377, 4.724989894537073)
(2.5111578804766745, 4.723246271552136)
(2.4797043356080772, 4.720508341156454)
(2.4483529000202116, 4.716778832578589)
(2.4171348255058915, 4.7120614634738)
(2.3860812309207127, 4.706360936218201)
(2.3552230711631004, 4.699682933221335)
(2.3245911063177935, 4.692034111261819)
(2.294215870993524, 4.683422094851727)
(2.2641276438854523, 4.673855468636306)
(2.234356417592708, 4.663343768836622)
(2.2049318687211144, 4.651897473743638)
(2.175883328300902, 4.639527993273234)
(2.1472397525488973, 4.626247657592549)
(2.1190296940043427, 4.612069704829006)
(2.091281273067097, 4.597008267874257)
(2.0640221499666134, 4.581078360296209)
(2.03727949718962, 4.564295861373174)
(2.0110799723939956, 4.5466775002650595)
(1.9854496918358344, 4.528240839337375)
(1.9604142043361954, 4.509004256654688)
(1.9359984658134808, 4.4889869276609655)
(1.9122268144068353, 4.46820880606508)
(1.8891229462153587, 4.446690603950513)
(1.8667098916773193, 4.424453771129103)
(1.8450099926129115, 4.401520473759406)
(1.824044879953445, 4.377913572250984)
(1.8038354521791604, 4.353656598476655)
(1.7844018544871711, 4.328773732315412)
(1.7657634587102913, 4.303289777549385)
(1.747938844006773, 4.277230137138904)
(1.730945778340196, 4.2506207879002655)
(1.714801200767976, 4.22348825461148)
(1.6995212045561434, 4.1958595835718)
(1.685121021137227, 4.167762315641376)
(1.6716150049272283, 4.139224458787931)
(1.6590166190168298, 4.110274460167808)
(1.6473384217510922, 4.080941177769225)
(1.6365920542110235, 4.051253851646009)
(1.6267882286094957, 4.021242074770467)
(1.6179367176130788, 3.9909357635344755)
(1.6100463446004336, 3.9603651279281658)
(1.603124974866976, 3.929560641425949)
(1.59717950778458, 3.8985530106098967)
(1.5922158699241333, 3.8673731445607484)
(1.5882390091478027, 3.8360521240470717)
(1.5852528896768971, 3.8046211705432733)
(1.583260488140247, 3.773111615107355)
(1.5822637906070331, 3.7415548671494343)
(1.5822637906070331, 3.70998238312216)
(1.583260488140247, 3.678425635164239)
(1.5852528896768971, 3.6469160797283204)
(1.5882390091478027, 3.615485126224522)
(1.592215869924133, 3.5841641057108458)
(1.5971795077845798, 3.552984239661697)
(1.6031249748669758, 3.5219766088456446)
(1.6100463446004336, 3.4911721223434284)
(1.6179367176130786, 3.460601486737118)
(1.6267882286094957, 3.430295175501127)
(1.6365920542110233, 3.4002833986255854)
(1.6473384217510922, 3.3705960725023685)
(1.6590166190168296, 3.3412627901037864)
(1.6716150049272283, 3.312312791483663)
(1.6851210211372267, 3.283774934630218)
(1.6995212045561434, 3.255677666699794)
(1.7148012007679758, 3.2280489956601137)
(1.7309457783401958, 3.2009164623713287)
(1.747938844006773, 3.1743071131326897)
(1.7657634587102913, 3.1482474727222085)
(1.784401854487171, 3.122763517956183)
(1.8038354521791602, 3.097880651794939)
(1.824044879953445, 3.0736236780206103)
(1.8450099926129115, 3.050016776512188)
(1.866709891677319, 3.0270834791424903)
(1.8891229462153585, 3.004846646321081)
(1.912226814406835, 2.983328444206514)
(1.9359984658134803, 2.9625503226106287)
(1.9604142043361952, 2.9425329936169065)
(1.985449691835834, 2.923296410934219)
(2.0110799723939956, 2.9048597500065343)
(2.03727949718962, 2.8872413888984196)
(2.064022149966613, 2.870458889975385)
(2.091281273067097, 2.8545289823973374)
(2.1190296940043423, 2.8394675454425884)
(2.1472397525488973, 2.825289592679045)
(2.175883328300902, 2.81200925699836)
(2.204931868721114, 2.7996397765279557)
(2.234356417592708, 2.7881934814349716)
(2.264127643885452, 2.7776817816352875)
(2.294215870993524, 2.7681151554198675)
(2.324591106317794, 2.759503139009775)
(2.3552230711631, 2.751854317050259)
(2.3860812309207122, 2.745176314053393)
(2.4171348255058906, 2.739475786797794)
(2.448352900020211, 2.734758417693005)
(2.4797043356080772, 2.73102890911514)
(2.511157880476674, 2.7282909787194582)
(2.5426821810484377, 2.726547355734521)
(2.5742458132149766, 2.7257997782416403)
(2.6058173136613143, 2.726048991442319)
(2.637365211229199, 2.727294746915418)
(2.668858058288241, 2.72953580286479)
(2.7002644620835987, 2.732769925357127)
(2.731553116028951, 2.7369938905487943)
(2.7626928309135925, 2.742203487899427)
(2.7936525659925096, 2.7483935243690896)
(2.8244014599284735, 2.7555578295948107)
(2.8549088615552938, 2.763689262041334)
(2.8851443604315627, 2.7727797161199574)
(2.9150778171544514, 2.7828201302683597)
(2.944679393403314, 2.793800495983362)
(2.9739195816831834, 2.8057098677976224)
(3.0027692347384747, 2.8185363741903156)
(3.0311995946076102, 2.8322672294209226)
(3.05918232128958, 2.8468887462743364)
(3.0866895209938674, 2.862386349704573)
(3.1136937739455917, 2.878744591363498)
(3.1401681617181305, 2.895947165000071)
(3.1660862940659964, 2.913976922714776)
(3.191422335231207, 2.9328158920530183)
(3.2161510296969285, 2.9524452939204573)
(3.240247727362728, 2.9728455613024196)
(3.2636884081163244, 2.99399635876872)
(3.2864497057773625, 3.0158766027444637)
(3.30850893138933, 3.0384644825266127)
(3.3298440958363993, 3.0617374820253653)
(3.350433931762661, 3.0856724022086897)
(3.3702579147718827, 3.1102453842276176)
(3.389296283886676, 3.135431933199268)
(3.407530061246667, 3.161206942623879)
(3.4249410710260406, 3.187544719411508)
(3.441511957551602, 3.21441900949347)
(3.4572262026032843, 3.2418030239929583)
(3.4720681418798707, 3.2696694659287804)
(3.486022980613514, 3.2979905574255874)
(3.4990768083174792, 3.3267380674034555)
(3.511216612652421, 3.35588333971925)
(3.522430292397366, 3.3853973217316833)
(3.532706669512473, 3.4152505932616277)
(3.5420355002815476, 3.4454133959187825)
(3.5504074855231975, 3.475855662765488)
(3.557814279860464, 3.5065470482881054)
(3.5642485000396706, 3.5374569586460782)
(3.569703732290214, 3.568554582168546)
(3.574174538717948, 3.5998089200680794)
(3.5776564627257965, 3.6311888173409517)
(3.5801460334561837, 3.662662993823123)
(3.581640769250864, 3.694200075370986)
(3.5821391801246905, 3.7257686251357964)
};
\addlegendentry{$E_1$}
\addplot+ [color = {rgb,1:red,0.24222430;green,0.64327509;blue,0.30444865},
draw opacity = 1.0,
line width = 1,
solid,mark = none,
mark size = 2.0,
mark options = {
    color = {rgb,1:red,0.00000000;green,0.00000000;blue,0.00000000}, draw opacity = 1.0,
    fill = {rgb,1:red,0.24222430;green,0.64327509;blue,0.30444865}, fill opacity = 1.0,
    line width = 1,
    rotate = 0,
    solid
}]coordinates {
(4.324183803520279, 1.1154337173027569)
(4.323486028296922, 1.1470022670675675)
(4.3213933981843695, 1.1785393486154305)
(4.317907999161827, 1.2100135250976018)
(4.31303330555084, 1.2413934223704743)
(4.306774176552012, 1.2726477602700077)
(4.299136851401252, 1.3037453837924748)
(4.290128943150362, 1.3346552941504481)
(4.279759431078189, 1.3653466796730651)
(4.268038651739879, 1.3957889465197713)
(4.254978288663175, 1.4259517491769258)
(4.240591360702025, 1.4558050207068698)
(4.224892209059101, 1.4853190027193037)
(4.207896482990183, 1.5144642750350978)
(4.189621124204632, 1.5432117850129665)
(4.1700843499775315, 1.5715328765097727)
(4.14930563499031, 1.5993993184455957)
(4.127305691917956, 1.6267833329450836)
(4.10410645078217, 1.6536576230270454)
(4.079731037091046, 1.679995399814675)
(4.054203748787058, 1.7057704092392854)
(4.027550032026348, 1.730956958210936)
(3.999796455813438, 1.7555299402298639)
(3.9709706855166718, 1.7794648604131882)
(3.941101455290774, 1.8027378599119412)
(3.9102185394340196, 1.8253257396940898)
(3.8783527227085663, 1.8472059836698336)
(3.8455357696535315, 1.868356781136134)
(3.811800392921413, 1.8887570485180958)
(3.7771802206694023, 1.9083864503855354)
(3.7417097630381075, 1.9272254197237775)
(3.705424377751095, 1.9452551774384825)
(3.668360234869541, 1.9624577510750556)
(3.6305542807371274, 1.9788159927339801)
(3.592044201151124, 1.994313596164217)
(3.5528683837963673, 2.008935113017631)
(3.5130658799795773, 2.022665968248238)
(3.4726763657021693, 2.0354924746409315)
(3.4317401021103535, 2.0474018464551915)
(3.3902978953619445, 2.058382212170194)
(3.3483910559499006, 2.068422626318596)
(3.3060613575231232, 2.0775130803972197)
(3.2633509952455753, 2.0856445128437433)
(3.2203025437352255, 2.092808818069464)
(3.176958914624742, 2.0989988545391265)
(3.133363313786244, 2.1042084518897592)
(3.08955919826275, 2.1084324170814264)
(3.0455902329492504, 2.1116665395737635)
(3.0015002470665904, 2.113907595523136)
(2.9573331904715525, 2.115153350996235)
(2.9131330898466805, 2.115402564196913)
(2.868944004813525, 2.1146549867040325)
(2.824809984013057, 2.1129113637190957)
(2.7807750211970204, 2.1101734333234137)
(2.736883011374008, 2.106443924745549)
(2.69317770705396, 2.1017265556407594)
(2.64970267463471, 2.096026028385161)
(2.606501250974053, 2.089348025388295)
(2.5636165001906237, 2.0816992034287787)
(2.521091170736646, 2.0730871870186864)
(2.4789676527853457, 2.0635205608032665)
(2.4372879359755037, 2.053008861003582)
(2.3960935675552726, 2.0415625659105983)
(2.3554256109669747, 2.029193085440194)
(2.315324604914169, 2.0159127497595084)
(2.275830522951792, 2.0017347969959656)
(2.236982733639648, 1.9866733600412165)
(2.198819961298971, 1.9707434524631688)
(2.1613802474111803, 1.9539609535401343)
(2.1247009126973064, 1.9363425924320194)
(2.088818519915881, 1.9179059315043347)
(2.053768837416386, 1.8986693488216475)
(2.019586803484586, 1.8786520198279255)
(1.9863064915152817, 1.85787389823204)
(1.9539610760472146, 1.8363556961174732)
(1.9225827996939593, 1.8141188632960634)
(1.8922029410037886, 1.7911855659263658)
(1.8628517832805356, 1.7675786644179436)
(1.834558584396537, 1.743321690643615)
(1.807351547627752, 1.7184388244823714)
(1.7812577935401204, 1.6929548697163455)
(1.7563033329551947, 1.6668952293058643)
(1.7325130410219867, 1.6402858800672253)
(1.7099106324208786, 1.6131533467784402)
(1.6885186377243133, 1.5855246757387598)
(1.6683583809378302, 1.557427407808336)
(1.649449958243832, 1.528889550954891)
(1.6318122179692742, 1.4999395523347678)
(1.6154627417972416, 1.4706062699361855)
(1.6004178272411451, 1.4409189438129686)
(1.5866924713990063, 1.410907166937427)
(1.5743003560040227, 1.3806008557014355)
(1.5632538337863193, 1.3500302200951257)
(1.5535639161594788, 1.3192257335929092)
(1.5452402622441246, 1.2882181027768567)
(1.5382911692394992, 1.2570382367277084)
(1.5327235641526362, 1.225717216214032)
(1.5285429968933686, 1.1942862627102335)
(1.525753634742058, 1.1627767072743151)
(1.5243582581955588, 1.131219959316394)
(1.5243582581955588, 1.0996474752891199)
(1.525753634742058, 1.0680907273311988)
(1.5285429968933686, 1.0365811718952804)
(1.532723564152636, 1.005150218391482)
(1.538291169239499, 0.9738291978778055)
(1.5452402622441244, 0.9426493318286573)
(1.5535639161594788, 0.9116417010126048)
(1.5632538337863193, 0.8808372145103882)
(1.5743003560040225, 0.8502665789040784)
(1.5866924713990063, 0.819960267668087)
(1.600417827241145, 0.7899484907925455)
(1.6154627417972414, 0.7602611646693285)
(1.631812217969274, 0.7309278822707461)
(1.649449958243832, 0.701977883650623)
(1.66835838093783, 0.673440026797178)
(1.688518637724313, 0.6453427588667542)
(1.7099106324208786, 0.6177140878270737)
(1.7325130410219864, 0.5905815545382885)
(1.7563033329551945, 0.5639722052996495)
(1.7812577935401201, 0.5379125648891684)
(1.8073515476277517, 0.5124286101231426)
(1.8345585843965369, 0.48754574396189876)
(1.8628517832805351, 0.4632887701875703)
(1.8922029410037884, 0.43968186867914816)
(1.922582799693959, 0.41674857130945053)
(1.9539610760472144, 0.39451173848804066)
(1.9863064915152815, 0.372993536373474)
(2.019586803484585, 0.35221541477758866)
(2.053768837416386, 0.33219808578386645)
(2.08881851991588, 0.3129615031011793)
(2.124700912697306, 0.2945248421734944)
(2.1613802474111807, 0.2769064810653794)
(2.19881996129897, 0.2601239821423452)
(2.236982733639648, 0.24419407456429731)
(2.2758305229517912, 0.2291326376095485)
(2.3153246049141685, 0.21495468484600533)
(2.3554256109669747, 0.20167434916532012)
(2.396093567555272, 0.1893048686949158)
(2.4372879359755037, 0.1778585736019318)
(2.478967652785345, 0.16734687380224755)
(2.5210911707366455, 0.1577802475868274)
(2.5636165001906237, 0.14916823117673494)
(2.6065012509740524, 0.14151940921721917)
(2.64970267463471, 0.1348414062203528)
(2.6931777070539593, 0.12914087896475424)
(2.736883011374008, 0.12442350985996475)
(2.780775021197021, 0.12069400128209984)
(2.824809984013056, 0.11795607088641813)
(2.868944004813525, 0.11621244790148122)
(2.9131330898466796, 0.11546487040860054)
(2.9573331904715525, 0.11571408360927893)
(3.001500247066591, 0.11695983908237806)
(3.0455902329492495, 0.11920089503175013)
(3.08955919826275, 0.12243501752408725)
(3.1333633137862438, 0.12665898271575426)
(3.176958914624742, 0.1318685800663869)
(3.220302543735226, 0.13805861653604967)
(3.263350995245575, 0.14522292176177054)
(3.3060613575231232, 0.15335435420829402)
(3.3483910559499, 0.16244480828691743)
(3.3902978953619445, 0.17248522243531983)
(3.4317401021103526, 0.18346558815032177)
(3.472676365702169, 0.19537495996458232)
(3.513065879979577, 0.20820146635727554)
(3.5528683837963664, 0.22193232158788256)
(3.592044201151124, 0.23655383844129652)
(3.6305542807371265, 0.25205144187153317)
(3.6683602348695405, 0.2684096835304579)
(3.705424377751095, 0.2856122571670311)
(3.741709763038107, 0.3036420148817359)
(3.7771802206694023, 0.3224809842199783)
(3.8118003929214126, 0.3421103860874174)
(3.8455357696535315, 0.3625106534693797)
(3.8783527227085663, 0.38366145093568016)
(3.9102185394340196, 0.40554169491142367)
(3.9411014552907737, 0.4281295746935726)
(3.9709706855166713, 0.4514025741923252)
(3.9997964558134376, 0.47533749437564954)
(4.027550032026348, 0.49991047639457786)
(4.054203748787058, 0.5250970253662282)
(4.079731037091046, 0.5508720347908388)
(4.10410645078217, 0.5772098115784678)
(4.127305691917956, 0.60408410166043)
(4.14930563499031, 0.6314681161599183)
(4.170084349977531, 0.6593345580957406)
(4.189621124204632, 0.6876556495925473)
(4.207896482990183, 0.7164031595704154)
(4.224892209059101, 0.7455484318862099)
(4.240591360702025, 0.7750624138986434)
(4.254978288663175, 0.8049156854285877)
(4.268038651739879, 0.8350784880857425)
(4.279759431078189, 0.8655207549324481)
(4.290128943150362, 0.8962121404550654)
(4.299136851401252, 0.9271220508130384)
(4.306774176552012, 0.9582196743355058)
(4.31303330555084, 0.9894740122350394)
(4.317907999161827, 1.0208539095079114)
(4.3213933981843695, 1.0523280859900832)
(4.323486028296922, 1.0838651675379458)
(4.324183803520279, 1.1154337173027566)
};
\addlegendentry{$E_2$}
\end{axis}

\end{tikzpicture}

### 2019-05-04 quali/quali.presentation/slides.tex
wip

@@
 %\tikzexternalize
+%\usepackage{natbib}
+
+\usepackage[
+backend=biber,style=authoryear,autocite=inline
+]{biblatex}
+%\DeclareLanguageMapping{english}{english-apa}
+
+\addbibresource{../references.bib} %Imports bibliography file
+%\DeclareLanguageMapping{american}{american-apa}
 
@@
 
-\centering Thanks to CAPES
+\centering Agradecimentos à CAPES.
 \end{frame}
@@
 		\item Minimum Cover Problem
-		\item Maximal Covering Problem
+		\item Maximal Covering Problem \autocite{church:1974}
 	\end{itemize}
@@
 
-\begin{frame}{Preliminaries}
+%\begin{frame}{Preliminaries}
 
-	\begin{block}{Norms}
-		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
-		\begin{itemize}
-			\item Euclidean
-			\begin{equation*}
-			||u||_2 = \sqrt{u^Tu}
-			\end{equation*}
+%	\begin{block}{Norms}
+%		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
+%		\begin{itemize}
+%			\item Euclidean
+%			\begin{equation*}
+%			||u||_2 = \sqrt{u^Tu}
+%			\end{equation*}
+%			
+%			\item Elliptical
+%			\begin{equation*}
+%			||u||_{Q} = \sqrt{u^TQu}
+%			\end{equation*}
+%		\end{itemize}
+%	\end{block}
 
-			\item Elliptical
-			\begin{equation*}
-			||u||_{Q} = \sqrt{u^TQu}
-			\end{equation*}
-		\end{itemize}
-	\end{block}
-
-\end{frame}
-
-\begin{frame}{Preliminaries}
-	\begin{figure}[H]
-		\centering
-
-		\caption{The elliptical and euclidean norms.}
-		\input{figures/elliptical.and.euclidean.norms.tex}
-		\source{Elaborated by the author.}
-		\label{fig:3ellipses_intersect}
-
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Preliminaries}
-
-	\begin{block}{Ellipse}
-		Given a center $c \in \R^2$ and a $2x2$ p.d. matrix $Q$, an ellipse is the set of points that satisfy
-
-		\begin{equation*}
-		||u-c||_Q = 1,
-		\end{equation*}
-
-		with $\le$ representing the set of covered points
-	\end{block}
-
-	\begin{block}{Axis-parallel ellipse}
-		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by
-
-		\begin{equation*}
-		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1,
-		\end{equation*}
-
-		where $(a,b)$ are the shape parameters and $c=(c_x,c_y)$ is the center.
-	\end{block}
-
-\end{frame}
+%\end{frame}
 
@@
 		\item $D(q)$ is a unit disk with center at point $q$
-		\item \cite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
-		\item \cite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
+		\item \autocite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
+		\item \autocite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
 		\item We will introduce an equivalent problem...
@@
 	\begin{itemize}
-		\item In \cite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.
+		\item In \autocite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.
 
-		\item In \cite{zhou} a heuristic method using an algorithm called mean-shift was developed.
+		\item In \autocite{zhou} a heuristic method using an algorithm called mean-shift was developed.
 The mean-shift algorithm converges to a local density maxima of any probability distribution and it is used to find a smaller candidate list of centers for the disks.
@@
 \end{frame}
+\section{Maximal Covering by Ellipses}
 
-\section{Maximal Covering by Ellipses}
+\begin{frame}{Ellipses}
+
+	\begin{block}{Ellipse}
+		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$, an ellipse is the set of points that satisfy
+
+		\begin{equation*}
+		||u-c||_Q^2 = (u-c)^TQ(u-c) = 1,
+		\end{equation*}
+
+		with $\le$ representing the set of covered points
+	\end{block}
+
+	\begin{block}{Axis-parallel ellipse}
+		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by
+
+		\begin{equation*}
+		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1,
+		\end{equation*}
+
+		where $(a,b)$ are the shape parameters and $c=(c_x,c_y)$ is the center.
+	\end{block}
+
+\end{frame}
+
+\begin{frame}{Ellipses}
+	\begin{figure}[H]
+		\centering
+
+		\caption{The ellipse seen as just a linear transformation of a circle.}
+		\input{figures/elliptical.and.euclidean.norms.tex}
+		\source{Elaborated by the author.}
+		\label{fig:3ellipses_intersect}
+
+	\end{figure}
+\end{frame}
 
@@
 		\item $\E$ is a set of $m$ ellipses
-		\item \cite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
-		\item \cite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
+		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
+		\item \autocite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
 	\end{itemize}
@@
 
+\begin{frame}
+	\begin{figure}
+		\caption{Optimal solution with two ellipses for a random instance.}
+		\input{figures/example_2_ellipses.tex}
+		\source{Elaborated by the author.}
+	\end{figure}
+\end{frame}
+
 \begin{frame}{Maximal Covering by Ellipses}
@@
 
-		\item Simpler than the $m$ disks algorithm proposed by \cite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).
+		\item Simpler than the $m$ disks algorithm proposed by \autocite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).
 
@@
 \begin{itemize}
-	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
+	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \autocite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
 
-	\item Develop an exact method for the version of the problem introduced in \cite{andreta} where the ellipses can be freely rotated.
+	\item Develop an exact method for the version of the problem introduced in \autocite{andreta} where the ellipses can be freely rotated.
 \end{itemize}
@@
 
-	\item Develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
+	\item Develop a probabilistic approximation algorithm based on \autocite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
 The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse.
@@
 
-	\item In \cite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity.
+	\item In \autocite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity.
 We want to generalize this for the elliptical distance function and achieve a better run-time complexity.
@@
 \begin{frame}[allowframebreaks]
-	\frametitle{References}
-	\bibliographystyle{amsalpha}
-	\bibliography{../references.bib}
+%	\frametitle{References}
+%\bibliographystyle{authoryear-comp}
+%	\bibliography{../references.bib}
+\printbibliography
 \end{frame}

### 2019-05-04 implementation/main.jl

@@ -55,13 +55,16 @@ function main()
 	#@show(length(ret.Cover))
 	#@show(ret.x, ret.y)
 
+	X = map(p->p.x, P)
+	Y = map(p->p.y, P)
 
-
-
-
-	ret2 = ex2(P, Ellipse(1,1), Ellipse(1.4, 1))
-	plt = plotpointsellipse(map(p -> p.x, P), map(p -> p.y, P), [ret2...])
+	e1, e2, iscov = ex2(P, Ellipse(1,1), Ellipse(1.4, 1))
+	plt = plotpointsellipse(X, Y, [e1, e2], iscov)
 	savefig(plt, "c.pdf")
+	savefig(plt, "c.tex")
+
+	@show(X)
+	@show(Y)
 
 	#return ret
 end

### 2019-05-04 implementation/plotting.jl

@@ -9,11 +9,14 @@ function versor(A::AbstractArray)::AbstractArray{Real}
 	return map(x -> x / norm(A), A)
 end
 
-function plotpointsellipse(X::AbstractVector{<:Real}, Y::AbstractVector{<:Real}, Es::AbstractVector{Ellipse})
+function plotpointsellipse(X::AbstractVector{<:Real}, Y::AbstractVector{<:Real}, Es::AbstractVector{Ellipse}, iscov::Vector{Bool})
+	colors = [(h) ? :black : :red for h in iscov]
+
 	plt = plot(X, Y, seriestype=:scatter,lab="", 
 			   markersize = 2.5, 
 			   markerstrokewidth=0.5,
-			   grid=false,
+			   #grid=false,
+			   color=colors,
 			   aspect_ratio=:equal, xaxis=false,yaxis=false)
 
 

### 2019-05-04 implementation/solution.jl

@@ -38,10 +38,12 @@ function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Solution}
 		e1 = Ellipse(E.a, E.b, P[i].x, P[i].y)
 
 		#angle, point, entering or leaving
-		A::AbstractArray{Tuple{Real,PointW,Int}} = 
-		[(0, PointW(i,e1.center,P[i].w), 1), (2π, PointW(i,e1.center,P[i].w), -1)]
+		A::AbstractArray{Tuple{Real,PointW,Int}} = []
+		#[(0, PointW(i,e1.center,P[i].w), 1), (2π, PointW(i,e1.center,P[i].w), -1)]
 
-		for j in i+1:n
+		for j in 1:n
+			if (i == j) continue end
+
 			e2 = Ellipse(E.a, E.b, P[j].x, P[j].y)
 			ret = angles(e1, e2)
 			if (ret === nothing) continue end
@@ -57,7 +59,7 @@ function MCE1(P::AbstractArray{PointW}, E::Ellipse)::AbstractArray{Solution}
 		
 		sort!(A)
 
-		Cov::Set{PointW} = Set{PointW}()
+		Cov::Set{PointW} = Set{PointW}([P[i]])
 
 		xx = 0
 
@@ -118,12 +120,15 @@ function ex1(P::AbstractArray{PointW}, a::Real, b::Real)::Ellipse
 	return Ellipse(a, b, so.p.x, so.p.y)
 end
 
-function ex2(P::AbstractVector{PointW}, e1::Ellipse, e2::Ellipse)::Tuple{Ellipse,Ellipse}
+function ex2(P::AbstractVector{PointW}, e1::Ellipse, e2::Ellipse)::Tuple{Ellipse,Ellipse, Vector{Bool}}
 	Z = [MCE1(P,e1), MCE1(P,e2)]
 
 	fopt = 0
 	opt1::Ellipse = e1
 	opt2::Ellipse = e2
+	n = length(P)
+	iscov::Vector{Bool} = [false for i in 1:n]
+	optC::Set{PointW} = Set()
 
 	for z1 in Z[1], z2 in Z[2]
 		co = union(z1.Cover, z2.Cover)
@@ -132,11 +137,18 @@ function ex2(P::AbstractVector{PointW}, e1::Ellipse, e2::Ellipse)::Tuple{Ellipse
[…]

### 2019-05-05 quali/quali.presentation/figures/cover.tex
WIP

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.7,xscale=0.7]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

% Text Node
\draw  [fill={rgb, 255:red, 126; green, 211; blue, 33 }  ,fill opacity=1 ]  (93, 74) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (93,74) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 219; green, 24; blue, 24 }  ,fill opacity=1 ]  (46, 132) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (46,132) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 126; green, 211; blue, 33 }  ,fill opacity=1 ]  (192, 105) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (192,105) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=1 ]  (119, 148) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (119,148) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=1 ]  (188, 178) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (188,178) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 208; green, 2; blue, 27 }  ,fill opacity=1 ]  (87, 196) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (87,196) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ]  (155, 227) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (155,227) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 126; green, 211; blue, 33 }  ,fill opacity=1 ]  (281, 75) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (281,75) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 208; green, 2; blue, 27 }  ,fill opacity=1 ]  (234, 132) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (234,132) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 126; green, 211; blue, 33 }  ,fill opacity=1 ]  (380, 105) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (380,105) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=1 ]  (307, 148) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (307,148) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=1 ]  (376, 178) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (376,178) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 208; green, 2; blue, 27 }  ,fill opacity=1 ]  (275, 196) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (275,196) node [scale=0.8]  {$$};
% Text Node
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ]  (343, 227) circle [x radius= 12.75, y radius= 12.75]   ;
\draw (343,227) node [scale=0.8]  {$$};
% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (54.03,122.1) -- (84.97,83.9) ;

% Connection
\draw [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]    (179.83,101.19) -- (105.17,77.81) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (129.99,141.53) -- (181.01,111.47) ;

% Connection
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1.5]    (80.12,185.26) -- (52.88,142.74) ;

% Connection
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]    (98.6,201.29) -- (143.4,221.71) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (162.12,216.43) -- (180.88,188.57) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (94.07,185.39) -- (111.93,158.61) ;

% Connection
\draw [color={rgb, 255:red, 245; green, 166; blue, 35 }  ,draw opacity=1 ][line width=1.5]    (176.31,172.92) -- (130.69,153.08) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (242.11,122.16) -- (272.89,84.84) ;

% Connection
\draw [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]    (367.8,101.3) -- (293.2,78.7) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (317.99,141.53) -- (369.01,111.47) ;

% Connection
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1.5]    (268.12,185.26) -- (240.88,142.74) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (286.6,201.29) -- (331.4,221.71) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (350.12,216.43) -- (368.88,188.57) ;

% Connection
\draw [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][line width=1.5]    (282.07,185.39) -- (299.93,158.61) ;

% Connection
\draw [color={rgb, 255:red, 245; green, 166; blue, 35 }  ,draw opacity=1 ][line width=1.5]    (364.31,172.92) -- (318.69,153.08) ;

\end{tikzpicture}

### 2019-05-05 quali/quali.presentation/slides.tex
WIP

@@
 \usepackage[
-backend=biber,style=authoryear,autocite=inline
+backend=biber,
+style=authoryear,
+autocite=inline
 ]{biblatex}
@@
 	\begin{itemize}
-		\item Minimum Cover Problem
+		\item Minimum Cover Problem \autocite{karp}
 		\item Maximal Covering Problem \autocite{church:1974}
 	\end{itemize}
+
+\end{itemize}
+
+\begin{figure}
+	\caption{Minimum Vertex Cover and its maximal counterpart. The colored edges are in the cover.}
+	\input{figures/cover.tex}
+
+	\source{Elaborated by the author.}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Introduction}
+\begin{itemize}
+
 	\item Maximal Covering Location Problem (MCLP)
+
+	\begin{itemize}
+		\item Introduce at first for networks. Facilities are placed on nodes, covering a radius of neighboring vertexes.
+	\end{itemize}
 	\item Planar Maximal Covering Location Problem (PMCLP)
 	\begin{itemize}
-	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
-	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
+		\item One disk is 3SUM-Hard \autocite{3SUM-kopelowitz:2014}.
+		\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms.
+		\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
-		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm
+		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case.
+		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm.
 	\end{itemize}
@@
 
-\end{frame}
-
-\begin{frame}
-	\begin{figure}
-		\only<1>{\caption{Maximal cover by two disks.}}
-		\only<2>{\caption{Minimum number of disks needed to cover the set of points.}}
-		\only<1>{\input{figures/intro_a.tex}}
-		\only<2>{\input{figures/intro_b.tex}}
-		\source{Elaborated by the author.}
-	\end{figure}
 \end{frame}
@@
 
-	$MCD(\Pp, 1)$ is the problem of placing one disk on the plane to cover a subset of a demand set $\Pp$ maximizing the weights of the covered points.
+	$MCD(\Pp, 1)$ is the problem of placing one disk on the plane to cover a subset of a demand set $\Pp$, with $n$ points, maximizing the weights of the covered points.
 
@@
 	\begin{itemize}
-		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
-		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
-		\item $D(q)$ is a unit disk with center at point $q$
-		\item \autocite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
-		\item \autocite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
-		\item We will introduce an equivalent problem...
+		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$.
+		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$.
+		\item $D(q)$ is a unit disk with center at point $q$.
+		%\item \autocite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
+		%\item \autocite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
+		%\item We will introduce an equivalent problem...
 	\end{itemize}
+\end{frame}
+
+\begin{frame}{Maximal Covering by Disks}{One disk}
+\begin{figure}
+	\caption{An instance of $MCD(\Pp,1)$.}
+	\includegraphics[scale=0.6]{figures/mcd_one_disk.pdf}
+	\source{Elaborated by the author.}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Maximal Covering By Disks}{One disk}
+
+	Works and results found in the literature:
+
+	\begin{itemize}
+		\item $MCD$ is as difficult the problem of given $n$ numbers, find three of them that sum to $0$. Proved by \autocite{aronov:2008}.
+
+		\item In \autocite{drezner} a $\bigO(n^2\log{n})$ algorithm was developed. The idea of our algorithm to sort the intersections by their angles comes from here.
+
+		\item In \autocite{chazelle:1986}, a $\bigO(n^2)$ algorithm was developed. It actually solves an equivalent problem which is introduced next.
+	\end{itemize}
+
 \end{frame}
@@
 	\begin{itemize}
-		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
+		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$.
 		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.
@@
 
-\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
-		\begin{figure}[H]
-		\centering
-
-		\only<1>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
-
-		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
-
-		\only<1>{\input{figures/max_w_clique.tex}}
-		\only<2>{\input{figures/max_w_clique_b.tex}}
-      %\center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
+\begin{frame}{Maximum Weight Clique Problem}
+	\begin{figure}
+		\only<1>{\caption{An instance of $MCD(\Pp, 1)$.}}
+		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
+		\only<3>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
+		\only<1>{\includegraphics[scale=0.55]{figures/mwc_1.pdf}}
+		\only<2>{\includegraphics[scale=0.55]{figures/mwc_2.pdf}}
+		\only<3>{\includegraphics[scale=0.55]{figures/mwc_3.pdf}}
+		%\only<2>{\input{figures/intro_b.tex}}
 		\source{Elaborated by the author.}
-		\label{fig:mcd_instance}
 	\end{figure}
@@
 
+%\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
+%		\begin{figure}[H]
+%		\centering
+
+%		\only<1>{}
+
+%		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
+
+%		\only<1>{\input{figures/max_w_clique_v2.tex}}
+%		\only<2>{\input{figures/max_w_clique_b.tex}}
+      %\center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
+%		\source{Elaborated by the author.}
+%		\label{fig:mcd_instance}
+%	\end{figure}
+%\end{frame}
+
 \begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	Defining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$:
+	Defining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$:\\~\\
 
-	Let $D_i$ and $D_j$ be two unit disks that intersect at two points.
+	Let $D_i$ (at the origin) and $D_j$ be two unit disks that intersect at two points.
 
 	\begin{itemize}
-		\item Assume $D_i$ is at the origin
-		\item We can find the polar angle of the intersection points. Let's call them $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ with the following condition:
-		\begin{itemize}
-			\item The arc defined by $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ bounds the region $D_i \cap D_j$
+		\item We know that the two intersection points define two arcs in $D_i$.
+		\item One of the arcs bounds $D_i\cap D_j$. That is the one we want to determine.
 
+		\item We can determine the polar angles of the two intersection points.
+		%\item Assume $D_i$ is at the origin.
+		\item Assuming counter-clockwise direction, we define $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ as the angles of intersection that determines the arc of $D_i$ that bounds $D_i \cap D_j$.
 	\end{itemize}
-		\item Later it will be shown how to find which one is which algorithmically.
-	\end{itemize}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+
+\begin{figure}
+	\caption{$\Gamma_+(1,2)$ and $\Gamma_-(1,2)$ example.}
+	\includegraphics[scale=0.65]{figures/gammas.pdf}
+		\source{Elaborated by the author.}
+\end{figure}
 \end{frame}
@@
 	\begin{itemize}
-		\item There are $\bigO(n^2)$ intersections among $n$ disks
+		\item There are $\bigO(n^2)$ intersections among $n$ disks.
 
-		\item Sorting takes $\bigO(n^2\log{n})$
+		\item Sorting takes $\bigO(n^2\log{n})$.
 
@@
 
-		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections.
+		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.
 	\end{itemize}
@@
 
-		with $\le$ representing the set of covered points
+		with $\le$ representing the set of covered points.
 	\end{block}
@@
 	\begin{equation*}
-	\max_q |\Pp \cap (q)|,
+	\max_q |\Pp \cap E(q)|,
 	\end{equation*}
@@
 	\begin{itemize}
-		\item $E(q)$ is an axis-parallel ellipse with center point $q$
-		\item Assuming unit weights for now
-		\item Same algorithm for one disk
+		\item $E(q)$ is an axis-parallel ellipse with center point $q$.
+		\item Assuming unit weights for now.
+		\item Same algorithm for one disk.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item $\E$ is a set of $m$ ellipses
+		\item $\E$ is a set of $m$ ellipses.
 		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
@@
 			\STATE $Z \gets \{\}$
-
+			\STATE $Cov \gets \{p_i\}$
 			\FOR{$cnt=1..2$} 
@@
 	\begin{itemize}
-		\item The algorithm for $m$ ellipses tries every possible assignment of coverage for every one of the ellipses
-		\item Run-time complexity of $\bigO(n^2)^m = \bigO(n^{2m})$
+		\item The algorithm for $m$ ellipses tries every possible assignment of coverage for every one of the ellipses.
+		\item Run-time complexity of $\bigO(n^{2m})$.
 
@@
 
-		\item The unit-weight assumption can be easily dropped
+		\item The unit-weight assumption can be easily dropped.
 	\end{itemize}

### 2019-05-05 quali/quali.presentation/figures/fig:array_disks.tex
WIP

--- 2019-03-27 tex/figures/fig:array_disks.tex
@@
-\usetikzlibrary{matrix}
-
 \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
 
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1.4,xscale=1.4]
 %uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.6]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.6]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
+\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (44.02,39.56) node [scale=0.6]  {$4_-$};
 
 % Text Node
-\draw (20,35) node [scale=0.5]  {$E_{1}$};
+\draw (20,35) node [scale=0.5]  {$D_{1}$};
 \end{tikzpicture}
@@
 {
-$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
 %$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_1.tex
WIP

@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.6]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
+\draw (74.22,50) node [scale=0.6,color=red]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
+\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (44.02,39.56) node [scale=0.6]  {$4_-$};
 
@@
 {
-	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
 	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_2.tex
WIP

@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.6]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.6]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
+\draw (64.22,36.56) node [scale=0.6,color=red]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
+\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (44.02,39.56) node [scale=0.6]  {$4_-$};
 

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_2_5.tex
WIP

@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6, color=red]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.6]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.6]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
+\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (44.02,39.56) node [scale=0.6]  {$4_-$};
 

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_3.tex
WIP

@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5,color=red]  {$+$};
+\draw (65.22,66) node [scale=0.6,color=red]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.6]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
+\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (44.02,39.56) node [scale=0.6]  {$4_-$};
 

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_6.tex
WIP

--- 2019-04-29 quali/quali.presentation/figures/mcd_sim.tex
@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.6]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.6]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5,color=red]  {$-$};
+\draw (54.32,40.66) node [scale=0.6,color=red]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5]  {$-$};
+\draw (44.02,39.56) node [scale=0.6]  {$4_-$};
 
@@
 \end{tikzpicture}
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95
 
-%Shape: Circle [id:dp37777408295388804] 
-\draw   (21,59.5) ..
-controls (21,45.69) and (32.19,34.5) ..
-(46,34.5) ..
-controls (59.81,34.5) and (71,45.69) ..
-(71,59.5) ..
-controls (71,73.31) and (59.81,84.5) ..
-(46,84.5) ..
-controls (32.19,84.5) and (21,73.31) ..
-(21,59.5) -- cycle ;
+\begin{tikzpicture}
 
-%Shape: Circle [id:dp4562198988843913] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 },draw opacity=1 ] (47.5,46.94) ..
-controls (47.5,33.14) and (58.69,21.94) ..
-(72.5,21.94) ..
-controls (86.31,21.94) and (97.5,33.14) ..
-(97.5,46.94) ..
-controls (97.5,60.75) and (86.31,71.94) ..
-(72.5,71.94) ..
-controls (58.69,71.94) and (47.5,60.75) ..
-(47.5,46.94) -- cycle ;
+\matrix [matrix of nodes,row sep=,row sep=0mm,
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
+column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
+] (O)
+{
+$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
+	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+};
 
-%Shape: Circle [id:dp8913971633985722] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 } ,draw opacity=1 ] (33,53.5) ..
-controls (33,39.69) and (44.19,28.5) ..
-(58,28.5) ..
-controls (71.81,28.5) and (83,39.69) ..
-(83,53.5) ..
-controls (83,67.31) and (71.81,78.5) ..
-(58,78.5) ..
-controls (44.19,78.5) and (33,67.31) ..
-(33,53.5) -- cycle ;
-
-%Shape: Circle [id:dp05970043129919356] 
-\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] (57.81,32.47) ..
-controls (57.81,18.66) and (69,7.47) ..
-(82.81,7.47) ..
-controls (96.62,7.47) and (107.81,18.66) ..
-(107.81,32.47) ..
-controls (107.81,46.27) and (96.62,57.47) ..
-(82.81,57.47) ..
-controls (69,57.47) and (57.81,46.27) ..
-(57.81,32.47) -- cycle ;
-%Straight Lines [id:da04725899028195979] 
-%\draw[densely dotted]  (21,59.5) -- (71,59.5) ;
-
-%Flowchart: Extract [id:dp5267407418119328] 
-\draw  [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (71,57.45) -- (72.52,59.55) -- (69.48,59.55) -- cycle ;
-
-\draw (60,73) node [scale=0.5]  {$+$};
-% Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
-% Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
-% Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
-% Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
-% Text Node
-\draw (38.02,31.56) node [scale=0.5,color=red]  {\textbf{$-$}};
-
-% Text Node
-\draw (20,35) node [scale=0.5]  {$D_{1}$};
+\node at (-4,-0.5) {$0$};
+\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_7.tex
WIP

--- 2019-04-29 quali/quali.presentation/figures/mcd_sim.tex
@@
 
-\draw (60,73) node [scale=0.5]  {$+$};
+\draw (60,73) node [scale=0.6]  {$4_+$};
 % Text Node
-\draw (65.22,66) node [scale=0.5]  {$+$};
+\draw (65.22,66) node [scale=0.6]  {$3_+$};
 % Text Node
-\draw (74.22,50) node [scale=0.5]  {$+$};
+\draw (74.22,50) node [scale=0.6]  {$2_+$};
 % Text Node
-\draw (54.22,39.56) node [scale=0.5]  {$-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (45.62,36.96) node [scale=0.5]  {$-$};
+\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
 % Text Node
-\draw (38.02,31.56) node [scale=0.5,color=red]  {\textbf{$-$}};
+\draw (44.02,39.56) node [scale=0.6,color=red]  {$4_-$};
 
@@
 \end{tikzpicture}
+
+\begin{tikzpicture}
+
+\matrix [matrix of nodes,row sep=,row sep=0mm,
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
+column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
+] (O)
+{
+$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
+	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+};
+
+\node at (-4,-0.5) {$0$};
+\node at (0,-0.5) {$2\pi$};
+\end{tikzpicture}

### 2019-05-05 quali/quali.presentation/slides.tex
WIP

@@
 \begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.
+
+	Some observations allow us to arrive at the algorithm:
+
+%	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.
 
@@
 
-		\item The arc $\Gamma_+(i,j),\Gamma_-(i,j)$ (counter-clockwise) determines a region where $i$ and $j$ intersect.
+		\item The arc $A(\Gamma_+(i,j),\Gamma_-(i,j))$ (counter-clockwise) determines a region where $i$ and $j$ intersect.
 
-		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. The traversal is on a circle, where to start?
+		\item For every disk $D_i$, we want to find an angle $\theta$, such that $$w(\{D_k : \theta \in A(\Gamma_+(i,k),\Gamma_-(i,k))\}),$$ is maximized. Most overlapping intervals (circular).
 
-		\item If the traversal reaches a opening angle, we mark the intersecting disk as active. If it reaches a closing angle we unmark it.
-
-		\item We want to find a point in the traversal with the most active disks.
+		\item To transform it to the problem of finding the most overlapping intervals, just copy the list of intersection angles. The arcs such that $\Gamma_+(i,j) > \Gamma_-(i,j)$ will be considered.
 	\end{itemize}
@@
 
-	For every disk, traverse the sorted list of intersection angles twice, keeping a set of active disks, and the current best solution.
-
-	Doing the traversal twice solves the problem of deciding where to start.
+	Transforming it to the most overlapping intervals.
 
@@
 		\source{Elaborated by the author.}
-	\label{fig:array_disks}
+		%\label{fig:array_disks}
 	\end{figure}
+\end{frame}
+
+\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
+	Our algorithm for the Maximum Weight Clique Problem:\\~\\
+
+	For every disk $D_i$, do:
+	\begin{itemize}
+		\item Get the sorted list of intersection angles with $D_i$
+				$A=\cap_{j}\Gamma_+(i,j) \cup \Gamma_-(i,j)$.
+		\item Traverse it twice starting at the angle with smallest value.
+		\begin{itemize}
+			\item Keep a set of active disks. When an opening angle is visited, make the disk active, otherwise remove it from the set.
+			\item Update the optimal solution. Use the closing angle.
+		\end{itemize}
+	\end{itemize}
 \end{frame}
@@
 		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.
+
+		\item The algorithm is basically finding the most number of overlapping intervals $n$ times.
+
+		\item As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.
 	\end{itemize}

### 2019-05-07 implementation/julia/Ellipses.jl
WIP

@@ -45,6 +45,9 @@ function ellipseinter(e₁::Ellipse, e₂::Ellipse)::Union{Nothing,Tuple{Point,P
 
 	α = (-2k*a^2)/(2h*b^2)
 	β = (b^2*h^2 + a^2*k^2) / (2h*b^2)
+
+	@show(a, b, α, β)
+	@show(2h*b^2)
 	
 	ro = root2(b^2*α^2+a^2, 2β*α*b^2, b^2*β^2 - a^2*b^2)
 

### 2019-05-07 implementation/julia/main.jl

@@ -12,6 +12,14 @@ using Ellipses
 
 pgfplots()
 
+function mainT()
+	e1 = Ellipse(2,1,0,0)
+	e2 = Ellipse(2,1,0.6,0.6)
+
+	@show(ellipseinter(e1, e2))
+
+end
+
 function main2()
 	e₁ = Ellipse(3,2,0,0)
 	e₂ = Ellipse(3,2,first(randn(1)), first(randn(1)))

### 2019-05-07 quali/quali.presentation/slides.tex
WIP

@@
 	\begin{itemize}
-		\item Introduce at first for networks. Facilities are placed on nodes, covering a radius of neighboring vertexes.
+		\item Introduce at first for networks \autocite{church:1974}. Facilities are placed on nodes, covering a radius of neighboring vertexes.
 	\end{itemize}
@@
 	\begin{itemize}
+		\item Introduced by \autocite{church:1984}.
 		\item One disk is 3SUM-Hard \autocite{3SUM-kopelowitz:2014}.
@@
 
-\section{Preliminaries}
+%\section{Preliminaries}
 
@@
 	\begin{itemize}
-		\item $MCD$ is as difficult the problem of given $n$ numbers, find three of them that sum to $0$. Proved by \autocite{aronov:2008}.
+		\item $MCD$ is as difficult the problem of given $n$ numbers, find three of them that sum to $0$ (3SUM-HARD). Proved by \autocite{aronov:2008}.
 
@@
 	\begin{equation*}
-	\max_q \sum_{D_k \cap q \neq \emptyset} w_k,
+	\max_{q\in\R^2} \sum_{D_k \cap q \neq \emptyset} w_k,
 	\end{equation*}
@@
 	\begin{itemize}
-		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$.
 		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.
-		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
+
+		\item The weight of a clique is the sum of the weights of the disks that intersect with it.
+
+		\item In our case, we just want a point from the optimum clique.
+
+		\item Given an instance $MCD(\Pp, 1)$: fix the disk centers at $\Pp =\{p_1,\dots,p_n\}$ with weights $w_k=w(p_k)$.
+
+		%\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
 	\end{itemize}
@@
 
-\begin{frame}{Maximum Weight Clique Problem}
+\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
 	\begin{figure}
-		\only<1>{\caption{An instance of $MCD(\Pp, 1)$.}}
+		\only<1>{\caption{An instance of $MCD(\Pp, 1)$. We will show how an instance of the Maximum Weight Clique Problem is constructed from it.}}
 		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
 		\only<3>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
-		\only<1>{\includegraphics[scale=0.55]{figures/mwc_1.pdf}}
-		\only<2>{\includegraphics[scale=0.55]{figures/mwc_2.pdf}}
-		\only<3>{\includegraphics[scale=0.55]{figures/mwc_3.pdf}}
+		\only<1>{\includegraphics[scale=0.50]{figures/mwc_1.pdf}}
+		\only<2>{\includegraphics[scale=0.50]{figures/mwc_2.pdf}}
+		\only<3>{\includegraphics[scale=0.50]{figures/mwc_3.pdf}}
 		%\only<2>{\input{figures/intro_b.tex}}
@@
 
-	Let $D_i$ (at the origin) and $D_j$ be two unit disks that intersect at two points.
+	Let $D_i$ (at the origin) and $D_j$ be two unit disks that have their corresponding circles intersect at two points.
 
@@
 \begin{frame}{Maximal Covering by Ellipses}{One ellipse}
-	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by
+	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, and $\Pp=\{p_1,\dots,p_n\}$ is a set of $n$ points with each point having a positive weight $w_i$, an optimal solution of $MCE(\Pp, a, b)$ is given by
 
 	\begin{equation*}
-	\max_q |\Pp \cap E(q)|,
+	\max_q w(\Pp \cap E(q)),
 	\end{equation*}
@@
 		\item $E(q)$ is an axis-parallel ellipse with center point $q$.
-		\item Assuming unit weights for now.
+		\item $w(A)$, $A \subset \Pp$, is the sum of the weights of every point in $\Pp$.
 		\item Same algorithm for one disk.
@@
 	\begin{equation*}
-	\max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|},
+	\max_{q_1, \dots, q_m}{w(\bigcup_{i=1}^{m} \Pp \cap E_i(q_i))},
 	\end{equation*}
@@
 	\begin{itemize}
-		\item $\E$ is a set of $m$ ellipses.
+		\item $\Pp$ is a set of $n$ points, $\E$ is a set of $m$ ellipses.
 		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
@@
 	\begin{algorithm}[H]
-		%\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
+		\caption{Adaptation of the algorithm for one disk to produce a candidate list for every ellipse.}\label{algoritmo:mce1}
 		\begin{algorithmic}[1]
@@
 	\end{algorithm}
+\end{frame}
+
+\begin{frame}{Maximal Covering by Ellipses}{$m$ Ellipses}
+	The modified one-disk-cover algorithm produces a list of candidates of location for each ellipse. An optimal solution is guaranteed to be in this list.
 \end{frame}

### 2019-05-07 quali/quali.presentation/slides.tex
WIP

@@
 
-		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.
+		\item It can be implemented in $\bigO(K\log{n})$ where $K$ is the number of intersections \autocite{bentley:1979}.
 
@@
 
-		\item As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.
 	\end{itemize}
+	As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.
 
@@
 	\begin{block}{Ellipse}
-		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$, an ellipse is the set of points that satisfy
+		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$ a positive definite matrix, an ellipse is the set of points that satisfy
 
@@
 	\begin{block}{Axis-parallel ellipse}
-		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by
+		Any $2$ by $2$ diagonal p.d. matrix determines an axis-parallel ellipse, which can also be described by
 
@@
 
-\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
+\begin{frame}[fragile]{Maximal Covering by Ellipses}{The algorithm for $m$ ellipses}
 	\begin{algorithm}[H]
-		\caption{Adaptation of the algorithm for one disk to produce a candidate list for every ellipse.}\label{algoritmo:mce1}
+		%\caption{Adaptation of the algorithm for one disk to produce a candidate list for every ellipse.}\label{algoritmo:mce1}
 		\begin{algorithmic}[1]
-			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
-			\STATE $Z \gets \{\}$
-			\STATE $Cov \gets \{p_i\}$
-			\FOR{$cnt=1..2$} 
-			\FOR{$a \in A$}
-			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
-			\IF{$a$ is a starting angle}
-			\STATE $Cov \gets Cov \cup \{p_a\}$
-			\ELSE
-			\STATE $Cov \gets Cov \setminus \{p_a\}$
+			\FOR{$E_i \in \E$}
+				\STATE{Fix an ellipse with the same shape as $E_i$ at each point.}
+				\STATE{$Z_i \gets $ every solution of Maximum Weight Clique for it.}
+			\ENDFOR
+		\end{algorithmic}
+	\end{algorithm}
+\begin{algorithm}[H]
+	\begin{algorithmic}[1]
+
+			\STATE{\textbf{function} $f(\Pp, j)$}
+
+				\IF{$j=m$}{
+					\RETURN 0
+				}
 				\ENDIF
-			\STATE $Z \gets Z \cup \{Cov\}$
+				\STATE{$ans \gets 0$}
+				\FOR{$z \in Z_j$}
+					\STATE{Fix $E_j$ at $z$}
+					\STATE{$Q \gets$ points covered by $E_j(z)$}
+					\STATE{$ans \gets \max\{ans,f(\Pp \setminus Q, j+1) + w(Q)\}$}
 				\ENDFOR
-			\ENDFOR
+				\RETURN{$ans$}
+
+			%\FOR{$p_i \in \Pp$}
+			%\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
+			%\STATE $Z \gets \{\}$
+			%\STATE $Cov \gets \{p_i\}$
+			%\FOR{$cnt=1..2$} 
+			%\FOR{$a \in A$}
+			%\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
+			%\IF{$a$ is a starting angle}
+			%\STATE $Cov \gets Cov \cup \{p_a\}$
+			%\ELSE
+			%\STATE $Cov \gets Cov \setminus \{p_a\}$
+			%\ENDIF
+			%\STATE $Z \gets Z \cup \{Cov\}$
+			%\ENDFOR
+			%\ENDFOR
+			%\ENDFOR
 
@@
 
-\begin{frame}{Maximal Covering by Ellipses}{$m$ Ellipses}
-	The modified one-disk-cover algorithm produces a list of candidates of location for each ellipse. An optimal solution is guaranteed to be in this list.
-\end{frame}
+%\begin{frame}{Maximal Covering by Ellipses}{$m$ Ellipses}
+%	The modified one-disk-cover algorithm produces a list of candidates of location for each ellipse. An optimal solution is guaranteed to be in this list.
+%\end{frame}
 

### 2019-05-09 implementation/julia/main.jl
wip

@@ -13,10 +13,12 @@ using Ellipses
 pgfplots()
 
 function mainT()
-	e1 = Ellipse(2,1,0,0)
-	e2 = Ellipse(2,1,0.6,0.6)
+	e1 = Ellipse(3,2,0,0)
+	e2 = Ellipse(3,2,1,1)
 
 	@show(ellipseinter(e1, e2))
+
+	plt=plotwihtoutquiver([e1,e2])
 
 end
 

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_1.tex
WIP

@@
 
-\matrix [matrix of nodes,row sep=,row sep=0mm,
+\matrix [matrix of nodes,row sep=0,row sep=0mm,
 column 1/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+|[color=red!]|$1$\\ %& $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
 };
-
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_2.tex
WIP

@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+|[color=red!]|$1$ & |[color=black!]|$0$\\
 };
 
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
+%\node at (-4,-0.5) {$0$};
+%\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_2_1.tex
WIP

--- 2019-05-09 quali/quali.presentation/figures/mcd_sim_2.tex
@@
 % Text Node
-\draw (64.22,36.56) node [scale=0.6,color=red]  {$2_-$};
+\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
 % Text Node
-\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
+\draw (54.32,40.66) node [scale=0.6,color=red]  {$3_-$};
 % Text Node
@@
 column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 2/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
-column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
 column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-|[color=red!]|$1$ & |[color=black!]|$0$\\
+|[color=red]|$1$ & |[color=black]|$0$ & |[color=black]|$0$\\
 };

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_2_2.tex
WIP

--- 2019-05-09 quali/quali.presentation/figures/mcd_sim_2_1.tex
@@
 column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
-column 3/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
-column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 4/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
 column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
@@
 	$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-|[color=red]|$1$ & |[color=black]|$0$ & |[color=black]|$0$\\
+	|[color=red]|$1$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$0$\\
 };

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_2_5.tex
WIP

@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+|[color=red]|$1$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$1$\\
 };
 
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
+%\node at (-4,-0.5) {$0$};
+%\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_3.tex
WIP

@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+|[color=black]|$1$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$1$ & |[color=red]|$2$\\
 };
 
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
+%\node at (-4,-0.5) {$0$};
+%\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_4.tex
WIP

@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+|[color=black]|$1$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$1$ & |[color=black]|$2$ & |[color=red]|$3$\\
 };
 
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
+%\node at (-4,-0.5) {$0$};
+%\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_5.tex
WIP

@@
 $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
-	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
+|[color=black]|$1$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$1$ & |[color=black]|$2$ & |[color=red]|$3$ & |[color=black]|$2$\\
 };
 
-\node at (-4,-0.5) {$0$};
-\node at (0,-0.5) {$2\pi$};
+%\node at (-4,-0.5) {$0$};
+%\node at (0,-0.5) {$2\pi$};
 \end{tikzpicture}

### 2019-05-09 quali/quali.presentation/figures/mcd_sim_7.tex
WIP

--- 2019-04-29 quali/quali.presentation/figures/mcd_sim.tex
@@
 \end{tikzpicture}
+
+\begin{tikzpicture}
+
+\matrix [matrix of nodes,row sep=,row sep=0mm,
+column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
+column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
+column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
+column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
+] (O)
+{
+$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
+|[color=black]|$1$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$0$ & |[color=black]|$1$ & |[color=black]|$2$ & |[color=red]|$3$ & |[color=black]|$2$ & |[color=black]|$1$ &|[color=black]|$0$\\
+};
+
+%\node at (-4,-0.5) {$0$};
+%\node at (0,-0.5) {$2\pi$};
+\end{tikzpicture}

### 2019-05-18 quali/tex/chapter/definicoes.tex
wip

@@
 \begin{equation}\label{eq:norm2}
-||u||_2 = \sqrt{u^{T}u},
+||u||_2 = \sqrt{u^{T}u}.
 \end{equation}
 
-\noindent the elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
+\noindent The elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
 This matrix can be seen as a linear transformation of the Euclidean norm.
-Let $u \in \R^2$ be a vector, the elliptical norm of $u$ is defined as
+The elliptical norm of $u \in\R^2$ is defined as
 
@@
 
-Determining the distance between two points, given a norm function is done by calculating the norm of the vector defined by the difference between the two points.
+Determining the distance between two points, given a norm function, is done by calculating the norm of the vector defined by the difference between the two points.
 For example, the elliptical distance between the points $p,q \in \R^2$ is given by $||p-q||_{Q}$.
@@
 
-A circle (or circumference) is a set of points in $\R^2$ that have constant Euclidean distance, also known as radius, to another point, also referred to as the center of the circle.
+A circle (or circumference) is a set of points in $\R^2$ that have the same Euclidean distance, also known as radius, to another point, also referred to as the center of the circle.
 A unit circle is a circle with radius equal to $1$.
 
-A disk is the set of points bounded by a circle. In other words let $c \in \R^2$, a unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfy
+A disk is the set of points bounded by a circle. In other words let $c \in \R^2$. A unit disk with center $c$ is the set of every point $p \in \R^2$ which satisfies
 
@@
 
-Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse,
+Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse.
 
@@
     Let $c\in \R^2$ be the center of an ellipse and $Q$ be a $2$ by $2$ positive definite matrix.
-An ellipse is the set of every point $p \in \R^2$ that have $||p-c||_{Q}^2 = (p-c)^{T}Q(p-c) = 1$.
+An ellipse is the set of every point $p \in \R^2$ such that $||p-c||_{Q}^2 = (p-c)^{T}Q(p-c) = 1$.
 Also, a point $p$ is considered covered by an ellipse if $||p-c||_{Q}^2 = (p-c)^{T}Q(p-c) \le 1$.

### 2019-05-18 quali/tex/chapter/introducao.tex
wip

--- 2019-04-23 tex/chapter/introducao.tex
@@
 One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic.
-Given a demand set and collection of subsets of the demand set, the problem asks what is the minimum number of elements from the collection of subsets needed to cover the whole demand set.
+Given a demand set and a collection of subsets of the demand set, the problem asks what is the minimum number of elements from the collection of subsets needed to cover the whole demand set.
 One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.
@@
 Only two articles have been found published in the literature that study this problem.
-In \cite{canbolat}, a mixed non-linear programming method was proposed as a first approach to the problem.
+In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
 For some instances the method took too long and did not find an optimal solution.
-For this reason a heuristic method was developed using a technique called Simulated Annealing, solutions for the instances that timed-out with the first method were then obtained.
+For this reason a heuristic method was developed using a technique called Simulated Annealing.
+Solutions for the instances that timed-out with the first method were then obtained.
 The problem was further explored in \cite{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances which the first method could not.

### 2019-05-31 drafts/3points-ellipse5.tex
wip

--- 2019-05-05 quali/quali.presentation/slides.tex
@@
-\documentclass{beamer}
+\documentclass{article}
 
-\mode<presentation>{
-\usetheme{Madrid}
-%\usecolortheme{beaver}
-}
-\usepackage[utf8]{inputenc}
-%\usepackage{default}
-%\usepackage[portuguese]{babel}
-%\usepackage{pgfplots}
-%\pgfplotsset{/pgf/number format/use comma,compat=newest}
-%\usepackage{color}
 \usepackage{amsfonts}
+\usepackage{amsmath}
 \usepackage{mathrsfs}
-
-%\usepackage{hyperref}
-
-%MEUS COMANDOs
 
@@
 \newcommand{\bigO}{\mathscr{O}}
-\usetikzlibrary{matrix}
-\usepackage{pgfplots}
-\pgfplotsset{compat=1.4}
+%\usetikzlibrary{matrix}
+%\usepackage{pgfplots}
+%\pgfplotsset{compat=1.4}
 \usepackage{algorithm2e}
 \usepackage{algorithmic}
-\usepackage{float}
+
 \usepackage{caption}
@@
 
-%\usepgfplotslibrary{external}
-%\tikzexternalize
-%\usepackage{natbib}
+\begin{document}
+	\section{Intro}
+	Let's assume that $x_1, y_1 = (0,0)$ and $x_2 = 0$. Then we have:
 
-\usepackage[
-backend=biber,
-style=authoryear,
-autocite=inline
-]{biblatex}
-%\DeclareLanguageMapping{english}{english-apa}
+	\begin{align*}
+	E=-Cy_2\\
+	Dx_3=-(Ax_3^2 + Bx_3y_3 + C(y_3^2-y_2y_3))\\
+	\end{align*}
 
-\addbibresource{../references.bib} %Imports bibliography file
-%\DeclareLanguageMapping{american}{american-apa}
+	Renaming things:
 
-%FIM MEUS COMANDOS
+	\begin{align}
+	E=C\beta\\
+	D = A\alpha_a + B\alpha_b + C\alpha_c
+	\end{align}
 
-\title[Qualificação de Mestrado]{Planar Maximal Covering with Ellipses}
-\author[Tedeschi, D. F.]{Danilo F. Tedeschi\\ \small Orientadora: Dra. Marina Andretta}
+	\section{Working with $a$ and $b$}
 
-\institute[ICMC]{Instituto de Ciências Matemáticas e Computação}
-\date{\today}
+	Let's call $q$ the normalizor factor:
 
-\begin{document}
-
-\begin{frame}
- \maketitle
-
-\centering Agradecimentos à CAPES.
-\end{frame}
-
-\begin{frame}
-\frametitle{Contents}
- \tableofcontents
-\end{frame}
-
-\section{Introduction}
-\begin{frame}
-\frametitle{Introduction}
-\begin{itemize}
-	\item Covering problems
-	\begin{itemize}
-		\item Minimum Cover Problem \autocite{karp}
-		\item Maximal Covering Problem \autocite{church:1974}
-	\end{itemize}
-
-\end{itemize}
-
-\begin{figure}
-	\caption{Minimum Vertex Cover and its maximal counterpart. The colored edges are in the cover.}
-	\input{figures/cover.tex}
-
-	\source{Elaborated by the author.}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Introduction}
-\begin{itemize}
-
-	\item Maximal Covering Location Problem (MCLP)
-
-	\begin{itemize}
-		\item Introduce at first for networks. Facilities are placed on nodes, covering a radius of neighboring vertexes.
-	\end{itemize}
-	\item Planar Maximal Covering Location Problem (PMCLP)
-	\begin{itemize}
-		\item One disk is 3SUM-Hard \autocite{3SUM-kopelowitz:2014}.
-		\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms.
-		\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm.
-	\end{itemize}
-	\item Goals
-	\begin{itemize}
-		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case.
-		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm.
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-\section{Preliminaries}
-
-%\begin{frame}{Preliminaries}
-
-%	\begin{block}{Norms}
-%		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
-%		\begin{itemize}
-%			\item Euclidean
-%			\begin{equation*}
-%			||u||_2 = \sqrt{u^Tu}
-%			\end{equation*}
-%			
-%			\item Elliptical
-%			\begin{equation*}
-%			||u||_{Q} = \sqrt{u^TQu}
-%			\end{equation*}
-%		\end{itemize}
-%	\end{block}
-
-%\end{frame}
-
-\section{Maximal Covering by Disks}
-\begin{frame}{Maximal Covering by Disks}{One disk}
-
-	$MCD(\Pp, 1)$ is the problem of placing one disk on the plane to cover a subset of a demand set $\Pp$, with $n$ points, maximizing the weights of the covered points.
-
-	\begin{equation*}\label{eq:max_one_disk}
-		\max_q w(\Pp \cap D(q)),
-	\end{equation*}
-
-	\begin{itemize}
-		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$.
-		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$.
-		\item $D(q)$ is a unit disk with center at point $q$.
-		%\item \autocite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
-		%\item \autocite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
-		%\item We will introduce an equivalent problem...
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Maximal Covering by Disks}{One disk}
-\begin{figure}
-	\caption{An instance of $MCD(\Pp,1)$.}
-	\includegraphics[scale=0.6]{figures/mcd_one_disk.pdf}
-	\source{Elaborated by the author.}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Maximal Covering By Disks}{One disk}
-
-	Works and results found in the literature:
-
-	\begin{itemize}
-		\item $MCD$ is as difficult the problem of given $n$ numbers, find three of them that sum to $0$. Proved by \autocite{aronov:2008}.
-
-		\item In \autocite{drezner} a $\bigO(n^2\log{n})$ algorithm was developed. The idea of our algorithm to sort the intersections by their angles comes from here.
-
-		\item In \autocite{chazelle:1986}, a $\bigO(n^2)$ algorithm was developed. It actually solves an equivalent problem which is introduced next.
-	\end{itemize}
-
-\end{frame}
-
-\subsection{Maximum Weight Clique Problem}
-\begin{frame}{Maximum Weight Clique Problem}
-	Let $\D=\{D_1,\dots,D_n\}$ be a set of $n$ unit disks with weights $w_i>0$. The maximum weight clique is defined as
-
-	\begin{equation*}
-	\max_q \sum_{D_k \cap q \neq \emptyset} w_k,
-	\end{equation*}
-
-	\begin{itemize}
-		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$.
-		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.
-		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}
-	\begin{figure}
-		\only<1>{\caption{An instance of $MCD(\Pp, 1)$.}}
-		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
-		\only<3>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
-		\only<1>{\includegraphics[scale=0.55]{figures/mwc_1.pdf}}
-		\only<2>{\includegraphics[scale=0.55]{figures/mwc_2.pdf}}
-		\only<3>{\includegraphics[scale=0.55]{figures/mwc_3.pdf}}
-		%\only<2>{\input{figures/intro_b.tex}}
-		\source{Elaborated by the author.}
-	\end{figure}
-\end{frame}
-
-%\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
-%		\begin{figure}[H]
-%		\centering
-
-%		\only<1>{}
-
-%		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
-
-%		\only<1>{\input{figures/max_w_clique_v2.tex}}
-%		\only<2>{\input{figures/max_w_clique_b.tex}}
-      %\center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
-%		\source{Elaborated by the author.}
-%		\label{fig:mcd_instance}
-%	\end{figure}
-%\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	Defining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$:\\~\\
-
-	Let $D_i$ (at the origin) and $D_j$ be two unit disks that intersect at two points.
-
-	\begin{itemize}
-		\item We know that the two intersection points define two arcs in $D_i$.
-		\item One of the arcs bounds $D_i\cap D_j$. That is the one we want to determine.
-
-		\item We can determine the polar angles of the two intersection points.
-		%\item Assume $D_i$ is at the origin.
-		\item Assuming counter-clockwise direction, we define $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ as the angles of intersection that determines the arc of $D_i$ that bounds $D_i \cap D_j$.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-
-\begin{figure}
-	\caption{$\Gamma_+(1,2)$ and $\Gamma_-(1,2)$ example.}
-	\includegraphics[scale=0.65]{figures/gammas.pdf}
-		\source{Elaborated by the author.}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	\begin{figure}[H]
-		\centering
-
-		\caption{Three disks and their intersection points and angles.}
-		\input{figures/img2.tex}
-		\source{Elaborated by the author.}
-		\label{fig:3disks_intersect}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-
-	Some observations allow us to arrive at the algorithm:
-
-%	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.
-
-	\begin{itemize}
-		\item An intersection region of disks is bounded by arcs.
-
-		\item The arc $A(\Gamma_+(i,j),\Gamma_-(i,j))$ (counter-clockwise) determines a region where $i$ and $j$ intersect.
-
-		\item For every disk $D_i$, we want to find an angle $\theta$, such that $$w(\{D_k : \theta \in A(\Gamma_+(i,k),\Gamma_-(i,k))\}),$$ is maximized. Most overlapping intervals (circular).
-
-		\item To transform it to the problem of finding the most overlapping intervals, just copy the list of intersection angles. The arcs such that $\Gamma_+(i,j) > \Gamma_-(i,j)$ will be considered.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-
-	Transforming it to the most overlapping intervals.
-
-	\begin{figure}[H]
-		\centering
-
-		\caption{The intersections list of a disk with three other disks.}
-		\input{figures/fig:array_disks.tex}
-		\source{Elaborated by the author.}
-		%\label{fig:array_disks}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-	Our algorithm for the Maximum Weight Clique Problem:\\~\\
-
-	For every disk $D_i$, do:
-	\begin{itemize}
-		\item Get the sorted list of intersection angles with $D_i$
-				$A=\cap_{j}\Gamma_+(i,j) \cup \Gamma_-(i,j)$.
-		\item Traverse it twice starting at the angle with smallest value.
-		\begin{itemize}
-			\item Keep a set of active disks. When an opening angle is visited, make the disk active, otherwise remove it from the set.
-			\item Update the optimal solution. Use the closing angle.
-		\end{itemize}
-	\end{itemize}
-\end{frame}
-
-%\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-%\begin{figure}
-	%\centering
-
-%	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
-%	\input{figures/mcd_sim.tex}
-%		\source{Elaborated by the author.}
-	%\label{fig:array_disks}
-%\end{figure}
-%\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-
-	\begin{figure}
-		\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
-		\only<1>{\input{figures/mcd_sim_1.tex}}
-		\only<2>{\input{figures/mcd_sim_2.tex}}
-		\only<3>{\input{figures/mcd_sim_2_5.tex}}
-		\only<4>{\input{figures/mcd_sim_3.tex}}
-		\only<5>{\input{figures/mcd_sim_4.tex}}
-		\only<6>{\input{figures/mcd_sim_5.tex}}
-		\only<7>{\input{figures/mcd_sim_6.tex}}
-		\only<8>{\input{figures/mcd_sim_7.tex}}
-			\source{Elaborated by the author.}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
-
-	The run-time complexity of the algorithm is $\bigO(n^2\log{n})$.
-
-	\begin{itemize}
-		\item There are $\bigO(n^2)$ intersections among $n$ disks.
-
-		\item Sorting takes $\bigO(n^2\log{n})$.
-
-		\item The traversal takes $\bigO(n)$ for every disk.
-
-		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.
-
-		\item The algorithm is basically finding the most number of overlapping intervals $n$ times.
-
-		\item As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.
-	\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Maximum Covering by Disks}{Multiple disks}
-
-	Works found in the literature:
-
-	\begin{itemize}
-		\item In \autocite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.
-
-		\item In \autocite{zhou} a heuristic method using an algorithm called mean-shift was developed.
-The mean-shift algorithm converges to a local density maxima of any probability distribution and it is used to find a smaller candidate list of centers for the disks.
-	\end{itemize}
-
-	Because of the similarities, we will discuss only the multiple ellipses algorithm later.
-
-\end{frame}
-\section{Maximal Covering by Ellipses}
-
-\begin{frame}{Ellipses}
-
-	\begin{block}{Ellipse}
-		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$, an ellipse is the set of points that satisfy
-
-		\begin{equation*}
-		||u-c||_Q^2 = (u-c)^TQ(u-c) = 1,
-		\end{equation*}
-
-		with $\le$ representing the set of covered points.
-	\end{block}
-
-	\begin{block}{Axis-parallel ellipse}
-		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by
-
-		\begin{equation*}
-		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1,
-		\end{equation*}
-
-		where $(a,b)$ are the shape parameters and $c=(c_x,c_y)$ is the center.
-	\end{block}
-
-\end{frame}
-
-\begin{frame}{Ellipses}
-	\begin{figure}[H]
-		\centering
-
-		\caption{The ellipse seen as just a linear transformation of a circle.}
-		\input{figures/elliptical.and.euclidean.norms.tex}
-		\source{Elaborated by the author.}
-		\label{fig:3ellipses_intersect}
-
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
-	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by
-
-	\begin{equation*}
-	\max_q |\Pp \cap E(q)|,
-	\end{equation*}
-
-	\begin{itemize}
-		\item $E(q)$ is an axis-parallel ellipse with center point $q$.
-		\item Assuming unit weights for now.
-		\item Same algorithm for one disk.
-	\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
-\begin{figure}[H]
-	\centering
-
-	\caption{Intersection points of $E_1$ with $E_2$ and $E_3$ along with opening and closing angles indicators.}
-	\input{figures/3ellipses_with_gammas.tex}
-	\source{Elaborated by the author.}
-	\label{fig:3ellipses_with_gammas}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
-	Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by
-
-	\begin{equation*}
-	\max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|},
-	\end{equation*}
-
-	\begin{itemize}
-		\item $\E$ is a set of $m$ ellipses.
-		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
-		\item \autocite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
-	\begin{algorithm}[H]
-		%\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
-		\begin{algorithmic}[1]
-			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
-			\STATE $Z \gets \{\}$
-			\STATE $Cov \gets \{p_i\}$
-			\FOR{$cnt=1..2$} 
-			\FOR{$a \in A$}
-			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
-			\IF{$a$ is a starting angle}
-			\STATE $Cov \gets Cov \cup \{p_a\}$
-			\ELSE
-			\STATE $Cov \gets Cov \setminus \{p_a\}$
-			\ENDIF
-			\STATE $Z \gets Z \cup \{Cov\}$
-			\ENDFOR
-			\ENDFOR
-
-		\end{algorithmic}
-	\end{algorithm}
-\end{frame}
-
-\begin{frame}
-	\begin{figure}
-		\caption{Optimal solution with two ellipses for a random instance.}
-		\input{figures/example_2_ellipses.tex}
-		\source{Elaborated by the author.}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Maximal Covering by Ellipses}
-
-	\begin{itemize}
-		\item The algorithm for $m$ ellipses tries every possible assignment of coverage for every one of the ellipses.
-		\item Run-time complexity of $\bigO(n^{2m})$.
-
-		\item Simpler than the $m$ disks algorithm proposed by \autocite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).
-
-		\item Small improvements can be made in the pre-processing exhibited earlier in oder to reduce the size of the search space:
-		\begin{itemize}
-			\item Non-maximal coverage sets.
-			\item Ellipses that are too distant do not need to be checked.
-		\end{itemize}
-
-		\item The unit-weight assumption can be easily dropped.
-	\end{itemize}
-
-\end{frame}
-
-\section{Future Work}
-
-\begin{frame}{Future Work}
-	Primary goals:
-\begin{itemize}
-	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \autocite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
-
-	\item Develop an exact method for the version of the problem introduced in \autocite{andreta} where the ellipses can be freely rotated.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Future Work}
-
-	Secondary goals:
-	\begin{itemize}
-
-	\item Develop a probabilistic approximation algorithm based on \autocite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
-The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse.
-The case with more than one ellipse is left as a challenge for us for the next steps of our research.
-
-	\item In \autocite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity.
-We want to generalize this for the elliptical distance function and achieve a better run-time complexity.
-We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.
-
-		\end{itemize}
-\end{frame}
-
-\begin{frame}[allowframebreaks]
-%	\frametitle{References}
-%\bibliographystyle{authoryear-comp}
-%	\bibliography{../references.bib}
-\printbibliography
-\end{frame}
+	\begin{align*}
+	q = \frac{64(BDE - AE^2 - CD^2)}{(4AC-B^2)^2}
+	\end{align*}
 

### 2019-06-10 drafts/3points-ellipse5.tex
wip

@@
 \usepackage{algorithmic}
-
+\usepackage[utf8]{inputenc}
 \usepackage{caption}
@@
 	\section{Intro}
-	Let's assume that $x_1, y_1 = (0,0)$ and $x_2 = 0$. Then we have:
+	Queremos encontrar uma ellipse com major-axis $a$ e minor-axis $b$, tal que ela contenha três pontos $(x_1, y_1), (x_2, y_2), (x_3, y_3)$.
+
+	Vamos assumir que $(x_1, y_1) = (0,0)$ e $x_2 = 0$. Veja que podemos aplicar translação e rotação aos pontos originais para obter uma instância desta forma.
+
+	A equação da ellipse é dada por
+
+	\begin{equation}
+	Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0
+	\end{equation}
+
+	Substituindo $(x_1, y_1)$ chegamos que $F=0$.
+
+	Vamos assumir que todos os outros parametros são diferente de $0$.
+Veja que  as equações dadas por $(A, B, C, D, E)$ e $(\lambda A, \lambda B, \lambda C, \lambda D, \lambda E)$ representam a mesma elipse.
+Por isso vamos fixar $B=-1$.
+
+	Substituindo $(0, y_2)$ obtemos:
 
 	\begin{align*}
-	E=-Cy_2\\
-	Dx_3=-(Ax_3^2 + Bx_3y_3 + C(y_3^2-y_2y_3))\\
+	Cy_2^2 + Ey_2 = 0\\
+	E = -Cy_2
 	\end{align*}
 
-	Renaming things:
+	Substituindo $(x_3, y_3)$ obtemos:
+
+	\begin{align*}
+	Ax_3^2 + x_3y_3 + C(y_3^2 - y_2y_3) + Dx_3 = 0\\
+	D = -\frac{Ax_3^2 - x_3y_3 + C(y_3^2 - y_2y_3)}{x3}
+	\end{align*}
+
+	Agora nos resta fixar os parametros da forma da elipse $(a, b)$ e determinar $A$ e $C$.
+
+	\section{Determinando $A, C$}
+
+	Fixando $B=1$ impomos que o angulo de rotação da elipse seja diferente de $0$.
+
+	Temos duas equações que determinam $a,b$. Seja $\Delta=4AC-B^2=4AC-1$.
 
 	\begin{align}
-	E=C\beta\\
-	D = A\alpha_a + B\alpha_b + C\alpha_c
+	a^2 = \dfrac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C - \sqrt{1 + (A-C)^2}}\\
+	b^2 = \frac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C + \sqrt{1 + (A-C)^2}}
 	\end{align}
 
-	\section{Working with $a$ and $b$}
-
-	Let's call $q$ the normalizor factor:
+	Deixe que $q = \frac{a^2}{b^2}$, $q$ representa a ecentricidade ou a proporção entre $a$ e $b$.
+Fixando $q$, conseguimos fixar a forma, mas não a escala da elipse.
+Vamos fazer isso pois as contas ficam mais simples.
 
 	\begin{align*}
-	q = \frac{64(BDE - AE^2 - CD^2)}{(4AC-B^2)^2}
+	q = \frac{A + C + \sqrt{1 + (A-C)^2}}{A + C - \sqrt{1 + (A-C)^2}}\\
+	\sqrt{1 + (A-C)^2}(q+1) = (A+C)(q-1)\\
 	\end{align*}
 
+	Seja $w = \frac{q-1}{q+1} = \frac{a^2-b^2}{a^2+b^2}$, veja que $w < 1$, isso será útil em algum momento. Portanto:
+
+	\begin{align*}
+	1 + (A-C)^2 = w^2(A+C)^2\\	
+	\end{align*}
+
+	Também vamos fixar o angulo de rotação $\theta \in [0, \frac{\pi}{4}]$. Seja $t = \tan{(2\theta)}$, temos:
+
+	\begin{align*}
+	t = \frac{B}{A-C}\\
+	A = C - \frac{1}{t}
+	\end{align*}
+
+	Voltando a equação anterior, temos:
+
+	\begin{align*}
+	1 + (C - \frac{1}{t} - C)^2 = w^2(C-\frac{1}{t} + C)^2\\
+	1 + \frac{1}{t^2} = w^2(2C-\frac{1}{t})^2
+	\end{align*}
+
+	Resolvendo a quadrática, achamos o valor de $C$:
+
+	\begin{align}
+	C = \frac{w \pm \sqrt{t^2+1}}{2tw}
+	\end{align}
+
+	Só vamos utilizar $C^+$ (o $C^-$ da um angulo de rotação maior que $\frac{\pi}{4}$, ainda nao sei o porquê).
+
+	\subsection{Algumas propriedades}
+
+	A condição $4AC - B^2 > 0$ tem que ser satisfeita para que a equação da conica represente uma elipse.
+
+	Seja $\Gamma = A+C+\sqrt{1+(A-C)^2}$, substituindo $A$ em $\Gamma$, temos:
+
+	\begin{align*}
+	\Gamma = 2C - \frac{1}{t} + \sqrt{1 + \frac{1}{t^2}}
+	\end{align*}
+
+	Como estamos lidando primeiro com $t>0$, temos:
+
+	\begin{align*}
+	\Gamma = 2C - \frac{\sqrt{1+t^2} - 1}{t}
+	\end{align*}
+
+	Algumas propriedades que verifiquei utilizando Wolfram:
+
+	\begin{itemize}
+		\item $4AC - B^2>0$ faz com que $A>0$ e $C>0$.
+		\item $C'<0$ para todo $t$.
+		\item $A'<0$ se e só se $t < \dfrac{\sqrt{1-w^2}}{w}$
+		\item $\Delta' < 0$ para todo $t$.
+		\item $\Gamma>0$ e $\Gamma' < 0$ para todo $t$.
+	\end{itemize}
+
+%	Vamos agora olhar para $D$ e $E$:
+
+	\begin{align*}
+	D = -(A\alpha + \beta + C\gamma)\\
+	E = -C\eta\\
+	\alpha, \gamma, \eta>0
+	\end{align*}
+
+	Suas derivadas
+
+	\begin{align*}
+	D' = -(A'\alpha + C'\gamma)
+	\end{align*}
+
+	\subsection{Só Falta achar $t$}
+
+	Infelizmente não é fácil achar $t$.
+
+	\section{Outro Approach}
+
+	Vamos supor que os pontos são $(0,0), (h, 0), (\alpha h, m \times \alpha h)$ e que $m$ é positivo.
+
+	Temos que $D = -Ah$ e também fixamos $B=-1$.
+
+	Vamos agora utilizar a equação que fixa a ecentricidade para isolar $C$.
+
+	\begin{align*}
+	1 + (A-C)^2 = w^2(A+C)^2\\
+	C = \frac{-Aw^2 - A \pm \sqrt{4A^2w^2 + w^2 -1}}{w^2 - 1}
+	\end{align*}
+
+	Fixando o $A$ e encontrando $C$, talque $4AC > 1$ irá fixar a ecentricidade da elipse.
+
+	\subsection{O terceiro ponto}
+
+	Vamos olhar para a área detemrminada pelo triangulo dos pontos, chamamos a de $s$. Veja que o diametro da elipse que contem este triangulo é monótona em $s$ que por sua vez é monotona em $h$.
+
+	Primeiro, econtramos a intersecção da reta $y=mx$ com a elipse.
+
+	\begin{align*}
+	Ax^2 -x^2m + Cx^2m^2 -Ahx + Emx = 0\\
+	Ax -xm + Cxm^2 -Ah + Em = 0\\
+	x(A-m + Cm^2) = Ah - Em\\
+	x = \frac{Ah-Em}{A-m + Cm^2}
+	\end{align*}
+
+	Para determinar $E$, utilizamos o terceiro ponto.
+
+	\begin{align*}
+	A\alpha^2h^2 + B\alpha^2 h^2 m + Cm^2\alpha^2h^2 -Ah^2 \alpha + E m \alpha h = 0\\
+	Em = -(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)
+	\end{align*}
+
+	Voltando para a equação anterior obtemos:
+
+	\begin{align*}
+	x = \frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2}\\
+	y = mx\\
+	y = m\frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2}
+	\end{align*}
+
+	Tomando a área do triangulo obtemos, veja que $s$ é conhecida dado $h$:
+
+	\begin{align*}
+	m\frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2} \times h = s\\
+	A(mh^2\alpha) - h^2m^2\alpha + Cm^3h^2\alpha = s(A-m+Cm^2)\\
+	A(mh^2\alpha -s) + C(m^3h^2\alpha -sm^2) = h^2m^2\alpha\\
+	A\beta_1 + C\beta_2 + \beta_3 = 0
+	\end{align*}
 \end{document}

### 2019-06-11 drafts/3points-ellipse5.tex
wip

@@
 	A\alpha^2h^2 + B\alpha^2 h^2 m + Cm^2\alpha^2h^2 -Ah^2 \alpha + E m \alpha h = 0\\
-	Em = -(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)
+	Em = -(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)\\
+	Em = h(-A(\alpha  - 1) +\alpha m - Cm^2\alpha)\\
+	E = h\beta
+	\end{align*}
+
+	\subsection{Semi-major}
+
+	Fixando $A$ e utilizando a formula do semi-major, fazendo $H=\Delta(A + C - \sqrt{1 + (A-C)^2})$.
+
+	\begin{align*}
+	a^2 H = AE^2 + DE + CD^2\\
+	a^2H = Ah^2\beta^2 -Ah^2\beta + CA^2h^2\\
+	h^2(A\beta^2 - A\beta + CA^2) = a^2H\\
+	h^2 = \frac{a^2H}{A\beta^2 - A\beta + CA^2}
 	\end{align*}

### 2019-08-06 defesa/tex/chapter/ellipses.tex
add defesa folder

--- 2019-03-29 tex/chapter/ellipses.tex
@@
-In this chapter, two versions of the Planar Maximal Covering by Ellipses Problem will be introduced.
-Firstly, the axis-parallel variant will be defined and a method for it will be developed.
-Secondly, the version where there is no axis-parallel constraint and the ellipses can be freely rotated will be introduced.
+In this chapter, the version of the Planar Maximal Covering by Ellipses Problem where every ellipse has to be parallel to the coordinate axis will be introduced and a method for it will be developed.
 
@@
 Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$ is a pair of real numbers called the shape parameters of an ellipse.
-In the general case, every point has weights, but without loss of generality (later explained), this detail will be ignored and the weights are assumed to be unitary.
+In the general case, every point has weights, but firstly this detail will be ignored and the weights are assumed to be unitary.
 The notation used here is similar to the one introduced on \autoref{chapter:pmclp}, the ellipse with an undefined center is referred to as $E$.
@@
 Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse} (in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$).
+Also, to denote the points on the border of $E(q)$ we use the notation $\tilde{E}(q)$, therefore $p \in \tilde{E}(q)$ translates to $p$ being on the border of $E(q)$.
 Hence, the problem can be defined as follows.
@@
 
-\begin{definicao}
+\begin{definicao}\label{def:MCE}
 Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by

### 2019-08-06 defesa/tex/chapter/ellipses_n.tex
add defesa folder

This section introduces the covering problem that does not have any axis-parallel constraint for the ellipses, we denote this version of the problem as $MCER$. The removal of this constraint introduces a new variable which is responsible for determining the rotation angle of every ellipse.

An instance of the non-axis-parallel is defined exactly like the axis-parallel one on \autoref{chapter:ellipses}. It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, with every point having a unitary weight, and a set of ellipses $\E=\{E_1, \dots, E_m\}$, with fixed shape parameters $(a_i, b_i) \in \R^2_{>0}$, $i \in \{1, \dots, n\}$ with the additional condition that $a_i > b_i$. Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, 2\pi]^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$. Also, we denote $\Pp \cap E_i(q_i, \theta_i)$ as the set of points covered by $E_i$ on this configuration. Therefore $MCER$ is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the number of points covered by the $m$ ellipses, which is given by \autoref{eq:optMCEn}.

\begin{equation}\label{eq:optMCEn}
\max_{Q, \Theta}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i, \theta_i)\right|}.
\end{equation}

An additional notation is used on this chapter, we define $\tilde{E_i}(q_i, \theta_i)$ to be the set of points on the border of $E_i(q_i, \theta_i)$, we will specially use the operation $\Pp \cap \tilde{E_i}(q_i, \theta_i)$ referring to the set of points from $\Pp$ that lie on the border of $E_i(q_i, \theta_i)$.

\begin{lema}\label{lema:mce_2b}
	Let $(\Pp, \E)$ be an instance of $MCER$. In an optimal solution of $MCER$, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j)=\Pp \cap E_j(q_j, \theta_j)$ and $\Pp \cap \tilde{E_j}(q_j', \theta_j) \ge 2$.
\end{lema}

\begin{demonstracao}
	First, the angle of rotation can be ignored as it does not change.

	Let $A=\Pp \cap E_j(q_j, \theta_j)$ be the set of points covered by $E_j$ and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point from $A$.

	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses. As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertice. Selecting any of these vertices as $q_j'$ will make $|\Pp \cap E_j(q_j', \theta_j)| \ge 2$.

\end{demonstracao}

\begin{definicao}\label{def:feasible_angle}
	Let $E$ be an ellipse and $u, v \in \R^2$. An angle $\theta \in [0, \pi]$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
\end{definicao}

\begin{lema}\label{lema:3pnts}
	Let $(\Pp, \E)$ be an instance of $MCER$, in an optimal solution, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|>2$, one of the two cases is true:

	\begin{enumerate}
		\item There is $q', \theta'$, and $\{u, v, w\} \subset \Pp \cap E_j(q_j, \theta_j)$, such that $\{u, v, w\} \subset \tilde{E}(q', \theta')$.

		\item Let $A=\Pp \cap E_j(q_j, \theta_j)$, and $u, v \in A$ such that there exists $\hat{q}_j$ such that $\{u, v\} \subset \tilde{E_j}(\hat{q}_j, \theta_j)$ and $A \subset E_j(\hat{q}_j, \theta_j)$. Then for any $(E_j, u, v)$-feasible angle $\theta \in [0, 2\pi]$, there exists $\bar{q}_j$ such that $\{u, v\} \subset \tilde{E_j}(\bar{q}_j, \theta)$ and $A \subset E_j(\bar{q}_j, \theta)$.
	\end{enumerate}
\end{lema}

The first case of \autoref{lema:3pnts} is saying that there is another optimal solution which has $E_j$ covering the same set of points, but with three points on its border.

The second case says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$ the covered set will stay the same.

The idea to prove \autoref{lema:3pnts} is that after fixing $u, v$ on the border of $E_j$, which is possible by \autoref{lema:mce_2b}, the movement of rotation and translation while keeping $u, v$ on the border is continuous. Because of that, the negation of case two implies case one and vice versa.

As a consequence of \autoref{lema:3pnts}, from any optimal solution of $MCER$ it is possible to obtain another optimal solution which every ellipse has one, two or three points on its border.
This result cuts the search space to $\bigO(mn^3)$ which is a very nice gain from where we started, with a infinite search space. Breaking down every possible case, for every ellipse in an optimal solution we obtain:

\begin{itemize}
	\item The ellipse covers only one point. You could place the ellipse so it has one point on its border, satisfying the claim above.
	\item The ellipse covers exactly two points. Using \autoref{lema:mce_2b}, there is a solution with those two points on the border.
	\item The ellipse covers more than two points. First we can use \autoref{lema:mce_2b} to fix two points on the border. By \autoref{lema_3} the angle can be ignored as long as the two fixed points are on the border or exists another optimal solution with three (or more) points on the border.
\end{itemize}

From those cases, three sub-problems need to be solved so we can have a method for $MCER$.

The first one is covering one point with an ellipse which is trivial. For a point $(x, y) \in \R$ just set the center of the ellipse to be $(x, y) \in \R$.

The second problem and third problems deserve sections on their own.

\section{Two points on the border}

Because of the case 2 of \autoref{lema:3pnts}, we want to find for every pair of points the set of points an ellipse with them on its border can cover

### 2019-08-06 defesa/tex/chapter/future.tex
add defesa folder

To take advantage of the great amount of work found in the literature,
 we decided to first introduce the planar maximal covering by disks problem, develop a method for it, and just then adapt it for the ellipses case. It turned out that because of the similarities between the two problems, adapting was possible and actually very simple. This made the method developed by us have a very different approach than the ones in \cite{andreta} and \cite{canbolat}. The next step is to implement it and compare the results that \cite{andreta} obtained.

For the next step of our master's research we set the following objectives as primary:

\begin{itemize}
    \item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

    \item Develop an exact method for the version of the problem introduced in \cite{andreta} where the ellipses can be freely rotated.

\end{itemize}

The following goals are set as secondary:

\begin{itemize}
    \item Develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse. The case with more than one ellipse is left as a challenge for us for the next steps of our research.

    \item In \cite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity. We want to generalize this for the elliptical distance function and achieve a better run-time complexity. We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.
\end{itemize}

%Also, the version of the problem where every ellipse can be freely rotated is set as a primary goal for this master's research. In \cite{andreta}, the deterministic method developed by them could not obtain solutions for moderate-to-large instances within reasonable time. Because of that, a stochastic global optimization method was proposed, it performed well and was able to obtain an optimal solution for small cases. The goal we have in mind for the future is to develop an exact method that takes into consideration the algorithm we developed for the axis-parallel version of the problem and compare the results.

%Finally, as a secondary goal, we want to

### 2019-08-06 defesa/tex/chapter/pmclp.tex
add defesa folder

--- 2019-03-27 tex/chapter/pmclp.tex
@@
 In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP.
-Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$ where $\Pp$ is a set of points and $m$ is the number of unit disks.
+Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$, where $\Pp$ is a set of points and $m$ is the number of unit disks.
 
@@
 A $\bigO(n^2)$ algorithm is proposed by \cite{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \cite{drezner}.
-As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real number that sum to $0$, given $n$ real numbers).
+As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers).
 Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for $MCD(\Pp,1)$, which meant that no better time-complexity could be achieved.
@@
 
-Initially, the input of the problem defines a unit disk with its center point undefined, a solution for the problem will then choose a point to be the center of the unit disk, in other words a solution places the disk somewhere in the plane.
+Initially, the input of the problem defines a unit disk with its center point undefined, a solution for the problem will then choose a point to be the center of the unit disk.
+In other words, a solution places the disk somewhere in the plane.
 We refer to the unit disk with undefined center as $D$. If it is placed at a center $q \in \R^2$, we call it $D(q)$.
@@
 \begin{definicao}
-    Let $\Pp=\{p_1,\dots,p_n\}$ be a set of $n$ points in $\R^2$, and $w(p)>0, p \in \Pp$ the weight of every point in $\Pp$, we denote $w(A)$, with $A \subset \Pp$, as the sum of weights of every point in $A$.
-Finally, let $D$ be a unit disk, we define the optimal solution of $MCD(\Pp,1)$ as
+    Let $\Pp=\{p_1,\dots,p_n\}$ be a set of $n$ points in $\R^2$ and $w(p)>0, p \in \Pp$, the weight of every point in $\Pp$.
+We denote $w(A)$, with $A \subset \Pp$, as the sum of weights of every point in $A$.
+Finally, let $D$ be a unit disk, we define an optimal solution of $MCD(\Pp,1)$ as
 
@@
 
-Therefore, an optimal solution for an instance of $MCD(\Pp,1)$ will be a point in which a unit disk located at it, covers points whose weights, when summed, is maximal.
+Therefore, an optimal solution for an instance of $MCD(\Pp,1)$ will be a point in which a unit disk located at, covers points whose weights, when summed, is maximal.
 
@@
 
-In \cite{chazelle:1986, cabello:2006}, on the other hand, the authors instead of working directly with $MCD(P,1)$, introduced an equivalent problem called maximum weight clique.
-Both methods for this problem consist on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
-With the graph constructed, a traversal would be done to obtain the answer, thus the time complexity of $\bigO(n^2)$.
+In \cite{chazelle:1986} and \cite{cabello:2006}, on the other hand, instead of working directly with $MCD(P,1)$, an equivalent problem called Maximum Weight Clique was introduced.
 The algorithm that we later describe in this work also uses this equivalence.
-That is why it has been taken to be fundamental to introduce the maximum weight clique problem and discuss the equivalence.
+That is why it has been taken to be fundamental to introduce the Maximum Weight Clique Problem and discuss the equivalence.
 
-\section{Maximum weight clique}
+\section{Maximum Weight Clique Problem}
 
-Let $\Pp=\{p_1,\dots,p_n\}$, with $p\in \R^2$ be a set of points, $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$.
+Let $\Pp=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$, be a set of points, $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$.
 A clique, in this context, is a non-empty intersection area of a subset of disks.
@@
 As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique), but the intersection of all the three together is empty.
-That is why the clique problem for unit disks is also referred to as the maximum geometric clique problem when the condition of common intersection exists and as the maximum graphical clique problem where there is only the pairwise intersection condition \cite{inplace:2014}.
-The graphical version of the problem was studied by \cite{graphical-clique} where a $\bigO(n^{4.5})$ algorithm was proposed.
-Also, in \cite{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm, which needs $\bigO(1)$ extra space, for arbitrary radii disks was proposed.
+That is why the clique problem for unit disks is also referred to as the Maximum Geometric Clique Problem when the condition of common intersection exists and as the Maximum Graphical Clique Problem when there is only the pairwise intersection condition \cite{inplace:2014}.
+The graphical version of the problem was studied by \cite{graphical-clique}, where a $\bigO(n^{4.5})$ algorithm was proposed.
+Also, in \cite{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm\footnote{An in-place algorithm is an algorithm that needs $\bigO(1)$ extra space.} for arbitrary radii disks was proposed.
+In \cite{chazelle:1986}, the method for the Maximum Geometric Weight Clique Problem consists on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
+With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.
 
@@
 
-    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection}
-    \begin{tikzpicture}[scale=0.55]
+    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}
+    \begin{tikzpicture}[scale=1]
     %\draw [help lines] (-5,-3) grid (5,3);
@@
 
-    \node[below] at (0,0) {\tiny $p_1$};
-    \node[below] at (0.9, 1.6) {\tiny $p_2$};
-    \node[below] at (-0.9, 1.6) {\tiny $p_3$};
+    \node[below] at (0,0) {$p_1$};
+    \node[below] at (0.9, 1.6) {$p_2$};
+    \node[below] at (-0.9, 1.6) {$p_3$};
 
@@
 
-A solution for the maximum weight clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized.
-Even though there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the maximum weight clique is enough.
+A solution for the Maximum Weight Clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized.
+Even though there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the Maximum Weight Clique is enough.
 This will become clear when the equivalence is stated.
-With everything in hands, we can define the maximum weight clique problem as follows
+With everything in hands, we can define the Maximum Weight Clique Problem as follows.
 
 \begin{definicao}\label{def:max_weight_clique}
-    Let $\D$ be a set of unit disks and $\Pp$ be a set of points as defined before, an optimal solution for the maximum weight clique problem is given by
+    Let $\D$ be a set of unit disks and $\Pp$ be a set of points as defined before. An optimal solution for the Maximum Weight Clique Problem is given by
 
@@
 
-As it has been proposed, with the equivalence of the two problems, the optimal solution of the maximum weight clique problem is also the optimal solution of the $MCD(\Pp,1)$, which means that a disk centered at $q$, defined in \autoref{def:max_weight_clique}, will have a maximal weight covering of the set $\Pp$.
+As it has been proposed, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of the $MCD(\Pp,1)$, which means that a disk centered at $q$, defined in \autoref{def:max_weight_clique}, will have a maximal weight covering of the set $\Pp$.
 
-Given an instance of $MCD(\Pp,1)$, the equivalent maximum weight clique problem is obtained by defining the set $\D$ to be the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
-A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$, this means that a intersection between some disks is an area where a disk could be placed to cover the corresponding points.
+Given an instance of $MCD(\Pp,1)$, the equivalent Maximum Weight Clique Problem is obtained by defining set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
+A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$.
+This means that a intersection between some disks is an area where a disk could be placed to cover the corresponding points.
 
-In \autoref{fig:three_disks_no_intersection}, it can be seen that there is no point where a disk could be placed such that it would cover $p_1, p_2$ and $p_3$, nonetheless anywhere, in any of the pairwise intersections, a disk could be placed to cover the two corresponding points.
+In \autoref{fig:three_disks_no_intersection}, it can be seen that there is no point where a disk could be placed such that it would cover $p_1, p_2$ and $p_3$, nonetheless, in any of the pairwise intersections, a disk could be placed to cover the two corresponding points.
 
-Formally, in the maximum weight clique problem, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the $MCD(P,1)$ problem.
+Formally, in the Maximum Weight Clique Problem, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the $MCD(P,1)$ problem.
 Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the one disk maximal covering problem.
-It means that $q$ will lie inside the region $\bigcap_{k \in I} D_k$.
+It means that $q$ will lie inside region $\bigcap_{k \in I} D_k$.
 
-\subsection{An algorithm for the maximum weight clique problem}
+\subsection{An algorithm for the Maximum Weight Clique Problem}
 
@@
 
-Without loss of generality, the weights will be ignored, and the method will be described for the maximum clique problem, assuming that every disk has unit weight.
+Without loss of generality, the weights will be ignored, and the method will be described for the Maximum Clique Problem, assuming that every disk has unit weight.
 Also, it will be assumed that no pair of disks are placed at the same center.
@@
 Let $\D$ be a set of $n$ unit disks, a non-empty intersection area of a subset of disks is convex and bounded by the arcs of the disks that are intersecting \cite{inplace:2014}.
-This observation makes checking for every disk $\Cc$, every intersection area that is bounded by its arc sufficient in order to find the optimal solution.
+With this observation, in order to find an optimal solution, it is sufficient to check, for every disk $D$, every intersection area that is bounded by its arc.
 
@@
 If $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$.
-Then, We define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
+Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
 \end{definicao}
@@
 
-    \caption{Three disks and their intersection points}
+    \caption{Three disks and their intersection points.}
     \input{tex/img2.tex}
@@
 
-In \autoref{fig:3disks_intersect}, it is shown all the intersection points between $D_1$ with $D_2$ and $D_3$, also they are labeled according to \autoref{def:inter_arc}, note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).
+In \autoref{fig:3disks_intersect}, it is shown all the intersection points between $D_1$ with $D_2$ and $D_3$.
+Also, they are labeled according to \autoref{def:inter_arc}.
+Note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).
 
-With \autoref{def:inter_arc} in hands, we can establish the basis of the algorithm to find the maximum clique that a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$ in counter-clockwise order keeping a set of active disks, when an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
+With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm to find the maximum clique in which a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$, in counter-clockwise order, keeping a set of active disks.
+When an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
 This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ (see \autoref{fig:3disks_intersect}).
 If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it.
-If there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and the optimal solution could end up not being found.
-This can be worked around repeating the traversal once without resetting the active disks set, that way in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$.
-This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal repetition (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
+If there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and an optimal solution could end up not being found.
+This can be worked around repeating the traversal once without resetting the active disks set, that way, in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$.
+This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated, simulating the traversal repetition (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
 It can be seen that without the repetition, the algorithm would find $2$ as the value of an optimal solution, which is wrong.
@@
 \begin{algorithmic}[1]
-\Procedure{$MCD_1$}{$\Pp$}\Comment{Returns the maximum number of disks that have a non-empty.}
+\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$.}
+\Ensure{The maximum number of points that can be covered by a unit disk.}
+
+\item[]
+
+\Procedure{$MCD_1$}{$\Pp$}
 \State $Q_{best} \gets \{\}$
@@
 \State Let $I_i$ be the set of disks that intersect with $D_i$
-\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
-\State $Q \gets \{D_i\}$ \Comment{The set of active disks}
-\For{$cnt=1..2$} \Comment{Do it twice}
-\For{$a \in A$}\Comment{Assuming $A$ is sorted}
+\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $D_i$.}
+
+\ForAll{$j \in I_i$}
+\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
+\EndFor
+
+%\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
+\State $Q \gets \{D_i\}$ \Comment{The set of active disks.}
+\For{$cnt=1..2$} \Comment{Do it twice.}
+\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
 \State Let $D_a$ be the disk that intersects $D_i$ at angle $a$. 
@@
 \begin{lema}\label{lema:disk}
-The \autoref{algoritmo:mcd_1} for the maximum clique has a $\bigO((n+K)\log{n})$ run time complexity where $K$ is the number of intersections of the $n$ disks.
+\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
 \end{lema}
@@
 
-If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.
+If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (the set of disks that intersect with $D_i$, defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.
 
-\section{Multiple disks $MCD(\Pp, m)$}
+\section{Multiple disks, $MCD(\Pp, m)$}
 
@@
 Firstly, they solve the sub-problem $MCD(\Pp, 2)$ in $\bigO(n^3\log{n})$.
-Then for the rest of the points that are not in that solution, it uses the algorithm developed in \cite{chazelle:1986} for the one-disk case checking every possible solution for every one of the disks left.
+Then for the rest of the points that are not in that solution, it uses the algorithm developed in \cite{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.
 
-It can be seen that in any solution of $MCD(\Pp, m)$, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the maximum weight clique problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be the optimal solution.
+Also, in \cite{zhou} an heuristic method for large-scale $MCD$ is proposed.
+It uses a probabilistic algorithm called mean-shift which is a gradient ascent method proven to converge to a local density maxima of any probability distribution.
+The mean-shift is utilized to find good candidates of centers for the unit disks, then the method backtracks to find the best assignment.
+The results showed that the greedy algorithm achieves an optimal coverage in some instances, but for some other ones it has a 15 percent worse coverage ratio.
+
+It can be seen that in any solution of $MCD(\Pp, m)$, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be an optimal solution.
 The number of points \autoref{algoritmo:mcd_1} goes through is $\bigO(n^2)$, then checking every possible center for every ellipse yields a $\bigO(n^{2m})$ run-time complexity.
@@
 
-The choice of developing a different method for the problem, instead of using the one from \cite{cabello:2006}, is taken for the sake of simplicity considering both algorithms achieve similar bounds.
+The choice of developing a different method for the problem, instead of using the one from \cite{cabello:2006}, is taken for the sake of simplicity, considering both algorithms achieve similar bounds.

### 2019-08-06 drafts/3points-ellipse5.tex
add defesa folder

@@
 
-	Voltando para a equação anterior obtemos:
+	\subsubsection{Domínio $A$}
 
+	A função $h^2$ não está definida para todo $A$. Como $A$ pode ser encontrado em função de $t = tan(2\theta)$, em que $\theta$ é o angulo de rotação da elipse, omitindo-se as contas temos:
+
+	\begin{align}
+	A = \frac{-w + \sqrt{t^2 + 1}}{2tw}\\
+	\lim\limits_{t\to \infty} A = \frac{1}{2w}\\
+	\lim\limits_{t\to 0^+} A = \infty\\
+	A' = -\frac{w + \frac{1}{\sqrt{t^2+1}}}{2wt^2} < 0
+	\end{align}
+
+	Logo, o domínio de $A$ é $\left[\dfrac{1}{2w}, \infty\right)$.
+
+	Vamos propor que $h$ é uma função monótona. Portanto, será possível aplicar o algoritmo da bisseção para encontrar a resposta.
+
+	A partir desse definição de $A$, também obtemos que $C = A + \frac{1}{t}$, ou seja $C > A$.
+
+	\subsection{Monotonicidade}
+
+	É possível, calculando a derivada de $C$ em função de $A$, ver que $C$ é crescente.
+	Como $\Delta>0$ e $\Delta'>0$, verificamos a seguir que $H$ é crescente:
 	\begin{align*}
-	x = \frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2}\\
-	y = mx\\
-	y = m\frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2}
-	\end{align*}
-
-	Tomando a área do triangulo obtemos, veja que $s$ é conhecida dado $h$:
-
-	\begin{align*}
-	m\frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2} \times h = s\\
-	A(mh^2\alpha) - h^2m^2\alpha + Cm^3h^2\alpha = s(A-m+Cm^2)\\
-	A(mh^2\alpha -s) + C(m^3h^2\alpha -sm^2) = h^2m^2\alpha\\
-	A\beta_1 + C\beta_2 + \beta_3 = 0
+	(A+C-\sqrt{1+(A-C)^2})' = 1 + C' - \frac{(A-C)(1-C')}{\sqrt{1+(A-C)^2}}
 	\end{align*}

### 2019-08-07 defesa/tex/appendix/3pnts_ellipse_1.tex
add appendix

Let $p_1, p_2, p_3 \in \R^2$ and $E$ be an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$. The problem is to find every pair $(q, \theta)$, with $q \in \R^2$ and $\theta \in [0, \pi]$, such that $\{p_1, p_2, p_3\} \subset \tilde{E}(q, \theta)$. In other words, one wants to find every center and angle of rotation of $E$, such that $p_1$, $p_2$ and $p_3$ are on the border of $E$.
The goal of this section is to show that the number of solutions of such problem is limited, finding every one of them analytically is beyond the scope of this work.

\section{Transforming the input}

To make it simpler, let us translate the system to put $p_1$ at $(0,0)$. Then, we assume that the ellipse is actually axis-parallel and the points are the ones rotating. When an angle is found such that the three points lie on the border of the ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$. This is described by \autoref{eq:trpnts}.

\begin{equation}\label{eq:trpnts}
\hat{p}=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
\sin{\theta}&-\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right]
\end{equation}

The only unknown variable in \autoref{eq:trpnts} is $\theta$. Instead of dealing with trigonometric equations, we will use the following relations:

\begin{equation}\label{eq:trigId}
	\begin{array}{c}
\cos{\theta} = \dfrac{t^2-1}{t^2+1}\\
\sin{\theta} = \dfrac{2t}{t^2+1}.
\end{array}
\end{equation}

After replacing the trigonometric functions with \autoref{eq:trigId}, we get $\hat{p}_1, \hat{p}_2, \hat{p}_3$ as quotients of polynomials on $t$ of degree $2$.

\section{Three points on a circle}
%find ref%
There is a known way to determine the circle which contains three given points. 
Let $(x_1, y_1)$, $(x_2, y_2)$, $(x_3, y_3)$ be three non-colinear points in $\R^2$, the equation of the circle passing through these points is given by the determinant on \autoref{3pnt_circle}

\begin{equation}\label{3pnt_circle}
\left|
\begin{array}{cccc}
x^2+y^2&x&y&1\\
x_1^2+y_1^2&x_1&y_1&1\\
x_2^2+y_2^2&x_2&y_2&1\\
x_3^2+y_3^2&x_3&y_3&1
\end{array}
\right| = 0.
\end{equation}

Replacing the points by $\hat{p_1}, \hat{p_2}, \hat{p_3}$, we get:

\begin{eqnarray*}
\left|
\begin{array}{cccc}
x^2+y^2&x&y&1\\
0&0&0&1\\
\hat{p}_{2x}^2+\hat{p}_{2y}^2&\hat{p}_{2x}&\hat{p}_{2y}&1\\
\hat{p}_{3x}^2+\hat{p}_{3y}^2&\hat{p}_{3x}&\hat{p}_{3y}&1\\
\end{array}
\right| = 0\\
(x^2+y^2)\left|
\begin{array}{cc}
\hat{p}_{2x}& \hat{p}_{2y}\\
\hat{p}_{3x}& \hat{p}_{3y}
\end{array}\right|
+
x\left|
\begin{array}{cc}
	\hat{p}_{2x}^2+\hat{p}_{2y}^2& \hat{p}_{2y}\\
	\hat{p}_{3x}^2+\hat{p}_{3y}^2& \hat{p}_{3y}
\end{array}\right|
y\left|
\begin{array}{cc}
	\hat{p}_{2x}& \hat{p}_{2x}^2+\hat{p}_{2y}^2\\
	\hat{p}_{3x}& \hat{p}_{3x}^2+\hat{p}_{3y}^2
\end{array}\right|=0.
\end{eqnarray*}

We need to determine the radius of the circle and find the value of $t$, so the radius is equal to $b$. Rearranging the terms we obtain the expression:

\begin{equation}\label{eq:le3}
\dfrac{\left|
	\begin{array}{cc}
	\hat{p}_{2x}& \hat{p}_{2x}^2+\hat{p}_{2y}^2\\
	\hat{p}_{3x}& \hat{p}_{3x}^2+\hat{p}_{3y}^2
	\end{array}\right|^2
+\left|
\begin{array}{cc}
\hat{p}_{2x}^2+\hat{p}_{2y}^2& \hat{p}_{2y}\\
\hat{p}_{3x}^2+\hat{p}_{3y}^2& \hat{p}_{3y}
\end{array}\right|^2
}{4\left|
\begin{array}{cc}
\hat{p}_{2x}& \hat{p}_{2y}\\
\hat{p}_{3x}& \hat{p}_{3y}
\end{array}\right|^2} = b^2,
\end{equation}

After replacing \autoref{eq:trpnts} on \autoref{eq:le3}, we obtain a polynomial of degree $12$, which gives an upper-bound of $12$ to the number of solutions.

Nevertheless, because ellipses are symmetrical over their major-axis, we only need to consider rotations on the range $[0, \pi]$ as $\theta$ and $\theta+\pi$ represent the exact same solution geometrically. This ends halving the upper-bound to $6$.

### 2019-08-07 defesa/tex/appendix/3pnts_ellipse_1.tex
add2

@@
 \begin{equation}\label{eq:trpnts}
-\hat{p}=\left[\begin{array}{cc}
+\varphi(p)=\left[\begin{array}{cc}
 \frac{b}{a}&0\\
@@
 \cos{\theta}&\sin{\theta}\\
-\sin{\theta}&-\cos{\theta}
+-\sin{\theta}&\cos{\theta}
 \end{array}\right]\left[\begin{array}{c}
@@
 
-After replacing the trigonometric functions with \autoref{eq:trigId}, we get $\hat{p}_1, \hat{p}_2, \hat{p}_3$ as quotients of polynomials on $t$ of degree $2$.
+After replacing the trigonometric functions with \autoref{eq:trigId}, we get:
+
+\begin{equation}
+\varphi(p)=\left[\begin{array}{c}
+\frac{b}{a}(\dfrac{t^2-1}{t^2+1}p_x + \dfrac{2t}{t^2+1}p_y)\\
+\dfrac{t^2-1}{t^2+1}p_y - \dfrac{2t}{t^2+1}p_x\\
+\end{array}\right],
+\end{equation}
+
+Thus $\varphi(p_1), \varphi(p_2), \varphi(p_2)$ can be written as quotients of polynomials on of degree $2$.
 
@@
 Nevertheless, because ellipses are symmetrical over their major-axis, we only need to consider rotations on the range $[0, \pi]$ as $\theta$ and $\theta+\pi$ represent the exact same solution geometrically.
-This ends halving the upper-bound to $6$.
+This ends up halving the upper-bound to $6$.

### 2019-08-07 defesa/tex/appendix/3pnts_ellipse_1.tex
wip

@@
 \begin{equation}
-\varphi(p)=\left[\begin{array}{c}
-\frac{b}{a}(\dfrac{t^2-1}{t^2+1}p_x + \dfrac{2t}{t^2+1}p_y)\\
-\dfrac{t^2-1}{t^2+1}p_y - \dfrac{2t}{t^2+1}p_x\\
-\end{array}\right],
+\varphi(p)=\left[\begin{array}{cc}
+\dfrac{b}{a}\dfrac{t^2-1}{t^2+1}& \dfrac{b}{a}\dfrac{2t}{t^2+1}\\
+\dfrac{t^2-1}{t^2+1}& -\dfrac{2t}{t^2+1}\\
+\end{array}\right]p.
 \end{equation}
 
-Thus $\varphi(p_1), \varphi(p_2), \varphi(p_2)$ can be written as quotients of polynomials on of degree $2$.
+Thus $\varphi(p_1), \varphi(p_2), \varphi(p_2)$ can be written as quotients of univariate polynomials of degree $2$.
 
@@
 
-Replacing the points by $\hat{p_1}, \hat{p_2}, \hat{p_3}$, we get:
+As for this problem $(x_1, y_1)=(0,0)$, we can rewrite \autoref{3pnt_circle} as:
 
-\begin{eqnarray*}
+\begin{equation}
 \left|
-\begin{array}{cccc}
-x^2+y^2&x&y&1\\
-0&0&0&1\\
-\hat{p}_{2x}^2+\hat{p}_{2y}^2&\hat{p}_{2x}&\hat{p}_{2y}&1\\
-\hat{p}_{3x}^2+\hat{p}_{3y}^2&\hat{p}_{3x}&\hat{p}_{3y}&1\\
+\begin{array}{ccc}
+x^2+y^2&x&y\\
+x_2^2+y_2^2&x_2&y_2\\
+x_3^2+y_3^2&x_3&y_3
 \end{array}
-\right| = 0\\
+\right| = 0.
+\end{equation}
+
+Expanding the determinant we get:
+
+\begin{equation*}
 (x^2+y^2)\left|
 \begin{array}{cc}
-\hat{p}_{2x}& \hat{p}_{2y}\\
-\hat{p}_{3x}& \hat{p}_{3y}
+x_2&y_2\\
+x_3&y_3
 \end{array}\right|
@@
 \begin{array}{cc}
-	\hat{p}_{2x}^2+\hat{p}_{2y}^2& \hat{p}_{2y}\\
-	\hat{p}_{3x}^2+\hat{p}_{3y}^2& \hat{p}_{3y}
+x_2^2+y_2^2&y_2\\
+x_3^2+y_3^2&y_3
 \end{array}\right|
++
 y\left|
 \begin{array}{cc}
-	\hat{p}_{2x}& \hat{p}_{2x}^2+\hat{p}_{2y}^2\\
-	\hat{p}_{3x}& \hat{p}_{3x}^2+\hat{p}_{3y}^2
+x_2&x_2^2+y_2^2\\
+x_3&x_3^2+y_3^2
 \end{array}\right|=0.
-\end{eqnarray*}
+\end{equation*}
 
-We need to determine the radius of the circle and find the value of $t$, so the radius is equal to $b$. Rearranging the terms we obtain the expression:
+After completing the square we obtain \autoref{eq:le3} which is an expression for the radius of the circle, which has to be equal $b$.
 
@@
 	\begin{array}{cc}
-	\hat{p}_{2x}& \hat{p}_{2x}^2+\hat{p}_{2y}^2\\
-	\hat{p}_{3x}& \hat{p}_{3x}^2+\hat{p}_{3y}^2
+	x_2^2+y_2^2&y_2\\
+	x_3^2+y_3^2&y_3
 	\end{array}\right|^2
@@
 \begin{array}{cc}
-\hat{p}_{2x}^2+\hat{p}_{2y}^2& \hat{p}_{2y}\\
-\hat{p}_{3x}^2+\hat{p}_{3y}^2& \hat{p}_{3y}
+x_2&x_2^2+y_2^2\\
+x_3&x_3^2+y_3^2
 \end{array}\right|^2
@@
 \begin{array}{cc}
-\hat{p}_{2x}& \hat{p}_{2y}\\
-\hat{p}_{3x}& \hat{p}_{3y}
-\end{array}\right|^2} = b^2,
+x_2&y_2\\
+x_3&y_3
+\end{array}\right|^2} = b^2.
 \end{equation}
 
-After replacing \autoref{eq:trpnts} on \autoref{eq:le3}, we obtain a polynomial of degree $12$, which gives an upper-bound of $12$ to the number of solutions.
+We want to show that \autoref{eq:le3}, after replacing $(x_2, y_2)$ and $(x_3, y_3)$ with $\varphi(p_2)$ and $\varphi(p_3)$, is a polynomial on $t$ of degree $12$.
+As the denominator of $\varphi(p)_x$ and $\varphi(p)_y$ are the same, we can ignore it as it cancels out when it is equal to $0$.
+Let us analyze one of the determinants from the numerator of \autoref{eq:le3} which is the term with the highest degree.
 
-Nevertheless, because ellipses are symmetrical over their major-axis, we only need to consider rotations on the range $[0, \pi]$ as $\theta$ and $\theta+\pi$ represent the exact same solution geometrically.
-This ends up halving the upper-bound to $6$.
+\begin{equation}\label{eq:num1}
+\left|
+	\begin{array}{cc}
+	||\varphi(p_2)||^2&\varphi(p_2)_y\\
+	||\varphi(p_3)||^2&\varphi(p_3)_y
+	\end{array}\right|^2=(||\varphi(p_2)||^2\varphi(p_3)_y-||\varphi(p_3)||^2\varphi(p_2)_y)^2.
+\end{equation}
+
+As $||\varphi(p_2)||^2$ has degree $4$ and $\varphi(p_3)_y$ has degree $2$ (ignoring the denominator), after multiplying and squaring we arrive at the conclusion that the polynomial has degree $12$.
+
+\section{Final Remarks}
+
+Expressing the actual polynomial would take too much space, and actually finding every one of its roots is a very expensive task computationally, so just determining its degree was enough for what we wanted to show.
+
+Also, ellipses are symmetrical with respect to their major-axis which means that an ellipse is identical to itself rotate by $\pi$.
+Because of that, any solution found has a symmetrical one, which is obtained by adding $\pi$ to it.
+This halves the upper-bound for the number of solutions to $6$.

### 2019-08-08 defesa/tex/appendix/3pnts_ellipse_1.tex
wip

@@
 
-As $||\varphi(p_2)||^2$ has degree $4$ and $\varphi(p_3)_y$ has degree $2$ (ignoring the denominator), after multiplying and squaring we arrive at the conclusion that the polynomial has degree $12$.
+As $||\varphi(p_2)||^2$ has degree $4$ and $\varphi(p_3)_y$ has degree $2$ (ignoring the denominator). After multiplying and squaring we arrive at the conclusion that the polynomial has degree $12$.
 

### 2019-08-08 defesa/tex/chapter/ellipses_n.tex
wip

@@
 As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertice.
-Selecting any of these vertices as $q_j'$ will make $|\Pp \cap E_j(q_j', \theta_j)| \ge 2$.
+Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \tilde{E}_j(q_j', \theta_j)| \ge 2$.
 
@@
 
-The second case says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$ the covered set will stay the same.
+The second case of \autoref{lema:3pnts} says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$, there is a center that maintains the covered set the same.
 
@@
 
-As a consequence of \autoref{lema:3pnts}, from any optimal solution of $MCER$ it is possible to obtain another optimal solution which every ellipse has one, two or three points on its border.
-This result cuts the search space to $\bigO(mn^3)$ which is a very nice gain from where we started, with a infinite search space.
-Breaking down every possible case, for every ellipse in an optimal solution we obtain:
+If we define an equivalence relation between optimal solutions as: $S_1$ is equivalent to $S_2$ if they both cover the same set of points, we can use \autoref{lema:3pnts} and \autoref{lema:mce_2b} to identify the equivalence classes.
+Let $S$ be any optimal solution, in $[S]$ (its equivalence class) there is another solution where any ellipse $E_j \in \E$ falls in at least one of the cases below:
 
 \begin{itemize}
-	\item The ellipse covers only one point. You could place the ellipse so it has one point on its border, satisfying the claim above.
-	\item The ellipse covers exactly two points. Using \autoref{lema:mce_2b}, there is a solution with those two points on the border.
-	\item The ellipse covers more than two points.
-First we can use \autoref{lema:mce_2b} to fix two points on the border.
-By \autoref{lema_3} the angle can be ignored as long as the two fixed points are on the border or exists another optimal solution with three (or more) points on the border.
+	\item $E_j$ covers only on point.
+	\item $E_j$ covers more than one point with $u$ and $v$ being on the border of $E_j$.
+Note that there could be infinitely many of solutions like that, however \autoref{lema:3pnts} guarantees that any $(E_j, u, v)$-feasible angle yields an equivalent optimal solution.
+	\item $E_j$ covers more than two points with three of them on its border.
 \end{itemize}
 
-From those cases, three sub-problems need to be solved so we can have a method for $MCER$.
+The following two sections will treat the second and third cases (the first case is trivial).
+Going through every possibility of an ellipse falling in any of the three cases guarantees that an optimal solution is found.
 
-The first one is covering one point with an ellipse which is trivial. For a point $(x, y) \in \R$ just set the center of the ellipse to be $(x, y) \in \R$.
+\section{Ellipse by two points}
 
-The second problem and third problems deserve sections on their own.
+Let $E$ be an ellipse with shape parameters $(a, b)\in \R^2_{>0}$ and $u, v\in \R^2$, one wants to find a $(E, u, v)$-feasible angle $\theta\in[0,\pi]$ and every center $q\in\R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
 
-\section{Two points on the border}
-
-Because of the case 2 of \autoref{lema:3pnts}, we want to find for every pair of points the set of points an ellipse with them on its border can cover
+For a fixed angle, finding every center such that two points are on the border of the ellipse is done on \autoref{chapter:ellipses_intersection}, from there we know that there could be at most $2$ of such centers.

### 2019-08-08 defesa/tex/chapter/ellipses_n.tex
wip

@@
 \begin{itemize}
-	\item $E_j$ covers only on point.
+	\item $E_j$ covers only one point.
 	\item $E_j$ covers more than one point with $u$ and $v$ being on the border of $E_j$.
-Note that there could be infinitely many of solutions like that, however \autoref{lema:3pnts} guarantees that any $(E_j, u, v)$-feasible angle yields an equivalent optimal solution.
+Note that there could be infinitely many of solutions like that, however, \autoref{lema:3pnts} guarantees that any $(E_j, u, v)$-feasible angle yields an equivalent optimal solution.
 	\item $E_j$ covers more than two points with three of them on its border.
@@
 For a fixed angle, finding every center such that two points are on the border of the ellipse is done on \autoref{chapter:ellipses_intersection}, from there we know that there could be at most $2$ of such centers.
+The only thing left to be done is finding a feasible angle.
+It turns out that the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$ will be a feasible angle if, and only if the set of feasible angles is not empty.
+This can be seen geometrically as other angles achieve a lesser maximum distance between the two points on the border.

### 2019-08-23 defesa/tex/chapter/definicoes.tex
wip

--- 2019-05-18 quali/tex/chapter/definicoes.tex
@@
 
-It is easy to see that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.
+The elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.
 
@@
 
-An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal.}.
+An axis-parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal.}.
 This can be understood as a scaling transformation applied to the Euclidean norm.
@@
 For example, when we define $\Pp \cap E$ as the set of points in $\Pp$ that are covered by $E$, we are implicitly calling $E$ the set of points that are covered by the ellipse itself as it is defined by \autoref{def:ellipse}.
+
+\subsection{Non-axis-parallel}
+
+An non-axis-parallel ellipse centered at $c\in\R^2$ can also be described by \autoref{def:ellipse}.
+Nonetheless, a simpler equation is going to be used here.
+Besides the center, the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in [0, \pi]$ is given.
+This angle represents the angle between the $x$-axis and the major-axis of the ellipse.
+
+A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations.
+First, the ellipse can be translated to the origin and then rotated by $-\theta$, the reverse transformations are expressed by \autoref{eq:rotated_ellipse}.
+
+\begin{equation}\label{eq:rotated_ellipse}
+\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
+\end{equation}
+
+Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in [0, \pi]$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co}.
+
+\begin{equation}\label{eq:rotated_ellipse_co}
+\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1.
+\end{equation}

### 2019-08-23 defesa/tex/chapter/ellipses_n.tex
wip

@@
-This section introduces the covering problem that does not have any axis-parallel constraint for the ellipses, we denote this version of the problem as $MCER$.
+This section introduces the covering problem that does not have any axis-parallel constraint for the ellipses, we denote this version of the problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
 The removal of this constraint introduces a new variable which is responsible for determining the rotation angle of every ellipse.
@@
 It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, with every point having a unitary weight, and a set of ellipses $\E=\{E_1, \dots, E_m\}$, with fixed shape parameters $(a_i, b_i) \in \R^2_{>0}$, $i \in \{1, \dots, n\}$ with the additional condition that $a_i > b_i$.
-Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, 2\pi]^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$.
-Also, we denote $\Pp \cap E_i(q_i, \theta_i)$ as the set of points covered by $E_i$ on this configuration.
-Therefore $MCER$ is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the number of points covered by the $m$ ellipses, which is given by \autoref{eq:optMCEn}.
+Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, 2\pi]^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$, which is given by \autoref{eq:rotated_ellipse_co}.
+Also, $\Pp \cap E_i(q_i, \theta_i)$ is denoted as the set of points covered by $E_i$ on this configuration.
+Therefore MCER is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the number of points covered by the $m$ ellipses, which is given by \autoref{eq:optMCEn}.
 
@@
 
-An additional notation is used on this chapter, we define $\tilde{E_i}(q_i, \theta_i)$ to be the set of points on the border of $E_i(q_i, \theta_i)$, we will specially use the operation $\Pp \cap \tilde{E_i}(q_i, \theta_i)$ referring to the set of points from $\Pp$ that lie on the border of $E_i(q_i, \theta_i)$.
+An additional notation is used on this chapter, $\tilde{E_i}(q_i, \theta_i)$ is defined to be the set of points on the border of $E_i(q_i, \theta_i)$, specially, the operation $\Pp \cap \tilde{E_i}(q_i, \theta_i)$ is used to refer to the set of points from $\Pp$ that lie on the border of $E_i(q_i, \theta_i)$.
 
 \begin{lema}\label{lema:mce_2b}
-	Let $(\Pp, \E)$ be an instance of $MCER$.
-In an optimal solution of $MCER$, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j)=\Pp \cap E_j(q_j, \theta_j)$ and $\Pp \cap \tilde{E_j}(q_j', \theta_j) \ge 2$.
+	Let $(\Pp, \E)$ be an instance of MCER.
+In an optimal solution of MCER, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j)=\Pp \cap E_j(q_j, \theta_j)$ and $\Pp \cap \tilde{E_j}(q_j', \theta_j) \ge 2$.
 \end{lema}
@@
 	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses.
-As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertice.
+As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertex.
 Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \tilde{E}_j(q_j', \theta_j)| \ge 2$.
@@
 \end{demonstracao}
+
+What \autoref{lema:mce_2b} is saying is that any optimal solution for MCER can be transformed into another optimal solution where every ellipse covers the same set of points and those which cover more than one point has two points on their border.
+Also, this equivalent optimal solution can be always achieved by just translating the ellipses.
+An example is shown on \autoref{fig:ellipse-2-points} for one ellipse.
+
+A lot of the ideas developed in this chapter are based on fixing two points on the border of an ellipse, which is why \autoref{def:feasible_angle} introduces a new notation for angles that an ellipse rotated by it can be translated into a center, such that it contains two fixed points.
+
+\begin{figure}[H]
+	\centering
+	\caption{An optimal solution before and after applying \autoref{lema:mce_2b}.}
+	\includegraphics{tex/figures/scripts/ellipse-2-points}
+	\fautor
+	\label{fig:ellipse-2-points}
+\end{figure}
 
@@
 
+On \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
+On one of them, an ellipse is rotated by $\pi/4$ and it is located such that it contains the two fixed points on its border.
+That means $\pi/4$ is a $(E, u, v)$-feasible angle.
+On the other example, the ellipse is rotated by $\pi/2$ and there is not a center where the ellipse can be placed so it contains the two fixed points--they are too far apart.
+This makes $\pi/2$ a not $(E, u, v)$-feasible angle.
+
+\begin{figure}
+	\centering
+	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
+	\includegraphics{tex/figures/scripts/feasible-angle}
+	\fautor
+	\label{fig:feasible-angle}
+\end{figure}
+
 \begin{lema}\label{lema:3pnts}
-	Let $(\Pp, \E)$ be an instance of $MCER$, in an optimal solution, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|>2$, one of the two cases is true:
+	Let $(\Pp, \E)$ be an instance of MCER, in an optimal solution, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|>2$, at least one of the two cases is true:
 
@@
 The second case of \autoref{lema:3pnts} says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$, there is a center that maintains the covered set the same.
+
+On \autoref{fig:lema-3-points} both cases of \autoref{lema:3pnts} are shown.
+There, it can be seen that for the second case, it does not matter which feasible angle by which the ellipse is rotated, the third point will always be inside the coverage area.
+Also, an example of the first case is shown where there are three points lie exactly on the border of the ellipse.
+
+\begin{figure}
+	\centering
+	\caption{An example of \autoref{lema:3pnts}.}
+	\includegraphics{tex/figures/scripts/lema-3-points}
+	\fautor
+	\label{fig:lema-3-points}
+\end{figure}
 
@@
 This can be seen geometrically as other angles achieve a lesser maximum distance between the two points on the border.
+
+\section{Ellipse by three points}
+
+In this section the problem of finding every location (center, angle of rotation), that makes an ellipse have three points on its border is presented, we will refer to this problem as \sigla{E3PNT}{Ellipse by Three points}.
+Firstly, it is going to be shown that the number of solutions of this problem is limited, this is a fundamental result which allows an algorithm for MCER to be developed.
+Secondly, a method to find every solution of E3PNT is described.
+
+\subsection{The number of solutions is limited by a constant}
+
+To prove that the number of solutions is limited by a constant, the problem is going to be modeled as finding the roots of an univariate polynomial of degree $12$.
+Let $u, v, w \in \R^2$ and $E$ be an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
+The problem is to find every pair $(q, \theta)$, with $q \in \R^2$ and $\theta \in [0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
+
+To make it simpler, let us translate the system, so the point $u$ is at $(0,0)$.
+Then, we assume that the ellipse is actually axis-parallel and the points are the ones rotating.
+When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$.
+This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle.
+This process can be parametrized by the angle of rotation of the points, as described by \autoref{eq:trpnts}, and because of the invertibility of linear transformations solutions for E3PNT can be obtained by reversing the transformations.
+
+\begin{figure}[H]
+	\centering
+	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+	\includegraphics{tex/figures/scripts/circumscribed-circle}
+	\fautor
+	\label{fig:circumscribed-circle}
+\end{figure}
+\begin{equation}\label{eq:trpnts}
+\varphi(p, \theta)=\left[\begin{array}{cc}
+\frac{b}{a}&0\\
+0&1
+\end{array}\right]
+\left[\begin{array}{cc}
+\cos{\theta}&\sin{\theta}\\
+-\sin{\theta}&\cos{\theta}
+\end{array}\right]\left[\begin{array}{c}
+p_x\\
+p_y
+\end{array}\right].
+\end{equation}
+
+Then, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\varphi(u, \theta), \varphi(v, \theta)$ and $\varphi(w, \theta)$, such that the circle has radius $b$.
+As, for three non-colinear fixed points, there is always an unique circumscribed circle for the triangle formed by those three points, the only variable to be determined ends up being the angle of rotation $\theta$.
+
+Let $d_u(\theta), d_v(\theta), d_w(\theta)$ be the length of each of the sides of the triangle formed by the points $\varphi(u, \theta), \varphi(v, \theta)$ and $\varphi(w, \theta)$; and $A(\theta)$ be its area--note that the transformation does not preserve distance or area.
+Then, the radius $R$ of the circumscribed circle is given by \autoref{eq:circumscribed_circle} \cite[p.~189]{johnson1960}.
+
+\begin{equation}\label{eq:circumscribed_circle}
+R = \dfrac{d_u(\theta)d_v(\theta)d_w(\theta)}{4A(\theta)}.
+\end{equation}
+
+Instead of working with trigonometric functions, the following identities given by \autoref{eq:trigId} are used, so a polynomial can be obtained.
+
+\begin{equation}\label{eq:trigId}
+\begin{array}{c}
+\cos{\theta} = \dfrac{t^2-1}{t^2+1}\\
+\sin{\theta} = \dfrac{2t}{t^2+1}.
+\end{array}
+\end{equation}
+
+Looking at $\varphi(u, \theta)$, after replacing the trigonometric functions with \autoref{eq:trigId}, it then becomes a quotient of polynomials.
+Let $\Delta=t^2+1$, then $\varphi(u, \theta)$ is a polynomial of degree $2$ divided by $\Delta$.
+The area $A(\theta)$ can be calculated by taking the cross product of the vectors induced by $\varphi(v, \theta)$ and $\varphi(w, \theta)$ which ends up being a polynomial of degree $4$ divided by $\Delta^2$.
+Finally, let $\gamma_d(t)$ be a polynomial of degree $d\in\mathbb{N}$, then we get the following expressions for the length of the triangle and its area,
+\begin{align*}
+d_u(\theta)=||\varphi(v, \theta)-\varphi(u, \theta)|| = \sqrt{\dfrac{\gamma_4(t)}{\Delta^2}}\\
+A(\theta)=\dfrac{1}{2}|\varphi(v, \theta) \times \varphi(w, \theta)|=\frac{\gamma_4(t)}{\Delta^2}
+\end{align*}
+imposing \autoref{eq:circumscribed_circle} so the radius of the circumscribed circle is equal to $b$, we get the following equation,
+
+\begin{align*}
+\left(\sqrt{\dfrac{\gamma_4(t)}{\Delta^2}}\right)^3 - \dfrac{b\gamma_4(t)}{\Delta^2} = 0\\
+\dfrac{\gamma_{12}(t)}{\Delta^6} - \dfrac{b\gamma_8(t)}{\Delta^4} = 0,
+\end{align*}
+which after some manipulation, becomes an univariate polynomial of degree $12$ which can have up to $12$ different real roots.
+Because ellipses are symmetrical with respect to their major-axis, and any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$, the number of different solutions is cut in half.
+Therefore, the number of angles of rotation and centers that an ellipse of fixed shape can be placed, so it has three fixed points on its border is limited to $6$.
+
+Because there is no closed formula to find roots of polynomials of degree $12$ \cite{skopenkov2015}, and root-finding iterative methods, such as Newton's method, generally are not convergent for polynomials of degree $4$ or more \cite{mc1}, this approach is only useful to show the limitedness of the set of solutions.
+
+\subsection{A method for E3PNT}
+
+In this section we present a method for E3PNT and we try to justify it being correct, however, a proof is left as future work.

### 2019-08-23 defesa/tex/chapter/ellipses_n.tex
wip

@@
 
-\begin{lema}\label{lema:mce_2b}
+\begin{proposicao}\label{lema:mce_2b}
 	Let $(\Pp, \E)$ be an instance of MCER.
 In an optimal solution of MCER, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j)=\Pp \cap E_j(q_j, \theta_j)$ and $\Pp \cap \tilde{E_j}(q_j', \theta_j) \ge 2$.
-\end{lema}
+\end{proposicao}
 
@@
 Let $S$ be any optimal solution, in $[S]$ (its equivalence class) there is another solution where any ellipse $E_j \in \E$ falls in at least one of the cases below:
-
 \begin{itemize}
@@
 
-In this section the problem of finding every location (center, angle of rotation), that makes an ellipse have three points on its border is presented, we will refer to this problem as \sigla{E3PNT}{Ellipse by Three points}.
-Firstly, it is going to be shown that the number of solutions of this problem is limited, this is a fundamental result which allows an algorithm for MCER to be developed.
+The problem of finding every center and angle of rotation of an ellipse which makes it have three points on its border is presented in this section.
+We refer to it as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
+The objective is to find every pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
+
+Firstly, it is going to be shown that the number of solutions of E3PNT is limited by a constant, this is a fundamental result which allows an algorithm for MCER to be developed.
 Secondly, a method to find every solution of E3PNT is described.
@@
 To prove that the number of solutions is limited by a constant, the problem is going to be modeled as finding the roots of an univariate polynomial of degree $12$.
-Let $u, v, w \in \R^2$ and $E$ be an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
-The problem is to find every pair $(q, \theta)$, with $q \in \R^2$ and $\theta \in [0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
 
@@
 
-In this section we present a method for E3PNT and we try to justify it being correct, however, a proof is left as future work.
+In this section we present a method for E3PNT and we try to make a case of it being correct, however, a proof is left as future work.
+
+The idea of the method is to let two points fixed on the border of the ellipse and vary the angle to find it when the third point hits the border of the ellipse.
+
+Let $u$ and $v$ be the pair out of the three points that are most distant from each other, also let $\theta_u \in [0, \pi)$ be the greatest $(E, u, v)$-feasible angle.
+Given an angle $\theta \in [0, \theta_u]$, let $q_\theta\in\R^2$ be a center of $E$, such that $\{u, v\} \subset \tilde{E}(q_\theta, \theta)$.
+Note that in general, there are two such centers, they could be told apart by their $y$-coordinate, and the method needs to be executed for both of them separately.
+Then, a function $\rho : [0, \theta_u] \mapsto \R$ is defined to be the elliptical norm of the point $w$ with respect to $E(q_\theta, \theta)$.
+
+\begin{equation}\label{eq:rho}
+\rho(\theta) = \dfrac{}{}
+\end{equation}
+
+The angles such that \autoref{eq:rho} is equal to $1$ are the ones that are part of the solution and achieve three points on the border of the ellipse.
+From now on, a method is presented that tries to find those points in a efficient way.
+We conjecture that \autoref{eq:rho} is unimodal by parts, and we present a method that takes advantage of that.

### 2019-09-24 defesa/tex/chapter/ellipses_n.tex
wip

@@
 It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, with every point having a unitary weight, and a set of ellipses $\E=\{E_1, \dots, E_m\}$, with fixed shape parameters $(a_i, b_i) \in \R^2_{>0}$, $i \in \{1, \dots, n\}$ with the additional condition that $a_i > b_i$.
-Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, 2\pi]^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$, which is given by \autoref{eq:rotated_ellipse_co}.
+Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, \pi)^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$, which is given by \autoref{eq:rotated_ellipse_co}.
 Also, $\Pp \cap E_i(q_i, \theta_i)$ is denoted as the set of points covered by $E_i$ on this configuration.
@@
 \begin{definicao}\label{def:feasible_angle}
-	Let $E$ be an ellipse and $u, v \in \R^2$. An angle $\theta \in [0, \pi]$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
+	Let $E$ be an ellipse and $u, v \in \R^2$. An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
 \end{definicao}
@@
 \cos{\theta}&\sin{\theta}\\
--\sin{\theta}&\cos{\theta}
+\sin{\theta}&-\cos{\theta}
 \end{array}\right]\left[\begin{array}{c}
@@
 
-Then, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\varphi(u, \theta), \varphi(v, \theta)$ and $\varphi(w, \theta)$, such that the circle has radius $b$.
+Then, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $(0, 0), \varphi(v, \theta)$ and $\varphi(w, \theta)$, such that the circle has radius $b$.
 As, for three non-colinear fixed points, there is always an unique circumscribed circle for the triangle formed by those three points, the only variable to be determined ends up being the angle of rotation $\theta$.
 
-Let $d_u(\theta), d_v(\theta), d_w(\theta)$ be the length of each of the sides of the triangle formed by the points $\varphi(u, \theta), \varphi(v, \theta)$ and $\varphi(w, \theta)$; and $A(\theta)$ be its area--note that the transformation does not preserve distance or area.
+Let $A(\theta)$ be the area of the triangle formed by the points $(0, 0), \varphi(v, \theta)$ and $\varphi(w, \theta)$--note that the transformation does not preserve distance or area.
 Then, the radius $R$ of the circumscribed circle is given by \autoref{eq:circumscribed_circle} \cite[p.~189]{johnson1960}.
@@
 \begin{equation}\label{eq:circumscribed_circle}
-R = \dfrac{d_u(\theta)d_v(\theta)d_w(\theta)}{4A(\theta)}.
+R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)}.
 \end{equation}
 
-Instead of working with trigonometric functions, the following identities given by \autoref{eq:trigId} are used, so a polynomial can be obtained.
+Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, \pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b}.
+Note that, the problem now becomes the one of finding every $\theta \in [0, \pi)$, such that $\xi(\theta)=0$.
 
-\begin{equation}\label{eq:trigId}
-\begin{array}{c}
-\cos{\theta} = \dfrac{t^2-1}{t^2+1}\\
-\sin{\theta} = \dfrac{2t}{t^2+1}.
-\end{array}
+\begin{equation}\label{eq:circumscribed_circle_b}
+\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2.
 \end{equation}
 
-Looking at $\varphi(u, \theta)$, after replacing the trigonometric functions with \autoref{eq:trigId}, it then becomes a quotient of polynomials.
-Let $\Delta=t^2+1$, then $\varphi(u, \theta)$ is a polynomial of degree $2$ divided by $\Delta$.
-The area $A(\theta)$ can be calculated by taking the cross product of the vectors induced by $\varphi(v, \theta)$ and $\varphi(w, \theta)$ which ends up being a polynomial of degree $4$ divided by $\Delta^2$.
-Finally, let $\gamma_d(t)$ be a polynomial of degree $d\in\mathbb{N}$, then we get the following expressions for the length of the triangle and its area,
-\begin{align*}
-d_u(\theta)=||\varphi(v, \theta)-\varphi(u, \theta)|| = \sqrt{\dfrac{\gamma_4(t)}{\Delta^2}}\\
-A(\theta)=\dfrac{1}{2}|\varphi(v, \theta) \times \varphi(w, \theta)|=\frac{\gamma_4(t)}{\Delta^2}
-\end{align*}
-imposing \autoref{eq:circumscribed_circle} so the radius of the circumscribed circle is equal to $b$, we get the following equation,
+According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$.
+The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree, denoted by $\max_{i\in \{1, \dots, M\}}$, zero.
 
-\begin{align*}
-\left(\sqrt{\dfrac{\gamma_4(t)}{\Delta^2}}\right)^3 - \dfrac{b\gamma_4(t)}{\Delta^2} = 0\\
-\dfrac{\gamma_{12}(t)}{\Delta^6} - \dfrac{b\gamma_8(t)}{\Delta^4} = 0,
-\end{align*}
-which after some manipulation, becomes an univariate polynomial of degree $12$ which can have up to $12$ different real roots.
+ To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}, combine the parts as $\xi(\theta)$ is just addition and multiplication of terms in that form.
+It is also possible to see that the term of higher the degree of $\xi(\theta)$ is the multiplication of the three squared distances, as $\norm{\varphi(v, \theta)}^2$ has degree $2$ the degree of $\xi(\theta)$ is $6$.
+
+\begin{align}\label{eq:dd}
+	\norm{\varphi(v, \theta)}^2 = (v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta)^2 + (v_x\cos\theta - v_y\sin\theta)^2\\
+	\label{eq:dd2} A(\theta)^2=\dfrac{1}{4}\det\left(
+	\begin{array}{cc}
+		v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta&v_x\cos\theta - v_y\sin\theta\\
+		w_x\frac{b}{a}\cos\theta + w_y\frac{b}{a}\sin\theta&w_x\cos\theta - w_y\sin\theta
+	\end{array}\right)^2
+\end{align}
+
 Because ellipses are symmetrical with respect to their major-axis, and any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$, the number of different solutions is cut in half.
@@
 
-Because there is no closed formula to find roots of polynomials of degree $12$ \cite{skopenkov2015}, and root-finding iterative methods, such as Newton's method, generally are not convergent for polynomials of degree $4$ or more \cite{mc1}, this approach is only useful to show the limitedness of the set of solutions.
+A possible approach to find all the roots of a high-degree polynomial is to find all the eigenvalues of its companion matrix\cite{horn}.
+There are methods that do that with the observation that roots not close to the origin are susceptible to large errors and some times can not be found.
+This was experienced in some instances where the method could not find any roots which were priorly known.
+Therefore, Because there is no closed formula to find roots of polynomials of degree $12$ \cite{skopenkov2015}, and root-finding iterative methods, such as Newton's method, generally are not convergent for polynomials of degree $4$ or more \cite{mc1}, this approach is only useful to show the limitedness of the set of solutions.
+In the next section we present a method to approximate the roots of \autoref{eq:circumscribed_circle_b}.
 
@@
 
-The idea of the method is to let two points fixed on the border of the ellipse and vary the angle to find it when the third point hits the border of the ellipse.
+The idea of the method is to let two of the three points be fixed on the border of the ellipse and vary the angle to find it when the third point hits the border of the ellipse.
 
@@
 \begin{equation}\label{eq:rho}
-\rho(\theta) = \dfrac{}{}
+\rho(\theta) = \dfrac{\left((w-q_\theta)^T\left(\begin{array}{c}
+	\cos{\theta}\\
+	\sin{\theta}
+	\end{array}\right)\right)^2}{a^2}+
+\dfrac{\left((w-q_\theta)^T\left(\begin{array}{c}
+	\sin{\theta}\\
+	-\cos{\theta}
+	\end{array}\right)\right)^2}{b^2}
 \end{equation}

### 2019-09-27 defesa/tex/chapter/e3p.tex
wip

--- 2019-09-24 defesa/tex/chapter/ellipses_n.tex
@@
-This section introduces the covering problem that does not have any axis-parallel constraint for the ellipses, we denote this version of the problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
-The removal of this constraint introduces a new variable which is responsible for determining the rotation angle of every ellipse.
+The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section.
+Even though its simple statement--it is short and uses only basic mathematics concepts--we were not able to find any work that dealt with this problem, or even related ones, either as its main goal or as a sub-problem.
+As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way.
+We try to give a review of some of those, and also make a case for the method we propose in terms of velocity of convergence and quality of the solutions.
 
-An instance of the non-axis-parallel is defined exactly like the axis-parallel one on \autoref{chapter:ellipses}.
-It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, with every point having a unitary weight, and a set of ellipses $\E=\{E_1, \dots, E_m\}$, with fixed shape parameters $(a_i, b_i) \in \R^2_{>0}$, $i \in \{1, \dots, n\}$ with the additional condition that $a_i > b_i$.
-Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, \pi)^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$, which is given by \autoref{eq:rotated_ellipse_co}.
-Also, $\Pp \cap E_i(q_i, \theta_i)$ is denoted as the set of points covered by $E_i$ on this configuration.
-Therefore MCER is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the number of points covered by the $m$ ellipses, which is given by \autoref{eq:optMCEn}.
+We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
+A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
+In other words, the objective is to develop a method to find every solution of E3PNT.
 
-\begin{equation}\label{eq:optMCEn}
-\max_{Q, \Theta}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i, \theta_i)\right|}.
-\end{equation}
-
-An additional notation is used on this chapter, $\tilde{E_i}(q_i, \theta_i)$ is defined to be the set of points on the border of $E_i(q_i, \theta_i)$, specially, the operation $\Pp \cap \tilde{E_i}(q_i, \theta_i)$ is used to refer to the set of points from $\Pp$ that lie on the border of $E_i(q_i, \theta_i)$.
-
-\begin{proposicao}\label{lema:mce_2b}
-	Let $(\Pp, \E)$ be an instance of MCER.
-In an optimal solution of MCER, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j)=\Pp \cap E_j(q_j, \theta_j)$ and $\Pp \cap \tilde{E_j}(q_j', \theta_j) \ge 2$.
-\end{proposicao}
-
-\begin{demonstracao}
-	First, the angle of rotation can be ignored as it does not change.
-
-	Let $A=\Pp \cap E_j(q_j, \theta_j)$ be the set of points covered by $E_j$ and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point from $A$.
-
-	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses.
-As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertex.
-Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \tilde{E}_j(q_j', \theta_j)| \ge 2$.
-
-\end{demonstracao}
-
-What \autoref{lema:mce_2b} is saying is that any optimal solution for MCER can be transformed into another optimal solution where every ellipse covers the same set of points and those which cover more than one point has two points on their border.
-Also, this equivalent optimal solution can be always achieved by just translating the ellipses.
-An example is shown on \autoref{fig:ellipse-2-points} for one ellipse.
-
-A lot of the ideas developed in this chapter are based on fixing two points on the border of an ellipse, which is why \autoref{def:feasible_angle} introduces a new notation for angles that an ellipse rotated by it can be translated into a center, such that it contains two fixed points.
-
-\begin{figure}[H]
-	\centering
-	\caption{An optimal solution before and after applying \autoref{lema:mce_2b}.}
-	\includegraphics{tex/figures/scripts/ellipse-2-points}
-	\fautor
-	\label{fig:ellipse-2-points}
-\end{figure}
-
-\begin{definicao}\label{def:feasible_angle}
-	Let $E$ be an ellipse and $u, v \in \R^2$. An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
-\end{definicao}
-
-On \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
-On one of them, an ellipse is rotated by $\pi/4$ and it is located such that it contains the two fixed points on its border.
-That means $\pi/4$ is a $(E, u, v)$-feasible angle.
-On the other example, the ellipse is rotated by $\pi/2$ and there is not a center where the ellipse can be placed so it contains the two fixed points--they are too far apart.
-This makes $\pi/2$ a not $(E, u, v)$-feasible angle.
-
-\begin{figure}
-	\centering
-	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
-	\includegraphics{tex/figures/scripts/feasible-angle}
-	\fautor
-	\label{fig:feasible-angle}
-\end{figure}
-
-\begin{lema}\label{lema:3pnts}
-	Let $(\Pp, \E)$ be an instance of MCER, in an optimal solution, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|>2$, at least one of the two cases is true:
-
-	\begin{enumerate}
-		\item There is $q', \theta'$, and $\{u, v, w\} \subset \Pp \cap E_j(q_j, \theta_j)$, such that $\{u, v, w\} \subset \tilde{E}(q', \theta')$.
-
-		\item Let $A=\Pp \cap E_j(q_j, \theta_j)$, and $u, v \in A$ such that there exists $\hat{q}_j$ such that $\{u, v\} \subset \tilde{E_j}(\hat{q}_j, \theta_j)$ and $A \subset E_j(\hat{q}_j, \theta_j)$.
-Then for any $(E_j, u, v)$-feasible angle $\theta \in [0, 2\pi]$, there exists $\bar{q}_j$ such that $\{u, v\} \subset \tilde{E_j}(\bar{q}_j, \theta)$ and $A \subset E_j(\bar{q}_j, \theta)$.
-	\end{enumerate}
-\end{lema}
-
-The first case of \autoref{lema:3pnts} is saying that there is another optimal solution which has $E_j$ covering the same set of points, but with three points on its border.
-
-The second case of \autoref{lema:3pnts} says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$, there is a center that maintains the covered set the same.
-
-On \autoref{fig:lema-3-points} both cases of \autoref{lema:3pnts} are shown.
-There, it can be seen that for the second case, it does not matter which feasible angle by which the ellipse is rotated, the third point will always be inside the coverage area.
-Also, an example of the first case is shown where there are three points lie exactly on the border of the ellipse.
-
-\begin{figure}
-	\centering
-	\caption{An example of \autoref{lema:3pnts}.}
-	\includegraphics{tex/figures/scripts/lema-3-points}
-	\fautor
-	\label{fig:lema-3-points}
-\end{figure}
-
-The idea to prove \autoref{lema:3pnts} is that after fixing $u, v$ on the border of $E_j$, which is possible by \autoref{lema:mce_2b}, the movement of rotation and translation while keeping $u, v$ on the border is continuous.
-Because of that, the negation of case two implies case one and vice versa.
-
-If we define an equivalence relation between optimal solutions as: $S_1$ is equivalent to $S_2$ if they both cover the same set of points, we can use \autoref{lema:3pnts} and \autoref{lema:mce_2b} to identify the equivalence classes.
-Let $S$ be any optimal solution, in $[S]$ (its equivalence class) there is another solution where any ellipse $E_j \in \E$ falls in at least one of the cases below:
-\begin{itemize}
-	\item $E_j$ covers only one point.
-	\item $E_j$ covers more than one point with $u$ and $v$ being on the border of $E_j$.
-Note that there could be infinitely many of solutions like that, however, \autoref{lema:3pnts} guarantees that any $(E_j, u, v)$-feasible angle yields an equivalent optimal solution.
-	\item $E_j$ covers more than two points with three of them on its border.
-\end{itemize}
-
-The following two sections will treat the second and third cases (the first case is trivial).
-Going through every possibility of an ellipse falling in any of the three cases guarantees that an optimal solution is found.
-
-\section{Ellipse by two points}
-
-Let $E$ be an ellipse with shape parameters $(a, b)\in \R^2_{>0}$ and $u, v\in \R^2$, one wants to find a $(E, u, v)$-feasible angle $\theta\in[0,\pi]$ and every center $q\in\R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
-
-For a fixed angle, finding every center such that two points are on the border of the ellipse is done on \autoref{chapter:ellipses_intersection}, from there we know that there could be at most $2$ of such centers.
-The only thing left to be done is finding a feasible angle.
-It turns out that the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$ will be a feasible angle if, and only if the set of feasible angles is not empty.
-This can be seen geometrically as other angles achieve a lesser maximum distance between the two points on the border.
-
-\section{Ellipse by three points}
-
-The problem of finding every center and angle of rotation of an ellipse which makes it have three points on its border is presented in this section.
-We refer to it as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
-The objective is to find every pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
-
-Firstly, it is going to be shown that the number of solutions of E3PNT is limited by a constant, this is a fundamental result which allows an algorithm for MCER to be developed.
-Secondly, a method to find every solution of E3PNT is described.
-
-\subsection{The number of solutions is limited by a constant}
+\section{The number of solutions is limited by a constant}
 
@@
 
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 
-Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, \pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b}.
-Note that, the problem now becomes the one of finding every $\theta \in [0, \pi)$, such that $\xi(\theta)=0$.
+Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, \pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b} in such a way that its zeros determine solutions to the E3PNT's instance.
+Two questions about $\xi(\theta)$ that arise are: is its set of roots finite?
+And, can they be found analytically?
 
@@
 \begin{align}\label{eq:dd}
-	\norm{\varphi(v, \theta)}^2 = (v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta)^2 + (v_x\cos\theta - v_y\sin\theta)^2\\
+	\norm{\varphi(v, \theta)}^2 = (v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta)^2 + (v_y\cos\theta - v_x\sin\theta)^2\\
 	\label{eq:dd2} A(\theta)^2=\dfrac{1}{4}\det\left(
 	\begin{array}{cc}
-		v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta&v_x\cos\theta - v_y\sin\theta\\
-		w_x\frac{b}{a}\cos\theta + w_y\frac{b}{a}\sin\theta&w_x\cos\theta - w_y\sin\theta
+		v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta&v_y\cos\theta - v_x\sin\theta\\
+		w_x\frac{b}{a}\cos\theta + w_y\frac{b}{a}\sin\theta&w_y\cos\theta - w_x\sin\theta
 	\end{array}\right)^2
@@
 
-\subsection{A method for E3PNT}
+\section{A method for E3PNT}
 
@@
 \dfrac{\left((w-q_\theta)^T\left(\begin{array}{c}
-	\sin{\theta}\\
-	-\cos{\theta}
+	-\sin{\theta}\\
+	\cos{\theta}
 	\end{array}\right)\right)^2}{b^2}

### 2019-09-27 defesa/tex/chapter/ellipses_n.tex
wip

--- 2019-08-23 defesa/tex/chapter/ellipses_n.tex
@@
 \section{Ellipse by three points}
-
-In this section the problem of finding every location (center, angle of rotation), that makes an ellipse have three points on its border is presented, we will refer to this problem as \sigla{E3PNT}{Ellipse by Three points}.
-Firstly, it is going to be shown that the number of solutions of this problem is limited, this is a fundamental result which allows an algorithm for MCER to be developed.
-Secondly, a method to find every solution of E3PNT is described.
-
-\subsection{The number of solutions is limited by a constant}
-
-To prove that the number of solutions is limited by a constant, the problem is going to be modeled as finding the roots of an univariate polynomial of degree $12$.
-Let $u, v, w \in \R^2$ and $E$ be an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
-The problem is to find every pair $(q, \theta)$, with $q \in \R^2$ and $\theta \in [0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
-
-To make it simpler, let us translate the system, so the point $u$ is at $(0,0)$.
-Then, we assume that the ellipse is actually axis-parallel and the points are the ones rotating.
-When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$.
-This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle.
-This process can be parametrized by the angle of rotation of the points, as described by \autoref{eq:trpnts}, and because of the invertibility of linear transformations solutions for E3PNT can be obtained by reversing the transformations.
-
-\begin{figure}[H]
-	\centering
-	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics{tex/figures/scripts/circumscribed-circle}
-	\fautor
-	\label{fig:circumscribed-circle}
-\end{figure}
-\begin{equation}\label{eq:trpnts}
-\varphi(p, \theta)=\left[\begin{array}{cc}
-\frac{b}{a}&0\\
-0&1
-\end{array}\right]
-\left[\begin{array}{cc}
-\cos{\theta}&\sin{\theta}\\
--\sin{\theta}&\cos{\theta}
-\end{array}\right]\left[\begin{array}{c}
-p_x\\
-p_y
-\end{array}\right].
-\end{equation}
-
-Then, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\varphi(u, \theta), \varphi(v, \theta)$ and $\varphi(w, \theta)$, such that the circle has radius $b$.
-As, for three non-colinear fixed points, there is always an unique circumscribed circle for the triangle formed by those three points, the only variable to be determined ends up being the angle of rotation $\theta$.
-
-Let $d_u(\theta), d_v(\theta), d_w(\theta)$ be the length of each of the sides of the triangle formed by the points $\varphi(u, \theta), \varphi(v, \theta)$ and $\varphi(w, \theta)$; and $A(\theta)$ be its area--note that the transformation does not preserve distance or area.
-Then, the radius $R$ of the circumscribed circle is given by \autoref{eq:circumscribed_circle} \cite[p.~189]{johnson1960}.
-
-\begin{equation}\label{eq:circumscribed_circle}
-R = \dfrac{d_u(\theta)d_v(\theta)d_w(\theta)}{4A(\theta)}.
-\end{equation}
-
-Instead of working with trigonometric functions, the following identities given by \autoref{eq:trigId} are used, so a polynomial can be obtained.
-
-\begin{equation}\label{eq:trigId}
-\begin{array}{c}
-\cos{\theta} = \dfrac{t^2-1}{t^2+1}\\
-\sin{\theta} = \dfrac{2t}{t^2+1}.
-\end{array}
-\end{equation}
-
-Looking at $\varphi(u, \theta)$, after replacing the trigonometric functions with \autoref{eq:trigId}, it then becomes a quotient of polynomials.
-Let $\Delta=t^2+1$, then $\varphi(u, \theta)$ is a polynomial of degree $2$ divided by $\Delta$.
-The area $A(\theta)$ can be calculated by taking the cross product of the vectors induced by $\varphi(v, \theta)$ and $\varphi(w, \theta)$ which ends up being a polynomial of degree $4$ divided by $\Delta^2$.
-Finally, let $\gamma_d(t)$ be a polynomial of degree $d\in\mathbb{N}$, then we get the following expressions for the length of the triangle and its area,
-\begin{align*}
-d_u(\theta)=||\varphi(v, \theta)-\varphi(u, \theta)|| = \sqrt{\dfrac{\gamma_4(t)}{\Delta^2}}\\
-A(\theta)=\dfrac{1}{2}|\varphi(v, \theta) \times \varphi(w, \theta)|=\frac{\gamma_4(t)}{\Delta^2}
-\end{align*}
-imposing \autoref{eq:circumscribed_circle} so the radius of the circumscribed circle is equal to $b$, we get the following equation,
-
-\begin{align*}
-\left(\sqrt{\dfrac{\gamma_4(t)}{\Delta^2}}\right)^3 - \dfrac{b\gamma_4(t)}{\Delta^2} = 0\\
-\dfrac{\gamma_{12}(t)}{\Delta^6} - \dfrac{b\gamma_8(t)}{\Delta^4} = 0,
-\end{align*}
-which after some manipulation, becomes an univariate polynomial of degree $12$ which can have up to $12$ different real roots.
-Because ellipses are symmetrical with respect to their major-axis, and any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$, the number of different solutions is cut in half.
-Therefore, the number of angles of rotation and centers that an ellipse of fixed shape can be placed, so it has three fixed points on its border is limited to $6$.
-
-Because there is no closed formula to find roots of polynomials of degree $12$ \cite{skopenkov2015}, and root-finding iterative methods, such as Newton's method, generally are not convergent for polynomials of degree $4$ or more \cite{mc1}, this approach is only useful to show the limitedness of the set of solutions.
-
-\subsection{A method for E3PNT}
-
-In this section we present a method for E3PNT and we try to justify it being correct, however, a proof is left as future work.

### 2019-10-01 defesa/tex/chapter/e3p.tex
wip

@@
 The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section.
-Even though its simple statement--it is short and uses only basic mathematics concepts--we were not able to find any work that dealt with this problem, or even related ones, either as its main goal or as a sub-problem.
+Even though its simple statement--it is short and uses only basic mathematical concepts--we were not able to find any work on it, or even on related problems.
 As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way.
-We try to give a review of some of those, and also make a case for the method we propose in terms of velocity of convergence and quality of the solutions.
+We try to give a review of some of those, and also make a case for the method we propose in terms of velocity of convergence and quality of the solutions that it finds.
 
@@
 A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
-In other words, the objective is to develop a method to find every solution of E3PNT.
+In other words, the goal is to develop a method to find every solution of E3PNT.
 
@@
 
-To prove that the number of solutions is limited by a constant, the problem is going to be modeled as finding the roots of an univariate polynomial of degree $12$.
+The basis of the method developed on \autoref{chapter:ellipses_n} is that the number of solutions of E3PNT is limited and they can be found efficiently. At first we introduce a way to model
 
@@
 According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$.
-The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree, denoted by $\max_{i\in \{1, \dots, M\}}$, zero.
+The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree, denoted by $\max_{i\in \{1, \dots, M\}} \{j_i, k_i\}$.
 

### 2019-10-04 defesa/tex/chapter/e3p.tex
wip

@@
 
-\section{The number of solutions is limited by a constant}
-
-The basis of the method developed on \autoref{chapter:ellipses_n} is that the number of solutions of E3PNT is limited and they can be found efficiently. At first we introduce a way to model
+\section{Transforming the problem}
 
@@
 
+\subsection{The number of solutions is limited}
+
+The method developed on \autoref{chapter:ellipses_n} iterates over every solution of E3PNT for every triplet of points, this is only possible if the size of this set of solutions is limited.
+Also, if this was not true, it would be very difficult to describe a method to get every solution which could be infinite.
+
 According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$.
-The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree, denoted by $\max_{i\in \{1, \dots, M\}} \{j_i, k_i\}$.
+The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree.
 
@@
 
-A possible approach to find all the roots of a high-degree polynomial is to find all the eigenvalues of its companion matrix\cite{horn}.
-There are methods that do that with the observation that roots not close to the origin are susceptible to large errors and some times can not be found.
-This was experienced in some instances where the method could not find any roots which were priorly known.
-Therefore, Because there is no closed formula to find roots of polynomials of degree $12$ \cite{skopenkov2015}, and root-finding iterative methods, such as Newton's method, generally are not convergent for polynomials of degree $4$ or more \cite{mc1}, this approach is only useful to show the limitedness of the set of solutions.
-In the next section we present a method to approximate the roots of \autoref{eq:circumscribed_circle_b}.
+\section{Attempts on solving E3PNT}
+
+\subsection{Converting $\xi(\theta)$ into a polynomial}
+
+Using the identity $x = \tan{\frac{\theta}{2}}$ it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate polynomial of degree $12$.
+The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
+A possible approach, as described by \citeonline[p.~191]{horn}, is to find all the eigenvalues of a matrix related to the polynomial called the companion matrix.
+There are methods that do that fairly efficiently with the observation that roots which are not close to the origin are susceptible to large errors and some times can not be found, this indeed happened in practice, as for some instances the method did not find roots which were priorly known.
+Another possibility would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method cannot converge.
+Nevertheless, a result published by \citeonline{mc1} says that iterative methods generally are not convergent for polynomials of degree $4$ or more, and also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.
+
+\subsection{Using the conic general equation}
+
+The idea of this approach was to use the six-parameter conic equation to represent an ellipse. This equation is given by \autoref{eq:gen_ellipse}.
+
+\begin{equation}\label{eq:gen_ellipse}
+Ax^2+Bxy+Cy^2+Dy+Ex+F=0
+\end{equation}
+
+Setting the first point to be the origin, we get $F=0$, using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$.
+As any multiple of \autoref{eq:gen_ellipse} represents the same conic, we can set $B$ to be equal $1$.
+Then, we end up with two variables, $A$ and $C$, and still need to impose that the final equation represents an ellipse and its major-axis and minor-axis have the predefined value.
+Let $\Delta=4AC-B^2=4AC-1$, \autoref{eq:gen_ellipse_a} and \autoref{eq:gen_ellipse_b} for both major-axis and minor-axis respectively, assuming $F=0$.
+
+\begin{align}\label{eq:gen_ellipse_a}
+a^2 = \dfrac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C - \sqrt{1 + (A-C)^2}}\\
+\label{eq:gen_ellipse_b}b^2 = \frac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C + \sqrt{1 + (A-C)^2}}
+\end{align}
+
+These two equations define two curves in $\R^2$ with $A$ and $C$ being the chosen variables.
+The solutions lie in the set of intersection of these curves.
+Finding this set was judged to be non-trivial and probably could be approximated numerically, however, we decided not to further pursue this approach.
+
+Another idea which has been explored was working with the ratio $\frac{a^2}{b^2}$ which becomes an expression that allows $A$ to be written as a function of $C$.
+This function appeared, at first we thought, to be monotonic, we tried to develop a method based on that, however, cases where the function does not behave as nicely were found.
+It is likely that developing a method to approximate solutions working with this function is possible, but we decided not to continue on this track.
 
@@
 
-In this section we present a method for E3PNT and we try to make a case of it being correct, however, a proof is left as future work.
+One of the most useful techniques when dealing with complicated functions is approximation.
+They appear in various methods whenever a derivative or integral needs to be calculated or for example, in our case, when the roots of a function need to be determined.
+In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}.
+For this problem, the approximation set of functions is going to be the set of $N$-degree Chebyshev polynomials.
 
-The idea of the method is to let two of the three points be fixed on the border of the ellipse and vary the angle to find it when the third point hits the border of the ellipse.
+\subsection{Chebyshev interpolation}
 
-Let $u$ and $v$ be the pair out of the three points that are most distant from each other, also let $\theta_u \in [0, \pi)$ be the greatest $(E, u, v)$-feasible angle.
-Given an angle $\theta \in [0, \theta_u]$, let $q_\theta\in\R^2$ be a center of $E$, such that $\{u, v\} \subset \tilde{E}(q_\theta, \theta)$.
-Note that in general, there are two such centers, they could be told apart by their $y$-coordinate, and the method needs to be executed for both of them separately.
-Then, a function $\rho : [0, \theta_u] \mapsto \R$ is defined to be the elliptical norm of the point $w$ with respect to $E(q_\theta, \theta)$.
+Chebyshev polynomials are widely used in Numerical Analysis
 
-\begin{equation}\label{eq:rho}
-\rho(\theta) = \dfrac{\left((w-q_\theta)^T\left(\begin{array}{c}
-	\cos{\theta}\\
-	\sin{\theta}
-	\end{array}\right)\right)^2}{a^2}+
-\dfrac{\left((w-q_\theta)^T\left(\begin{array}{c}
-	-\sin{\theta}\\
-	\cos{\theta}
-	\end{array}\right)\right)^2}{b^2}
+There are two kinds of very known Chebyshev polynomials. Here, only the first kind will be used, for a more through introduction see \citeonline{chebbook}.
+
+Also known as Chebyshev polynomial of the first kind, $T_n : [-1, 1] \mapsto [-1, 1]$ is defined as follows:
+
+\begin{equation}
+T_n(x) = \cos({n\arccos x})
 \end{equation}
 
-The angles such that \autoref{eq:rho} is equal to $1$ are the ones that are part of the solution and achieve three points on the border of the ellipse.
-From now on, a method is presented that tries to find those points in a efficient way.
-We conjecture that \autoref{eq:rho} is unimodal by parts, and we present a method that takes advantage of that.
+Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is very well-behaved (it is continuous with infinite continuous derivatives) and it is defined over a closed interval.
+These two properties provide very nice guarantees about the approximation function that is going to be constructed.

### 2019-10-06 defesa/tex/chapter/e3p.tex
wip

@@
 In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}.
-For this problem, the approximation set of functions is going to be the set of $N$-degree Chebyshev polynomials.
+For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered.
+The approximation set of functions is going to be the set of $N$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $N$ by $N$ matrix.
 
@@
 
-Chebyshev polynomials are widely used in Numerical Analysis
+Chebyshev polynomials are widely used in Numerical Analysis in areas like numerical integration, polynomial approximation, and ordinary and partial differential equations.
+They are also very useful in practice and are present in extension libraries in Python and MATLAB.
 
-There are two kinds of very known Chebyshev polynomials. Here, only the first kind will be used, for a more through introduction see \citeonline{chebbook}.
+Because of the scope of this work, only a brief introduction of Chebyshev polynomials of the first kind and its usage in polynomial interpolation is given.
+For a more thorough work on the subject, please check the book by \citeonline{chebbook}.
 
-Also known as Chebyshev polynomial of the first kind, $T_n : [-1, 1] \mapsto [-1, 1]$ is defined as follows:
+We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind:
 
@@
 
-Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is very well-behaved (it is continuous with infinite continuous derivatives) and it is defined over a closed interval.
-These two properties provide very nice guarantees about the approximation function that is going to be constructed.
+Although, its definition can be extended, so its domain is the whole real line, It also respects the following recurrence relation:
+
+\begin{equation}
+\begin{array}{ll}
+T_0(x) = 1& \\
+T_1(x) = x& \\
+T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x)&n = 2, 3, \dots
+\end{array}
+\end{equation}
+
+Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is very well-behaved (it is continuous with infinite continuous derivatives).
+This property provides very nice guarantees about the approximation function that is going to be constructed.
+
+Polynomial interpolation is a form of approximating a function by a polynomial of degree $N$ that passes through $N+1$ points.
+In fact, this polynomial is unique and it is determined by Lagrange's formula:
+
+\begin{equation}
+\sum_{j=0}^{N} \dfrac{\prod_{k \neq j}^{N+1} (x-x_k)}{\prod_{k \neq j}^{N+1} (x_j-x_k)}.
+\end{equation}

### 2019-10-08 defesa/tex/chapter/e3p.tex
wip

@@
 For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered.
-The approximation set of functions is going to be the set of $N$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $N$ by $N$ matrix.
+The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n$ by $n$ matrix.
 
@@
 
-We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind:
+We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind, and it is defined as follows:
 
@@
 
-Although, its definition can be extended, so its domain is the whole real line, It also respects the following recurrence relation:
+It is important to mention that this definition can be extended to the whole real line. Using some trigonometric identities, $T_n$ can also be expressed as a recurrence relation:
 
 \begin{equation}
-\begin{array}{ll}
-T_0(x) = 1& \\
-T_1(x) = x& \\
-T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x)&n = 2, 3, \dots
-\end{array}
+T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x).
 \end{equation}
+
+An important property worth bringing up is that Chebyshev polynomials are orthogonal and form a basis for the polynomial space.
+This implies that any $p_n$ of degree up to $n$ can be expressed as a truncated Chebyshev series:
+
+\begin{equation}\label{eq:chebseries}
+p_n(x) = \sum_{j=0}^{n} a_j T_j(x).
+\end{equation}
+
+One of the greatest qualities of Chebyshev polynomials is its numerical stability.
+\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{$p_n$ is in the power form or the monomial form if it can be written as $p_n=\sum_{j=0}^{n}a_jx^j$} has a condition number that grows exponentially with $n$.
+On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries}, has a linear condition number bounded by $\sqrt{2}n$.
 
@@
 
-Polynomial interpolation is a form of approximating a function by a polynomial of degree $N$ that passes through $N+1$ points.
+Polynomial interpolation is a form of approximating a function by a polynomial of degree $n$ that passes through $n+1$ chosen points.
 In fact, this polynomial is unique and it is determined by Lagrange's formula:
 
+\begin{equation}\label{eq:lagrange}
+f_n(x) = \sum_{j=0}^{n} f(x_j)\dfrac{\prod_{k \neq j}^{n+1} (x-x_k)}{\prod_{k \neq j}^{n+1} (x_j-x_k)},
+\end{equation} 
+with $f$ being the function to be approximated and $f_n$ the unique $n$ degree polynomial that passes through $\{(x_j, f(x_j)): j=0, 1, \dots n\}$.
+Because of the uniqueness of interpolant polynomials, there is a direct link between the quality of an approximation and the points chosen to interpolate.
+As a matter of fact, depending on the points one chooses, even increasing the degree of the interpolation makes the approximation worsen.
+This is known as Runge's phenomenon and an example can be seen in \citeonline[p.~37]{powell} where uniformly spaced points are chosen to interpolate the function $f(x) = (1+x^2)^{-1}$ on the interval $[-5, 5]$.
+That is where Chebyshev interpolation comes in, instead of $n+1$ arbitrary points, the interpolation is done on the $n+1$ roots of $T_n$, which are also known as Chebyshev Nodes:
+
 \begin{equation}
-\sum_{j=0}^{N} \dfrac{\prod_{k \neq j}^{N+1} (x-x_k)}{\prod_{k \neq j}^{N+1} (x_j-x_k)}.
+x_j = \cos{\left(\pi\dfrac{2n-2j+1}{2n}\right)},
 \end{equation}
+for $j=1, \dots, n$.
+If the domain of the function to be interpolated is in another range other than $[-1, 1]$, let us say $[a, b]$, then a transformation can be done to map it to the Chebyshev Nodes' domain:
+
+\begin{equation}
+\hat{x_j} = \frac{a+b}{2} + \frac{b-a}{2}x_j.
+\end{equation}
+
+Then, the Chebyshev interpolation of a function $f: [a, b] \mapsto \R$ can be determined using Lagrange's formula and the points $\hat{x}_1, \dots, \hat{x}_n$. 
+As it was mentioned, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called companion matrix.
+For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
+
+An alternative method can be found in \citeonline{boyd:2013}.
+It turns out that the Chebyshev interpolation can be calculated directly as a truncated Chebyshev series in $\bigO(n^2)$.
+Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial.
+Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials which have great numerical stability.

### 2019-10-08 defesa/tex/chapter/e3p.tex
wip

@@
 
-Using the identity $x = \tan{\frac{\theta}{2}}$ it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate polynomial of degree $12$.
+Using the identity $x = \tan{\frac{\theta}{2}}$, it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate polynomial of degree $12$.
 The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
 A possible approach, as described by \citeonline[p.~191]{horn}, is to find all the eigenvalues of a matrix related to the polynomial called the companion matrix.
-There are methods that do that fairly efficiently with the observation that roots which are not close to the origin are susceptible to large errors and some times can not be found, this indeed happened in practice, as for some instances the method did not find roots which were priorly known.
+In general, finding all the eigenvalues of a matrix is not easy, however, companion matrices have a special form which allows their eigenvalues to be found through a QR decomposition, a $\bigO(n^2)$ algorithm can be found in \citeonline{bini:2007}.
+ The only problem is that for degree $12$ polynomials, roots which are not close to the origin are susceptible to large errors and some times can not be found.
+This indeed happened in practice, as for some instances the method did not find roots which were priorly known.
 Another possibility would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method cannot converge.
-Nevertheless, a result published by \citeonline{mc1} says that iterative methods generally are not convergent for polynomials of degree $4$ or more, and also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.
+A result published by \citeonline{mc1}, however, says that iterative methods generally are not convergent for polynomials of degree $4$ or more, and also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.
 
@@
 One of the greatest qualities of Chebyshev polynomials is its numerical stability.
-\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{$p_n$ is in the power form or the monomial form if it can be written as $p_n=\sum_{j=0}^{n}a_jx^j$} has a condition number that grows exponentially with $n$.
+\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{A polynomial is in the power form or the monomial form if it can be written as $\sum_{j=0}^{n}a_jx^j$} has a condition number that grows exponentially with $n$.
 On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries}, has a linear condition number bounded by $\sqrt{2}n$.
@@
 Then, the Chebyshev interpolation of a function $f: [a, b] \mapsto \R$ can be determined using Lagrange's formula and the points $\hat{x}_1, \dots, \hat{x}_n$. 
-As it was mentioned, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called companion matrix.
+As it was mentioned, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called Frobenius companion matrix.
 For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
@@
 It turns out that the Chebyshev interpolation can be calculated directly as a truncated Chebyshev series in $\bigO(n^2)$.
-Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial.
+Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial, the author refers to this matrix as the Chebyshev-Frobenius companion matrix.
 Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials which have great numerical stability.
+Also, Chebyshev-Frobenius matrices have the same property as companion matrices which allows their eigenvalues to be found by a QR decomposition.
+Summing the two steps, a $\bigO(n^2)$ algorithm can be achieved.

### 2019-10-12 defesa/tex/chapter/e3p.tex
wip

@@
 
+In this section we give a brief review of some of the approaches we tried on developing a method for E3PNT.
+
 \subsection{Converting $\xi(\theta)$ into a polynomial}
@@
 The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
-A possible approach, as described by \citeonline[p.~191]{horn}, is to find all the eigenvalues of a matrix related to the polynomial called the companion matrix.
-In general, finding all the eigenvalues of a matrix is not easy, however, companion matrices have a special form which allows their eigenvalues to be found through a QR decomposition, a $\bigO(n^2)$ algorithm can be found in \citeonline{bini:2007}.
- The only problem is that for degree $12$ polynomials, roots which are not close to the origin are susceptible to large errors and some times can not be found.
-This indeed happened in practice, as for some instances the method did not find roots which were priorly known.
-Another possibility would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method cannot converge.
-A result published by \citeonline{mc1}, however, says that iterative methods generally are not convergent for polynomials of degree $4$ or more, and also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.
+Therefore, pursuing a numerical method would be a good choice for this problem.
+
+Perhaps the first idea one would have for this problem would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method does not converge.
+A result published by \citeonline{mc1}, however, says that iterative methods generally are not convergent for polynomials of degree $4$ or more.
+Also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.
+
+This next approach is very popular in practice as it is present in external libraries like NumPy for Python \cite{python}.
+In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial.
+At first it seems that we are just trading for the same problem as, in general, to find the eigenvalues of a matrix, one needs to determine the roots of that matrix's characteristic polynomial.
+Nevertheless, it turns out that companion matrices are very convenient when it comes to finding eigenvalues.
+They are what is called Hessenberg matrices, and QR algorithms can be used to find their eigenvalues (a $\bigO(n^2)$ algorithm that does that can be found in \citeonline{bini:2007}).
+
+This method seemed to work fine, but for some instances it did not find roots which were priorly known.
+This happened probably because of the transformation that was used to convert $\xi$ into a polynomial.
+It can be very numerically unstable as the tangent function grows to fast for angles that are greater than $\frac{\pi}{4}$.
+Depending on the instance, there could be roots very close to $0$ and others that are too far from it.
 
@@
 
-Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is very well-behaved (it is continuous with infinite continuous derivatives).
-This property provides very nice guarantees about the approximation function that is going to be constructed.
-
 Polynomial interpolation is a form of approximating a function by a polynomial of degree $n$ that passes through $n+1$ chosen points.
@@
 
-An alternative method can be found in \citeonline{boyd:2013}.
-It turns out that the Chebyshev interpolation can be calculated directly as a truncated Chebyshev series in $\bigO(n^2)$.
-Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial, the author refers to this matrix as the Chebyshev-Frobenius companion matrix.
-Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials which have great numerical stability.
+An alternative method can be found in \citeonline{boyd:2013} where the Chebyshev interpolation is calculated directly as a truncated Chebyshev series, as in \autoref{eq:chebseries}, in $\bigO(n^2)$.
+Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial.
+\citeonline{boyd:2013} refers to this matrix as the Chebyshev-Frobenius companion matrix.
+
+Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials, which have great numerical stability.
 Also, Chebyshev-Frobenius matrices have the same property as companion matrices which allows their eigenvalues to be found by a QR decomposition.
 Summing the two steps, a $\bigO(n^2)$ algorithm can be achieved.
+
+The last question that needs to be addressed is how close the roots of the Chebyshev interpolant $f_n$ are to the roots of $\xi$?
+
+Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is a very well-behaved function: it is analytic and  has infinitely many continuous and integrable derivatives.
+This satisfy all the requirements of the result in \citeonline[p.~28]{gottlieb} which says that if a function has $m$ continuous and integrable derivatives on a closed interval, then its absolute difference between the Chebyshev truncate series is $\bigO(n^{-m})$.
+Also, in \citeonline{battles:2004} a theorem is presented stating that if a function is analytic on a neighborhood of $[-1, 1]$, then the convergence is $\bigO(C^n)$, for some $C<1$.
+
+\section{Numerical Experiments}
+
+In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved.
+Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we measure the error by using the infinite norm:
+
+\begin{equation}
+r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|
+\end{equation}
+
+Also we adopt two suggestions from \cite{boyd:2013}.
+The first is to divide the interval into $K$ subintervals to achieve a precision without having to increase the degree of the interpolant too much.
+The second is to use a couple of Newton's iterations to refine the roots found.
+
+Let $\theta^*$ be a root of $f_n$, then we measure the error associated with that root as $|\xi(\theta^*)|$.
+For the numerical experiments, we considered every triplet of points from an instance with $25$ points.
+Then for some values of $K$ and $n$ we define the error as the maximum error for every root that were found.
+
+\begin{figure}
+	\centering
+	\caption{The interpolation error measured on roots that were found.}
+	\includegraphics{tex/figures/interpolant_error}
+	\fautor
+	\label{fig:interpolant_error}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\caption{The interpolation error measured on roots that were found after three Newton's iterations.}
+	\includegraphics{tex/figures/interpolant_error_after_newton}
+	\fautor
+	\label{fig:interpolant_error_after_newton}
+\end{figure}

### 2019-10-16 ONPCE/slides.tex
wip

\documentclass{beamer}

\usepackage{amsthm, amsfonts, amsmath, amssymb} % Pacote para a definicao dos ambientes matematicos
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[mathscr]{eucal}
\usepackage{tikz}
\usetikzlibrary{quotes, angles, intersections}
\newcommand{\R}{\mathbb{R}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}

\author{Danilo Tedeschi\\Dra. Marina Andretta}
\title{Fixed-Shape Ellipse by Three Points}
\institute{Universidade de São Paulo}
\date{25 de Outubro de 2019}

\begin{document}

	\begin{frame}[t,plain]
		\titlepage
	\end{frame}

	\begin{frame}{Introduction}
		The shape of an ellipse is given by its major-axis and minor-axis, $(a, b) \in \mathbb{R}^2$, with $a > b > 0$.

		\begin{figure}[H]
			\centering

			%\caption{The ellipse as a parametric curve.}
			\input{ellipse_figure.tex}
			\label{fig:ellipse_params}
			\caption{An ellipse with shape parameters $a$ and $b$.}
		\end{figure}

	\end{frame}

\begin{frame}{Introduction}
	Here, the shape will be fixed and the center and angle of rotation are free.

	\begin{figure}
	\centering

	%\caption{The ellipse as a parametric curve.}
	\includegraphics[scale=.5]{3ellipses.pdf}
	\label{fig:ell}
	\caption{A fix-shape ellipse at different centers and with different angles of rotation.}
	\end{figure}
\end{frame}

\begin{frame}{Introduction}{Problem definition}
Given three points $u, v, w \in \R^2$, and the shape $(a,b) \in \R^2$ of an ellipse:
	\begin{figure}
	\centering

	%\caption{The ellipse as a parametric curve.}
	\includegraphics[scale=.5]{e3psol1.pdf}
	\label{fig:e3psol1}
	\caption{An instance of the problem.}
\end{figure}
\end{frame}

\begin{frame}{Introduction}{Problem definition}
	A solution is given by the ellipse's center $q \in \R^2$ and the angle of rotation $\theta \in [0, \pi)$, such that $u, v, w$ lie on its border. \textbf{We want to find every solution!}
	\begin{figure}
		\centering

		%\caption{The ellipse as a parametric curve.}
		\includegraphics[scale=.5]{e3psol2.pdf}
		\label{fig:e3psol2}
		\caption{Every solution for that instance.}
	\end{figure}
\end{frame}

\begin{frame}{Introduction}
	The equation of an ellipse is given by:

	\begin{equation*}
	\frac{\left(\left[\begin{array}{c}
	x-q_x\\
	y-q_y
		\end{array}\right]^T
		\left[\begin{array}{c}
		\cos\theta\\
		\sin\theta
		\end{array}\right]
		\right)^2}{a^2}+\frac{\left(\left[\begin{array}{c}
		x-q_x\\
		q_y-y
		\end{array}\right]^T
		\left[\begin{array}{c}
		\sin\theta\\
		\cos\theta
		\end{array}\right]
		\right)^2}{b^2} = 1.
	\end{equation*}

	\begin{itemize}
		\item Fixing the points $u, v, w$, we get $3$ equations and $3$ unknowns $(q_x, q_y, \theta)$.
		\item Finding every solution is difficult.
	\end{itemize}
\end{frame}

\begin{frame}{Transforming the problem}
	Let's make the problem simpler by transforming it into a circle problem.

	Given any non-colinear points, there is an unique circumscribed circle. Also, we can turn an axis-parallel ellipse into a circle:
	\begin{figure}
		\centering

		%\caption{The ellipse as a parametric curve.}
		\includegraphics[scale=.5]{el1.pdf}
		\label{fig:el1}
		\caption{Turning an ellipse with shape $(a, b)$ into a circle of radius $b$.}
	\end{figure}

\end{frame}

\begin{frame}{Transforming the problem}

	Let's rotate the points instead of rotating the ellipse. A solution can be transformed into the original problem.

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics{circumscribed-circle}
		\caption{}
		\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}
	Transforming it into a circle problem.

	\begin{itemize}
		\item Translate the points so $u=(0, 0)$.
		\item The ellipse is fixed, the points rotate.
		\item Scale the $x$-axis by $\frac{b}{a}$.
	\end{itemize}

	After the transformation, the points are defined by $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$:

	\begin{equation*}\label{eq:trpnts}
	\varphi(p, \theta)=\left[\begin{array}{cc}
	\frac{b}{a}&0\\
	0&1
	\end{array}\right]
	\left[\begin{array}{cc}
	\cos{\theta}&\sin{\theta}\\
	-\sin{\theta}&\cos{\theta}
	\end{array}\right]\left[\begin{array}{c}
	p_x\\
	p_y
	\end{array}\right].
	\end{equation*}
\end{frame}

\begin{frame}{Transforming the problem}
	Find every $\theta \in [0, \pi)$, such that:

	\begin{itemize}
		\item The circumscribe circle determined by: $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ has radius $b$.

		\item As long as they are not colinear, there is an unique circumscribe circle by three points.

	\end{itemize}

\end{frame}

\begin{frame}{Fixed-shape ellipse by three points}
	There is a known formula for the radius of a circumscribed circle:

	\begin{equation*}
	R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)}
	\end{equation*}

	\begin{itemize}
		\item $R$ is the radius.
		\item $A(\theta)$ is the area of the triangle defined by the points $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
	\end{itemize}
	\vspace{\baselineskip}

\end{frame}

\begin{frame}{Fixed-shape ellipse by three points}
We define the function $\xi : [0, \pi) \mapsto \R$:

	\begin{equation*}
	\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2
	\end{equation*}

The roots of $\xi$ are solutions of our problem.
	\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.5]{036}

%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

\end{document}

### 2019-10-16 defesa/tex/chapter/e3p.tex
wip

@@
 In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved. 
-Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we measure the error by using the infinite norm:
+Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we define the interpolation error $r_n$ as:
 
 \begin{equation}
-r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|
+r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|.
 \end{equation}
+
+Then, we want to determine the smallest $n$, such that $r_n \le \epsilon$, for a predefined $\epsilon$.
+Unfortunately, calculating $r_n$ involves taking samples from both functions on the whole interval, which is not viable computationally.
+In \citeonline[p.~50]{boyd:2001} a rule-thumb for estimating the interpolation error is given.
+It is worth mentioning that this rule
+
+It uses a theorem that states that $r_n$ is limited by the sum of the coefficients of the Chebyshev series that were removed by the truncation. The rule-of-thumb for estimating $r_n$ is given by:
+
+\begin{equation}
+r_n \approx |a_n|.
+\end{equation}
+
+Note that
+
+Obtaining an expression for it is not trivial, and sampling the whole interval is not viable computationally.
+
+Therefore, an estimation of $r_n$ is used to measure how good is the approximation.
 

### 2019-10-17 ONPCE/slides.tex
wip

@@
 
-	Let's rotate the points instead of rotating the ellipse. A solution can be transformed into the original problem.
+	Let's rotate the points instead of rotating the ellipse. It is equivalent:
 
@@
 \begin{frame}{Transforming the problem}
-	Transforming it into a circle problem.
+	Formally, we can transform the problem by:
 
@@
 		\item Translate the points so $u=(0, 0)$.
-		\item The ellipse is fixed, the points rotate.
 		\item Scale the $x$-axis by $\frac{b}{a}$.
@@
 
-	After the transformation, the points are defined by $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$:
+	Then, we rotate the points. The rotated points are $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$:
 
@@
 	\end{equation*}
+
+	After that, we need to look at the circumscribed circle formed by $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
 \end{frame}
@@
 \begin{frame}{Transforming the problem}
-	Find every $\theta \in [0, \pi)$, such that:
+
+	\textbf{An angle is a solution if, and only if the circumscribed circle of the points  $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ has radius $b$.}
 
 	\begin{itemize}
-		\item The circumscribe circle determined by: $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ has radius $b$.
-
-		\item As long as they are not colinear, there is an unique circumscribe circle by three points.
+		\item This is a problem of one variable!
 
@@
 
+\begin{frame}{Fixed-shape ellipse by three points}
+	There is no clear pattern in $\xi$.
+\begin{figure}
+	\centering
+
+	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+	\includegraphics[scale=.5]{035}
+	\caption{Another example of $\xi$.}
+	%	\label{fig:circumscribed-circle}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Fixed-shape ellipse by three points}
+	An example with two roots.
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.5]{012}
+		\caption{Another example of $\xi$.}
+		%	\label{fig:circumscribed-circle}
+	\end{figure}
+\end{frame}
+
 \end{document}

### 2019-10-17 ONPCE/slides.tex
wip

@@
 \newcommand{\Pp}{\mathscr{P}}
+\newcommand{\bigO}{\mathscr{O}}
 \newcommand{\Cc}{\mathscr{C}}
@@
 		\label{fig:e3psol2}
-		\caption{Every solution for that instance.}
+		\caption{Every solution for the instance shown previously.}
 	\end{figure}
@@
 
-	Given any non-colinear points, there is an unique circumscribed circle. Also, we can turn an axis-parallel ellipse into a circle:
+	An ellipse with shape $(a, b)$ can be transformed into a circle of radius $b$ through scaling the $x$-axis by $\frac{b}{a}$:
 	\begin{figure}
@@
 
-	Let's rotate the points instead of rotating the ellipse. It is equivalent:
+	Let's rotate the points instead of rotating the ellipse:
 
@@
 		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics{circumscribed-circle}
-		\caption{}
-		\label{fig:circumscribed-circle}
+		\includegraphics[scale=.5]{sol1}
+		\caption{Three points at their initial location.}
+		\label{fig:sol1}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Transforming the problem}
+
+	Firstly, we rotate leaving one point fixed at $(0, 0)$:
+
+	\begin{figure}
+		\centering
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.5]{sol2}
+		\caption{After rotation.}
+		\label{fig:sol2}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Transforming the problem}
+
+	Then, we scale by $\frac{b}{a}$ and check the radius of the circle:
+
+	\begin{figure}
+		\centering
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.5]{sol3}
+		\caption{After scaling.}
+		\label{fig:sol33}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Transforming the problem}
+
+	If the radius is $b$, the angle is a solution:
+
+	\begin{figure}
+		\centering
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.5]{sol4}
+		\caption{One solution for this instance.}
+		\label{fig:sol4}
 	\end{figure}
@@
 		\item Translate the points so $u=(0, 0)$.
-		\item Scale the $x$-axis by $\frac{b}{a}$.
+		\item Rotate by $\theta$ and scale the $x$-axis by $\frac{b}{a}$.
+		\item Find the $\theta$'s which produce a circle with radius $b$.
 	\end{itemize}
 
-	Then, we rotate the points. The rotated points are $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$:
+	This transformation is expressed by:
 
@@
 	p_y
-	\end{array}\right].
+	\end{array}\right],
 	\end{equation*}
+	with $p=u, v, w$.
 
-	After that, we need to look at the circumscribed circle formed by $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-
-	\textbf{An angle is a solution if, and only if the circumscribed circle of the points  $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ has radius $b$.}
-
-	\begin{itemize}
-		\item This is a problem of one variable!
-
-	\end{itemize}
+	\textbf{This is an one variable problem on a closed interval!}
 
@@
 	\includegraphics[scale=.5]{036}
-
+	\caption{An example of $\xi$.}
 %	\label{fig:circumscribed-circle}
@@
 		\includegraphics[scale=.5]{012}
-		\caption{Another example of $\xi$.}
+		\caption{Yet another example of $\xi$.}
 		%	\label{fig:circumscribed-circle}
@@
 
+\begin{frame}{Chebyshev Interpolation}
+
+	\begin{block}{Chebyshev Polynomial}
+		$T_n: [-1, 1] \mapsto [-1, 1]$ is the $n$-degree Chebyshev polynomial:
+		\begin{equation*}
+		T_n(\cos t) = \cos(nt)
+		\end{equation*}
+	\end{block}
+	Also, it can be defined recursively:	
+	\begin{align*}
+	&T_0(x) = 1\\
+	&T_1(x) = x\\
+	&T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x)
+	\end{align*}
+
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}
+	Interpolation on the roots of $T_n$, also known as Chebyshev Nodes:
+
+	\begin{equation*}
+		x_k = \cos\left(\pi\frac{2k - 1}{2n}\right)
+	\end{equation*}
+
+	The interpolation of a function $f : [-1, 1] \mapsto \R$ can be written directly using Chebyshev polynomial as basis:
+
+	\begin{equation*}
+	f(x) \approx \sum_{k=0}^{n} a_k T_k(x)
+	\end{equation*}
+
+	\begin{itemize}
+		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}
+		Why is it good?
+
+	\begin{itemize}
+		\item Numerically stable! Way better then polynomials in the power format.
+
+		\item No Runge's Phenomenon, the interpolation converges to $f$.
+		\begin{itemize}
+			\item $\bigO(n^{-m})$ if $f$ is $m$ times differentiable.
+			\item $\bigO(C^n)$, for $C<1$, if $f$ is analytical in a neighborhood of $[-1, 1]$.
+		\end{itemize}
+
+		\item Very used in practice: present in external libraries like NumPy for Python.
+	\end{itemize}
+\end{frame}
+
 \end{document}

### 2019-10-18 ONPCE/slides.tex
wip

@@
 		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
+		\item This can be done in $\bigO(n^2)$.
 	\end{itemize}
@@
 
+\begin{frame}{Chebyshev Interpolation}
+	Choosing the degree of the interpolation:
+
+	\begin{itemize}
+		\item There is no guaranteed way to choose it.
+		\item A good rule is to examine the last coefficient.
+		\item For a predefined $\epsilon$, choose $n$, such that:
+
+		\begin{equation*}
+		|a_n| \le \epsilon
+		\end{equation*}
+
+		\item There are other ways like checking the error on a Lobatto grid.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}
+	For $n=32$, a precision of $10^{-10}$ is expected.
+
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{error_coef}
+		\caption{$|a_n|$ for the interpolation of $\xi$ for an instance.}
+		%	\label{fig:circumscribed-circle}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}{Roots}
+	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix. This is it for $n=5$:
+
+	\begin{equation*}
+	\left[\begin{array}{cccccc}
+	0&1&0&0&0\\
+	\frac{1}{2} & 0 & \frac{1}{2} & 0 & 0\\
+	0 & \frac{1}{2} & 0 & \frac{1}{2} & 0\\
+	0 & 0 & \frac{1}{2} & 0 & \frac{1}{2}\\
+	-\frac{a_0}{2a_5} & -\frac{a_1}{2a_5} &-\frac{a_2}{2a_5} &-\frac{a_3}{2a_5} &-\frac{a_4}{2a_5}\\
+	\end{array}\right]
+	\end{equation*}
+
+	\begin{itemize}
+		\item This matrix is a Hessenberg matrix.
+		\item Its eigenvalues can be found by a QR algorithm in $\bigO(n^3)$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}{Roots}
+	The largest error on roots that were found for $n=32$ is around $10^{-14}$ for an instance:
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{error_roots}
+		\caption{$|\xi(\hat{\theta})|$, where $\hat{\theta}$ is a root of $f_n$.}
+		%	\label{fig:circumscribed-circle}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}{Roots}
+	The experiments were made using Python with the NumPy library. The running time is really low, even for $n=64$.
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{running_time}
+		\caption{The running time to find the roots of $f_n$.}
+		%	\label{fig:circumscribed-circle}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Example}
+	An example with $4$ solutions.\cite{andreta}.
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{e3psol012}
+		\caption{An example with $4$ solutions.}
+		%	\label{fig:circumscribed-circle}
+	\end{figure}
+\end{frame}
+
 \end{document}

### 2019-10-19 ONPCE/slides.tex
wip

@@
 
-	If the radius is $b$, the angle is a solution:
+	If the radius is $b$, the angle of rotation is a solution:
 
@@
 	\end{equation*}
-	with $p=u, v, w$.
+	for $p=u, v, w$.
 
@@
 \begin{frame}{Fixed-shape ellipse by three points}
-	There is a known formula for the radius of a circumscribed circle:
+	There is a known formula for the radius of a circumscribed circle \cite[p.~189]{johnson1960}:
 
@@
 	There is no clear pattern in $\xi$.
+	\begin{itemize}
+		\item It can be written as $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$.
+		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
+	\end{itemize}
 \begin{figure}
@@
 
+\begin{frame}{Polynomial Interpolation}
+	It is a way to approximate a function by a simpler one (a polynomial).
+
+	\begin{itemize}
+		\item A degree $n$ of the interpolation is determined.
+		\item $n+1$ points are chosen, such that the polynomial has to pass through.
+		\item Can be calculated using Lagrange's formula.
+
+		\item We can find every root of a polynomial by determining the eigenvalues of a matrix called The Companion Matrix \cite[p.~195]{horn}.
+
+		\item Depending on the points, the interpolation can be a bad approximation. It can get worse even if $n$ is increased (Runge's Phenomenon) \cite[p.~37]{powell}.
+	\end{itemize}
+\end{frame}
+
 \begin{frame}{Chebyshev Interpolation}
@@
 	\begin{block}{Chebyshev Polynomial}
-		$T_n: [-1, 1] \mapsto [-1, 1]$ is the $n$-degree Chebyshev polynomial:
+		$T_n: [-1, 1] \mapsto [-1, 1]$ is the $n$-degree Chebyshev polynomial \cite{chebbook}:
 		\begin{equation*}
@@
 
+\end{frame}
+
+\begin{frame}{Chebyshev Interpolation}
+\begin{figure}
+	\centering
+
+	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+	\includegraphics[scale=.6]{chebpoly}
+	\caption{Chebyshev Polynomials of degree $1, 2, 3, 4$.}
+	%	\label{fig:circumscribed-circle}
+\end{figure}
 \end{frame}
@@
 		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
-		\item This can be done in $\bigO(n^2)$.
+		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Numerically stable! Way better then polynomials in the power format.
+		\item Numerically stable! Way better then polynomials in the power format \cite{gautschi:1979}.
 
@@
 		\begin{itemize}
-			\item $\bigO(n^{-m})$ if $f$ is $m$ times differentiable.
-			\item $\bigO(C^n)$, for $C<1$, if $f$ is analytical in a neighborhood of $[-1, 1]$.
+			\item $\bigO(n^{-m})$ if $f$ is $m$ times differentiable \cite[p.~28]{gottlieb}.
+			\item $\bigO(C^n)$, for $C<1$, if $f$ is analytical in a neighborhood of $[-1, 1]$ \cite{battles:2004}.
 		\end{itemize}
@@
 		\item There is no guaranteed way to choose it.
-		\item A good rule is to examine the last coefficient.
+		\item A good rule is to examine the last coefficient (the last coefficient rule-of-thumb \cite[p~.50]{boyd:2001}).
 		\item For a predefined $\epsilon$, choose $n$, such that:
@@
 
-		\item There are other ways like checking the error on a Lobatto grid.
+		\item There are other ways like checking the error on a Lobatto grid \cite{boyd:2007}.
 	\end{itemize}
@@
 \begin{frame}{Chebyshev Interpolation}{Roots}
-	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix. This is it for $n=5$:
+	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. This is it for $n=5$:
 
@@
 		\item This matrix is a Hessenberg matrix.
-		\item Its eigenvalues can be found by a QR algorithm in $\bigO(n^3)$.
+		\item Its eigenvalues can be found by a QR decomposition in $\bigO(n^3)$.
 	\end{itemize}
@@
 \begin{frame}{Example}
-	An example with $4$ solutions.\cite{andreta}.
+	An example with $4$ solutions.
 	\begin{figure}
@@
 
+\begin{frame}[allowframebreaks]
+	\frametitle{References}
+	\bibliographystyle{amsalpha}
+	\bibliography{references}
+\end{frame}
+
 \end{document}

### 2019-10-23 ONPCE/slides.tex
wip

@@
 	\begin{itemize}
-		\item It can be written as $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$.
+		\item It can be written as 
+		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
 		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
@@
 	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics[scale=.5]{035}
+	\includegraphics[scale=.4]{012}
 	\caption{Another example of $\xi$.}
@@
 		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.5]{012}
-		\caption{Yet another example of $\xi$.}
+		\includegraphics[scale=.5]{g4sol}
+		\caption{An example of $\xi$ with $4$ roots.}
 		%	\label{fig:circumscribed-circle}
@@
 	\begin{itemize}
+		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
 		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
-		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
 	\end{itemize}
@@
 
-		\item Very used in practice: present in external libraries like NumPy for Python.
+		\item Very used in practice: 
+		\begin{itemize}
+			\item Present in external libraries like NumPy for Python.
+			\item Matlab tool Chebfun: allows functions to be treated as vectors.
 		\end{itemize}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Example}
+	$\xi$ and its approximation of degree $8$.
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{inexn8}
+		\caption{An example of degree $8$ approximation.}
+		%	\label{fig:circumscribed-circle}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Example}
+	$\xi$ and its approximation of degree $10$.
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{inexn10}
+		\caption{An example of degree $10$ approximation.}
+
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Example}
+	$\xi$ and its approximation of degree $12$.
+	\begin{figure}
+		\centering
+
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.6]{inexn12}
+		\caption{An example of degree $12$ approximation.}
+
+	\end{figure}
 \end{frame}
@@
 \begin{frame}{Chebyshev Interpolation}{Roots}
-	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. This is it for $n=5$:
+	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$ we have:
 

### 2019-10-23 ONPCE/slides.tex
wip

@@
 
-The roots of $\xi$ are solutions of our problem.
+	\begin{itemize}
+		\item It can be written as 
+		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
+		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
+		\item The roots of $\xi$ are solutions of our problem.	
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Fixed-shape ellipse by three points}
+	An example with no roots.
 	\begin{figure}
@@
 \begin{frame}{Fixed-shape ellipse by three points}
-	There is no clear pattern in $\xi$.
-	\begin{itemize}
-		\item It can be written as 
-		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
-		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
-	\end{itemize}
+	An example with two roots.
 \begin{figure}
@@
 	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics[scale=.4]{012}
+	\includegraphics[scale=.5]{012}
 	\caption{Another example of $\xi$.}
@@
 \begin{frame}{Fixed-shape ellipse by three points}
-	An example with two roots.
+	An example with four roots.
 	\begin{figure}
@@
 \begin{frame}{Chebyshev Interpolation}{Roots}
-	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$ we have:
+	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$, we have:
 
@@
 	\begin{itemize}
-		\item This matrix is a Hessenberg matrix.
+		\item This is a Hessenberg matrix.
 		\item Its eigenvalues can be found by a QR decomposition in $\bigO(n^3)$.

### 2019-11-01 defesa/tex/chapter/e3p.tex
wip

@@
 According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$.
-The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree.
+The reason to bring up this fact is that $\xi$ can be written as $$\sum_{0 \le j+k \le 6} c_{j,k} \cos^{j}(\theta)\sin^{k}(\theta),$$ for some $\{c_{j,k} \in \R: 0 \le j+k \le 6\}$, which implies that it can be converted to a real trigonometric polynomial of degree $6$ which can have up to $12$ roots.
 
- To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}, combine the parts as $\xi(\theta)$ is just addition and multiplication of terms in that form.
-It is also possible to see that the term of higher the degree of $\xi(\theta)$ is the multiplication of the three squared distances, as $\norm{\varphi(v, \theta)}^2$ has degree $2$ the degree of $\xi(\theta)$ is $6$.
-
+ To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}.
+It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared distances, as $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
 \begin{align}\label{eq:dd}
@@
 
-\subsection{Converting $\xi(\theta)$ into a polynomial}
+\subsection{Converting $\xi$ into a polynomial}
 
-Using the identity $x = \tan{\frac{\theta}{2}}$, it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate polynomial of degree $12$.
+Using the identity $x = \tan{\frac{\theta}{2}}$, it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate real polynomial of degree $12$.
 The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
@@
 This method seemed to work fine, but for some instances it did not find roots which were priorly known.
-This happened probably because of the transformation that was used to convert $\xi$ into a polynomial.
+This happened probably because of the transformation that was used to convert $\xi$ into a polynomial--later we introduce a different transformation which is more convenient.
 It can be very numerically unstable as the tangent function grows to fast for angles that are greater than $\frac{\pi}{4}$.
@@
 
-\section{A method for E3PNT}
+\section{Two methods for E3PNT}
+
+In this section we introduce two methods that successfully find every solution of E3P on the instances we use for experiments. 
+The first one uses an approximation of $\xi$, it is slightly more efficient in respect to running time than the second method, however, it the approximation has only asymptotic guarantees and we can assure that it will always work.
+The second method converts $\xi$ into a complex polynomial and finds its roots by determining the eigenvalues of its companion matrix.
+
+\subsection{An approximation method}
 
@@
 
-\subsection{Chebyshev interpolation}
+\subsubsection{Chebyshev interpolation}
 
@@
 \end{equation} 
-with $f$ being the function to be approximated and $f_n$ the unique $n$ degree polynomial that passes through $\{(x_j, f(x_j)): j=0, 1, \dots n\}$.
+with $f$ being the function to be approximated, and $f_n$ the unique $n$-degree polynomial that passes through $\{(x_j, f(x_j)): j=0, 1, \dots n\}$.
 Because of the uniqueness of interpolant polynomials, there is a direct link between the quality of an approximation and the points chosen to interpolate.
@@
 This is known as Runge's phenomenon and an example can be seen in \citeonline[p.~37]{powell} where uniformly spaced points are chosen to interpolate the function $f(x) = (1+x^2)^{-1}$ on the interval $[-5, 5]$.
-That is where Chebyshev interpolation comes in, instead of $n+1$ arbitrary points, the interpolation is done on the $n+1$ roots of $T_n$, which are also known as Chebyshev Nodes:
 
+That is where Chebyshev interpolation comes in.
+Instead of choosing $n+1$ arbitrary points, the $n+1$ roots of $T_{n+1}$, which are also known as Chebyshev Nodes, are chosen as the interpolation points:
 \begin{equation}
-x_j = \cos{\left(\pi\dfrac{2n-2j+1}{2n}\right)},
+x_j = \cos{\left(\dfrac{\pi(k-\frac{1}{2})}{n+1}\right)},
 \end{equation}
-for $j=1, \dots, n$.
-If the domain of the function to be interpolated is in another range other than $[-1, 1]$, let us say $[a, b]$, then a transformation can be done to map it to the Chebyshev Nodes' domain:
+for $j=1, \dots, n+1$. This particular choice defeats Runge's phenomenon and provides a convergent approximation.
 
+Note that, if the domain of the function to be interpolated is defined on a range other than $[-1, 1]$, let us say $[a, b]$, then a transformation can be done to map it to the Chebyshev Nodes' domain:
 \begin{equation}
@@
 For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
-
 An alternative method can be found in \citeonline{boyd:2013} where the Chebyshev interpolation is calculated directly as a truncated Chebyshev series, as in \autoref{eq:chebseries}, in $\bigO(n^2)$.
@@
 
-Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is a very well-behaved function: it is analytic and  has infinitely many continuous and integrable derivatives.
+Even though $\xi$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is a very well-behaved function: it is analytic and  has infinitely many continuous and integrable derivatives.
 This satisfy all the requirements of the result in \citeonline[p.~28]{gottlieb} which says that if a function has $m$ continuous and integrable derivatives on a closed interval, then its absolute difference between the Chebyshev truncate series is $\bigO(n^{-m})$.
 Also, in \citeonline{battles:2004} a theorem is presented stating that if a function is analytic on a neighborhood of $[-1, 1]$, then the convergence is $\bigO(C^n)$, for some $C<1$.
+
+To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}.
+There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error $r_n$:
+\begin{equation}
+r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|.
+\end{equation}
+
+\subsection{Transforming $\xi$ into a complex polynomial}
+
+This approach is based on a idea published on \citeonline{boyd:2006} which converts a real trigonometric polynomial into a polynomial with a variable $z = e^{i\theta}$.
+In our case, we replace $\cos{\theta}$ and $\sin{\theta}$ with the following identities:
+\begin{align}
+\cos{\theta} = \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
+\sin{\theta} = \dfrac{e^{i\theta} - e^{-i\theta}}{2i}.
+\end{align}
+
+It is possible to show that with that substitution and changing the variable to $z=e^{it}$, we obtain a function on the form:
+\begin{equation}
+g(z)=\sum_{k=-6}^6 c_k z^k.
+\end{equation}
+Then, multiplying it by
 
@@
 Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we define the interpolation error $r_n$ as:
-
-\begin{equation}
-r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|.
-\end{equation}
 

### 2019-11-04 defesa/tex/chapter/definicoes.tex
wip

@@
 First, the ellipse can be translated to the origin and then rotated by $-\theta$, the reverse transformations are expressed by \autoref{eq:rotated_ellipse}.
-
 \begin{equation}\label{eq:rotated_ellipse}
@@
 \end{equation}
-
 Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in [0, \pi]$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co}.
-
 \begin{equation}\label{eq:rotated_ellipse_co}
@@
 \end{equation}
+
+\section{Polynomials and their roots}
+
+In this work, only univariate polynomials are used, so the definition and results are focused on this case.
+
+A function $p_n: \mathbb{C} \mapsto \mathbb{C}$ is a $n$-degree polynomial if it can be written as:
+\begin{equation}\label{eq:poly}
+p_n(x) = \sum_{k=0}^{n} a_k x^k.
+\end{equation}
+The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
+However, a numerical approach exists for higher-degree polynomials.
+
+ In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial.
+At first it seems that we are just trading for the same problem as, in general, to find the eigenvalues of a matrix, one needs to determine the roots of that matrix's characteristic polynomial.
+Nevertheless, it turns out that companion matrices are very convenient when it comes to finding eigenvalues.
+They are what is called Hessenberg matrices, and QR algorithms can be used to find their eigenvalues (a $\bigO(n^2)$ algorithm that does that can be found in \citeonline{bini:2007}).
+ For example, given a polynomial of degree $4$ written as \autoref{eq:poly} its companion matrix is given by:
+
+ \begin{equation}
+ \left[\begin{array}{ccccc}
+ 0 & 1 & 0 & 0 & 0\\
+ 0 & 0 & 1 & 0 & 0\\
+ 0 & 0 & 0 & 1 & 0\\
+ 0 & 0 & 0 & 0 & 1\\
+ -a_0 & -a_1 & -a_2 & -a_3 & -a_4
+ \end{array}\right].
+ \end{equation}
+
+\section{Real trigonometric polynomial}
+
+The same definition found in \citeonline[p.~150]{powell} for real trigonometric polynomials is given here.
+They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by:
+\begin{equation}\label{eq:trig_poly}
+p_n(\theta) = \sum_{k=0}^{n} a_k\cos(k\theta) + \sum_{k=1}^{n} b_k\sin(k\theta).
+\end{equation}
+We say that $p_n$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial.
+An important property is stated in \citeonline[p.~150]{powell}, it says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$.
+It also says that a function written in the format:
+$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta} & \quad j, k \in \mathbb{Z}_+ \end{array},$$
+can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial:
+\begin{equation}\label{eq:trig_poly_2}
+\sum_{0 \le j+k \le n}c_{j,k}\cos^j{\theta}\sin^k{\theta},
+\end{equation}
+for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$.

### 2019-11-04 defesa/tex/chapter/e3p.tex
wip

@@
 
-According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$.
-The reason to bring up this fact is that $\xi$ can be written as $$\sum_{0 \le j+k \le 6} c_{j,k} \cos^{j}(\theta)\sin^{k}(\theta),$$ for some $\{c_{j,k} \in \R: 0 \le j+k \le 6\}$, which implies that it can be converted to a real trigonometric polynomial of degree $6$ which can have up to $12$ roots.
-
+It turns out that $\xi$ can be written as a real trigonometric polynomial of degree $6$ in the format given by \autoref{eq:trig_poly_2}, which implies that it can have up to $12$ distinct roots.
  To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}.
-It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared distances, as $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
+It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared distances.
+As $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
 \begin{align}\label{eq:dd}
@@
 
-\section{Attempts on solving E3PNT}
-
-In this section we give a brief review of some of the approaches we tried on developing a method for E3PNT.
-
-\subsection{Converting $\xi$ into a polynomial}
-
-Using the identity $x = \tan{\frac{\theta}{2}}$, it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate real polynomial of degree $12$.
-The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
-Therefore, pursuing a numerical method would be a good choice for this problem.
-
-Perhaps the first idea one would have for this problem would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method does not converge.
-A result published by \citeonline{mc1}, however, says that iterative methods generally are not convergent for polynomials of degree $4$ or more.
-Also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.
-
-This next approach is very popular in practice as it is present in external libraries like NumPy for Python \cite{python}.
-In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial.
-At first it seems that we are just trading for the same problem as, in general, to find the eigenvalues of a matrix, one needs to determine the roots of that matrix's characteristic polynomial.
-Nevertheless, it turns out that companion matrices are very convenient when it comes to finding eigenvalues.
-They are what is called Hessenberg matrices, and QR algorithms can be used to find their eigenvalues (a $\bigO(n^2)$ algorithm that does that can be found in \citeonline{bini:2007}).
-
-This method seemed to work fine, but for some instances it did not find roots which were priorly known.
-This happened probably because of the transformation that was used to convert $\xi$ into a polynomial--later we introduce a different transformation which is more convenient.
-It can be very numerically unstable as the tangent function grows to fast for angles that are greater than $\frac{\pi}{4}$.
-Depending on the instance, there could be roots very close to $0$ and others that are too far from it.
-
-\subsection{Using the conic general equation}
+\section{An attempt using the conic general equation}
 
@@
 \begin{equation}\label{eq:gen_ellipse}
-Ax^2+Bxy+Cy^2+Dy+Ex+F=0
+Ax^2+Bxy+Cy^2+Dy+Ex+F=0.
 \end{equation}
+This equation actually represents any conic, for it to be an ellipse the condition $B^2 -4AC < 0$ must be satisfied.
 
@@
 
-\section{Two methods for E3PNT}
-
-In this section we introduce two methods that successfully find every solution of E3P on the instances we use for experiments. 
-The first one uses an approximation of $\xi$, it is slightly more efficient in respect to running time than the second method, however, it the approximation has only asymptotic guarantees and we can assure that it will always work.
-The second method converts $\xi$ into a complex polynomial and finds its roots by determining the eigenvalues of its companion matrix.
-
-\subsection{An approximation method}
+\section{An approximation method}
 
@@
 
-\subsubsection{Chebyshev interpolation}
+\subsection{Chebyshev interpolation}
 
@@
 
-\subsection{Transforming $\xi$ into a complex polynomial}
+\section{Converting $\xi$ into a polynomial}
 
-This approach is based on a idea published on \citeonline{boyd:2006} which converts a real trigonometric polynomial into a polynomial with a variable $z = e^{i\theta}$.
+As it was pointed out on \autoref{chapter:definitions}, it is possible to find the roots of a univariate polynomial through an algorithm.
+For that reason, converting $\xi$ somehow into a polynomial can provide a good way to get the solutions of E3PNT.
+
+The first attempt was using the identity $x = \tan{\frac{\theta}{2}}$.
+This transforms $\xi$ into a polynomial of degree $12$.
+At first this method seemed to work fine, however, for some instances it did not find roots which were priorly known.
+This happened probably because of the transformation that was used to convert $\xi$ into a polynomial.
+It can be very numerically unstable as the tangent function grows to fast for angles that are greater than $\frac{\pi}{4}$.
+Because of that, depending on the instance, there could be roots very close to $0$ and others that are too far from it.
+
+The second approach is based on a idea published on \citeonline{boyd:2006} which converts a real trigonometric polynomial into a polynomial with a variable $z = e^{i\theta}$.
 In our case, we replace $\cos{\theta}$ and $\sin{\theta}$ with the following identities:
@@
 \end{equation}
-Then, multiplying it by
+Then, multiplying $g$ by $z^6 = e^{6i\theta}$, the following polynomial is obtained:
+
+\begin{equation}
+h(z) = z^6 g(z) = \sum_{k=0}^{12} c_k z^k.
+\end{equation}
+
+Then, every root of $\xi$ is a root of $h$.
+Note that the converse is not true, there could be roots of $h$ which are not roots of $\xi$, because a root $\hat{z}$ could have $|\hat{z}| \neq 1$ whereas $|e^{it}|$ is $1$.
 

### 2019-11-04 ONPCE/slides.tex

@@
 		\titlepage
+
+		\footnotesize This research has been funded by Cordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES).
+This is part of a Master's research project on the problem: \textit{Planar Maximal Covering by Ellipses with Rotation}.
 	\end{frame}
@@
 		\includegraphics[scale=.5]{sol3}
-		\caption{After scaling.}
+		\caption{After scaling by $\frac{b}{a}$.}
 		\label{fig:sol33}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Transforming the problem}
+	Then, we apply the inverse transformation.
+
+	\begin{figure}
+		\centering
+		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+		\includegraphics[scale=.5]{sol31}
+		\caption{After scaling by $\frac{a}{b}$.}
+
 	\end{figure}
@@
 		\includegraphics[scale=.5]{sol4}
-		\caption{One solution for this instance.}
+		\caption{A solution is obtained after scaling by $\frac{a}{b}$ and rotating by $-\theta$.}
 		\label{fig:sol4}
@@
 		\item It can be written as 
-		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
+		$$\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
 		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}

### 2019-12-06 defesa/tex/chapter/definicoes.tex
wip

@@
 
+\section{Complex numbers}
+
+We introduce here some things about complex numbers that are used later on \autoref{chapter:e3p}.
+
+Any complex number $z = a + bi \in \mathbb{C}$ can be written as follows:
+\begin{equation}
+z = re^{i\theta},
+\end{equation}
+where $\theta$ is the polar angle of the vector $(a, b)$, we refer to it as $angle(z)$, and $r$ is the length of this vector, we refer to it as $|z| = \sqrt{a^2 + b^2}$.
+This is known as the Euler's Formula.
+If $r=1$, then we say that $z$ is in the unit circle.
+The complex conjugate is another important operator that we need.
+Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
+\begin{equation}
+\bar{z} = a - bi.
+\end{equation}
+Also, it is useful to see that, then $1/z=\bar{z}/|z|$. Two observations about the angles of complex numbers are worth mentioning:
+\begin{align}
+angle(\bar{z}) = -angle(z)\\
+angle(-z) = \pi - angle(z).
+\end{align}
+
 \section{Polynomials and their roots}
@@
 \begin{equation}\label{eq:poly}
-p_n(x) = \sum_{k=0}^{n} a_k x^k.
+p_n(z) = \sum_{k=0}^{n} a_k z^k.
 \end{equation}
@@
  In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial.
-At first it seems that we are just trading for the same problem as, in general, to find the eigenvalues of a matrix, one needs to determine the roots of that matrix's characteristic polynomial.
-Nevertheless, it turns out that companion matrices are very convenient when it comes to finding eigenvalues.
-They are what is called Hessenberg matrices, and QR algorithms can be used to find their eigenvalues (a $\bigO(n^2)$ algorithm that does that can be found in \citeonline{bini:2007}).
- For example, given a polynomial of degree $4$ written as \autoref{eq:poly} its companion matrix is given by:
-
+For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by:
  \begin{equation}
@@
  0 & 0 & 0 & 0 & 1\\
- -a_0 & -a_1 & -a_2 & -a_3 & -a_4
+ -\dfrac{a_0}{a_5} & -\dfrac{a_1}{a_5} & -\dfrac{a_2}{a_5} & -\dfrac{a_3}{a_5} & -\dfrac{a_4}{a_5}
  \end{array}\right].
  \end{equation}
+
+ Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory.
+In \cite[p.~341]{golub} a practical version of it is developed.
+The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and under some assumptions, convergence to the eigenvalues is achieved.
+It is worth mentioning that this approach is actually used in MATLAB and LAPACK, which is the external library used in NumPy for Python.
+ Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary.
+This and other properties are used in \citeonline{barel} on the development of a $\bigO(n^2)$ algorithm for the specific case of companion matrices.
 

### 2019-12-06 defesa/tex/chapter/e3p.tex
wip

@@
 
-As it was pointed out on \autoref{chapter:definitions}, it is possible to find the roots of a univariate polynomial through an algorithm.
-For that reason, converting $\xi$ somehow into a polynomial can provide a good way to get the solutions of E3PNT.
+On \autoref{chapter:definitions} a brief introduction is given on how to get the roots of a polynomial.
+For that reason, we discuss two ways of converting $\xi$ into a polynomial.
+Symbolic computing was used to compute the polynomials, in practice an external Python library called SymPy was utilized (see \citeonline{sympy} for more details).
 
-The first attempt was using the identity $x = \tan{\frac{\theta}{2}}$.
-This transforms $\xi$ into a polynomial of degree $12$.
-At first this method seemed to work fine, however, for some instances it did not find roots which were priorly known.
-This happened probably because of the transformation that was used to convert $\xi$ into a polynomial.
-It can be very numerically unstable as the tangent function grows to fast for angles that are greater than $\frac{\pi}{4}$.
-Because of that, depending on the instance, there could be roots very close to $0$ and others that are too far from it.
+The first attempt was using the identity $x = \tan{\frac{\theta}{2}}$ from which it is possible to construct a $12$-degree polynomial.
+At first,  the root-finding algorithm described on \autoref{chapter:definitions} seemed to work fine and return every solution of E3PNT, however, we later found out that for some instances, priorly known roots were not being found.
+The cause was not for sure identified, but a good guess would be that for angles which are greater than $\frac{\pi}{4}$, $x$ starts growing too rapidly which could lead to numerical instability.
 
-The second approach is based on a idea published on \citeonline{boyd:2006} which converts a real trigonometric polynomial into a polynomial with a variable $z = e^{i\theta}$.
-In our case, we replace $\cos{\theta}$ and $\sin{\theta}$ with the following identities:
-\begin{align}
+The second approach is based on a idea published on \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials into univariate complex polynomials in order to obtain its roots using the companion matrix scheme.
+Also, in \citeonline{weidner} it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
+
+\begin{align}\label{eq:complex_trig}
 \cos{\theta} = \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
@@
 
-It is possible to show that with that substitution and changing the variable to $z=e^{it}$, we obtain a function on the form:
+It is possible to show that with that substitution and changing the variable to $z=e^{it}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$:
+
 \begin{equation}
-g(z)=\sum_{k=-6}^6 c_k z^k.
+g(z)=\sum_{k=0}^{12} c_k z^{k-6},
 \end{equation}
+for some $c_0, \dots, c_{12} \in \mathbb{C}$.
+It is important to notice that this definition of $g$ does not impose that $z$ stays in the unit circle as any complex number, for that the additional condition: $|z|=1$ would need to be added.
+
 Then, multiplying $g$ by $z^6 = e^{6i\theta}$, the following polynomial is obtained:

### 2019-12-11 defesa/tex/chapter/definicoes.tex
wip

@@
 
-We introduce here some things about complex numbers that are used later on \autoref{chapter:e3p}.
+The set of complex numbers $\mathbb{C}$ is an extension of the set of real numbers $\R$ and can be very useful depending on the problem at hand.
+A thorough introduction on this topic is out of the scope and we just go through some basic properties that are going to be used later on \autoref{chapter:e3p}.
 
-Any complex number $z = a + bi \in \mathbb{C}$ can be written as follows:
+A complex number is composed of a real part added to an imaginary part which is a multiple of $i = \sqrt{-1}$, this is expressed as $a + bi$, with $a, b \in \R$.
+Because $z$ is composed of two real numbers, the complex number system can be visualized on $\R^2$ as shown on \autoref{fig:complex-numbers}.
+This is also a good way to visualize Euler's Formula, as it can be also seen on \autoref{fig:complex-numbers}, which says that any complex number can be written in terms of its radius and polar angle as follows:
 \begin{equation}
@@
 \end{equation}
-where $\theta$ is the polar angle of the vector $(a, b)$, we refer to it as $angle(z)$, and $r$ is the length of this vector, we refer to it as $|z| = \sqrt{a^2 + b^2}$.
-This is known as the Euler's Formula.
-If $r=1$, then we say that $z$ is in the unit circle.
-The complex conjugate is another important operator that we need.
-Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
+with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle.
+\begin{figure}[ht]
+	\centering
+	\def\svgwidth{\columnwidth}
+	\includegraphics[scale=.5]{tex/figures/complex_numbers}
+	\caption{The representation of a complex number on two dimensions.}
+	\label{fig:complex-numbers}
+\end{figure}
+
+The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
 \begin{equation}
@@
 \end{equation}
-Also, it is useful to see that, then $1/z=\bar{z}/|z|$. Two observations about the angles of complex numbers are worth mentioning:
+Finally two observations about the angles of complex numbers are given here:
 \begin{align}
 angle(\bar{z}) = -angle(z)\\
-angle(-z) = \pi - angle(z).
+angle(-z) = \pi - angle(z),
 \end{align}
+checking their validity can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.
 
@@
 \end{equation}
-The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots.
+The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots.
 However, a numerical approach exists for higher-degree polynomials.

### 2019-12-11 defesa/tex/chapter/definicoes.tex
wip

@@
 
-An non-axis-parallel ellipse centered at $c\in\R^2$ can also be described by \autoref{def:ellipse}.
+A non-axis-parallel ellipse centered at $c\in\R^2$ can also be described by \autoref{def:ellipse}.
 Nonetheless, a simpler equation is going to be used here.
@@
 A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations.
-First, the ellipse can be translated to the origin and then rotated by $-\theta$, the reverse transformations are expressed by \autoref{eq:rotated_ellipse}.
+Reversing these transformations produces the following equation for a non-axis-parallel ellipse:
 \begin{equation}\label{eq:rotated_ellipse}
@@
 \end{equation}
-Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in [0, \pi]$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co}.
+Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in [0, \pi)$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co}.
 \begin{equation}\label{eq:rotated_ellipse_co}
@@
 
-A complex number is composed of a real part added to an imaginary part which is a multiple of $i = \sqrt{-1}$, this is expressed as $a + bi$, with $a, b \in \R$.
+A complex number is composed of a real part added to an imaginary part which is a multiple of the imaginary unit $i = \sqrt{-1}$.
+This is expressed as $a + bi$, with $a, b \in \R$.
 Because $z$ is composed of two real numbers, the complex number system can be visualized on $\R^2$ as shown on \autoref{fig:complex-numbers}.
@@
 \begin{equation}
-z = re^{i\theta},
+z = re^{i\theta}=r(\cos{\theta} + i\sin{\theta}),
 \end{equation}
 with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle.
+Note that $angle$ is a function from $\mathbb{C}$ to $[0, 2\pi)$.
 \begin{figure}[ht]
@@
 	\def\svgwidth{\columnwidth}
-	\includegraphics[scale=.5]{tex/figures/complex_numbers}
+	\includegraphics[scale=.4]{tex/figures/complex_numbers}
 	\caption{The representation of a complex number on two dimensions.}
@@
 \end{equation}
-Finally two observations about the angles of complex numbers are given here:
+Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}.
 \begin{align}
-angle(\bar{z}) = -angle(z)\\
-angle(-z) = \pi - angle(z),
+angle(\bar{z}) = 2\pi-angle(z)\\
+angle(-z) = \pi + angle(z),
 \end{align}
-checking their validity can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.
+checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.
 
@@
 
-In this work, only univariate polynomials are used, so the definition and results are focused on this case.
+In this work, we are mostly interested in univariate polynomials defined over the complex numbers.
 
@@
 \begin{equation}\label{eq:poly}
-p_n(z) = \sum_{k=0}^{n} a_k z^k.
+p_n(z) = \sum_{k=0}^{n} a_k z^k,
 \end{equation}
+with $a_0, \dots, a_n \in \mathbb{C}$.
 The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots.
-However, a numerical approach exists for higher-degree polynomials.
+Fortunately, a numerical approach exists for higher-degree polynomials which in practice works really well.
 
@@
  Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory.
-In \cite[p.~341]{golub} a practical version of it is developed.
+A very complete introduction to this algorithm can be found on \citeonline{watkins:2008}.
 The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and under some assumptions, convergence to the eigenvalues is achieved.
-It is worth mentioning that this approach is actually used in MATLAB and LAPACK, which is the external library used in NumPy for Python.
  Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary.
 This and other properties are used in \citeonline{barel} on the development of a $\bigO(n^2)$ algorithm for the specific case of companion matrices.
+
+ In practice, LAPACK's ZGEEV routine is utilized--the user guide can be found in \citeonline{lapack}--which is an implementation of the QR algorithm that returns every eigenvalue of a complex matrix.
 
@@
 \end{equation}
-We say that $p_n$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial.
+We say that $p_n: \R \mapsto \R$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial.
 An important property is stated in \citeonline[p.~150]{powell}, it says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$.

### 2019-12-11 defesa/tex/chapter/e3p.tex
wip

@@
 On \autoref{chapter:definitions} a brief introduction is given on how to get the roots of a polynomial.
-For that reason, we discuss two ways of converting $\xi$ into a polynomial.
+For that reason, we discuss two ways of converting $\xi$ into a polynomial in this section.
 Symbolic computing was used to compute the polynomials, in practice an external Python library called SymPy was utilized (see \citeonline{sympy} for more details).
@@
 
-It is possible to show that with that substitution and changing the variable to $z=e^{it}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$:
+It is possible to show that with that substitution and changing the variable to $z=e^{i\theta}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$, with $\mathbb{S}$ being the unit circle ($\mathbb{S} = \{z \in \mathbb{C} : |z|=1\}$):
 
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-It is important to notice that this definition of $g$ does not impose that $z$ stays in the unit circle as any complex number, for that the additional condition: $|z|=1$ would need to be added.
-
-Then, multiplying $g$ by $z^6 = e^{6i\theta}$, the following polynomial is obtained:
-
+Even though $g$ is not a polynomial, it is easy to obtain one from it.
+Firstly, the negative exponentials need to be shifted, this can be done by just multiplying $g$ by $z^6$.
+Secondly, the domain cannot be restricted to the unit circle, so we define $h : \mathbb{C} \mapsto \mathbb{C}$ as:
 \begin{equation}
@@
 
-Then, every root of $\xi$ is a root of $h$.
-Note that the converse is not true, there could be roots of $h$ which are not roots of $\xi$, because a root $\hat{z}$ could have $|\hat{z}| \neq 1$ whereas $|e^{it}|$ is $1$.
+Then, by its definition is possible to see that every root of $g$ is also a root of $h$.
+Conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$--or $|\hat{z}|=1$--is also a root of $g$.
+Naturally, the angle of a root $\hat{z}$ of $g$ is a root of $\xi$ by Euler's Formula.
+
+It is possible to make another reduction to obtain a degree-$6$ polynomial from $h$ whose roots form a superset of the roots of $g$.
+As it has been mentioned on this chapter, an ellipse is symmetric with respect to its own axis.
+This means $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$\footnote{$\xi$ is only defined over $[0, \pi)$, so this equality is not actually valid.}.
+On \autoref{chapter:definitions}, it was stated that the angle of $z$ and $-z$ has the same symmetry with each other as an ellipse's angle of rotation:
+\begin{equation*}
+angle(-z) = \pi + angle(z).
+\end{equation*}
+From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$.
+This implies that $h$ is, in fact an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
+\begin{align}
+h(-z) = (-z)^6g(-z) = z^6g(z).
+\end{align}
+Therefore, all the odd degree coefficients of $h$ are $0$ and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$:
+\begin{equation}
+f(y) = \sum_{k=0}^{6} c_{2k} y^k.
+\end{equation}
+Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$.
+As the angle of $-\sqrt{\hat{y}}$ is not between $[0, pi)$ we can ignore it.
+Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
+\begin{equation}
+angle(\sqrt{z}) = angle(z)/2.
+\end{equation}
+Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm, with $n=6$, can be constructed for E3P.
+
+It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe for future work it can be used for further improvements.
+Analyzing the polynomials produced for several instances, the following seems to true:
+\begin{equation}
+c_k = \hat{c_{6-k}},
+\end{equation}
+for $k=0, \dots, 6$.
+For now, we do not have any ideas on how it could be proved.
+Nevertheless, this seems to lead somewhere interesting because this condition guarantees that $f$ is a self-reciprocal polynomial which implies that its roots will always come in pairs $(\hat{z}, 1/\hat{z})$.
 

### 2019-12-12 defesa/tex/chapter/e3p.tex
wip

@@
 Conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$--or $|\hat{z}|=1$--is also a root of $g$.
-Naturally, the angle of a root $\hat{z}$ of $g$ is a root of $\xi$ by Euler's Formula.
+Naturally, the angle of a root $\hat{z}$ of $g$ is a root of $\xi$ by Euler's Formula used in the substitution $z=e^{i\theta}$.
 
@@
 As it has been mentioned on this chapter, an ellipse is symmetric with respect to its own axis.
-This means $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$\footnote{$\xi$ is only defined over $[0, \pi)$, so this equality is not actually valid.}.
+This means that $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$\footnote{The domain of $\xi$ is initially set to be $[0, \pi)$, .}.
 On \autoref{chapter:definitions}, it was stated that the angle of $z$ and $-z$ has the same symmetry with each other as an ellipse's angle of rotation:

### 2019-12-12 defesa/tex/chapter/e3p.tex
wip

--- 2019-12-11 defesa/tex/chapter/e3p.tex
@@
 As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way.
-We try to give a review of some of those, and also make a case for the method we propose in terms of velocity of convergence and quality of the solutions that it finds.
+We try to give a review of some of those going through the issues with the failing approaches, at the end we propose a $\bigO(1)$ algorithm that finds every solution of the problem and run some numerical experiments to show the precision of the found solutions.
 
 We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
-A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
-In other words, the goal is to develop a method to find every solution of E3PNT.
+A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
+The goal is to develop a method to find every solution of E3PNT.
 
@@
 This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle.
-This process can be parametrized by the angle of rotation of the points, as described by \autoref{eq:trpnts}, and because of the invertibility of linear transformations solutions for E3PNT can be obtained by reversing the transformations.
+This process can be parametrized by the angle of rotation of the points, as described by \autoref{eq:trpnts}, and because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.
 
@@
 
-Then, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $(0, 0), \varphi(v, \theta)$ and $\varphi(w, \theta)$, such that the circle has radius $b$.
-As, for three non-colinear fixed points, there is always an unique circumscribed circle for the triangle formed by those three points, the only variable to be determined ends up being the angle of rotation $\theta$.
+After that transformation, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$, such that the circle has radius $b$.
+Therefore, the only unknown of this problem is the angle of rotation.
+This idea reduces the number of variables from $3$ to only $1$, however, this would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
 
-Let $A(\theta)$ be the area of the triangle formed by the points $(0, 0), \varphi(v, \theta)$ and $\varphi(w, \theta)$--note that the transformation does not preserve distance or area.
+It turns out that for three non-colinear fixed points, there is always an unique circumscribed circle.
+Also, finding this unique circle can be done analytically, hence its radius can be easily computed and compared to $b$ when an angle is given.
+Let $A(\theta)$ be the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$--note that the transformation does not preserve distance or area.
 Then, the radius $R$ of the circumscribed circle is given by \autoref{eq:circumscribed_circle} \cite[p.~189]{johnson1960}.
@@
 
-Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, \pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b} in such a way that its zeros determine solutions to the E3PNT's instance.
+Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b} in such a way that its zeros determine solutions to the E3PNT's instance.
 Two questions about $\xi(\theta)$ that arise are: is its set of roots finite?
@@
 
-The method developed on \autoref{chapter:ellipses_n} iterates over every solution of E3PNT for every triplet of points, this is only possible if the size of this set of solutions is limited.
-Also, if this was not true, it would be very difficult to describe a method to get every solution which could be infinite.
+One of the steps of the method developed on \autoref{chapter:ellipses_n} is to iterate over every solution of E3PNT for every triplet of points.
+Of course doing that is only possible for a finite number of solutions.
+Also, discovering a bound for that is essential for determining the efficiency of the algorithm.
 
-It turns out that $\xi$ can be written as a real trigonometric polynomial of degree $6$ in the format given by \autoref{eq:trig_poly_2}, which implies that it can have up to $12$ distinct roots.
+Back on \autoref{chapter:definitions} real trigonometric polynomials were introduced.
+It was stated that a $n$-degree polynomial can have up to $2n$ distinct roots.
+It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2} which implies that it can have up to $12$ distinct roots.
  To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}.
@@
 For that reason, we discuss two ways of converting $\xi$ into a polynomial in this section.
-Symbolic computing was used to compute the polynomials, in practice an external Python library called SymPy was utilized (see \citeonline{sympy} for more details).
+Symbolic computing was used to compute the polynomials, the Python external library called SymPy was utilized (see \citeonline{sympy} for more details).
 
@@
 The second approach is based on a idea published on \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials into univariate complex polynomials in order to obtain its roots using the companion matrix scheme.
-Also, in \citeonline{weidner} it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
+This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial--more details about this can be found in \citeonline{weidner} where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
 
@@
 
-It is possible to show that with that substitution and changing the variable to $z=e^{i\theta}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$, with $\mathbb{S}$ being the unit circle ($\mathbb{S} = \{z \in \mathbb{C} : |z|=1\}$):
-
+It is possible to show that with that substitution and changing the variable to $z=e^{i\theta}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$, with $\mathbb{S}$ being the unit complex circle ($\mathbb{S} = \{z \in \mathbb{C} : |z|=1\}$):
 \begin{equation}
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-Even though $g$ is not a polynomial, it is easy to obtain one from it.
-Firstly, the negative exponentials need to be shifted, this can be done by just multiplying $g$ by $z^6$.
-Secondly, the domain cannot be restricted to the unit circle, so we define $h : \mathbb{C} \mapsto \mathbb{C}$ as:
+As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, the function $g'(\theta)=g(e^{i\theta})$ and the function $\xi$ are equivalent since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
+
+Now there is only two things preventing $g$ from being a polynomial: firstly, $z$ shows up with negative exponents up to $-6$, secondly its domain is the unit circle, not the whole complex set $\mathbb{C}$.
+The first issue can be fixed by multiplying $g$ by $z^6$, note that this does not create further problems as $0\not\in \mathbb{S}$.
+The second issue is removed by extending the domain to $\mathbb{C}$, and considering only roots that lie on $\mathbb{S}$, notice also that no roots can go missing as $\mathbb{S} \subset \mathbb{C}$.
+Finally, the polynomial $h : \mathbb{C} \mapsto \mathbb{C}$ is defined as follows:
 \begin{equation}
@@
 
-Then, by its definition is possible to see that every root of $g$ is also a root of $h$.
-Conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$--or $|\hat{z}|=1$--is also a root of $g$.
-Naturally, the angle of a root $\hat{z}$ of $g$ is a root of $\xi$ by Euler's Formula.
+By its definition is possible to see that every root of $g$ is also a root of $h$, and conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$ is also a root of $g$.
+Naturally, given a root $\hat{z}$ of $g$, the angle of $\hat{z}$ is a root of $\xi$ by Euler's Formula used in the substitution $z=e^{i\theta}$.
 
-It is possible to make another reduction to obtain a degree-$6$ polynomial from $h$ whose roots form a superset of the roots of $g$.
-As it has been mentioned on this chapter, an ellipse is symmetric with respect to its own axis.
-This means $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$\footnote{$\xi$ is only defined over $[0, \pi)$, so this equality is not actually valid.}.
+It is possible to make another reduction to obtain a degree-$6$ polynomial, lowering in half the number of rows of the companion matrix utilized on obtaining the roots of $h$. 
+As it has been mentioned before, an ellipse is symmetric with respect to its own axis.
+This means that $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$.
 On \autoref{chapter:definitions}, it was stated that the angle of $z$ and $-z$ has the same symmetry with each other as an ellipse's angle of rotation:
@@
 It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe for future work it can be used for further improvements.
-Analyzing the polynomials produced for several instances, the following seems to true:
+Analyzing the polynomials produced for several instances, the following seems to be true:
 \begin{equation}
-c_k = \hat{c_{6-k}},
+c_k = \overline{c_{6-k}},
 \end{equation}

### 2019-12-13 defesa/tex/chapter/definicoes.tex
wip

@@
 
-Also, the coverage region is determined by just changing the equality to a inequality as follows
+Also, the coverage region is determined by just changing the equality to an inequality as follows:
 
@@
 Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
-Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
+Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows:
 

### 2019-12-13 defesa/tex/chapter/e3p.tex
wip

@@
 
+\subsection{Real polynomial}
+
 The first attempt was using the identity $x = \tan{\frac{\theta}{2}}$ from which it is possible to construct a $12$-degree polynomial.
@@
 
-The second approach is based on a idea published on \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials into univariate complex polynomials in order to obtain its roots using the companion matrix scheme.
+\subsection{Complex polynomial}
+
+The second approach is based on a idea published on \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials in order to obtain its roots using the companion matrix scheme.
 This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial--more details about this can be found in \citeonline{weidner} where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
-
 \begin{align}\label{eq:complex_trig}
@@
 
-Now there is only two things preventing $g$ from being a polynomial: firstly, $z$ shows up with negative exponents up to $-6$, secondly its domain is the unit circle, not the whole complex set $\mathbb{C}$.
+Now there is only two things preventing $g$ from being a polynomial: firstly, $z$ shows up with negative exponents (up to $-6$); secondly its domain is the unit circle $\mathbb{S}$, not the whole complex set $\mathbb{C}$.
 The first issue can be fixed by multiplying $g$ by $z^6$, note that this does not create further problems as $0\not\in \mathbb{S}$.
-The second issue is removed by extending the domain to $\mathbb{C}$, and considering only roots that lie on $\mathbb{S}$, notice also that no roots can go missing as $\mathbb{S} \subset \mathbb{C}$.
-Finally, the polynomial $h : \mathbb{C} \mapsto \mathbb{C}$ is defined as follows:
+The second issue is removed by simply extending the domain from $\mathbb{S}$ to $\mathbb{C}$, as $\mathbb{S} \subset \mathbb{C}$, roots outside the unit circle could appear which requires a further check for every root that is found.
+Finally, from $g$, the polynomial $h : \mathbb{C} \mapsto \mathbb{C}$ is defined as follows:
 \begin{equation}
@@
 \end{equation}
+By its definition it is possible to see that every root of $g$ is also a root of $h$, and conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$, is also a root of $g$.
+Lastly, every root of $g$ will correspond to a root of $\xi$ though their angles on the unit circle.
 
-By its definition is possible to see that every root of $g$ is also a root of $h$, and conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$ is also a root of $g$.
-Naturally, given a root $\hat{z}$ of $g$, the angle of $\hat{z}$ is a root of $\xi$ by Euler's Formula used in the substitution $z=e^{i\theta}$.
+\subsubsection{Further improvements}
 
-It is possible to make another reduction to obtain a degree-$6$ polynomial, lowering in half the number of rows of the companion matrix utilized on obtaining the roots of $h$. 
-As it has been mentioned before, an ellipse is symmetric with respect to its own axis.
-This means that $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$.
-On \autoref{chapter:definitions}, it was stated that the angle of $z$ and $-z$ has the same symmetry with each other as an ellipse's angle of rotation:
+It is possible to make another reduction to obtain a degree-$6$ polynomial, this can lower the size of the companion matrix utilized on obtaining the roots of $h$ from $12^2=144$ to $6^2=36$.
+As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
+In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
+On the other hand, on \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
 \begin{equation*}
@@
 From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$.
-This implies that $h$ is, in fact an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
+This implies that $h$ is, in fact, an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
 \begin{align}

### 2019-12-15 defesa/tex/chapter/definicoes.tex
wip

--- 2019-12-11 defesa/tex/chapter/definicoes.tex
@@
 \end{equation}
-
-\noindent The elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
+The elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
 This matrix can be seen as a linear transformation of the Euclidean norm.
@@
 \end{equation}
-
-\noindent where $Q$ is a $2$ by $2$ positive definite matrix.
-
-The elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.
+where $Q$ is a $2$ by $2$ positive definite matrix. Note that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.
 
@@
 An ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section. 
-As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}.
+They get this name because conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}.
 From that definition, an equation which describes any conic section is given as follows
-
 \begin{equation}\label{equation:quadratic_form}
@@
 \end{equation}
-
-\noindent where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$.
-
-To distinguish an ellipse from the other conic sections given an instance of \autoref{equation:quadratic_form}, the condition $4AC - B^2>0$ must be verified \cite{ayoub}.
+where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$.
+Distinguishing an ellipse from the other conic sections ca be done using the condition given by \autoref{eq:conic_ellipse}.
+More details about conic sections can be found in \citeonline{ayoub}.
+\begin{equation}\label{eq:conic_ellipse}
+4AC - B^2>0.
+\end{equation}
 
 Assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
-
+with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
 \[
@@
 \]
-
 Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse.
@@
  \end{equation}
+where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.
 
-\noindent where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.
-
-Also, the coverage region is determined by just changing the equality to a inequality as follows
-
+Also, the coverage region is determined by just changing the equality to an inequality as follows
 \begin{equation}\label{equation:cover_pellipse}
@@
 Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
-
 \begin{equation}\label{eq:parametric_ellipse}
@@
 \end{equation}
-
-No equivalent disk-circle wording exists for ellipses, this could be a source of ambiguity in the text, that is why a note for the reader was judged to be necessary.
-Throughout this work an ellipse will represent the set of points that satisfy \autoref{def:ellipse}.
-In some places, though, with prior clarification, we will denote as an ellipse the set of points that are covered by the ellipse itself.
-For example, when we define $\Pp \cap E$ as the set of points in $\Pp$ that are covered by $E$, we are implicitly calling $E$ the set of points that are covered by the ellipse itself as it is defined by \autoref{def:ellipse}.
 
@@
 \dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1.
+\end{equation}
+
+The word ellipse can be a source of ambiguity, that is because it is not clear if we are talking about its border or its coverage area.
+To make things clear, throughout the text, ellipses will refer only to the border and for its coverage area we introduce a new notation: for any ellipse $E$ (parallel or not), its coverage region is defined as
+\begin{equation}
+cov(E).
 \end{equation}

### 2019-12-16 defesa/tex/chapter/definicoes.tex
wip

@@
 Nonetheless, a simpler equation is going to be used here.
-Besides the center, the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in [0, \pi]$ is given.
+Besides the center, the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given.
 This angle represents the angle between the $x$-axis and the major-axis of the ellipse.
@@
 A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations.
-Reversing these transformations produces the following equation for a non-axis-parallel ellipse:
+Reversing these transformations produces the following equation for a non-axis-parallel ellipse
 \begin{equation}\label{eq:rotated_ellipse}
@@
 \end{equation}
-Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in [0, \pi)$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co}.
+Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in \R$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co} as follows
 \begin{equation}\label{eq:rotated_ellipse_co}
@@
 
-The word ellipse can be a source of ambiguity, that is because it is not clear if we are talking about its border or its coverage area.
-To make things clear, throughout the text, ellipses will refer only to the border and for its coverage area we introduce a new notation: for any ellipse $E$ (parallel or not), its coverage region is defined as
-\begin{equation}
-cov(E).
-\end{equation}
+An example of rotated ellipse can be seen on \autoref{fig:rotated_ellipse}. The dashed lines represent its major and minor axes which are rotated with respect to the coordinate axes.
+On this picture, it is also displayed the symmetry of rotation angles regarding the ellipse's axes.
+From that, it can be seen that any angle of rotation $\theta$ is equivalent--as it produces the same ellipse--to the angle of rotation $\theta + k\pi$, with $k \in \mathbb{Z}$.
+Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.
+
+\begin{figure}[H]
+	\centering
+
+	\caption{A rotated ellipse.}
+	\includegraphics[scale=.5]{tex/figures/rotated_ellipse}
+	\fautor
+	\label{fig:rotated_ellipse}
+\end{figure}
+
+\subsection{Notation}
+
+As stated by \autoref{def:ellipse}, the word ellipse is used to refer to the set of points that satisfies the equality equation, which can be seen as the border of an ellipse's coverage area.
+For this work, however, it is more convenient to refer directly to the coverage area of an ellipse and add a notation to express its border.
+For example, let $E$ be an ellipse's coverage area, and $\Pp \subset \R^2$ a set of points, then $E \cap \Pp$ denotes the set of points from $\Pp$ inside the coverage area of that ellipse.
+When we need to refer specifically to the border of $E$, we use the boundary operator: $\partial E$.
 
@@
 In this work, we are mostly interested in univariate polynomials defined over the complex numbers.
-
-A function $p_n: \mathbb{C} \mapsto \mathbb{C}$ is a $n$-degree polynomial if it can be written as:
+A function $p_n: \mathbb{C} \mapsto \mathbb{C}$ is a $n$-degree polynomial if it can be written as
 \begin{equation}\label{eq:poly}
@@
  In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial.
-For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by:
+For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by
  \begin{equation}
@@
 The same definition found in \citeonline[p.~150]{powell} for real trigonometric polynomials is given here.
-They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by:
+They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by
 \begin{equation}\label{eq:trig_poly}
@@
 An important property is stated in \citeonline[p.~150]{powell}, it says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$.
-It also says that a function written in the format:
+It also says that a function written in the format
 $$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta} & \quad j, k \in \mathbb{Z}_+ \end{array},$$
-can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial:
+can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial
 \begin{equation}\label{eq:trig_poly_2}

### 2019-12-17 defesa/tex/chapter/definicoes.tex
wip

@@
     \caption{The ellipse as a parametric curve.}
-    \input{tex/figures/ellipse_definition.tex}
+%    \input{tex/figures/ellipse_definition.tex}
+   	\includegraphics[scale=.4]{tex/figures/ellipse_definition.pdf}
     \fautor
@@
 
-A non-axis-parallel ellipse centered at $c\in\R^2$ can also be described by \autoref{def:ellipse}.
+A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}.
 Nonetheless, a simpler equation is going to be used here.
-Besides the center, the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given.
-This angle represents the angle between the $x$-axis and the major-axis of the ellipse.
+Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given.
+This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse} where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.
 
-A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations.
+A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations: translation, so its center is at $(0, 0)$, then rotation so its major-axis is parallel to the $x$-axis.
 Reversing these transformations produces the following equation for a non-axis-parallel ellipse
@@
 \end{equation}
-Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in \R$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co} as follows
+The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation, which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$
 \begin{equation}\label{eq:rotated_ellipse_co}
@@
 
-An example of rotated ellipse can be seen on \autoref{fig:rotated_ellipse}. The dashed lines represent its major and minor axes which are rotated with respect to the coordinate axes.
-On this picture, it is also displayed the symmetry of rotation angles regarding the ellipse's axes.
-From that, it can be seen that any angle of rotation $\theta$ is equivalent--as it produces the same ellipse--to the angle of rotation $\theta + k\pi$, with $k \in \mathbb{Z}$.
+Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}.
+The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent--they produce the same ellipse.
+This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$.
 Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.
@@
 
-	\caption{A rotated ellipse.}
-	\includegraphics[scale=.5]{tex/figures/rotated_ellipse}
+	\caption{The rotated ellipse.}
+	\includegraphics[scale=.38]{tex/figures/rotated_ellipse}
 	\fautor

### 2019-12-17 defesa/tex/chapter/e3p.tex
wip

@@
 As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way.
-We try to give a review of some of those going through the issues with the failing approaches, at the end we propose a $\bigO(1)$ algorithm that finds every solution of the problem and run some numerical experiments to show the precision of the found solutions.
+We try to give a review of some of those, going through the issues with the failing ones.
+At the end we propose a $\bigO(1)$ algorithm that finds every solution of the problem, and also run some experiments to analyze efficiency in terms of numerical precision and CPU time.
 
-We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
-A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
-The goal is to develop a method to find every solution of E3PNT.
+We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, the coverage area of an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
+A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
+Because of its application on \autoref{chapter:ellipses_n}, every solution of E3PNT must be encountered.
+This is a vital piece of information which makes this problem more challenging.
 
@@
 
-After that transformation, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$, such that the circle has radius $b$.
+After that transformation, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$, such that the circle's radius is $b$.
 Therefore, the only unknown of this problem is the angle of rotation.

### 2019-12-18 defesa/tex/chapter/introducao.tex
wip

Two main types of optimal covering problems can be found in the literature: the Minimum Cover Problem, also known as just Set Cover Problem, and the Maximal Covering Problem \cite{karatas}.

One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic. 
Given a demand set and a collection of subsets of the demand set, the problem asks what is the minimum number of elements from the collection of subsets needed to cover the whole demand set. One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title. In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}. In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used. Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}, and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it. A very complete survey of developments on this area can be found in \citeonline{mclp_review}.

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximum Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on a network. Instead, on PMCLP the demand set and the facilities are located in $\R^2$ having a facility's coverage area be defined by a distance function. 
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP, and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, so the optimal solution could be found. From the CLS, a graph was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which is described here on \autoref{chapter:pmclp}.

Also, some variations of PMCLP can be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance; in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{numerical experiments for up to $3000$ points} PMCLP was proposed; and in \citeonline{bansal} a version with partial coverage and demand and facility zones represented by rectangles was introduced.

The Euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}. 
Early works only tackled the one-disk version of the problem, in \citeonline{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
The $m$ unit disks maximum covering was studied in \citeonline{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$. To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
Additionally, in \citeonline{aronov:2008} one-disk maximum covering is proven to be 3SUM-HARD. This means that maximizing the amount of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.

Planar maximum covering with ellipses differs from its disks counterpart only in the shape of the facility's coverage area. The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.

Only two articles have been found published in the literature that study this problem. In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem. For some instances the method took too long and did not find an optimal solution. For this reason a heuristic method was developed using a technique called Simulated Annealing. Solutions for the instances that timed-out with the first method were then obtained. The problem was further explored in \citeonline{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances which the first method could not. Also, in \citeonline{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances, and a heuristic method were proposed for it. Despite the similarities, none of the works cited above base their development on the maximum covering with disks algorithms found in the literature.

This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work. Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

### 2019-12-18 defesa/tex/chapter/e3p.tex
b1

@@
 We try to give a review of some of those, going through the issues with the failing ones.
-At the end we propose a $\bigO(1)$ algorithm that finds every solution of the problem, and also run some experiments to analyze efficiency in terms of numerical precision and CPU time.
+At the end we propose an algorithm that takes around $6^3$ operations to compute every solution of the problem.
+Also, we run some experiments to analyze its efficiency in terms of numerical precision and CPU time.
 
@@
 A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
-Because of its application on \autoref{chapter:ellipses_n}, every solution of E3PNT must be encountered.
-This is a vital piece of information which makes this problem more challenging.
+As a last remark, because of its application on \autoref{chapter:ellipses_n}, we need to encounter every solution of E3PNT, this requirement, of course, makes the problem more challenging.
 
 \section{Transforming the problem}
+
+Initially, E3PNT is a problem with $3$ unknown variables: $q_x, q_y, $ and $\theta$.
+In this section, we transform E3PNT into the problem of finding the roots of an univariate function using the known problem of determining the circumcenter of a triangle.
+We also shown that the number of solutions of E3PNT is at most $6$.
 
@@
 \end{equation}
-Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm, with $n=6$, can be constructed for E3P.
+Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm can be constructed for E3P.
+Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm.
 

### 2019-12-18 defesa/tex/chapter/introducao.tex
b1

@@
-Two main types of optimal covering problems can be found in the literature: the Minimum Cover Problem, also known as just Set Cover Problem, and the Maximal Covering Problem \cite{karatas}.
+aTwo main types of optimal covering problems can be found in the literature: the Minimum Cover Problem, also known as just Set Cover Problem, and the Maximal Covering Problem \cite{karatas}.
 
@@
 The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}.
-This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title.
-In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
+This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \cite{church:1974}.
 In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used.
-Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}, and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it.
-A very complete survey of developments on this area can be found in \citeonline{mclp_review}.
+Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming \cite{church:1974}, and heuristic methods \cite{revelle:2008} have been proposed to solve it.
 
-In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximum Covering Location Problem} was introduced.
-Unlike its predecessor, this version of the problem was not defined on a network.
-Instead, on PMCLP the demand set and the facilities are located in $\R^2$ having a facility's coverage area be defined by a distance function.
-Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP, and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
-This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, so the optimal solution could be found.
-From the CLS, a graph was built on which MCLP could be applied.
-Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which is described here on \autoref{chapter:pmclp}.
-
-Also, some variations of PMCLP can be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance; in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{numerical experiments for up to $3000$ points} PMCLP was proposed; and in \citeonline{bansal} a version with partial coverage and demand and facility zones represented by rectangles was introduced.
-
+In \cite{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced.
+This version of the problem was not defined on a network, instead the demand set and the facilities are located in $\R^2$ having the coverage area of a facility be defined by a distance function.
+PMCLP is said to have been studied under Euclidean and rectilinear distance functions \cite{younies}.
 The Euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
-Early works only tackled the one-disk version of the problem, in \citeonline{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
-The $m$ unit disks maximum covering was studied in \citeonline{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
+Early works only tackled the one-disk version of the problem, in \cite{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \cite{drezner}.
+The $m$ unit disks maximal covering was studied in \cite{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
 To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
-Additionally, in \citeonline{aronov:2008} one-disk maximum covering is proven to be 3SUM-HARD.
+Additionally, in \cite{aronov:2008} one-disk maximal covering is proven to be 3SUM-HARD.
 This means that maximizing the amount of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.
 
-Planar maximum covering with ellipses differs from its disks counterpart only in the shape of the facility's coverage area.
+Planar maximal covering with ellipses differs from its disks counterpart only in the shape of the facility's coverage area.
 The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.
-
 Only two articles have been found published in the literature that study this problem.
-In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
+In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
 For some instances the method took too long and did not find an optimal solution.
@@
 Solutions for the instances that timed-out with the first method were then obtained.
-The problem was further explored in \citeonline{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances which the first method could not.
-Also, in \citeonline{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances, and a heuristic method were proposed for it.
-Despite the similarities, none of the works cited above base their development on the maximum covering with disks algorithms found in the literature.
+The problem was further explored in \cite{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances which the first method could not.
+Also, in \cite{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances, and a heuristic method were proposed for it.
+Despite the similarities, none of the works cited above base their development on the maximal covering with disks algorithms found in the literature.
 
-This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work.
+This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximal covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximal covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work.
 Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

### 2019-12-19 defesa/tex/chapter/introducao.tex
wip

--- 2019-12-18 defesa/tex/chapter/introducao.tex
@@
 Instead, on PMCLP the demand set and the facilities are located in $\R^2$ having a facility's coverage area be defined by a distance function.
-Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP, and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
+Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
 This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, so the optimal solution could be found.
-From the CLS, a graph was built on which MCLP could be applied.
+From the CLS, a network was built on which MCLP could be applied.
 Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which is described here on \autoref{chapter:pmclp}.
 
-Also, some variations of PMCLP can be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance; in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{numerical experiments for up to $3000$ points} PMCLP was proposed; and in \citeonline{bansal} a version with partial coverage and demand and facility zones represented by rectangles was introduced.
+Also, some variations of PMCLP can be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance; in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{Numerical experiments were done for up to $3000$ points.} PMCLP was proposed; and in \citeonline{bansal} a version with partial coverage and demand and facility zones represented by rectangles was introduced.
 
-The Euclidean norm PMCLP, which has a lot of results that can be applied for the elliptical PMCLP, is also found in the literature as the problem of maximization of points covered by a fixed number of unit disks \cite{cabello:2006}.
-Early works only tackled the one-disk version of the problem, in \citeonline{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
-The $m$ unit disks maximum covering was studied in \citeonline{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
+The classical PMCLP under Euclidean distance is also found in the literature as the \sigla{MCD}{Maximum Covering by Disks} problem. 
+Early works only tackled the one-disk version of it.
+In \citeonline{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
+The $m$ disks version of MCD was studied in \citeonline{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
 To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
@@
 
-Planar maximum covering with ellipses differs from its disks counterpart only in the shape of the facility's coverage area.
-The main motivation to study this modified version is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.
+Finally, the problem studied by this work is referred to as the \sigla{PMCE}{Planar Maximum Covering by Ellipses} problem.
+As its name suggests, this version of PMCLP differs from its disks counterpart only in the shape of the facility's coverage area.
+Additionally, the version where the ellipses can be freely rotated is also studied by this work--note that this is actually a slightly bigger modification of PMCLP, as not only the location for the facilities must be determined, but also their angle of rotation.
+This problem will be referred to as the \sigla{PMCER}{Planar Maximum Covering by Ellipses with Rotation}.
+The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.
 
@@
 
-This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work.
+The main results of this work are found in \autoref{chapter:ellipses_n} where a new algorithm for the version of the elliptical PMCLP where the ellipses can be freely rotated is developed.
+The proposed algorithm has a runtime complexity of $\bigO(n^{3m})$ and one of its most important steps is finding every solution of a not-previously-known problem introduced in \autoref{chapter:e3p} which also presents an algorithm for it.
+The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work.
 Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

### 2019-12-19 defesa/tex/chapter/introducao.tex
wip

@@
 In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
-In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used.
+In this first study, it was defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used.
 Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}, and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it.
@@
 From the CLS, a network was built on which MCLP could be applied.
-Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which is described here on \autoref{chapter:pmclp}.
+Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which will be described here on \autoref{chapter:pmclp}.
 

### 2019-12-19 defesa/tex/chapter/introducao.tex
wip

--- 2019-12-19 defesa/tex/chapter/introducao.tex
@@
-Two main types of optimal covering problems can be found in the literature: the Minimum Cover Problem, also known as just Set Cover Problem, and the Maximal Covering Problem \cite{karatas}.
+The Minimum Cover Problem --also known as just the Set Cover Problem--, and the Maximal Covering Problem are the two main types of optimal covering problems found in the literature \cite{karatas}.
 
 One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic.
-Given a demand set and a collection of subsets of the demand set, the problem asks what is the minimum number of elements from the collection of subsets needed to cover the whole demand set.
+Given a demand set along with a collection of subsets of the demand set.
+The problem is then to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set.
 One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.
@@
 In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
-In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used.
-Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}, and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it.
-A very complete survey of developments on this area can be found in \citeonline{mclp_review}.
+In this first study, the problem was defined on a network and a set of demand nodes, a subset of the network's vertices; and a set of facilities, each with its coverage radius is given. 
+A demand node was considered covered if it was within any facility's coverage radius. The objective was then to maximize the demand set's coverage by choosing vertices to place every facility.
+
+Just like the Minimum Cover problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}; and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it.
+A very complete survey of developments in this area can be found in \citeonline{mclp_review}.
 
@@
 Unlike its predecessor, this version of the problem was not defined on a network.
-Instead, on PMCLP the demand set and the facilities are located in $\R^2$ having a facility's coverage area be defined by a distance function.
+Instead, on PMCLP the demand set and the facilities are located in $\R^2$ and a facility's coverage area is determined by a distance function.
 Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
-This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, so the optimal solution could be found.
+This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found.
 From the CLS, a network was built on which MCLP could be applied.
-Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which is described here on \autoref{chapter:pmclp}.
+Generating the CLS specifically for the case of Euclidean distance will be described here on \autoref{chapter:pmclp}.
 
-Also, some variations of PMCLP can be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance; in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{Numerical experiments were done for up to $3000$ points.} PMCLP was proposed; and in \citeonline{bansal} a version with partial coverage and demand and facility zones represented by rectangles was introduced.
+Furthermore, some variations of PMCLP can also be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance, in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{Numerical experiments were done for up to $3000$ points.} PMCLP was proposed, and in \citeonline{bansal} a version with partial coverage and rectangular demand and facility zones was introduced.
 
-The classical PMCLP under Euclidean distance is also found in the literature as the \sigla{MCD}{Maximum Covering by Disks} problem. 
+PMCLP under Euclidean distance is also found in the literature as the \sigla{MCD}{Maximum Covering by Disks} problem.
 Early works only tackled the one-disk version of it.
@@
 Additionally, in \citeonline{aronov:2008} one-disk maximum covering is proven to be 3SUM-HARD.
-This means that maximizing the amount of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.
+This means that maximizing the number of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.
 
-Finally, the problem studied by this work is referred to as the \sigla{PMCE}{Planar Maximum Covering by Ellipses} problem.
-As its name suggests, this version of PMCLP differs from its disks counterpart only in the shape of the facility's coverage area.
-Additionally, the version where the ellipses can be freely rotated is also studied by this work--note that this is actually a slightly bigger modification of PMCLP, as not only the location for the facilities must be determined, but also their angle of rotation.
-This problem will be referred to as the \sigla{PMCER}{Planar Maximum Covering by Ellipses with Rotation}.
-The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptical shaped coverage area, so in order to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by its signal, an elliptical PMCLP is better suited \cite{canbolat}.
+Two versions of PMCLP are studied in this work, both of them related to ellipses.
+The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximum Covering by Ellipses}.
+This version does not allow the ellipses to rotate, so basically it only differs from its disks counterpart in the shape of the facility's coverage area.
+The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximum Covering by Ellipses with Rotation}.
+This version of the problem had no restriction on the rotation of ellipses--note that this is a slightly bigger modification of PMCLP compared to the first one, as not only the location for the facilities must be determined, but also their angle of rotation.
+The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.
 
@@
 In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
-For some instances the method took too long and did not find an optimal solution.
-For this reason a heuristic method was developed using a technique called Simulated Annealing.
+For some instances, the method took too long and did not find an optimal solution.
+For this reason, a heuristic method was developed using a technique called Simulated Annealing.
 Solutions for the instances that timed-out with the first method were then obtained.
-The problem was further explored in \citeonline{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances which the first method could not.
-Also, in \citeonline{andreta}, a version of the problem where every ellipse can be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances, and a heuristic method were proposed for it.
-Despite the similarities, none of the works cited above base their development on the maximum covering with disks algorithms found in the literature.
+The problem was further explored in \citeonline{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances, which the first method could not.
+Also, in \citeonline{andreta}, the version of the problem where the ellipses could be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances; and a heuristic method were proposed for it.
+Despite the similarities, none of the works cited above base their development on the maximum covering by disks algorithms found in the literature.
 
 The main results of this work are found in \autoref{chapter:ellipses_n} where a new algorithm for the version of the elliptical PMCLP where the ellipses can be freely rotated is developed.
-The proposed algorithm has a runtime complexity of $\bigO(n^{3m})$ and one of its most important steps is finding every solution of a not-previously-known problem introduced in \autoref{chapter:e3p} which also presents an algorithm for it.
+The proposed algorithm has a runtime complexity of $\bigO(n^{3m})$ and one of its most important steps is finding every solution of a not-previously-known problem.
+In \autoref{chapter:e3p}, this problem is introduced and an algorithm for it is presented.
 The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work.

### 2019-12-20 defesa/tex/chapter/introducao.tex
wip

@@
 In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
-In this first study, the problem was defined on a network and a set of demand nodes, a subset of the network's vertices; and a set of facilities, each with its coverage radius is given. 
-A demand node was considered covered if it was within any facility's coverage radius. The objective was then to maximize the demand set's coverage by choosing vertices to place every facility.
+In this first study, the author defined the problem for graphs, such that the demand set is a subset of the graph's vertices.
+Given a facility set where each facility has a coverage radius, the problem asks to choose vertices to place the facilities to maximize the coverage of the demand set.
 

### 2019-12-21 defesa/tex/chapter/introducao.tex
wip

@@
 In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
-In this first study, the author defined the problem for graphs, such that the demand set is a subset of the graph's vertices.
-Given a facility set where each facility has a coverage radius, the problem asks to choose vertices to place the facilities to maximize the coverage of the demand set.
+
+In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices.
+Given a facility set where each facility has a coverage radius, the objective was then to maximize the coverage of the demand set by choosing vertices to place each facility.
 

### 2019-12-23 defesa/tex/chapter/e3p.tex
wip

@@
 
-We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, the coverage area of an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
-A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
-As a last remark, because of its application on \autoref{chapter:ellipses_n}, we need to encounter every solution of E3PNT, this requirement, of course, makes the problem more challenging.
+\section{Definition}
+
+We call the problem introduced in this section \sigla{E3PNT}{Ellipse by Three points}.
+An instance of it is given by three points $u, v, w \in \R^2$ and the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, with $a > b$.
+
+Let $E$ be the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
+As a last remark, because of its application on \autoref{chapter:ellipses_n}, it is only useful a method would only be useful to our case if it can encounter every solution of E3PNT.
+This requirement, of course, makes the problem more challenging.
 
@@
 This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle.
-This process can be parametrized by the angle of rotation of the points, as described by \autoref{eq:trpnts}, and because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.
+This process can be parametrized by the angle of rotation of the points, as described by
 
-\begin{figure}
-	\centering
-	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics{tex/figures/scripts/circumscribed-circle}
-	\fautor
-	\label{fig:circumscribed-circle}
-\end{figure}
 \begin{equation}\label{eq:trpnts}
@@
 p_y
-\end{array}\right].
+\end{array}\right],
 \end{equation}
+because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.
+
+\begin{figure}
+	\centering
+	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
+	\includegraphics{tex/figures/scripts/circumscribed-circle}
+	\fautor
+	\label{fig:circumscribed-circle}
+\end{figure}
 
@@
 It turns out that for three non-colinear fixed points, there is always an unique circumscribed circle.
-Also, finding this unique circle can be done analytically, hence its radius can be easily computed and compared to $b$ when an angle is given.
-Let $A(\theta)$ be the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$--note that the transformation does not preserve distance or area.
-Then, the radius $R$ of the circumscribed circle is given by \autoref{eq:circumscribed_circle} \cite[p.~189]{johnson1960}.
+Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the expression
+\begin{equation}\label{eq:circumscribed_circle}
+R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)},
+\end{equation}
+with $A(\theta)$ being the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$--note that the transformation does not preserve distance or area.
+For more details about \autoref{eq:circumscribed_circle} see \citeonline[p.~189]{johnson1960}.
 
-\begin{equation}\label{eq:circumscribed_circle}
-R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)}.
+Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as 
+\begin{equation}\label{eq:circumscribed_circle_b}
+\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
 \end{equation}
+in such a way that its zeros determine solutions for E3PNT.
 
-Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b} in such a way that its zeros determine solutions to the E3PNT's instance.
-Two questions about $\xi(\theta)$ that arise are: is its set of roots finite?
-And, can they be found analytically?
-
-\begin{equation}\label{eq:circumscribed_circle_b}
-\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2.
-\end{equation}
+Lastly, two questions about $\xi(\theta)$ that arise are: is its set of roots finite? And, if its set of roots is finite, can they be found analytically?
 
@@
 Of course doing that is only possible for a finite number of solutions.
-Also, discovering a bound for that is essential for determining the efficiency of the algorithm.
+Also, given that it is limited, discovering a bound for it is essential for determining the efficiency of the algorithm.
 
@@
 It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2} which implies that it can have up to $12$ distinct roots.
- To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}.
-It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared distances.
-As $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
+ To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form
  \begin{align}\label{eq:dd}
@@
  		w_x\frac{b}{a}\cos\theta + w_y\frac{b}{a}\sin\theta&w_y\cos\theta - w_x\sin\theta
-	\end{array}\right)^2
+ 	\end{array}\right)^2.
  \end{align}
+  It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared lengths of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$.
+This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
 
@@
 
-The idea of this approach was to use the six-parameter conic equation to represent an ellipse. This equation is given by \autoref{eq:gen_ellipse}.
-
+The idea of this approach was to use the six-parameter conic equation to represent an ellipse. This equation is given by
 \begin{equation}\label{eq:gen_ellipse}
@@
 Then, we end up with two variables, $A$ and $C$, and still need to impose that the final equation represents an ellipse and its major-axis and minor-axis have the predefined value.
-Let $\Delta=4AC-B^2=4AC-1$, \autoref{eq:gen_ellipse_a} and \autoref{eq:gen_ellipse_b} for both major-axis and minor-axis respectively, assuming $F=0$.
-
+Let $\Delta=4AC-B^2=4AC-1$, and assume $F=0$, then the expressions for both major-axis and minor-axis respectively are
 \begin{align}\label{eq:gen_ellipse_a}
 a^2 = \dfrac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C - \sqrt{1 + (A-C)^2}}\\
-\label{eq:gen_ellipse_b}b^2 = \frac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C + \sqrt{1 + (A-C)^2}}
+\label{eq:gen_ellipse_b}b^2 = \frac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C + \sqrt{1 + (A-C)^2}}.
 \end{align}
-
 These two equations define two curves in $\R^2$ with $A$ and $C$ being the chosen variables.
@@
 For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered.
-The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n$ by $n$ matrix.
+The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n\times n$ matrix.
 
@@
 Chebyshev polynomials are widely used in Numerical Analysis in areas like numerical integration, polynomial approximation, and ordinary and partial differential equations.
-They are also very useful in practice and are present in extension libraries in Python and MATLAB.
+They are also very useful in practice and are present in extension libraries in Python, MATLAB and C.
 
@@
 
-We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind, and it is defined as follows:
-
+We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind, and it is defined as
 \begin{equation}
-T_n(x) = \cos({n\arccos x})
+T_n(x) = \cos({n\arccos x}).
 \end{equation}
-
-It is important to mention that this definition can be extended to the whole real line. Using some trigonometric identities, $T_n$ can also be expressed as a recurrence relation:
-
+It is important to mention that this definition can be extended to the whole real line. Using some trigonometric identities, $T_n$ can also be expressed as a recurrence relation
 \begin{equation}
@@
 An important property worth bringing up is that Chebyshev polynomials are orthogonal and form a basis for the polynomial space.
-This implies that any $p_n$ of degree up to $n$ can be expressed as a truncated Chebyshev series:
-
+This implies that any $p_n$ of degree up to $n$ can be expressed as a truncated Chebyshev series
 \begin{equation}\label{eq:chebseries}
@@
 \begin{equation}
-r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|.
+r_n = \max_{0 \le \theta < \pi} |f_n(\theta) - \xi(\theta)|.
 \end{equation}
@@
 Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$.
-As the angle of $-\sqrt{\hat{y}}$ is not between $[0, pi)$ we can ignore it.
+As the angle of one of the roots will not be between $[0, \pi)$ we can ignore on of them.
 Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
@@
 Analyzing the polynomials produced for several instances, the following seems to be true:
-\begin{equation}
+\begin{equation}\label{eq:palindromic_pol}
 c_k = \overline{c_{6-k}},
 \end{equation}
-for $k=0, \dots, 6$.
-For now, we do not have any ideas on how it could be proved.
-Nevertheless, this seems to lead somewhere interesting because this condition guarantees that $f$ is a self-reciprocal polynomial which implies that its roots will always come in pairs $(\hat{z}, 1/\hat{z})$.
+for $k=0, \dots, 6$. For now, we neither have any ideas on how \autoref{eq:palindromic_pol} could be proved nor how it could be used for further improving our algorithm.
 

### 2019-12-23 defesa/tex/chapter/introducao.tex
wip

@@
 One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic.
-Given a demand set along with a collection of subsets of the demand set.
-The problem is then to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set.
+Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set.
 One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.
@@
 The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}.
-This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title.
-In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.
-
+This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \citeonline{church:1974}.
 In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices.
-Given a facility set where each facility has a coverage radius, the objective was then to maximize the coverage of the demand set by choosing vertices to place each facility.
+The objective was to maximize the coverage of the demand set by choosing the location of a given facility set on the graph.
+Every facility had a given coverage radius, which meant that after it was placed on the graph, every vertex within that radius would be considered covered.
 
@@
 
-In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximum Covering Location Problem} was introduced.
-Unlike its predecessor, this version of the problem was not defined on a network.
+In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced.
+Unlike its predecessor, this version of the problem was not defined on graphs.
 Instead, on PMCLP the demand set and the facilities are located in $\R^2$ and a facility's coverage area is determined by a distance function.
@@
 Two versions of PMCLP are studied in this work, both of them related to ellipses.
-The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximum Covering by Ellipses}.
+The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximal Covering by Ellipses}.
 This version does not allow the ellipses to rotate, so basically it only differs from its disks counterpart in the shape of the facility's coverage area.
-The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximum Covering by Ellipses with Rotation}.
+The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximal Covering by Ellipses with Rotation}.
 This version of the problem had no restriction on the rotation of ellipses--note that this is a slightly bigger modification of PMCLP compared to the first one, as not only the location for the facilities must be determined, but also their angle of rotation.

### 2019-12-23 defesa/tex/chapter/e3p.tex
wip

@@
 
-\subsection{Chebyshev interpolation}
+\subsection{Chebyshev polynomial}
 
@@
 One of the greatest qualities of Chebyshev polynomials is its numerical stability.
-\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{A polynomial is in the power form or the monomial form if it can be written as $\sum_{j=0}^{n}a_jx^j$} has a condition number that grows exponentially with $n$.
+\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{A polynomial is in the power form or the monomial form if it can be written as $\sum_{j=0}^{n}a_jx^j$.} has a condition number that grows exponentially with $n$.
 On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries}, has a linear condition number bounded by $\sqrt{2}n$.
 
+\subsection{Chebyshev interpolation}
 Polynomial interpolation is a form of approximating a function by a polynomial of degree $n$ that passes through $n+1$ chosen points.
-In fact, this polynomial is unique and it is determined by Lagrange's formula:
-
+In fact, this polynomial is unique and it is determined by Lagrange's formula
 \begin{equation}\label{eq:lagrange}
@@
 That is where Chebyshev interpolation comes in.
-Instead of choosing $n+1$ arbitrary points, the $n+1$ roots of $T_{n+1}$, which are also known as Chebyshev Nodes, are chosen as the interpolation points:
+Instead of choosing $n+1$ arbitrary points, the $n+1$ roots of $T_{n+1}$, which are also known as Chebyshev Nodes, are chosen as the interpolation points.
+The $n+1$ Chebyshev nodes are given by
 \begin{equation}
-x_j = \cos{\left(\dfrac{\pi(k-\frac{1}{2})}{n+1}\right)},
+x_j = \cos{\left(\dfrac{\pi(j-\frac{1}{2})}{n+1}\right)},
 \end{equation}
 for $j=1, \dots, n+1$. This particular choice defeats Runge's phenomenon and provides a convergent approximation. 
-
-Note that, if the domain of the function to be interpolated is defined on a range other than $[-1, 1]$, let us say $[a, b]$, then a transformation can be done to map it to the Chebyshev Nodes' domain:
+Note that, if the domain of the function to be interpolated is defined on a range other than $[-1, 1]$, let us say $[a, b]$, then the transformation
 \begin{equation}
-\hat{x_j} = \frac{a+b}{2} + \frac{b-a}{2}x_j.
+\hat{x_j} = \frac{a+b}{2} + \frac{b-a}{2}x_j
 \end{equation}
+can be done to map it to the Chebyshev Nodes' domain $[-1, 1]$.
 
 Then, the Chebyshev interpolation of a function $f: [a, b] \mapsto \R$ can be determined using Lagrange's formula and the points $\hat{x}_1, \dots, \hat{x}_n$. 
-As it was mentioned, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called Frobenius companion matrix.
+As it was mentioned in \autoref{chapter:definitions}, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called Frobenius companion matrix.
 For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
@@
 Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials, which have great numerical stability.
-Also, Chebyshev-Frobenius matrices have the same property as companion matrices which allows their eigenvalues to be found by a QR decomposition.
-Summing the two steps, a $\bigO(n^2)$ algorithm can be achieved.
+Also, Chebyshev-Frobenius matrices have the same property as companion matrices which allows their eigenvalues to be found by a QR algorithm.
+Summing the two steps, a $\bigO(n^3)$ algorithm can be achieved, with $n$ being the degree of the interpolation.
 
@@
 To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}.
-There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error $r_n$:
+There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error
 \begin{equation}
-r_n = \max_{0 \le \theta < \pi} |f_n(\theta) - \xi(\theta)|.
+r_n = \max_{0 \le \theta < \pi} |f_n(\theta) - \xi(\theta)|,
 \end{equation}
+which measures how far the interpolation is at the point it worst approximates.
 
@@
 
-On \autoref{chapter:definitions} a brief introduction is given on how to get the roots of a polynomial.
+In \autoref{chapter:definitions}, a brief introduction is given on how to get the roots of a polynomial.
 For that reason, we discuss two ways of converting $\xi$ into a polynomial in this section.

### 2019-12-24 defesa/tex/chapter/definicoes.tex
wip

@@
 with $a_0, \dots, a_n \in \mathbb{C}$.
+In this work, when a polynomial is written in the form of \autoref{eq:poly} we say that it is in the power form or in the monomial form, we have these terms for it because we also use a different base to represent polynomials which as a result .
+
 The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots.
@@
 
- In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial.
+ In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial of degree $n$, there exists a companion matrix which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial.
 For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by

### 2019-12-24 defesa/tex/chapter/definicoes.tex
wip

@@
 \end{equation}
-with $a_0, \dots, a_n \in \mathbb{C}$.
-In this work, when a polynomial is written in the form of \autoref{eq:poly} we say that it is in the power form or in the monomial form, we have these terms for it because we also use a different base to represent polynomials which as a result .
+with $a_0, \dots, a_n \in \mathbb{C}$. In this work, when a polynomial is written in the form of \autoref{eq:poly} we say that it is in the power form or in the monomial form.
 
 The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots.
-Fortunately, a numerical approach exists for higher-degree polynomials which in practice works really well.
+Fortunately, a numerical approach exists for higher-degree polynomials which works really well in practice.
 

### 2019-12-24 defesa/tex/chapter/introducao.tex
wip

@@
 
-Just like the Minimum Cover problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}; and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it.
+Just like the Minimum Cover problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming, and heuristic methods have been proposed to solve it.
 A very complete survey of developments in this area can be found in \citeonline{mclp_review}.

### 2019-12-28 defesa/tex/chapter/introducao.tex
wip

@@
 This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \citeonline{church:1974}.
-In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices.
-The objective was to maximize the coverage of the demand set by choosing the location of a given facility set on the graph.
-Every facility had a given coverage radius, which meant that after it was placed on the graph, every vertex within that radius would be considered covered.
+In this first study, the author defined the problem on graphs, and the objective was to maximize the coverage of a demand set, which was a subset of the graph's vertices, by choosing the location of a facility set, which covered any vertex within a given coverage radius.
 

### 2019-12-28 defesa/tex/chapter/pmclp.tex
wip

@@
-In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP.
-Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$, where $\Pp$ is a set of points and $m$ is the number of unit disks.
+In this chapter, we introduce the classical version of PMCLP using radius one disks, we refer to this problem as \sigla{MCD}{Maximum Covering by Disks}.
+We also propose a method for it intending to adapt it for the elliptical PMCLP introduced next chapter.
+
+\section{Definition}
+
+An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ unit disks $\D:=\{D_1, \dots, D_m\}$, which represent the facilities and are used to cover the demand set.
+
+A solution for an instance of MCD chooses the location of the $m$ disks in $\D$. Formally, a solution is given by $Q:=(q_1, \dots, q_m)$, with $q_j\in\R^2$.
+
+Let $D\in \D$ and $q\in\R^2$, then we denote $D(q)$ as disk $D$ centered at $q$. Therefore, $\Pp \cap D(q)$ denotes the set of points from $\Pp$ covered by $D$.
+
+Given an instance of MCD, a solution for it is defined by the cen as .
 
@@
     \caption{The intersections list of a disk with three other disks.}
-    \input{tex/figures/fig:array_disks.tex}
+    \input{tex/figures/array_disks.tex}
     \fautor

### 2019-12-29 defesa/tex/chapter/introducao.tex
wip

@@
 One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic.
-Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set.
+Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets needed to cover the whole demand set.
 One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.

### 2019-12-29 defesa/tex/chapter/pmclp.tex
wip

--- 2019-08-06 defesa/tex/chapter/pmclp.tex
@@
-In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP.
-Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$, where $\Pp$ is a set of points and $m$ is the number of unit disks.
+In this chapter, we introduce a version of the classical Euclidean norm PMCLP where the facilities have a radius-one coverage area.
+We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}, as a radius-one coverage area in a Euclidean normed space is simply a unit disk.
+We also propose a method for it intending to adapt it for the elliptical PMCLP that will be introduced in the next chapter.
 
-\section{One disk, $MCD(\Pp,1)$}
+\section{Definition}
 
-Two exact methods for the $MCD(\Pp, 1)$ have been found in the literature.
-A $\bigO(n^2)$ algorithm is proposed by \cite{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \cite{drezner}.
-As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers).
-Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for $MCD(\Pp,1)$, which meant that no better time-complexity could be achieved.
+An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ disks $\D:=\{D_1, \dots, D_m\}$, which represents the facilities and are used to cover the demand set.
+Additionally, for every point in $\Pp$ a weight is given, and for every disk in $\D$ a coverage radius is given.
+The weight of the $j$-th point is denoted by $w_j\in\R_{>0}$, and the coverage radius of the $j$-th facility is denoted by $r_j \in \R_{>0}$.
+
+A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$ which specifies the center of every disk in $\D$.
+The coverage area of $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{>0}$ be the function
+
+\begin{equation}
+w(A) = \sum_{j : p_j \in A} w_j,
+\end{equation}
+which takes a subset of $\Pp$ and returns the sum of the weights of every point in that subset, then an optimal solution of MCD is given by the optmization problem:
+
+\begin{equation}
+\max_{Q} w\left(\bigcup_{j=1}^m \Pp \cap D_j(q_j)\right).
+\end{equation}
+
+\subsection{CLS and CIPS}
+
+The method proposed in \cite{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set} which is a finite set of possible solutions that needs to be considered so the optimal solution is found.
+
+\section{One unit disk version}
+
+This is the case of MCD where $m=1$ and the only given disk has radius one.
+This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk}.
+Two exact methods for it have been found in the literature.
+A $\bigO(n^2)$ algorithm is proposed by \citeonline{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \citeonline{drezner}.
+As it has been mentioned, MCD-1 is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers).
+Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for MCD-1, which meant that no better time-complexity could be achieved.
 Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.
 
-The $m=1$ version is treated here before the general case because it will be shown that, using the algorithm here proposed for $MCD(\Pp, 1)$, an optimal solution can be obtained for the $MCD(\Pp, m)$ as well as for the axis-parallel ellipse version of the problem.
+This version is treated here before the general case because it will be shown that, using the algorithm here proposed for MCD-1, an optimal solution can be obtained for the MCD as well as for the axis-parallel ellipse version of the problem that will be introduced in the next chapter.
 

### 2019-12-29 defesa/tex/chapter/pmclp.tex
wip

@@
-In this chapter, we introduce a version of the classical Euclidean norm PMCLP where the facilities have a radius-one coverage area.
-We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}, as a radius-one coverage area in a Euclidean normed space is simply a unit disk.
-We also propose a method for it intending to adapt it for the elliptical PMCLP that will be introduced in the next chapter.
+In this chapter, we introduce a version of the classical Euclidean norm PMCLP where each facility has a given coverage radius. 
+We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}. We also propose a method for it intending to adapt it for the elliptical PMCLP that will be introduced in the next chapter.
 
@@
 \end{equation}
-which takes a subset of $\Pp$ and returns the sum of the weights of every point in that subset, then an optimal solution of MCD is given by the optmization problem:
+which takes a subset of $\Pp$ and returns the sum of the weights of every point in that subset; then an optimal solution of MCD is given by the optmization problem:
 
@@
 
+It is important to note that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}.
+There, a coverage radius is given for each demand, rather than for each facility, and a demand is only considered covered if a facility is located within its radius.
+
 \subsection{CLS and CIPS}
 
-The method proposed in \cite{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set} which is a finite set of possible solutions that needs to be considered so the optimal solution is found.
+The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set} which is a finite set of possible solutions for each facility.
+After a CLS is constructed, a complete search can be executed to find the best solution.
 
-\section{One unit disk version}
+As this work is developed torwards an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
+This is done in \citeonline{church:1984} where a circle is defined for every demand point and a \sigla{CIPS}{circle intersection point set} is constructed containing every pairwise intersection of circles and the demand points.
+We introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.
 
-This is the case of MCD where $m=1$ and the only given disk has radius one.
-This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk}.
+\section{One disk version}
+
+This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk} and it is just a specific case of MCD with one unit disk ($m=1$ and $r_1=1$).
+It is treated before the case with multiple facilities because it is used to construct a CLS that is guaranteed to contain an optimal solution.
+
 Two exact methods for it have been found in the literature.
@@
 
-This version is treated here before the general case because it will be shown that, using the algorithm here proposed for MCD-1, an optimal solution can be obtained for the MCD as well as for the axis-parallel ellipse version of the problem that will be introduced in the next chapter.
-
-\subsection{Notation and definition of the problem}
-
-Initially, the input of the problem defines a unit disk with its center point undefined, a solution for the problem will then choose a point to be the center of the unit disk.
-In other words, a solution places the disk somewhere in the plane.
-We refer to the unit disk with undefined center as $D$. If it is placed at a center $q \in \R^2$, we call it $D(q)$.
-
-\begin{definicao}
-    Let $\Pp=\{p_1,\dots,p_n\}$ be a set of $n$ points in $\R^2$ and $w(p)>0, p \in \Pp$, the weight of every point in $\Pp$.
-We denote $w(A)$, with $A \subset \Pp$, as the sum of weights of every point in $A$.
-Finally, let $D$ be a unit disk, we define an optimal solution of $MCD(\Pp,1)$ as
-
-    \begin{equation}\label{eq:max_one_disk}
-        \max_q w(\Pp \cap D(q)).
-    \end{equation}
-
-\end{definicao}
-
-Therefore, an optimal solution for an instance of $MCD(\Pp,1)$ will be a point in which a unit disk located at, covers points whose weights, when summed, is maximal.
-
-In \cite{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal one.
+In \citeonline{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal one--this is also the idea used to construct the CIPS in \citeonline{church:1984}.
 The algorithm, for every point, sorts the other points with respect to the angle they form with the first one.
@@
 
-In \cite{chazelle:1986} and \cite{cabello:2006}, on the other hand, instead of working directly with $MCD(P,1)$, an equivalent problem called Maximum Weight Clique was introduced.
-The algorithm that we later describe in this work also uses this equivalence.
-That is why it has been taken to be fundamental to introduce the Maximum Weight Clique Problem and discuss the equivalence.
+In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD-1, an equivalent problem called Maximum Weight Clique was introduced.
+The algorithm that we later describe in this work also uses this equivalence and it is described next.
 
@@
 
-Let $\Pp=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$, be a set of points, $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$.
-A clique, in this context, is a non-empty intersection area of a subset of disks.
+Let $\Pp=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$, be a set of points; $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$.
+A clique, in this context, is a non-empty intersection area of two or more disks.
+A solution for the problem is a clique.
+
 Note that this is different than the clique problem on a intersection graph (a graph where the vertices are the disks and an edge exists if there is an intersection between two disks).
-As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique), but the intersection of all the three together is empty.
-That is why the clique problem for unit disks is also referred to as the Maximum Geometric Clique Problem when the condition of common intersection exists and as the Maximum Graphical Clique Problem when there is only the pairwise intersection condition \cite{inplace:2014}.
-The graphical version of the problem was studied by \cite{graphical-clique}, where a $\bigO(n^{4.5})$ algorithm was proposed.
-Also, in \cite{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm\footnote{An in-place algorithm is an algorithm that needs $\bigO(1)$ extra space.} for arbitrary radii disks was proposed.
-In \cite{chazelle:1986}, the method for the Maximum Geometric Weight Clique Problem consists on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
+
+As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique on the intersection graph), however, the intersection of all the three together still be empty.
+That is why the clique problem for unit disks is also referred to as the Maximum Geometric Clique Problem and as the Maximum Graphical Clique Problem when there is only the pairwise intersection condition \cite{inplace:2014}.
+
+The graphical version of the problem was studied by \citeonline{graphical-clique}, where a $\bigO(n^{4.5})$ algorithm was proposed.
+Also, in \citeonline{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm\footnote{An in-place algorithm is an algorithm that needs $\bigO(1)$ extra space.} for arbitrary radii disks was proposed.
+
+In \citeonline{chazelle:1986}, the method for the Maximum Geometric Weight Clique Problem consists on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
 With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.

### 2019-12-30 defesa/tex/chapter/pmclp.tex
wip

@@
 
-As this work is developed torwards an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
-This is done in \citeonline{church:1984} where a circle is defined for every demand point and a \sigla{CIPS}{circle intersection point set} is constructed containing every pairwise intersection of circles and the demand points.
+As this work is developed towards an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
+This is done in \citeonline{church:1984} where a circle is defined for every demand point, and a \sigla{CIPS}{circle intersection point set} is constructed containing the demand points and every pairwise circle intersection.
 We introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.
@@
 This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk} and it is just a specific case of MCD with one unit disk ($m=1$ and $r_1=1$).
-It is treated before the case with multiple facilities because it is used to construct a CLS that is guaranteed to contain an optimal solution.
+We later use the algorithm for MCD-1 to construct a CLS which is guaranteed to contain an optimal solution for MCD.
 
@@
 
-In \citeonline{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal one--this is also the idea used to construct the CIPS in \citeonline{church:1984}.
+In \citeonline{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal one.
 The algorithm, for every point, sorts the other points with respect to the angle they form with the first one.
@@
 
-In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD-1, an equivalent problem called Maximum Weight Clique was introduced.
-The algorithm that we later describe in this work also uses this equivalence and it is described next.
+In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD-1, an equivalent problem called \sigla{MWC}{Maximum Weight Clique} was introduced.
+The algorithm for MCD that is developed in this chapter also uses that equivalence.
+Because of that, MWC is introduced in the next section.
 
@@
 
-Let $\Pp=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$, be a set of points; $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$.
-A clique, in this context, is a non-empty intersection area of two or more disks.
-A solution for the problem is a clique.
+An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; and a set of disks $\D:=\{D_1,\dots,D_n\}$, such that $D_i$ is centered at $p_i$, for $i=1,\dots,n$, and with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it.
 
-Note that this is different than the clique problem on a intersection graph (a graph where the vertices are the disks and an edge exists if there is an intersection between two disks).
+A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
+Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$ as from $q$, the corresponding clique $S$ can be obtained as follows:
 
-As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique on the intersection graph), however, the intersection of all the three together still be empty.
-That is why the clique problem for unit disks is also referred to as the Maximum Geometric Clique Problem and as the Maximum Graphical Clique Problem when there is only the pairwise intersection condition \cite{inplace:2014}.
+\begin{equation}
+S = \bigcap_{j : q \in D_j} D_j.
+\end{equation}
+With a geometric observation, the number of possible values for the solution can be reduced.
+Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, the clique contains obviously the center of that disk.
+Therefore, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as $\Pp$.
+Finally, an optimal solution of MWC is given by the optimization problem
 
-The graphical version of the problem was studied by \citeonline{graphical-clique}, where a $\bigO(n^{4.5})$ algorithm was proposed.
+\begin{equation}
+\max_{q} \sum_{D_k \cap q \neq \emptyset} w_k,
+\end{equation}
+with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$.
+It can be shown that the number of possible solutions for an instance of MWC is bounded by $\binom{n}{2} + n = \bigO(n^2)$.
+
+It is worth pointing out that MWC is a different problem than the maximum clique on a intersection graph (a graph where the vertices are the disks and an edge exists if there is an intersection between two disks).
+As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection and still have an empty intersection of all of them together.
+That is why MWC is also referred to as the Maximum Geometric Clique Problem and the other version, when there is only the pairwise intersection condition, is referred to as the Maximum Graphical Clique Problem \cite{inplace:2014}.
+
+%The graphical version of the problem was studied by \citeonline{graphical-clique}, where a $\bigO(n^{4.5})$ algorithm was proposed.
 Also, in \citeonline{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm\footnote{An in-place algorithm is an algorithm that needs $\bigO(1)$ extra space.} for arbitrary radii disks was proposed.
 
-In \citeonline{chazelle:1986}, the method for the Maximum Geometric Weight Clique Problem consists on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
+In \citeonline{chazelle:1986}, the method for MWC consists on building a planar graph on which the vertices were the $\binom{n}{2}$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
 With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.
@@
 
-A solution for the Maximum Weight Clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized.
-Even though there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the Maximum Weight Clique is enough.
-This will become clear when the equivalence is stated.
-With everything in hands, we can define the Maximum Weight Clique Problem as follows.
+As it has been mentioned, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of the MCD-1, which means that a disk centered at $q^*$ which is an optimal solution of MWC, will have a maximal weight covering of the demand set $\Pp$.
 
-\begin{definicao}\label{def:max_weight_clique}
-    Let $\D$ be a set of unit disks and $\Pp$ be a set of points as defined before. An optimal solution for the Maximum Weight Clique Problem is given by
-
-    \begin{equation}
-        \max_q \sum_{D_k \cap q \neq \emptyset} w_k.
-    \end{equation}
-
-\end{definicao}
-
-As it has been proposed, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of the $MCD(\Pp,1)$, which means that a disk centered at $q$, defined in \autoref{def:max_weight_clique}, will have a maximal weight covering of the set $\Pp$.
-
-Given an instance of $MCD(\Pp,1)$, the equivalent Maximum Weight Clique Problem is obtained by defining set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
+Given an instance of MCD-1, the equivalent MWC intance is obtained by defining set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
 A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$.
-This means that a intersection between some disks is an area where a disk could be placed to cover the corresponding points.
+This means that a intersection between some disks is a region where a disk could be placed to cover the corresponding points.
 
@@
 
-Formally, in the Maximum Weight Clique Problem, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the $MCD(P,1)$ problem.
+Formally, in MWC, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the MCD-1 problem.
 Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the one disk maximal covering problem.
@@
 
-The algorithm described here is based on the one in \cite{drezner}, also with some ideas from \cite{inplace:2014} and \cite{cabello:2006}.
+The algorithm described here is based on the one in \citeonline{drezner}, also with some ideas from \citeonline{inplace:2014} and \citeonline{cabello:2006}.
 It has a run time complexity of $\bigO(n^2\log{n})$ and uses $\bigO(n)$ of extra space.
-It is worth noting, however, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \cite{bentley:1979} to find all the intersections among the $n$ circumferences.
+It is worth noting, however, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \citeonline{bentley:1979} to find all the intersections among the $n$ circumferences.
 
-Without loss of generality, the weights will be ignored, and the method will be described for the Maximum Clique Problem, assuming that every disk has unit weight.
+Without loss of generality, the weights will be ignored, and the method will be described for MWC, assuming that every disk has unit weight.
 Also, it will be assumed that no pair of disks are placed at the same center.

### 2020-01-05 defesa/tex/chapter/pmclp.tex
wip

@@
 
-An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; and a set of disks $\D:=\{D_1,\dots,D_n\}$, such that $D_i$ is centered at $p_i$, for $i=1,\dots,n$, and with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it.
+An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; and a set of unit disks $\D:=\{D_1,\dots,D_n\}$, such that $D_i$ is centered at $p_i$, for $i=1,\dots,n$, and with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it.
 
 A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
-Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$ as from $q$, the corresponding clique $S$ can be obtained as follows:
+Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$ which is inside any of the given disks in $\D$.
+From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$:
 
@@
 \end{equation}
-With a geometric observation, the number of possible values for the solution can be reduced.
-Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, the clique contains obviously the center of that disk.
-Therefore, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as $\Pp$.
+With a geometric observation, though, the number of possible values for the solution can be reduced.
+Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, it contains obviously the center of its only disk.
+Therefore, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$.
 Finally, an optimal solution of MWC is given by the optimization problem
@@
 with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$.
-It can be shown that the number of possible solutions for an instance of MWC is bounded by $\binom{n}{2} + n = \bigO(n^2)$.
+With this new observation, it can be shown that the number of possible solutions that need to be considered, so an optimal solution is found for an instance of MWC is bounded by $\binom{n}{2} + n = \bigO(n^2)$.
 
@@
 
-As it has been mentioned, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of the MCD-1, which means that a disk centered at $q^*$ which is an optimal solution of MWC, will have a maximal weight covering of the demand set $\Pp$.
+As it has been mentioned, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of MCD-1, which means that a disk centered at $q^*$ which is an optimal solution of MWC, will have a maximal weight covering of the demand set $\Pp$.
 
-Given an instance of MCD-1, the equivalent MWC intance is obtained by defining set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
+Given an instance of MCD-1, the equivalent MWC intance is obtained by defining the set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
 A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$.
@@
 
-Formally, in MWC, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the MCD-1 problem.
-Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the one disk maximal covering problem.
-It means that $q$ will lie inside region $\bigcap_{k \in I} D_k$.
+Formally, in MWC, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the equivalent MCD-1 instance.
+Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the MCD-1 instance.
+It means that $q$ will lie inside region $\bigcap_{k \in I} D_k$ in MWC.
 
@@
 
-Without loss of generality, the weights will be ignored, and the method will be described for MWC, assuming that every disk has unit weight.
-Also, it will be assumed that no pair of disks are placed at the same center.
-
-Let $\D$ be a set of $n$ unit disks, a non-empty intersection area of a subset of disks is convex and bounded by the arcs of the disks that are intersecting \cite{inplace:2014}.
-With this observation, in order to find an optimal solution, it is sufficient to check, for every disk $D$, every intersection area that is bounded by its arc.
+In \citeonline{inplace:2014} an important observation is made about the intersection regions of disks.
+Given an instance of MWC, any clique formed by a subset of $\D$ is bounded by the arcs of circles that intersect with it.
+Also, those arcs have the intersection of circles as its end-points.
+This can be seen on \autoref{fig:3disks_intersect} where the cliques that $D_1$ is part of are bounded by $D_1$'s arcs which have its intersections with the other circles as end-points.
+Following this, a definition is presented to characterize the end-points of an arc bordering a clique.
 
 \begin{definicao}\label{def:inter_arc}
-    Let $D_i$ and $D_j$ be two unit disks that intersect (at least at one point).
-Also let $(\theta_1, \theta_2) \in [0,2\pi]^2$ be the two angles that the circumferences induced by $D_i$ and $D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$.
+    Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and $(\theta_1, \theta_2) \in [0,2\pi)^2$ be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$.
 If $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$.
@@
 Also, they are labeled according to \autoref{def:inter_arc}.
-Note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).
+Note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi)$ interval).
 
-With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm to find the maximum clique in which a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$, in counter-clockwise order, keeping a set of active disks.
-When an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
-This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ (see \autoref{fig:3disks_intersect}).
-If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it.
-If there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and an optimal solution could end up not being found.
-This can be worked around repeating the traversal once without resetting the active disks set, that way, in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$.
-This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated, simulating the traversal repetition (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
-It can be seen that without the repetition, the algorithm would find $2$ as the value of an optimal solution, which is wrong.
+With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm for MWC.
+The idea is to find for every disk, the best clique it is part of, this way an optimal solution is surely found.
+
+Finding the best clique that $D_i$ participates is done by traversing every intersection of $\partial D_i$ with every circle from $\partial \D$ in counter-clockwise order while keeping a set of active disks.
+In other words, the set
+
+\begin{equation}
+A_i = \{\Gamma_+(i,j) : 1 \le j \le n\} \cup \{\Gamma_-(i,j) : 1 \le j \le n\},
+\end{equation}
+is traversed in counter-clockwise order and when an opening intersection angle is reached, the corresponding disk is added to the active set; and when a closing one is seen, the corresponding disk is removed from the active set.
+This way, finding an optimal solution can be achieved by keeping the weight of the active disks as well as the best one found so far.
+
+This simple traversal, however, would not handle the case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ which would cause the algorithm to remove a disk wihtout first adding it leading to a possible non-optimal solution.
+This can be fixed by traversing the following set instead
+
+\begin{equation}
+B_i = A_i \cup \{\Gamma_+(i,j) + 2\pi : 1 \le j \le n\} \cup \{\Gamma_-(i,j) + 2\pi: 1 \le j \le n\},
+\end{equation}
+which basically duplicates the list of intersections.
+This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$.
+This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
+It can be seen that without the duplication, the algorithm would find $2$ as the value of an optimal solution, which is wrong.
 
@@
 
-\begin{lema}\label{lema:disk}
+\begin{teorema}\label{lema:disk}
 \autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
-\end{lema}
+\end{teorema}
 
 \begin{proof}
-    Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \cite{bentley:1979}. 
+    Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \citeonline{bentley:1979}. 
     Because the traversal is made in counter-clockwise order, the intersection points have to be sorted by their intersection angles, so an additional $\bigO(K\log{K})$ pre-processing is needed.

### 2020-01-06 defesa/tex/chapter/pmclp.tex
wip

@@
 \end{equation}
-which takes a subset of $\Pp$ and returns the sum of the weights of every point in that subset; then an optimal solution of MCD is given by the optmization problem:
+which takes a subset of $\Pp$ and returns the sum of the weights of every point in it; then an optimal solution of MCD is given by the optmization problem:
 
@@
     Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and $(\theta_1, \theta_2) \in [0,2\pi)^2$ be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$.
-If $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$.
 Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
+As a convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and $\Gamma_-(i, i)=0$ and $\Gamma_+(i,i)=2\pi$.
 \end{definicao}
@@
 Finding the best clique that $D_i$ participates is done by traversing every intersection of $\partial D_i$ with every circle from $\partial \D$ in counter-clockwise order while keeping a set of active disks.
+This way, finding an optimal solution can be achieved by keeping the weight of the active disks as well as the best clique found so far.
+
 In other words, the set
@@
 is traversed in counter-clockwise order and when an opening intersection angle is reached, the corresponding disk is added to the active set; and when a closing one is seen, the corresponding disk is removed from the active set.
-This way, finding an optimal solution can be achieved by keeping the weight of the active disks as well as the best one found so far.
 
-This simple traversal, however, would not handle the case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ which would cause the algorithm to remove a disk wihtout first adding it leading to a possible non-optimal solution.
+This simple traversal, however, would not handle the case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ which would cause the algorithm to remove a disk wihtout first adding it to the active set list leading to a possible non-optimal solution.
 This can be fixed by traversing the following set instead
@@
 \end{equation}
-which basically duplicates the list of intersections.
+which basically duplicates the set of intersections $A_i$ shifting it to the interval $[2\pi, 4\pi)$.
+
 This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$.

### 2020-01-07 defesa/tex/chapter/e3p.tex
wip

@@
 
-We call the problem introduced in this section \sigla{E3PNT}{Ellipse by Three points}.
+We call the problem introduced in this section \sigla{E3PNT}{Ellipse by Three Points}.
 An instance of it is given by three points $u, v, w \in \R^2$ and the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, with $a > b$.
 
-Let $E$ be the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
-As a last remark, because of its application on \autoref{chapter:ellipses_n}, it is only useful a method would only be useful to our case if it can encounter every solution of E3PNT.
+Let $E$ represent the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3PNT can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
+As a last remark, because of its application on \autoref{chapter:ellipses_n}, a method would only be useful for our case if it can encounter every solution of E3PNT.
 This requirement, of course, makes the problem more challenging.
@@
 
-Initially, E3PNT is a problem with $3$ unknown variables: $q_x, q_y, $ and $\theta$.
+Initially, E3PNT is a problem with $3$ unknown variables: the two coordinates of the center point $q_x, q_y, $ and the angle of rotation $\theta$.
 In this section, we transform E3PNT into the problem of finding the roots of an univariate function using the known problem of determining the circumcenter of a triangle.
-We also shown that the number of solutions of E3PNT is at most $6$.
+We also show E3PNT has at most $6$ solutions.
 
-To make it simpler, let us translate the system, so the point $u$ is at $(0,0)$.
-Then, we assume that the ellipse is actually axis-parallel and the points are the ones rotating.
+To make the problem simpler, let us translate the system, so the point $u$ is at the origin.
+After that, we assume that the ellipse is actually axis-parallel and the points are the ones rotating.
 When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$.
@@
 p_y
-\end{array}\right],
+\end{array}\right].
 \end{equation}
-because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.
+Because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.
 
@@
 
-After that transformation, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$, such that the circle's radius is $b$.
-Therefore, the only unknown of this problem is the angle of rotation.
-This idea reduces the number of variables from $3$ to only $1$, however, this would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
+After that transformation, the problem to be solved is the one of checking if there is a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$ with radius $b$.
+That implies that the only unknown of this problem is the angle of rotation $\theta$, reducing the number of variables from three to one.
+This idea, however, would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
 
@@
 Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the expression
+
 \begin{equation}\label{eq:circumscribed_circle}
@@
 Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as
+
 \begin{equation}\label{eq:circumscribed_circle_b}
@@
 
-It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe for future work it can be used for further improvements.
+It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe, for future work, it can be used for further improvements.
 Analyzing the polynomials produced for several instances, the following seems to be true:

### 2020-01-07 defesa/tex/chapter/pmclp.tex
wip

@@
 A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$ which specifies the center of every disk in $\D$.
-The coverage area of $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{>0}$ be the function
+The coverage region of the $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{>0}$ be the function
 
@@
 
-It is important to note that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}.
+As a remark, it is important to note that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}.
 There, a coverage radius is given for each demand, rather than for each facility, and a demand is only considered covered if a facility is located within its radius.
@@
 
-The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set} which is a finite set of possible solutions for each facility.
+The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set}, which is a finite set of possible solutions, for each facility.
 After a CLS is constructed, a complete search can be executed to find the best solution.
 
-As this work is developed towards an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
+As this work is developed towards the creation of an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
 This is done in \citeonline{church:1984} where a circle is defined for every demand point, and a \sigla{CIPS}{circle intersection point set} is constructed containing the demand points and every pairwise circle intersection.
-We introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.
+Here, we introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.
 
@@
 
-This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk} and it is just a specific case of MCD with one unit disk ($m=1$ and $r_1=1$).
-We later use the algorithm for MCD-1 to construct a CLS which is guaranteed to contain an optimal solution for MCD.
+This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk} and it is just a specific case of MCD with only one disk with radius one ($m=1$ and $r_1=1$).
+We later use the algorithm for MCD-1 here described to construct a CLS which is guaranteed to contain an optimal solution for MCD.
 
-Two exact methods for it have been found in the literature.
+Two exact methods for MCD-1 have been found in the literature.
 A $\bigO(n^2)$ algorithm is proposed by \citeonline{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \citeonline{drezner}.
-As it has been mentioned, MCD-1 is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers).
+As it has been mentioned, MCD-1 is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding three real numbers that sum to zero, given $n$ real numbers).
 Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for MCD-1, which meant that no better time-complexity could be achieved.
@@
 
-In \citeonline{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal one.
+In \citeonline{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal solution.
 The algorithm, for every point, sorts the other points with respect to the angle they form with the first one.
@@
 With a geometric observation, though, the number of possible values for the solution can be reduced.
-Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, it contains obviously the center of its only disk.
-Therefore, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$.
-Finally, an optimal solution of MWC is given by the optimization problem
+Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, it contains the center of its only disk.
+Because of that, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$.
+Then, with this observation, an optimal solution of MWC can be defined by the optimization problem
 
@@
 with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$.
-With this new observation, it can be shown that the number of possible solutions that need to be considered, so an optimal solution is found for an instance of MWC is bounded by $\binom{n}{2} + n = \bigO(n^2)$.
+With this new specification of the solution's search space, it can be shown that given an instance of MWC, an optimal solution for it can be found by going through $\binom{n}{2} + n = \bigO(n^2)$ possible ones.
 
@@
     \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}
-    \begin{tikzpicture}[scale=1]
+    %\begin{tikzpicture}[scale=1]
     %\draw [help lines] (-5,-3) grid (5,3);
-    \draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);
+    %\draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);
 
@@
 
-    \draw[fill] (0.9,1.6) circle [radius=.5pt];
-	\draw[fill] (0,0) circle [radius=.5pt];
-    \draw[fill] (-0.9,1.6) circle [radius=.5pt];
+    %\draw[fill] (0.9,1.6) circle [radius=.5pt];
+	%\draw[fill] (0,0) circle [radius=.5pt];
+    %\draw[fill] (-0.9,1.6) circle [radius=.5pt];
 
-    \node[below] at (0,0) {$p_1$};
-    \node[below] at (0.9, 1.6) {$p_2$};
-    \node[below] at (-0.9, 1.6) {$p_3$};
+    %\node[below] at (0,0) {$p_1$};
+    %\node[below] at (0.9, 1.6) {$p_2$};
+    %\node[below] at (-0.9, 1.6) {$p_3$};
 
@@
      %\draw [|-|] (0.001,-0.1) -- (4.999,-0.1);
-    \end{tikzpicture}
+    %\end{tikzpicture}
+
+    \includegraphics[scale=.35]{tex/figures/three_disks_no_intersection.pdf}
     \label{fig:three_disks_no_intersection}
@@
 Given an instance of MWC, any clique formed by a subset of $\D$ is bounded by the arcs of circles that intersect with it.
-Also, those arcs have the intersection of circles as its end-points.
+Also, those arcs have the intersection of circles as their end-points.
 This can be seen on \autoref{fig:3disks_intersect} where the cliques that $D_1$ is part of are bounded by $D_1$'s arcs which have its intersections with the other circles as end-points.
@@
     Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and $(\theta_1, \theta_2) \in [0,2\pi)^2$ be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$.
-Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
-As a convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and $\Gamma_-(i, i)=0$ and $\Gamma_+(i,i)=2\pi$.
+Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$.
+For convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and if $i=j$, then $\Gamma_-(i, j)=0$ and $\Gamma_+(i,j)=2\pi$.
 \end{definicao}
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
     \caption{Three disks and their intersection points.}
-    \input{tex/img2.tex}
+    \includegraphics[scale=.36]{tex/figures/3_disks_intersect.pdf}
+%    \input{tex/img2.tex}
     \fautor
@@
 
+Also, we refer to $\Gamma_+(i,j)$ as an opening angle, and to $\Gamma_-(i,j)$ as a closing angle.
 In \autoref{fig:3disks_intersect}, it is shown all the intersection points between $D_1$ with $D_2$ and $D_3$.
 Also, they are labeled according to \autoref{def:inter_arc}.
-Note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi)$ interval).
+Note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).
 
 With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm for MWC.
-The idea is to find for every disk, the best clique it is part of, this way an optimal solution is surely found.
-
-Finding the best clique that $D_i$ participates is done by traversing every intersection of $\partial D_i$ with every circle from $\partial \D$ in counter-clockwise order while keeping a set of active disks.
-This way, finding an optimal solution can be achieved by keeping the weight of the active disks as well as the best clique found so far.
-
-In other words, the set
+For every disk $D_i$, let us describe an algorithm that gets the best clique which $D_i$ is part of.
+This way, an algorithm for MWC just uses that method for every disk and returns the best solution found.
+Firstly, let $A_i$ be a list that contains the intersection angles of $\partial D_i$ with every circle in $\partial \D$.
+Assume also that $A_i$ is actually a circular list sorted in ascending order and it is defined as
 
 \begin{equation}
-A_i = \{\Gamma_+(i,j) : 1 \le j \le n\} \cup \{\Gamma_-(i,j) : 1 \le j \le n\},
+A_i = \bigcup_{j=1}^n \{ \Gamma_-(i,j), \Gamma_+(i,j) \}.
 \end{equation}
-is traversed in counter-clockwise order and when an opening intersection angle is reached, the corresponding disk is added to the active set; and when a closing one is seen, the corresponding disk is removed from the active set.
+Finding the best solution which $D_i$ is part of can be done by traversing $A_i$ while keeping a set of active disks.
+When an opening intersection angle is reached, the corresponding disk is added to the active set; and when a closing one is seen, the corresponding disk is removed from the active set.
+This way, finding an optimal solution can be achieved by keeping the weight of the active disks as well as the best clique found so far.
+Notice also that because $\Gamma_+(i,i)=0$ and $\Gamma_-(i,i)=2\pi$, any clique found by the traversal will also contain $D_i$.
 
-This simple traversal, however, would not handle the case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ which would cause the algorithm to remove a disk wihtout first adding it to the active set list leading to a possible non-optimal solution.
-This can be fixed by traversing the following set instead
+In practice, traversing a circular list can be emulated by traversing a regular list that has a copy of the original circular list added to its end.
+This is done here by traversing the regular list $B_i$ defined as
 
-\begin{equation}
-B_i = A_i \cup \{\Gamma_+(i,j) + 2\pi : 1 \le j \le n\} \cup \{\Gamma_-(i,j) + 2\pi: 1 \le j \le n\},
+\begin{equation}\label{eq:b_i}
+B_i = A_i\cup\bigcup_{j=1}^n \{ 2\pi+\Gamma_-(i,j), 2\pi+\Gamma_+(i,j) \}.
 \end{equation}
-which basically duplicates the set of intersections $A_i$ shifting it to the interval $[2\pi, 4\pi)$.
-
+Assuming $B_i$ is sorted in ascending order, a copy of the elements of $A_i$ shifted to the interval $[2\pi, 4\pi]$ is added to its end and a simple traversal, going through the first element until the last one, simulates a traversal on the circular list $A_i$.
 This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$.
 This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
-It can be seen that without the duplication, the algorithm would find $2$ as the value of an optimal solution, which is wrong.
 
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
     \caption{The intersections list of a disk with three other disks.}
-    \input{tex/figures/array_disks.tex}
+	 %\input{tex/figures/array_disks.tex}
+    \includegraphics[scale=.28]{tex/figures/3_disks_intersect2.pdf}
     \fautor
@@
 \begin{algoritmo}
-\caption{Algorithm for $MCD(\Pp, 1)$ with unit weights}\label{algoritmo:mcd_1}
+\caption{Algorithm for MCD-1.}\label{algoritmo:mcd_1}
 \begin{algorithmic}[1]
-\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$.}
-\Ensure{The maximum number of points that can be covered by a unit disk.}
+\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\{w_1, \dots, w_n\}$.}
+\Ensure{The maximum cover by a unit disk.}
 
@@
 \State Let $D_i$ be the disk with center at $p_i$
-\State Let $I_i$ be the set of disks that intersect with $D_i$
-\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $D_i$.}
+\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}.
 
-\ForAll{$j \in I_i$}
-\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
-\EndFor
-
-%\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
-\State $Q \gets \{D_i\}$ \Comment{The set of active disks.}
-\For{$cnt=1..2$} \Comment{Do it twice.}
-\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
+\State $Q \gets \{\}$ \Comment{The set of active disks.}
+\For{$a \in B_i$}\Comment{Assuming $B_i$ is sorted.}
 \State Let $D_a$ be the disk that intersects $D_i$ at angle $a$. 
@@
 \EndIf
-\If{$|Q_{best}| < |Q|$}
+\If{$w(Q_{best}) < w(Q)$} \Comment{$w(Q)$ returns the weights of the disks in $Q$.}
 \State $Q_{best} \gets Q$
@@
 \EndIf
-\EndFor
+
 \EndFor
@@
     Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \citeonline{bentley:1979}. 
-    Because the traversal is made in counter-clockwise order, the intersection points have to be sorted by their intersection angles, so an additional $\bigO(K\log{K})$ pre-processing is needed.
+    Because sorting the intersection angles needs to be done, an additional $\bigO(K\log{K})$ pre-processing is added.
 All the other operations can be done in constant time.
@@
 
-\section{Multiple disks, $MCD(\Pp, m)$}
+\section{Multiple disks}
 
-In \cite{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD(\Pp, m)$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.
-Firstly, they solve the sub-problem $MCD(\Pp, 2)$ in $\bigO(n^3\log{n})$.
-Then for the rest of the points that are not in that solution, it uses the algorithm developed in \cite{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.
+In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.
+Firstly, they solve a sub-problem for two disks in $\bigO(n^3\log{n})$.
+Then, for the rest of the points that are not in that solution, it uses the algorithm developed in \citeonline{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.
 
-Also, in \cite{zhou} an heuristic method for large-scale $MCD$ is proposed.
+Also, in \citeonline{zhou} an heuristic method for large-scale $MCD$ is proposed.
 It uses a probabilistic algorithm called mean-shift which is a gradient ascent method proven to converge to a local density maxima of any probability distribution.
@@
 
-It can be seen that in any solution of $MCD(\Pp, m)$, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be an optimal solution.
+\subsection{An algorithm for MCD}
+
+A simple adaptation can be done on \autoref{algoritmo:mcd_1}, so it returns a CLS that contains an optimal solution for the disk, instead of just finding the best solution.
+Also, the detail that MCD-1 is defined for unit disks can be ignored as \autoref{algoritmo:mcd_1} works for disks of any radius.
+
+It can be seen that in any solution of MCD, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be an optimal solution.
 The number of points \autoref{algoritmo:mcd_1} goes through is $\bigO(n^2)$, then checking every possible center for every ellipse yields a $\bigO(n^{2m})$ run-time complexity.
-This algorithm is described in \autoref{chapter:ellipses} for the ellipses case.
+This algorithm is described in \autoref{chapter:ellipses} for the axis-parallel ellipses case.
 
-The choice of developing a different method for the problem, instead of using the one from \cite{cabello:2006}, is taken for the sake of simplicity, considering both algorithms achieve similar bounds.
+It is worth mentioning that the choice of developing a different method for the problem, instead of using the one from \citeonline{cabello:2006}, is taken for the sake of simplicity, considering both algorithms achieve similar bounds.

### 2020-01-07 defesa/tex/chapter/e3p.tex
wip

@@
 
-After that transformation, the problem to be solved is the one of checking if there is a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$ with radius $b$.
-That implies that the only unknown of this problem is the angle of rotation $\theta$, reducing the number of variables from three to one.
+After that transformation, the problem to be solved is the one of checking the existence of a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$ with radius $b$.
+Notice that the problems are indeed equivalent, which implies that a bijection between the set of solutions of each problem exists.
+Working with this problem instead is preferred because of the reduction in the number of variables from three to one.
 This idea, however, would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
 
-It turns out that for three non-colinear fixed points, there is always an unique circumscribed circle.
+It turns out that for three non-colinear points, there is always an unique circumscribed circle.
 Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the expression
@@
 \end{equation}
-with $A(\theta)$ being the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$--note that the transformation does not preserve distance or area.
-For more details about \autoref{eq:circumscribed_circle} see \citeonline[p.~189]{johnson1960}.
+with $A(\theta)$ being the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$ (for more details about \autoref{eq:circumscribed_circle} see \citeonline[p.~189]{johnson1960}
+). It is important to note that the transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
 
-Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as
+With the formula for the circumradius in hands, a function can be defined, such that its roots provide solutions for E3PNT.
+Imposing the radius $R$ to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as
 
 \begin{equation}\label{eq:circumscribed_circle_b}
-\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
+\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2.
 \end{equation}
-in such a way that its zeros determine solutions for E3PNT.
+Any root of $\xi$ produces a triangle whose circumradius is $b$ and subsequently provides a solution for E3PNT.
 
-Lastly, two questions about $\xi(\theta)$ that arise are: is its set of roots finite? And, if its set of roots is finite, can they be found analytically?
+Before continuing with this approach of trying to determine the roots of $\xi$, it is important to answer the question whether this set of roots is finite or not?
+Answering this question is also important because it automatically relates to the question about the number of solutions of E3PNT.
 
-\subsection{The number of solutions is limited}
+\subsection{The number of solutions of E3PNT}
 
-One of the steps of the method developed on \autoref{chapter:ellipses_n} is to iterate over every solution of E3PNT for every triplet of points.
+One of the steps of the method developed in \autoref{chapter:ellipses_n} is to iterate over every solution of E3PNT for every triplet of points.
 Of course doing that is only possible for a finite number of solutions.
@@
 
-Back on \autoref{chapter:definitions} real trigonometric polynomials were introduced.
+\begin{lema}
+	E3PNT has at most $6$ solutions.
+\end{lema}
+
+\begin{proof}
+
+Back on \autoref{chapter:definitions}, real trigonometric polynomials were introduced.
 It was stated that a $n$-degree polynomial can have up to $2n$ distinct roots.
-It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2} which implies that it can have up to $12$ distinct roots.
- To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form
+It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2}.
+This implies that $\xi$ can have up to $12$ distinct roots.
+ To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in the same form as given by \autoref{eq:trig_poly_2}:
+
  \begin{align}\label{eq:dd}
@@
   It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared lengths of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$.
-This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
-
-Because ellipses are symmetrical with respect to their major-axis, and any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$, the number of different solutions is cut in half.
-Therefore, the number of angles of rotation and centers that an ellipse of fixed shape can be placed, so it has three fixed points on its border is limited to $6$.
+This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\norm{\varphi(v, \theta)}^2$ is $6$ which consequently is the degree of $\xi$.
+Going from $12$ solutions to $6$ is done by using the symmetry of ellipses.
+In \autoref{chapter:definitions}, it was stated that any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$.
+Therefore, half of the roots of $\xi$ are in $[\pi, 2\pi)$ and can be ignored.
+\end{proof}
 
@@
 In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}.
-For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered.
+For this problem, the approximation of $\xi$ on the interval $[0, \pi)$ is considered.
 The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n\times n$ matrix.
@@
 There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error
+
 \begin{equation}
@@
 which measures how far the interpolation is at the point it worst approximates.
+
+\subsection{Numerical Experiments}
+
+In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved. 
+The interpolation was run for several degrees for every triplet of points present in an instance from \citeonline{canbolat}.
+We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found.
+
+The results are shown in \autoref{fig:interpolant_error} where the worst error found among every root found is plotted against the interpolant degree used.
+A parameter $K$ is also used in the experiments.
+This is an idea suggested in \citeonline{boyd:2013} to improve accuracy.
+This parameter represents the number of sub-intervals that $[0, \pi)$ is divided into.
+This way $K$ interpolations are used to obtain every root in the whole interval.
+It can be seen in \autoref{fig:interpolant_error} that this strategy helps a lot in improving the accuracy even when not so large degrees are used.
+
+\begin{figure}
+	\centering
+	\caption{The interpolation error measured on roots that were found.}
+	\includegraphics{tex/figures/interpolant_error}
+	\fautor
+	\label{fig:interpolant_error}
+\end{figure}
 
@@
 The cause was not for sure identified, but a good guess would be that for angles which are greater than $\frac{\pi}{4}$, $x$ starts growing too rapidly which could lead to numerical instability.
+This issue made us abandon this approach and pursue a different way to convert $\xi$ into a polynomial.
 
@@
 
-The second approach is based on a idea published on \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials in order to obtain its roots using the companion matrix scheme.
+The second approach is based on a idea published in \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
 This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial--more details about this can be found in \citeonline{weidner} where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
+
 \begin{align}\label{eq:complex_trig}
@@
 It is possible to show that with that substitution and changing the variable to $z=e^{i\theta}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$, with $\mathbb{S}$ being the unit complex circle ($\mathbb{S} = \{z \in \mathbb{C} : |z|=1\}$):
+
 \begin{equation}
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, the function $g'(\theta)=g(e^{i\theta})$ and the function $\xi$ are equivalent since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
+As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, the function $g(e^{i\theta})$ and the function $\xi$ are equivalent since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
 
-Now there is only two things preventing $g$ from being a polynomial: firstly, $z$ shows up with negative exponents (up to $-6$); secondly its domain is the unit circle $\mathbb{S}$, not the whole complex set $\mathbb{C}$.
+The function $g$ is still not a polynomial as $z$ shows up with negative exponents (up to $-6$), and its domain is the unit circle $\mathbb{S}$, not the whole complex set $\mathbb{C}$. 
 The first issue can be fixed by multiplying $g$ by $z^6$, note that this does not create further problems as $0\not\in \mathbb{S}$.
 The second issue is removed by simply extending the domain from $\mathbb{S}$ to $\mathbb{C}$, as $\mathbb{S} \subset \mathbb{C}$, roots outside the unit circle could appear which requires a further check for every root that is found.
-Finally, from $g$, the polynomial $h : \mathbb{C} \mapsto \mathbb{C}$ is defined as follows:
-\begin{equation}
+Finally, from $g$, the polynomial $h : \mathbb{C} \mapsto \mathbb{C}$ is defined as
+
+\begin{equation}\label{eq:h}
 h(z) = z^6 g(z) = \sum_{k=0}^{12} c_k z^k.
 \end{equation}
-By its definition it is possible to see that every root of $g$ is also a root of $h$, and conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$, is also a root of $g$.
-Lastly, every root of $g$ will correspond to a root of $\xi$ though their angles on the unit circle.
+By its definition it is possible to see that every root of $g$ is also a root of $h$, and conversely, every root of $h$ which is in $\mathbb{S}$, is also a root of $g$.
+Lastly, every root of $g$ will correspond to a root of $\xi$ through their angles on the unit circle.
 
@@
 In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
-On the other hand, on \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
+On the other hand, in \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
 \begin{equation*}
@@
 \end{align}
-Therefore, all the odd degree coefficients of $h$ are $0$ and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$:
+Therefore, all the odd degree coefficients of $h$ are zero and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$ as follows
 \begin{equation}
@@
 Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$.
-As the angle of one of the roots will not be between $[0, \pi)$ we can ignore on of them.
-Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
+As the angle of one of the roots will not be between $[0, \pi)$ we can ignore one of them.
+Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the following identity
 \begin{equation}
@@
 \end{equation}
-Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm can be constructed for E3P.
-Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm.
+Finally, using the QR algorithm mentioned in \autoref{chapter:definitions}, a $\bigO(n^3)$ algorithm can be constructed for E3PNT.
+Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm that takes around $6^3$ operations.
 
@@
 
-\section{Numerical Experiments}
+Assuming that an algorithm to obtain the eigenvalues of a matrix, the following algorithm to obtain every solution of E3PNT is described as follows.
 
-In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved. 
-Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we define the interpolation error $r_n$ as:
+\begin{algoritmo}
+	\caption{Algorithm for E3P.}\label{algoritmo:e3p}
+	\begin{algorithmic}[1]
+		\Require{$u, v, w\in\R^2$, and $a, b\in\R_{>0}$, with $a>b$.}
+		\Ensure{Every solution of E3P.}
 
-Then, we want to determine the smallest $n$, such that $r_n \le \epsilon$, for a predefined $\epsilon$.
-Unfortunately, calculating $r_n$ involves taking samples from both functions on the whole interval, which is not viable computationally.
-In \citeonline[p.~50]{boyd:2001} a rule-thumb for estimating the interpolation error is given.
-It is worth mentioning that this rule
+		\item[]
 
-It uses a theorem that states that $r_n$ is limited by the sum of the coefficients of the Chebyshev series that were removed by the truncation. The rule-of-thumb for estimating $r_n$ is given by:
+		\Procedure{$E3PNT$}{$u,v,w,a,b$}
 
-\begin{equation}
-r_n \approx |a_n|.
-\end{equation}
+		\State $\hat{u}\gets (0,0)$
+		\State $\hat{v} \gets v-u$
+		\State $\hat{w} \gets w-u$
 
-Note that
+		\State Let $c_0, \dots, c_{12}$ be the coefficients of polynomial $h$ as \autoref{eq:h}.
+		\State Let $A$ be a $6\times6$ zero matrix.
 
-Obtaining an expression for it is not trivial, and sampling the whole interval is not viable computationally.
+		\For{$i\in\{1, \dots, 6\}$}
+			\State $A_{i,i+1} \gets 1$
+		\EndFor
 
-Therefore, an estimation of $r_n$ is used to measure how good is the approximation.
+		\For{$j\in\{0, \dots, 5\}$}
+			\State $A_{6,j+1} \gets -\frac{c_j}{c_6}$
+		\EndFor
 
-Also we adopt two suggestions from \cite{boyd:2013}.
-The first is to divide the interval into $K$ subintervals to achieve a precision without having to increase the degree of the interpolant too much.
-The second is to use a couple of Newton's iterations to refine the roots found.
+		\State $Q \gets \{\}$
 
-Let $\theta^*$ be a root of $f_n$, then we measure the error associated with that root as $|\xi(\theta^*)|$.
-For the numerical experiments, we considered every triplet of points from an instance with $25$ points.
-Then for some values of $K$ and $n$ we define the error as the maximum error for every root that were found.
+		\ForAll{$q \in eig(A)$} \Comment{$eig(A)$ returns every eigenvalue of $A$.}
+		\State $\theta\gets angle(q)$
+		\If{$|\theta|=1$}
+			\State $Q \gets Q \cup \{\theta\}$
+		\EndIf
+		\EndFor
 
-\begin{figure}
-	\centering
-	\caption{The interpolation error measured on roots that were found.}
-	\includegraphics{tex/figures/interpolant_error}
-	\fautor
-	\label{fig:interpolant_error}
-\end{figure}
+		\State $Sols\gets\{\}$
+		\ForAll{$\theta\in Q$}
+		\State Let $c$ be the center of the circumscribe circle of the points $(0,0); \varphi(\hat{v}, \theta); \varphi(\hat{w}, \theta)$.
+		\State $Sols \gets \cup \{(\theta, \varphi^{-1}(c, \theta)+u)\}$
+		\EndFor
 
-\begin{figure}
-	\centering
-	\caption{The interpolation error measured on roots that were found after three Newton's iterations.}
-	\includegraphics{tex/figures/interpolant_error_after_newton}
-	\fautor
-	\label{fig:interpolant_error_after_newton}
-\end{figure}
+		\State \Return $Sols$
+		\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}

### 2020-01-08 defesa/tex/chapter/e3p.tex
wip

@@
 This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle.
-This process can be parametrized by the angle of rotation of the points, as described by
+This process can be parameterized by the angle of rotation of the points, as described by
 
@@
 \end{equation}
-Because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.
 
@@
 
+\subsection{The circumradius problem}
+
 After that transformation, the problem to be solved is the one of checking the existence of a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$ with radius $b$.
-Notice that the problems are indeed equivalent, which implies that a bijection between the set of solutions of each problem exists.
+Note that the problems are indeed equivalent: $\varphi$ is a linear function, thus its inverse $\varphi^{-1}$ is well defined and can be used to determine a bijection between the set of solutions of both problems.
 Working with this problem instead is preferred because of the reduction in the number of variables from three to one.
@@
 In \autoref{chapter:definitions}, it was stated that any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$.
-Therefore, half of the roots of $\xi$ are in $[\pi, 2\pi)$ and can be ignored.
+Therefore, half of the roots of $\xi$ are in $[\pi, 2\pi)$ and can be dismissed.
 \end{proof}

### 2020-01-09 defesa/tex/chapter/e3p.tex
wip

@@
 
-Initially, E3PNT is a problem with $3$ unknown variables: the two coordinates of the center point $q_x, q_y, $ and the angle of rotation $\theta$.
-In this section, we transform E3PNT into the problem of finding the roots of an univariate function using the known problem of determining the circumcenter of a triangle.
+Initially, E3PNT is a problem with three unknown variables: the two coordinates of the center point $q_x, q_y, $ and the angle of rotation $\theta$.
+In this section, we transform E3PNT into the problem of finding the roots of an univariate function using the known problem of determining the circumcircle of a triangle.
 We also show E3PNT has at most $6$ solutions.
 
-To make the problem simpler, let us translate the system, so the point $u$ is at the origin.
+To make the problem simpler, let us translate the system, so the point $u$ is at the origin; that is, assume that the three points given by the E3PNT instance are $(0, 0); v; w$.
 After that, we assume that the ellipse is actually axis-parallel and the points are the ones rotating.
-When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$.
-This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle.
+When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$ transforming the ellipse into a circle of radius $b$.
+This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed firstly into an axis-parallel ellipse, and then into a circle of radius $b$.
 This process can be parameterized by the angle of rotation of the points, as described by
@@
 \end{equation}
+Also, to make the notation more clear, we denote by $\Lambda(\theta)$ the triangle formed by the points $(0, 0); \varphi(v, \theta); \varphi(w, \theta)$, as long as they are not collinear.
+This being said, we go further to introduce another problem which is equivalent to E3PNT.
 
@@
 
-\subsection{The circumradius problem}
+\subsection{A circumradius problem}
 
-After that transformation, the problem to be solved is the one of checking the existence of a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$ with radius $b$.
-Note that the problems are indeed equivalent: $\varphi$ is a linear function, thus its inverse $\varphi^{-1}$ is well defined and can be used to determine a bijection between the set of solutions of both problems.
-Working with this problem instead is preferred because of the reduction in the number of variables from three to one.
+The term circumradius, in this work, is used to describe the radius of a triangle's circumscribed circle, which is a circle that has the triangle's vertices on its border.
+Given an instance of E3PNT, we define the circumradius problem as the problem of determining an angle of rotation $\theta$, such that the circumradius of $\Lambda(\theta)\in[0, \pi)$ is equal to $b$.
+
+As it can be seen on \autoref{fig:circumscribed-circle}, given an instance of E3PNT and an angle of rotation $\theta\in[0, \pi)$ that makes $\Lambda(\theta)$ have a circumradius $b$; a solution for E3PNT can be obtained using the inverse transformation $\varphi^{-1}$.
+This is possible because for any fixed $\theta$, $\varphi$ is just a linear function which are known to be invertible.
+With that in mind, it is possible to conclude that both problems are equivalent because, from a solution of one, an unique solution of the other can be obtained.
+
+The main reason to work with this problem is the reduction in the number of unknown variables from three to just one.
 This idea, however, would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
 
-It turns out that for three non-colinear points, there is always an unique circumscribed circle.
+It turns out that for three non-collinear points, there is always an unique circumscribed circle.
 Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the expression
@@
 \end{equation}
-with $A(\theta)$ being the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$ (for more details about \autoref{eq:circumscribed_circle} see \citeonline[p.~189]{johnson1960}
-). It is important to note that the transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
+with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle see \citeonline[p.~189]{johnson1960}
+). It should be pointed out that the transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
 
-With the formula for the circumradius in hands, a function can be defined, such that its roots provide solutions for E3PNT.
+With the formula for the circumradius in hands, a function can be defined, such that its roots provide solutions for the circumradius problem.
 Imposing the radius $R$ to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as
@@
 
-Before continuing with this approach of trying to determine the roots of $\xi$, it is important to answer the question whether this set of roots is finite or not?
-Answering this question is also important because it automatically relates to the question about the number of solutions of E3PNT.
+The next step is then to develop an algorithm to find every root of $\xi$.
+Before continuing with this approach though, it is important to address the question about the number of roots of $\xi$ in the interval $[0, \pi)$.
 
@@
 Of course doing that is only possible for a finite number of solutions.
-Also, given that it is limited, discovering a bound for it is essential for determining the efficiency of the algorithm.
+Moreover, even if the number of solutions is finite, discovering a bound for it is essential for determining the algorithm's efficiency.
 
@@
 The interpolation was run for several degrees for every triplet of points present in an instance from \citeonline{canbolat}.
-We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found.
+We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found; simply put we measure how close the roots are to zero.
 
@@
 A parameter $K$ is also used in the experiments.
-This is an idea suggested in \citeonline{boyd:2013} to improve accuracy.
-This parameter represents the number of sub-intervals that $[0, \pi)$ is divided into.
-This way $K$ interpolations are used to obtain every root in the whole interval.
+This is an idea suggested in \citeonline{boyd:2013} to improve accuracy, this parameter represents the number of sub-intervals that $[0, \pi)$ is divided into.
+This way, $K$ interpolations are used to obtain every root in the whole interval.
 It can be seen in \autoref{fig:interpolant_error} that this strategy helps a lot in improving the accuracy even when not so large degrees are used.
@@
 
-Assuming that an algorithm to obtain the eigenvalues of a matrix, the following algorithm to obtain every solution of E3PNT is described as follows.
+Assuming that an algorithm to obtain the eigenvalues of a matrix, the following algorithm to obtain every solution of E3PNT is described in \autoref{algoritmo:e3p}.
+
+\section{Numerical Experiments}
+
+\begin{figure}
+	\centering
+	\caption{The interpolation error measured on roots that were found.}
+	\includegraphics{tex/figures/e3p_error}
+	\fautor
+	\label{fig:e3p_error}
+\end{figure}
 
 \begin{algoritmo}
-	\caption{Algorithm for E3P.}\label{algoritmo:e3p}
+	\caption{The algorithm for E3P.}\label{algoritmo:e3p}
 	\begin{algorithmic}[1]
@@
 
-		\For{$i\in\{1, \dots, 6\}$}
+		\For{$i\in\{1, \dots, 6\}$}\Comment{Constructing the companion matrix.}
 			\State $A_{i,i+1} \gets 1$
-		\EndFor
-
-		\For{$j\in\{0, \dots, 5\}$}
-			\State $A_{6,j+1} \gets -\frac{c_j}{c_6}$
+			\State $A_{6,i} \gets -\dfrac{c_{i-1}}{c_6}$
 		\EndFor
@@
 		\ForAll{$\theta\in Q$}
-		\State Let $c$ be the center of the circumscribe circle of the points $(0,0); \varphi(\hat{v}, \theta); \varphi(\hat{w}, \theta)$.
-		\State $Sols \gets \cup \{(\theta, \varphi^{-1}(c, \theta)+u)\}$
+		\State Let $c$ be the center of the circumscribe circle of $\Lambda(\theta)$.
+		\State $Sols \gets \cup \{(\varphi^{-1}(c, \theta)+u, \theta)\}$
 		\EndFor

### 2020-01-09 defesa/tex/chapter/e3p.tex
wip

@@
 
-It is possible to make another reduction to obtain a degree-$6$ polynomial, this can lower the size of the companion matrix utilized on obtaining the roots of $h$ from $12^2=144$ to $6^2=36$.
+It is possible to make another reduction to obtain a degree-$6$ polynomial.
 As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
@@
 As the angle of one of the roots will not be between $[0, \pi)$ we can ignore one of them.
-Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the following identity
+Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the identity
 \begin{equation}
@@
 \end{equation}
-Finally, using the QR algorithm mentioned in \autoref{chapter:definitions}, a $\bigO(n^3)$ algorithm can be constructed for E3PNT.
-Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm that takes around $6^3$ operations.
 
@@
 \end{equation}
-for $k=0, \dots, 6$. For now, we neither have any ideas on how \autoref{eq:palindromic_pol} could be proved nor how it could be used for further improving our algorithm.
+for $k=0, \dots, 6$. For now, we neither have any ideas on how \autoref{eq:palindromic_pol} could be proved nor how it could be used to find the roots of $f$.
 
-Assuming that an algorithm to obtain the eigenvalues of a matrix, the following algorithm to obtain every solution of E3PNT is described in \autoref{algoritmo:e3p}.
+Finally, in the next section we use this approach of converting $\xi$ into a complex polynomial to develop an algorithm for E3PNT.
 
-\section{Numerical Experiments}
+\section{An algorithm for E3PNT}
 
-\begin{figure}
-	\centering
-	\caption{The interpolation error measured on roots that were found.}
-	\includegraphics{tex/figures/e3p_error}
-	\fautor
-	\label{fig:e3p_error}
-\end{figure}
+Among the approaches that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
+The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation.
+Ultimately this approach requires finding the eigenvalues of a companion matrix, this matrix, however, is usually going to be larger than the $6\times 6$, which is the size of the matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.
+
+Details about getting the eigenvalues of a companion matrix, or determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity and can be found elsewhere in this work.
+Also, we assume that the $angle$ function used in the algorithm returns the angle of a complex number in the interval $[0, 2\pi)$.
 
@@
 			\State $A_{i,i+1} \gets 1$
-			\State $A_{6,i} \gets -\dfrac{c_{i-1}}{c_6}$
+			\State $A_{6,i} \gets -\dfrac{c_{2(i-1)}}{c_{12}}$
 		\EndFor
@@
 		\ForAll{$q \in eig(A)$} \Comment{$eig(A)$ returns every eigenvalue of $A$.}
-		\State $\theta\gets angle(q)$
+		\State $\theta\gets \min\{angle(-q)/2, angle(q)/2\}$
 		\If{$|\theta|=1$}
-			\State $Q \gets Q \cup \{\theta\}$
+			\State Let $c$ be the center of the circumscribe circle of $\Lambda(\theta)$.
+			\State $Q \gets Q\cup \{(\varphi^{-1}(c, \theta)+u, \theta)\}$
 		\EndIf
@@
 
-		\State $Sols\gets\{\}$
-		\ForAll{$\theta\in Q$}
-		\State Let $c$ be the center of the circumscribe circle of $\Lambda(\theta)$.
-		\State $Sols \gets \cup \{(\varphi^{-1}(c, \theta)+u, \theta)\}$
-		\EndFor
-
-		\State \Return $Sols$
+		\State \Return $Q$
 		\EndProcedure
@@
 \end{algoritmo}
+
+\begin{teorema}
+	The \autoref{algoritmo:e3p} computes every solution of E3PNT in $\bigO(1)$ operations.
+\end{teorema}
+
+\begin{proof}
+	It has already been shown that computing every root of $\xi$ through the complex polynomial yields every solution of E3PNT, the only thing left to prove is the running time of the algorithm.
+	Computing every eigenvalue of a matrix can be done in $\bigO(n^3)$, but as for our case $n$ is fixed at $6$, it can be stated that computing the eigenvalues for the companion matrix of $f$ can be done in $\bigO(1)$.
+Therefore, the whole algorithm runs in constant time.
+\end{proof}
+
+\subsection{Numerical Experiments}
+
+In this section we show the results of an experiment made to study the numerical stability of \autoref{algoritmo:e3p}.
+For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.
+
+We generate random instances according to a normal distribution with $0$ mean and standard deviation $K$.
+We tried different values for $K$ and generated $1000$ instances for each one.
+The maximum error and the average error for different values of $K$ can be seen in \autoref{fig:e3p_error}.
+
+From this experiment we can say that \autoref{algoritmo:e3p} has a good numerical stability as the accuracy of the roots found shows to have a linear relation .
+
+\begin{figure}
+	\centering
+	\caption{The interpolation error measured on roots that were found.}
+	\includegraphics{tex/figures/e3p_error}
+	\fautor
+	\label{fig:e3p_error}
+\end{figure}

### 2020-01-11 defesa/tex/chapter/e3p.tex
wip

@@
 
-Among the approaches that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
+Among the methods that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
 The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation.
-Ultimately this approach requires finding the eigenvalues of a companion matrix, this matrix, however, is usually going to be larger than the $6\times 6$, which is the size of the matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.
+Ultimately, this method requires finding the eigenvalues of a companion matrix, which is usually going to be larger than the $6\times 6$, which is the size of the companion matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.
 
-Details about getting the eigenvalues of a companion matrix, or determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity and can be found elsewhere in this work.
-Also, we assume that the $angle$ function used in the algorithm returns the angle of a complex number in the interval $[0, 2\pi)$.
+Details about getting the eigenvalues of a companion matrix, and determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity. 
+Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}).
+This way, $c_0, \dots, c_{12}$ can be written as functions of E3PNT's instance.
 
@@
 
-		\State $\hat{u}\gets (0,0)$
+		\State $\hat{u}\gets (0,0)$ \Comment{Translate the system, so $u$ is at the origin.}
 		\State $\hat{v} \gets v-u$
@@
 
-In this section we show the results of an experiment made to study the numerical stability of \autoref{algoritmo:e3p}.
+In this section we show the results of an experiment we made to study the numerical stability of \autoref{algoritmo:e3p}.
 For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.

### 2020-01-11 defesa/tex/chapter/e3p.tex
wip

@@
 Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}).
-This way, $c_0, \dots, c_{12}$ can be written as functions of E3PNT's instance.
+This way, $c_0, \dots, c_{12}$ can be written as functions of a E3PNT's instance.
 
@@
 In this section we show the results of an experiment we made to study the numerical stability of \autoref{algoritmo:e3p}.
-For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.
 
-We generate random instances according to a normal distribution with $0$ mean and standard deviation $K$.
-We tried different values for $K$ and generated $1000$ instances for each one.
-The maximum error and the average error for different values of $K$ can be seen in \autoref{fig:e3p_error}.
+We generate random instances of E3PNT according to
+\begin{equation}
+u, v, w \sim \mathcal{N}(0, K^2),
+\end{equation}
+with $K\in \R_{>0}$ being a parameter of the experiment. We also define the ellipse's shape parameters ass
+\begin{align}
+	a = K\\
+	b = \frac{K}{2}.
+\end{align}
+For the experiment, we tried several values for $K$ and adopted the error measure to be $|\xi(\hat{\theta})|$, with $\hat{\theta}$ being a root of the complex polynomial $h$. 
+For each different value of $K$, we ran the algorithm for $1000$ random instances.
+The results are shown in \autoref{fig:e3p_error} where the maximum and the average error  is plotted for each value of $K$ for which the experiment was run.
 
-From this experiment we can say that \autoref{algoritmo:e3p} has a good numerical stability as the accuracy of the roots found shows to have a linear relation .
-
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 \end{figure}
+
+From this experiment, it is possible to conclude that the accuray of \autoref{algoritmo:e3p} is acceptable when the instance of E3PNT has numerical values within the box $[-10^5, 10^5]^2$.
+A more rigorous study on the numerical stability of E3PNT is left as future work.

### 2020-01-13 defesa/tex/chapter/ellipses.tex
wip

--- 2019-03-29 tex/chapter/ellipses.tex
@@
-In this chapter, two versions of the Planar Maximal Covering by Ellipses Problem will be introduced.
-Firstly, the axis-parallel variant will be defined and a method for it will be developed.
-Secondly, the version where there is no axis-parallel constraint and the ellipses can be freely rotated will be introduced.
+In this chapter, we introduce the version of PMCLP where every 
+facility has an axis-parallel ellipse as its coverage area.
+We refer to this problem as \sigla{MCE}{Maximum Covering by Ellipses}.
+We also present an algorithm for it which is an adaptation of the algorithm developed for MCD in \autoref{chapter:pmclp}.
 
-\section{Axis-Parallel}
-The maximal planar covering using axis-parallel ellipses was first introduced in \cite{canbolat} which proposed a mixed integer non-linear programming method for the problem.
+\section{Definition}
+
+Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}.
+Note that all it takes to describe an axis-parallel ellipse is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, also called its shape parameters, and a center point $q \in \R^2$.
+
+An instance of MCE is given by a set of $n$ demand points $\Pp = \{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ ellipses $\E = \{E_1, \dots, E_m\}$, which represents the facilities and are used to cover the demand set.
+Additionally,
+a list of weights $\Ww:=\{w_1, \dots, w_n\}$ and a list of shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$ are given.
+The weight of the $j$-th point is $w_j\in\R_{>0}$, and the shape parameters of the $j$-th ellipse is given by $(a_j, b_j)\in\R_{>0}^2$, with $a_j>b_j$.
+To make the text more clear, we denote an instance of MCE as $\Pi:=(\Pp, \Ww, \Rr)$.
+
+A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
+The coverage region of $j$-th ellipse centered at $q_j$ is denoted by $E_j(q_j)$.
+Finally, let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem
+
+\begin{equation}
+\max_q w\left(\bigcup_{j=1}^m \Pp \cap E_j(q_j)\right).
+\end{equation}
+
+Firstly, we describe a method for the case with only one ellipse, and then use it in the algorithm for multiple ellipses to construct a CLS containing an optimal solution.
+
+\section{Related work}
+The maximal planar covering using axis-parallel ellipses was first introduced in \citeonline{canbolat} which proposed a mixed integer non-linear programming method for the problem.
 This first approach showed to be not that efficient as it could not find an optimal solution for some instances within a timeout defined by them.
@@
 
-The second work found in the literature was \cite{andreta}, which developed a method that breaks the problem into smaller ones fixing the set of points an ellipse is going to cover.
+The second work found in the literature was \citeonline{andreta}, which developed a method that breaks the problem into smaller ones fixing the set of points an ellipse is going to cover.
 For each set of points fixed as the points an ellipse is going to cover, a small optimization problem is solved to find out if there is a location where the ellipse can be placed, so to cover the set of fixed points.
@@
 
-\subsection{Notation and definition of the problem}
+\section{One Ellipse Version}
 
-Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}.
-Therefore, all it takes to describe one is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, also called the shape parameters, and a center point $q \in \R^2$.
-
-Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$ is a pair of real numbers called the shape parameters of an ellipse.
-In the general case, every point has weights, but without loss of generality (later explained), this detail will be ignored and the weights are assumed to be unitary.
-The notation used here is similar to the one introduced on \autoref{chapter:pmclp}, the ellipse with an undefined center is referred to as $E$.
-To denote the ellipse with center set to be at point $q$, $E(q)$ is used.
-Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse} (in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$).
-Hence, the problem can be defined as follows.
-
-\begin{definicao}
-Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by
-
+Firstly, the case with only one ellipse is considered.
+An instance of it has $m=1$, and we set $(a, b):=(a_1, b_1)$ and $\E := \{E\}$.
+We refer to this version as \sigla{MCE-1}{Maximum Cover by One Ellipse} and a solution of it is given by a point $q\in\R^2$.
+Also, an optimal solution of MCE-1 is given by
 \begin{equation}
-    \max_q |\Pp \cap E(q)|.
+\max_q w(\Pp \cap E(q)).
 \end{equation}
-\end{definicao}
-
-\subsection{One Disk algorithm adaptation}
 
@@
 
-The intersection of two ellipses as well as determining $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ is described thoroughly in \autoref{chapter:ellipses_intersection}.
+The intersection of two ellipses as well as determining $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ are described thoroughly in \autoref{chapter:ellipses_intersection}.
 
@@
 
-\subsection{Multiple ellipses}
+\section{An algorithm for MCE}
 
-The multiple ellipses case is handled using the same idea of the multiple disks case.
-The only difference is that an instance of the multiple ellipses may contain ellipses of different shapes, which does not happen for the disks case as every disk has the same radius.
-For this reason, a different pre-processing has to be done for every one of them.
+The basis of the algorithm for MCE that will be described in this section is the adaptation of the algorithm for MCE-1, so it returns a CLS for every ellipse in $\E$.
+Once a CLS is obtained for every facility, a simple complete search can be done to find an optimal solution.
+The procedure that does that is described by procedure MCE-CLS in \autoref{algoritmo:mce1}.
 
-An instance of the multiple ellipses case is denoted as $MCE(\Pp, \E)$, with $\Pp$ being a set of $n$ points and $\E = \{E_1, \dots, E_m\}$ being a set of $m$ ellipses, each one with shape parameters $(a_i, b_i) \in \R^2_{>0}, i = 1 \dots m$.
-Also, without loss of generality, the weight of every point is assumed to be unitary.
+\begin{lema}
+	Given an instance of MCE, and $j\in\{1, \dots, m\}$, then \autoref{algoritmo:mce1}, with $(\Pp; \Ww; (a_j,b_j))$ as its input, takes $\bigO(n^2\log{n})$ computations and returns a CLS of size $\bigO(n^2)$ that contains an optimal solution of the given MCE's instance.
+\end{lema}
 
-\begin{definicao}
-Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by
-
-\begin{equation}
-    \max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|}.
-\end{equation}
-\end{definicao}
+\begin{proof}
+	\autoref{algoritmo:mce1} is an adaption of \autoref{algoritmo:mcd_1}, which relies on the idea of transforming MCD into the MWC problem.
+\end{proof}
 

### 2020-01-13 defesa/tex/chapter/mcd.tex
wip

--- 2020-01-07 defesa/tex/chapter/pmclp.tex
@@
 
-An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ disks $\D:=\{D_1, \dots, D_m\}$, which represents the facilities and are used to cover the demand set.
-Additionally, for every point in $\Pp$ a weight is given, and for every disk in $\D$ a coverage radius is given.
-The weight of the $j$-th point is denoted by $w_j\in\R_{>0}$, and the coverage radius of the $j$-th facility is denoted by $r_j \in \R_{>0}$.
+An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; a set of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$; and $m$ disks given by their radii $\Rr:=\{r_1, \dots, r_m\}$, with $r_j\in\R_{>0}$.
+Additionally, to make the text more clear, we define a set of $m$ disks as $\D = \{D_1, \dots, D_m\}$, with $D_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th disk is located as input, and returns its coverage region as defined by \autoref{eq:disk}.
 
 A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$ which specifies the center of every disk in $\D$.
-The coverage region of the $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{>0}$ be the function
+The coverage region of the $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{\ge0}$ be the function
 
-\begin{equation}
+\begin{equation}\label{eq:subset_w}
 w(A) = \sum_{j : p_j \in A} w_j,
@@
 
-An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; and a set of unit disks $\D:=\{D_1,\dots,D_n\}$, such that $D_i$ is centered at $p_i$, for $i=1,\dots,n$, and with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it.
+An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; a set of unit disks $\D:=\{D_1(p_1),\dots,D_n(p_n)\}$; and a set of weights $\Ww=\{w_1, \dots, w_n\}$ with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it.
+To make the notation less cluttered, we use, in this problem, $D_j:=D_j(p_j)$, for $j\in\{1, \dots, n\}$.
 
@@
 
-\begin{algoritmo}
+\begin{teorema}\label{lema:disk}
+	\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
+\end{teorema}
+
+\begin{proof}
+	Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \citeonline{bentley:1979}. 
+	Because sorting the intersection angles needs to be done, an additional $\bigO(K\log{K})$ pre-processing is added.
+All the other operations can be done in constant time.
+Therefore, the final algorithm complexity is $\bigO((n+K)\log{n})$.
+\end{proof}
+
+If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (the set of disks that intersect with $D_i$, defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.
+
+\begin{algoritmo}[b]
 \caption{Algorithm for MCD-1.}\label{algoritmo:mcd_1}
 \begin{algorithmic}[1]
-\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\{w_1, \dots, w_n\}$.}
+\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$.}
 \Ensure{The maximum cover by a unit disk.}
@@
 
-\begin{teorema}\label{lema:disk}
-\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
-\end{teorema}
-
-\begin{proof}
-    Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \citeonline{bentley:1979}. 
-    Because sorting the intersection angles needs to be done, an additional $\bigO(K\log{K})$ pre-processing is added.
-All the other operations can be done in constant time.
-Therefore, the final algorithm complexity is $\bigO((n+K)\log{n})$.
-\end{proof}
-
-If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (the set of disks that intersect with $D_i$, defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.
-
 \section{Multiple disks}
@@
 
-A simple adaptation can be done on \autoref{algoritmo:mcd_1}, so it returns a CLS that contains an optimal solution for the disk, instead of just finding the best solution.
-Also, the detail that MCD-1 is defined for unit disks can be ignored as \autoref{algoritmo:mcd_1} works for disks of any radius.
+A simple adaptation can be done on \autoref{algoritmo:mcd_1} to make it return a CLS that contains an optimal solution of MCD for that disk. This is shown in \autoref{algoritmo:mcd_cls}. 
+Notice also that MCD-1 is defined only for unit disks, however, this constrained can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius.
+A result about the runtime complexity of \autoref{algoritmo:mcd_cls} has already been given by \autoref{lema:disk}, the following result states about the adaption of it to be used in an algorithm for MCD.
 
-It can be seen that in any solution of MCD, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be an optimal solution.
-The number of points \autoref{algoritmo:mcd_1} goes through is $\bigO(n^2)$, then checking every possible center for every ellipse yields a $\bigO(n^{2m})$ run-time complexity.
+\begin{lema}
+	Suppose that an instance of MCD and an index $j\in\{1, \dots, m\}$ are given.
+	Then \autoref{algoritmo:mcd_cls}, when given the instance $(\Pp, \Ww, r_j)$ as input, returns a CLS $S_j$ of size $\bigO(n^2)$, such that $q^*_j\in S_j$, with $(q^*_1, \dots, q^*_m)$ being an optimal solution of the given MCD's instance.
+\end{lema}
+
+\begin{proof}
+It can be seen that in any solution of MCD, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_cls} as a candidate to be an optimal solution.
+The number of points \autoref{algoritmo:mcd_cls} goes through is $\bigO(n^2)$, then
+obviously $|S_j|=\bigO(n^2)$.
+\end{proof}
+
+Then, with \autoref{algoritmo:mcd_cls}, an algorithm for MCD that checks every possible center for every disk yields a $\bigO(n^{2m})$ run-time complexity.
 This algorithm is described in \autoref{chapter:ellipses} for the axis-parallel ellipses case.
@@
 It is worth mentioning that the choice of developing a different method for the problem, instead of using the one from \citeonline{cabello:2006}, is taken for the sake of simplicity, considering both algorithms achieve similar bounds.
+
+\begin{algoritmo}
+	\caption{Algorithm for MCD-1 that returns a CLS.}\label{algoritmo:mcd_cls}
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$, and a radius $r\in\R_{>0}$.}
+		\Ensure{A CLS for the disk given by radius $r$.}
+
+		\item[]
+
+		\Procedure{$MCD_1$}{$\Pp, \Ww, r$}
+		\State $S \gets \{\}$
+		\ForAll{$p_i \in \Pp$}
+		\State Let $D_i$ be the disk with center at $p_i$
+		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}.
+
+		\State $Cov \gets \{\}$
+		\For{$a \in B_i$}\Comment{Assuming $B_i$ is sorted.}
+		\State Let $q_a$ be the intersection point correspondent to angle $a$. 
+		\State $S \gets S \cup \{q_a\}$	
+		\EndFor
+		\EndFor
+
+		\State \Return $S$
+		\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}

### 2020-01-13 defesa/tex/chapter/mce.tex
wip

--- 2020-01-13 defesa/tex/chapter/ellipses.tex
@@
 
-An instance of MCE is given by a set of $n$ demand points $\Pp = \{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ ellipses $\E = \{E_1, \dots, E_m\}$, which represents the facilities and are used to cover the demand set.
-Additionally,
-a list of weights $\Ww:=\{w_1, \dots, w_n\}$ and a list of shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$ are given.
-The weight of the $j$-th point is $w_j\in\R_{>0}$, and the shape parameters of the $j$-th ellipse is given by $(a_j, b_j)\in\R_{>0}^2$, with $a_j>b_j$.
-To make the text more clear, we denote an instance of MCE as $\Pi:=(\Pp, \Ww, \Rr)$.
+An instance of MCE is given by a set of $n$ demand points $\Pp = \{p_1, \dots, p_n\}$, with $p_j\in\R^2$; 
+a set of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$;
+and a set of $m$ axis-parallel ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
+Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th ellipse is located as input, and returns its coverage region.
 
 A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
-The coverage region of $j$-th ellipse centered at $q_j$ is denoted by $E_j(q_j)$.
 Finally, let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem
@@
 
-Firstly, we describe a method for the case with only one ellipse, and then use it in the algorithm for multiple ellipses to construct a CLS containing an optimal solution.
+In the next sections, we first describe a method for the case with only one ellipse, and then use it in the algorithm for multiple ellipses to construct a CLS containing an optimal solution.
 
@@
 
-Firstly, the case with only one ellipse is considered.
-An instance of it has $m=1$, and we set $(a, b):=(a_1, b_1)$ and $\E := \{E\}$.
-We refer to this version as \sigla{MCE-1}{Maximum Cover by One Ellipse} and a solution of it is given by a point $q\in\R^2$.
-Also, an optimal solution of MCE-1 is given by
+The case with only one ellipse is considered first because it will be adapted to become the basis of the algorithm for more than one ellipse.
+We refer to this version as \sigla{MCE-1}{Maximum Cover by One Ellipse}.
+
+An instance of MCE-1 has $m=1$, and we set $(a, b):=(a_1, b_1)$, and $\E := \{E\}$.
+Therefore, an instance of MCE-1 is described by the tuple $(\Pp; \Ww; (a, b))$.
+A solution of MCE-1 is then given by a point $q\in\R^2$, and an optimal solution is given by the optimization problem
+
 \begin{equation}
@@
 \end{equation}
-
-An adaptation of \autoref{algoritmo:mcd_1} is obtained by just replacing the function that finds the intersection points between two disks by a function that finds the intersection points between two ellipses $E_i$ and $E_j$.
+An adaptation of \autoref{algoritmo:mcd_1} is obtained by just replacing the function that finds the intersection points between two disks by a function that finds the intersection points between two ellipses $\partial E_i$ and $\partial E_j$.
 It can be seen in \autoref{fig:3ellipses_intersect} that the intersection points and their correspondents $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ functions behave the same way as in the disks case.
-
 The intersection of two ellipses as well as determining $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ are described thoroughly in \autoref{chapter:ellipses_intersection}.
@@
 \centering
-
     \caption{Three ellipses and their intersection points}
-    \input{tex/img.ellipses.1.tex}
+    \includegraphics[scale=.32]{tex/figures/3ellipses_intersect.pdf}
     \fautor
@@
 \end{figure}
-
 \section{An algorithm for MCE}
 
-The basis of the algorithm for MCE that will be described in this section is the adaptation of the algorithm for MCE-1, so it returns a CLS for every ellipse in $\E$.
-Once a CLS is obtained for every facility, a simple complete search can be done to find an optimal solution.
-The procedure that does that is described by procedure MCE-CLS in \autoref{algoritmo:mce1}.
-
-\begin{lema}
-	Given an instance of MCE, and $j\in\{1, \dots, m\}$, then \autoref{algoritmo:mce1}, with $(\Pp; \Ww; (a_j,b_j))$ as its input, takes $\bigO(n^2\log{n})$ computations and returns a CLS of size $\bigO(n^2)$ that contains an optimal solution of the given MCE's instance.
-\end{lema}
-
-\begin{proof}
-	\autoref{algoritmo:mce1} is an adaption of \autoref{algoritmo:mcd_1}, which relies on the idea of transforming MCD into the MWC problem.
-\end{proof}
-
-\autoref{algoritmo:mce} describes the adapted version of the maximal disk covering algorithm for the ellipses case.
-In \autoref{algoritmo:mce1}, the $MCE_1$ procedure returns every possible set of points that an ellipse with shape parameters $(a,b)$ can cover.
-With that, procedure $MCE$ does the backtracking process, assigning every possible cover to every ellipse.
-
-As stated in \autoref{lema:disk}, $MCE_1$ runs in $\bigO(n^2\log{n})$, where $n$ is the number of points.
-The number of sets of points an ellipse can cover, however, is $\bigO(n^2)$.
-Note that the $\log{n}$ being part of the complexity is due to sorting the set $A$.
-If $MCE_1$ is called only in a pre-process phase storing its return for every ellipse, a $\bigO(n^{2m})$ run-time complexity can be achieved.
-
-Also, it can be seen that the unitary weights assumption can be easily removed through replacing the way the answer is updated: 
-the weights of the covered points should be added to the answer instead of the number of covered points, this could be done by keeping an extra variable along with every possible set of points an ellipse can cover that is returned by $MCE_1$.
+The same procedure defined in \autoref{algoritmo:mcd_cls} can be used to get a CLS for every ellipse in MCE.
+We refer to the elliptical version of that procedure as $MCE_1$.
+Then, we define \autoref{algoritmo:mce} which just does a complete search in the CLS of every ellipse, therefore, counting every possibility, the runtime complexity of \autoref{algoritmo:mce} is $\bigO(n^{2m})$.
 
 It is worth noting that some easy improvements, which do not change the algorithm's overall complexity, can be made in the implementation.
-For example, if an ellipse covers two sets of points $X$ and $Y$, with $X \subset Y$, then set $X$ can be ignored by the algorithm because of the positive weights constraint.
+For example, if an ellipse covers two sets of points $X$ and $Y$, with $X \subset Y$, then set $X$ can be ignored by the algorithm because of the non-negative weights constraint.
 Also, if two ellipses have their centers with Euclidean distance greater than their semi-major parameter, they for sure do not intersect.
 Depending on the input, this observation can make the algorithm not go through the whole list of ellipses every time it needs to determine the ellipses pairwise intersections.
-
-\begin{algoritmo}
-\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
-%\KwIn{alskdjf}
-
-\begin{algorithmic}[1]
-\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and the shape parameters $(a, b)$ of an ellipse.}
-\Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}
-
-\item[]
-\Procedure{$MCE_1$}{$\Pp, a, b$}
-\State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}
-
-\ForAll{$p_i \in \Pp$}
-\State Let $E_i$ be the ellipse with center at $p_i$ and parameters $(a,b)$
-
-\State Let $I_i$ be the set of ellipses that intersect with $E_i$
-
-%\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $E_i$}
-
-\State $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$ \Comment{The multiset of intersection angles with $E_i$.}
-
-%\ForAll{$j \in I_i$}
-%\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
-%\EndFor
-
-\State $Z \gets Z \cup \{\{p_i\}\}$
-\State $Cov \gets \{p_i\}$ \Comment{The set of active disks.}
-
-\For{$cnt=1..2$} \Comment{Do it twice.}
-\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
-\State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
-\If{$a$ is a starting angle}
-\State $Cov \gets Cov \cup \{p_a\}$
-\Else
-\State $Cov \gets Cov \setminus \{p_a\}$
-\EndIf
-\State $Z \gets Z \cup \{Cov\}$
-\EndFor
-\EndFor
-\EndFor
-
-\State \Return $Z$
-\EndProcedure
-
-\end{algorithmic}
-\end{algoritmo}
 
@@
         \State $ans \gets 0$
-        \For{$E \in \E$}
-        \State Let $(a,b)$ be the shape parameters of $E$
-        \State $Q \gets MCE_1(\Pp, a, b)$
-        \For{$Cov \in Q$}
-        \State $ans \gets \max\{ans, |Cov| + MCE(\Pp \setminus Cov, \E, j+1)\}$ \Comment{Calls the procedure for the next ellipse.}
-        \EndFor
+
+        \State $S_j \gets MCE_1(\Pp, a_j, b_j)$
+        \For{$q \in S_j$}
+        \State $Cov \gets \Pp \cap q$
+        \State $ans \gets \max\{ans, w(Cov) + MCE(\Pp \setminus Cov, \E, j+1)\}$ \Comment{Calls the procedure for the next ellipse.}
         \EndFor

### 2020-01-13 defesa/tex/chapter/mcer.tex
wip

--- 2019-09-27 defesa/tex/chapter/ellipses_n.tex
@@
-This section introduces the covering problem that does not have any axis-parallel constraint for the ellipses, we denote this version of the problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
-The removal of this constraint introduces a new variable which is responsible for determining the rotation angle of every ellipse.
+This section introduces the elliptical PMCLP where there is no axis-parallel constraint, that is, the ellipses can be freely rotated.
+We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
+In comparison with MCE, this problem introduces a new a new variable which is responsible for determining the rotation angle of every ellipse making MCER a more challenging problem.
+
+\section{Definition}
 
 An instance of the non-axis-parallel is defined exactly like the axis-parallel one on \autoref{chapter:ellipses}.
-It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, with every point having a unitary weight, and a set of ellipses $\E=\{E_1, \dots, E_m\}$, with fixed shape parameters $(a_i, b_i) \in \R^2_{>0}$, $i \in \{1, \dots, n\}$ with the additional condition that $a_i > b_i$.
+It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; a list of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$;
+and a set of $m$ axis-parallel ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
+Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2\times\R^2 \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region.
+
 Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, \pi)^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$, which is given by \autoref{eq:rotated_ellipse_co}.
-Also, $\Pp \cap E_i(q_i, \theta_i)$ is denoted as the set of points covered by $E_i$ on this configuration.
-Therefore MCER is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the number of points covered by the $m$ ellipses, which is given by \autoref{eq:optMCEn}.
+Therefore MCER is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the weight of points covered by the $m$ ellipses, which is given by
 
 \begin{equation}\label{eq:optMCEn}
-\max_{Q, \Theta}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i, \theta_i)\right|}.
+\max_{Q, \Theta}{w\left(\bigcup_{i=1}^{m} \Pp \cap E_i(q_i, \theta_i)\right)}.
 \end{equation}

### 2020-01-13 defesa/tex/chapter/mcer.tex
wip

@@
 Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2\times\R^2 \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region.
+Lastly, an instance of MCER is defined as the tuple $(\Pp, \Ww, \Rr)$.
 
@@
 \end{equation}
-
-An additional notation is used on this chapter, $\tilde{E_i}(q_i, \theta_i)$ is defined to be the set of points on the border of $E_i(q_i, \theta_i)$, specially, the operation $\Pp \cap \tilde{E_i}(q_i, \theta_i)$ is used to refer to the set of points from $\Pp$ that lie on the border of $E_i(q_i, \theta_i)$.
+Next, we introduce a proposition which says that given an optimal solution of MCER, it is possible to find another optimal solution with two points on the border of every ellipse that is already covering at least two points.
 
 \begin{proposicao}\label{lema:mce_2b}
-	Let $(\Pp, \E)$ be an instance of MCER.
-In an optimal solution of MCER, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j)=\Pp \cap E_j(q_j, \theta_j)$ and $\Pp \cap \tilde{E_j}(q_j', \theta_j) \ge 2$.
+	Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
+Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j^*)=\Pp \cap E_j(q_j^*, \theta_j^*)$ and $\Pp \cap \partial E_j(q_j', \theta_j^*) \ge 2$.
 \end{proposicao}
 
-\begin{demonstracao}
+\begin{proof}
 	First, the angle of rotation can be ignored as it does not change.
 
-	Let $A=\Pp \cap E_j(q_j, \theta_j)$ be the set of points covered by $E_j$ and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point from $A$.
+	Let $A=\Pp \cap E_j(q_j^*, \theta_j)$ be the set of points covered by the $j$-th ellipse and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point from $A$.
 
@@
 As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertex.
-Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \tilde{E}_j(q_j', \theta_j)| \ge 2$.
+Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
 
-\end{demonstracao}
+\end{proof}
 
@@
 \begin{definicao}\label{def:feasible_angle}
-	Let $E$ be an ellipse and $u, v \in \R^2$. An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
+	Let $E$ be the coverage region of an ellipse and $u, v \in \R^2$.
+An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
 \end{definicao}
@@
 On \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
-On one of them, an ellipse is rotated by $\pi/4$ and it is located such that it contains the two fixed points on its border.
+On one of them, an ellipse is rotated by $\pi/4$ and it is located, such that it contains the two fixed points on its border.
 That means $\pi/4$ is a $(E, u, v)$-feasible angle.
@@
 \begin{lema}\label{lema:3pnts}
-	Let $(\Pp, \E)$ be an instance of MCER, in an optimal solution, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j, \theta_j)|>2$, at least one of the two cases is true:
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
+Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$, at least one of the two cases is true:
 
-	\begin{enumerate}
-		\item There is $q', \theta'$, and $\{u, v, w\} \subset \Pp \cap E_j(q_j, \theta_j)$, such that $\{u, v, w\} \subset \tilde{E}(q', \theta')$.
+	\begin{enumerate}[label=(\alph*)]
+		\item There is $q', \theta'$, and $\{u, v, w\} \subset \Pp \cap E_j(q_j, \theta_j)$, such that $\{u, v, w\} \subset \partial E_j(q', \theta')$.
 
-		\item Let $A=\Pp \cap E_j(q_j, \theta_j)$, and $u, v \in A$ such that there exists $\hat{q}_j$ such that $\{u, v\} \subset \tilde{E_j}(\hat{q}_j, \theta_j)$ and $A \subset E_j(\hat{q}_j, \theta_j)$.
-Then for any $(E_j, u, v)$-feasible angle $\theta \in [0, 2\pi]$, there exists $\bar{q}_j$ such that $\{u, v\} \subset \tilde{E_j}(\bar{q}_j, \theta)$ and $A \subset E_j(\bar{q}_j, \theta)$.
+		\item Let $A=\Pp \cap E_j(q_j^*, \theta_j^*)$, and $u, v \in A$, such that there exists $\hat{q}_j$, with $\{u, v\} \subset \partial E_j(\hat{q}_j, \theta_j^*)$ and $A \subset E_j(\hat{q}_j, \theta_j^*)$.
+Then, for any $(E_j, u, v)$-feasible angle $\theta \in [0, 2\pi]$, there exists $\bar{q}_j$ such that $\{u, v\} \subset \partial E_j(\bar{q}_j, \theta)$ and $A \subset E_j(\bar{q}_j, \theta)$.
 	\end{enumerate}

### 2020-01-14 defesa/tex/chapter/mce.tex
wip

@@
 and a set of $m$ axis-parallel ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
-Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th ellipse is located as input, and returns its coverage region.
+Additionally, to make the text more clear, we define a set $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{equation:cover_pellipse}.
 
-A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
+Then, a solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
 Finally, let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem
@@
 We refer to the elliptical version of that procedure as $MCE_1$.
-Then, we define \autoref{algoritmo:mce} which just does a complete search in the CLS of every ellipse, therefore, counting every possibility, the runtime complexity of \autoref{algoritmo:mce} is $\bigO(n^{2m})$.
+Then, we define \autoref{algoritmo:mce} which just does a complete search in the CLS of every ellipse, therefore, counting every possibility, the run-time complexity of \autoref{algoritmo:mce} is $\bigO(n^{2m})$.
 
@@
 
+\section{Ellipses' costs and utilization constraint}
+
+Additionally, in \citeonline{andreta} and \citeonline{canbolat}, two other parameters are present in the definition of the problem.
+One of them is the cost of each ellipse, which is defined as a list $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the cost of the $j$-th ellipse.
+The other parameter is a number $K\in \mathbb{N}$ which introduces a restriction on the number of ellipses that can be used (we will consider the equality restriction, that is, the number of ellipses utilized must be equal to $K$).
+We refer to this version of the problem as \sigla{MCE-K}{Maximum Covering by Ellipses with a $K$-constraint}.
+
+We use \autoref{algoritmo:mce} to develop an algorithm for MCE-K as follows.
+Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = K$, we invoke the algorithm for MCE for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$, note that we also need to keep track of the cost of using the ellipses whose indexes are in $I$.
+This simple adjustment achieves a run-time complexity of $\binom{n}{k} \times \bigO(n^{2m}) = \bigO(n^{2m})$.
+
 \begin{algoritmo}
-    \caption{Algorithm for $MCE(\Pp, \E)$ with unit weights}\label{algoritmo:mce}
+    \caption{Algorithm for MCE}\label{algoritmo:mce}
     \begin{algorithmic}[1]
-        \Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and a set of ellipses $\E = \{E_1, \dots, E_m\}$.}
-        \Ensure{The maximum number of points that can be covered by the set of ellipses $\E$.}
+        \Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}
+
+        \Ensure{The value of an optimal solution of MCE.}
 

### 2020-01-14 defesa/tex/chapter/mce.tex
wip

@@
 The same procedure defined in \autoref{algoritmo:mcd_cls} can be used to get a CLS for every ellipse in MCE.
-We refer to the elliptical version of that procedure as $MCE_1$.
-Then, we define \autoref{algoritmo:mce} which just does a complete search in the CLS of every ellipse, therefore, counting every possibility, the run-time complexity of \autoref{algoritmo:mce} is $\bigO(n^{2m})$.
+We refer to the elliptical version of that procedure as $MCE_1$ (we do not define it in this chapter because it would look the same as $MCD_1$, apart from the name, of course).
 
-It is worth noting that some easy improvements, which do not change the algorithm's overall complexity, can be made in the implementation.
+Then, with the algorithm to construct a CLS for every ellipse in hands, an algorithm for MCE naturally comes into existence.
+In \autoref{algoritmo:mce}, a complete search is done backtracking every possibility in the CLS of every ellipse.
+This strategy is backed-up by \autoref{lema:mcd}, which says that there is an optimal solution in the CLS of each ellipse.
+Following this, counting every possibility that the algorithm goes through, we arrive at the run-time complexity of $\bigO(n^{2m})$.
+
+It is worth mentioning that, even though we call $MCE_1$ every time in the recursion, in practice, it is probably best to pre-process this step, and only call it $m$ times for the whole set of points.
+Some other easy improvements can also be made in the implementation.
 For example, if an ellipse covers two sets of points $X$ and $Y$, with $X \subset Y$, then set $X$ can be ignored by the algorithm because of the non-negative weights constraint.
@@
 
-\section{Ellipses' costs and utilization constraint}
+\section{Adding facility cost}
 
 Additionally, in \citeonline{andreta} and \citeonline{canbolat}, two other parameters are present in the definition of the problem.
-One of them is the cost of each ellipse, which is defined as a list $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the cost of the $j$-th ellipse.
-The other parameter is a number $K\in \mathbb{N}$ which introduces a restriction on the number of ellipses that can be used (we will consider the equality restriction, that is, the number of ellipses utilized must be equal to $K$).
-We refer to this version of the problem as \sigla{MCE-K}{Maximum Covering by Ellipses with a $K$-constraint}.
+This augmentation is caused by the introduction of a cost associated with each ellipse.
+Then, of course, having a cost for each facility only makes sense if there is a decision to be made about which ones are used.
+Therefore, another parameter $k\in\mathbb{N}$ is also given, and the problem is defined, such that exactly $k$ ellipses need to be selected to cover the demand set.
 
-We use \autoref{algoritmo:mce} to develop an algorithm for MCE-K as follows.
-Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = K$, we invoke the algorithm for MCE for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$, note that we also need to keep track of the cost of using the ellipses whose indexes are in $I$.
-This simple adjustment achieves a run-time complexity of $\binom{n}{k} \times \bigO(n^{2m}) = \bigO(n^{2m})$.
+We refer to this version of the problem as  \sigla{MCE-k}{Maximum Covering by Ellipses with a $k$-constraint}.
+An instance of it is given by the same parameters as MCE, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the cost of the $j$-th ellipse, and $k\in\mathbb{N}$.
+
+ A solution for MCE-k, however,  when compared to MCE's, has a bit more cluttered description.
+We define it as a set $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$, such that $|I|=k$; and a tuple $Q:=(q_1, \dots, q_k)$, with $q_j\in\R^2$ being the center of the $j$-th ellipse in $I$.
+An optimal solution of MCE-k is given by the optimization problem
+
+\begin{equation}
+\max_{I, Q} w\left(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j)\right).
+\end{equation}
+
+Finally, \autoref{algoritmo:mce} can serve as basis for an algorithm for MCE-k. 
+Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
+After that, by keeping track of the costs of the utilized ellipses for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
+This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k})$.
 
@@
 
-        \Procedure{$MCE$}{$\Pp, \E, j=1$}
+        \Procedure{$MCE$}{$\Pp, \Ww, \Rr, j=1$}
         \If{$j = m+1$}
@@
         \State $Cov \gets \Pp \cap q$
-        \State $ans \gets \max\{ans, w(Cov) + MCE(\Pp \setminus Cov, \E, j+1)\}$ \Comment{Calls the procedure for the next ellipse.}
+        \State $ans \gets \max\{ans, w(Cov) + MCE(\Pp \setminus Cov, \Ww, \Rr, j+1)\}$ \Comment{Calls the procedure for the next ellipse.}
         \EndFor

### 2020-01-14 defesa/tex/chapter/mcer.tex
wip

@@
-This section introduces the elliptical PMCLP where there is no axis-parallel constraint, that is, the ellipses can be freely rotated.
+This section introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated.
 We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
-In comparison with MCE, this problem introduces a new a new variable which is responsible for determining the rotation angle of every ellipse making MCER a more challenging problem.
+In comparison with MCE, this problem introduces a new variable which is responsible for determining the rotation angle of every ellipse making MCER a more challenging problem.
 

### 2020-01-15 defesa/tex/chapter/definicoes.tex
wip

@@
 
+Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
+Suppose that this line intersects the ellipse at a least one point, then plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points.
+The final expression is given by
+\begin{equation}\label{eq:dist_line_ellipse}
+D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
+\end{equation}
+with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters.
+It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$.
+From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $(-\infty, D(m, 0)]$.
+Following that, the function $D(m, 0)^2$ is also a parabola, as a
+
 \subsection{Non-axis-parallel}

### 2020-01-15 defesa/tex/chapter/mcer.tex
wip

@@
 We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
-In comparison with MCE, this problem introduces a new variable which is responsible for determining the rotation angle of every ellipse making MCER a more challenging problem.
+In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem.
 
@@
 It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; a list of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$;
-and a set of $m$ axis-parallel ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
-Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2\times\R^2 \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region.
+and $m$ ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
+Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2\times\R^2 \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
 Lastly, an instance of MCER is defined as the tuple $(\Pp, \Ww, \Rr)$.
@@
 \end{equation}
+In addition to that, we define an equivalence relation between solutions of MCER.
+As likely expected, we say that two solutions are equivalent if the set of points covered by them is the same.
+In other words, two solutions of MCER $(Q, \Theta)$ and $(Q', \Theta')$ are said to be equivalent if, and only if
+$$\bigcup_{j=1}^m\Pp \cap E_j(q_j', \theta_j') = \bigcup_{j=1}^m\Pp \cap E_j(q_j, \theta_j).$$
+
 Next, we introduce a proposition which says that given an optimal solution of MCER, it is possible to find another optimal solution with two points on the border of every ellipse that is already covering at least two points.
@@
 	Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. 
-Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, there is $q_j'$ such that $\Pp \cap E_j(q_j', \theta_j^*)=\Pp \cap E_j(q_j^*, \theta_j^*)$ and $\Pp \cap \partial E_j(q_j', \theta_j^*) \ge 2$.
+	Then, for any $E_j \in \E$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, 
+	an equivalent solution $(Q', \Theta^*)$ exists, such that $|\Pp \cap \partial E_j(q_j', \theta_j^*)|\ge 2$.
 \end{proposicao}
@@
 	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses.
-As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertex.
+As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point, creating a vertex.
 Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
@@
 An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
+In addition to that, given an instance of MCER, we refer to the set of $(E_j, u, v)$-feasible angles as
+
+	\begin{equation}
+	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
+	\end{equation}
 \end{definicao}
 
-On \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
-On one of them, an ellipse is rotated by $\pi/4$ and it is located, such that it contains the two fixed points on its border.
-That means $\pi/4$ is a $(E, u, v)$-feasible angle.
-On the other example, the ellipse is rotated by $\pi/2$ and there is not a center where the ellipse can be placed so it contains the two fixed points--they are too far apart.
-This makes $\pi/2$ a not $(E, u, v)$-feasible angle.
+In \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
+The example with a solid contour shows an ellipse rotated by $\pi/4$ with two points on its border, making $\pi/4$ a $(E, u, v)$-feasible angle.
+The other example, with a dashed contour, presents a case where an ellipse rotated by $\pi/2$ is not able to have the two points on its border, no matter where it is placed; because of that, $\pi/2$ is said to be a not $(E, u, v)$-feasible angle.
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
-	\includegraphics{tex/figures/scripts/feasible-angle}
+	\includegraphics[scale=.8]{tex/figures/scripts/feasible-angle}
 	\fautor
@@
 \end{figure}
+
+In \autoref{chapter:definitions}, it was stated that the line that has the most distant intersection points with an ellipse is the one that passes through the origin, given that the linear parameter is fixed.
+It also says that the function $D$ given by \autoref{eq:dist_line_ellipse}, which represents the distance between the intersection points (it is negative when there is no intersection), attains every value less than its maximum.
+This result provides a direct way to check if a certain angle $\theta\in[0, \pi]$ is feasible or not: rotate the points by $-\theta$ and check if $D(m, 0)$ is $\ge d$ with $m$ being the angular coefficient of the line that passes through the two points, and $d$ being the distance between them.
+
+Furthermore, in \autoref{eq:dist_line_ellipse}, it can also be observed that $D(m, 0)^2$ is a parabola, which means that the set $\{m\in\R: D(m, 0)^2 \ge d^2\}$ is the union of at most two intervals.
+From there, given an instance of MCER, it is possible to arrive at the conclusion that a set of feasible angles for an ellipse and two points can be written as
+
+\begin{equation}\label{eq:phi_j}
+\Phi_j(u,v) = [\theta_1, \theta_2] \cup [\theta_3, \theta_4], 
+\end{equation}
+where $\theta_i$, $i=1\dots 4$, can be obtained from the solutions of $D(m, 0)^2=d$ and the extreme points $\{0, \pi, \pi/2\}$.
+As a final remark, the angle which makes the two points form a vertical line deserves special treatment as its line cannot be represented by the equation $y=mx$.
 
@@
 	\begin{enumerate}[label=(\alph*)]
-		\item There is $q', \theta'$, and $\{u, v, w\} \subset \Pp \cap E_j(q_j, \theta_j)$, such that $\{u, v, w\} \subset \partial E_j(q', \theta')$.
+		\item There is an equivalent solution $(Q', \Theta')$, such that $|\Pp\cap \partial E_j(q'_j, \theta'_j)| \ge 3$.\label{lema:3pnts_a}
 
-		\item Let $A=\Pp \cap E_j(q_j^*, \theta_j^*)$, and $u, v \in A$, such that there exists $\hat{q}_j$, with $\{u, v\} \subset \partial E_j(\hat{q}_j, \theta_j^*)$ and $A \subset E_j(\hat{q}_j, \theta_j^*)$.
-Then, for any $(E_j, u, v)$-feasible angle $\theta \in [0, 2\pi]$, there exists $\bar{q}_j$ such that $\{u, v\} \subset \partial E_j(\bar{q}_j, \theta)$ and $A \subset E_j(\bar{q}_j, \theta)$.
+		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
+\label{lema:3pnts_b}
 	\end{enumerate}
 \end{lema}
+
+\begin{proof}
+	We are going to prove that if \autoref{lema:3pnts}\ref{lema:3pnts_a} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_b} is true; and if \autoref{lema:3pnts}\ref{lema:3pnts_b} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_a} is true.
+
+	Before that, let us define $\Phi_j'$ as the open interval version of $\Phi_j$ as $\Phi_j'(u,v) = (\theta_1, \theta_2)\cup(\theta_3, \theta_4)$.
+
+	Suppose that \autoref{lema:3pnts}\ref{lema:3pnts_a} is false.  
+	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp$, such that an equivalent optimal solution exists with $u, v$ on the border of $E_j$.
+
+	For any $\theta\in\Phi_j'(u,v)$, we have get an 
+\end{proof}
 
@@
 	\caption{An example of \autoref{lema:3pnts}.}
-	\includegraphics{tex/figures/scripts/lema-3-points}
+	\includegraphics[scale=.8]{tex/figures/scripts/lema-3-points}
 	\fautor

### 2020-01-15 defesa/tex/chapter/mcer.tex
wip

@@
 	\begin{equation}
-	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
+	\Phi_j(u, v) := \{\theta \in [0, \pi] : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
 	\end{equation}
@@
 Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
-Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$, at least one of the two cases is true:
+Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$, the following statements are equivalent:
 
 	\begin{enumerate}[label=(\alph*)]
-		\item There is an equivalent solution $(Q', \Theta')$, such that $|\Pp\cap \partial E_j(q'_j, \theta'_j)| \ge 3$.\label{lema:3pnts_a}
+		\item $|\Pp\cap \partial E_j(q'_j, \theta'_j)| < 3$, for any equivalent solution $(Q', \Theta')$, \label{lema:3pnts_a}
 
-		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
-\label{lema:3pnts_b}
+		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta'\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.\label{lema:3pnts_b}
 	\end{enumerate}
@@
 \begin{proof}
+	To make the text more clear, let $A=\Pp\cap E_j(q^*_j, \theta^*_j)$.
+
+	$\Rightarrow$
+
+	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp$, such that an equivalent optimal solution $(Q', \Theta^*)$ exists with $u, v$ on the border of $E_j(q_j', \theta_j^*)$.
+Therefore, $\theta_j^*\in\Phi_j(u,v)$.
+
+	Suppose that $|\Phi_j(u,v)|>1$
+
 	We are going to prove that if \autoref{lema:3pnts}\ref{lema:3pnts_a} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_b} is true; and if \autoref{lema:3pnts}\ref{lema:3pnts_b} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_a} is true.
@@
 	Suppose that \autoref{lema:3pnts}\ref{lema:3pnts_a} is false.
-	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp$, such that an equivalent optimal solution exists with $u, v$ on the border of $E_j$.
 

### 2020-01-16 defesa/tex/chapter/definicoes.tex
wip

--- 2019-12-24 defesa/tex/chapter/definicoes.tex
@@
 
+Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
+Suppose that this line intersects the ellipse at a least one point.
+Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points.
+The final expression is given by
+\begin{equation}\label{eq:dist_line_ellipse}
+D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
+\end{equation}
+with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$.
+It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$.
+From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$.
+Following that, we define a function $L:m\mapsto\R_{>0}$ that describes the maximum squared distance between the points of the intersection of an ellipse with a line with a fixed angular coefficient:
+\begin{equation}\label{eq:function-l}
+L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2}.
+\end{equation}
+It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $x=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
+Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
+In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.
+
+\begin{figure}[H]
+	\centering
+
+	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
+	\includegraphics[scale=.5]{tex/figures/L-function-plot}
+	\fautor
+	\label{fig:L-function-plot}
+\end{figure}
+
 \subsection{Non-axis-parallel}

### 2020-01-16 defesa/tex/chapter/mcer.tex
wip

@@
 
-		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta'\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.\label{lema:3pnts_b}
+		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.\label{lema:3pnts_b}
 	\end{enumerate}
@@
 
-	Suppose that $|\Phi_j(u,v)|>1$
+	Now suppose that $u$ and $v$ have the $y$-coordinate, that is, the angle between them is $0$.
+If they are not, a rotation can be applied to make have the same $y$-coordinate.
+Then, we are going to prove that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that can be used in the proof.
 
-	We are going to prove that if \autoref{lema:3pnts}\ref{lema:3pnts_a} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_b} is true; and if \autoref{lema:3pnts}\ref{lema:3pnts_b} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_a} is true.
+	In \autoref{chapter:definitions}, a great deal of explanation was given on the maximum distance between the intersection points of a line with an axis-parallel ellipse.
+In particular, we are interested in the function $L$, defined in \autoref{eq:function-l}, which represents the squared distance of the intersection points of a line  $y=mx + c$, where $m$ is fixed, and an ellipse.
 
-	Before that, let us define $\Phi_j'$ as the open interval version of $\Phi_j$ as $\Phi_j'(u,v) = (\theta_1, \theta_2)\cup(\theta_3, \theta_4)$.
+	To use those results here, we need to rotate the points, instead of rotating the ellipse.
+Let $\theta \in [0, \pi]\setminus\{\pi/2\}$, then if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to fit $u$ and $v$ on the ellipse's border.
+Defining $l(\theta)=L(\tan{\theta})$, with $l:[0, \pi]\setminus\{\pi/2\}$, we can say that
 
-	Suppose that \autoref{lema:3pnts}\ref{lema:3pnts_a} is false.
+	\begin{itemize}
+		\item $l$ is decreasing in $[0, \pi/2)$ because $L$ is decreasing in $[0, \infty)$.
+Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\alpha, \pi/2)$.
+		\item $l(\theta) = l(\pi-\theta)$ because $L$ is an even function.
+Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\pi/2,\pi-\alpha)$.
+	\end{itemize}
+	Then, we can conclude that $\Phi_j(u, v) = [0, \alpha]\cup [\pi-\alpha, \pi]$. Of course, if there is no $\alpha\in[0, \pi/2)$, such that $l(\alpha)=||v-u||_2^2$, then $\Phi_j(u,v)=[0, \pi]$.
+	From that, if we rotate the points by $\pi-\alpha$, we obtain $\Phi_j(u,v)=[0, 2\alpha]$. From now on, we assume that $\alpha>0$.
 
-	For any $\theta\in\Phi_j'(u,v)$, we have get an 
+	With this result in hands, we can use a continuity argument to prove that \autoref{lema:3pnts}\ref{lema:3pnts_b} is true.
+	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$.
+In general, there are two possible centers that makes $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, choosing the right one makes $\delta$ be a continuous function having that $\delta(\theta_j^*) = q_j'$.
+
+	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^3 \mapsto \R_{\ge0}$ to be a function that takes a center point $q$ and an angle of rotation $\theta$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$.
+
+	We have that $f_w(q_j', \theta_j^*) < 1$ for any $w\in \Pp \cap E_j(q_j^*, \theta_j^*)$.
+We then, define function $g_w : \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
+As $g_w$ is a composition of continuous functions, it is also continuous.
+
+	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)$ leaves the coverage of the ellipse, it must have $g_w(\theta)>1$, which by continuity, there must be another $\hat{\theta}$, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
+
+	$\Leftarrow$
+
 \end{proof}
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 \end{figure}
-
-The idea to prove \autoref{lema:3pnts} is that after fixing $u, v$ on the border of $E_j$, which is possible by \autoref{lema:mce_2b}, the movement of rotation and translation while keeping $u, v$ on the border is continuous.
-Because of that, the negation of case two implies case one and vice versa.
-
-If we define an equivalence relation between optimal solutions as: $S_1$ is equivalent to $S_2$ if they both cover the same set of points, we can use \autoref{lema:3pnts} and \autoref{lema:mce_2b} to identify the equivalence classes.
-Let $S$ be any optimal solution, in $[S]$ (its equivalence class) there is another solution where any ellipse $E_j \in \E$ falls in at least one of the cases below:
-\begin{itemize}
-	\item $E_j$ covers only one point.
-	\item $E_j$ covers more than one point with $u$ and $v$ being on the border of $E_j$.
-Note that there could be infinitely many of solutions like that, however, \autoref{lema:3pnts} guarantees that any $(E_j, u, v)$-feasible angle yields an equivalent optimal solution.
-	\item $E_j$ covers more than two points with three of them on its border.
-\end{itemize}
-
-The following two sections will treat the second and third cases (the first case is trivial).
-Going through every possibility of an ellipse falling in any of the three cases guarantees that an optimal solution is found.
 

### 2020-01-16 defesa/tex/chapter/mcer.tex
wip

@@
 
-	Now suppose that $u$ and $v$ have the $y$-coordinate, that is, the angle between them is $0$.
-If they are not, a rotation can be applied to make have the same $y$-coordinate.
-Then, we are going to prove that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that can be used in the proof.
+	Now suppose that $u$ and $v$ have the same $y$-coordinate, that is, the angle between them is $0$.
+If they do not, a rotation can be applied to make them have the same $y$-coordinate.
+Then, the first thing we are proving is that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that can be used in the proof.
 

### 2020-01-17 defesa/tex/chapter/mcer.tex
wip

@@
 and $m$ ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
-Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2\times\R^2 \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
-Lastly, an instance of MCER is defined as the tuple $(\Pp, \Ww, \Rr)$.
+Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j\colon \R^2\times\R \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
+Lastly, an instance of MCER is defined as a tuple $(\Pp, \Ww, \Rr)$.
 
@@
 In addition to that, we define an equivalence relation between solutions of MCER.
-As likely expected, we say that two solutions are equivalent if the set of points covered by them is the same.
+We say that two solutions are equivalent if the set of points covered by them is the same.
 In other words, two solutions of MCER $(Q, \Theta)$ and $(Q', \Theta')$ are said to be equivalent if, and only if
@@
 	Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. 
-	Then, for any $E_j \in \E$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, 
+	Then, for any $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, 
 	an equivalent solution $(Q', \Theta^*)$ exists, such that $|\Pp \cap \partial E_j(q_j', \theta_j^*)|\ge 2$.
@@
 
-	Let $A=\Pp \cap E_j(q_j^*, \theta_j)$ be the set of points covered by the $j$-th ellipse and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point from $A$.
+	Let $A=\Pp \cap E_j(q_j^*, \theta_j)$ be the set of points covered by the $j$-th ellipse and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point in $A$.
 
@@
 
-What \autoref{lema:mce_2b} is saying is that any optimal solution for MCER can be transformed into another optimal solution where every ellipse covers the same set of points and those which cover more than one point has two points on their border.
-Also, this equivalent optimal solution can be always achieved by just translating the ellipses.
-An example is shown on \autoref{fig:ellipse-2-points} for one ellipse.
+What \autoref{lema:mce_2b} is saying is that any optimal solution for MCER can be transformed into an equivalent optimal solution where every ellipse that covers more than one point has two points on their border.
+Also, this equivalent optimal solution can be always achieved by just translating the ellipses, an example of that can be seen in \autoref{fig:ellipse-2-points}.
+
+\begin{definicao}
+	Let $(Q^*, \Theta^*)$ be an optimal solution for an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We define $\Omega(Q^*, \Theta^*)$ as the set of every equivalent solution of $(Q^*, \Theta^*)$, such that for any $(Q, \Theta)\in\Omega(Q^*, \Theta^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
+\end{definicao}
 
@@
 
-In \autoref{chapter:definitions}, it was stated that the line that has the most distant intersection points with an ellipse is the one that passes through the origin, given that the linear parameter is fixed.
-It also says that the function $D$ given by \autoref{eq:dist_line_ellipse}, which represents the distance between the intersection points (it is negative when there is no intersection), attains every value less than its maximum.
-This result provides a direct way to check if a certain angle $\theta\in[0, \pi]$ is feasible or not: rotate the points by $-\theta$ and check if $D(m, 0)$ is $\ge d$ with $m$ being the angular coefficient of the line that passes through the two points, and $d$ being the distance between them.
-
-Furthermore, in \autoref{eq:dist_line_ellipse}, it can also be observed that $D(m, 0)^2$ is a parabola, which means that the set $\{m\in\R: D(m, 0)^2 \ge d^2\}$ is the union of at most two intervals.
-From there, given an instance of MCER, it is possible to arrive at the conclusion that a set of feasible angles for an ellipse and two points can be written as
-
-\begin{equation}\label{eq:phi_j}
-\Phi_j(u,v) = [\theta_1, \theta_2] \cup [\theta_3, \theta_4], 
-\end{equation}
-where $\theta_i$, $i=1\dots 4$, can be obtained from the solutions of $D(m, 0)^2=d$ and the extreme points $\{0, \pi, \pi/2\}$.
-As a final remark, the angle which makes the two points form a vertical line deserves special treatment as its line cannot be represented by the equation $y=mx$.
+Following that, we present a lemma that, given an optimal solution, it says that for any ellipse that covers more than two points, an equivalent solution exists with at least one of the two properties:
+\begin{itemize}
+	\item Three points lie on the ellipse's border.
+	\item Two points lie on the ellipse's border, for any feasible angle.
+\end{itemize}
 
 \begin{lema}\label{lema:3pnts}
-Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
-Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$, the following statements are equivalent:
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$; $(Q', \Theta')\in\Omega(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.
 
-	\begin{enumerate}[label=(\alph*)]
-		\item $|\Pp\cap \partial E_j(q'_j, \theta'_j)| < 3$, for any equivalent solution $(Q', \Theta')$, \label{lema:3pnts_a}
+If, for every equivalent solution $(\hat{Q}, \hat{\theta})$, $|\Pp\cap \partial E_j(\hat{q}_j, \hat{\theta}'_j)| < 3$, then for all $\theta\in\Phi_j(u,v)$, there exists $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
 
-		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.\label{lema:3pnts_b}
-	\end{enumerate}
 \end{lema}
@@
 \begin{proof}
-	To make the text more clear, let $A=\Pp\cap E_j(q^*_j, \theta^*_j)$.
-
-	$\Rightarrow$
-
-	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp$, such that an equivalent optimal solution $(Q', \Theta^*)$ exists with $u, v$ on the border of $E_j(q_j', \theta_j^*)$.
+	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E_j(q^*_j, \theta^*_j)$, such that an equivalent optimal solution $(Q', \Theta')$ exists with $u$ and $v$ on the border of $E_j(q_j', \theta_j^*)$.
 Therefore, $\theta_j^*\in\Phi_j(u,v)$.
@@
 If they do not, a rotation can be applied to make them have the same $y$-coordinate.
-Then, the first thing we are proving is that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that can be used in the proof.
+Then, the first thing we are proving is that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that any instance can be transformed into using translation and rotation on every element of $\Pp$.
 
-	In \autoref{chapter:definitions}, a great deal of explanation was given on the maximum distance between the intersection points of a line with an axis-parallel ellipse.
-In particular, we are interested in the function $L$, defined in \autoref{eq:function-l}, which represents the squared distance of the intersection points of a line  $y=mx + c$, where $m$ is fixed, and an ellipse.
+	In \autoref{chapter:definitions}, a function $L\colon \R \to \R_{\ge0}$ was defined in \autoref{eq:function-l}.
+This function takes the angular coefficient $m\in\R$ and, considering the family of lines parallel to the one described by $y=mx$, returns the maximum squared distance between two intersection points of a line in that family and an axis-parallel ellipse centered at the origin.
 
-	To use those results here, we need to rotate the points, instead of rotating the ellipse.
-Let $\theta \in [0, \pi]\setminus\{\pi/2\}$, then if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to fit $u$ and $v$ on the ellipse's border.
+	To use those results here, we need to consider the ellipse to be fixed at the origin and axis-parallel, and instead, rotate the points in $\Pp$.
+
+	Let $\theta \in [0, \pi]\setminus\{\pi/2\}$, and $u', v'$ be the points $u, v$ after a rotation by $\theta$.
+Then, if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to apply a translation to $u',v'$, such that they end up in the border of the fixed ellipse.
+This means that, it is possible to find an angle of rotation and a center to place $E_j$, such that it has $u, v$ on its border.
+
+	Now we use some properties of function $L$ whose details are given in \autoref{chapter:definitions}.
 	Defining $l(\theta)=L(\tan{\theta})$, with $l:[0, \pi]\setminus\{\pi/2\}$, we can say that
@@
 Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\alpha, \pi/2)$.
+That implies $[0, \alpha] \subset \Phi_j(u,v)$.
 		\item $l(\theta) = l(\pi-\theta)$ because $L$ is an even function.
 Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\pi/2,\pi-\alpha)$.
+That implies $[\pi-\alpha, \pi] \subset \Phi_j(u,v)$.
 	\end{itemize}
-	Then, we can conclude that $\Phi_j(u, v) = [0, \alpha]\cup [\pi-\alpha, \pi]$. Of course, if there is no $\alpha\in[0, \pi/2)$, such that $l(\alpha)=||v-u||_2^2$, then $\Phi_j(u,v)=[0, \pi]$.
-	From that, if we rotate the points by $\pi-\alpha$, we obtain $\Phi_j(u,v)=[0, 2\alpha]$. From now on, we assume that $\alpha>0$.
+	We then conclude that $\Phi_j(u, v) = [0, \alpha]\cup [\pi-\alpha, \pi]$, and, of course, in the case that there is no $\alpha\in[0, \pi/2)$, such that $l(\alpha)=||v-u||_2^2$, we have $\Phi_j(u,v)=[0, \pi]$.
+	From that, if we rotate every point in $\Pp$ by $\pi-\alpha$, we obtain $\Phi_j(u,v)=[0, 2\alpha]$.
 
-	With this result in hands, we can use a continuity argument to prove that \autoref{lema:3pnts}\ref{lema:3pnts_b} is true.
-	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$.
-In general, there are two possible centers that makes $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, choosing the right one makes $\delta$ be a continuous function having that $\delta(\theta_j^*) = q_j'$.
+	With this result in hands, we can use a continuity argument to complete our proof as follows.
+	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
+	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:2point-ellipse} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.
 
-	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^3 \mapsto \R_{\ge0}$ to be a function that takes a center point $q$ and an angle of rotation $\theta$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$.
+	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^3 \mapsto \R_{\ge0}$ to be a function that takes a center point $q$ and an angle of rotation $\theta$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}.
 
-	We have that $f_w(q_j', \theta_j^*) < 1$ for any $w\in \Pp \cap E_j(q_j^*, \theta_j^*)$.
-We then, define function $g_w : \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
+	We have that $f_w(q_j', \theta_j^*) < 1$ for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)$.
+We then define function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
 As $g_w$ is a composition of continuous functions, it is also continuous.
@@
 	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)$ leaves the coverage of the ellipse, it must have $g_w(\theta)>1$, which by continuity, there must be another $\hat{\theta}$, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
+The same can be said about a point that enters the coverage of $E_j$.
+\end{proof}
 
-	$\Leftarrow$
-
-\end{proof}
+\begin{figure}[H]
+	\centering
+	\caption{Every ellipse that contains two points for a fixed angle of rotation.}
+	\includegraphics[scale=.36]{tex/figures/2point-ellipse}
+	\fautor
+	\label{fig:2point-ellipse}
+\end{figure}
 

### 2020-01-19 defesa/tex/chapter/mcer.tex
wip

@@
 
+Next, a notation is defined for the set of equivalent solutions of an optimal solution which has at least two points on the border of every ellipse.
+
 \begin{definicao}
@@
 	\caption{An optimal solution before and after applying \autoref{lema:mce_2b}.}
-	\includegraphics{tex/figures/scripts/ellipse-2-points}
+	\includegraphics[scale=.38]{tex/figures/ellipse-2-points}
 	\fautor
@@
 	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
-	\includegraphics[scale=.8]{tex/figures/scripts/feasible-angle}
+	\includegraphics[scale=.33]{tex/figures/feasible-angle2}
 	\fautor
@@
 	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
-	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:2point-ellipse} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.
+	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.
 
@@
 
-	We have that $f_w(q_j', \theta_j^*) < 1$ for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)$.
-We then define function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
+	For all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j^*) < 1$.
+We then define a function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
 As $g_w$ is a composition of continuous functions, it is also continuous.
 
-	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)$ leaves the coverage of the ellipse, it must have $g_w(\theta)>1$, which by continuity, there must be another $\hat{\theta}$, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
-The same can be said about a point that enters the coverage of $E_j$.
+	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>1$.
+Then, by continuity, another angle $\hat{\theta} \in(\theta_j^*, \theta)$ must exist, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
+The same can be said about a point that enters the coverage of $E_j(\delta(\theta), \theta)$.
 \end{proof}
 
-\begin{figure}[H]
-	\centering
-	\caption{Every ellipse that contains two points for a fixed angle of rotation.}
-	\includegraphics[scale=.36]{tex/figures/2point-ellipse}
-	\fautor
-	\label{fig:2point-ellipse}
-\end{figure}
+%\begin{figure}[H]%
+%	\centering%
+%	\caption{Every ellipse that contains two points for a fixed angle of %rotation.}
+%	\includegraphics[scale=.36]{tex/figures/2point-ellipse}
+%	\fautor
+%	\label{fig:2point-ellipse}
+%\end{figure}
 

### 2020-01-20 defesa/tex/chapter/mcer.tex
wip

@@
 	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.
+This is shown in \autoref{fig:lema-3-points} where $\delta$ is plotted for the whole interval $\Phi_j(u,v)$.
 
@@
 
-The first case of \autoref{lema:3pnts} is saying that there is another optimal solution which has $E_j$ covering the same set of points, but with three points on its border.
-
-The second case of \autoref{lema:3pnts} says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$, there is a center that maintains the covered set the same.
-
-On \autoref{fig:lema-3-points} both cases of \autoref{lema:3pnts} are shown.
-There, it can be seen that for the second case, it does not matter which feasible angle by which the ellipse is rotated, the third point will always be inside the coverage area.
-Also, an example of the first case is shown where there are three points lie exactly on the border of the ellipse.
+In \autoref{fig:lema-3-points} a visualization of \autoref{lema:3pnts} is presented.
+An initial optimal solution is given by the dashed-border ellipse.
+From it, the continuous function $\delta$ is defined by moving the ellipse through the rotation angles in $\Phi_j(u,v)$ while maintaining $u, v$ on its border.
+Consistently with \autoref{lema:3pnts}, the points in $\Pp \setminus \{u, v, w\}$ stay within the ellipse's cover for any angle of rotation, and, for point $w$, there exists an angle, such that it is on the ellipse's border.
 
@@
 	\centering
-	\caption{An example of \autoref{lema:3pnts}.}
-	\includegraphics[scale=.8]{tex/figures/scripts/lema-3-points}
+	\caption{A visualization of \autoref{lema:3pnts}.}
+	\includegraphics[scale=.6]{tex/figures/lema-3-points}
 	\fautor
@@
 
-\section{Ellipse by two points}
+For every ellipse in an instance, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
+That is what \autoref{lema:3pnts} is saying, that the implication of a non-existent equivalent optimal solution with three points on the ellipse's border implies that any feasible angle can be used.
+Therefore, we introduce a corollary next which describes a way of constructing a CLS that contains at least one optimal solution.
 
-Let $E$ be an ellipse with shape parameters $(a, b)\in \R^2_{>0}$ and $u, v\in \R^2$, one wants to find a $(E, u, v)$-feasible angle $\theta\in[0,\pi]$ and every center $q\in\R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.
+\begin{corolario}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. We define for all $j\in\{1, \dots, m\}$, $\Gamma_j^{(1)}, \Gamma_j^{(2)}, $and $\Gamma_j^{(3)}$ as
+	\begin{align*}
+	\Gamma_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\in \R^2\times\R\}\\
+	\Gamma_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, angle(u,v))\in \R^2\times\R: \{u, v ,w\} \subset \partial E_j(q, angle(u,v))\}\\
+	\Gamma_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v ,w\} \subset \partial E_j(q, \theta)\}.
+	\end{align*}
+	Then, there exists an optimal solution $(Q^*, \Theta^*)$, such that
+	\begin{equation*}
+	(Q^*, \Theta^*)\in \left\{(Q, \Theta) : (q_j, \theta_j)\in \{\Gamma_j^{(1)}\cup\Gamma_j^{(2)}\cup\Gamma_j^{(3)}\}\right\}.
+	\end{equation*}
 
-For a fixed angle, finding every center such that two points are on the border of the ellipse is done on \autoref{chapter:ellipses_intersection}, from there we know that there could be at most $2$ of such centers.
-The only thing left to be done is finding a feasible angle.
-It turns out that the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$ will be a feasible angle if, and only if the set of feasible angles is not empty.
-This can be seen geometrically as other angles achieve a lesser maximum distance between the two points on the border.
-
-\section{Ellipse by three points}
+\end{corolario}

### 2020-01-20 defesa/tex/chapter/mcer.tex
wip

@@
 
-For every ellipse in an instance, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
-That is what \autoref{lema:3pnts} is saying, that the implication of a non-existent equivalent optimal solution with three points on the ellipse's border implies that any feasible angle can be used.
-Therefore, we introduce a corollary next which describes a way of constructing a CLS that contains at least one optimal solution.
+For every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
+That is what \autoref{lema:3pnts} is saying, and because of that, we can construct a CLS which is finite and also contains an optimal solution.
+
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We will define a set $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$.
+This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ contains an optimal solution.
+Before that, we define 
+\begin{equation*}
+S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)},
+\end{equation*}
+for all $j \in \{1, \dots, m\}$, as the set of all possible solutions for the $j$-th ellipse.
+We break the construction of $S_j$ into three separated cases, that is, $S_j^{(1)}, S_j^{(2)}$, and $S_j^{(3)}$.
+
+Firstly, consider the case where $|E_j(q_j^*, \theta_j^*)|=1$. 
+This case is not treated by any of the previous results presented in this chapter.
+Nevertheless, taking this possibility into account can be done by including solutions in $S_j$ that are guaranteed to cover at least one point.
+This is represented by
+\begin{equation}
+	S_j^{(1)} = \bigcup_{1 \le i \le n} \{(p_i, 0)\}.
+\end{equation}
+
+Then, the case in which the $j$-th ellipse covers more than one point is treated by \autoref{lema:3pnts}.
+There are two possible categories into which an optimal solution can be put according two \autoref{lema:3pnts}.
+
+The first one is when there is no equivalent solution with three points on the $j$-th ellipse's border.
+This implies that, this solution can be represented by one that has a certain pair of points $u, v$ on the ellipse's border and is rotated by some angle in $\Phi_j(u,v)$.
+As only one angle is needed, we define $\theta_{uv}$ as the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the major-axis is the longest segment that crosses an ellipse.
+Having said that, we refer to $S_j^{(2)}$ the set of possible solutions that takes this case into account; we define it as
+\begin{equation}
+S_j^{(2)} = \bigcup_{1 \le i < j\le n} \{(q, \theta_{ij})\in \R^2\times\R: \{p_i, p_j\} \subset \partial E_j(q, \theta_{ij})\}.\\
+\end{equation}
+
+The only case left is when there is an equivalent solution with three points on the ellipse's border. We call this set of possible solutions $S_j^{(3)}$, and define it as
+\begin{equation}
+	S_j^{(3)} = \bigcup_{1 \le i < j < k \le n} \{(q, \theta)\in \R^2\times\R: \{p_i, p_j, p_k\} \subset \partial E_j(q, \theta)\},
+\end{equation}
+
+For a CLS to cover solutions in that category,
+
+that the implication of a non-existent equivalent optimal solution with three points on the ellipse's border implies that any feasible angle can be used and it is possible to maintain two points on the ellipse's border.
 
 \begin{corolario}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. We define for all $j\in\{1, \dots, m\}$, $\Gamma_j^{(1)}, \Gamma_j^{(2)}, $and $\Gamma_j^{(3)}$ as
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\theta_{ij} \in [0, 2\pi]$ be the polar angle  of vector $p_j-p_i$, for all $i, j \in \{1, \dots, n\}$. We define, for all $j\in\{1, \dots, m\}$,
 	\begin{align*}
-	\Gamma_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\in \R^2\times\R\}\\
-	\Gamma_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, angle(u,v))\in \R^2\times\R: \{u, v ,w\} \subset \partial E_j(q, angle(u,v))\}\\
-	\Gamma_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v ,w\} \subset \partial E_j(q, \theta)\}.
+	S_j^{(1)} &= \bigcup_{1 \le i \le n} \{(p_i, 0)\in \R^2\times\R\},\\
+	S_j^{(2)} &= \bigcup_{1 \le i < j\le n} \{(q, \theta_{ij})\in \R^2\times\R: \{p_i, p_j\} \subset \partial E_j(q, \theta_{ij})\},\\
+	S_j^{(3)} &= \bigcup_{1 \le i < j < k \le n} \{(q, \theta)\in \R^2\times\R: \{p_i, p_j, p_k\} \subset \partial E_j(q, \theta)\},\\
+	S_j &= S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}.
 	\end{align*}

### 2020-01-21 defesa/tex/chapter/e3p.tex
wip

@@
 
-\begin{lema}
+\begin{lema}\label{lema:e3p}
 	E3PNT has at most $6$ solutions.
@@
 
-\begin{teorema}
+\begin{teorema}\label{th:e3p}
 	The \autoref{algoritmo:e3p} computes every solution of E3PNT in $\bigO(1)$ operations.

### 2020-01-21 defesa/tex/chapter/mce.tex
wip

@@
 Additionally, in \citeonline{andreta} and \citeonline{canbolat}, two other parameters are present in the definition of the problem.
-This augmentation is caused by the introduction of a cost associated with each ellipse.
-Then, of course, having a cost for each facility only makes sense if there is a decision to be made about which ones are used.
-Therefore, another parameter $k\in\mathbb{N}$ is also given, and the problem is defined, such that exactly $k$ ellipses need to be selected to cover the demand set.
+This extension is the result of having costs associated with every facility.
+In MCE, though, the total cost, which is the sum of costs of every used facility, is constant; hence, to create a decision about which ones are utilized, a new parameter $k\in\mathbb{N}$ is given, along with a constraint on the number of used ellipses.
 
 We refer to this version of the problem as  \sigla{MCE-k}{Maximum Covering by Ellipses with a $k$-constraint}.
-An instance of it is given by the same parameters as MCE, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the cost of the $j$-th ellipse, and $k\in\mathbb{N}$.
+An instance of it is given by the same parameters as MCE, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost, and $k\in\mathbb{N}$.
 
@@
 Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
-After that, by keeping track of the costs of the utilized ellipses for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
+After that, by keeping track of the utilized ellipses' costs for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
 This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k})$.

### 2020-01-21 defesa/tex/chapter/mcer.tex
wip

--- 2020-01-20 defesa/tex/chapter/mcer.tex
@@
 
-Next, we introduce a proposition which says that given an optimal solution of MCER, it is possible to find another optimal solution with two points on the border of every ellipse that is already covering at least two points.
+In the next section we present some results which ultimately lead up to the construction of a CLS that contains an optimal solution for MCER.
+
+\section{Constructing a CLS}
+
+The goal of this section is to construct a finite set of solutions, also referred to as CLS, for MCER that contains at least one optimal solution.
+The main idea for doing that is to take advantage of \autoref{lema:e3p} and use the fact that there are at most six solutions for any instance of E3P.
+This set of solutions is then used in the next section on the development of a $\bigO(n^{3m})$ runtime algorithm for MCER.
+
+To begin with, a proposition is introduced which says that given an optimal solution of MCER, it is possible to find another optimal solution with two points on the border of every ellipse that is already covering at least two points.
 
@@
 What \autoref{lema:mce_2b} is saying is that any optimal solution for MCER can be transformed into an equivalent optimal solution where every ellipse that covers more than one point has two points on their border.
-Also, this equivalent optimal solution can be always achieved by just translating the ellipses, an example of that can be seen in \autoref{fig:ellipse-2-points}.
+Also, this equivalent optimal solution can be always achieved by just translating the ellipses.
+An example of that can be seen in \autoref{fig:ellipse-2-points}.
 
-Next, a notation is defined for the set of equivalent solutions of an optimal solution which has at least two points on the border of every ellipse.
+Next, a notation is defined for the set of equivalent solutions of an optimal solution that has at least two points on the border of every ellipse. This helps us make the text less cluttered.
 
@@
 	Let $(Q^*, \Theta^*)$ be an optimal solution for an instance $(\Pp, \Ww, \Rr)$ of MCER.
-We define $\Omega(Q^*, \Theta^*)$ as the set of every equivalent solution of $(Q^*, \Theta^*)$, such that for any $(Q, \Theta)\in\Omega(Q^*, \Theta^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
+We define $\Pi(Q^*, \Theta^*)$ as the set of every equivalent solution of $(Q^*, \Theta^*)$, such that for any $(Q, \Theta)\in\Pi(Q^*, \Theta^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
 \end{definicao}
 
-A lot of the ideas developed in this chapter are based on fixing two points on the border of an ellipse, which is why \autoref{def:feasible_angle} introduces a new notation for angles that an ellipse rotated by it can be translated into a center, such that it contains two fixed points.
+A lot of the ideas developed in this chapter are based on fixing two points on the border of an ellipse.
+Based on that, \autoref{def:feasible_angle} introduces a new notation for angles that, given two points and an ellipse, it is possible to find a center where the ellipse rotated by that angle is placed, such that the two given points lie on its border.
 
@@
 An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
-	In addition to that, given an instance of MCER, we refer to the set of $(E_j, u, v)$-feasible angles as
+	In addition to that, given an instance  $(\Pp, \Ww, \Rr)$ of MCER, the set of $(E_j, u, v)$-feasible angles is referred to as
 
@@
 In \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
-The example with a solid contour shows an ellipse rotated by $\pi/4$ with two points on its border, making $\pi/4$ a $(E, u, v)$-feasible angle.
+The example with a solid contour shows two ellipses rotated by $\pi/4$ with the two given points on its border, making $\pi/4$ a $(E, u, v)$-feasible angle.
 The other example, with a dashed contour, presents a case where an ellipse rotated by $\pi/2$ is not able to have the two points on its border, no matter where it is placed; because of that, $\pi/2$ is said to be a not $(E, u, v)$-feasible angle.
@@
 \begin{lema}\label{lema:3pnts}
-Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$; $(Q', \Theta')\in\Omega(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.
 
@@
 
+What \autoref{lema:3pnts} is saying is that, for every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
+Because of that, it will be shown that we can construct a CLS which is finite and also contains an optimal solution.
+
 In \autoref{fig:lema-3-points} a visualization of \autoref{lema:3pnts} is presented.
-An initial optimal solution is given by the dashed-border ellipse.
+An initial optimal solution is given by the dashed-border ellipse, and its center, represented by a star point.
 From it, the continuous function $\delta$ is defined by moving the ellipse through the rotation angles in $\Phi_j(u,v)$ while maintaining $u, v$ on its border.
+Ten angles were chosen from $\Phi_j(u,v)$ to be shown in \autoref{fig:lema-3-points}, among those were $0$ and $\max\{\Phi_j(u,v)\}$; their corresponding ellipses are displayed with solid-line borders.
 Consistently with \autoref{lema:3pnts}, the points in $\Pp \setminus \{u, v, w\}$ stay within the ellipse's cover for any angle of rotation, and, for point $w$, there exists an angle, such that it is on the ellipse's border.
@@
 	\label{fig:lema-3-points}
-\end{figure}
+\end{figure}.
 
-For every ellipse in an instance, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
-That is what \autoref{lema:3pnts} is saying, that the implication of a non-existent equivalent optimal solution with three points on the ellipse's border implies that any feasible angle can be used.
-Therefore, we introduce a corollary next which describes a way of constructing a CLS that contains at least one optimal solution.
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We will define a set $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$.
+This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
+The whole set $\Omega(\Pp, \Ww, \Rr)$ is constructed from a set of solutions for every ellipse.
+Let $j\in\{1, \dots, m\}$, we denote by $S_j$ the CLS for the $j$-th ellipse; its construction is broken into three separated cases denoted by $S_j^{(1)}$, $S_j^{(2)}$, and $S_j^{(3)}$.
+Next, we define them precisely.
 
-\begin{corolario}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. We define for all $j\in\{1, \dots, m\}$, $\Gamma_j^{(1)}, \Gamma_j^{(2)}, $and $\Gamma_j^{(3)}$ as
-	\begin{align*}
-	\Gamma_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\in \R^2\times\R\}\\
-	\Gamma_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, angle(u,v))\in \R^2\times\R: \{u, v ,w\} \subset \partial E_j(q, angle(u,v))\}\\
-	\Gamma_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v ,w\} \subset \partial E_j(q, \theta)\}.
-	\end{align*}
-	Then, there exists an optimal solution $(Q^*, \Theta^*)$, such that
-	\begin{equation*}
-	(Q^*, \Theta^*)\in \left\{(Q, \Theta) : (q_j, \theta_j)\in \{\Gamma_j^{(1)}\cup\Gamma_j^{(2)}\cup\Gamma_j^{(3)}\}\right\}.
-	\end{equation*}
+\subsection{First case}
 
-\end{corolario}
+This is the case where $|E_j(q_j^*, \theta_j^*)|=1$, that is, the $j$-th ellipse only covers one point. 
+This case is not treated by any of the previous results presented in this chapter.
+Nevertheless, taking this possibility into account can be done by including solutions in $S_j$ that are guaranteed to cover at least one point.
+This is represented by
+\begin{equation}
+	S_j^{(1)} = \bigcup_{u \in \Pp} \{(u, 0)\}.
+\end{equation}
+
+\subsection{Second case}
+
+The second and third cases are addressed by \autoref{lema:3pnts}. 
+Consider the second case to be the one where the $j$-ellipse covers more than one point and there is no equivalent solution with three points on the its border. 
+By \autoref{lema:3pnts}, $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v$ on the ellipse's border, and is rotated by some angle in $\Phi_j(u,v)$. 
+As only one angle is needed, we define $\theta_{uv}$ as the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
+Having said that, we refer to $S_j^{(2)}$ the set of possible solutions that takes this case into account; we define it as
+\begin{equation}
+S_j^{(2)} = \bigcup_{\{u, v\} \subset \Pp} \{(q, \theta_{uv})\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \theta_{uv})\}.\\
+\end{equation}
+For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters.
+This problem is discussed with great detail in \autoref{chapter:ellipses_intersection}.
+
+\subsection{Third case}
+
+The only case left is the one where there is an equivalent solution with three points on the $j$-th ellipse's border. We call this set of possible solutions $S_j^{(3)}$, and define it as
+\begin{equation}
+	S_j^{(3)} = \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v, w\} \subset \partial E_j(q, \theta)\}.
+\end{equation}
+Determining the set $S_j^{(3)}$ can be done using the results from \autoref{chapter:e3p} for every triplet of points.
+
+Finally, we define the CLS for the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$, and the set of possible solutions of an instance of MCER as
+\begin{equation}\label{eq:omega}
+\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
+\end{equation}
+
+\begin{teorema}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}.
+Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
+\end{teorema}
+\begin{proof}
+	For every $j \in \{1, \dots, m\}$, by \autoref{lema:3pnts}, any optimal solution that covers more than one point can be transformed into one that is in $S_j^{(2)}$ or in $S_j^{(3)}$.
+	If an optimal solution covers only one point, it can be transformed into another one that is in $S_j^{(1)}$.
+
+	From \autoref{chapter:ellipses_intersection}, we can conclude that $|S_j^{(2)}|\le 2\binom{n}{2} = \bigO(n^2)$.
+	By \autoref{lema:e3p}, we have that $|S_j^{(3)}| \le 6\binom{n}{3} = \bigO(n^3)$.
+	Therefore, $|S_j|=\bigO(n^3)$, and as $|\Omega(\Pp, \Ww, \Rr)|= |S_1|\times|S_2|\times\dots\times|S_m|$, we have $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
+\end{proof}
+
+\section{An algorithm for MCER}

### 2020-01-22 defesa/tex/chapter/mcer.tex
wip

@@
 
-\begin{teorema}
+\begin{theorem}\label{th:mcer}
 	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}.
 Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
-\end{teorema}
+\end{theorem}
+
 \begin{proof}
@@
 \section{An algorithm for MCER}
+
+In this section we describe an algorithm for MCER that simply goes through every solution in $\Omega(\Pp, \Ww, \Rr)$ and therefore finds an optimal solution.
+
+Firstly, we describe an algorithm that returns a CLS for an ellipse given a demand set. 
+We assume that in \autoref{algoritmo:mcer1} the procedure $e2p(u, v, a, b)$ returns every $(q, \theta) \in \R^2\times\R$, such that, let $E$ be the coverage region of the ellipse with shape parameters $(a, b)$, $\{u, v\}\subset \partial E(q, \theta)$, and
+$\theta$ is an rotation angle that makes $E$'s major-axis parallel to the line defined by $u$ and $v$.
+
+\begin{algoritmo}
+	\caption{Algorithm for MCER}\label{algoritmo:mcer1}
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and an ellipse's shape parameters $(a, b)$.}
+
+		\Ensure{A CLS for the ellipse with shape parameters $(a, b)$ considering the demand set $\Pp$.}
+
+		\item[]
+
+		\Procedure{$MCER_1$}{$\Pp, a, b$}
+		\State $S \gets \{\}$
+
+		\For {$u \in \Pp$}
+		\State $S \gets S \cup \{(u, 0)\}$
+		\EndFor
+
+		\For {$\{u, v\} \in \Pp$}
+		\State $S \gets S \cup e2p(u, v, a, b)$
+		\EndFor
+
+		\For{$\{u, v, w\} \in \Pp$}
+		\State $S \gets S \cup e3p(u, v, a, b)$ \Comment{Defined in \autoref{algoritmo:e3p}.}
+		\EndFor
+
+		\State \Return $S$
+		\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}
+
+After that, we define \autoref{algoritmo:mcer} which takes an instance $(\Pp, \Ww, \Rr)$ of MCER, and returns an optimal solution for it.
+
+\begin{algoritmo}
+	\caption{Algorithm for MCER}\label{algoritmo:mcer}
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}
+
+		\Ensure{An optimal solution of MCER.}
+
+		\item[]
+
+		\Procedure{$MCER$}{$\Pp, \Ww, \Rr, j=1$}
+		\If{$j = m+1$}
+		\State \Return $0$
+		\EndIf
+
+		\State $ans \gets 0$
+		\State Let $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*)$ be the optimal solution, initially set to $0$.
+
+		\State $S_j \gets MCE_1(\Pp, a_j, b_j)$
+
+		\For{$(q_j, \theta_j) \in S_j$}
+		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
+%		\State $((q_{j+1},\theta_{j+1}); \dots; (q_m, \theta_m)) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)\}$
+
+		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)$
+
+		\State $Cov \gets \bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)$
+		\If {$w(Cov) > ans$}
+			\State $ans \gets w(Cov)$
+			%\State $((q_{j}^*,\theta_{j}^*); \dots; (q_m^*, \theta_m^*)) \gets ((q_{j},\theta_{j}); \dots; (q_m, \theta_m))$
+
+			\State $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*) \gets (q_{j}, \dots, q_m); (\theta_{j}, \dots, \theta_m)$
+		\EndIf
+		\EndFor
+
+		\State \Return $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*)$
+		\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}
+
+\begin{corolario}
+	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ computations and returns an optimal solution.
+\end{corolario}
+
+\begin{proof}
+	For every $j\in\{1, \dots, m\}$, let $Z \subset \Pp$ be the set of covered points by ellipses $1, \dots, j-1$. 
+	Unless $Z=\Pp$, \autoref{algoritmo:mcer} does not go through a solution that has $(q_j, \theta_j)$, such that $\Pp \cap E_j(q_j, \theta_j) \subset Z$.
+Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
+\end{proof}
+
+\subsection{Improvements and implementation details}
+
+Some improvements can be made when implementing \autoref{algoritmo:mcer}.

### 2020-01-22 defesa/tex/chapter/mcer.tex
wip

@@
 	For every $j\in\{1, \dots, m\}$, let $Z \subset \Pp$ be the set of covered points by ellipses $1, \dots, j-1$. 
-	Unless $Z=\Pp$, \autoref{algoritmo:mcer} does not go through a solution that has $(q_j, \theta_j)$, such that $\Pp \cap E_j(q_j, \theta_j) \subset Z$.
+	Unless $Z=\Pp$, when choosing the center and angle of rotation for the $j$-th ellipse, \autoref{algoritmo:mcer} does not consider $(q_j, \theta_j) \in S_j$, such that $\Pp \cap E_j(q_j, \theta_j) \subset Z$.
 Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
@@
 
-Some improvements can be made when implementing \autoref{algoritmo:mcer}.
+Some improvements can be made in the implementation of \autoref{algoritmo:mcer}.
+Instead of calling procedure $MCE_1$ every time in the backtracking routine, it is suggested that it is done outside in a pre-processing phase.
+
+Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER.
+If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, solution $(Q', \Theta')$ can be dismissed.
+This can be done in the $MCE_1$ procedure in \autoref{algoritmo:mcer1}.
+
+In our implementation we use a tree-like data structure to verify if a  that is also used in \citeonline{andreta}.

### 2020-01-23 defesa/tex/chapter/mcer.tex
wip

@@
 
-In this section we describe an algorithm for MCER that simply goes through every solution in $\Omega(\Pp, \Ww, \Rr)$ and therefore finds an optimal solution.
+In this section we describe an algorithm for MCER that does a complete search on the CLS of each ellipse.
 
-Firstly, we describe an algorithm that returns a CLS for an ellipse given a demand set. 
-We assume that in \autoref{algoritmo:mcer1} the procedure $e2p(u, v, a, b)$ returns every $(q, \theta) \in \R^2\times\R$, such that, let $E$ be the coverage region of the ellipse with shape parameters $(a, b)$, $\{u, v\}\subset \partial E(q, \theta)$, and
-$\theta$ is an rotation angle that makes $E$'s major-axis parallel to the line defined by $u$ and $v$.
+Firstly, we describe an algorithm that constructs a CLS for a given ellipse.
+Let $E$ be the coverage region of an ellipse with shape parameters $(a, b)$.
+We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \theta) \in \R^2\times\R$, such that, $\{u, v\}\subset \partial E(q, \theta)$, and $\theta$ is an rotation angle that makes $E$'s major-axis parallel to the line defined by $u$ and $v$.
+Also, the procedure $e3p$ called in \autoref{algoritmo:mcer1} is defined in \autoref{algoritmo:e3p}.
 
 \begin{algoritmo}
-	\caption{Algorithm for MCER}\label{algoritmo:mcer1}
+	\caption{An algorithm that constructs a CLS for a given ellipse.}\label{algoritmo:mcer1}
 	\begin{algorithmic}[1]
@@
 
-In our implementation we use a tree-like data structure to verify if a  that is also used in \citeonline{andreta}.
+In our implementation we use the same approach used in \citeonline{andreta}.
+When constructing the CLS for the $j$-th ellipse, a tree-like data struct is utilized to verify if a solution $(q, \theta)$ covers a subset of another solution or not.
+
+Keeping an upper-bound for the solution during the backtracking in \autoref{algoritmo:mcer} can also provide a good improvement in practice.
+Let $z_j = \max_{(q, \theta) \in S_j} w(\Pp \cap E_j(q, \theta))$, and $OPT$ the value of an optimal solution.
+When the algorithm chooses $(q_j, \theta_j) \in S_j$ as the solution for the $j$-th ellipse, we have
+
+\begin{equation}
+OPT \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k.
+\end{equation}
+This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be pre-processed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER$ procedure.

### 2020-01-23 defesa/tex/chapter/definicoes.tex
wip

@@
 
-\begin{equation}\label{eq:norm2}
+\begin{equation*}
 ||u||_2 = \sqrt{u^{T}u}.
-\end{equation}
+\end{equation*}
 The elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter.
@@
 
-\begin{equation}
+\begin{equation*}
 ||u||_{Q} = \sqrt{u^{T}Qu},
-\end{equation}
+\end{equation*}
 where $Q$ is a $2$ by $2$ positive definite matrix. Note that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.
@@
 \end{equation}
-where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$.
-Distinguishing an ellipse from the other conic sections ca be done using the condition given by \autoref{eq:conic_ellipse}.
+where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections ca be done using the condition given by 
+\begin{equation*}
+4AC - B^2>0.
+\end{equation*}
 More details about conic sections can be found in \citeonline{ayoub}.
-\begin{equation}\label{eq:conic_ellipse}
-4AC - B^2>0.
-\end{equation}
 
 Assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
-\begin{equation}
+\begin{equation*}
 (p-c)^{T}Q(p-c) = 1,
-\end{equation}
+\end{equation*}
 with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
@@
 
-\subsection{Axis-parallel}
+\subsection{Axis-parallel ellipse}
 
@@
 \]
+then, starting from \autoref{def:ellipse}, we can obtain the following equation
 
-\noindent then, starting from \autoref{def:ellipse}, we can obtain the following equation
-
-\begin{align*}
-        (p-c)^{T}Q(p-c) = 1 & \Rightarrow \\
-    (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) = 1 & \Rightarrow
- \end{align*}
- \begin{equation}\label{equation:pellipse}
-  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} = 1,
- \end{equation}
+ \begin{align}\label{equation:pellipse}
+ \begin{aligned}
+ (p-c)^{T}Q(p-c) &= 1 & \Rightarrow \\
+ (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) &= 1 & \Rightarrow\\
+  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} &= 1,&
+   \end{aligned}
+ \end{align}
 where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.
@@
 
-Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve, function of the angle with its major-axis (see \autoref{fig:ellipse_params}).
+Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve function of the angle with its major-axis (see \autoref{fig:ellipse_params}).
 
@@
 %    \input{tex/figures/ellipse_definition.tex}
-   	\includegraphics[scale=.4]{tex/figures/ellipse_definition.pdf}
+   	\includegraphics[scale=.36]{tex/figures/ellipse_definition.pdf}
     \fautor
@@
 Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
-Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
+Then $\gamma\colon[0, 2\pi]\mapsto\R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
 \begin{equation}\label{eq:parametric_ellipse}
@@
 Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
-Suppose that this line intersects the ellipse at a least one point.
+Suppose that this line intersects the ellipse at least at one point.
 Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points.
 The final expression is given by
-\begin{equation}\label{eq:dist_line_ellipse}
+\begin{equation*}\label{eq:dist_line_ellipse}
 D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
-\end{equation}
+\end{equation*}
 with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$.
@@
 	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
-	\includegraphics[scale=.5]{tex/figures/L-function-plot}
+	\includegraphics[scale=.4]{tex/figures/L-function-plot}
 	\fautor
@@
 
-\subsection{Non-axis-parallel}
+\subsection{Non-axis-parallel ellipse}
 
@@
 Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given.
-This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse} where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.
+This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse}, where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.
 
@@
 Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}.
-The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent--they produce the same ellipse.
+The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent -- they produce the same ellipse.
 This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$.
@@
 This is also a good way to visualize Euler's Formula, as it can be also seen on \autoref{fig:complex-numbers}, which says that any complex number can be written in terms of its radius and polar angle as follows:
-\begin{equation}
+\begin{equation*}
 z = re^{i\theta}=r(\cos{\theta} + i\sin{\theta}),
-\end{equation}
+\end{equation*}
 with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle.
@@
 	\def\svgwidth{\columnwidth}
-	\includegraphics[scale=.4]{tex/figures/complex_numbers}
+	\includegraphics[scale=.37]{tex/figures/complex_numbers}
 	\caption{The representation of a complex number on two dimensions.}
@@
 The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
-\begin{equation}
+\begin{equation*}
 \bar{z} = a - bi.
-\end{equation}
-Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}.
-\begin{align}
-angle(\bar{z}) = 2\pi-angle(z)\\
-angle(-z) = \pi + angle(z),
-\end{align}
-checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.
+\end{equation*}
+Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}:
+\begin{align*}
+angle(\bar{z}) = 2\pi-angle(z),\\
+angle(-z) = \pi + angle(z).
+\end{align*}
+Checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.
 
@@
 
-The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots.
+The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A formula with a finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots.
 Fortunately, a numerical approach exists for higher-degree polynomials which works really well in practice.
@@
 For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by
- \begin{equation}
+ \begin{equation*}
  \left[\begin{array}{ccccc}
@@
  \end{array}\right].
- \end{equation}
+ \end{equation*}
 
@@
 A very complete introduction to this algorithm can be found on \citeonline{watkins:2008}.
-The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and under some assumptions, convergence to the eigenvalues is achieved.
+The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and, under some assumptions, convergence to the eigenvalues is achieved.
  Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary.
@@
 
- In practice, LAPACK's ZGEEV routine is utilized--the user guide can be found in \citeonline{lapack}--which is an implementation of the QR algorithm that returns every eigenvalue of a complex matrix.
+ In practice, LAPACK's ZGEEV routine is utilized (the user guide can be found in \citeonline{lapack}), which is an implementation of the QR algorithm that returns every eigenvalue of a complex matrix.
 
@@
 We say that $p_n: \R \mapsto \R$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial.
-An important property is stated in \citeonline[p.~150]{powell}, it says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$.
+An important property is stated in \citeonline[p.~150]{powell}, which says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$.
 It also says that a function written in the format
-$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta} & \quad j, k \in \mathbb{Z}_+ \end{array},$$
+$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta}, & \quad j, k \in \mathbb{Z}_+, \end{array}$$
 can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial

### 2020-01-23 defesa/tex/chapter/mcd.tex
wip

@@
 An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; a set of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$; and $m$ disks given by their radii $\Rr:=\{r_1, \dots, r_m\}$, with $r_j\in\R_{>0}$.
-Additionally, to make the text more clear, we define a set of $m$ disks as $\D = \{D_1, \dots, D_m\}$, with $D_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th disk is located as input, and returns its coverage region as defined by \autoref{eq:disk}.
+Additionally, to make the text more clear, we define a set of $m$ disks as $\D:=\{D_1, \dots, D_m\}$, with $D_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th disk is located as input, and returns its coverage region as defined by \autoref{eq:disk}.
 
@@
 Here, we introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.
+
+\section{Related Work}
+In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.
+Firstly, they solve a sub-problem for two disks in $\bigO(n^3\log{n})$.
+Then, for the rest of the points that are not in that solution, it uses the algorithm developed in \citeonline{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.
+
+Also, in \citeonline{zhou} an heuristic method for large-scale $MCD$ is proposed.
+It uses a probabilistic algorithm called mean-shift which is a gradient ascent method proven to converge to a local density maxima of any probability distribution.
+The mean-shift is utilized to find good candidates of centers for the unit disks, then the method backtracks to find the best assignment.
+The results showed that the greedy algorithm achieves an optimal coverage in some instances, but for some other ones it has a 15 percent worse coverage ratio.
 
@@
 
-In \citeonline{chazelle:1986}, the method for MWC consists on building a planar graph on which the vertices were the $\binom{n}{2}$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections.
+In \citeonline{chazelle:1986}, the method for MWC consists on building a planar graph on which the vertices are the $\binom{n}{2}$ pairwise intersection of the circumferences and the edges are the arcs of the circumferences connecting the intersections.
 With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.
@@
 
-\section{Multiple disks}
-
-In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.
-Firstly, they solve a sub-problem for two disks in $\bigO(n^3\log{n})$.
-Then, for the rest of the points that are not in that solution, it uses the algorithm developed in \citeonline{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.
-
-Also, in \citeonline{zhou} an heuristic method for large-scale $MCD$ is proposed.
-It uses a probabilistic algorithm called mean-shift which is a gradient ascent method proven to converge to a local density maxima of any probability distribution.
-The mean-shift is utilized to find good candidates of centers for the unit disks, then the method backtracks to find the best assignment.
-The results showed that the greedy algorithm achieves an optimal coverage in some instances, but for some other ones it has a 15 percent worse coverage ratio.
-
-\subsection{An algorithm for MCD}
+\section{An algorithm for MCD}
 
@@
 
-\begin{lema}
+\begin{lema}\label{lema:mcd}
 	Suppose that an instance of MCD and an index $j\in\{1, \dots, m\}$ are given.

### 2020-01-23 defesa/tex/chapter/mcer.tex
wip

@@
 After that, we define \autoref{algoritmo:mcer} which takes an instance $(\Pp, \Ww, \Rr)$ of MCER, and returns an optimal solution for it.
+Even though it is based on \autoref{th:mcer}, the set of solutions $\Omega(\Pp, \Ww, \Rr)$ is not explicitly built in \autoref{algoritmo:mcer}.
+Instead, a complete search is done by backtracking the CLS of every ellipse returned by procedure $MCER_1$.
+
+Two procedures are defined in \autoref{algoritmo:mcer}.
+The first one, called $MCER$, returns an optimal solution for an instance $(\Pp, \Ww, \Rr)$ using the second procedure $MCER_{bt}$.
+This second procedure is responsible for the backtracking and takes two additional parameters $j\in\{1, \dots, m\}$, which represents the index of the ellipse that $MCER_{bt}$ is currently processing, and $Z\subset \Pp$, which represents the set of points that have not been covered by the ellipses already processed by $MCER_{bt}$.
 
@@
 		\item[]
+		\Procedure{$MCER$}{$\Pp, \Ww, \Rr$}
+		\State \Return $MCER_{bt}(\Pp, \Ww, \Rr, 1)$
+		\EndProcedure
 
-		\Procedure{$MCER$}{$\Pp, \Ww, \Rr, j=1$}
+		\item[]
+
+		\Procedure{$MCER_{bt}$}{$Z, \Ww, \Rr, j$}
 		\If{$j = m+1$}
@@
 		\State $ans \gets 0$
-		\State Let $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*)$ be the optimal solution, initially set to $0$.
+		\State $(q_{j}^*\gets 0, \dots, q_m^*\gets0); (\theta_{j}^*\gets 0, \dots, \theta_m^*\gets 0)$ \Comment{Setting to $0$ as a default value.}
 
-		\State $S_j \gets MCE_1(\Pp, a_j, b_j)$
+		\State $S_j \gets MCER_1(Z, a_j, b_j)$
 
@@
 		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
-%		\State $((q_{j+1},\theta_{j+1}); \dots; (q_m, \theta_m)) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)\}$
 
-		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)$
+		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$
 
@@
 \begin{proof}
-	For every $j\in\{1, \dots, m\}$, let $Z \subset \Pp$ be the set of covered points by ellipses $1, \dots, j-1$. 
-	Unless $Z=\Pp$, when choosing the center and angle of rotation for the $j$-th ellipse, \autoref{algoritmo:mcer} does not consider $(q_j, \theta_j) \in S_j$, such that $\Pp \cap E_j(q_j, \theta_j) \subset Z$.
+	For every $j\in\{1, \dots, m\}$, unless $Z=\{\}$, when choosing the center and angle of rotation for the $j$-th ellipse, \autoref{algoritmo:mcer} does not consider any $(q_j, \theta_j) \in \R^2 \times \R$, such that $Z \cap E_j(q_j, \theta_j) = \{\}$.
 Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
 \end{proof}
+
+\subsection{Adding facility cost}
 

### 2020-01-23 defesa/tex/chapter/mcd.tex
wip

@@
 The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set}, which is a finite set of possible solutions, for each facility.
-After a CLS is constructed, a complete search can be executed to find the best solution.
+After a CLS is constructed, a complete search is executed to find the best solution.
+That is why, as an heuristic, it is a good idea to create small CLSs that somehow can still provide good solutions.
 
@@
 This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$.
-This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
+This is shown in \autoref{fig:array_disks}, where the list of intersection between $\partial D_1$ with circles $\partial D_2, \partial D_3$ and $\partial D_4$ is duplicated simulating a traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
 
@@
 	 %\input{tex/figures/array_disks.tex}
-    \includegraphics[scale=.28]{tex/figures/3_disks_intersect2.pdf}
+    \includegraphics[scale=.3]{tex/figures/3_disks_intersect2.pdf}
     \fautor
@@
 
-\begin{teorema}\label{lema:disk}
+\begin{theorem}\label{lema:disk}
 	\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
-\end{teorema}
+\end{theorem}
 
@@
 A simple adaptation can be done on \autoref{algoritmo:mcd_1} to make it return a CLS that contains an optimal solution of MCD for that disk. This is shown in \autoref{algoritmo:mcd_cls}. 
-Notice also that MCD-1 is defined only for unit disks, however, this constrained can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius.
+Notice also that MCD-1 is defined only for unit disks, however, this constraint can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius.
 A result about the runtime complexity of \autoref{algoritmo:mcd_cls} has already been given by \autoref{lema:disk}, the following result states about the adaption of it to be used in an algorithm for MCD.

### 2020-01-24 defesa/tex/chapter/mcd.tex
wip

@@
 
-\begin{equation}
+\begin{equation*}
 \max_{Q} w\left(\bigcup_{j=1}^m \Pp \cap D_j(q_j)\right).
-\end{equation}
+\end{equation*}
 
@@
 
-This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk} and it is just a specific case of MCD with only one disk with radius one ($m=1$ and $r_1=1$).
-We later use the algorithm for MCD-1 here described to construct a CLS which is guaranteed to contain an optimal solution for MCD.
+This version of the problem will be refered to as \sigla{MCD1}{Maximum Covering by One Unit Disk} and it is just a specific case of MCD with only one disk with radius one ($m=1$ and $r_1=1$).
+We refer to an instance of MCD1 as the tuple $(\Pp, \Ww)$.
+We later use the algorithm for MCD1 here described to construct a CLS which is guaranteed to contain an optimal solution for MCD.
 
-Two exact methods for MCD-1 have been found in the literature.
+Two exact methods for MCD1 have been found in the literature.
 A $\bigO(n^2)$ algorithm is proposed by \citeonline{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \citeonline{drezner}.
-As it has been mentioned, MCD-1 is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding three real numbers that sum to zero, given $n$ real numbers).
-Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for MCD-1, which meant that no better time-complexity could be achieved.
+As it has been mentioned, MCD1 is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding three real numbers that sum to zero, given $n$ real numbers).
+Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for MCD1, which meant that no better time-complexity could be achieved.
 Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.
@@
 
-In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD-1, an equivalent problem called \sigla{MWC}{Maximum Weight Clique} was introduced.
+In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD1, an equivalent problem called \sigla{MWC}{Maximum Weight Clique} was introduced.
 The algorithm for MCD that is developed in this chapter also uses that equivalence.
@@
 
-\begin{equation}
+\begin{equation*}
 S = \bigcap_{j : q \in D_j} D_j.
-\end{equation}
+\end{equation*}
 With a geometric observation, though, the number of possible values for the solution can be reduced.
@@
 
-\begin{equation}
+\begin{equation*}
 \max_{q} \sum_{D_k \cap q \neq \emptyset} w_k,
-\end{equation}
+\end{equation*}
 with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$.
@@
 
-As it has been mentioned, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of MCD-1, which means that a disk centered at $q^*$ which is an optimal solution of MWC, will have a maximal weight covering of the demand set $\Pp$.
+As it has been mentioned, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of MCD1, which means that a disk centered at $q^*$ which is an optimal solution of MWC, will have a maximal weight covering of the demand set $\Pp$.
 
-Given an instance of MCD-1, the equivalent MWC intance is obtained by defining the set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
+Given an instance of MCD1, the equivalent MWC intance is obtained by defining the set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$.
 A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$.
@@
 
-Formally, in MWC, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the equivalent MCD-1 instance.
-Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the MCD-1 instance.
+Formally, in MWC, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the equivalent MCD1 instance.
+Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the MCD1 instance.
 It means that $q$ will lie inside region $\bigcap_{k \in I} D_k$ in MWC.
@@
 Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$.
-For convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and if $i=j$, then $\Gamma_-(i, j)=0$ and $\Gamma_+(i,j)=2\pi$.
+For convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and if $i=j$, then $\Gamma_+(i, j)=0$ and $\Gamma_-(i,j)=2\pi$.
 \end{definicao}
@@
 This way, an algorithm for MWC just uses that method for every disk and returns the best solution found.
-Firstly, let $A_i$ be a list that contains the intersection angles of $\partial D_i$ with every circle in $\partial \D$.
-Assume also that $A_i$ is actually a circular list sorted in ascending order and it is defined as
+Firstly, let $A_i$ be a circular list that contains the intersection angles of $\partial D_i$ with every circle in $\partial \D$ defined as
 
-\begin{equation}
+\begin{equation*}
 A_i = \bigcup_{j=1}^n \{ \Gamma_-(i,j), \Gamma_+(i,j) \}.
-\end{equation}
+\end{equation*}
+Assume also that $A_i$ is sorted in ascending order by the angle values with ties being broken by prioritizing opening angles.
+
 Finding the best solution which $D_i$ is part of can be done by traversing $A_i$ while keeping a set of active disks.
@@
 In practice, traversing a circular list can be emulated by traversing a regular list that has a copy of the original circular list added to its end. 
-This is done here by traversing the regular list $B_i$ defined as
+Therefore, the list $B_i$ is defined here as a list that contains the elements of $A_i$ and a copy of it shifted to the interval $[2\pi, 4\pi]$. It is defined as
 
@@
 \end{equation}
-Assuming $B_i$ is sorted in ascending order, a copy of the elements of $A_i$ shifted to the interval $[2\pi, 4\pi]$ is added to its end and a simple traversal, going through the first element until the last one, simulates a traversal on the circular list $A_i$.
-This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$.
-This is shown in \autoref{fig:array_disks}, where the list of intersection between $\partial D_1$ with circles $\partial D_2, \partial D_3$ and $\partial D_4$ is duplicated simulating a traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).
+Assuming $B_i$ is sorted with the same criteria as $A_i$. A simple traversal, starting at the first element and going until the last one, simulates a traversal on the circular list $A_i$.
+This works because for any pair of disks $D_i$, $D_j$; $B_i$ contains $\Gamma_+(i,j) < \Gamma_-(i,j) + 2\pi$.
+That is, the algorithm encounters an opening angle before reaching a closing one for any circle.
+
+In \autoref{fig:array_disks}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection angles.
+The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing every point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk.
+The region of optimal solutions is highlighted and can also be obtained by following $B_1$ while keeping track of $Q$.
+The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks}.
+Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point and removes $D_1$ only after every point has been processed.
+
+Finally, we define \autoref{algoritmo:mcd_1} for MWC.
+Given an instance $(\Pp, \Ww)$ of MWC, the algorithm uses the approach described here of keeping a set of active disks while traversing the list $B_i$.
+It returns a point that is inside an optimal clique, this way \autoref{algoritmo:mcd_1} can also be used to get an optimal solution for an instance $(\Pp, \Ww)$ of MCD1.
 
@@
 
-    \caption{The intersections list of a disk with three other disks.}
+    \caption{The intersection list of a disk with three other disks.}
 	 %\input{tex/figures/array_disks.tex}
@@
 \begin{algoritmo}[b]
-\caption{Algorithm for MCD-1.}\label{algoritmo:mcd_1}
+\caption{Algorithm for MWC.}\label{algoritmo:mcd_1}
 \begin{algorithmic}[1]
-\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$.}
-\Ensure{The maximum cover by a unit disk.}
+\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and a set of weights $\Ww=\{w_1, \dots, w_n\}$.}
+\Ensure{A point that is inside the maximum weight clique of unit disks.}
 
@@
 
-\Procedure{$MCD_1$}{$\Pp$}
+\Procedure{$MWC$}{$\Pp, \D, \Ww$}
+\State Let $\D=\{D_1(p_1), \dots, D_n(p_n)\}$ be a set of unit disks
 \State $Q_{best} \gets \{\}$
-\State $ans \gets$ center of $D_1$
-\ForAll{$p_i \in \Pp$}
-\State Let $D_i$ be the disk with center at $p_i$
-\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}.
+\State $q^* \gets$ $p_1$
+\ForAll{$D_i \in \Pp$}
+\State Let $B_i$ be the list of intersection angles of $D_i(p_i)$ as defined by \autoref{eq:b_i}
 
 \State $Q \gets \{\}$ \Comment{The set of active disks.}
-\For{$a \in B_i$}\Comment{Assuming $B_i$ is sorted.}
-\State Let $D_a$ be the disk that intersects $D_i$ at angle $a$. 
-\If{$a$ is a starting angle}
-\State $Q \gets Q \cup \{D_a\}$
+\For{$\theta \in B_i$}\Comment{Assuming $B_i$ is sorted.}
+\State Let $D_j$ be the disk, such that $\theta \in D_j(p_j)\cap D_i(p_i)$
+\If{$\theta$ is a opening angle}
+\State $Q \gets Q \cup \{D_j\}$
 \Else
-\State $Q \gets Q \setminus \{D_a\}$
+\State $Q \gets Q \setminus \{D_j\}$
 \EndIf
-\If{$w(Q_{best}) < w(Q)$} \Comment{$w(Q)$ returns the weights of the disks in $Q$.}
+\If{$w(Q_{best}) < w(Q)$} 
 \State $Q_{best} \gets Q$
-\State $ans \gets $ point corresponding to the intersection angle $a$
+\State $q^* \gets$ point corresponding to the intersection angle $\theta$
 \EndIf
@@
 
-\State \Return $ans$
+\State \Return $q^*$
 \EndProcedure
@@
 A simple adaptation can be done on \autoref{algoritmo:mcd_1} to make it return a CLS that contains an optimal solution of MCD for that disk. This is shown in \autoref{algoritmo:mcd_cls}. 
-Notice also that MCD-1 is defined only for unit disks, however, this constraint can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius.
+Notice also that MCD1 is defined only for unit disks, however, this constraint can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius.
 A result about the runtime complexity of \autoref{algoritmo:mcd_cls} has already been given by \autoref{lema:disk}, the following result states about the adaption of it to be used in an algorithm for MCD.
@@
 \begin{algoritmo}
-	\caption{Algorithm for MCD-1 that returns a CLS.}\label{algoritmo:mcd_cls}
+	\caption{Algorithm for MCD1 that returns a CLS.}\label{algoritmo:mcd_cls}
 	\begin{algorithmic}[1]
@@
 
-		\Procedure{$MCD_1$}{$\Pp, \Ww, r$}
+		\Procedure{CLS-MCD}{$\Pp, \Ww, r$}
 		\State $S \gets \{\}$
 		\ForAll{$p_i \in \Pp$}
-		\State Let $D_i$ be the disk with center at $p_i$
-		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}.
+		\State Let $D_i(p_i)$ be the disk with center at $p_i$
+		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}
 
-		\State $Cov \gets \{\}$
-		\For{$a \in B_i$}\Comment{Assuming $B_i$ is sorted.}
-		\State Let $q_a$ be the intersection point correspondent to angle $a$. 
-		\State $S \gets S \cup \{q_a\}$	
+		\For{$\theta \in B_i$}\Comment{Assuming $B_i$ is sorted.}
+		\If{$\theta$ is a opening angle}
+		\State Let $q_\theta$ be the intersection point correspondent to angle $\theta$
+		\State $S \gets S \cup \{q_\theta\}$	
+		\EndIf
 		\EndFor

### 2020-01-24 defesa/tex/chapter/mce.tex
wip

@@
 
-\begin{equation}
+\begin{equation*}
 \max_q w\left(\bigcup_{j=1}^m \Pp \cap E_j(q_j)\right).
-\end{equation}
+\end{equation*}
 
@@
 
-\begin{equation}
+\begin{equation*}
 \max_q w(\Pp \cap E(q)).
-\end{equation}
+\end{equation*}
 An adaptation of \autoref{algoritmo:mcd_1} is obtained by just replacing the function that finds the intersection points between two disks by a function that finds the intersection points between two ellipses $\partial E_i$ and $\partial E_j$.
 It can be seen in \autoref{fig:3ellipses_intersect} that the intersection points and their correspondents $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ functions behave the same way as in the disks case.
-The intersection of two ellipses as well as determining $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ are described thoroughly in \autoref{chapter:ellipses_intersection}.
+The intersection of two ellipses as well as determining $\Gamma_-(i,j)$ and $\Gamma_+(i,j)$ are described in the next section.
 
@@
 	\caption{Three ellipses and their intersection points}
-    \includegraphics[scale=.32]{tex/figures/3ellipses_intersect.pdf}
+	\includegraphics[scale=.34]{tex/figures/3ellipses_intersect.pdf}
 	\fautor
@@
 \end{figure}
+
+\section{Determining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$}\label{section:ellipses_intersection}
+
+Let $E_1(q_1)$, and $E_2(q_2)$ be two coverage region of ellipses centered at $q_1, q_2\in\R^2$ respectively, with shape parameters $(a, b)\in\R^2_{>0}$.
+After changing the coordinates to make the center of the first ellipse be at the origin, the intersection points between the two ellipses are defined by
+
+\begin{align}
+\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1 && (E_1) \label{eq:ell_inter_1}\\
+\frac{(x-h)^2}{a^2} + \frac{(y-k)^2}{b^2} = 1 && (E_2), \nonumber
+\end{align}
+where $(h,k)\in\R^2$ is the center of the second ellipse after the coordinates were translated by $-q_1$. As both equations are equal to $1$, we have
+\begin{align}
+    b^2x^2 + a^2y^2 &= b^2(x-h)^2 + a^2(y-k)^2 \nonumber\\
+    x &= y\frac{-2ka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2} \nonumber\\
+    x &= y\alpha + \beta.\label{eq:ell_inter_2}
+\end{align}
+Replacing \autoref{eq:ell_inter_2} into \autoref{eq:ell_inter_1}, we get
+\begin{align}\label{eq:ell_inter_3}
+y^2(b^2\alpha^2 + a^2) + y(2\beta\alpha b^2) + b^2\beta^2 -a^2b^2 = 0,
+\end{align}
+Which is a second degree polynomial.
+Then, $\partial E_1(q_1) \cap \partial E_2(q_2) \neq \{\}$ if, and only if the roots of \autoref{eq:ell_inter_3} are real.
+The intersection points itself can be obtained by solving the polynomial for $y$ and applying its value onto the $x=y\alpha + \beta$ equation.
+
+Suppose that $\partial E_1(q_1) \cap \partial E_2(q_2) = \{p_1, p_2\}$, with $p_1 \neq p_2$.
+To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the angles of intersection of $p_1$ and $p_2$ on $E_1(q_1)$ using the parametric equation for an ellipse defined in \autoref{eq:parametric_ellipse}.
+Given a point $(x, y)\in \partial E_1(q_1)$, using \autoref{eq:parametric_ellipse} we have
+
+\begin{equation*}
+\dfrac{a}{b}\dfrac{y-q_{1y}}{x-q_{1x}} = \tan{t}.
+\end{equation*}
+Solving for $t$ gives the angle of point $(x,y)$ on $E_1(q_1)$.
+Using that process we obtain $t^{(1)}_1, t^{(1)}_2$ as the angles of the points $\{p_1, p_2\}$ on $E_1(q_1)$; and $t^{(2)}_1, t^{(2)}_2$ as the angles of points $\{p_1, p_2\}$ on $E_2(q_2)$.
+Let $\gamma_1$ be the curve defined by $E_1(q_1)$ and $\gamma_2$ the curve defined by $E_2(q_2)$.
+Considering its derivatives \autoref{eq:der_parametric_ellipse} at the intersection points, as it can be seen in \autoref{fig:ellipse_gamma}, we have that $p_1$ is $\Gamma_+(1,2)$ if, and only if
+\begin{equation*}
+angle(\gamma_1'(t_1^{(1)}), -\gamma_2'(t_1^{(2)}) < \pi.
+\end{equation*}
+The case where that angle is equal to $\pi$ happens when both ellipses intersect at only one point.
+This case has to be treated separately as we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.
+
+\begin{figure}
+	\centering
+
+	\caption{The intersection list of a disk with three other disks.}
+	%\input{tex/figures/array_disks.tex}
+	\includegraphics[scale=.38]{tex/figures/ellipse_gamma.pdf}
+	\fautor
+	\label{fig:ellipse_gamma}
+\end{figure}
+
 \section{An algorithm for MCE}
@@
 The same procedure defined in \autoref{algoritmo:mcd_cls} can be used to get a CLS for every ellipse in MCE.
-We refer to the elliptical version of that procedure as $MCE_1$ (we do not define it in this chapter because it would look the same as $MCD_1$, apart from the name, of course).
+We refer to the elliptical version of that procedure as CLS-MCE (we do not define it in this chapter because it would look the same as CLS-MCD defined in \autoref{algoritmo:mcd_cls}, apart from the name, of course).
 
@@
 
-It is worth mentioning that, even though we call $MCE_1$ every time in the recursion, in practice, it is probably best to pre-process this step, and only call it $m$ times for the whole set of points.
+It is worth mentioning that, even though we call CLS-MCE every time in the recursion, in practice, it is probably best to pre-process this step, and only call it $m$ times for the whole set of points.
 Some other easy improvements can also be made in the implementation.
@@
 
-We refer to this version of the problem as  \sigla{MCE-k}{Maximum Covering by Ellipses with a $k$-constraint}.
-An instance of it is given by the same parameters as MCE, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost, and $k\in\mathbb{N}$.
+We refer to this version of the problem as  \sigla{MCE-$k$}{Maximum Covering by Ellipses with a $k$-constraint}.
+An instance of it is given by the same parameters as MCE, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost, and $k\in\mathbb{N}$, $k\le m$.
 
- A solution for MCE-k, however,  when compared to MCE's, has a bit more cluttered description.
+ A solution for MCE-$k$, however,  when compared to MCE's, has a bit more cluttered description.
 We define it as a set $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$, such that $|I|=k$; and a tuple $Q:=(q_1, \dots, q_k)$, with $q_j\in\R^2$ being the center of the $j$-th ellipse in $I$.
-An optimal solution of MCE-k is given by the optimization problem
+An optimal solution of MCE-$k$ is given by the optimization problem
 
-\begin{equation}
+\begin{equation*}
 \max_{I, Q} w\left(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j)\right).
-\end{equation}
+\end{equation*}
 
-Finally, \autoref{algoritmo:mce} can serve as basis for an algorithm for MCE-k. 
+Finally, \autoref{algoritmo:mce} can serve as basis for the \autoref{algoritmo:mce-k} for MCE-$k$. 
 Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
 After that, by keeping track of the utilized ellipses' costs for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
-This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k})$.
+This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k}) = \bigO(n^{3m})$.
 
@@
     \caption{Algorithm for MCE}\label{algoritmo:mce}
+
     \begin{algorithmic}[1]
@@
 
-        \Ensure{The value of an optimal solution of MCE.}
+        \Ensure{An optimal solution for MCE.}
 
         \item[]
+        \Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
+	    \State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
+        \EndProcedure
 
-        \Procedure{$MCE$}{$\Pp, \Ww, \Rr, j=1$}
+        \Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j=1$}
         \If{$j = m+1$}
@@
 
-        \State $ans \gets 0$
+        \State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$
 
-        \State $S_j \gets MCE_1(\Pp, a_j, b_j)$
-        \For{$q \in S_j$}
-        \State $Cov \gets \Pp \cap q$
-        \State $ans \gets \max\{ans, w(Cov) + MCE(\Pp \setminus Cov, \Ww, \Rr, j+1)\}$ \Comment{Calls the procedure for the next ellipse.}
+        \State $S_j \gets \textnormal{CLS-MCE}(Z, a_j, b_j)$
+        \For{$q_j \in S_j$}
+        \State $Cov \gets \Pp \cap E_j(q_j)$
+        \State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$
+
+        \If{$w(Cov) + w(\cup_{k=j+1}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
+        \State $(q_j^*, \dots, q_j^*) \gets(q_j, \dots, q_m)$
+        \EndIf
         \EndFor
 
-        \State \Return $ans$
+        \State \Return $(q_j^*, \dots, q_m^*)$
         \EndProcedure
@@
 \end{algoritmo}
+
+\begin{algoritmo}
+	\caption{Algorithm for MCE-$k$}\label{algoritmo:mce-k}
+
+	\begin{algorithmic}[1]
+   \Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, a list of costs $\Cc=\{c_1, \dots, c_m\}$, and $k\in \mathbb{N}$.}
+	\Ensure{An optimal solution for MCE-$k$.}
+
+	\item[]
+
+\Procedure{MCE-$k$}{$\Pp, \Ww, \Rr, \Cc, k$}
+	\State $I^* = \{i_1^*, \dots, i_k^*\}\gets \{1, \dots, k\}$
+	\State $Q^* = (q_1^*, \dots, q_k^*) \gets (0, \dots, 0)$
+
+	\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$, such that $|I|=k$}
+
+		\State $(q_1, \dots, q_k) \gets MCE(\Pp, \Ww, \{(a_j, b_j) \in \Rr: j \in I\})$
+
+		\If{$w(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j)) - \sum_{j\in I} c_j > w(\bigcup_{j=1}^k \Pp \cap E_{i_j^*}(q_j^*)) - \sum_{j\in I^*}c_{j}$}
+			\State $Q^* \gets (q_1, \dots, q_k)$
+			\State $I^* \gets I$
+		\EndIf
+	\EndFor
+
+	\State \Return $I^*, Q^*$
+\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}

### 2020-01-26 defesa/tex/chapter/definicoes.tex
wip

@@
 \end{equation}
-where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections ca be done using the condition given by 
+where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections can be done using the condition
 \begin{equation*}
@@
 These two values are also referred to as the shape parameters of an ellipse.
-Let $d = ||c-f_1||_2$, then it is easy to see that $a = R - d$ and $b = \sqrt{\frac{R^2}{4} - d^2}$.
-
-Finally, an ellipse is said to be axis-parallel if its major-axis (see \autoref{fig:ellipse_with_foci}), which is the line that passes through its two foci points, is parallel to the $x$-axis.
+Finally, an ellipse is said to be axis-parallel if its major axis (see \autoref{fig:ellipse_with_foci}), which is the line that passes through its two foci points, is parallel to the $x$-axis.
 
@@
  \begin{align}\label{equation:pellipse}
- \begin{aligned}
- (p-c)^{T}Q(p-c) &= 1 & \Rightarrow \\
- (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) &= 1 & \Rightarrow\\
+ (p-c)^{T}Q(p-c) &= 1 & \Rightarrow \nonumber \\
+ (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) &= 1 & \Rightarrow \nonumber\\
   \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} &= 1,&
-   \end{aligned}
  \end{align}
-where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.
-
+where $(a, b) \in \R^2_{>0}$, with $a>b$, are ellipse's shape parameters.
 Also, the coverage region is determined by just changing the equality to an inequality as follows
@@
 
-Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve function of the angle with its major-axis (see \autoref{fig:ellipse_params}).
+Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve function of the angle with its major axis (see \autoref{fig:ellipse_params}).
 
@@
 
-Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
-Then $\gamma\colon[0, 2\pi]\mapsto\R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
+Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$, with $a>b$.
+Then $\gamma\colon[0, 2\pi)\mapsto\R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
 \begin{equation}\label{eq:parametric_ellipse}
@@
 \end{equation}
+Also, its derivative with respect to $t$ is given as follows
+\begin{equation}\label{eq:der_parametric_ellipse}
+\gamma'(t) = \left\{
+\begin{array}{l}
+x'(t)= -a\sin{t},\\
+y'(t)=b\cos{t}.
+\end{array}
+\right.
+\end{equation}
 
-Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
+\subsection{The distance between points of an ellipse-line intersection}
+
+Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$, centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
 Suppose that this line intersects the ellipse at least at one point.
@@
 From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$.
-Following that, we define a function $L:m\mapsto\R_{>0}$ that describes the maximum squared distance between the points of the intersection of an ellipse with a line with a fixed angular coefficient:
+Following that, we define a function $L:\R\mapsto\R_{>0}$ as
+
 \begin{equation}\label{eq:function-l}
-L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2}.
+L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
 \end{equation}
-It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $x=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
+which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.
+
+It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
 Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
@@
 
-A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}.
-Nonetheless, a simpler equation is going to be used here.
-Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given.
-This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse}, where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.
+A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}, nonetheless, in this work,  a simpler equation is used instead. 
+Besides the center and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$; an angle of rotation $\theta \in \R$ is given representing the angle between the $x$-axis and the major axis of the ellipse.
+This can be seen on \autoref{fig:rotated_ellipse}, where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.
 
-A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations: translation, so its center is at $(0, 0)$, then rotation so its major-axis is parallel to the $x$-axis.
+An ellipse rotated by $\theta$ can be transformed into an axis-parallel, and origin-centered ellipse by applying two linear transformations: translation to make its center be at $(0, 0)$, and rotation to make its major axis parallel to the $x$-axis.
 Reversing these transformations produces the following equation for a non-axis-parallel ellipse
@@
 \end{equation}
-The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation, which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$
+The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation
 \begin{equation}\label{eq:rotated_ellipse_co}
-\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1.
+\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1,
 \end{equation}
+which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$.
 
 Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}.
-The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent -- they produce the same ellipse.
+The two angles of rotation between the major axis and the $x$-axis ($\theta$ and $\theta+\pi$) are equivalent -- they produce the same ellipse.
 This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$.
-Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.
+Therefore, to represent any ellipse, it is enough to specify the domain of $\theta$ as $[0, \pi)$.
 
@@
 
-The set of complex numbers $\mathbb{C}$ is an extension of the set of real numbers $\R$ and can be very useful depending on the problem at hand.
-A thorough introduction on this topic is out of the scope and we just go through some basic properties that are going to be used later on \autoref{chapter:e3p}.
+The set of complex numbers $\mathbb{C}$ can be seen as just an extension of the set of real numbers $\R$.
+A thorough introduction on this topic is out of the scope and we just go through some basic properties that are going to be used later in \autoref{chapter:e3p}.
 
-A complex number is composed of a real part added to an imaginary part which is a multiple of the imaginary unit $i = \sqrt{-1}$.
-This is expressed as $a + bi$, with $a, b \in \R$.
-Because $z$ is composed of two real numbers, the complex number system can be visualized on $\R^2$ as shown on \autoref{fig:complex-numbers}.
-This is also a good way to visualize Euler's Formula, as it can be also seen on \autoref{fig:complex-numbers}, which says that any complex number can be written in terms of its radius and polar angle as follows:
+Any complex number $z\in\mathbb{C}$ is composed of a real part $a\in\R$, and an imaginary part $b\in\R$, multiple of the imaginary unit $i = \sqrt{-1}$. This is expressed as $z=a+ib$. 
+Because complex numbers are composed of two real numbers, mapping $\mathbb{C}$ to $\R^2$, as shown in  \autoref{fig:complex-numbers}, provides a good way to visualize the set of complex numbers. 
+This is also a good way to visualize Euler's Formula. As it can be seen on \autoref{fig:complex-numbers}, any complex number can be written in terms of its radius and polar angle as
+
 \begin{equation*}
@@
 
-The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
+The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as
 \begin{equation*}
@@
 \end{equation*}
-Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}:
+Lastly, two observations that are very important for the developments of \autoref{chapter:e3p} need to be stated. Let $z\in \mathbb{C}$, then we have 
 \begin{align*}
@@
 
- Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory.
-A very complete introduction to this algorithm can be found on \citeonline{watkins:2008}.
-The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and, under some assumptions, convergence to the eigenvalues is achieved.
- Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary.
-This and other properties are used in \citeonline{barel} on the development of a $\bigO(n^2)$ algorithm for the specific case of companion matrices.
+Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \citeonline{watkins:2008}).
+The first step of the QR algorithm is to convert the input matrix into the Hessenberg form.
+This is done because matrices in the Hessenberg form maintain its form under the iterations of the algorithm.
+After that, the algorithm, under some assumptions, converges to the matrix's eigenvalues after $\bigO(n)$ iterations, each one taking $\bigO(n^2)$ computations.
+Another method specific to companion matrices can be found in \citeonline{barel}.
+It uses the fact that companion matrices are already in the Hessenberg form to proposes a $\bigO(n^2)$ algorithm to find the roots of a $n$-degree polynomial.
 
@@
 $$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta}, & \quad j, k \in \mathbb{Z}_+, \end{array}$$
-can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial
+can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$, the expression
 \begin{equation}\label{eq:trig_poly_2}
@@
 \end{equation}
-for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$.
+also represents a $n$-degree real trigonometric polynomial.

### 2020-01-26 defesa/tex/chapter/mcd.tex
wip

@@
 
-In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD1, an equivalent problem called \sigla{MWC}{Maximum Weight Clique} was introduced.
-The algorithm for MCD that is developed in this chapter also uses that equivalence.
-Because of that, MWC is introduced in the next section.
+The algorithm for MCD1, developed in this chapter, can be seen as a parallel version of the algorithm developed by \citeonline{drezner}.
+We, however, based on \citeonline{chazelle:1986} and \citeonline{cabello:2006}, decided to work with an equivalent problem called \sigla{MWC}{Maximum Weight Clique} which is introduced in the next section.
 
@@
 In \autoref{fig:array_disks}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection angles.
-The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing every point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk.
-The region of optimal solutions is highlighted and can also be obtained by following $B_1$ while keeping track of $Q$.
+The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing a point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk.
+It is possible to see that the optimal clique highlighted in \autoref{fig:array_disks} is enclosed by the arcs defined by $\Gamma_+(1,4)$ and $\Gamma_-(1,4)$, and can also be identified by following $B_1$ while keeping track of $Q$.
 The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks}.
-Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point and removes $D_1$ only after every point has been processed.
+Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point, and removes $D_1$ only after every point has been processed.
 
@@
 		\ForAll{$p_i \in \Pp$}
-		\State Let $D_i(p_i)$ be the disk with center at $p_i$
-		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}
+		%\State Let $D_i(p_i)$ be the disk with center at $p_i$
+		\State Let $B_i$ be the list of intersection angles of $\partial D_i(p_i)$ as defined by \autoref{eq:b_i}
 

### 2020-01-26 defesa/tex/chapter/mce.tex
wip

@@
 We refer to this problem as \sigla{MCE}{Maximum Covering by Ellipses}.
-We also present an algorithm for it which is an adaptation of the algorithm developed for MCD in \autoref{chapter:pmclp}.
+We also present an algorithm for it which is an adaptation of the one developed for MCD in \autoref{chapter:pmclp}.
 
@@
 \end{align}
-Which is a second degree polynomial.
+which is a second degree polynomial.
 Then, $\partial E_1(q_1) \cap \partial E_2(q_2) \neq \{\}$ if, and only if the roots of \autoref{eq:ell_inter_3} are real.
-The intersection points itself can be obtained by solving the polynomial for $y$ and applying its value onto the $x=y\alpha + \beta$ equation.
+The intersection points itself can be obtained by solving the polynomial for $y$ and plugging its value back into the $x=y\alpha + \beta$ equation.
 
 Suppose that $\partial E_1(q_1) \cap \partial E_2(q_2) = \{p_1, p_2\}$, with $p_1 \neq p_2$.
-To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the angles of intersection of $p_1$ and $p_2$ on $E_1(q_1)$ using the parametric equation for an ellipse defined in \autoref{eq:parametric_ellipse}.
-Given a point $(x, y)\in \partial E_1(q_1)$, using \autoref{eq:parametric_ellipse} we have
+To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the intersection angles corresponding to $p_1$ and $p_2$ on $E_1(q_1)$.
+
+Let $\gamma_1$ and $\gamma_2$ be two curves defined as \autoref{eq:parametric_ellipse} for $E_1(q_1)$ and $E_2(q_2)$ respectively. 
+The intersection angle of $p_i$ in $E_j(q_j)$ is defined as $t_i^{(j)} \in [0, 2\pi)$, such that $\gamma_j(t_i^{(j)}) = p_i$, for $i, j \in \{1, 2\}$.
+Obtaining $t_i^{(j)}$ can be done analytically solving the equation
 
 \begin{equation*}
-\dfrac{a}{b}\dfrac{y-q_{1y}}{x-q_{1x}} = \tan{t}.
+	\dfrac{a}{b}\dfrac{p_{iy}-q_{jy}}{p_{ix}-q_{jx}} = \tan{(t_i^{(j)})}.
 \end{equation*}
-Solving for $t$ gives the angle of point $(x,y)$ on $E_1(q_1)$.
-Using that process we obtain $t^{(1)}_1, t^{(1)}_2$ as the angles of the points $\{p_1, p_2\}$ on $E_1(q_1)$; and $t^{(2)}_1, t^{(2)}_2$ as the angles of points $\{p_1, p_2\}$ on $E_2(q_2)$.
-Let $\gamma_1$ be the curve defined by $E_1(q_1)$ and $\gamma_2$ the curve defined by $E_2(q_2)$.
-Considering its derivatives \autoref{eq:der_parametric_ellipse} at the intersection points, as it can be seen in \autoref{fig:ellipse_gamma}, we have that $p_1$ is $\Gamma_+(1,2)$ if, and only if
+
+Let $\gamma_1'$ and $\gamma_2'$ be the derivatives of $\gamma_1$ and $\gamma_2$ respectively as defined by \autoref{eq:der_parametric_ellipse}.
+Then, considering the tangent vectors $\gamma_1'(t_i^{(1)})$ and $-\gamma_2'(t_i^{(2)})$, $i\in \{1, 2\}$, as shown in \autoref{fig:ellipse_gamma}, we can define a function $\phi_{1,2}\colon \{p_1, p_2\} \to \{\Gamma_+(1,2), \Gamma_-(1,2)\}$ that takes an intersection point and returns its corresponding closing/opening intersection angle as
+
 \begin{equation*}
-angle(\gamma_1'(t_1^{(1)}), -\gamma_2'(t_1^{(2)}) < \pi.
+\phi_{1,2}(p_i) = \begin{cases}
+\Gamma_+(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) > \pi\\
+\Gamma_-(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) < \pi.
+\end{cases}
 \end{equation*}
-The case where that angle is equal to $\pi$ happens when both ellipses intersect at only one point.
-This case has to be treated separately as we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.
+At last, the case where that angle is equal to $\pi$ happens only when both ellipses intersect at only one point.
+This case has to be treated separately as, by \autoref{def:inter_arc}, we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.
 
@@
 
-	\caption{The intersection list of a disk with three other disks.}
+	\caption{Determining $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$.}
 	%\input{tex/figures/array_disks.tex}
@@
 
-Finally, \autoref{algoritmo:mce} can serve as basis for the \autoref{algoritmo:mce-k} for MCE-$k$. 
+Finally, \autoref{algoritmo:mce} can serve as basis for MCE-$k$'s \autoref{algoritmo:mce-k}. 
 Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
@@
 
-        \If{$w(Cov) + w(\cup_{k=j+1}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
+        \If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
         \State $(q_j^*, \dots, q_j^*) \gets(q_j, \dots, q_m)$

### 2020-01-30 defesa/tex/chapter/mcd.tex
wip

@@
-In this chapter, we introduce a version of the classical Euclidean norm PMCLP where each facility has a given coverage radius. 
-We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}. We also propose a method for it intending to adapt it for the elliptical PMCLP that will be introduced in the next chapter.
+In this chapter, we introduce a version of the classical Euclidean norm PMCLP, where each facility has a given coverage radius. 
+We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}. We also propose an algorithm for it to later adapt it for the elliptical PMCLP in the next chapter.
 
@@
 
-A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$ which specifies the center of every disk in $\D$.
-The coverage region of the $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{\ge0}$ be the function
+A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$, which specifies the center of every disk in $\D$.
+Let $w: 2^{\Pp} \mapsto \R_{\ge0}$ be a function, which takes a subset of $\Pp$ and returns the sum of the weights of every point in it, defined as
 
 \begin{equation}\label{eq:subset_w}
-w(A) = \sum_{j : p_j \in A} w_j,
+w(A) = \sum_{j : p_j \in A} w_j.
 \end{equation}
-which takes a subset of $\Pp$ and returns the sum of the weights of every point in it; then an optimal solution of MCD is given by the optmization problem:
+Then an optimal solution of MCD is formulated as a solution of
 
@@
 
-As a remark, it is important to note that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}.
-There, a coverage radius is given for each demand, rather than for each facility, and a demand is only considered covered if a facility is located within its radius.
+It is worth mentioning that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}.
+There, a coverage radius is given for each demand, rather than for each facility, and a demand point is considered covered if a facility is located within its radius.
 
@@
 
-The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set}, which is a finite set of possible solutions, for each facility.
-After a CLS is constructed, a complete search is executed to find the best solution.
-That is why, as an heuristic, it is a good idea to create small CLSs that somehow can still provide good solutions.
+The method proposed in \citeonline{church:1984} involves the construction of a finite set of locations where each facility can be placed as a way of transforming a problem, where every point in $\R^2$ is a possible solution, into one where only a finite number of possibilities need to be considered.
+This set of possible locations is called \sigla{CLS}{Candidate List Set}.
 
-As this work is developed towards the creation of an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
-This is done in \citeonline{church:1984} where a circle is defined for every demand point, and a \sigla{CIPS}{circle intersection point set} is constructed containing the demand points and every pairwise circle intersection.
-Here, we introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.
+In \citeonline{church:1984}, a CLS is set to be the \sigla{CIPS}{circle intersection point set}, which contains the intersection of circles with fixed radii centered at every demand point.
+This approach provides an optimal solution if a complete search on the CLS for every facility is done.
+
+We introduce, in this chapter, a $\bigO(n^2\lg{n})$ algorithm that returns a CLS for each facility, which is based on the idea presented in \citeonline{church:1984} and in the works for the one disk case by \citeonline{chazelle:1986} and \citeonline{cabello:2006}.
+We refer to the CLS for the $j$-th facility as $S_j$ and prove that, indeed, an optimal solution can be found by just considering the centers in $S_j$ for each facility.
 
@@
 
-\section{Maximum Weight Clique Problem}
+\section{Maximum Weight Clique}
 
-An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; a set of unit disks $\D:=\{D_1(p_1),\dots,D_n(p_n)\}$; and a set of weights $\Ww=\{w_1, \dots, w_n\}$ with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it.
-To make the notation less cluttered, we use, in this problem, $D_j:=D_j(p_j)$, for $j\in\{1, \dots, n\}$.
+An instance of the \sigla{MWC}{Maximum Weight Clique} is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$ representing the center of a unit disk;  and \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$ being the weight of the $i$-th unit disk.
+We also define a list $\D=\{D_1, \dots, D_n\}$, such that $D_i$, $i\in\{1,\dots,n\}$, is a unit disk centered at $p_i$ having weight $w_i$ assigned to it.
 
 A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
-Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$ which is inside any of the given disks in $\D$.
-From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$:
+Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$, which is inside any of the given disks in $\D$.
+From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$ as follows
 
@@
 \end{equation*}
+
 With a geometric observation, though, the number of possible values for the solution can be reduced.
-Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, it contains the center of its only disk.
-Because of that, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$.
-Then, with this observation, an optimal solution of MWC can be defined by the optimization problem
+Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$. 
+Unless a clique is formed by only one disk, its boundary contains at least two points, which are the intersection of two circles that are part of the clique.
+Because of that, $q$ can be limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$, which considers the case where the optimal clique is composed of only one disk.
+With this observation, an optimal solution of MWC can be defined by the optimization problem
 
@@
 with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$.
-With this new specification of the solution's search space, it can be shown that given an instance of MWC, an optimal solution for it can be found by going through $\binom{n}{2} + n = \bigO(n^2)$ possible ones.
+With this new specification of the solution's search space, given an instance of MWC, an optimal solution can be found by going through $\binom{n}{2} + n$ points, that is, $\bigO(n^2)$ points.
 
@@
 
-\begin{figure}[H]
-\centering
-
-    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}
-    %\begin{tikzpicture}[scale=1]
-    %\draw [help lines] (-5,-3) grid (5,3);
-    %\draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);
-
-    %a^2-b^2=c^2 -> c^2=25-9=16 -> c=4
-
-    %\draw[fill] (0.9,1.6) circle [radius=.5pt];
-	%\draw[fill] (0,0) circle [radius=.5pt];
-    %\draw[fill] (-0.9,1.6) circle [radius=.5pt];
-
-    %\node[below] at (0,0) {$p_1$};
-    %\node[below] at (0.9, 1.6) {$p_2$};
-    %\node[below] at (-0.9, 1.6) {$p_3$};
-
-    %\draw [-] (-5,0) -- (5,0);
-     %\draw [-] (0,-3) -- (0,3);
-     %\draw [|-|] (0.001,-0.1) -- (4.999,-0.1);
-    %\end{tikzpicture}
-
-    \includegraphics[scale=.35]{tex/figures/three_disks_no_intersection.pdf}
-    \label{fig:three_disks_no_intersection}
-    \fautor
-\end{figure}
-
 As it has been mentioned, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of MCD1, which means that a disk centered at $q^*$ which is an optimal solution of MWC, will have a maximal weight covering of the demand set $\Pp$.
@@
 A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$.
-This means that a intersection between some disks is a region where a disk could be placed to cover the corresponding points.
+This means that an intersection between some disks is a region where a disk could be placed to cover the corresponding points.
 
 In \autoref{fig:three_disks_no_intersection}, it can be seen that there is no point where a disk could be placed such that it would cover $p_1, p_2$ and $p_3$, nonetheless, in any of the pairwise intersections, a disk could be placed to cover the two corresponding points.
+
+\begin{figure}[h]
+	\centering
+
+	\caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}
+
+	\includegraphics[scale=.25]{tex/figures/three_disks_no_intersection.pdf}
+	\label{fig:three_disks_no_intersection}
+	\fautor
+\end{figure}
 
@@
 It has a run time complexity of $\bigO(n^2\log{n})$ and uses $\bigO(n)$ of extra space.
-It is worth noting, however, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \citeonline{bentley:1979} to find all the intersections among the $n$ circumferences.
+It is worth noting, though, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \citeonline{bentley:1979} to find all the intersections among the $n$ circumferences.
 
@@
 \begin{definicao}\label{def:inter_arc}
-    Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and $(\theta_1, \theta_2) \in [0,2\pi)^2$ be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$.
+    Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and \mbox{$(\theta_1, \theta_2) \in [0,2\pi)^2$} be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$.
 Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$.
@@
     \caption{Three disks and their intersection points.}
-    \includegraphics[scale=.36]{tex/figures/3_disks_intersect.pdf}
+    \includegraphics[scale=.3]{tex/figures/3_disks_intersect.pdf}
 %    \input{tex/img2.tex}
@@
 Firstly, let $A_i$ be a circular list that contains the intersection angles of $\partial D_i$ with every circle in $\partial \D$ defined as
-
 \begin{equation*}
@@
 \end{equation}
-Assuming $B_i$ is sorted with the same criteria as $A_i$. A simple traversal, starting at the first element and going until the last one, simulates a traversal on the circular list $A_i$.
+Assuming $B_i$ is sorted with the same criteria as $A_i$, a simple traversal, starting at the first element and going until the last one, simulates a traversal on the circular list $A_i$.
 This works because for any pair of disks $D_i$, $D_j$; $B_i$ contains $\Gamma_+(i,j) < \Gamma_-(i,j) + 2\pi$.
@@
 Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point, and removes $D_1$ only after every point has been processed.
-
-Finally, we define \autoref{algoritmo:mcd_1} for MWC.
-Given an instance $(\Pp, \Ww)$ of MWC, the algorithm uses the approach described here of keeping a set of active disks while traversing the list $B_i$.
-It returns a point that is inside an optimal clique, this way \autoref{algoritmo:mcd_1} can also be used to get an optimal solution for an instance $(\Pp, \Ww)$ of MCD1.
-
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 
-\begin{theorem}\label{lema:disk}
-	\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
-\end{theorem}
-
-\begin{proof}
-	Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \citeonline{bentley:1979}. 
-	Because sorting the intersection angles needs to be done, an additional $\bigO(K\log{K})$ pre-processing is added.
-All the other operations can be done in constant time.
-Therefore, the final algorithm complexity is $\bigO((n+K)\log{n})$.
-\end{proof}
-
-If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (the set of disks that intersect with $D_i$, defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.
-
-\begin{algoritmo}[b]
+Finally, we define \autoref{algoritmo:mcd_1} for MWC.
+Given an instance $(\Pp, \Ww)$ of MWC, the algorithm uses the approach described here of keeping a set of active disks while traversing the list $B_i$.
+It returns a point that is inside an optimal clique, this way \autoref{algoritmo:mcd_1} can also be used to get an optimal solution for an instance $(\Pp, \Ww)$ of MCD1.
+\clearpage
+\begin{algoritmo}[!htb]
 	\caption{Algorithm for MWC.}\label{algoritmo:mcd_1}
@@
 
-\Procedure{$MWC$}{$\Pp, \D, \Ww$}
-\State Let $\D=\{D_1(p_1), \dots, D_n(p_n)\}$ be a set of unit disks
+		\Procedure{$MWC$}{$\Pp, \Ww$}
+		\State Let $\D=\{D_1, \dots, D_n\}$ be a set of unit disks, with centers in $\Pp$ and weights in $\Ww$
+
 		\State $Q_{best} \gets \{\}$
 		\State $q^* \gets$ $p_1$
-\ForAll{$D_i \in \Pp$}
-\State Let $B_i$ be the list of intersection angles of $D_i(p_i)$ as defined by \autoref{eq:b_i}
+		\ForAll{$D_i \in \D$}
+		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}
 
@@
 		\For{$\theta \in B_i$}\Comment{Assuming $B_i$ is sorted.}
-\State Let $D_j$ be the disk, such that $\theta \in D_j(p_j)\cap D_i(p_i)$
+		\State Let $D_j$ be the disk, such that $\theta \in D_j\cap D_i$
 		\If{$\theta$ is a opening angle}
@@
 \end{algoritmo}
+
+\begin{theorem}\label{lema:disk}
+	\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
+\end{theorem}
+
+\begin{proof}
+	Finding every intersection can be done in $\bigO((n+K)\log{n})$  by a plane sweep, the method is described in \citeonline{bentley:1979}. 
+	Because sorting the intersection angles needs to be done, an additional $\bigO(K\log{K})$ pre-processing is added.
+All the other operations can be done in constant time.
+Therefore, the final algorithm complexity is $\bigO((n+K)\log{n})$.
+\end{proof}
+
+If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (the set of disks that intersect with $D_i$, defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.
 

### 2020-01-30 defesa/tex/chapter/mce.tex
wip

@@
 Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}.
-Note that all it takes to describe an axis-parallel ellipse is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, also called its shape parameters, and a center point $q \in \R^2$.
+All it takes to describe one is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, with $a>b$, also called its shape parameters, and a center $q \in \R^2$.
 
@@
 
-Then, a solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
-Finally, let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem
+A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
+Let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem
 
@@
 
-In the next sections, we first describe a method for the case with only one ellipse, and then use it in the algorithm for multiple ellipses to construct a CLS containing an optimal solution.
+In the next sections, we first study the specific case of MCE with only one facility and discuss that the results of \autoref{chapter:pmclp} still apply when ellipses are used instead of disks.
+After that, we use the approach mentioned in \autoref{chapter:pmclp} of constructing a CLS for each facility and propose an algorithm for MCE.
 
@@
 The case with only one ellipse is considered first because it will be adapted to become the basis of the algorithm for more than one ellipse.
-We refer to this version as \sigla{MCE-1}{Maximum Cover by One Ellipse}.
+We refer to this version as \sigla{MCE1}{Maximum Cover by One Ellipse}.
 
-An instance of MCE-1 has $m=1$, and we set $(a, b):=(a_1, b_1)$, and $\E := \{E\}$.
-Therefore, an instance of MCE-1 is described by the tuple $(\Pp; \Ww; (a, b))$.
-A solution of MCE-1 is then given by a point $q\in\R^2$, and an optimal solution is given by the optimization problem
+An instance of MCE1 has $m=1$, and we set $(a, b):=(a_1, b_1)$, and $\E := \{E\}$.
+Therefore, an instance of MCE1 is described by the tuple $(\Pp; \Ww; (a, b))$.
+A solution of MCE1 is then given by a point $q\in\R^2$, and an optimal solution is given by the optimization problem
 
@@
 \end{equation*}
-At last, the case where that angle is equal to $\pi$ happens only when both ellipses intersect at only one point.
+Lastly, the case where that angle is equal to $\pi$ happens only when both ellipses intersect at only one point.
 This case has to be treated separately as, by \autoref{def:inter_arc}, we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.
@@
         \EndProcedure
-
-        \Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j=1$}
+        \State
+        \Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
         \If{$j = m+1$}
@@
         \If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
-        \State $(q_j^*, \dots, q_j^*) \gets(q_j, \dots, q_m)$
+        \State $(q_j^*, \dots, q_m^*) \gets(q_j, \dots, q_m)$
         \EndIf
@@
 
-	\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$, such that $|I|=k$}
+	\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$}
 
-		\State $(q_1, \dots, q_k) \gets MCE(\Pp, \Ww, \{(a_j, b_j) \in \Rr: j \in I\})$
+		\State $\Rr' \gets \{(a_j, b_j) \in \Rr: j \in I\}$
+		\State $(q_1, \dots, q_k) \gets MCE(\Pp, \Ww, \Rr')$
 

### 2020-01-30 defesa/tex/chapter/mcer.tex
wip

@@
-This section introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated.
+This chapter introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated.
 We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
@@
 For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters.
-This problem is discussed with great detail in \autoref{chapter:ellipses_intersection}.
+This problem is discussed with great detail in \autoref{section:ellipses_intersection}.
 

### 2020-02-03 defesa/tex/chapter/e3p.tex
wip

@@
 Let $E$ represent the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3PNT can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
-As a last remark, because of its application on \autoref{chapter:ellipses_n}, a method would only be useful for our case if it can encounter every solution of E3PNT.
+As a last remark, because of its application on \autoref{chapter:mcer}, a method would only be useful for our case if it can encounter every solution of E3PNT.
 This requirement, of course, makes the problem more challenging.
@@
 
-One of the steps of the method developed in \autoref{chapter:ellipses_n} is to iterate over every solution of E3PNT for every triplet of points.
+One of the steps of the method developed in \autoref{chapter:mcer} is to iterate over every solution of E3PNT for every triplet of points.
 Of course doing that is only possible for a finite number of solutions.
@@
 \begin{lema}\label{lema:e3p}
-	E3PNT has at most $6$ solutions.
+	Any instance of E3PNT has at most $6$ solutions.
 \end{lema}
@@
 
-\subsection{Numerical Experiments}
+\subsection{Solutions for some instances}
 
-In this section we show the results of an experiment we made to study the numerical stability of \autoref{algoritmo:e3p}.
-
-We generate random instances of E3PNT according to
-\begin{equation}
-u, v, w \sim \mathcal{N}(0, K^2),
-\end{equation}
-with $K\in \R_{>0}$ being a parameter of the experiment. We also define the ellipse's shape parameters ass
-\begin{align}
-	a = K\\
-	b = \frac{K}{2}.
-\end{align}
-For the experiment, we tried several values for $K$ and adopted the error measure to be $|\xi(\hat{\theta})|$, with $\hat{\theta}$ being a root of the complex polynomial $h$. 
-For each different value of $K$, we ran the algorithm for $1000$ random instances.
-The results are shown in \autoref{fig:e3p_error} where the maximum and the average error  is plotted for each value of $K$ for which the experiment was run.
+From \autoref{lema:e3p}, we know that any instance of E3P has at most six solutions.
+At first, though, it seemed like that bound was loose as we could not find any instances that made \autoref{algoritmo:e3p} return six solutions.
+After some investigation, this turned out not to be the case.
+An example with six solutions is presented in \autoref{fig:e3p_6sols}.
+It is worth mentioning that the only instances that we found which produce six solutions have their three points form an equilateral triangle.
 
@@
 	\centering
-	\caption{The interpolation error measured on roots that were found.}
-	\includegraphics{tex/figures/e3p_error}
+	\caption{An instance of E3P with six solutions.}
+	\includegraphics[scale=.35]{tex/figures/e3p_6sols}
+	\fautor
+	\label{fig:e3p_6sols}
+\end{figure}
+
+Another example is shown in \autoref{fig:e3p_4sols} where an instance of E3P is displayed along with its four solutions.
+
+\begin{figure}[H]
+	\centering
+	\caption{An instance of E3P with four solutions.}
+	\includegraphics[scale=.35]{tex/figures/e3p_4sols}
+	\fautor
+	\label{fig:e3p_4sols}
+\end{figure}
+
+\subsection{Numerical Stability}
+
+In this section we show the results of an experiment that is developed to study the numerical stability of \autoref{algoritmo:e3p}.
+
+We define $K\in\R_{>0}$ as an experiment parameter and consider instances that the ellipse has shape parameters $(K, \frac{K}{2})$.
+Then, random instances are created by setting the three points to be $(K\cos(t_j), \frac{K\sin{(t_j)}}{2})$, $j=1..3$, with $t_j$ being uniformly distributed in the interval $[0, 2\pi]$.
+To evaluate the stability of \autoref{algoritmo:e3p}, for any solution $(\hat{q}, \hat{\theta})$ found, we adopt its error measure to be $|\xi(\hat{\theta})|$.
+
+The experiment was run for various values of $K$.
+For each one of them, $100$ randomly generated instances were considered.
+The results are shown in \autoref{fig:e3p_error}, where the average and the maximum error are plotted.
+
+\begin{figure}[H]
+	\centering
+	\caption{The error measured on solutions found by \autoref{algoritmo:e3p}.}
+	\includegraphics[scale=.9]{tex/figures/e3p_error}
 	\fautor

### 2020-02-03 defesa/tex/chapter/mcer.tex
wip

@@
 
-An instance of the non-axis-parallel is defined exactly like the axis-parallel one on \autoref{chapter:ellipses}.
+An instance of the non-axis-parallel is defined exactly like the axis-parallel one on \autoref{chapter:mce}.
 It is given by a set of demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; a list of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$;
@@
 
-	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses.
+	As it was shown on \autoref{chapter:mce}, $X$ is a region that is limited by arcs of ellipses.
 As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point, creating a vertex.
@@
 
-	From \autoref{chapter:ellipses_intersection}, we can conclude that $|S_j^{(2)}|\le 2\binom{n}{2} = \bigO(n^2)$.
+	From \autoref{section:ellipses_intersection}, we can conclude that $|S_j^{(2)}|\le 2\binom{n}{2} = \bigO(n^2)$.
 	By \autoref{lema:e3p}, we have that $|S_j^{(3)}| \le 6\binom{n}{3} = \bigO(n^3)$.
@@
 
-		\Procedure{$MCER_1$}{$\Pp, a, b$}
+		\Procedure{CLS-MCER}{$\Pp, a, b$}
 		\State $S \gets \{\}$
@@
 Even though it is based on \autoref{th:mcer}, the set of solutions $\Omega(\Pp, \Ww, \Rr)$ is not explicitly built in \autoref{algoritmo:mcer}.
-Instead, a complete search is done by backtracking the CLS of every ellipse returned by procedure $MCER_1$.
+Instead, a complete search is done by backtracking the CLS of every ellipse returned by procedure CLS-MCER.
 
@@
 		\State $ans \gets 0$
-		\State $(q_{j}^*\gets 0, \dots, q_m^*\gets0); (\theta_{j}^*\gets 0, \dots, \theta_m^*\gets 0)$ \Comment{Setting to $0$ as a default value.}
+		\State $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*) \gets (0, \dots 0); (0, \dots, 0)$ \Comment{Setting to $0$ as a default value.}
 
-		\State $S_j \gets MCER_1(Z, a_j, b_j)$
+		\State $S_j \gets \textnormal{CLS-MCER}(Z, a_j, b_j)$
 
@@
 \begin{corolario}
-	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ computations and returns an optimal solution.
+	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ computations and returns an optimal solution for an instance of MCER.
 \end{corolario}
@@
 
+In this section, we consider the extended version of MCER where each facility has a cost assigned to it and exactly $k$ of them must be used in a solution.
+We refer to this version of the problem as \sigla{MCER-$k$}{Maximum Covering by Ellipses with Rotation and a $k$-constraint}.
+
+An instance of MCER-$k$ has the same parameters as MCER plus a list of costs \mbox{$\Cc:=\{c_1, \dots, c_m\}$}, with $c_j\in\R_{>0}$ being the cost of the $j$-th facility; and $k\in\mathbb{N}$, $k\le m$.
+
+A solution for MCER-$k$ is given by $(I, Q, \Theta)$, with $I:=\{i_1, \dots, i_k\}\subset \{1, \dots, m\}$; \\\mbox{$Q:=(q_1, \dots, q_k)\in\R^{2k}$}, with $q_j$ being the center of the $i_j$-th ellipse; and \mbox{$\Theta:=(\theta_1, \dots, \theta_k) \in [0, \pi)^k$}, with $\theta_j$ being the angle of rotation of the $i_j$-th ellipse.
+An optimal solution of MCER-$k$ is given by the optimization problem
+
+\begin{equation*}
+	\max_{I, Q, \Theta} w\left(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j, \theta_j)\right).
+\end{equation*}
+
+Then, in the same way that it is done in \autoref{chapter:mce}, we introduce \autoref{algoritmo:mcer-k} for MCER-$k$ that uses \autoref{algoritmo:mcer} for every $I:=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$.
+Therefore, \autoref{algoritmo:mcer-k} returns an optimal solution for MCER-$k$ in $\bigO(\binom{m}{k}n^{3k}) = \bigO(n^{4m})$ time.
+
+\begin{algoritmo}
+	\caption{Algorithm for MCER-$k$}\label{algoritmo:mcer-k}
+
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, a list of costs $\Cc=\{c_1, \dots, c_m\}$, and $k\in \mathbb{N}$.}
+		\Ensure{An optimal solution for MCER-$k$.}
+
+		\item[]
+
+		\Procedure{MCE-$k$}{$\Pp, \Ww, \Rr, \Cc, k$}
+		\State $I^* = \{i_1^*, \dots, i_k^*\}\gets \{1, \dots, k\}$
+		\State $Q^* = (q_1^*, \dots, q_k^*) \gets (0, \dots, 0)$
+		\State $\Theta^* = (\theta_1^*, \dots, \theta_k^*) \gets (0, \dots, 0)$
+
+		\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$}
+
+		\State $\Rr' \gets \{(a_j, b_j) \in \Rr: j \in I\}$
+		\State $(q_1, \dots, q_k); (\theta_1, \dots, \theta_k) \gets MCER(\Pp, \Ww, \Rr')$
+
+		\If{$w(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j, \theta_j)) - \sum_{j\in I} c_j > w(\bigcup_{j=1}^k \Pp \cap E_{i_j^*}(q_j^*, \theta_j^*)) - \sum_{j\in I^*}c_{j}$}
+		\State $Q^* \gets (q_1, \dots, q_k)$
+		\State $\Theta^* \gets (\theta_1, \dots, \theta_k)$
+		\State $I^* \gets I$
+		\EndIf
+		\EndFor
+
+		\State \Return $I^*, Q^*, \Theta^*$
+		\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}
+
 \subsection{Improvements and implementation details}
@@
 Some improvements can be made in the implementation of \autoref{algoritmo:mcer}.
-Instead of calling procedure $MCE_1$ every time in the backtracking routine, it is suggested that it is done outside in a pre-processing phase.
+Instead of calling procedure CLS-MCER every time in the backtracking routine, it is suggested that it is done outside in a pre-processing phase.
 
@@
 If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, solution $(Q', \Theta')$ can be dismissed.
-This can be done in the $MCE_1$ procedure in \autoref{algoritmo:mcer1}.
+This can be done in the CLS-MCER procedure in \autoref{algoritmo:mcer1}.
 
@@
 This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be pre-processed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER$ procedure.
+
+I n the next section we present the results of numerical experiments for MCER and MCER-$k$ and compare them with the results published in \citeonline{andreta}.

### 2020-02-04 defesa/tex/chapter/e3p.tex
wip

@@
-The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section.
-Even though its simple statement--it is short and uses only basic mathematical concepts--we were not able to find any work on it, or even on related problems.
-As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way.
+The problem of finding every center and angle of rotation of a fixed shape ellipse, which makes it have three points on its border, is presented in this section.
+
+Even though its simple statement -- it is short and uses only basic mathematical concepts -- we were not able to find any work on it, or even on related problems.
+As a result, starting from scratch, we ended up trying a handful of approaches, with most of them failing on the way.
 We try to give a review of some of those, going through the issues with the failing ones.
-At the end we propose an algorithm that takes around $6^3$ operations to compute every solution of the problem.
-Also, we run some experiments to analyze its efficiency in terms of numerical precision and CPU time.
+In the end, we propose an algorithm that takes around $6^3$ operations to compute every solution for any instance of the problem and run some experiments to analyze its efficiency in terms of numerical precision and CPU time.
 
@@
 
-We call the problem introduced in this section \sigla{E3PNT}{Ellipse by Three Points}.
+We call the problem introduced in this section \sigla{E3P}{Ellipse by Three Points}.
 An instance of it is given by three points $u, v, w \in \R^2$ and the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, with $a > b$.
 
-Let $E$ represent the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3PNT can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
-As a last remark, because of its application on \autoref{chapter:mcer}, a method would only be useful for our case if it can encounter every solution of E3PNT.
+Let $E$ represent the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3P can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
+As a last remark, because of its application on \autoref{chapter:mcer}, a method would only be useful for our case if it can encounter every solution of E3P.
 This requirement, of course, makes the problem more challenging.
@@
 
-Initially, E3PNT is a problem with three unknown variables: the two coordinates of the center point $q_x, q_y, $ and the angle of rotation $\theta$.
-In this section, we transform E3PNT into the problem of finding the roots of an univariate function using the known problem of determining the circumcircle of a triangle.
-We also show E3PNT has at most $6$ solutions.
+Initially, E3P is a problem with three unknown variables: the two coordinates of the center point, $q_x$ and $q_y$, and the angle of rotation $\theta$.
+In this section, we transform E3P into the problem of finding the roots of a univariate function using a known circumcircle problem.
+This transformation, besides reducing the number of unknown variables to one, is later utilized in the demonstration that E3P has at most six distinct solutions, which is one of the most important properties of E3P.
 
-To make the problem simpler, let us translate the system, so the point $u$ is at the origin; that is, assume that the three points given by the E3PNT instance are $(0, 0); v; w$.
-After that, we assume that the ellipse is actually axis-parallel and the points are the ones rotating.
-When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$ transforming the ellipse into a circle of radius $b$.
-This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed firstly into an axis-parallel ellipse, and then into a circle of radius $b$.
-This process can be parameterized by the angle of rotation of the points, as described by
-
+To make the problem simpler, let us translate the system, so the point $u$ is at the origin.
+That is, assume that the three points given by the E3P instance are $(0, 0); v; w$.
+After that, we assume that the ellipse is axis-parallel, and the points are the ones rotating.
+When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to squeeze the x-axis by $\frac{b}{a}$.
+This compression on the $x$-axis makes the ellipse become a circle of radius $b$.
+As only invertible transformations are used, given the final state where the three points are on the border of a circle of radius $b$, reversing the two transformations (stretching by $\frac{a}{b}$, rotating by $-\theta$) provides a solution of E3P.
+The whole process can be seen in \autoref{fig:circumscribed-circle} where a solution of the E3P is transformed firstly into an axis-parallel ellipse, and then into a circle of radius $b$.
+We introduce a function $\varphi\colon \R^2 \to \R^2$ that takes any point and apply these transformations to it as
 \begin{equation}\label{eq:trpnts}
@@
 Also, to make the notation more clear, we denote by $\Lambda(\theta)$ the triangle formed by the points $(0, 0); \varphi(v, \theta); \varphi(w, \theta)$, as long as they are not collinear.
-This being said, we go further to introduce another problem which is equivalent to E3PNT.
+This being said, we go further to introduce a circumcircle problem which is equivalent to E3P.
 
@@
 The term circumradius, in this work, is used to describe the radius of a triangle's circumscribed circle, which is a circle that has the triangle's vertices on its border.
-Given an instance of E3PNT, we define the circumradius problem as the problem of determining an angle of rotation $\theta$, such that the circumradius of $\Lambda(\theta)\in[0, \pi)$ is equal to $b$.
+Given an instance of E3P, we define the circumradius problem as the problem of determining an angle of rotation $\theta\in[0, \pi)$, such that the circumradius of $\Lambda(\theta)$ is equal to $b$.
 
-As it can be seen on \autoref{fig:circumscribed-circle}, given an instance of E3PNT and an angle of rotation $\theta\in[0, \pi)$ that makes $\Lambda(\theta)$ have a circumradius $b$; a solution for E3PNT can be obtained using the inverse transformation $\varphi^{-1}$.
-This is possible because for any fixed $\theta$, $\varphi$ is just a linear function which are known to be invertible.
-With that in mind, it is possible to conclude that both problems are equivalent because, from a solution of one, an unique solution of the other can be obtained.
+As it can be seen on \autoref{fig:circumscribed-circle}, given an instance of E3P and an angle of rotation $\theta\in[0, \pi)$ that makes $\Lambda(\theta)$ have a circumradius $b$; a solution for E3P can be obtained using the inverse transformation $\varphi^{-1}$.
+With that in mind, it is possible to conclude that both problems are equivalent because, from a solution of one, a unique solution of the other can be obtained.
 
 The main reason to work with this problem is the reduction in the number of unknown variables from three to just one.
-This idea, however, would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
-
-It turns out that for three non-collinear points, there is always an unique circumscribed circle.
-Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the expression
+This idea, however, would only be useful if checking the existence of a circumscribed circle with a radius $b$ is a convenient problem.
+It turns out that, for three non-collinear points, there is always a unique circumscribed circle.
+Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the following expression
 
@@
 with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle see \citeonline[p.~189]{johnson1960}
-). It should be pointed out that the transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
+). It should be pointed out that this transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
 
@@
 \end{equation}
-Any root of $\xi$ produces a triangle whose circumradius is $b$ and subsequently provides a solution for E3PNT.
+Any root of $\xi$ produces a triangle whose circumradius is $b$ and subsequently provides a solution for E3P.
 
-The next step is then to develop an algorithm to find every root of $\xi$.
-Before continuing with this approach though, it is important to address the question about the number of roots of $\xi$ in the interval $[0, \pi)$.
+Before attempting to develop an algorithm to find every root of $\xi$, we address the question about the number of roots of $\xi$ in the interval $[0, \pi)$.
 
-\subsection{The number of solutions of E3PNT}
+\subsection{The number of solutions of E3P}
 
-One of the steps of the method developed in \autoref{chapter:mcer} is to iterate over every solution of E3PNT for every triplet of points.
-Of course doing that is only possible for a finite number of solutions.
-Moreover, even if the number of solutions is finite, discovering a bound for it is essential for determining the algorithm's efficiency.
+One of the steps of the method developed in \autoref{chapter:mcer} is to iterate over every solution of E3P for every triplet of points.
+Of course, doing that is only possible for a finite number of solutions.
+Moreover, even if the number of solutions is finite, discovering an upper-bound for that is essential for determining the algorithm's efficiency.
 
 \begin{lema}\label{lema:e3p}
-	Any instance of E3PNT has at most $6$ solutions.
+	Any instance of E3P has at most $6$ solutions.
 \end{lema}
@@
 Back on \autoref{chapter:definitions}, real trigonometric polynomials were introduced.
-It was stated that a $n$-degree polynomial can have up to $2n$ distinct roots.
+It was stated that any $n$-degree polynomial can have up to $2n$ distinct roots.
 It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2}.
@@
  \end{align}
-  It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared lengths of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$.
+  It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared lengths of the triangle formed by the points $(0, 0), \varphi(v, \theta), \varphi(w, \theta)$.
 This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\norm{\varphi(v, \theta)}^2$ is $6$ which consequently is the degree of $\xi$.
@@
 Setting the first point to be the origin, we get $F=0$, using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$.
-As any multiple of \autoref{eq:gen_ellipse} represents the same conic, we can set $B$ to be equal $1$.
-Then, we end up with two variables, $A$ and $C$, and still need to impose that the final equation represents an ellipse and its major-axis and minor-axis have the predefined value.
-Let $\Delta=4AC-B^2=4AC-1$, and assume $F=0$, then the expressions for both major-axis and minor-axis respectively are
+As any multiple of \autoref{eq:gen_ellipse} represents the same conic, we can set $B$ to be equal to $1$.
+Then, we end up with two variables, $A$ and $C$, and still need to impose that the final equation represents an ellipse with the given shape parameters.
+Let $\Delta=4AC-B^2=4AC-1$, and assume $F=0$, then the expressions for both major-axis and minor-axis, respectively are
 \begin{align}\label{eq:gen_ellipse_a}
@@
 The solutions lie in the set of intersection of these curves.
-Finding this set was judged to be non-trivial and probably could be approximated numerically, however, we decided not to further pursue this approach.
+This set can probably be done approximated numerically, however, we decided not to further pursue this approach.
 
@@
 For this problem, the approximation of $\xi$ on the interval $[0, \pi)$ is considered.
-The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n\times n$ matrix.
+The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials whose roots can be found through determining the eigenvalues of a $n\times n$ matrix.
 
@@
 Even though $\xi$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is a very well-behaved function: it is analytic and has infinitely many continuous and integrable derivatives.
-This satisfy all the requirements of the result in \citeonline[p.~28]{gottlieb} which says that if a function has $m$ continuous and integrable derivatives on a closed interval, then its absolute difference between the Chebyshev truncate series is $\bigO(n^{-m})$.
-Also, in \citeonline{battles:2004} a theorem is presented stating that if a function is analytic on a neighborhood of $[-1, 1]$, then the convergence is $\bigO(C^n)$, for some $C<1$.
+This satisfies all the requirements of the result in \citeonline[p.~28]{gottlieb}, which says that if a function has $m$ continuous and integrable derivatives in a closed interval, its absolute difference to its respective Chebyshev truncate series is $\bigO(n^{-m})$.
+Also, in \citeonline{battles:2004}, a theorem is presented stating that if a function is analytic on a neighborhood of $[-1, 1]$, then the convergence is $\bigO(C^n)$, for some $C<1$.
 
 To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}.
-There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error
+There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is considered to be a good estimate for the error
 
@@
 
-In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved. 
-The interpolation was run for several degrees for every triplet of points present in an instance from \citeonline{canbolat}.
-We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found; simply put we measure how close the roots are to zero.
+In this section, we run some experiments to verify how big the interpolation degree must be for good precision to be achieved. 
+The interpolation was run for several degrees, for every triplet of points in an instance from \citeonline{canbolat}.
+We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found.
 
-The results are shown in \autoref{fig:interpolant_error} where the worst error found among every root found is plotted against the interpolant degree used.
-A parameter $K$ is also used in the experiments.
-This is an idea suggested in \citeonline{boyd:2013} to improve accuracy, this parameter represents the number of sub-intervals that $[0, \pi)$ is divided into.
-This way, $K$ interpolations are used to obtain every root in the whole interval.
-It can be seen in \autoref{fig:interpolant_error} that this strategy helps a lot in improving the accuracy even when not so large degrees are used.
+The results are shown in \autoref{fig:interpolant_error}, where the worst error found among every root is plotted against the interpolant degree.
+To improve accuracy while keeping the interpolation degree low, we took a suggestion from \citeonline{boyd:2013}, and divided  $[0, \pi)$ into $K$ sub-intervals.
+That way, $K$ interpolations are used to obtain every root in the whole interval.
+It can be seen in \autoref{fig:interpolant_error} that this strategy helps a lot in improving the accuracy even when degrees around $8$ are used.
 
@@
 For that reason, we discuss two ways of converting $\xi$ into a polynomial in this section.
-Symbolic computing was used to compute the polynomials, the Python external library called SymPy was utilized (see \citeonline{sympy} for more details).
+The first one converts $\xi$ into a real polynomial and the second one into a complex polynomial.
+
+%Symbolic computing was used to compute the polynomials, the Python external library called SymPy was utilized (see \citeonline{sympy} for more details).
 
@@
 
-The first attempt was using the identity $x = \tan{\frac{\theta}{2}}$ from which it is possible to construct a $12$-degree polynomial.
-At first,  the root-finding algorithm described on \autoref{chapter:definitions} seemed to work fine and return every solution of E3PNT, however, we later found out that for some instances, priorly known roots were not being found.
+From $\xi$, a real polynomial can be obtained by using the identity $x = \tan{\frac{\theta}{2}}$.
+We do not go in detail, but it is possible to show that a degree-$12$ polynomial can be obtained using that substitution.
+Computing the actual coefficients can be done using symbolic computing. In practice, we utilized Python's external library SymPy (see \citeonline{sympy} for more details).
+
+At first,  the root-finding algorithm described on \autoref{chapter:definitions} seemed to work fine and return every solution of E3P, however, we later found out that for some instances, priorly known roots were not being found.
 The cause was not for sure identified, but a good guess would be that for angles which are greater than $\frac{\pi}{4}$, $x$ starts growing too rapidly which could lead to numerical instability.
@@
 
-The second approach is based on a idea published in \citeonline{boyd:2006} which uses the identities on \autoref{eq:complex_trig} to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
-This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial--more details about this can be found in \citeonline{weidner} where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
-
+A complex polynomial can be obtained from $\xi$ by using an idea published in \citeonline{boyd:2006}. There, the author uses the identities
 \begin{align}\label{eq:complex_trig}
-\cos{\theta} = \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
-\sin{\theta} = \dfrac{e^{i\theta} - e^{-i\theta}}{2i}.
+	\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
+	\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i},
 \end{align}
+which relate complex numbers with trigonometric functions, to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
+This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner} where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
 
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, the function $g(e^{i\theta})$ and the function $\xi$ are equivalent since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
+As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, the function $g(e^{i\theta})$ and the $\xi$ are equivalent since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
 
-The function $g$ is still not a polynomial as $z$ shows up with negative exponents (up to $-6$), and its domain is the unit circle $\mathbb{S}$, not the whole complex set $\mathbb{C}$. 
-The first issue can be fixed by multiplying $g$ by $z^6$, note that this does not create further problems as $0\not\in \mathbb{S}$.
-The second issue is removed by simply extending the domain from $\mathbb{S}$ to $\mathbb{C}$, as $\mathbb{S} \subset \mathbb{C}$, roots outside the unit circle could appear which requires a further check for every root that is found.
+The first issue can be fixed by multiplying $g$ by $z^6$.
+Note that this does not create further problems as $0\not\in \mathbb{S}$.
+The second issue is removed by simply extending the domain from $\mathbb{S}$ to $\mathbb{C}$.
+As $\mathbb{S} \subset \mathbb{C}$, roots outside the unit circle could appear in the new polynomial, but they can be ignored as they are not roots of $g$.
 Finally, from $g$, the polynomial $h : \mathbb{C} \mapsto \mathbb{C}$ is defined as
@@
 Lastly, every root of $g$ will correspond to a root of $\xi$ through their angles on the unit circle.
+As in the first case, symbolic computing can be put in practice to determine the coefficients of $h$ as functions of E3P's instance.
+For more information about the Python's external library utilized called SymPy see \citeonline{sympy}.
 
@@
 
-Finally, in the next section we use this approach of converting $\xi$ into a complex polynomial to develop an algorithm for E3PNT.
+Finally, in the next section we use this approach of converting $\xi$ into a complex polynomial to develop an algorithm for E3P.
 
-\section{An algorithm for E3PNT}
+\section{An algorithm for E3P}
 
-Among the methods that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
+Among the methods that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3P.
 The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation.
@@
 Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}).
-This way, $c_0, \dots, c_{12}$ can be written as functions of a E3PNT's instance.
+This way, $c_0, \dots, c_{12}$ can be written as functions of a E3P's instance.
 
@@
 
-		\Procedure{$E3PNT$}{$u,v,w,a,b$}
+		\Procedure{$e3p$}{$u,v,w,a,b$}
 
@@
 \begin{teorema}\label{th:e3p}
-	The \autoref{algoritmo:e3p} computes every solution of E3PNT in $\bigO(1)$ operations.
+	The \autoref{algoritmo:e3p} computes every solution of E3P in $\bigO(1)$ operations.
 \end{teorema}
@@
 \begin{proof}
-	It has already been shown that computing every root of $\xi$ through the complex polynomial yields every solution of E3PNT, the only thing left to prove is the running time of the algorithm.
+	It has already been shown that computing every root of $\xi$ through the complex polynomial yields every solution of E3P, the only thing left to prove is the running time of the algorithm.
 	Computing every eigenvalue of a matrix can be done in $\bigO(n^3)$, but as for our case $n$ is fixed at $6$, it can be stated that computing the eigenvalues for the companion matrix of $f$ can be done in $\bigO(1)$.
@@
 
-\subsection{Solutions for some instances}
+\subsection{Instances with six and four solutions}
 
-From \autoref{lema:e3p}, we know that any instance of E3P has at most six solutions.
-At first, though, it seemed like that bound was loose as we could not find any instances that made \autoref{algoritmo:e3p} return six solutions.
-After some investigation, this turned out not to be the case.
-An example with six solutions is presented in \autoref{fig:e3p_6sols}.
-It is worth mentioning that the only instances that we found which produce six solutions have their three points form an equilateral triangle.
+Any instance of E3P, as stated by \autoref{lema:e3p} can have up to six solutions.
+At first, though, this bound seemed to be loose as for randomly generated instances like the ones generated by the model in the next section, only two solutions were returned by \autoref{algoritmo:e3p}.
+After some investigation, we were able to construct some four-solution instances (an example is displayed in \autoref{fig:e3p_4sols}).
+An interesting property of those solutions is that every one of them has their three points form an isosceles triangle.
+
+\begin{figure}[H]
+	\centering
+	\caption{An instance of E3P with four solutions.}
+	\includegraphics[scale=.35]{tex/figures/e3p_4sols}
+	\fautor
+	\label{fig:e3p_4sols}
+\end{figure}
+
+Obtaining six-solution instances, on the other hand, was done by taking a particular case of the isosceles-triangle approach.
+As it can be seen in \autoref{fig:e3p_6sols}, the three points on every one of the six ellipses' border form an equilateral triangle.
 
@@
 
-Another example is shown in \autoref{fig:e3p_4sols} where an instance of E3P is displayed along with its four solutions.
-
-\begin{figure}[H]
-	\centering
-	\caption{An instance of E3P with four solutions.}
-	\includegraphics[scale=.35]{tex/figures/e3p_4sols}
-	\fautor
-	\label{fig:e3p_4sols}
-\end{figure}
+It should be pointed out that neither non-isosceles instances with four solutions nor non-equilateral instances with six solutions could be found.
+Further investigating these possible properties of E3P is left as future work.
 
@@
 
-We define $K\in\R_{>0}$ as an experiment parameter and consider instances that the ellipse has shape parameters $(K, \frac{K}{2})$.
-Then, random instances are created by setting the three points to be $(K\cos(t_j), \frac{K\sin{(t_j)}}{2})$, $j=1..3$, with $t_j$ being uniformly distributed in the interval $[0, 2\pi]$.
+We define $K\in\R_{>0}$ as an experiment parameter and consider instances with the ellipse's shape parameters $(K, \frac{K}{2})$.
+The three points are generated randomly as $(K\cos(t_j), \frac{K\sin{(t_j)}}{2})$, $j=1..3$, with $t_j$ being uniformly distributed in the interval $[0, 2\pi]$.
 To evaluate the stability of \autoref{algoritmo:e3p}, for any solution $(\hat{q}, \hat{\theta})$ found, we adopt its error measure to be $|\xi(\hat{\theta})|$.
@@
 For each one of them, $100$ randomly generated instances were considered.
-The results are shown in \autoref{fig:e3p_error}, where the average and the maximum error are plotted.
+The results are shown in \autoref{fig:e3p_error}, where the average and the maximum error are plotted for each value of $K$.
+Analyzing the results shown in \autoref{fig:e3p_error}, it is fair to say that \autoref{algoritmo:e3p} is numerically stable for this example, and, as long as the instances have values within the box $[-10^5, 10^5]$, a small error can be expected.
 
@@
 
-From this experiment, it is possible to conclude that the accuray of \autoref{algoritmo:e3p} is acceptable when the instance of E3PNT has numerical values within the box $[-10^5, 10^5]^2$.
-A more rigorous study on the numerical stability of E3PNT is left as future work.
+This experiment served as a basis for us to define the precision constant as $10^{-7}$ for the implementation of \autoref{algoritmo:e3p}. 
+This constant is used floating point comparisons in situations like checking if a root of $h$ is in the unit circle, comparing if two roots of $\xi$ represent the same solution, and checking if the three points are in the border of an ellipse considered as a solution.

### 2020-02-05 defesa/tex/chapter/definicoes.tex
wip

@@
 Lastly, two observations that are very important for the developments of \autoref{chapter:e3p} need to be stated. Let $z\in \mathbb{C}$, then we have 
-\begin{align*}
-angle(\bar{z}) = 2\pi-angle(z),\\
-angle(-z) = \pi + angle(z).
-\end{align*}
+\begin{align}
+angle(\bar{z}) &= 2\pi-angle(z),\nonumber\\
+angle(-z) &= \pi + angle(z).\label{eq:angle_op_sign}
+\end{align}
 Checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.

### 2020-02-05 defesa/tex/chapter/e3p.tex
wip

@@
 We do not go in detail, but it is possible to show that a degree-$12$ polynomial can be obtained using that substitution.
-Computing the actual coefficients can be done using symbolic computing. In practice, we utilized Python's external library SymPy (see \citeonline{sympy} for more details).
+Computing the actual coefficients can be done using symbolic computing.
+
+%In practice, we utilized Python's external library SymPy (see \citeonline{sympy} for more details).
 
@@
 Lastly, every root of $g$ will correspond to a root of $\xi$ through their angles on the unit circle.
-As in the first case, symbolic computing can be put in practice to determine the coefficients of $h$ as functions of E3P's instance.
-For more information about the Python's external library utilized called SymPy see \citeonline{sympy}.
+As in the first approach, symbolic computing can be put in practice to determine the coefficients of $h$ as functions of E3P's instance.
 
@@
 
-It is possible to make another reduction to obtain a degree-$6$ polynomial.
-As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
-In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
-On the other hand, in \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
-\begin{equation*}
-angle(-z) = \pi + angle(z).
-\end{equation*}
-From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$.
-This implies that $h$ is, in fact, an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
-\begin{align}
-h(-z) = (-z)^6g(-z) = z^6g(z).
-\end{align}
-Therefore, all the odd degree coefficients of $h$ are zero and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$ as follows
+It is possible to make another reduction and cut the size of the polynomial in half.
+As it has been mentioned in \autoref{chapter:definitions}, an ellipse is symmetric with respect to its axis, which implies that rotating it by $\theta \in [0, \pi)$ is equivalent to rotating it by $\pi + \theta$.
+On the other hand, very conveniently, as given by \autoref{eq:angle_op_sign}, angles of complex numbers of opposite signs are $\pi$ apart from each other, which means that $g$ has to produce the same output for both $z$ and $-z$ as they represent equivalent angles of rotation for ellipses.
+From that, for all $z\in \mathbb{S}$ we have
+\begin{align*}
+h(-z) = (-z)^6g(-z) = z^6g(z) = h(z).
+\end{align*}
+Therefore, every odd degree coefficients of $h$ must be zero and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$ as follows
 \begin{equation}
@@
 Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the identity
-\begin{equation}
+\begin{equation*}
 angle(\sqrt{z}) = angle(z)/2.
-\end{equation}
+\end{equation*}
 
@@
 Among the methods that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3P.
-The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation.
-Ultimately, this method requires finding the eigenvalues of a companion matrix, which is usually going to be larger than the $6\times 6$, which is the size of the companion matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.
+Despite the good results shown by the Chebyshev interpolation method,
+it can still be classified as a heuristic as none of the approaches to determine the interpolation degree ensures a good approximation in the whole interval.
+On top of that, ultimately, the roots of the Chebyshev polynomial are computed through determining the eigenvalues of a companion matrix, which, unless a lower-than-seven interpolation degree is utilized, is going to be larger than the companion matrix whose eigenvalues are the roots of the complex polynomial $h$.
 
@@
 Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}).
-This way, $c_0, \dots, c_{12}$ can be written as functions of a E3P's instance.
+This way, $c_0, \dots, c_{12}$ can be written as functions of the E3P's instance.
+Then, basically, after building a companion matrix for the polynomial $h$, \autoref{algoritmo:e3p}, for every eigenvalue, applies the reverse transformations described by \autoref{eq:trpnts} to obtain a solution for E3P.
 
@@
 \begin{teorema}\label{th:e3p}
-	The \autoref{algoritmo:e3p} computes every solution of E3P in $\bigO(1)$ operations.
+	The \autoref{algoritmo:e3p} computes every solution for an instance of E3P in $\bigO(1)$ operations.
 \end{teorema}
@@
 	Computing every eigenvalue of a matrix can be done in $\bigO(n^3)$, but as for our case $n$ is fixed at $6$, it can be stated that computing the eigenvalues for the companion matrix of $f$ can be done in $\bigO(1)$.
-Therefore, the whole algorithm runs in constant time.
 \end{proof}
@@
 	\caption{The error measured on solutions found by \autoref{algoritmo:e3p}.}
-	\includegraphics[scale=.9]{tex/figures/e3p_error}
+	\includegraphics[scale=.8]{tex/figures/e3p_error}
 	\fautor
@@
 This experiment served as a basis for us to define the precision constant as $10^{-7}$ for the implementation of \autoref{algoritmo:e3p}. 
-This constant is used floating point comparisons in situations like checking if a root of $h$ is in the unit circle, comparing if two roots of $\xi$ represent the same solution, and checking if the three points are in the border of an ellipse considered as a solution.
+This constant is used in floating point comparisons in situations like checking if a root of $h$ is in the unit circle, comparing if two roots of $\xi$ represent the same solution, and checking if the three points are in the border of an ellipse considered as a solution.

### 2020-02-05 defesa/tex/chapter/mcer.tex
wip

@@
 	\label{fig:lema-3-points}
-\end{figure}.
+\end{figure}
 
@@
 
-		\Ensure{An optimal solution of MCER.}
+		\Ensure{An optimal solution for the given instance of MCER.}
 
@@
 
-		\Procedure{MCE-$k$}{$\Pp, \Ww, \Rr, \Cc, k$}
+		\Procedure{MCER-$k$}{$\Pp, \Ww, \Rr, \Cc, k$}
 		\State $I^* = \{i_1^*, \dots, i_k^*\}\gets \{1, \dots, k\}$
@@
 
-I n the next section we present the results of numerical experiments for MCER and MCER-$k$ and compare them with the results published in \citeonline{andreta}.
+In the next section we present the results of numerical experiments for MCER and MCER-$k$ and compare them with the results published in \citeonline{andreta}.

### 2020-02-06 defesa/tex/chapter/e3p.tex
wip

@@
 
-In this section we show the results of an experiment that is developed to study the numerical stability of \autoref{algoritmo:e3p}.
+In this section we show the results of some experiments made to study the numerical stability of \autoref{algoritmo:e3p}.
+For all the experiments, we define $K\in\R_{>0}$, and consider instances with ellipse's shape parameters $(K, \frac{K}{2})$, for $K\in\{10^j\colon j=0,\dots,10\}$.
+Let $\delta\colon\R^2\to\R$ be a function defined as the left-hand-size of \autoref{eq:rotated_ellipse}, then, for an instance with three points $u, v, w \in \R^2$, we define the error associated with a solution for that instance as $\max\{|\delta(u)|, |\delta(v)|, |\delta(w)|\}$.
 
-We define $K\in\R_{>0}$ as an experiment parameter and consider instances with the ellipse's shape parameters $(K, \frac{K}{2})$.
-The three points are generated randomly as $(K\cos(t_j), \frac{K\sin{(t_j)}}{2})$, $j=1..3$, with $t_j$ being uniformly distributed in the interval $[0, 2\pi]$.
-To evaluate the stability of \autoref{algoritmo:e3p}, for any solution $(\hat{q}, \hat{\theta})$ found, we adopt its error measure to be $|\xi(\hat{\theta})|$.
-
-The experiment was run for various values of $K$.
-For each one of them, $100$ randomly generated instances were considered.
-The results are shown in \autoref{fig:e3p_error}, where the average and the maximum error are plotted for each value of $K$.
-Analyzing the results shown in \autoref{fig:e3p_error}, it is fair to say that \autoref{algoritmo:e3p} is numerically stable for this example, and, as long as the instances have values within the box $[-10^5, 10^5]$, a small error can be expected.
-
+The first experiment considers instances where the three points are the vertices of an ellipse rotated by $\theta\in[0, \pi)$.
+It is possible to see that such instances only have one solution, and therefore, roots with multiplicity greater than one are expected, which can be seen as a special case.
+For each value of $K$, we ran the algorithm for $100$ instances generated randomly by sampling $\theta$ according to a uniform distribution.
+For each instance, we took the closest solution to the priorly known one, and then, for each $K$, as it can be seen in \autoref{fig:e3p_known_sols1}, we considered the maximum and the average error.
 \begin{figure}[H]
+	\centering
+	\caption{The maximum and average error for instances with known solutions.}
+	\includegraphics[scale=.8]{tex/figures/e3p_known_sols1}
+	\fautor
+	\label{fig:e3p_known_sols1}
+\end{figure}
+The second experiment takes the same instances as the previous one, but this time, we analyze how close the roots corresponding to the priorly known solutions are to the unit circle.
+The distance of a root $\hat{x}$ of $h$ to the unit circle is taken to be $|\hat{x}-1|$.
+This experiment is utilized mostly to determine a good precision constant for floating point comparisons in the implementation.
+The results are shown in \autoref{fig:e3p_known_sols2}.
+As it can be seen that the distance always stays under $10^{-6}$ we concluded that a good precision constant would be $10^{-5}$.
+\begin{figure}
+	\centering
+	\caption{The distance of the roots to the unit circle.}
+	\includegraphics[scale=.8]{tex/figures/e3p_known_sols2}
+	\fautor
+	\label{fig:e3p_known_sols2}
+\end{figure}
+For the last experiment we considered $100$ instances for each $K$ with three points $(K\cos(t_j), \frac{K\sin{(t_j)}}{2})$, $j=1\dots3$, generated randomly by sampling $t_j$ according to a uniform distribution in $[0, 2\pi]$.
+The average and the maximum error are plotted in \autoref{fig:e3p_error}, and analyzing it, it is fair to say that \autoref{algoritmo:e3p} is numerically stable for this example, and its error, in average, is expected to be small even if the instance's numerical values are big.
+\begin{figure}
 	\centering
@@
 \end{figure}
-
-This experiment served as a basis for us to define the precision constant as $10^{-7}$ for the implementation of \autoref{algoritmo:e3p}. 
-This constant is used in floating point comparisons in situations like checking if a root of $h$ is in the unit circle, comparing if two roots of $\xi$ represent the same solution, and checking if the three points are in the border of an ellipse considered as a solution.

### 2020-02-06 defesa/tex/chapter/mcer.tex
wip

@@
 
-In the next section we present some results which ultimately lead up to the construction of a CLS that contains an optimal solution for MCER.
+In the next section we present some results which ultimately lead up to the construction of a CLS for each facility that contains an optimal solution for MCER.
 
@@
 
+In \autoref{fig:AB120} a solution return by \autoref{algoritmo:mcer} for the instance AB120 taken from \citeonline{andreta} is displayed.
+The exact method developed by \citeonline{andreta}, for this instance, could not obtain an optimal solution within the established time limit, however, comparing with the solution obtained by our algorithm, their heuristic method does find an optimal solution.
+In the next chapter, we give more details about the solutions found by our algorithm, along with the proposal of some new instances for MCER and MCER-$k$.
+
+\begin{figure}[H]
+	\centering
+	\caption{An optimal solution for the instance AB120.}
+	\includegraphics[scale=.5]{tex/figures/AB120}
+	\fautor
+	\label{fig:AB120}
+\end{figure}
+
 \subsection{Adding facility cost}
@@
 In our implementation we use the same approach used in \citeonline{andreta}.
-When constructing the CLS for the $j$-th ellipse, a tree-like data struct is utilized to verify if a solution $(q, \theta)$ covers a subset of another solution or not.
+When constructing the CLS for the $j$-th ellipse, a tree-like data structure is utilized to verify if a solution $(q, \theta)$ covers a subset of another solution or not.
 
@@
 
-In the next section we present the results of numerical experiments for MCER and MCER-$k$ and compare them with the results published in \citeonline{andreta}.
+In the next chapter, we present the results of numerical experiments for MCER and MCER-$k$ and compare them with the results published in \citeonline{andreta}.

### 2020-02-07 defesa/tex/chapter/e3p.tex
wip

@@
-The problem of finding every center and angle of rotation of a fixed shape ellipse, which makes it have three points on its border, is presented in this section.
-
-Even though its simple statement -- it is short and uses only basic mathematical concepts -- we were not able to find any work on it, or even on related problems.
+In this chapter, we introduce the problem of determining every center and angle of rotation of an ellipse with fixed shape parameters, such that it contains three given points.
+Even though its simple statement -- it is short and uses only basic mathematical concepts -- we were not able to find any work on it or even on related problems.
 As a result, starting from scratch, we ended up trying a handful of approaches, with most of them failing on the way.
@@
 
-We call the problem introduced in this section \sigla{E3P}{Ellipse by Three Points}.
-An instance of it is given by three points $u, v, w \in \R^2$ and the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, with $a > b$.
+We call the problem of finding a center and an angle of rotation for an ellipse given its shape parameters and three points that have to be on its border \sigla{E3P}{Ellipse by Three Points}.
+An instance of it is given by three points $u, v, w \in \R^2$ and the ellipse's shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
 

### 2020-02-07 defesa/tex/chapter/mcer.tex
wip

@@
 and $m$ ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
-Additionally, to make the text more clear, we define a set of $m$ ellipses as $\E = \{E_1, \dots, E_m\}$, with $E_j\colon \R^2\times\R \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
-Lastly, an instance of MCER is defined as a tuple $(\Pp, \Ww, \Rr)$.
+Additionally, to make the text more clear, we define a set of $m$ functions that represent the coverage regions of each ellipse as $\E = \{E_1, \dots, E_m\}$, with $E_j\colon \R^2\times\R \mapsto \R^2$ being a function that takes the center and angle of rotation where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
+Lastly, an instance of MCER is defined as the tuple $(\Pp, \Ww, \Rr)$.
 
-Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ to be the centers of each ellipse, $\Theta:=(\theta_1, \dots, \theta_m) \in [0, \pi)^m$ to be the angle of rotation of each ellipse and $E_i(q_i, \theta_i)$ to be the coverage region of ellipse $E_i$ with its center at point $q_i$ rotated by angle $\theta_i$, which is given by \autoref{eq:rotated_ellipse_co}.
-Therefore MCER is defined as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the weight of points covered by the $m$ ellipses, which is given by
-
+Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ as the centers of each ellipse, and $\Theta:=(\theta_1, \dots, \theta_m) \in [0, \pi)^m$ as the angles of rotation of each ellipse.
+Then, we define MCER as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the weight of the points covered by the $m$ ellipses given by
 \begin{equation}\label{eq:optMCEn}
@@
 We say that two solutions are equivalent if the set of points covered by them is the same.
-In other words, two solutions of MCER $(Q, \Theta)$ and $(Q', \Theta')$ are said to be equivalent if, and only if
+That is, two solutions of MCER $(Q, \Theta)$ and $(Q', \Theta')$ are said to be equivalent if, and only if
 $$\bigcup_{j=1}^m\Pp \cap E_j(q_j', \theta_j') = \bigcup_{j=1}^m\Pp \cap E_j(q_j, \theta_j).$$
 
-In the next section we present some results which ultimately lead up to the construction of a CLS for each facility that contains an optimal solution for MCER.
+In the next section we present some results which ultimately lead up to the construction of a finite set that contains at least one optimal solution for MCER.
 
-\section{Constructing a CLS}
+\section{An optimal and finite set of solutions}
 
-The goal of this section is to construct a finite set of solutions, also referred to as CLS, for MCER that contains at least one optimal solution.
-The main idea for doing that is to take advantage of \autoref{lema:e3p} and use the fact that there are at most six solutions for any instance of E3P.
-This set of solutions is then used in the next section on the development of a $\bigO(n^{3m})$ runtime algorithm for MCER.
+In this section, we construct a finite list of centers and angles of rotation, also referred to as a CLS, for each ellipse and show that at least one optimal solution is in the set of solutions created from those lists.
+The results presented in this section are strongly based on \autoref{chapter:e3p}, more specifically on \autoref{lema:e3p}, which states that there exists at most six solutions for any instance of E3P.
 
-To begin with, a proposition is introduced which says that given an optimal solution of MCER, it is possible to find another optimal solution with two points on the border of every ellipse that is already covering at least two points.
+We start by introducing a lemma, which says that given an optimal solution of MCER, it is always possible to find an equivalent one, such that every ellipse covering more than one point has two of them on its border.
 
-\begin{proposicao}\label{lema:mce_2b}
+\begin{lema}\label{lema:mce_2b}
 	Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. 
@@
 	an equivalent solution $(Q', \Theta^*)$ exists, such that $|\Pp \cap \partial E_j(q_j', \theta_j^*)|\ge 2$.
-\end{proposicao}
+\end{lema}
 
@@
 
-What \autoref{lema:mce_2b} is saying is that any optimal solution for MCER can be transformed into an equivalent optimal solution where every ellipse that covers more than one point has two points on their border.
-Also, this equivalent optimal solution can be always achieved by just translating the ellipses.
-An example of that can be seen in \autoref{fig:ellipse-2-points}.
-
-Next, a notation is defined for the set of equivalent solutions of an optimal solution that has at least two points on the border of every ellipse. This helps us make the text less cluttered.
-
-\begin{definicao}
-	Let $(Q^*, \Theta^*)$ be an optimal solution for an instance $(\Pp, \Ww, \Rr)$ of MCER.
-We define $\Pi(Q^*, \Theta^*)$ as the set of every equivalent solution of $(Q^*, \Theta^*)$, such that for any $(Q, \Theta)\in\Pi(Q^*, \Theta^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
-\end{definicao}
-
-A lot of the ideas developed in this chapter are based on fixing two points on the border of an ellipse.
-Based on that, \autoref{def:feasible_angle} introduces a new notation for angles that, given two points and an ellipse, it is possible to find a center where the ellipse rotated by that angle is placed, such that the two given points lie on its border.
+What \autoref{lema:mce_2b} is saying is that transforming any optimal solution of MCER into an equivalent optimal solution where every ellipse that covers more than one point has two points on its border is possible (an example can be seen in \autoref{fig:ellipse-2-points}).
+\autoref{lema:mce_2b} also says that this equivalent optimal solution can always be achieved by just translating the ellipses; that is, no change in the angle of rotation is required.
 
@@
 
+Next, a new notation is introduced for the set of equivalent solutions of an optimal one that has at least two points on the border of every ellipse.
+
+\begin{definicao}
+	Let $(Q^*, \Theta^*)$ be an optimal solution for an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We define $\Pi(Q^*, \Theta^*)$ as the set of every equivalent solution of $(Q^*, \Theta^*)$, such that for any $(Q, \Theta)\in\Pi(Q^*, \Theta^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
+\end{definicao}
+
+Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains the two points on its border.
+
 \begin{definicao}\label{def:feasible_angle}
@@
 	\begin{equation}
-	\Phi_j(u, v) := \{\theta \in [0, \pi] : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
+	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
 	\end{equation}
@@
 In \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
-The example with a solid contour shows two ellipses rotated by $\pi/4$ with the two given points on its border, making $\pi/4$ a $(E, u, v)$-feasible angle.
-The other example, with a dashed contour, presents a case where an ellipse rotated by $\pi/2$ is not able to have the two points on its border, no matter where it is placed; because of that, $\pi/2$ is said to be a not $(E, u, v)$-feasible angle.
+The example with a solid border shows two given points on the border of two ellipses rotated by $\pi/4$, making $\pi/4$ a $(E, u, v)$-feasible angle.
+The other example, with a dashed border, presents a case where an ellipse rotated by $\pi/2$ is not able to have the two points on its border, no matter where it is placed; because of that, $\pi/2$ is said to be a non $(E, u, v)$-feasible angle.
 
@@
 
-Following that, we present a lemma that, given an optimal solution, it says that for any ellipse that covers more than two points, an equivalent solution exists with at least one of the two properties:
+Following that, we introduce a lemma that is responsible for connecting the developments of this chapter with the results of \autoref{chapter:e3p}.
+This lemma makes it possible to describe a type of solution which, for sure, is part of the equivalence class of any optimal solution.
+It says that, for any ellipse that covers more than two points in a given optimal solution, an equivalent solution exists with at least one of the two properties:
 \begin{itemize}
@@
 
-If, for every equivalent solution $(\hat{Q}, \hat{\theta})$, $|\Pp\cap \partial E_j(\hat{q}_j, \hat{\theta}'_j)| < 3$, then for all $\theta\in\Phi_j(u,v)$, there exists $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
+If, for all $(\hat{Q}, \hat{\theta})$ equivalent solution of $(Q^*, \Theta^*)$, $|\Pp\cap \partial E_j(\hat{q}_j, \hat{\theta}_j)| < 3$, then for all $\theta\in\Phi_j(u,v)$, there exists $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
 
@@
 
-	To use those results here, we need to consider the ellipse to be fixed at the origin and axis-parallel, and instead, rotate the points in $\Pp$.
+	To use those results here, we need to consider the ellipse to be fixed at the origin and axis-parallel, and consider the problem of rotating and translating the points in $\Pp$ instead.
 
@@
 
-	With this result in hands, we can use a continuity argument to complete our proof as follows.
+	With this result in hand, we can use a continuity argument to complete our proof as follows.
 	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
-	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.
+Notice that, in general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, imposing $\delta(\theta_j') = q_j'$ makes $\delta$ be a well-defined function.
 This is shown in \autoref{fig:lema-3-points} where $\delta$ is plotted for the whole interval $\Phi_j(u,v)$.
 
-	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^3 \mapsto \R_{\ge0}$ to be a function that takes a center point $q$ and an angle of rotation $\theta$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}.
+	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}.
+Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$.
 
-	For all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j^*) < 1$.
-We then define a function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
-As $g_w$ is a composition of continuous functions, it is also continuous.
+	For all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j^*) < 0$ as they are covered by the $j$-th ellipse.
+	Then, to evaluate $f_w$ for every center and feasible angle that maintains $u$ and $v$ on $E_j$'s border, we introduce a new function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$, which is defined as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
+	As $f_w$ and $\delta$ are continuous functions, $g_w$ is also continuous.
 
 	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>1$.
-Then, by continuity, another angle $\hat{\theta} \in(\theta_j^*, \theta)$ must exist, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
-The same can be said about a point that enters the coverage of $E_j(\delta(\theta), \theta)$.
+Then, by continuity, another angle $\bar{\theta} \in \Phi_j(u,v)$ must exist, such that $g_w(\bar{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
+The same can be said about the case where there exists an angle $\theta \in \Phi_j(u,v)$, such that a point $w \in \Pp \setminus E_j(q_j^*, \theta_j^*)$ enters the coverage of $E_j(\delta(\theta), \theta)$.
 \end{proof}
@@
 
-In \autoref{fig:lema-3-points} a visualization of \autoref{lema:3pnts} is presented.
-An initial optimal solution is given by the dashed-border ellipse, and its center, represented by a star point.
+In \autoref{fig:lema-3-points}, a visualization of \autoref{lema:3pnts} is presented.
+An initial optimal solution is given by the dashed-border ellipse and its center, represented by a star point.
 From it, the continuous function $\delta$ is defined by moving the ellipse through the rotation angles in $\Phi_j(u,v)$ while maintaining $u, v$ on its border.

### 2020-02-08 defesa/tex/chapter/e3p.tex
wip

@@
 In this chapter, we introduce the problem of determining every center and angle of rotation of an ellipse with fixed shape parameters, such that it contains three given points.
-Even though its simple statement -- it is short and uses only basic mathematical concepts -- we were not able to find any work on it or even on related problems.
+This problem comes up in the development of an algorithm in \autoref{chapter:mcer}.
+The reason to have a whole chapter devoted to it is that we could not find any work that studies this problem or even related ones.
 As a result, starting from scratch, we ended up trying a handful of approaches, with most of them failing on the way. 
-We try to give a review of some of those, going through the issues with the failing ones.
-In the end, we propose an algorithm that takes around $6^3$ operations to compute every solution for any instance of the problem and run some experiments to analyze its efficiency in terms of numerical precision and CPU time.
+We thought it would be a useful source for future works if we gave a review of some of those, going through the issues with the failing ones, and discussing the qualities of the successful ones. 
+In the end, we propose an algorithm for the problem that involves determining the eigenvalues of a $6\times6$ matrix.
+We also analyze its efficiency in terms of numerical accuracy and display solutions that it found.
+
+%Even though its simple statement -- it is short and uses only basic mathematical concepts -- we were not able to find any work on it or even on related problems.
 
@@
 
-Initially, E3P is a problem with three unknown variables: the two coordinates of the center point, $q_x$ and $q_y$, and the angle of rotation $\theta$.
+Initially, E3P is a problem with three unknown variables: the two coordinates of the ellipse's center point, $q_x$ and $q_y$, and the angle of rotation $\theta$.
 In this section, we transform E3P into the problem of finding the roots of a univariate function using a known circumcircle problem.
@@
 
-To make the problem simpler, let us translate the system, so the point $u$ is at the origin.
-That is, assume that the three points given by the E3P instance are $(0, 0); v; w$.
-After that, we assume that the ellipse is axis-parallel, and the points are the ones rotating.
-When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to squeeze the x-axis by $\frac{b}{a}$.
-This compression on the $x$-axis makes the ellipse become a circle of radius $b$.
-As only invertible transformations are used, given the final state where the three points are on the border of a circle of radius $b$, reversing the two transformations (stretching by $\frac{a}{b}$, rotating by $-\theta$) provides a solution of E3P.
-The whole process can be seen in \autoref{fig:circumscribed-circle} where a solution of the E3P is transformed firstly into an axis-parallel ellipse, and then into a circle of radius $b$.
-We introduce a function $\varphi\colon \R^2 \to \R^2$ that takes any point and apply these transformations to it as
+To make the problem simpler, let us assume that point $u$ is at the origin. If it is not, a simple translation by $-u$ applied to the three points can be made to put $u$ at the origin.
+Assume as well that $(q, \theta)$ is a solution of E3P, which means that an ellipse rotated by $\theta$, centered at $q$ has $u$, $v$, and $w$ on its border (see \autoref{fig:circumscribed-circle} for an example).
+From a solution of E3P, applying a rotation of $-\theta$ to the coordinate system, an axis-parallel ellipse can be obtained.
+After that, squeezing the $x$-axis by $\frac{b}{a}$ can be utilized to transform the ellipse into a circle of radius $b$.
+An example of this whole process is shown in \autoref{fig:circumscribed-circle}.
+These transformations can be written as a function $\varphi\colon \R^2 \to \R^2$ defined as
+
 \begin{equation}\label{eq:trpnts}
@@
 \end{equation}
-Also, to make the notation more clear, we denote by $\Lambda(\theta)$ the triangle formed by the points $(0, 0); \varphi(v, \theta); \varphi(w, \theta)$, as long as they are not collinear.
-This being said, we go further to introduce a circumcircle problem which is equivalent to E3P.
+Notice that the transformations represented by $\varphi$ are invertible.
+This means that given a final state, where after applying $\varphi$, the three points are on the border of a radius-$b$ circle, a solution of E3P can be obtained by using the well-defined inverse function $\varphi^{-1}$.
+Additionally, to make the notation more clear, we denote by $\Lambda(\theta)$ the triangle formed by the points $\varphi(u,\theta); \varphi(v, \theta); \varphi(w, \theta)$, as long as they are not collinear.
+This being said, we can go further and introduce a problem equivalent to E3P which is based on determining angles $\theta$ that make the triangle $\Lambda(\theta)$ be circumscribed in a circle of radius $b$.
 
@@
 	\centering
-	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics{tex/figures/scripts/circumscribed-circle}
+	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
+	\includegraphics[scale=.43]{tex/figures/circumscribed-circle}
 	\fautor
@@
 The term circumradius, in this work, is used to describe the radius of a triangle's circumscribed circle, which is a circle that has the triangle's vertices on its border.
-Given an instance of E3P, we define the circumradius problem as the problem of determining an angle of rotation $\theta\in[0, \pi)$, such that the circumradius of $\Lambda(\theta)$ is equal to $b$.
+Given an instance of E3P, we define the circumradius problem as the problem of determining an angle $\theta\in[0, \pi)$, such that the circumradius of $\Lambda(\theta)$ is equal to $b$.
 
@@
 \end{equation}
-with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle see \citeonline[p.~189]{johnson1960}
-). It should be pointed out that this transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
+with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle see \citeonline[p.~189]{johnson1960}).
+It should be pointed out that this transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
 
@@
  \end{align}
-  It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared lengths of the triangle formed by the points $(0, 0), \varphi(v, \theta), \varphi(w, \theta)$.
-This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\norm{\varphi(v, \theta)}^2$ is $6$ which consequently is the degree of $\xi$.
+  It is also possible to see that the term which has $\xi$'s highest degree is the multiplication of the three squared lengths of $\Lambda(\theta)$'s sides.
+This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\norm{\varphi(v, \theta)}^2$ is $6$, which consequently is $\xi$'s degree.
 Going from $12$ solutions to $6$ is done by using the symmetry of ellipses.
@@
 
-Setting the first point to be the origin, we get $F=0$, using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$.
+Setting the first point to be the origin, we get $F=0$.
+Using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$.
 As any multiple of \autoref{eq:gen_ellipse} represents the same conic, we can set $B$ to be equal to $1$.
@@
 
-Another idea which has been explored was working with the ratio $\frac{a^2}{b^2}$ which becomes an expression that allows $A$ to be written as a function of $C$.
-This function appeared, at first we thought, to be monotonic, we tried to develop a method based on that, however, cases where the function does not behave as nicely were found.
+Another idea which has been explored was working with the ratio $\frac{a^2}{b^2}$, which becomes an expression that allows $A$ to be written as a function of $C$.
+At first, this function appeared to be monotonic, so we tried to develop a method based on that.
+However, cases where the function does not behave as nicely were found.
 It is likely that developing a method to approximate solutions working with this function is possible, but we decided not to continue on this track.
@@
 One of the most useful techniques when dealing with complicated functions is approximation.
-They appear in various methods whenever a derivative or integral needs to be calculated or for example, in our case, when the roots of a function need to be determined.
+They appear in various methods whenever a derivative or integral needs to be calculated or, for example, like in our case, when the roots of a function need to be determined.
 In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}.
-For this problem, the approximation of $\xi$ on the interval $[0, \pi)$ is considered.
-The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials whose roots can be found through determining the eigenvalues of a $n\times n$ matrix.
+For this problem, we consider the approximation of $\xi$ on the interval $[0, \pi)$ by a function in the family of $n$-degree Chebyshev polynomials.
 
@@
 One of the greatest qualities of Chebyshev polynomials is its numerical stability.
-\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{A polynomial is in the power form or the monomial form if it can be written as $\sum_{j=0}^{n}a_jx^j$.} has a condition number that grows exponentially with $n$.
-On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries}, has a linear condition number bounded by $\sqrt{2}n$.
+\citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form has a condition number that grows exponentially with $n$.
+On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries} has a linear condition number bounded by $\sqrt{2}n$.
 
@@
 Instead of choosing $n+1$ arbitrary points, the $n+1$ roots of $T_{n+1}$, which are also known as Chebyshev Nodes, are chosen as the interpolation points.
-The $n+1$ Chebyshev nodes are given by
+The $n+1$ Chebyshev Nodes are given by
 \begin{equation}
@@
 For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
-An alternative method can be found in \citeonline{boyd:2013} where the Chebyshev interpolation is calculated directly as a truncated Chebyshev series, as in \autoref{eq:chebseries}, in $\bigO(n^2)$.
+An alternative method can be found in \citeonline{boyd:2013}, where the Chebyshev interpolation is calculated directly as a truncated Chebyshev series, as in \autoref{eq:chebseries}, in $\bigO(n^2)$.
 Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial.
@@
 Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials, which have great numerical stability.
-Also, Chebyshev-Frobenius matrices have the same property as companion matrices which allows their eigenvalues to be found by a QR algorithm.
+Also, Chebyshev-Frobenius matrices have the same property as companion matrices, which allows their eigenvalues to be found by a QR algorithm.
 Summing the two steps, a $\bigO(n^3)$ algorithm can be achieved, with $n$ being the degree of the interpolation.
 
-The last question that needs to be addressed is how close the roots of the Chebyshev interpolant $f_n$ are to the roots of $\xi$?
+The last question that needs to be addressed is: how close the are roots of the Chebyshev interpolant $f_n$ to the roots of $\xi$?
 
@@
 To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}.
-There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is considered to be a good estimate for the error
+There is no guarantee that this method will choose $n$ such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$.
+Nonetheless, in practice, it is considered to be a good estimate for the error
 
@@
 
-\subsection{Numerical Experiments}
+\subsection{Testing different interpolant degrees}
 
@@
 	\caption{The interpolation error measured on roots that were found.}
-	\includegraphics{tex/figures/interpolant_error}
+	\includegraphics[scale=.84]{tex/figures/interpolant_error}
 	\fautor
@@
 
-At first,  the root-finding algorithm described on \autoref{chapter:definitions} seemed to work fine and return every solution of E3P, however, we later found out that for some instances, priorly known roots were not being found.
+At first,  the root-finding algorithm described on \autoref{chapter:definitions} seemed to work fine and return every solution of E3P.
+However, we later found out that for some instances, priorly known roots were not being found.
 The cause was not for sure identified, but a good guess would be that for angles which are greater than $\frac{\pi}{4}$, $x$ starts growing too rapidly which could lead to numerical instability.
@@
 which relate complex numbers with trigonometric functions, to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
-This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner} where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
+This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner}, where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
 
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, the function $g(e^{i\theta})$ and the $\xi$ are equivalent since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
+As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, function $g(e^{i\theta})$ and $\xi$ are equivalent, since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
 
@@
 As the angle of one of the roots will not be between $[0, \pi)$ we can ignore one of them.
-Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the identity
+Note that the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the identity
 \begin{equation*}
@@
 \begin{teorema}\label{th:e3p}
-	The \autoref{algoritmo:e3p} computes every solution for an instance of E3P in $\bigO(1)$ operations.
+	\autoref{algoritmo:e3p} computes every solution for an instance of E3P in $\bigO(1)$ operations.
 \end{teorema}

### 2020-02-10 defesa/tex/chapter/e3p.tex
wip

@@
 	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
-	\includegraphics[scale=.43]{tex/figures/circumscribed-circle}
+	\includegraphics[scale=.5]{tex/figures/circumscribed-circle}
 	\fautor
@@
 Nonetheless, in practice, it is considered to be a good estimate for the error
-
 \begin{equation}
@@
 which measures how far the interpolation is at the point it worst approximates. 
-
+\clearpage
 \subsection{Testing different interpolant degrees}
 
-In this section, we run some experiments to verify how big the interpolation degree must be for good precision to be achieved. 
-The interpolation was run for several degrees, for every triplet of points in an instance from \citeonline{canbolat}.
-We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found.
+In this section, we describe the results of an experiment we made to verify the accuracy of solutions found by the Chebyshev Interpolation method for different interpolation degrees. 
+The main reason for doing this experiment was to obtain a practical lower-bound for the interpolation degree, which can be used later to decide whether to use this method or not.
+We also investigate if dividing the interpolation interval into $K$ sub-intervals, which is a suggestion given in \citeonline{boyd:2013}, yields an improvement in the accuracy of solutions.
 
-The results are shown in \autoref{fig:interpolant_error}, where the worst error found among every root is plotted against the interpolant degree.
-To improve accuracy while keeping the interpolation degree low, we took a suggestion from \citeonline{boyd:2013}, and divided  $[0, \pi)$ into $K$ sub-intervals.
-That way, $K$ interpolations are used to obtain every root in the whole interval.
-It can be seen in \autoref{fig:interpolant_error} that this strategy helps a lot in improving the accuracy even when degrees around $8$ are used.
+Let $\delta : \R^2 \to \R_{>0}$ be a function defined as the left-hand-side of \autoref{eq:rotated_ellipse}, then, for an instance of E3P with three points $u, v, w$, we define the error of a solution as $$\max\{|\delta(u)|, |\delta(v)|, |\delta(w)| \}.$$
+We created instances of E3P taking every triplet of points, and every ellipse from an MCE's instance named CM3 proposed in \citeonline{canbolat}.
+We also tried dividing the interval $[0, \pi]$ into a different number of sub-intervals taking $K \in\{1, 2, 4, 8\}$.
 
@@
 	\centering
-	\caption{The interpolation error measured on roots that were found.}
-	\includegraphics[scale=.84]{tex/figures/interpolant_error}
+	\caption{The maximum interpolation error.}
+	\includegraphics[scale=.9]{tex/figures/error_roots}
 	\fautor
@@
 \end{figure}
+
+In \autoref{fig:interpolant_error}, for each $K$, the maximum error observed among every instance of E3P for each interpolation degree is shown.
+It may be stated that adopting the strategy of dividing the interpolation interval into $K$ sub-intervals provides a significant improvement in accuracy.
+
+Also, as expected, in \autoref{fig:last-coeff}, using the same instances, we were able to observe that the maximum absolute value of the last coefficient among every instance has the same behavior as its corresponding error in \autoref{fig:interpolant_error}.
+
+\begin{figure}
+	\centering
+	\caption{The maximum absolute value of the last coefficient interpolation.}
+	\includegraphics[scale=.9]{tex/figures/last_coeff}
+	\fautor
+	\label{fig:last-coeff}
+\end{figure}
+
+Assuming that $K=4$, we can say that for a small error to be achieved, we need to take an interpolation degree of at least $10$, increasing it based on the last coefficient rule.
+A suggestion in \citeonline{boyd:2013} says that if the last coefficient is not small, the interpolation degree must be doubled.
+This is only a suggestion of how to approach the problem of choosing a good interpolation degree. 
+This procedure could still fail as a small last coefficient does not necessarily imply a small error everywhere in the interpolation interval.
 
@@
 A complex polynomial can be obtained from $\xi$ by using an idea published in \citeonline{boyd:2006}. There, the author uses the identities
+
 \begin{align}\label{eq:complex_trig}

### 2020-02-10 defesa/tex/chapter/mcer.tex
wip

@@
 	\end{equation}
+	We also refer to $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
+Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$.
 \end{definicao}
@@
 \begin{lema}\label{lema:3pnts}
-Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.
 
@@
 
-	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}.
-Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$.
+	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}.
+Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$ as they are covered by the $j$-th ellipse.
 
-	For all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j^*) < 0$ as they are covered by the $j$-th ellipse.
 	Then, to evaluate $f_w$ for every center and feasible angle that maintains $u$ and $v$ on $E_j$'s border, we introduce a new function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$, which is defined as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
-	As $f_w$ and $\delta$ are continuous functions, $g_w$ is also continuous.
+	As $f_w$ and $\delta$ are both continuous functions, $g_w$ is also continuous.
 
-	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>1$.
+	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>0$.
 Then, by continuity, another angle $\bar{\theta} \in \Phi_j(u,v)$ must exist, such that $g_w(\bar{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
@@
 What \autoref{lema:3pnts} is saying is that, for every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
-Because of that, it will be shown that we can construct a CLS which is finite and also contains an optimal solution.
+Because of that, it will be shown that we can construct a CLS for each ellipse which is finite and also contains an optimal solution.
 
@@
 
-Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
-We will define a set $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$.
-This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
-The whole set $\Omega(\Pp, \Ww, \Rr)$ is constructed from a set of solutions for every ellipse.
-Let $j\in\{1, \dots, m\}$, we denote by $S_j$ the CLS for the $j$-th ellipse; its construction is broken into three separated cases denoted by $S_j^{(1)}$, $S_j^{(2)}$, and $S_j^{(3)}$.
-Next, we define them precisely.
+Let $(Q^*, \Theta^*)$ be any optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We will define a set of solutions $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$.
+This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ for sure contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
+Before that, we introduce a definition for the CLS of every ellipse, which is then used to construct the set of solutions $\Omega(\Pp, \Ww, \Rr)$.
+
+\begin{definicao}\label{def:Sj}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER.
+Then, for all $j\in\{1, \dots, m\}$, we define the \sigla{CLS}{Candidate Locations Set} of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
+	\begin{align}
+		S_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
+		S_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \tilde{\Phi}_j(u,v))\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \tilde{\Phi}_j(u,v))\}\\
+		S_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v, w\} \subset \partial E_j(q, \theta)\}.
+	\end{align}
+\end{definicao}
+
+This definition breaks the construction of the CLS $S_j$ into three separated cases.
+The first one, $S_j^{(1)}$, represents solutions where the $j$-th ellipse covers only one point.
+The second one, $S_j^{(2)}$, takes into account solutions where the $j$-th ellipse covers at least two points, and no equivalent solution with three points on the ellipse's border exists.
+The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse's border.
+Following this, we move forward and introduce the main result of this section.
+
+\begin{theorem}\label{th:mcer}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined as 
+	\begin{equation*}\label{eq:omega}
+	\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
+	\end{equation*}
+Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
+\end{theorem}
+\begin{proof}
+	The first thing to notice is that $\Omega(\Pp, \Ww, \Rr)$ is defined as the combination of every possible solution from each CLS.
+To prove that it contains an optimal solution $(Q^*, \Theta^*)$, we only need to prove that for all $j\in\{1, \dots, m\}$, there exists $(q_j, \theta_j)\in S_j$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) \subset \Pp \cap E_j(q_j, \theta_j)$.
+That is, we only need to show that the CLS of every ellipse contains a center and angle of rotation that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
+To do that, we use \autoref{lema:3pnts} and break the possible optimal solutions into three cases.
+
+	 In the first case, we consider solutions where the $j$-th ellipse covers less than one point, that is, $|\Pp \cap E_j(q_j^*, \theta_j^*)|\le1$.
+It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega(\Pp, \Ww, \Rr)$ every solution that has an ellipse centered at a point from $\Pp$.
+
+	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on its border.
+This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse's border, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
+	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$.
+
+	The third case is the complement of the other two cases, that is, the $j$-eh ellipse covers at least three points, and there is an equivalent solution with three points on its border. 
+	As for every triplet of points, $S_j^{(3)}$ contains every possible center and angle of rotation that puts the three points on the ellipse's border, for sure the equivalent solution is in $S_j^{(3)}$.
+
+\end{proof}
 
@@
 
-This is the case where $|E_j(q_j^*, \theta_j^*)|=1$, that is, the $j$-th ellipse only covers one point. 
-This case is not treated by any of the previous results presented in this chapter.
-Nevertheless, taking this possibility into account can be done by including solutions in $S_j$ that are guaranteed to cover at least one point.
-This is represented by
+This is the case where $|\Pp \cap E_j(q_j^*, \theta_j^*)|=1$, that is, the $j$-th ellipse only covers one point in the optimal solution $(Q^*, \Theta^*)$. 
+This case is not treated by any of the previous results presented in this chapter. Nevertheless, taking this into account can be done by
+considering, for all $u\in\Pp$, the possibility of having the $j$-th ellipse centered at $u$ with an angle of rotation $0$.
+We do that by defining 
 \begin{equation}
@@
 \subsection{Second case}
-
-The second and third cases are addressed by \autoref{lema:3pnts}. 
-Consider the second case to be the one where the $j$-ellipse covers more than one point and there is no equivalent solution with three points on the its border. 
-By \autoref{lema:3pnts}, $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v$ on the ellipse's border, and is rotated by some angle in $\Phi_j(u,v)$. 
-As only one angle is needed, we define $\theta_{uv}$ as the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
-Having said that, we refer to $S_j^{(2)}$ the set of possible solutions that takes this case into account; we define it as
+This is the case where $|\Pp \cap E_j(q_j^*, \theta_j^*)| \ge 2$ and there is no equivalent solution that has the $j$-th ellipse with three points on its border.
+This case is addressed by \autoref{lema:3pnts}, which says that $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse's border, and is rotated by some angle $\theta \in \Phi_j(u,v)$.
+As only one angle is needed, we define $\theta_{uv}$ as the one that makes the major-axis of the ellipse be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
+Having said that, we refer to $S_j^{(2)}$ as the set of possible solutions that takes this case into account; we define it as
 \begin{equation}
@@
 
-Finally, we define the CLS for the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$, and the set of possible solutions of an instance of MCER as
-\begin{equation}\label{eq:omega}
-\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
-\end{equation}
+define the CLS for the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$, and the set of possible solutions of an instance of MCER as
+%\begin{equation}\label{eq:omega}
+%\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
+%\end{equation}
 
-\begin{theorem}\label{th:mcer}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}.
+%\begin{theorem}\label{th:mcer}
+%	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}.
 Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
-\end{theorem}
+%\end{theorem}
 

### 2020-02-11 defesa/tex/chapter/e3p.tex
wip

@@
 
-\begin{align}\label{eq:complex_trig}
+\begin{align}\label{eq:complex_trig_cos}
 	\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
+	\label{eq:complex_trig_sin}
 	\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i},
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-As the equalities on \autoref{eq:complex_trig} are valid for any $\theta \in \R$, function $g(e^{i\theta})$ and $\xi$ are equivalent, since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
+As the equalities on \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin} are valid for any $\theta \in \R$, function $g(e^{i\theta})$ and $\xi$ are equivalent, since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
 

### 2020-02-11 defesa/tex/chapter/mcer.tex
wip

@@
 	\end{equation}
-	We also refer to $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
-Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$.
+	We also define $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
+Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
 \end{definicao}
@@
 It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega(\Pp, \Ww, \Rr)$ every solution that has an ellipse centered at a point from $\Pp$.
+From that, we can also conclude that $|S_j^{(1)}| = n$.
 
@@
 	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
+	Moreover, in \autoref{section:ellipses_intersection}, we discuss the problem of determining the intersections between two ellipses.
+This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on the border of an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
+In \autoref{section:ellipses_intersection}, it is shown that this problem has at most two solutions.
+Therefore, we have that $|S_j^{(2)}| = 2\binom{n}{2}$.
 
-	The third case is the complement of the other two cases, that is, the $j$-eh ellipse covers at least three points, and there is an equivalent solution with three points on its border. 
-	As for every triplet of points, $S_j^{(3)}$ contains every possible center and angle of rotation that puts the three points on the ellipse's border, for sure the equivalent solution is in $S_j^{(3)}$.
+	For the last case, we are left with solutions where the $j$-th ellipse covers more than two points, and there exists an equivalent solution with three points on its border. 
+	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the border of the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega(\Pp, \Ww, \Rr)$.
+Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse have three given points on its border is at most six.
+Therefore, we have that $|S_j^{(3)}| = 6\binom{n}{3}$.
 
-\end{proof}
-
-\subsection{First case}
-
-This is the case where $|\Pp \cap E_j(q_j^*, \theta_j^*)|=1$, that is, the $j$-th ellipse only covers one point in the optimal solution $(Q^*, \Theta^*)$. 
-This case is not treated by any of the previous results presented in this chapter. Nevertheless, taking this into account can be done by
-considering, for all $u\in\Pp$, the possibility of having the $j$-th ellipse centered at $u$ with an angle of rotation $0$.
-We do that by defining 
-\begin{equation}
-	S_j^{(1)} = \bigcup_{u \in \Pp} \{(u, 0)\}.
-\end{equation}
-
-\subsection{Second case}
-This is the case where $|\Pp \cap E_j(q_j^*, \theta_j^*)| \ge 2$ and there is no equivalent solution that has the $j$-th ellipse with three points on its border.
-This case is addressed by \autoref{lema:3pnts}, which says that $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse's border, and is rotated by some angle $\theta \in \Phi_j(u,v)$.
-As only one angle is needed, we define $\theta_{uv}$ as the one that makes the major-axis of the ellipse be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
-Having said that, we refer to $S_j^{(2)}$ as the set of possible solutions that takes this case into account; we define it as
-\begin{equation}
-S_j^{(2)} = \bigcup_{\{u, v\} \subset \Pp} \{(q, \theta_{uv})\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \theta_{uv})\}.\\
-\end{equation}
-For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters.
-This problem is discussed with great detail in \autoref{section:ellipses_intersection}.
-
-\subsection{Third case}
-
-The only case left is the one where there is an equivalent solution with three points on the $j$-th ellipse's border. We call this set of possible solutions $S_j^{(3)}$, and define it as
-\begin{equation}
-	S_j^{(3)} = \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v, w\} \subset \partial E_j(q, \theta)\}.
-\end{equation}
-Determining the set $S_j^{(3)}$ can be done using the results from \autoref{chapter:e3p} for every triplet of points.
-
-define the CLS for the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$, and the set of possible solutions of an instance of MCER as
-%\begin{equation}\label{eq:omega}
-%\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
-%\end{equation}
-
-%\begin{theorem}\label{th:mcer}
-%	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}.
-Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
-%\end{theorem}
-
-\begin{proof}
-	For every $j \in \{1, \dots, m\}$, by \autoref{lema:3pnts}, any optimal solution that covers more than one point can be transformed into one that is in $S_j^{(2)}$ or in $S_j^{(3)}$.
-	If an optimal solution covers only one point, it can be transformed into another one that is in $S_j^{(1)}$.
-
-	From \autoref{section:ellipses_intersection}, we can conclude that $|S_j^{(2)}|\le 2\binom{n}{2} = \bigO(n^2)$.
-	By \autoref{lema:e3p}, we have that $|S_j^{(3)}| \le 6\binom{n}{3} = \bigO(n^3)$.
-	Therefore, $|S_j|=\bigO(n^3)$, and as $|\Omega(\Pp, \Ww, \Rr)|= |S_1|\times|S_2|\times\dots\times|S_m|$, we have $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
+	Finally, as $|S_j| \le |S_j^{(1)}| +  |S_j^{(2)}| +  |S_j^{(3)}| = \bigO(n^{3})$, it follows that $|\Omega(\Pp, \Ww, \Rr)| = |S_1|\times \dots \times |S_m| = \bigO(n^{3m})$.
 \end{proof}
@@
 Let $E$ be the coverage region of an ellipse with shape parameters $(a, b)$.
-We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \theta) \in \R^2\times\R$, such that, $\{u, v\}\subset \partial E(q, \theta)$, and $\theta$ is an rotation angle that makes $E$'s major-axis parallel to the line defined by $u$ and $v$.
-Also, the procedure $e3p$ called in \autoref{algoritmo:mcer1} is defined in \autoref{algoritmo:e3p}.
+We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \tilde{\Phi}_j(u,v)) \in \R^2\times\R$, such that, $\{u, v\}\subset \partial E(q, \tilde{\Phi}_j(u,v))$.
+This procedure can be defined using the results of \autoref{section:ellipses_intersection}.
 
@@
 Even though it is based on \autoref{th:mcer}, the set of solutions $\Omega(\Pp, \Ww, \Rr)$ is not explicitly built in \autoref{algoritmo:mcer}.
-Instead, a complete search is done by backtracking the CLS of every ellipse returned by procedure CLS-MCER.
+Instead, a complete search is done by backtracking the CLS of every ellipse returned by procedure CLS-MCER defined in \autoref{algoritmo:mcer1}.
 
@@
 The first one, called $MCER$, returns an optimal solution for an instance $(\Pp, \Ww, \Rr)$ using the second procedure $MCER_{bt}$.
-This second procedure is responsible for the backtracking and takes two additional parameters $j\in\{1, \dots, m\}$, which represents the index of the ellipse that $MCER_{bt}$ is currently processing, and $Z\subset \Pp$, which represents the set of points that have not been covered by the ellipses already processed by $MCER_{bt}$.
+This second procedure is responsible for the backtracking and takes two additional parameters $j\in\{1, \dots, m\}$, which represents the index of the ellipse that $MCER_{bt}$ is currently processing, and $Z\subset \Pp$, which represents the set of points that have not been covered by the ellipses with indexes $1, \dots, j-1$.
 
@@
 
-In \autoref{fig:AB120} a solution return by \autoref{algoritmo:mcer} for the instance AB120 taken from \citeonline{andreta} is displayed.
+In \autoref{fig:AB120}, a solution return by \autoref{algoritmo:mcer} for the instance AB120 taken from \citeonline{andreta} is displayed.
 The exact method developed by \citeonline{andreta}, for this instance, could not obtain an optimal solution within the established time limit, however, comparing with the solution obtained by our algorithm, their heuristic method does find an optimal solution.

### 2020-02-11 defesa/tex/chapter/numerical.tex
wip

The goal of this chapter is to show in practice the results of the algorithms for MCE and MCER proposed by us. We first give some implementation details, then we start discuss the solutions obtained for instances proposed in past works, and finally we propose some new instances with the intention of finding the limits of our algorithms.

\section{Implementation}

All the algorithms were implemented using the C++ language, with compiler g++ (G++ 6.3.0). To activate the optimization of compilation we used the -O4 flag.. All the experiments were run in a computer with the following specification:
\begin{itemize}
	\item CPU Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz;
	\item 16Gib of RAM memory;
	\item Linux Operating System: Debian 4.19.5.
\end{itemize}
\subsection{Determining the eigenvalues of a matrix}

In \autoref{algoritmo:e3p}, we assumed that a procedure which returns every eigenvalue of a given square matrix was available. In practice, we used the very famous linear algebra package LAPACK (see \citeonline{lapack} for more details).
LAPACK is a library for the FORTRAN programming language. However, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation. The only remarks, though, are that FORTAN represents matrices in a column-major fashion, and receives parameters only by reference. Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.

LAPACK offers a routine called ZGEEV that computes every eigenvalue of a complex matrix by using an implementation of the QR algorithm. 
This routine optionally can also be asked to compute the right or left eigenvectors depending on two of its parameters. 
ZGEEV receives in total $14$ parameters, with $4$ of them being used for output. We show a brief description of them in \autoref{tab:zgeev} along with the specification of the value we set each parameter in our implementation.
\renewcommand{\arraystretch}{1.5}

\begin{table}[H]\label{tab:zgeev}
	\begin{center}
	\begin{tabular}{|c|m{18em}|m{8em}|}

		\hline
		\textbf{Parameter} & \multicolumn{1}{|c|}{\textbf{Description}} & \multicolumn{1}{|c|}{\textbf{Value}}\\
		\hline
		JOBVL&  Indicates whether to compute the left eigenvalues&  'N' (no eigenvectors should be computed)\\
		\hline
		JOBVR&  Indicates whether to compute the right eigenvalues&  'N' (no eigenvectors should be computed)\\
		\hline
		N    &  Order of matrix A &  6\\
		\hline
		A    &  The square matrix whose eigenvalues are to be computed & The companion matrix \\
		\hline
		LDA  &  Leading dimension of A & 6 \\
		\hline
		W    &  The eigenvalues output array &  A complex array of size 6\\
		\hline
		VL   &  The left eigenvectors output array & A complex array of size 1 \\
		\hline
		LDVL &  Leading dimension of VL&  1\\
		\hline
		VR   &  The right eigenvectors output array&  A complex array of size 1\\
		\hline
		LDVR &  Leading dimension of VR&  1\\
		\hline
		WORK &  A workspace for the procedure to utilize&  A complex array of size 12\\
		\hline
		LWORK&  Dimension of WORK &  12\\
		\hline
		RWORK&  A real workspace of size 2N &  A double array of size 12\\
		\hline
		INFO &  An integer containing $0$ if the algorithm was able to compute every eigenvalue &  A pointer to an integer variable\\
		\hline
	\end{tabular}
	\end{center}
	\caption{The ZGEEV's parameter list.}
\end{table}

\subsection{Symbolic Computation}

Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally.

Back in \autoref{chapter:e3p}, we were faced with the problem of writing the function $\xi$ defined in \autoref{eq:circumscribed_circle_b} as a complex polynomial in the power format by replacing the sine and cosine functions with the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.

As expected, computing the coefficients of that polynomial in terms of the E3P's instance by hand is very challenging; the expressions get too long, and it becomes humanly impossible not to make any mistake. 
For that reason, we resort to Symbolic computation for this task.

In practice, we utilized an external library for Python called SymPy (see \citeonline{sympy} for more information).
This tool can create expressions using arithmetic operators on predefined symbols, numbers, and other expressions. It can also convert expressions into polynomials in the power format, and output them directly into C code. Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.

%This can be done by creating a composition of an expression for $\xi(\theta)(e^{i\theta})^6$ with the expressions for $\cos(\theta)$ and $\sin(\theta)$ defined by \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
%After that, running a command, we can ask SymPy to transform that expression into a polynomial informing it that its variable is $z=e^{i\theta}$. Finally, very conveniently for us, SymPy has a function that outputs expressions directly as C code, which can be used to import the polynomial into our implementation of \autoref{algoritmo:e3p}.

\subsection{Some details and improvements}

### 2020-02-12 defesa/tex/chapter/numerical.tex
wip

@@
 		\hline
-		\textbf{Parameter} & \multicolumn{1}{|c|}{\textbf{Description}} & \multicolumn{1}{|c|}{\textbf{Value}}\\
+		\textbf{Parameter} & \multicolumn{1}{c|}{\textbf{Description}} & \multicolumn{1}{c|}{\textbf{Value}}\\
 		\hline
@@
 It can also convert expressions into polynomials in the power format, and output them directly into C code.
-Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.
+Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++ implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.
 
@@
 \subsection{Some details and improvements}
+
+\section{A greedy algorithm}
+
+In \citeonline{church:1974} a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them.
+We do the same here and define a general greedy algorithm, which follows the same approach as the one in \citeonline{church:1974}, that works for both MCE and MCER.
+
+Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
+Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
+Considering $Z_j \subset \Pp$ is the set of uncovered points before the $j$-th iteration.
+Then, we set the solution for the $j$-th ellipse, as the solution an instance of MCE-1 or MCER-1 with demand points $Z_j$.
+That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
+
+\section{Results for known instances}
+
+In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for the instances proposed by \citeonline{canbolat} and \citeonline{andreta}.

### 2020-02-15 defesa/tex/chapter/numerical.tex
wip

@@
 Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
-Considering $Z_j \subset \Pp$ is the set of uncovered points before the $j$-th iteration.
-Then, we set the solution for the $j$-th ellipse, as the solution an instance of MCE-1 or MCER-1 with demand points $Z_j$.
+Considering $Z_j \subset \Pp$ as the set of uncovered points before the $j$-th iteration.
+Then, we set the solution for the $j$-th ellipse, as the solution of an instance of MCE-1 or MCER-1 with demand points $Z_j$.
 That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
@@
 
-In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for the instances proposed by \citeonline{canbolat} and \citeonline{andreta}.
+In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for the instances CM1-CM9, proposed by \citeonline{canbolat}, and for the instances AB001-AB120, proposed by \citeonline{andreta}.
+
+\subsection{MCE-$k$}
+
+\subsection{MCER-$k$}
+
+\begin{table}[H]\label{tab:mcer-results}
+	\begin{center}
+		\begin{tabular}[\textwidth]{|c c c c|m{4em} c|c|m{4em} m{4em} m{3em} m{5em}|}
+			\hline
+			\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & Greedy & \multicolumn{4}{c|}{Performance metrics}\\
+			\hline
+			Name & $n$ & $m$ & $k$ & 
+			Selected Ellipses & Income & Income 
+			& \parbox{4em}{\centering CLS\\avg. size }
+			& \parbox{4em}{\centering\# E3P\\ problems} 
+			& \# solutions 
+			& \parbox{5em}{\centering CPU Time\\ in secs.}\\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}

### 2020-02-16 defesa/tex/chapter/e3p.tex
wip

@@
-In this chapter, we introduce the problem of determining every center and angle of rotation of an ellipse with fixed shape parameters, such that it contains three given points.
+In this chapter, we introduce the problem of determining every location, here defined as the center and angle of rotation, of an ellipse with fixed shape parameters, such that is contains three given points.
 This problem comes up in the development of an algorithm in \autoref{chapter:mcer}.
@@
 
-We call the problem of finding a center and an angle of rotation for an ellipse given its shape parameters and three points that have to be on its border \sigla{E3P}{Ellipse by Three Points}.
+We call the problem of finding a center and an angle of rotation for an ellipse given its shape parameters and three points that have to be on it \sigla{E3P}{Ellipse by Three Points}.
 An instance of it is given by three points $u, v, w \in \R^2$ and the ellipse's shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
 
-Let $E$ represent the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3P can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
+Let $E: \R^3 \to \R^2$ be a function that takes an ellipse's location with given shape parameters $(a, b)$, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
+Then a solution of E3P can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
 As a last remark, because of its application on \autoref{chapter:mcer}, a method would only be useful for our case if it can encounter every solution of E3P.
-This requirement, of course, makes the problem more challenging.
+This requirement makes the problem more challenging.
 
-\section{Transforming the problem}
+\section{Transforming the problem}\label{section:transforming-the-problem}
 
@@
 To make the problem simpler, let us assume that point $u$ is at the origin. If it is not, a simple translation by $-u$ applied to the three points can be made to put $u$ at the origin.
-Assume as well that $(q, \theta)$ is a solution of E3P, which means that an ellipse rotated by $\theta$, centered at $q$ has $u$, $v$, and $w$ on its border (see \autoref{fig:circumscribed-circle} for an example).
+Assume as well that $(q, \theta)$ is a solution of E3P, which means that an ellipse rotated by $\theta$, centered at $q$ contains $u$, $v$, and $w$ (see \autoref{fig:circumscribed-circle} for an example).
 From a solution of E3P, applying a rotation of $-\theta$ to the coordinate system, an axis-parallel ellipse can be obtained.
@@
 Notice that the transformations represented by $\varphi$ are invertible.
-This means that given a final state, where after applying $\varphi$, the three points are on the border of a radius-$b$ circle, a solution of E3P can be obtained by using the well-defined inverse function $\varphi^{-1}$.
+This means that given a final state, where after applying $\varphi$, the three points are on the radius-$b$ circle, a solution of E3P can be obtained by using the well-defined inverse function $\varphi^{-1}$.
 Additionally, to make the notation more clear, we denote by $\Lambda(\theta)$ the triangle formed by the points $\varphi(u,\theta); \varphi(v, \theta); \varphi(w, \theta)$, as long as they are not collinear.
@@
 	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
-	\includegraphics[scale=.5]{tex/figures/circumscribed-circle}
+	\includegraphics[scale=.4]{tex/figures/circumscribed-circle}
 	\fautor
@@
 
-The term circumradius, in this work, is used to describe the radius of a triangle's circumscribed circle, which is a circle that has the triangle's vertices on its border.
+The term circumradius, in this work, is used to describe the radius of a triangle's circumscribed circle, which is a circle that contains the triangle's vertices.
 Given an instance of E3P, we define the circumradius problem as the problem of determining an angle $\theta\in[0, \pi)$, such that the circumradius of $\Lambda(\theta)$ is equal to $b$.
 
-As it can be seen on \autoref{fig:circumscribed-circle}, given an instance of E3P and an angle of rotation $\theta\in[0, \pi)$ that makes $\Lambda(\theta)$ have a circumradius $b$; a solution for E3P can be obtained using the inverse transformation $\varphi^{-1}$.
+As it can be seen on \autoref{fig:circumscribed-circle}, given an instance of E3P and an angle of rotation $\theta\in[0, \pi)$ that makes $\Lambda(\theta)$ have a circumradius $b$, a solution for E3P can be obtained using the inverse transformation $\varphi^{-1}$.
 With that in mind, it is possible to conclude that both problems are equivalent because, from a solution of one, a unique solution of the other can be obtained.
@@
 \end{equation}
-with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle see \citeonline[p.~189]{johnson1960}).
+with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle, see \citeonline[p.~189]{johnson1960}).
 It should be pointed out that this transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
@@
 \begin{equation}\label{eq:gen_ellipse}
-Ax^2+Bxy+Cy^2+Dy+Ex+F=0.
+Ax^2+Bxy+Cy^2+Dy+Ex+F=0,
 \end{equation}
+with $A, B, C, D, E,F \in \R$ being fixed parameters.
 This equation actually represents any conic, for it to be an ellipse the condition $B^2 -4AC < 0$ must be satisfied.
 
-Setting the first point to be the origin, we get $F=0$.
+Given an instance of E3P, assuming $u$ is at the origin, having that it satisfies \autoref{eq:gen_ellipse}, we get $F=0$.
 Using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$.
@@
 The solutions lie in the set of intersection of these curves.
-This set can probably be done approximated numerically, however, we decided not to further pursue this approach.
+This set can probably be approximated numerically, however, we decided not to further pursue this approach.
 
@@
 \begin{equation}
-T_n(x) = \cos({n\arccos x}).
+T_n(x) = \cos({n\arccos (x)}).
 \end{equation}
@@
 
-One of the greatest qualities of Chebyshev polynomials is its numerical stability.
+One of the greatest qualities of Chebyshev polynomials is their numerical stability.
 \citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form has a condition number that grows exponentially with $n$.
@@
 As it was mentioned in \autoref{chapter:definitions}, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called Frobenius companion matrix.
-For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
+For small values of $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.
 An alternative method can be found in \citeonline{boyd:2013}, where the Chebyshev interpolation is calculated directly as a truncated Chebyshev series, as in \autoref{eq:chebseries}, in $\bigO(n^2)$.
@@
 
-The last question that needs to be addressed is: how close the are roots of the Chebyshev interpolant $f_n$ to the roots of $\xi$?
+The last question that needs to be addressed is: how close are the roots of the Chebyshev interpolant $f_n$ to the roots of $\xi$?
 
@@
 We also investigate if dividing the interpolation interval into $K$ sub-intervals, which is a suggestion given in \citeonline{boyd:2013}, yields an improvement in the accuracy of solutions.
+
+We used the Python programming language in the implementation of this approach for E3P.
+More specifically, we utilized the external library SciPy, which has routines already implemented for Chebyshev interpolation, and finding the roots of a Chebyshev polynomial.
+More information about SciPy can be found in \cite{scipy}.
 
@@
 
-From $\xi$, a real polynomial can be obtained by using the identity $x = \tan{\frac{\theta}{2}}$.
+From $\xi$, a real polynomial can be obtained by using the identity $x = \tan{(\frac{\theta}{2})}$.
 We do not go in detail, but it is possible to show that a degree-$12$ polynomial can be obtained using that substitution.
@@
 \begin{align}\label{eq:complex_trig_cos}
-	\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
+	\cos{(\theta)} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
 	\label{eq:complex_trig_sin}
-	\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i},
+	\sin{(\theta)} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i},
 \end{align}
@@
 
-Among the methods that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3P.
+Among the methods that have been described here, converting $\xi$ into a complex polynomial, and then obtaining its roots by determining the eigenvalues of a companion matrix was the chosen one as the basis of the \autoref{algoritmo:e3p} for E3P.
 Despite the good results shown by the Chebyshev interpolation method,
@@
 Details about getting the eigenvalues of a companion matrix, and determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity. 
-Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}).
-This way, $c_0, \dots, c_{12}$ can be written as functions of the E3P's instance.
-Then, basically, after building a companion matrix for the polynomial $h$, \autoref{algoritmo:e3p}, for every eigenvalue, applies the reverse transformations described by \autoref{eq:trpnts} to obtain a solution for E3P.
+In our implementation, we use symbolic computation to determine the coefficients of $h$ in terms of the parameters of a E3P's instance.
+This way, we only need to compute once separately from the main algorithm.
+We get into more detail about that in \autoref{chapter:numerical}.
+
+Having all the coefficients of $h$ available, basically, after building a companion matrix, \autoref{algoritmo:e3p} applies the reverse transformations described by \autoref{eq:trpnts} to every eigenvalue of that companion matrix to obtain a solution for E3P.
 
@@
 \begin{proof}
-	It has already been shown that computing every root of $\xi$ through the complex polynomial yields every solution of E3P, the only thing left to prove is the running time of the algorithm.
+	It has already been shown in \autoref{section:transforming-the-problem} that computing every root of $\xi$ through the complex polynomial yields every solution of E3P.
+The only thing left to prove is the running time of the algorithm.
 	Computing every eigenvalue of a matrix can be done in $\bigO(n^3)$, but as for our case $n$ is fixed at $6$, it can be stated that computing the eigenvalues for the companion matrix of $f$ can be done in $\bigO(1)$.
@@
 \end{figure}
+
 For the last experiment we considered $100$ instances for each $K$ with three points $(K\cos(t_j), \frac{K\sin{(t_j)}}{2})$, $j=1\dots3$, generated randomly by sampling $t_j$ according to a uniform distribution in $[0, 2\pi]$.

### 2020-02-17 defesa/tex/chapter/e3p.tex
wip

@@
-In this chapter, we introduce the problem of determining every location, here defined as the center and angle of rotation, of an ellipse with fixed shape parameters, such that is contains three given points.
-This problem comes up in the development of an algorithm in \autoref{chapter:mcer}.
-The reason to have a whole chapter devoted to it is that we could not find any work that studies this problem or even related ones.
-As a result, starting from scratch, we ended up trying a handful of approaches, with most of them failing on the way. 
-We thought it would be a useful source for future works if we gave a review of some of those, going through the issues with the failing ones, and discussing the qualities of the successful ones. 
-In the end, we propose an algorithm for the problem that involves determining the eigenvalues of a $6\times6$ matrix.
-We also analyze its efficiency in terms of numerical accuracy and display solutions that it found.
-
-%Even though its simple statement -- it is short and uses only basic mathematical concepts -- we were not able to find any work on it or even on related problems.
+In this chapter, we introduce the problem of determining every location, here defined as the center and angle of rotation, of an ellipse with fixed shape parameters, such that it contains three given points.
+This problem comes up in the development of an algorithm in \autoref{chapter:mcer} as a subproblem.
+Because no studies were found on it, or even on related problems, we decide to devote a whole chapter to presenting a handful of approaches we attempted, going through the issues with the failing ones, as well as discussing the qualities of the ones that shown to be successful.
+In the end, we propose an algorithm for the problem that involves determining the eigenvalues of a $6\times6$ complex matrix.
+We also analyze its efficiency in terms of numerical accuracy and display some solutions that it was able to obtain.
 
@@
 We call the problem of finding a center and an angle of rotation for an ellipse given its shape parameters and three points that have to be on it \sigla{E3P}{Ellipse by Three Points}.
-An instance of it is given by three points $u, v, w \in \R^2$ and the ellipse's shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
+An instance of it is given by three points $u, v, w \in \R^2$, along with the ellipse's shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$.
 
-Let $E: \R^3 \to \R^2$ be a function that takes an ellipse's location with given shape parameters $(a, b)$, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
+Let $E: \R^2\times[0, \pi) \to \R^2$ be a function that takes the location of an ellipse with given shape parameters, and returns its coverage region as defined by \autoref{eq:rotated_ellipse_co}.
 Then a solution of E3P can be defined as a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$.
+
 As a last remark, because of its application on \autoref{chapter:mcer}, a method would only be useful for our case if it can encounter every solution of E3P.
@@
 In this section, we transform E3P into the problem of finding the roots of a univariate function using a known circumcircle problem.
-This transformation, besides reducing the number of unknown variables to one, is later utilized in the demonstration that E3P has at most six distinct solutions, which is one of the most important properties of E3P.
+This transformation, besides reducing the number of unknown variables to one, is later utilized in the demonstration that E3P has at most six distinct solutions.
 
@@
 Assume as well that $(q, \theta)$ is a solution of E3P, which means that an ellipse rotated by $\theta$, centered at $q$ contains $u$, $v$, and $w$ (see \autoref{fig:circumscribed-circle} for an example).
-From a solution of E3P, applying a rotation of $-\theta$ to the coordinate system, an axis-parallel ellipse can be obtained.
-After that, squeezing the $x$-axis by $\frac{b}{a}$ can be utilized to transform the ellipse into a circle of radius $b$.
-An example of this whole process is shown in \autoref{fig:circumscribed-circle}.
-These transformations can be written as a function $\varphi\colon \R^2 \to \R^2$ defined as
+Taking this solution and applying a rotation of $-\theta$ to the coordinate system makes the ellipse become axis-parallel.
+After that, we can transform that axis-parallel ellipse into a circle of radius $b$ by squeezing the $x$-axis by $\frac{b}{a}$.
+This two-step transformation can be written as a function $\varphi\colon \R^2 \to \R^2$ defined as
 
@@
 \end{equation}
-Notice that the transformations represented by $\varphi$ are invertible.
+An example of this two-step transformation being applied to a solution of E3P is shown in \autoref{fig:circumscribed-circle}. 
+Notice that $\varphi$ is a linear transformation.
 This means that given a final state, where after applying $\varphi$, the three points are on the radius-$b$ circle, a solution of E3P can be obtained by using the well-defined inverse function $\varphi^{-1}$.
+
 Additionally, to make the notation more clear, we denote by $\Lambda(\theta)$ the triangle formed by the points $\varphi(u,\theta); \varphi(v, \theta); \varphi(w, \theta)$, as long as they are not collinear.
-This being said, we can go further and introduce a problem equivalent to E3P which is based on determining angles $\theta$ that make the triangle $\Lambda(\theta)$ be circumscribed in a circle of radius $b$.
+This being said, we can move forward and introduce a problem equivalent to E3P which is based on determining angles $\theta$ that make the triangle $\Lambda(\theta)$ be circumscribed in a circle of radius $b$.
 
@@
 The main reason to work with this problem is the reduction in the number of unknown variables from three to just one.
-This idea, however, would only be useful if checking the existence of a circumscribed circle with a radius $b$ is a convenient problem.
-It turns out that, for three non-collinear points, there is always a unique circumscribed circle.
-Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the following expression
+This idea, however, would only be useful if checking the existence of a circumscribed circle with a radius $b$ given a triangle is a convenient problem.
+It turns out that, for any triangle, there is always a unique circumscribed circle, which can be determined analytically.
+Given an instance of E3P and an angle of rotation $\theta \in [0, 2\pi]$, the circumradius $R$ of $\Lambda(\theta)$ can be computed through the following expression
 
@@
 \end{equation}
-with $A(\theta)$ being the area of the triangle $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle, see \citeonline[p.~189]{johnson1960}).
+with $A(\theta)$ being the area of $\Lambda(\theta)$ (for more details about \autoref{eq:circumscribed_circle}, or on how to determine the center of a circumscribed circle, see \citeonline[p.~189]{johnson1960}).
 It should be pointed out that this transformation does not preserve distance or area; if that was true, the radius defined by \autoref{eq:circumscribed_circle} would be constant.
 
-With the formula for the circumradius in hands, a function can be defined, such that its roots provide solutions for the circumradius problem.
+With the formula for the circumradius in hands, a function can be defined, such that its roots provide solutions for the circumradius problem, and consequently, solutions for E3P.
 Imposing the radius $R$ to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as 
-
 \begin{equation}\label{eq:circumscribed_circle_b}
@@
 
-One of the steps of the method developed in \autoref{chapter:mcer} is to iterate over every solution of E3P for every triplet of points.
-Of course, doing that is only possible for a finite number of solutions.
+One of the steps of the method developed in \autoref{chapter:mcer} is to iterate over every solution of E3P.
+Of course, doing that is only possible if E3P has a finite number of solutions.
 Moreover, even if the number of solutions is finite, discovering an upper-bound for that is essential for determining the algorithm's efficiency.
@@
 In \autoref{chapter:definitions}, it was stated that any rotation in the interval $[0, \pi)$ is identical to a rotation in $[\pi, 2\pi)$.
-Therefore, half of the roots of $\xi$ are in $[\pi, 2\pi)$ and can be dismissed.
+Because of that, half of the roots of $\xi$ are in $[\pi, 2\pi)$ and can be dismissed.
 \end{proof}
@@
 The first one converts $\xi$ into a real polynomial and the second one into a complex polynomial.
+For these two approaches we put symbolic computation into practice to obtain the coefficients of the polynomials in terms of the E3P's instance.
 
@@
 We do not go in detail, but it is possible to show that a degree-$12$ polynomial can be obtained using that substitution.
-Computing the actual coefficients can be done using symbolic computing.
 
@@
 which relate complex numbers with trigonometric functions, to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
-This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner}, where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
+This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner}, where it is stated that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.
 
@@
 for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-As the equalities on \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin} are valid for any $\theta \in \R$, function $g(e^{i\theta})$ and $\xi$ are equivalent, since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi)$.
+As the equalities on \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin} are valid for any $\theta \in \R$, function $g(e^{i\theta})$ and $\xi$ are equivalent, since $g(e^{i\theta}) = \xi(\theta)$ for any $\theta \in [0, 2\pi]$.
+Notice that $g$ is not a complex polynomial it has negative exponents and its domain is not $\mathbb{C}$.
 
-The first issue can be fixed by multiplying $g$ by $z^6$.
-Note that this does not create further problems as $0\not\in \mathbb{S}$.
+We can get rid of negative exponents by multiplying $g$ by $z^6$.
+This does not create further problems as $0\not\in \mathbb{S}$.
 The second issue is removed by simply extending the domain from $\mathbb{S}$ to $\mathbb{C}$.
@@
 Lastly, every root of $g$ will correspond to a root of $\xi$ through their angles on the unit circle.
-As in the first approach, symbolic computing can be put in practice to determine the coefficients of $h$ as functions of E3P's instance.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\caption{An instance of E3P with four solutions.}
-	\includegraphics[scale=.35]{tex/figures/e3p_4sols}
+	\includegraphics[scale=.33]{tex/figures/e3p_4sols}
 	\fautor
@@
 	\caption{An instance of E3P with six solutions.}
-	\includegraphics[scale=.35]{tex/figures/e3p_6sols}
+	\includegraphics[scale=.33]{tex/figures/e3p_6sols}
 	\fautor
@@
 	\caption{The maximum and average error for instances with known solutions.}
-	\includegraphics[scale=.8]{tex/figures/e3p_known_sols1}
+	\includegraphics[scale=.75]{tex/figures/e3p_known_sols1}
 	\fautor
@@
 	\caption{The distance of the roots to the unit circle.}
-	\includegraphics[scale=.8]{tex/figures/e3p_known_sols2}
+	\includegraphics[scale=.75]{tex/figures/e3p_known_sols2}
 	\fautor
@@
 The average and the maximum error are plotted in \autoref{fig:e3p_error}, and analyzing it, it is fair to say that \autoref{algoritmo:e3p} is numerically stable for this example, and its error, in average, is expected to be small even if the instance's numerical values are big.
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\caption{The error measured on solutions found by \autoref{algoritmo:e3p}.}
-	\includegraphics[scale=.8]{tex/figures/e3p_error}
+	\includegraphics[scale=.75]{tex/figures/e3p_error}
 	\fautor

### 2020-02-17 defesa/tex/chapter/mcer.tex
wip

@@
 This chapter introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated.
-We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}.
+We refer to this problem as \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.
 In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem.
@@
 
-In this section, we construct a finite list of centers and angles of rotation, also referred to as a CLS, for each ellipse and show that at least one optimal solution is in the set of solutions created from those lists.
+In this section, we construct a finite list of centers and angles of rotation, also referred to as a \sigla{CLS}{Candidate Locations Set}, for each ellipse and show that at least one optimal solution is in the set of solutions created from those lists.
 The results presented in this section are strongly based on \autoref{chapter:e3p}, more specifically on \autoref{lema:e3p}, which states that there exists at most six solutions for any instance of E3P.
 
-We start by introducing a lemma, which says that given an optimal solution of MCER, it is always possible to find an equivalent one, such that every ellipse covering more than one point has two of them on its border.
+We start by introducing a lemma, which says that given an optimal solution of MCER, it is always possible to find an equivalent one, such that every ellipse covering more than one point contains two of them.
 
@@
 
-What \autoref{lema:mce_2b} is saying is that transforming any optimal solution of MCER into an equivalent optimal solution where every ellipse that covers more than one point has two points on its border is possible (an example can be seen in \autoref{fig:ellipse-2-points}).
-\autoref{lema:mce_2b} also says that this equivalent optimal solution can always be achieved by just translating the ellipses; that is, no change in the angle of rotation is required.
+What \autoref{lema:mce_2b} states is that transforming any optimal solution of MCER into an equivalent optimal solution where every ellipse that covers more than one point contains two points is possible (an example can be seen in \autoref{fig:ellipse-2-points}).
+\autoref{lema:mce_2b} also states that this equivalent optimal solution can always be achieved by just translating the ellipses; that is, no change in the angle of rotation is required.
 
@@
 	\caption{An optimal solution before and after applying \autoref{lema:mce_2b}.}
-	\includegraphics[scale=.38]{tex/figures/ellipse-2-points}
+	\includegraphics[scale=.28]{tex/figures/ellipse-2-points}
 	\fautor
@@
 
-Next, a new notation is introduced for the set of equivalent solutions of an optimal one that has at least two points on the border of every ellipse.
+Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.
 
@@
 
-Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains the two points on its border.
+Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.
 
@@
 In \autoref{fig:feasible-angle} two examples for \autoref{def:feasible_angle} are shown.
-The example with a solid border shows two given points on the border of two ellipses rotated by $\pi/4$, making $\pi/4$ a $(E, u, v)$-feasible angle.
-The other example, with a dashed border, presents a case where an ellipse rotated by $\pi/2$ is not able to have the two points on its border, no matter where it is placed; because of that, $\pi/2$ is said to be a non $(E, u, v)$-feasible angle.
+The example with a solid border shows two given points on two different ellipses rotated by $\pi/4$, making $\pi/4$ a $(E, u, v)$-feasible angle.
+The other example, with a dashed border, presents a case where the two points cannot be on the ellipse rotated by $\pi/2$, no matter where it is placed; because of that, $\pi/2$ is said to be a non $(E, u, v)$-feasible angle.
 
@@
 	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
-	\includegraphics[scale=.33]{tex/figures/feasible-angle2}
+	\includegraphics[scale=.28]{tex/figures/feasible-angle2}
 	\fautor
@@
 This lemma makes it possible to describe a type of solution which, for sure, is part of the equivalence class of any optimal solution.
-It says that, for any ellipse that covers more than two points in a given optimal solution, an equivalent solution exists with at least one of the two properties:
+It states that, for any ellipse that covers more than two points in a given optimal solution, an equivalent solution exists with at least one of the two properties:
 \begin{itemize}
-	\item Three points lie on the ellipse's border.
-	\item Two points lie on the ellipse's border, for any feasible angle.
+	\item The ellipse contains at least three points.
+	\item The ellipse contains two points for any feasible angle.
 \end{itemize}
@@
 \begin{lema}\label{lema:3pnts}
-Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.
-
+Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; \\$j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.\\
 If, for all $(\hat{Q}, \hat{\theta})$ equivalent solution of $(Q^*, \Theta^*)$, $|\Pp\cap \partial E_j(\hat{q}_j, \hat{\theta}_j)| < 3$, then for all $\theta\in\Phi_j(u,v)$, there exists $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
@@
 	Let $\theta \in [0, \pi]\setminus\{\pi/2\}$, and $u', v'$ be the points $u, v$ after a rotation by $\theta$.
-Then, if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to apply a translation to $u',v'$, such that they end up in the border of the fixed ellipse.
-This means that, it is possible to find an angle of rotation and a center to place $E_j$, such that it has $u, v$ on its border.
+Then, if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to apply a translation to $u',v'$, such that they end up on the fixed ellipse.
+This means that it is possible to find an angle of rotation and a center to place $E_j$, such that it has $u, v$ on its border.
 
@@
 
-	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}.
+	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-hand-side of \autoref{eq:rotated_ellipse}.
 Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$ as they are covered by the $j$-th ellipse.
@@
 
-What \autoref{lema:3pnts} is saying is that, for every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored.
+What \autoref{lema:3pnts} states is that, for every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on it exists, the angle of rotation can practically be ignored.
 Because of that, it will be shown that we can construct a CLS for each ellipse which is finite and also contains an optimal solution.
@@
 An initial optimal solution is given by the dashed-border ellipse and its center, represented by a star point.
-From it, the continuous function $\delta$ is defined by moving the ellipse through the rotation angles in $\Phi_j(u,v)$ while maintaining $u, v$ on its border.
+From it, the continuous function $\delta$ is defined by moving the ellipse through the rotation angles in $\Phi_j(u,v)$ while maintaining $u, v$ on it.
 Ten angles were chosen from $\Phi_j(u,v)$ to be shown in \autoref{fig:lema-3-points}, among those were $0$ and $\max\{\Phi_j(u,v)\}$; their corresponding ellipses are displayed with solid-line borders.
-Consistently with \autoref{lema:3pnts}, the points in $\Pp \setminus \{u, v, w\}$ stay within the ellipse's cover for any angle of rotation, and, for point $w$, there exists an angle, such that it is on the ellipse's border.
+Consistently with \autoref{lema:3pnts}, the points in $\Pp \setminus \{u, v, w\}$ stay within the ellipse's cover for any angle of rotation, and, for point $w$, there exists an angle, such that it is on the ellipse.
 
@@
 	\caption{A visualization of \autoref{lema:3pnts}.}
-	\includegraphics[scale=.6]{tex/figures/lema-3-points}
+	\includegraphics[scale=.9]{tex/figures/lema-3-points}
 	\fautor
@@
 The first one, $S_j^{(1)}$, represents solutions where the $j$-th ellipse covers only one point.
-The second one, $S_j^{(2)}$, takes into account solutions where the $j$-th ellipse covers at least two points, and no equivalent solution with three points on the ellipse's border exists.
-The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse's border.
+The second one, $S_j^{(2)}$, takes into account solutions where the $j$-th ellipse covers at least two points, and no equivalent solution with three points on the ellipse exists.
+The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse.
 Following this, we move forward and introduce the main result of this section.
@@
 
-	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on its border.
-This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse's border, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
+	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on it.
+This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
 	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
 	Moreover, in \autoref{section:ellipses_intersection}, we discuss the problem of determining the intersections between two ellipses.
-This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on the border of an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
+This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
 In \autoref{section:ellipses_intersection}, it is shown that this problem has at most two solutions.
@@
 
-	For the last case, we are left with solutions where the $j$-th ellipse covers more than two points, and there exists an equivalent solution with three points on its border. 
-	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the border of the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega(\Pp, \Ww, \Rr)$.
-Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse have three given points on its border is at most six.
+	For the last case, we are left with solutions where the $j$-th ellipse covers more than two points, and there exists an equivalent solution with three points on it. 
+	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega(\Pp, \Ww, \Rr)$.
+Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse contain three given points is at most six.
 Therefore, we have that $|S_j^{(3)}| = 6\binom{n}{3}$.
@@
 In this section we describe an algorithm for MCER that does a complete search on the CLS of each ellipse.
+Firstly, in \autoref{algoritmo:mcer1}, we present a procedure called CLS-MCER which returns the CLS for an ellipse with shape parameters $(a, b)$.
+Then, in \autoref{algoritmo:mcer} we describe the procedure that returns an optimal solution for MCER.
 
-Firstly, we describe an algorithm that constructs a CLS for a given ellipse.
 Let $E$ be the coverage region of an ellipse with shape parameters $(a, b)$.
-We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \tilde{\Phi}_j(u,v)) \in \R^2\times\R$, such that, $\{u, v\}\subset \partial E(q, \tilde{\Phi}_j(u,v))$.
+We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \tilde{\Phi}_j(u,v)) \in \R^2\times[0, \pi)$, such that, $\{u, v\}\subset \partial E(q, \tilde{\Phi}_j(u,v))$.
+That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse.
+
 This procedure can be defined using the results of \autoref{section:ellipses_intersection}.
@@
 		\Procedure{$MCER_{bt}$}{$Z, \Ww, \Rr, j$}
-		\If{$j = m+1$}
-		\State \Return $0$
-		\EndIf
+		%\If{$j = m+1$}
+		%\State \Return $0$
+		%\EndIf
 
-		\State $ans \gets 0$
+		%\State $ans \gets 0$
 		\State $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*) \gets (0, \dots 0); (0, \dots, 0)$ \Comment{Setting to $0$ as a default value.}
@@
 
-		\For{$(q_j, \theta_j) \in S_j$}
-		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
+		\ForAll{$(q_j, \theta_j) \in S_j$}
+		%\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
 
+		\If{$j < m$}
 		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$
+		\EndIf
 
-		\State $Cov \gets \bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)$
-		\If {$w(Cov) > ans$}
-			\State $ans \gets w(Cov)$
+		%\State $Cov \gets \bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)$
+		\If {$w(\bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)) > w(\bigcup_{k=j}^m \Pp \cap E_k(q_k^*, \theta_k^*))$}
+			%\State $ans \gets w(Cov)$
 			%\State $((q_{j}^*,\theta_{j}^*); \dots; (q_m^*, \theta_m^*)) \gets ((q_{j},\theta_{j}); \dots; (q_m, \theta_m))$
@@
 \begin{corolario}
-	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ computations and returns an optimal solution for an instance of MCER.
+	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ operations and returns an optimal solution for an instance of MCER.
 \end{corolario}
@@
 Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
+As evaluating each solution can be done in $\bigO(n)$, we get the overall runtime complexity of $\bigO(n^{3m+1})$ which is $\bigO(n^{3m})$.
 \end{proof}
 
-In \autoref{fig:AB120}, a solution return by \autoref{algoritmo:mcer} for the instance AB120 taken from \citeonline{andreta} is displayed.
+In \autoref{fig:AB120}, a solution returned by \autoref{algoritmo:mcer} for the instance AB120 taken from \citeonline{andreta} is displayed.
 The exact method developed by \citeonline{andreta}, for this instance, could not obtain an optimal solution within the established time limit, however, comparing with the solution obtained by our algorithm, their heuristic method does find an optimal solution.
-In the next chapter, we give more details about the solutions found by our algorithm, along with the proposal of some new instances for MCER and MCER-$k$.
+In the next chapter, we give more details about the solutions found by our algorithm, along with the proposal of some new instances for MCER.
 
-\begin{figure}
+\begin{figure}[!htb]
 	\centering

### 2020-02-17 defesa/tex/chapter/numerical.tex
wip

@@
 	\begin{center}
-		\begin{tabular}[\textwidth]{|c c c c|m{4em} c|c|m{4em} m{4em} m{3em} m{5em}|}
+		\resizebox{\textwidth}{!}{%
+
+		\begin{tabular}{|c c c c|m{4em} c|c|m{4em} m{4em} m{4em} m{4.5em}|}
 			\hline
@@
 			Name & $n$ & $m$ & $k$ & 
-			Selected Ellipses & Income & Income 
-			& \parbox{4em}{\centering CLS\\avg. size }
-			& \parbox{4em}{\centering\# E3P\\ problems} 
-			& \# solutions 
-			& \parbox{5em}{\centering CPU Time\\ in secs.}\\
+			Selected Ellipses& Income & Income 
+			& \centering CLS avg. size
+			& \parbox{4em}{\centering\# E3P\\problems} 
+			& \parbox{4em}{\centering\# Eval.\\solutions}
+			& \parbox{4.5em}{\centering CPU Time\\ in secs.}\\
 			\hline
 		\end{tabular}
+	}
 	\end{center}
 \end{table}
+
+\begin{table}[H]\label{tab:mcer-results2}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|c c c c|m{4em} c|c|m{4em} m{4em} m{4em} m{4.5em}|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & Greedy & \multicolumn{4}{c|}{Performance metrics}\\
+				\hline
+				\multirow{2}{*}{Name} & \multirow{2}{*}{$n$} & $m$ & $k$ & Selected&Income & Income 
+				& CLS avg.
+				& \# E3P
+				& \# Eval.
+				& CPU Time\\
+				& & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1\\
+				\hline
+			\end{tabular}
+ 		}
+	\end{center}
+\end{table}

### 2020-02-19 defesa/tex/chapter/numerical.tex
wip

--- 2020-02-15 defesa/tex/chapter/numerical.tex
@@
 We show a brief description of them in \autoref{tab:zgeev} along with the specification of the value we set each parameter in our implementation.
-\renewcommand{\arraystretch}{1.5}
+%\renewcommand{\arraystretch}{1.1}
 
@@
 
+To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} and \autoref{algoritmo:mcer} had to be done.
+Just translating those algorithms into a programming language was not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
+Therefore, we present here, some improvements that can be applied to the implementation of those algorithms, which can result in a significant improvement in performance, especially in terms of CPU time.
+
+In both algorithms, a subroutine to construct an ellipse's CLS is called inside the backtracking routine. This can potentially make the same combination of points be considered multiple times.
+To avoid this unnecessary computation, points that have already been considered for an ellipse's CLS can be stored, and only new combinations can then be taken into account each time the CLS subroutine is called.
+
+Another improvement that can be made in the construction of an ellipse's CLS is the elimination of redundant solutions.
+Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER.
+If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, then we can for sure dismiss solution $(Q', \Theta')$.
+In our implementation, we use the same tree-like data structure as the one described by \citeonline{andreta} to only keep solutions that are not redundant.
+
+Also, to avoid solving the subproblem E3P in the algorithm for MCER, we can check if the maximum distance between any of the three points is greater than $2a$, where $a$ is an ellipse's semi-major.
+This is useful because calling \autoref{algoritmo:e3p} for every triplet of points of an instance of MCER can be very expensive.
+
+The last implementation improvement was obtained by keeping an upper-bound for the optimal solution during the backtracking in both \autoref{algoritmo:mce} and \autoref{algoritmo:mcer}.
+Let us consider the case for the MCER's algorithm (the MCE's case is analogous).
+Let $$z_j = \max_{(q, \theta) \in S_j} w(\Pp \cap E_j(q, \theta)),$$ and $OPT_j$ be the value of the best solution which has the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+Then, as $z_k$ considers the best possible location for each ellipse, we have that
+\begin{equation*}\label{eq:upper-bound}
+OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k.
+\end{equation*}
+Let $OPT$ be the current optimal solution, we have that if
+\begin{equation}
+w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k \le OPT,
+\end{equation}
+then $OPT_j \le OPT$, which means that we can skip every solution with the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be preprocessed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER_{bt}$ procedure.
+
 \section{A greedy algorithm}
@@
 \subsection{MCER-$k$}
+\clearpage
 
-\begin{table}[H]\label{tab:mcer-results}
+\begin{table}[H]\label{tab:mcer-results2}
 	\begin{center}
-		\begin{tabular}[\textwidth]{|c c c c|m{4em} c|c|m{4em} m{4em} m{3em} m{5em}|}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cc|cccccc|}
 				\hline
-			\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & Greedy & \multicolumn{4}{c|}{Performance metrics}\\
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
 				\hline
-			Name & $n$ & $m$ & $k$ & 
-			Selected Ellipses & Income & Income 
-			& \parbox{4em}{\centering CLS\\avg. size }
-			& \parbox{4em}{\centering\# E3P\\ problems} 
-			& \# solutions 
-			& \parbox{5em}{\centering CPU Time\\ in secs.}\\
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				Average CLS&
+				\multicolumn{2}{c}{\# E3P subproblems}&
+				\# evaluated & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & size & \centering feasible & \centering unfeasible & solutions & E3P & Total\\
 				\hline
+				\input{tex/table_mcerk_ab_1.tex}
+
 			\end{tabular}
+ 		}
+ 	\caption{Solutions for AB001-AB060}
 	\end{center}

### 2020-02-21 defesa/tex/chapter/e3p.tex
wip

@@
 
-Among the methods that have been described here, converting $\xi$ into a complex polynomial, and then obtaining its roots by determining the eigenvalues of a companion matrix was the chosen one as the basis of the \autoref{algoritmo:e3p} for E3P.
+Among the methods that have been described here, converting $\xi$ into a complex polynomial, and then obtaining its roots by determining the eigenvalues of a companion matrix was the chosen one as the basis of \autoref{algoritmo:e3p} for E3P.
 Despite the good results shown by the Chebyshev interpolation method,

### 2020-02-21 defesa/tex/chapter/numerical.tex
wip

@@
 
-\subsection{Some details and improvements}
+\subsection{Some details and improvements}\label{section:improvements}
 
@@
 
-The last implementation improvement was obtained by keeping an upper-bound for the optimal solution during the backtracking in both \autoref{algoritmo:mce} and \autoref{algoritmo:mcer}.
+The last implementation improvement was obtained by keeping an upper-bound, which can be used to skip solutions that are surely not better than the current best solution.
+When the backtracking algorithm has the location for the first $j$ ellipses fixed, we want to have an upper-bound for the best solution that can still be found by choosing the location of the $m-j$ remaining ellipses.
 Let us consider the case for the MCER's algorithm (the MCE's case is analogous).
 Let $$z_j = \max_{(q, \theta) \in S_j} w(\Pp \cap E_j(q, \theta)),$$ and $OPT_j$ be the value of the best solution which has the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-Then, as $z_k$ considers the best possible location for each ellipse, we have that
-\begin{equation*}\label{eq:upper-bound}
+Then, as $z_k$ is the best value that the $k$-th ellipse can contribute to any solution, we get the following inequality
+\begin{equation*}
 OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k.
 \end{equation*}
+This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be preprocessed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER_{bt}$ procedure.
 Let $OPT$ be the current optimal solution, we have that if
 \begin{equation}
+\label{eq:upper-bound}
 w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k \le OPT,
@@
 then $OPT_j \le OPT$, which means that we can skip every solution with the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be preprocessed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER_{bt}$ procedure.
+
+It is worth pointing out that these improvement suggestions do not have an effect in a possible worst case scenario.
+We are adopting them in our implementation because they showed good results in practice.
+For example, without taking the suggestion given by \autoref{eq:upper-bound}, \autoref{algoritmo:mcer-k} takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions.
+In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for the instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
 
@@
 
-In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for the instances CM1-CM9, proposed by \citeonline{canbolat}, and for the instances AB001-AB120, proposed by \citeonline{andreta}.
+In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for the instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for the instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
+
+For every instance, we present some information about the obtained optimal solution, along with some performance metrics.
+For the optimal solution we present the selected ellipses, and the value of the optimal solution, which we denoted as Income.
+As performance metrics we have: the maximum CLS size, the number of nodes in the backtracking tree, the number of leaves that contain a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
+For the algorithms for MCER we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
 
@@
 
-\subsection{MCER-$k$}
-\clearpage
+In \autoref{tab:mce-results-cm}, the results for instances CM1-CM9. 
+The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than a second for every one of the instances CM1-CM9.
+Even though the experiments were run in a different environment, we can still say that this is a great improvement compared with the results from \citeonline{andreta}.
+For example, to obtain an optimal solution for the instance CM9, the method proposed by \citeonline{andreta} took more than thirty minutes.
+In \autoref{tab:mce-results-ab1} and \autoref{tab:mce-results-ab2}, we present the results for instances AB001-AB120.
+The only instance that our algorithm took more than one second to return an optimal solution was AB120, which it took 1.15 seconds.
 
-\begin{table}[H]\label{tab:mcer-results2}
+In practice, at least for these instances, the bound $\bigO(n^{3m})$ for the algorithm for MCE-$k$ seems to be loose.
+In instance CM9, for example, this bound says that the number of leaves in the backtrack tree should be close to $n^{3m} = (10^2)^{3\times 3} = 10^{18}$, which is very far from the actual number of $5243$ leaves obtained in practice.
+
+\begin{table}\label{tab:mce-results-cm}
 	\begin{center}
@@
 
-			\begin{tabular}{|cccc|cc|cccccc|}
+			\begin{tabular}{|cccc|cr|crrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				Max CLS&
+				\multicolumn{2}{c}{Backtrack Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & size & \# nodes & \# sol. leaves & CLS-MCE & Total\\
+				\hline
+				\input{tex/table_mcek_cm.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCE-$k$ for instances CM1-CM9.}
+	\end{center}
+\end{table}
+
+\begin{table}\label{tab:mce-results-ab1}
+	\begin{center}
+		\resizebox{0.85\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|rrrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+			\multirow{2}{*}{Name} & 
+			\multirow{2}{*}{$n$} & 
+			\multirow{2}{*}{$m$} & 
+			\multirow{2}{*}{$k$} & 
+			Selected & 
+			\multirow{2}{*}{Income} & 
+			Max CLS&
+			\multicolumn{2}{c}{Backtrack Tree} & 
+			\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+			& & & & \centering Ellipses & & size & \# nodes & \# sol. leaves & CLS-MCE & Total\\
+				\hline
+				\input{tex/table_mcek_ab_1.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCE-$k$ for instances AB001-AB060.}
+	\end{center}
+\end{table}
+
+\begin{table}\label{tab:mce-results-ab2}
+	\begin{center}
+		\resizebox{0.85\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|rrrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+\multirow{2}{*}{Name} & 
+\multirow{2}{*}{$n$} & 
+\multirow{2}{*}{$m$} & 
+\multirow{2}{*}{$k$} & 
+Selected & 
+\multirow{2}{*}{Income} & 
+Max CLS&
+\multicolumn{2}{c}{backtrack tree} & 
+\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+& & & & \centering Ellipses & & size & \# nodes & \#sol. leaves & CLS-MCE & Total\\
+				\hline
+				\input{tex/table_mcek_ab_2.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCE-$k$ for instances AB061-AB120.}
+	\end{center}
+\end{table}
+
+\subsection{MCER-$k$}
+
+\begin{table}\label{tab:mcer-results-cm}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|rrrrrr|}
 				\hline
@@
 				\multirow{2}{*}{Income} & 
-				Average CLS&
-				\multicolumn{2}{c}{\# E3P subproblems}&
-				\# evaluated & 
+				Max CLS&
+				\# E3P&
+				\multicolumn{2}{c}{backtrack tree} & 
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & size & \centering feasible & \centering unfeasible & solutions & E3P & Total\\
+				& & & & \centering Ellipses & & size & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%
+				%%%
+
 				\hline
-				\input{tex/table_mcerk_ab_1.tex}
+				\input{tex/table_mcerk_cm.tex}
+				\hline
 
@@
 		}
- 	\caption{Solutions for AB001-AB060}
+		\caption{Solutions of MCER-$k$ for instances CM1-CM9.}
 	\end{center}
 \end{table}
+
+\begin{table}\label{tab:mcer-results-ab1}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|rrrrrr|}
+				\hline
+\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
+\hline
+
+%%% Second line of header
+
+\multirow{2}{*}{Name} & 
+\multirow{2}{*}{$n$} & 
+\multirow{2}{*}{$m$} & 
+\multirow{2}{*}{$k$} & 
+Selected & 
+\multirow{2}{*}{Income} & 
+Max CLS&
+\# E3P&
+\multicolumn{2}{c}{backtrack tree} & 
+\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+& & & & \centering Ellipses & & size & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%
+				%%%
+
+				\hline
+				\input{tex/table_mcerk_ab_1.tex}
+				\hline
+
+			\end{tabular}
+ 		}
+ 	\caption{Solutions of MCER-$k$ for instances AB001-AB060.}
+	\end{center}
+\end{table}
+
+\begin{table}\label{tab:mcer-results-ab2}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|rrrrrr|}
+				\hline
+\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
+\hline
+
+%%% Second line of header
+
+\multirow{2}{*}{Name} & 
+\multirow{2}{*}{$n$} & 
+\multirow{2}{*}{$m$} & 
+\multirow{2}{*}{$k$} & 
+Selected & 
+\multirow{2}{*}{Income} & 
+Max CLS&
+\# E3P&
+\multicolumn{2}{c}{backtrack tree} & 
+\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+& & & & \centering Ellipses & & size & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/table_mcerk_ab_2.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCER-$k$ for instances AB061-AB120.}
+	\end{center}
+\end{table}

### 2020-02-22 defesa/tex/chapter/numerical.tex
wip

@@
 
-For every instance, we present some information about the obtained optimal solution, along with some performance metrics.
-For the optimal solution we present the selected ellipses, and the value of the optimal solution, which we denoted as Income.
-As performance metrics we have: the maximum CLS size, the number of nodes in the backtracking tree, the number of leaves that contain a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
-For the algorithms for MCER we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
+For each instance, we display the selected ellipses and the income of the found optimal solution. 
+We also display some performance metrics with the intention of giving an idea of how much computation had to be done for the algorithms to find an optimal solution. These metrics are: 
+the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
+For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
 
@@
 
-In \autoref{tab:mce-results-cm}, the results for instances CM1-CM9. 
-The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than a second for every one of the instances CM1-CM9.
+In \autoref{tab:mce-results-cm}, the results for instances CM1-CM9 are shown. 
+The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than one second for every one of the instances CM1-CM9.
 Even though the experiments were run in a different environment, we can still say that this is a great improvement compared with the results from \citeonline{andreta}.
@@
 In \autoref{tab:mce-results-ab1} and \autoref{tab:mce-results-ab2}, we present the results for instances AB001-AB120.
-The only instance that our algorithm took more than one second to return an optimal solution was AB120, which it took 1.15 seconds.
+The only instance that our algorithm took more than one second to return an optimal solution was AB120, which it took 1.08 second.
 
 In practice, at least for these instances, the bound $\bigO(n^{3m})$ for the algorithm for MCE-$k$ seems to be loose.
-In instance CM9, for example, this bound says that the number of leaves in the backtrack tree should be close to $n^{3m} = (10^2)^{3\times 3} = 10^{18}$, which is very far from the actual number of $5243$ leaves obtained in practice.
-
-\begin{table}\label{tab:mce-results-cm}
+In instance CM9, for example, this bound says that the number of leaves corresponding to a solution in the backtracking tree should be close to $n^{3m} = (10^2)^{3\times 3} = 10^{18}$, which is very far from the actual number of $649$ such leaves obtained in practice.
+This is also the case for the size of the CLSs, which are all very far away from its $\bigO(n^2)$ bound.
+The greatest CLS size observed was $174$ for instance CM9, which is still very far away from $n^2$, which in this case is $10^4$.
+\begin{table}
 	\begin{center}
@@
 				\multirow{2}{*}{Income} & 
-				Max CLS&
-				\multicolumn{2}{c}{Backtrack Tree} & 
+				CLS size&
+				\multicolumn{2}{c}{Backtracking Tree} & 
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & size & \# nodes & \# sol. leaves & CLS-MCE & Total\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
 				\hline
@@
 		\caption{Solutions of MCE-$k$ for instances CM1-CM9.}
+		\label{tab:mce-results-cm}
 	\end{center}
@@
 
-\begin{table}\label{tab:mce-results-ab1}
+\begin{table}
 	\begin{center}
@@
 
-			\begin{tabular}{|cccc|cr|rrrrr|}
+			\begin{tabular}{|cccc|cr|crrrr|}
 				\hline
@@
 			\multirow{2}{*}{Income} & 
-			Max CLS&
-			\multicolumn{2}{c}{Backtrack Tree} & 
+			CLS size&
+			\multicolumn{2}{c}{Backtracking Tree} & 
 			\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-			& & & & \centering Ellipses & & size & \# nodes & \# sol. leaves & CLS-MCE & Total\\
+			& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
 				\hline
@@
 		\caption{Solutions of MCE-$k$ for instances AB001-AB060.}
+		\label{tab:mce-results-ab1}
 	\end{center}
@@
 
-\begin{table}\label{tab:mce-results-ab2}
+\begin{table}
 	\begin{center}
@@
 \multirow{2}{*}{Income} & 
-Max CLS&
-\multicolumn{2}{c}{backtrack tree} & 
+CLS size&
+\multicolumn{2}{c}{Backtracking Tree} & 
 \multicolumn{2}{c|}{\centering CPU Time (s)}\\
-& & & & \centering Ellipses & & size & \# nodes & \#sol. leaves & CLS-MCE & Total\\
+& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol. leaves & CLS-MCE & Total\\
 				\hline
@@
 		\caption{Solutions of MCE-$k$ for instances AB061-AB120.}
+		\label{tab:mce-results-ab2}
 	\end{center}
@@
 
-\begin{table}\label{tab:mcer-results-cm}
+Two methods for MCER-$k$ were developed in \citeonline{andreta}: a deterministic method using global optimization, and a heuristic-stochastic method also using a global optimization, but taking the first found solution as a global optimizer.
+The deterministic method could not find solutions for every instance within a specified time limit, however, comparing with the results of our algorithm, which are displayed in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for isntances AB001-AB120, we could observe that the heuristic method did find an optimal solution for every instance.
+
+In general, our algorithm took much lower CPU time to return an optimal solution when compared with the heuristic method developed by \citeonline{andreta}.
+For example, for instance CM9 it ran for more than six hours, while our implementation of \autoref{algoritmo:mcer-k} obtained an optimal solution in less than twenty seconds.
+
+We can give the same remarks about the bounds for the algorithm and the CLS size as we did when analyzing the numerical results of MCE-$k$.
+Notice that, the greatest CLS size was $701$ obtained for instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
+By \autoref{th:mcer}, for MCER, the bound for the number of solutions that need to be considered for an optimal one to be found is $\bigO(n^{3m})$, in instance AB120, for example, the number of visited solutions is only $120$, which is way lower than $100^{15}$.
+
+\begin{table}
 	\begin{center}
@@
 
-			\begin{tabular}{|cccc|cr|rrrrrr|}
+			\begin{tabular}{|cccc|cr|crrrrr|}
 				\hline
@@
 				\multirow{2}{*}{Income} & 
-				Max CLS&
+				CLS size&
 				\# E3P&
-				\multicolumn{2}{c}{backtrack tree} & 
+				\multicolumn{2}{c}{Backtracking Tree} & 
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & size & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
 
@@
 		\caption{Solutions of MCER-$k$ for instances CM1-CM9.}
+		\label{tab:mcer-results-cm}
 	\end{center}
@@
 
-\begin{table}\label{tab:mcer-results-ab1}
+\begin{table}
 	\begin{center}
@@
 \multirow{2}{*}{Income} & 
-Max CLS&
+CLS size&
 \# E3P&
-\multicolumn{2}{c}{backtrack tree} & 
+\multicolumn{2}{c}{Backtracking Tree} & 
 \multicolumn{2}{c|}{\centering CPU Time (s)}\\
-& & & & \centering Ellipses & & size & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
 
@@
  	\caption{Solutions of MCER-$k$ for instances AB001-AB060.}
+ 	\label{tab:mcer-results-ab1}
 	\end{center}
@@
 
-\begin{table}\label{tab:mcer-results-ab2}
+\begin{table}
 	\begin{center}
@@
 		\caption{Solutions of MCER-$k$ for instances AB061-AB120.}
+		\label{tab:mcer-results-ab2}
 	\end{center}

### 2020-02-23 defesa/tex/chapter/numerical.tex
wip

@@
 
-\subsection{Some details and improvements}\label{section:improvements}
+\section{A greedy algorithm}
+
+In \citeonline{church:1974}, a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them. 
+Here we introduce a very similar algorithm for both MCE and MCER with the intention of using it in the development of a sufficient condition to skip non-optimal solutions.
+
+Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
+Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
+Considering $Z_j \subset \Pp$ as the set of uncovered points before the $j$-th iteration.
+Then, we set the solution for the $j$-th ellipse, as the solution of an instance of MCE-1 or MCER-1 with demand points $Z_j$.
+That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
+This algorithm can be implemented, such that it takes $\bigO(n^4m)$ operations to construct a solution.
+
+\section{Some details and improvements}\label{section:improvements}
 
@@
 
-The last implementation improvement was obtained by keeping an upper-bound, which can be used to skip solutions that are surely not better than the current best solution.
+The last implementation improvement was obtained by keeping an upper-bound, which can be used to skip solutions that are surely non-optimal.
 When the backtracking algorithm has the location for the first $j$ ellipses fixed, we want to have an upper-bound for the best solution that can still be found by choosing the location of the $m-j$ remaining ellipses.
 Let us consider the case for the MCER's algorithm (the MCE's case is analogous).
-Let $$z_j = \max_{(q, \theta) \in S_j} w(\Pp \cap E_j(q, \theta)),$$ and $OPT_j$ be the value of the best solution which has the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-Then, as $z_k$ is the best value that the $k$-th ellipse can contribute to any solution, we get the following inequality
+
+Given an instance $(\Pp, \Ww, \Rr)$ of MCER, assume that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
+We will use the solution returned by the greedy algorithm defined earlier as an upper-bound for the solution considering only the $m-j$ remaining ellipses.
+Let 
 \begin{equation*}
-OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k.
+Z_j=\Pp\setminus \cup_{k=1}^j E_k(q_k, \theta_k),
 \end{equation*}
-This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be preprocessed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER_{bt}$ procedure.
-Let $OPT$ be the current optimal solution, we have that if
+be the points from the demand set which are not covered by the first $j$ ellipses, and $(q_{j+1}', \dots, q_m')\in \R^{2(m-j)}$, $(\theta_{j+1}, \dots, \theta_m) \in [0, \pi)^{m-j}$ be the solution returned by the greedy algorithm for the instance $(Z_j, \{w_k \in \Ww: p_k \in Z_j\}, \{(a_{j+1}, b_{j+1}); \dots; (a_m, b_m)\})$ of MCER.
+That is, the instance with demand points that are not covered by the first $j$ ellipses.
+Then, let $OPT_j$ be the value of the best solution for the instance $(\Pp, \Ww, \Rr)$ with the first $j$ ellipses with location fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+Then, we have the following inequality
+
+\begin{equation}
+OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right)
+\end{equation}
+This upper-bound for $OPT_j$ can then be used in the backtracking process to skip solutions that are not better. Let $OPT_{lo}$ be a lower bound for the optimal solution, then the inequality
 \begin{equation}
 \label{eq:upper-bound}
-w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k \le OPT,
+w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) +w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right) \le OPT_{lo},
 \end{equation}
-then $OPT_j \le OPT$, which means that we can skip every solution with the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
+In practice, we can use the value of the best solution found so far by the backtracking process as the lower-bound $OPT_{lo}$.
 
@@
 In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for the instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
-
-\section{A greedy algorithm}
-
-In \citeonline{church:1974} a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them.
-We do the same here and define a general greedy algorithm, which follows the same approach as the one in \citeonline{church:1974}, that works for both MCE and MCER.
-
-Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
-Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
-Considering $Z_j \subset \Pp$ as the set of uncovered points before the $j$-th iteration.
-Then, we set the solution for the $j$-th ellipse, as the solution of an instance of MCE-1 or MCER-1 with demand points $Z_j$.
-That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
 
@@
 In general, our algorithm took much lower CPU time to return an optimal solution when compared with the heuristic method developed by \citeonline{andreta}.
-For example, for instance CM9 it ran for more than six hours, while our implementation of \autoref{algoritmo:mcer-k} obtained an optimal solution in less than twenty seconds.
+For example, for instance, CM9 it ran for more than six hours, while our implementation of \autoref{algoritmo:mcer-k} obtained an optimal solution in less than five seconds.
+One peculiarity that can be observed in the results for these instances is that the time spent in the backtracking phase is always very small, especially if compared to the time spent in the construction of the CLSs.
 
-We can give the same remarks about the bounds for the algorithm and the CLS size as we did when analyzing the numerical results of MCE-$k$.
+As it was said for the results of MCE-$k$, in practice, the bounds for the CLS size and the number of operations taken by the algorithm is very loose.
 Notice that, the greatest CLS size was $701$ obtained for instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
-By \autoref{th:mcer}, for MCER, the bound for the number of solutions that need to be considered for an optimal one to be found is $\bigO(n^{3m})$, in instance AB120, for example, the number of visited solutions is only $120$, which is way lower than $100^{15}$.
+By \autoref{th:mcer}, for MCER, the bound for the number of computations that \autoref{algoritmo:mcer-k} takes is $\bigO(n^{4m})$.
+In instance AB120, for example, the size of the backtracking tree is only $7102$, which is way lower than $100^{15}$.
 
@@
 \end{table}
+
+\section{Other instances}
+
+In this section, we describe some new instances which were created with the intention of further analyzing the algorithms developed by our work.
+We introduce larger instances and try to create cases which our algorithm does not perform as well as it does for the instances CM1-CM9 and AB001-AB120.

### 2020-02-25 defesa/tex/chapter/numerical.tex
wip

@@
 In this section, we describe some new instances which were created with the intention of further analyzing the algorithms developed by our work.
-We introduce larger instances and try to create cases which our algorithm does not perform as well as it does for the instances CM1-CM9 and AB001-AB120.
+
+To generate the demand set, for each point, we had its coordinates follow a normal distribution $\mathcal{N}(0, 1)$.
+This way, most of the points are expected to be near the origin, making optimal solutions cover bigger portions of the demand set when compared to the previously analyzed instances.
+We constructed eight instances with $n=150$ and $m=8$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=a_i\times b_i$, and the weight of every point as $1$.

### 2020-02-25 defesa/tex/chapter/numerical.tex
wip

@@
 This way, most of the points are expected to be near the origin, making optimal solutions cover bigger portions of the demand set when compared to the previously analyzed instances.
-We constructed eight instances with $n=150$ and $m=8$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=a_i\times b_i$, and the weight of every point as $1$.
+We constructed eight instances with $n=100$ and $m=8$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=10 \times a_i\times b_i$, and the weight of every point as its distance to the origin.

### 2020-02-25 defesa/tex/chapter/numerical.tex
wip

--- 2020-02-25 defesa/tex/chapter/numerical.tex
@@
 In both algorithms, a subroutine to construct an ellipse's CLS is called inside the backtracking routine. This can potentially make the same combination of points be considered multiple times.
-To avoid this unnecessary computation, points that have already been considered for an ellipse's CLS can be stored, and only new combinations can then be taken into account each time the CLS subroutine is called.
+To avoid this unnecessary computation, we compute the CLS for every ellipse beforehand in a preprocessing phase for the whole demand set.
+Then, in the backtracking, we only consider the options of locations that makes the ellipse cover points that have not been covered before.
 
 Another improvement that can be made in the construction of an ellipse's CLS is the elimination of redundant solutions.
-Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER.
+Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER (the same can be said about MCE).
 If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, then we can for sure dismiss solution $(Q', \Theta')$.
@@
 
-Also, to avoid solving the subproblem E3P in the algorithm for MCER, we can check if the maximum distance between any of the three points is greater than $2a$, where $a$ is an ellipse's semi-major.
-This is useful because calling \autoref{algoritmo:e3p} for every triplet of points of an instance of MCER can be very expensive.
+Calling \autoref{algoritmo:e3p} for E3P for every triplet of points in an instance of MCER can be expensive.
+To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than the ellipse's area, $\pi ab$.
 
-The last implementation improvement was obtained by keeping an upper-bound, which can be used to skip solutions that are surely non-optimal.
-When the backtracking algorithm has the location for the first $j$ ellipses fixed, we want to have an upper-bound for the best solution that can still be found by choosing the location of the $m-j$ remaining ellipses.
-Let us consider the case for the MCER's algorithm (the MCE's case is analogous).
+Without any improvement, backtracking through every possible combination in the CLS of every ellipse can take a very long time, while most of those combinations are easy-to-spot non-optimal solutions.
+Because of that, we introduce a sufficient condition, based on the algorithm for only one ellipse, which can be used to skip solutions that for sure are non-optimal.
+We are going to do that for the MCER's case (the MCE's case is analogous).
 
-Given an instance $(\Pp, \Ww, \Rr)$ of MCER, assume that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
-We will use the solution returned by the greedy algorithm defined earlier as an upper-bound for the solution considering only the $m-j$ remaining ellipses.
-Let 
-\begin{equation*}
-Z_j=\Pp\setminus \cup_{k=1}^j E_k(q_k, \theta_k),
-\end{equation*}
-be the points from the demand set which are not covered by the first $j$ ellipses, and $(q_{j+1}', \dots, q_m')\in \R^{2(m-j)}$, $(\theta_{j+1}, \dots, \theta_m) \in [0, \pi)^{m-j}$ be the solution returned by the greedy algorithm for the instance $(Z_j, \{w_k \in \Ww: p_k \in Z_j\}, \{(a_{j+1}, b_{j+1}); \dots; (a_m, b_m)\})$ of MCER.
-That is, the instance with demand points that are not covered by the first $j$ ellipses.
-Then, let $OPT_j$ be the value of the best solution for the instance $(\Pp, \Ww, \Rr)$ with the first $j$ ellipses with location fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-Then, we have the following inequality
+Given an instance $(\Pp, \Ww, \Rr)$ of MCER, suppose that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
+Let $Z_j$ be the points that are not covered by the first $j$ ellipses, and $OPT_j$ the value of the best solution with the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
 
+Then, we can obtain an upper-bound for $OPT_j$ by using, for $k\in\{j+1, \dots, m\}$, the solutions $(q_k', \theta_k')$ of MCER for instances with demand set $Z_j$ and only one ellipse with shape parameters $(a_k, b_k)$.
+As these solutions only consider the best cover individually for each ellipse, we have the following inequality
 \begin{equation}
-OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right)
+OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right).
 \end{equation}
-This upper-bound for $OPT_j$ can then be used in the backtracking process to skip solutions that are not better. Let $OPT_{lo}$ be a lower bound for the optimal solution, then the inequality
+This upper-bound for $OPT_j$ can then be used in the backtracking process to skip solutions that are not better than any optimal solution.
+Let $OPT_{lo}$ be a lower bound for the optimal solution, we have that if
 \begin{equation}
@@
 \end{equation}
-defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
-In practice, we can use the value of the best solution found so far by the backtracking process as the lower-bound $OPT_{lo}$.
+then $OPT_j \le OPT_{lo}$, which implies that $OPT_j$ is less than or equal the value of any optimal solution.
+This defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
+In practice, we can use the value of the best solution found so far as the lower-bound $OPT_{lo}$.
 
@@
 
-			\begin{tabular}{|cccc|cr|crrrrr|}
+			\begin{tabular}{|cccc|cr|ccrrrr|}
 				\hline
@@
 This way, most of the points are expected to be near the origin, making optimal solutions cover bigger portions of the demand set when compared to the previously analyzed instances.
-We constructed eight instances with $n=150$ and $m=8$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=a_i\times b_i$, and the weight of every point as $1$.
+We constructed seven instances with $n=100$ and $m=7$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=10 \times a_i\times b_i$, and the weight of every point as its distance to the origin.
+The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta1}.
+
+\begin{table}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|crrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/table_mcek_ta_1.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCE-$k$ for instances TA001-TA007.}
+		\label{tab:mce-results-ta1}
+	\end{center}
+\end{table}
+
+\begin{table}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|ccrrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\# E3P&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/table_mcerk_ta_1.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCER-$k$ for instances TA001-TA007.}
+		\label{tab:mcer-results-ta1}
+	\end{center}
+\end{table}
+
+For the next instances, we kept the number of ellipses at five, and increased the size of the demand set.

### 2020-02-26 defesa/tex/chapter/mcer.tex
wip

@@
 That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse.
-
-This procedure can be defined using the results of \autoref{section:ellipses_intersection}.
+This can be done using the results of \autoref{section:ellipses_intersection}.
 
@@
 Then, in the same way that it is done in \autoref{chapter:mce}, we introduce \autoref{algoritmo:mcer-k} for MCER-$k$ that uses \autoref{algoritmo:mcer} for every $I:=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$.
-Therefore, \autoref{algoritmo:mcer-k} returns an optimal solution for MCER-$k$ in $\bigO(\binom{m}{k}n^{3k}) = \bigO(n^{4m})$ time.
+Therefore, \autoref{algoritmo:mcer-k} returns an optimal solution for MCER-$k$ in $\bigO(\binom{m}{k}n^{3k}) = \bigO(2^mn^{3m})$ time.
 

### 2020-02-26 defesa/tex/chapter/numerical.tex
wip

@@
-The goal of this chapter is to show in practice the results of the algorithms for MCE and MCER proposed by us.
-We first give some implementation details, then we start discuss the solutions obtained for instances proposed in past works, and finally we propose some new instances with the intention of finding the limits of our algorithms.
+The goal of this chapter is to show the results of the algorithms for MCE and MCER proposed by us for instances proposed by other works as well as instances created by us. 
+We also give implementation details and suggestions to improve performance, which we adopted in our implementations.
+All the tables containing results referenced in this chapter are presented in \autoref{chapter:tables}.
 
@@
 
-All the algorithms were implemented using the C++ language, with compiler g++ (G++ 6.3.0).
-To activate the optimization of compilation we used the -O4 flag..
-All the experiments were run in a computer with the following specification:
+All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3. All the experiments were run in a computer with the following specification:
 \begin{itemize}
@@
 In practice, we used the very famous linear algebra package LAPACK (see \citeonline{lapack} for more details).
-LAPACK is a library for the FORTRAN programming language.
-However, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
+Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
 The only remarks, though, are that FORTAN represents matrices in a column-major fashion, and receives parameters only by reference.
@@
 
-\begin{table}[H]\label{tab:zgeev}
+\begin{table}[H]
 	\begin{center}
@@
 	\caption{The ZGEEV's parameter list.}
+	\label{tab:zgeev}
 \end{table}
@@
 Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
-
 Back in \autoref{chapter:e3p}, we were faced with the problem of writing the function $\xi$ defined in \autoref{eq:circumscribed_circle_b} as a complex polynomial in the power format by replacing the sine and cosine functions with the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
@@
 
-\section{A greedy algorithm}
+%\section{A greedy algorithm}
 
-In \citeonline{church:1974}, a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them. 
-Here we introduce a very similar algorithm for both MCE and MCER with the intention of using it in the development of a sufficient condition to skip non-optimal solutions.
+%In \citeonline{church:1974}, a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them. 
+%Here we introduce a very similar algorithm for both MCE and MCER with the intention of using it in the development of a sufficient condition to skip non-optimal solutions.
 
-Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
+%Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
 Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
@@
 Then, we set the solution for the $j$-th ellipse, as the solution of an instance of MCE-1 or MCER-1 with demand points $Z_j$.
-That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
+%That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
 This algorithm can be implemented, such that it takes $\bigO(n^4m)$ operations to construct a solution.
@@
 To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} and \autoref{algoritmo:mcer} had to be done.
-Just translating those algorithms into a programming language was not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
-Therefore, we present here, some improvements that can be applied to the implementation of those algorithms, which can result in a significant improvement in performance, especially in terms of CPU time.
+Just translating those algorithms into a programming language is not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
+Therefore, we present here some improvements that can be applied to the implementation of those algorithms, which can result in significant growth of performance, especially in terms of CPU time.
+
+\subsection{CLS construction}
 
@@
 To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than the ellipse's area, $\pi ab$.
+
+\subsection{Backtracking}
 
@@
 
-In practice, at least for these instances, the bound $\bigO(n^{3m})$ for the algorithm for MCE-$k$ seems to be loose.
-In instance CM9, for example, this bound says that the number of leaves corresponding to a solution in the backtracking tree should be close to $n^{3m} = (10^2)^{3\times 3} = 10^{18}$, which is very far from the actual number of $649$ such leaves obtained in practice.
+In practice, at least for these instances, the bound $\bigO(2^mn^{2m})$ for the algorithm for MCE-$k$ seems to be loose.
+In instance CM9, for example, this bound says that the number of leaves corresponding to a solution in the backtracking tree should be close to $2^mn^{2m} = 2^3(10^2)^{2\times 3} = 8\times10^{12}$, which is very far from the actual number of $649$ such leaves obtained in practice.
 This is also the case for the size of the CLSs, which are all very far away from its $\bigO(n^2)$ bound.
 The greatest CLS size observed was $174$ for instance CM9, which is still very far away from $n^2$, which in this case is $10^4$.
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|crrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
-				\hline
-				\input{tex/table_mcek_cm.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCE-$k$ for instances CM1-CM9.}
-		\label{tab:mce-results-cm}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{0.85\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|crrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-			\multirow{2}{*}{Name} & 
-			\multirow{2}{*}{$n$} & 
-			\multirow{2}{*}{$m$} & 
-			\multirow{2}{*}{$k$} & 
-			Selected & 
-			\multirow{2}{*}{Income} & 
-			CLS size&
-			\multicolumn{2}{c}{Backtracking Tree} & 
-			\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-			& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
-				\hline
-				\input{tex/table_mcek_ab_1.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCE-$k$ for instances AB001-AB060.}
-		\label{tab:mce-results-ab1}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{0.85\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|crrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-\multirow{2}{*}{Name} & 
-\multirow{2}{*}{$n$} & 
-\multirow{2}{*}{$m$} & 
-\multirow{2}{*}{$k$} & 
-Selected & 
-\multirow{2}{*}{Income} & 
-CLS size&
-\multicolumn{2}{c}{Backtracking Tree} & 
-\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol. leaves & CLS-MCE & Total\\
-				\hline
-				\input{tex/table_mcek_ab_2.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCE-$k$ for instances AB061-AB120.}
-		\label{tab:mce-results-ab2}
-	\end{center}
-\end{table}
 
@@
 
-Two methods for MCER-$k$ were developed in \citeonline{andreta}: a deterministic method using global optimization, and a heuristic-stochastic method also using a global optimization, but taking the first found solution as a global optimizer.
-The deterministic method could not find solutions for every instance within a specified time limit, however, comparing with the results of our algorithm, which are displayed in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for isntances AB001-AB120, we could observe that the heuristic method did find an optimal solution for every instance.
+The numerical results obtained by our implementation of \autoref{algoritmo:mcer-k} are shown in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for instances AB001-AB120.
+An optimal solution was obtained for every instance, and overall, at most six seconds of CPU time was taken.
 
-In general, our algorithm took much lower CPU time to return an optimal solution when compared with the heuristic method developed by \citeonline{andreta}.
-For example, for instance, CM9 it ran for more than six hours, while our implementation of \autoref{algoritmo:mcer-k} obtained an optimal solution in less than five seconds.
-One peculiarity that can be observed in the results for these instances is that the time spent in the backtracking phase is always very small, especially if compared to the time spent in the construction of the CLSs.
+Looking at the numerical results of the heuristic method proposed in \citeonline{andreta}, the only non-optimal solutions it encountered were for instances AB105-AB108.
+For these instances, our algorithm obtained an optimal solution covering one more point.
+In \autoref{fig:AB108}, the optimal solution for AB108 is displayed.
+In general, our algorithm took much lower CPU time compared to the methods developed in \citeonline{andreta}.
+For example, for instance CM9, their heuristic method took more than six hours to return a solution, our implementation of \autoref{algoritmo:mcer-k}, on the other hand, obtained an optimal solution in less than five seconds.
+
+\begin{figure}[!htb]
+	\centering
+	\caption{An optimal solution for the instance AB108.}
+	\includegraphics[scale=.5]{tex/figures/AB108}
+	\fautor
+	\label{fig:AB108}
+\end{figure}
 
 As it was said for the results of MCE-$k$, in practice, the bounds for the CLS size and the number of operations taken by the algorithm is very loose.
-Notice that, the greatest CLS size was $701$ obtained for instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
-By \autoref{th:mcer}, for MCER, the bound for the number of computations that \autoref{algoritmo:mcer-k} takes is $\bigO(n^{4m})$.
-In instance AB120, for example, the size of the backtracking tree is only $7102$, which is way lower than $100^{15}$.
-
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|ccrrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\# E3P&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
-
-				%%%
-				%%%
-
-				\hline
-				\input{tex/table_mcerk_cm.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCER-$k$ for instances CM1-CM9.}
-		\label{tab:mcer-results-cm}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|ccrrrr|}
-				\hline
-\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
-\hline
-
-%%% Second line of header
-
-\multirow{2}{*}{Name} & 
-\multirow{2}{*}{$n$} & 
-\multirow{2}{*}{$m$} & 
-\multirow{2}{*}{$k$} & 
-Selected & 
-\multirow{2}{*}{Income} & 
-CLS size&
-\# E3P&
-\multicolumn{2}{c}{Backtracking Tree} & 
-\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
-
-				%%%
-				%%%
-
-				\hline
-				\input{tex/table_mcerk_ab_1.tex}
-				\hline
-
-			\end{tabular}
- 		}
- 	\caption{Solutions of MCER-$k$ for instances AB001-AB060.}
- 	\label{tab:mcer-results-ab1}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|ccrrrr|}
-				\hline
-\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
-\hline
-
-%%% Second line of header
-
-\multirow{2}{*}{Name} & 
-\multirow{2}{*}{$n$} & 
-\multirow{2}{*}{$m$} & 
-\multirow{2}{*}{$k$} & 
-Selected & 
-\multirow{2}{*}{Income} & 
-CLS size&
-\# E3P&
-\multicolumn{2}{c}{Backtracking Tree} & 
-\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
-
-				%%%%
-				%%%%
-
-				\hline
-				\input{tex/table_mcerk_ab_2.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCER-$k$ for instances AB061-AB120.}
-		\label{tab:mcer-results-ab2}
-	\end{center}
-\end{table}
+Notice that, the greatest CLS size was $730$ obtained for the third ellipse in instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
+By \autoref{th:mcer}, for MCER, the bound for the number of computations that \autoref{algoritmo:mcer-k} takes is $\bigO(2^mn^{3m})$.
+In instance AB120, for example, the size of the backtracking tree is only $7102$, which is way lower than $2^5100^{15}$.
 
@@
 
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|crrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\
-
-				%%%%
-				%%%%
-
-				\hline
-				\input{tex/table_mcek_ta_1.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCE-$k$ for instances TA001-TA007.}
-		\label{tab:mce-results-ta1}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|ccrrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\# E3P&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
-
-				%%%%
-				%%%%
-
-				\hline
-				\input{tex/table_mcerk_ta_1.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Solutions of MCER-$k$ for instances TA001-TA007.}
-		\label{tab:mcer-results-ta1}
-	\end{center}
-\end{table}
-
 For the next instances, we kept the number of ellipses at five, and increased the size of the demand set.

### 2020-02-26 defesa/tex/chapter/tables.tex
wip

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
				\hline
				\input{tex/tables/table_mcek_cm.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCE-$k$ for instances CM1-CM9.}
		\label{tab:mce-results-cm}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%
				%%%

				\hline
				\input{tex/tables/table_mcerk_cm.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCER-$k$ for instances CM1-CM9.}
		\label{tab:mcer-results-cm}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{0.85\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
				\hline
				\input{tex/tables/table_mcek_ab_1.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCE-$k$ for instances AB001-AB060.}
		\label{tab:mce-results-ab1}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{0.85\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header
				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol. leaves & CLS-MCE & Total\\
				\hline
				\input{tex/tables/table_mcek_ab_2.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCE-$k$ for instances AB061-AB120.}
		\label{tab:mce-results-ab2}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%
				%%%

				\hline
				\input{tex/tables/table_mcerk_ab_1.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCER-$k$ for instances AB001-AB060.}
		\label{tab:mcer-results-ab1}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tex/tables/table_mcerk_ab_2.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCER-$k$ for instances AB061-AB120.}
		\label{tab:mcer-results-ab2}
	\end{center}
\end{table}

%\section{New instances}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tex/tables/table_mcek_ta_1.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCE-$k$ for instances TA001-TA007.}
		\label{tab:mce-results-ta1}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tex/tables/table_mcerk_ta_1.tex}
				\hline

			\end{tabular}
		}
		\caption{Solutions of MCER-$k$ for instances TA001-TA007.}
		\label{tab:mcer-results-ta1}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
	\hline
	\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
	\hline

	%%% Second line of header

	\multirow{2}{*}{Name} & 
	\multirow{2}{*}{$n$} & 
	\multirow{2}{*}{$m$} & 
	\multirow{2}{*}{$k$} & 
	Selected & 
	\multirow{2}{*}{Income} & 
	CLS size&
	\multicolumn{2}{c}{Backtracking Tree} & 
	\multicolumn{2}{c|}{\centering CPU Time (s)}\\
	& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\

	%%%%
	%%%%

				%%%%
				%%%%

				\hline
				\input{tex/tables/table_mcek_ta_2.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Solutions of MCER-$k$ for instances TA008-TA013.}

		\label{tab:mce-results-ta2}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tex/tables/table_mcerk_ta_2.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Solutions of MCER-$k$ for instances TA008-TA013.}

		\label{tab:mcer-results-ta2}
	\end{center}
\end{table}

### 2020-02-29 defesa/tex/chapter/future.tex
wip

@@
-To take advantage of the great amount of work found in the literature,
- we decided to first introduce the planar maximal covering by disks problem, develop a method for it, and just then adapt it for the ellipses case.
-It turned out that because of the similarities between the two problems, adapting was possible and actually very simple.
-This made the method developed by us have a very different approach than the ones in \cite{andreta} and \cite{canbolat}.
-The next step is to implement it and compare the results that \cite{andreta} obtained.
+In this work, we studied two problems of maximum planar covering using ellipses, with most of the substantial results being for the less previously-studied problem where the ellipses can be freely rotated, which we referred to as MCER.
+We devoted \autoref{chapter:e3p} and \autoref{chapter:mcer} of our work for the development of an exact algorithm for this problem, which depended on the development of an algorithm for a never-studied-before geometric subproblem, which we referred to as E3P.
 
-For the next step of our master's research we set the following objectives as primary:
+An exact algorithm was also developed for the other problem studied in this work, which the ellipse could not be rotated.
+We created an algorithm for it in \autoref{chapter:mce} based on an algorithm for maximum covering using disks, which we introduced in \autoref{chapter:pmclp}.
 
-\begin{itemize}
-    \item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.
+In \autoref{chapter:numerical}, numerical experiments were run for both algorithms.
+We first used instances found in the literature, and then proposed new instances to further analyze the performance of our algorithms.
+Even though the exponential nature of both algorithms proposed by us, 
+in \autoref{chapter:numerical}, we gave several improvements suggestions, which allowed our implementations to obtain optimal solutions for every previously published instance, including instances that no optimal solutions were obtained before, plus some fairly large new ones.
 
-    \item Develop an exact method for the version of the problem introduced in \cite{andreta} where the ellipses can be freely rotated.
-
-\end{itemize}
-
-The following goals are set as secondary:
-
-\begin{itemize}
-    \item Develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions.
-The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse.
-The case with more than one ellipse is left as a challenge for us for the next steps of our research.
-
-    \item In \cite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity.
-We want to generalize this for the elliptical distance function and achieve a better run-time complexity.
-We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.
-\end{itemize}
-
-%Also, the version of the problem where every ellipse can be freely rotated is set as a primary goal for this master's research.
-In \cite{andreta}, the deterministic method developed by them could not obtain solutions for moderate-to-large instances within reasonable time.
-Because of that, a stochastic global optimization method was proposed, it performed well and was able to obtain an optimal solution for small cases.
-The goal we have in mind for the future is to develop an exact method that takes into consideration the algorithm we developed for the axis-parallel version of the problem and compare the results.
-
-%Finally, as a secondary goal, we want to
+We believe there is plenty of room for furtherly working on these problems.
+Back in \autoref{chapter:e3p}, we raised the attention for some possible properties which could be used in the development of an improved version of our algorithm for E3P.
+In \autoref{chapter:numerical}, we observed that the bounds for the algorithms proposed by us might be a little loose, obtaining tighter bounds might be possible.
+Some other suggestions for future work are: modeling the problems as Linear Integer Programming problems, which could be an alternative to backtracking the optimal solution, done in the algorithms for both problems; adapting the probabilistic  approximation algorithm for the maximum covering by disks problem developed in \citeonline{cabello:2006} for the ellipses case; and developing and analyzing heuristics which avoid the backtracking phase of both algorithms.

### 2020-02-29 defesa/tex/chapter/mcer.tex
wip

@@
 \end{algoritmo}
-
-\subsection{Improvements and implementation details}
-
-Some improvements can be made in the implementation of \autoref{algoritmo:mcer}.
-Instead of calling procedure CLS-MCER every time in the backtracking routine, it is suggested that it is done outside in a pre-processing phase.
-
-Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER.
-If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, solution $(Q', \Theta')$ can be dismissed.
-This can be done in the CLS-MCER procedure in \autoref{algoritmo:mcer1}.
-
-In our implementation we use the same approach used in \citeonline{andreta}.
-When constructing the CLS for the $j$-th ellipse, a tree-like data structure is utilized to verify if a solution $(q, \theta)$ covers a subset of another solution or not.
-
-Keeping an upper-bound for the solution during the backtracking in \autoref{algoritmo:mcer} can also provide a good improvement in practice.
-Let $z_j = \max_{(q, \theta) \in S_j} w(\Pp \cap E_j(q, \theta))$, and $OPT$ the value of an optimal solution.
-When the algorithm chooses $(q_j, \theta_j) \in S_j$ as the solution for the $j$-th ellipse, we have
-
-\begin{equation}
-OPT \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + \sum_{k=j+1}^m z_k.
-\end{equation}
-This upper-bound is easy to compute as $\{z_1, \dots, z_m\}$ can be pre-processed, and the weight of every point covered so far in the backtrack can be obtained by adding another parameter to the $MCER$ procedure.
-
-In the next chapter, we present the results of numerical experiments for MCER and MCER-$k$ and compare them with the results published in \citeonline{andreta}.

### 2020-02-29 defesa/tex/chapter/numerical.tex
wip

@@
-The goal of this chapter is to show the results of the algorithms for MCE and MCER proposed by us for instances proposed by other works as well as instances created by us. 
+The goal of this chapter is to show the results of the algorithms for MCE-$k$ and MCER-$k$ proposed by us for instances proposed by other works as well as instances created by us. 
 We also give implementation details and suggestions to improve performance, which we adopted in our implementations.
-All the tables containing results referenced in this chapter are presented in \autoref{chapter:tables}.
 
@@
 \end{itemize}
+
 \subsection{Determining the eigenvalues of a matrix}
@@
 Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
-The only remarks, though, are that FORTAN represents matrices in a column-major fashion, and receives parameters only by reference.
+The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference.
 Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.
@@
 ZGEEV receives in total $14$ parameters, with $4$ of them being used for output.
-We show a brief description of them in \autoref{tab:zgeev} along with the specification of the value we set each parameter in our implementation.
+We show a brief description of them in \autoref{tab:zgeev}, along with the specification of the value we set each parameter in our implementation.
 %\renewcommand{\arraystretch}{1.1}
@@
 	\begin{center}
+				\resizebox{\textwidth}{!}{%
 	\begin{tabular}{|c|m{18em}|m{8em}|}
@@
 	\end{tabular}
+}
 	\end{center}
@@
 
-\subsection{Symbolic Computation}
+\subsection{Symbolic computation}
 
 Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
-Back in \autoref{chapter:e3p}, we were faced with the problem of writing the function $\xi$ defined in \autoref{eq:circumscribed_circle_b} as a complex polynomial in the power format by replacing the sine and cosine functions with the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
+Back in \autoref{chapter:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:circumscribed_circle_b} as a complex polynomial in the power format by replacing the sine and cosine functions with the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
 
@@
 Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++ implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.
+The actual coefficients of that polynomial are presented in \autoref{chapter:poly} in terms of a generic E3P's instance.
 
@@
 To avoid this unnecessary computation, we compute the CLS for every ellipse beforehand in a preprocessing phase for the whole demand set.
-Then, in the backtracking, we only consider the options of locations that makes the ellipse cover points that have not been covered before.
+Then, in the backtracking, we only consider the options of locations that makes the ellipse cover at least one point that has not been covered before.
 
@@
 If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, then we can for sure dismiss solution $(Q', \Theta')$.
-In our implementation, we use the same tree-like data structure as the one described by \citeonline{andreta} to only keep solutions that are not redundant.
+In our implementation, we use the same tree-like data structure as the one described in \citeonline{andreta} to only keep solutions that are not redundant.
 
 Calling \autoref{algoritmo:e3p} for E3P for every triplet of points in an instance of MCER can be expensive.
-To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than the ellipse's area, $\pi ab$.
+To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.
 
@@
 
-Without any improvement, backtracking through every possible combination in the CLS of every ellipse can take a very long time, while most of those combinations are easy-to-spot non-optimal solutions.
-Because of that, we introduce a sufficient condition, based on the algorithm for only one ellipse, which can be used to skip solutions that for sure are non-optimal.
-We are going to do that for the MCER's case (the MCE's case is analogous).
+Without any improvement, backtracking through every possible combination of every ellipse's CLS can take a very long time, possibly going through a lot of non-optimal solutions. 
+For this reason, we introduce a sufficient condition for the MCER's case (the MCE's case is analogous), based on MCER for one ellipse, which can be used to skip solutions that for sure are non-optimal.
 
-Given an instance $(\Pp, \Ww, \Rr)$ of MCER, suppose that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
-Let $Z_j$ be the points that are not covered by the first $j$ ellipses, and $OPT_j$ the value of the best solution with the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
+Given an instance $(\Pp, \Ww, \Rr)$ of MCER, suppose that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+Let $Z_j$ be the points that are not covered by the first $j$ ellipses, and $OPT_j$ the value of the best solution with the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
 
@@
 then $OPT_j \le OPT_{lo}$, which implies that $OPT_j$ is less than or equal the value of any optimal solution.
-This defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_m, \theta_m)$.
-In practice, we can use the value of the best solution found so far as the lower-bound $OPT_{lo}$.
+This defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+In practice, we can use the value of the best solution found so far as the lower-bound for the optimal solution.
 
@@
 For example, without taking the suggestion given by \autoref{eq:upper-bound}, \autoref{algoritmo:mcer-k} takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions.
-In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for the instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
+In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
 
@@
 
-In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for the instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for the instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
+In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
 
@@
 For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
+All the tables containing results referenced in this section are presented in \autoref{chapter:tables}.
+We also made available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/} every instance used here, along with the graphical representation of every obtained solution.
 
@@
 	\centering
-	\caption{An optimal solution for the instance AB108.}
-	\includegraphics[scale=.5]{tex/figures/AB108}
+	\caption{An optimal solution of MCER-$k$ for the instance AB108.}
+	\includegraphics[scale=.8]{tex/figures/AB108}
 	\fautor
@@
 
-\section{Other instances}
+\section{New instances}
 
-In this section, we describe some new instances which were created with the intention of further analyzing the algorithms developed by our work.
+After examining the results obtained by our algorithms for the formerly known instances, constructing new ones, more challenging for our work, can be taken as essential for further analyzing the algorithms proposed by us.
+Besides increasing the size of the demand set and the number of ellipses, we also designed instances with non-unitary weights, which is something none of the previous instances had. 
+Moreover, to create very distinct instances from the previously introduced ones, we used a different probability distribution, other than the uniform one, to generate the location of points.
+We set a time limit of two hours of running time for solving every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
+In total, we designed 46 new instances, which will be referred to as TA01, \dots, TA46, and are available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
+The numerical results for every one of them are displayed in \autoref{chapter:tables}.
 
-To generate the demand set, for each point, we had its coordinates follow a normal distribution $\mathcal{N}(0, 1)$.
-This way, most of the points are expected to be near the origin, making optimal solutions cover bigger portions of the demand set when compared to the previously analyzed instances.
-We constructed seven instances with $n=100$ and $m=7$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=10 \times a_i\times b_i$, and the weight of every point as its distance to the origin.
+The first set of instances were construct sampling each demand points from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
+This is expected to produce a demand set with most points located near the origin, but with the most valuable points located far away from it.
+We generated a set of $n=100$ points, with $m=7$ ellipses, making the $j$-th ellipse have shape parameters randomly taken from a uniform distribution in $[0.5, 1.5]$, and cost $c_j=10\times a_j \times b_j$.
+From that, we created seven instances taking $k \in \{1, \dots, m\}$.
 The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta1}.
+Because the normal distribution generates most of the points close to each other (see \autoref{fig:TA004} for an example), every ellipse's CLS's size ended up being significantly bigger if compared to previously introduced instances with $100$ points.
+This, and the subtle increase in the number of ellipses, made the algorithms for MCER-$k$ and MCE-$k$ time out for some instances.
+The algorithm for MCER-$k$ did not return an optimal solution within the predefined time limit for the last three instances ($k=5, 6, 7)$, while the algorithm for MCE-$k$ did not finish in time for the last instance ($k=7$).
+The optimal solution for MCER-$k$ for the instance with $k=4$ is displayed in \autoref{fig:TA004}.
 
-For the next instances, we kept the number of ellipses at five, and increased the size of the demand set.
+\begin{figure}[H]
+	\centering
+	\caption{An optimal solution of MCER-$k$ for the instance TA04.}
+	\includegraphics[scale=.8]{tex/figures/TA004}
+	\fautor
+	\label{fig:TA004}
+\end{figure}
+
+For the second set of instances, we used the same process used for the first set to generate the demand points and the ellipses.
+We kept the number of ellipses at $3$ and created five demand sets with $n\in\{200, 250, 300, 350, 400\}$.
+In total, we had $15$ instances having $k\in\{1, \dots, m\}$.
+The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta2} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta2}.
+The solution of MCER-$k$ for the instance with $n=400$, and $k=2$ is shown in \autoref{fig:TA021}.
+
+\begin{figure}[H]
+	\centering
+	\caption{An optimal solution of MCER-$k$ for the instance TA21.}
+	\includegraphics[scale=.8]{tex/figures/TA021}
+	\fautor
+	\label{fig:TA021}
+\end{figure}
+
+The third set of instances were constructed generating the demand set following a uniform distribution in $[0, 10]^2$, with each point having unitary weight; and the ellipses by the same process used for the first two set of instances.
+We created instances with $m=5$, $n\in \{400, 450, 500\}$, and $k\in\{1, \dots, m\}$, with a total of $15$ instances.
+The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta3} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta3}.
+Optimal solutions were obtained for every one of the instances in this set.
+It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
+The optimal solution of MCER-$k$ returned by \autoref{algoritmo:mcer-k} for the instance with $n=500$ and $k=5$ is shown in \autoref{fig:TA037}.
+
+\begin{figure}[!htb]
+	\centering
+	\caption{An optimal solution of MCER-$k$ for the instance TA37.}
+	\includegraphics[scale=.8]{tex/figures/TA037}
+	\fautor
+	\label{fig:TA037}
+\end{figure}
+
+The last set of instances were constructed using two bivariate normal distributions with unitary variance $\mathcal{N}(\mu^{(1)}, \mathbb{I})$ and $\mathcal{N}(\mu^{(2)}, \mathbb{I})$, $\mu^{(1)}, \mu^{(2)} \in \R^2$.
+Half of the points were generated following $\mathcal{N}(\mu^{(1)}, \mathbb{I})$, and the other half $\mathcal{N}(\mu^{(2)}, \mathbb{I})$; the weight of every point was set as its squared distance to the mean of the distribution from which it was generated.
+The ellipses were also divided into two halves, taking their shape parameters from uniform distributions in the intervals $[0.5, 1.5]$, and $[3, 4]$; setting the $j$-th ellipse's weight as $c_j=a_j \times b_j$.
+The purpose of this last set of instances was to create an example where the chosen ellipses in the solution of an instance of MCER-$k$ is not a subset of the chosen ellipses in an optimal solution of that same instance for MCER-$(k+1)$.
+We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$, and defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such counter-example.
+The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mce-results-ta4} for MCER-$k$.
+In \autoref{fig:TA44-45}, we show the solutions for the instances with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
+
+\begin{figure}[!htb]
+	\caption{Optimal solutions for instances TA44 and TA45.}
+	\begin{subfigure}{.5\textwidth}
+			\centering
+		\caption{TA44}
+		\includegraphics[scale=.6]{tex/figures/TA044}
+
+		%\fautor
+		\label{fig:TA043}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+			\centering
+		\caption{TA45}
+		\includegraphics[scale=.6]{tex/figures/TA045}
+		%\fautor
+		\label{fig:TA044}
+	\end{subfigure}
+\label{fig:TA44-45}
+	\fautor
+\end{figure}

### 2020-02-29 defesa/tex/chapter/tables.tex
wip

@@
 		}
-		\caption{Solutions of MCER-$k$ for instances TA008-TA013.}
+		\caption{Solutions of MCE-$k$ for instances TA008-TA022.}
 
@@
 		}
-		\caption{Solutions of MCER-$k$ for instances TA008-TA013.}
+		\caption{Solutions of MCER-$k$ for instances TA008-TA022.}
 
@@
 \end{table}
+
+\begin{table}[!htb]
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|crrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/tables/table_mcek_ta_4.tex}
+				\hline
+				%\input{tex/tables/table_mcerk_ta_3.tex}
+				%\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCE-$k$ for instances TA008-TA022.}
+
+		\label{tab:mce-results-ta3}
+	\end{center}
+\end{table}
+
+\begin{table}[!htb]
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|ccrrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\# E3P&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/tables/table_mcerk_ta_4.tex}
+				\hline
+				%\input{tex/tables/table_mcerk_ta_3.tex}
+				%\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCER-$k$ for instances TA008-TA022.}
+
+		\label{tab:mcer-results-ta3}
+	\end{center}
+\end{table}
+
+\begin{table}[!htb]
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|crrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/tables/table_mcek_ta_5.tex}
+				\hline
+				%\input{tex/tables/table_mcerk_ta_3.tex}
+				%\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCE-$k$ for instances TA008-TA022.}
+
+		\label{tab:mce-results-ta4}
+	\end{center}
+\end{table}
+
+\begin{table}[!htb]
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|ccrrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\# E3P&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+
+				%%%%
+				%%%%
+
+				\hline
+				\input{tex/tables/table_mcerk_ta_5.tex}
+				\hline
+				%\input{tex/tables/table_mcerk_ta_3.tex}
+				%\hline
+
+			\end{tabular}
+		}
+		\caption{Solutions of MCER-$k$ for instances TA008-TA022.}
+
+		\label{tab:mcer-results-ta4}
+	\end{center}
+\end{table}

### 2020-03-01 defesa/tex/chapter/introducao.tex
wip

@@
 Unlike its predecessor, this version of the problem was not defined on graphs.
-Instead, on PMCLP the demand set and the facilities are located in $\R^2$ and a facility's coverage area is determined by a distance function.
+Instead, on PMCLP, the demand set and the facilities are located in $\R^2$, and a facility's coverage area is determined by a distance function.
 Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
@@
 
-Two versions of PMCLP are studied in this work, both of them related to ellipses.
-The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximal Covering by Ellipses}.
-This version does not allow the ellipses to rotate, so basically it only differs from its disks counterpart in the shape of the facility's coverage area.
-The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximal Covering by Ellipses with Rotation}.
-This version of the problem had no restriction on the rotation of ellipses--note that this is a slightly bigger modification of PMCLP compared to the first one, as not only the location for the facilities must be determined, but also their angle of rotation.
-The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.
+We study two versions of PMCLP with elliptical coverage facilities in this work.
+For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
+In the first version, introduced in \citeonline{canbolat}, all the facilities are axis-parallel ellipses making this problem be a slightly modified MCD.
+Throughout this work, we will refer to this version of the problem as \sigla{MCE}{Maximum Cover by Ellipses}.
+In the second version, introduced in \citeonline{andreta}, an angle of rotation is also part of each ellipse's location, making the problem much more challenging.
+This version of the problem will be referred to as \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.
 
-Only two articles have been found published in the literature that study this problem.
+The main practical motivation to study these two versions of PMCLP is that cellphone towers can have an elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.
+
+It is fair to say that PMCLP with elliptical coverage has not been studied a lot as only two articles have been found on it.
 In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
 For some instances, the method took too long and did not find an optimal solution.
-For this reason, a heuristic method was developed using a technique called Simulated Annealing.
-Solutions for the instances that timed-out with the first method were then obtained.
-The problem was further explored in \citeonline{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances, which the first method could not.
-Also, in \citeonline{andreta}, the version of the problem where the ellipses could be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances; and a heuristic method were proposed for it.
-Despite the similarities, none of the works cited above base their development on the maximum covering by disks algorithms found in the literature.
+Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
+The problem was further explored in \citeonline{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \citeonline{canbolat} could not.
+The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though, returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.
 
-The main results of this work are found in \autoref{chapter:ellipses_n} where a new algorithm for the version of the elliptical PMCLP where the ellipses can be freely rotated is developed.
-The proposed algorithm has a runtime complexity of $\bigO(n^{3m})$ and one of its most important steps is finding every solution of a not-previously-known problem.
-In \autoref{chapter:e3p}, this problem is introduced and an algorithm for it is presented.
-The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work.
-Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.
+The main results of this work are presented in \autoref{chapter:mcer}, where a new algorithm for MCER is developed. 
+In the numerical experiments displayed in \autoref{chapter:numerical}, this algorithm shoed very good performance and even obtained optimal solutions for instances that the heuristic method proposed in \citeonline{andreta} reported non-optimal ones.
+In the development of the algorithm for MCER in \autoref{chapter:mcer}, a subproblem in which no prior study could be found surged.
+The whole \autoref{chapter:e3p} is devoted to the creation of an algorithm for that problem.
+The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work.

### 2020-03-01 defesa/tex/chapter/mcd.tex
wip

@@
 Then, with \autoref{algoritmo:mcd_cls}, an algorithm for MCD that checks every possible center for every disk yields a $\bigO(n^{2m})$ run-time complexity.
-This algorithm is described in \autoref{chapter:ellipses} for the axis-parallel ellipses case.
+This algorithm is described in \autoref{chapter:mce} for the axis-parallel ellipses case.
 
@@
 \begin{algoritmo}
-	\caption{Algorithm for MCD1 that returns a CLS.}\label{algoritmo:mcd_cls}
+	\caption{Algorithm for that returns a CLS given a radius and a demand set.}\label{algoritmo:mcd_cls}
 	\begin{algorithmic}[1]

### 2020-03-02 defesa/tex/chapter/e3p.tex
wip

@@
 Therefore, every odd degree coefficients of $h$ must be zero and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$ as follows
-\begin{equation}
+\begin{equation}\label{eq:poly_f}
 f(y) = \sum_{k=0}^{6} c_{2k} y^k.
@@
 \begin{algoritmo}
-	\caption{The algorithm for E3P.}\label{algoritmo:e3p}
+	\caption{Algorithm for E3P.}\label{algoritmo:e3p}
 	\begin{algorithmic}[1]
@@
 \begin{proof}
-	It has already been shown in \autoref{section:transforming-the-problem} that computing every root of $\xi$ through the complex polynomial yields every solution of E3P.
+	It has already been shown in Section~\ref{section:transforming-the-problem} that computing every root of $\xi$ through the complex polynomial yields every solution of E3P.
 The only thing left to prove is the running time of the algorithm.

### 2020-03-02 defesa/tex/chapter/future.tex
wip

@@
 In \autoref{chapter:numerical}, we observed that the bounds for the algorithms proposed by us might be a little loose, obtaining tighter bounds might be possible.
-Some other suggestions for future work are: modeling the problems as Linear Integer Programming problems, which could be an alternative to backtracking the optimal solution, done in the algorithms for both problems; adapting the probabilistic  approximation algorithm for the maximum covering by disks problem developed in \citeonline{cabello:2006} for the ellipses case; and developing and analyzing heuristics which avoid the backtracking phase of both algorithms.
+Some other suggestions for future work are: modeling the problems as Linear Integer Programming problems, which could be an alternative to backtracking the optimal solution, done in the algorithms for both problems; adapting the  approximation algorithm for the maximum covering by disks problem developed in \citeonline{cabello:2006} for the ellipses case; and developing and analyzing heuristics which avoid the backtracking phase of both algorithms.

### 2020-03-02 defesa/tex/chapter/introducao.tex
wip

@@
 
-In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced.
+In \citeonline{church:1984}, a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced.
 Unlike its predecessor, this version of the problem was not defined on graphs.
 Instead, on PMCLP, the demand set and the facilities are located in $\R^2$, and a facility's coverage area is determined by a distance function.
-Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
-This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found.
+Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert an instance of PMCLP into an instance of MCLP, and then utilize any of the previous developed exact methods to obtain a solution for PMCLP.
+This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set}, which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found.
 From the CLS, a network was built on which MCLP could be applied.
@@
 
-Furthermore, some variations of PMCLP can also be found in the literature: in \citeonline{younies} PMCLP was studied under the block norm distance, in \citeonline{mumtaz} a mean-shift algorithm for large scale\footnote{Numerical experiments were done for up to $3000$ points.} PMCLP was proposed, and in \citeonline{bansal} a version with partial coverage and rectangular demand and facility zones was introduced.
+Furthermore, some variations of PMCLP can also be found in the literature: in \citeonline{younies}, PMCLP was studied under the block norm distance; in \citeonline{mumtaz}, a mean-shift algorithm for large scale\footnote{Numerical experiments were done for up to $3000$ points.} PMCLP was proposed; and in \citeonline{bansal} a version with partial coverage and rectangular demand and facility zones was introduced.
 
@@
 Early works only tackled the one-disk version of it.
-In \citeonline{chazelle:1986} a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
-The $m$ disks version of MCD was studied in \citeonline{cabello:2006} which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
+In \citeonline{chazelle:1986}, a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
+The $m$ disks version of MCD was studied in \citeonline{cabello:2006}, which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
 To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
-Additionally, in \citeonline{aronov:2008} one-disk maximum covering is proven to be 3SUM-HARD.
+Additionally, in \citeonline{aronov:2008}, one-disk maximum covering is proven to be 3SUM-HARD.
 This means that maximizing the number of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.
@@
 For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
-In the first version, introduced in \citeonline{canbolat}, all the facilities are axis-parallel ellipses making this problem be a slightly modified MCD.
-Throughout this work, we will refer to this version of the problem as \sigla{MCE}{Maximum Cover by Ellipses}.
-In the second version, introduced in \citeonline{andreta}, an angle of rotation is also part of each ellipse's location, making the problem much more challenging.
-This version of the problem will be referred to as \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.
+In the first version, introduced in \citeonline{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \citeonline{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
+The first version will be referred to as \sigla{MCE}{Maximum Cover by Ellipses} and the second one as  \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.
 
-The main practical motivation to study these two versions of PMCLP is that cellphone towers can have an elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.
+The main practical motivation to study these two versions of PMCLP is that cellphone towers can have an elliptically shaped coverage area.
+Then, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.
 
-It is fair to say that PMCLP with elliptical coverage has not been studied a lot as only two articles have been found on it.
+It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
 In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
@@
 
-The main results of this work are presented in \autoref{chapter:mcer}, where a new algorithm for MCER is developed. 
-In the numerical experiments displayed in \autoref{chapter:numerical}, this algorithm shoed very good performance and even obtained optimal solutions for instances that the heuristic method proposed in \citeonline{andreta} reported non-optimal ones.
-In the development of the algorithm for MCER in \autoref{chapter:mcer}, a subproblem in which no prior study could be found surged.
-The whole \autoref{chapter:e3p} is devoted to the creation of an algorithm for that problem.
-The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work.
+The main results of this work are presented in \autoref{chapter:e3p} and  \autoref{chapter:mcer}. 
+In \autoref{chapter:e3p}, we introduce a new geometry problem and propose an algorithm for it.
+In \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to proposed a new algorithm for MCER.
+This new algorithm is proved to have a runtime complexity of $\bigO(mn^{3m+1})$, and in \autoref{chapter:numerical}, we analyze several numerical experiments to show its effectiveness and compare it to methods of previous works.
+The rest of our work is structured in the following way: In \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.

### 2020-03-02 defesa/tex/chapter/mcd.tex
wip

@@
 	Suppose that an instance of MCD and an index $j\in\{1, \dots, m\}$ are given.
-	Then \autoref{algoritmo:mcd_cls}, when given the instance $(\Pp, \Ww, r_j)$ as input, returns a CLS $S_j$ of size $\bigO(n^2)$, such that $q^*_j\in S_j$, with $(q^*_1, \dots, q^*_m)$ being an optimal solution of the given MCD's instance.
+	Then \autoref{algoritmo:mcd_cls}, when given the instance $(\Pp, \Ww, r_j)$ as input, returns a CLS $S_j$ of size less than or equal to $n^2$, such that $q^*_j\in S_j$, with $(q^*_1, \dots, q^*_m)$ being an optimal solution of the given MCD's instance.
 \end{lema}
@@
 It can be seen that in any solution of MCD, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_cls} as a candidate to be an optimal solution.
-The number of points \autoref{algoritmo:mcd_cls} goes through is $\bigO(n^2)$, then
-obviously $|S_j|=\bigO(n^2)$.
+We have that the number of opening angles that CLS-MCD goes through is greater than or equal to $|S_j|$, then
+\begin{eqnarray*}
+|S_j| \le \binom{n}{1} + \binom{n}{2} = \dfrac{n^2 + n}{2} \le n^2
+\end{eqnarray*}
 \end{proof}
 
-Then, with \autoref{algoritmo:mcd_cls}, an algorithm for MCD that checks every possible center for every disk yields a $\bigO(n^{2m})$ run-time complexity.
+Then, with \autoref{algoritmo:mcd_cls}, an algorithm for MCD that checks every possible center for every disk can be implemented with a $\bigO(mn^{2m+1})$ run-time complexity.
 This algorithm is described in \autoref{chapter:mce} for the axis-parallel ellipses case.
@@
 \begin{algoritmo}
-	\caption{Algorithm for that returns a CLS given a radius and a demand set.}\label{algoritmo:mcd_cls}
+	\caption{Algorithm that returns a CLS for a disk.}\label{algoritmo:mcd_cls}
 	\begin{algorithmic}[1]

### 2020-03-02 defesa/tex/chapter/mce.tex
wip

@@
 This strategy is backed-up by \autoref{lema:mcd}, which says that there is an optimal solution in the CLS of each ellipse.
-Following this, counting every possibility that the algorithm goes through, we arrive at the run-time complexity of $\bigO(n^{2m})$.
+Following this, counting every possibility that the algorithm goes through, an algorithm with run-time complexity of $\bigO(mn^{2m + 1})$ can be implemented.
 
@@
 After that, by keeping track of the utilized ellipses' costs for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
-This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k}) = \bigO(n^{3m})$.
+This simple adjustment achieves a run-time complexity of $\bigO(k\binom{m}{k} \times n^{2k}) = \bigO(m2^mn^{2m+1})$.
 

### 2020-03-02 defesa/tex/chapter/mcer.tex
wip

@@
 	\end{equation*}
-Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
+Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|\le n^{3m}$.
 \end{theorem}
@@
 It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega(\Pp, \Ww, \Rr)$ every solution that has an ellipse centered at a point from $\Pp$.
-From that, we can also conclude that $|S_j^{(1)}| = n$.
+From that, we can also conclude that $|S_j^{(1)}| \le n$.
 
@@
 	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
-	Moreover, in \autoref{section:ellipses_intersection}, we discuss the problem of determining the intersections between two ellipses.
+	Moreover, in Section~\ref{section:ellipses_intersection}, we discuss the problem of determining the intersections between two ellipses.
 This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
 In \autoref{section:ellipses_intersection}, it is shown that this problem has at most two solutions.
-Therefore, we have that $|S_j^{(2)}| = 2\binom{n}{2}$.
+Therefore, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
 
@@
 Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse contain three given points is at most six.
-Therefore, we have that $|S_j^{(3)}| = 6\binom{n}{3}$.
+Therefore, we have that $|S_j^{(3)}| \le 6\binom{n}{3}$.
 
-	Finally, as $|S_j| \le |S_j^{(1)}| +  |S_j^{(2)}| +  |S_j^{(3)}| = \bigO(n^{3})$, it follows that $|\Omega(\Pp, \Ww, \Rr)| = |S_1|\times \dots \times |S_m| = \bigO(n^{3m})$.
+	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound
+	\begin{eqnarray*}
+	|S_j| &\le 6\binom{n}{3} + 2\binom{n}{2} + n &= n(n-1)(n-2) + n(n-1) + n\\
+	|S_j| &\le 6\binom{n}{3} + 2\binom{n}{2} + n &= n((n-1)^2+1) \le n^3.
+	\end{eqnarray*}	
+	Therefore, we conclude that  $|\Omega(\Pp, \Ww, \Rr)| \le |S_1|\times \dots \times |S_m| \le n^{3m}$.
 \end{proof}
@@
 That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse.
-This can be done using the results of \autoref{section:ellipses_intersection}.
+This can be done using the results of Section~\ref{section:ellipses_intersection}.
 
 \begin{algoritmo}
-	\caption{An algorithm that constructs a CLS for a given ellipse.}\label{algoritmo:mcer1}
+	\caption{Algorithm that constructs a CLS for an ellipse.}\label{algoritmo:mcer1}
 	\begin{algorithmic}[1]
@@
 \begin{corolario}
-	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ operations and returns an optimal solution for an instance of MCER.
+	\autoref{algoritmo:mcer} takes $\bigO(mn^{3m+1})$ operations and returns an optimal solution for an instance of MCER.
 \end{corolario}
@@
 Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
-As evaluating each solution can be done in $\bigO(n)$, we get the overall runtime complexity of $\bigO(n^{3m+1})$ which is $\bigO(n^{3m})$.
+As evaluating each solution can be done in $\bigO(nm)$, we get the overall runtime complexity of $\bigO(mn^{3m+1})$.
 \end{proof}
@@
 	\centering
-	\caption{An optimal solution for the instance AB120.}
-	\includegraphics[scale=.5]{tex/figures/AB120}
+	\caption{An optimal solution of MCER-$k$ for the instance AB120.}
+	\includegraphics[scale=.8]{tex/figures/AB120}
 	\fautor
@@
 Then, in the same way that it is done in \autoref{chapter:mce}, we introduce \autoref{algoritmo:mcer-k} for MCER-$k$ that uses \autoref{algoritmo:mcer} for every $I:=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$.
-Therefore, \autoref{algoritmo:mcer-k} returns an optimal solution for MCER-$k$ in $\bigO(\binom{m}{k}n^{3k}) = \bigO(2^mn^{3m})$ time.
+Therefore, \autoref{algoritmo:mcer-k} returns an optimal solution for MCER-$k$ in $\bigO(k\binom{m}{k}n^{3k+1}) = \bigO(m2^mn^{3m+1})$ time.
 

### 2020-03-02 defesa/tex/chapter/numerical.tex
wip

@@
 the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
-For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
+For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in Section~\ref{section:improvements}.
 All the tables containing results referenced in this section are presented in \autoref{chapter:tables}.
@@
 
-In practice, at least for these instances, the bound $\bigO(2^mn^{2m})$ for the algorithm for MCE-$k$ seems to be loose.
-In instance CM9, for example, this bound says that the number of leaves corresponding to a solution in the backtracking tree should be close to $2^mn^{2m} = 2^3(10^2)^{2\times 3} = 8\times10^{12}$, which is very far from the actual number of $649$ such leaves obtained in practice.
-This is also the case for the size of the CLSs, which are all very far away from its $\bigO(n^2)$ bound.
-The greatest CLS size observed was $174$ for instance CM9, which is still very far away from $n^2$, which in this case is $10^4$.
+Back in \autoref{chapter:mce}, it was shown that the size of a CLS in an instance of MCE is less than or equal $n^2$.
+This bound, at least for these instances, seems to be very loose.
+Notice that the biggest CLS observed, which is $174$ in instance CM9, is very far away from $n^2$, which in this case is $10^4$.
+The same can be said about the bound for the running time of the algorithm, using the size of the backtracking tree times $n$ (the number of steps needed to evaluate an option in a CLS) as an estimate for the number of computations, it can be seen that the asymptotic bound of $\bigO(m2^mn^{2m+1})$ is very far from the actual number of computations.
 
@@
 As it was said for the results of MCE-$k$, in practice, the bounds for the CLS size and the number of operations taken by the algorithm is very loose.
-Notice that, the greatest CLS size was $730$ obtained for the third ellipse in instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
-By \autoref{th:mcer}, for MCER, the bound for the number of computations that \autoref{algoritmo:mcer-k} takes is $\bigO(2^mn^{3m})$.
-In instance AB120, for example, the size of the backtracking tree is only $7102$, which is way lower than $2^5100^{15}$.
+Notice that, the greatest CLS size was $730$ obtained for the third ellipse in instances CM7-CM9. Notice that $730$ is very distance from its upper-bound $n^3$, which in this case is $10^6$.
+Also, looking at the size of the backtracking tree times $n$ as an estimate for the number of computations taken by the algorithm, for example, for instance AB120, this number is $1579 \times 100$, which is very distant from its asymptotic upper-bound of $\bigO(m2^mn^{3m+1})$, which in this case would be $5\times 2^5 \times 100 ^ {16}$.
 
@@
 		\caption{TA44}
-		\includegraphics[scale=.6]{tex/figures/TA044}
+		\includegraphics[scale=.8]{tex/figures/TA044}
 
@@
 		\caption{TA45}
-		\includegraphics[scale=.6]{tex/figures/TA045}
+		\includegraphics[scale=.8]{tex/figures/TA045}
 		%\fautor

### 2020-03-03 defesa/tex/chapter/mcd2.tex
wip

In this section, we consider the problem which we refer to as \sigla{MCE}{Maximum Covering by Ellipses}. We introduce an algorithm for it, which in fact, works not only for ellipses, but for any disk in a strictly convex normed plane.

\section{Definition}

Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}. All it takes to describe one is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, with $a>b$, also called its shape parameters, and a center $q \in \R^2$.

An instance of MCE is given by a set of $n$ demand points $\Pp = \{p_1, \dots, p_n\}$, with $p_j\in\R^2$; 
a set of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$;
and a set of $m$ axis-parallel ellipses given by their shape parameters $\Rr:=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{>0}^2$ and $a_j>b_j$.
Additionally, to make the text more clear, we define a set $\E = \{E_1, \dots, E_m\}$, with $E_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th ellipse is located as input, and returns its coverage region as defined by \autoref{equation:cover_pellipse}.

A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse. Let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem

\begin{equation*}
	\max_q w\left(\bigcup_{j=1}^m \Pp \cap E_j(q_j)\right).
\end{equation*}

From now on, since ellipses are just unit circles in a strictly convex normed space $(\R^2, ||.||_Q)$, with $||.||_{a, b}$ being an elliptical norm whose unit disk is an ellipse with shape parameters $(a, b)$, we will develop this work for any set of strictly convex unit disks. The following notation is adopted: $D(x)$ represents a unit disk centered at $x\in \R^2$, which is the set of points $\{y \in \R^2 \colon ||y-x|| \le 1 \}$, for any strictly convex plane $(\R^2, ||.||)$, and we denote by $\partial D(x)$, the circle correspondent to that disk.

\section{Related work}
The maximal planar covering using axis-parallel ellipses was first introduced in \citeonline{canbolat} which proposed a mixed integer non-linear programming method for the problem. This first approach showed to be not that efficient as it could not find an optimal solution for some instances within a timeout defined by them. To obtain solutions, not necessarily optimal ones, for the instances which the exact method showed inefficiency, a heuristic technique called Simulated Annealing was used to develop another method. Comparisons were made, which showed that the second approach was able to obtain good solutions, compared to the optimal ones found for some of the instances, within a good run-time.

The second work found in the literature was \citeonline{andreta}, which developed a method that breaks the problem into smaller ones fixing the set of points an ellipse is going to cover. For each set of points fixed as the points an ellipse is going to cover, a small optimization problem is solved to find out if there is a location where the ellipse can be placed, so to cover the set of fixed points. To enumerate the possible solutions and then find an optimal one, the method defined a data structure that stores every set of points an ellipse can cover. This method showed better results and was able to find optimal solutions for the instances that the first method could not get as well as for new created instances.

\section{Maximum Weight Clique}

We introduce in this section a problem equivalent to MCE with only one facility. We refer to this equivalent problem as \sigla{MWC}{Maximum Weight Clique}. This equivalence is also used in the works for MCD in \citeonline{chazelle:1986} and \citeonline{cabello:2006}.

An instance of the \sigla{MWC}{Maximum Weight Clique} is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$; 
a set of unit disks $\D:=\{D_1(p_1), \dots, D_n(p_n)\}$, with $D_i(p_i)$ being a unit disk in any strictly convex plane; and a set of weights \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$ being the weight of the $i$-th unit disk. We omit the center of a unit disk whenever we are referring to an instance of MWC, that is, $D_i:=D_i(p_i)$.

A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$, which is inside any of the given disks in $\D$.
From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$ as follows
\begin{equation*}
	S = \bigcap_{j : q \in D_j} D_j.
\end{equation*}
Therefore, an optimal solution of MWC is defined by	$\max_{q} \sum_{D_k \cap q \neq \emptyset} w_k$.

Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with only one facility, and $(\Pp, \D, \Ww)$ an instance of MWC, with $\D$ being a set of unit disks in the strictly convex normed space $(\R^2, ||.||_{a,b})$.
If $q_1$ be a solution for the MCE's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have non-empty intersection.
Also, suppose that $q$ is a solution of MWC. Then, the ellipse with shape parameters $(a, b)$ centered at $q$ covers the points, which are the centers of disks, such that $q \in D_j$.
Therefore, both problems are equivalent.

Let us consider the intersection set of $k$ unit disks $\cap_{j=1}^k D_j(x_j)$, for any strictly convex normed space, with $x_j \in \R^2$ being all distinct.
Then, in \citeonline{bi}, two results are stated about that set: its boundary is formed by arcs of unit circles whose centers are in $\{x_1, \dots, x_k\}$, its vertices are in the set $\partial D_i(x_i) \cap \partial D_j(x_j)$, for any $i \neq j$; and $|\partial D_i(x_i) \cap \partial D_j(x_j)| \le 2$, for any $i\neq j$. 
Based on that, we introduce the next definition.

\begin{definicao}
	Let $D_i(p_i)$ and $D_j(p_j)$ be two unit disk in a strictly convex normed space, and $\{\alpha_{ij}^+, \alpha_{ij}^-\}=\partial D_i(p_i) \cap \partial D_j(p_j)$, we denote by $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ the minimal counter-clockwise arc of $D_i(p_i)$ starting in $\alpha_{ij}^+$ and ending in $\alpha_{ij}^-$. We also refer to $\alpha_{ij}^+$ as an opening intersection point, and to $\alpha_{ij}^-$ as a closing intersection point.
\end{definicao}
Let $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ and $\widehat{\alpha_{ij}^-, \alpha_{ij}^+}$ be the two arcs of $\partial D_i$ with respect to the endpoints $\alpha_{ij}^-, \alpha_{ij}^+$.
From \citeonline[Lemma 2]{bi}, we can state that, $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}\subset D_j$, and\\ $\widehat{\alpha_{ij}^-, \alpha_{ij}^+} \cap D_j = \{\alpha_{ij}^-, \alpha_{ij}^+\}$. That is, only the minimal arc is contained in the interior of $D_j$.

Based on that, we are going to develop an algorithm that finds the best clique that $\partial D_i$ is part of, for each $i=1, \dots, n$. Let \mbox{$q_i \in \partial D_i$} be an optimal solution of $\max_{q_i} \sum_{D_k \cap q_i} w_k$. Then, an optimal solution of MWC is just
$\max_{i=1}^n \max_{q_i} \sum_{D_k \cap q_i} w_k$. Notice that this is enough by the results in \citeonline{bi}.

\begin{lema}
	Let $(\Pp, \D, \Ww)$ be an instance of MWC. For each $i\in \{1, \dots, n\}$,
	if there is \mbox{$j \in \{1, \dots, n\}$}, $j\neq i$, such that $D_i \cap D_j \neq \emptyset$, then, for any solution $q_i \in \partial D_i$, let $J=\{j \colon q_i \in D_j\}$,
	$q_i \in \cap_{j \in J, j\neq i}\{\widehat{\alpha_{ij}^+, \alpha_{ij}^-}\}$.
\end{lema}

\begin{proof}
	Suppose that $q_i \not \in \widehat{\alpha_{ij}^+, \alpha_{ij}^-}$, for some $j \in J\setminus \{i\}$.
	By definition $q_i \in \partial D_i$, and by \citeonline[Lemma 2]{bi}, we have that $q_i \in \widehat{\alpha_{ij}^-, \alpha_{ij}^+}$, which implies that $q_i \in \{\alpha_{ij}^-, \alpha_{ij}^+\}$, which would imply that  $q_i \in \widehat{\alpha_{ij}^+, \alpha_{ij}^-}$, contradicting the assumption we made.
\end{proof}

For the algorithm, for each $i$, instead of looking for $q_i$, we are going to construct the best subset $J \in \{1, \dots, n\}$. This idea is based on the algorithms proposed in \citeonline{drezner} and \citeonline{cabello:2006}. Let us consider the following circular list
\begin{equation*}
	A_i = \{\alpha_{ij}^+ \colon j\neq i, D_i \cap D_j \neq \emptyset\} \cup \{\alpha_{ij}^- \colon j\neq i, D_i \cap D_j \neq \emptyset \}.
\end{equation*}
Suppose that $A_i$ is sorted by the angles of $D_i$ in $[0, 2\pi)$ corresponding to each intersection point, breaking ties by prioritizing opening ones.
Finding the best solution which $D_i$ is part of can be done by traversing $A_i$ while keeping a set of active disks. When an opening intersection angle is reached, the corresponding disk is added to the active set; and when a closing one is seen, the corresponding disk is removed from the active set. This way, finding an optimal solution can be achieved by keeping the weight of the active disks as well as the best clique found so far.

In practice, traversing a circular list can be emulated by traversing a regular list that has a copy of the original circular list added to its end. 
Therefore, the list $B_i$ is defined here as a list that contains the elements of $A_i$ and a copy of it shifted to the interval $[2\pi, 4\pi]$. It is defined as
\begin{equation}\label{eq:bi2}
B_i = A_i\cup\bigcup_{j\neq i} \{2\pi+\alpha_{ij}^+ \colon j\neq i, D_i \cap D_j \neq \emptyset\} \cup \{2\pi+\alpha_{ij}^- \colon j\neq i, D_i \cap D_j \neq \emptyset \}.
\end{equation}
Assuming $B_i$ is sorted with the same criteria as $A_i$, a simple traversal, starting at the first element and going until the last one, simulates a traversal on the circular list $A_i$.
This works because for any pair of disks $D_i$, $D_j$; $B_i$ contains $\alpha_{ij}^+ < \alpha_{ij}^- + 2\pi$. That is, the algorithm encounters an opening intersection point before reaching a closing one for any circle.

\section{From MWC to MCE}

Now we are going to modify the algorithm for MWC to work as a basis for the algorithm for multiple disks.
Suppose that an instance $(\Pp, \Ww, \Rr)$ of MCE is given. For each ellipse with shape parameters $(a_j, b_j)$, we have the instance $(\Pp, \D, \Ww)$ of MWC, with $\D$ being a set of unit disks from a strictly convex normed space where the unit disk is an axis-parallel ellipse with shape parameters $(a_j, b_j)$.

\begin{definicao}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCE. For each $j \in \{1, \dots, m\}$, let $(\Pp, \D, \Ww)$ be the equivalent instance of MWC using the $j$-th ellipse as their unit disk, we define as the \sigla{CLS}{Candidate List Set} $S_j$ for $j$-th ellipse as
	\begin{equation*}
	S_j = \bigcup_{i=1}^n \{\alpha_{ik}^+ \colon k\neq i, D_i \cap D_k \neq \emptyset\}\cup \{p_i\}.
	\end{equation*}
\end{definicao}

Based on this, we introduce a theorem that allows us to develop an algorithm for MCE based on the developments we made for MWC.

\begin{theorem}\label{th:mce2}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined as 
	\begin{equation*}\label{eq:omega2}
		\Omega(\Pp, \Ww, \Rr) = \{Q\in \R^{2m} \colon q_j \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
	\end{equation*}
	Then there exists an optimal solution $Q^*\in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|\le n^{2m}$.
\end{theorem}
\begin{proof}
		Notice that $\Omega(\Pp, \Ww, \Rr)$ is defined as the combination of every possible solution from each CLS. To prove that it contains an optimal solution $Q^*$, it is enough to prove that for all $j\in\{1, \dots, m\}$, there exists $q_j\in S_j$, such that $\Pp \cap E_j(q_j^*) \subset \Pp \cap E_j(q_j)$. That is, we only need to show that the CLS of every ellipse contains a center that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
		We ignore the case where an ellipse does not cover any points.

		First case, the $|\Pp \cap E_j(q_j^*)|=1$ covers only one point. This case is included in $S_j$ as it contains the possible solutions where the center of the ellipse is the actual points in $\Pp$.

		Second case, $|\Pp \cap E_j(q_j^*)| > 1$. Let $X = \{i \colon p_i \in \Pp \cap E_j(q_j^*)$. In the equivalent instance of MWC, we have that $\cap_{i\in X} D_i \neq \emptyset$ is a region bounded by arcs of circles with centers in $\Pp \cap E_j(q_j^*)$ with vertices being pairwise intersections of $\partial \D$, with at least one of them being an opening intersection point.

		Lastly, we have that $|S_j| \le \binom{n}{2} + n = \frac{n(n+1)}{2} \le n^2$. Therefore,
		$|\Omega(\Pp, \Ww, \Rr)| \le |S_1|\times \dots \times |S_m| \le n^{2m}$.
\end{proof}

\section{An algorithm for MCE}

First, we describe, based on \autoref{th:mce2}, an algorithm to return the CLS for every ellipse. This algorithm runs in $\bigO(n)$, and is based on the idea used on the development of the algorithm for MWC.

\begin{algoritmo}
	\caption{Algorithm that returns a CLS for a disk.}\label{algoritmo:mce_cls}
	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$, and the shape parameters $(a, b)\in\R_{>0}^2$.}
		\Ensure{A CLS for the axis-parallel ellipse.}

		\item[]

		\Procedure{CLS-MCE}{$\Pp, \Ww, (a,b)$}
		\State Let $\D$ be a set of unit disks on the strictly convex normed space $(\R^2, ||.||_{a,b})$.
		\State $S \gets \{\}$
		\ForAll{$p_i \in \Pp$}
		\State $S \gets S \cup \{p_i\}$

		\ForAll{$j \neq i \colon D_j \cap D_i \neq \emptyset$}

		\State $S \gets S \cup \{\alpha_{ij}^+\}$

		\EndFor
		\EndFor

		\State \Return $S$
		\EndProcedure
	\end{algorithmic}
\end{algoritmo}

Then, we define in \autoref{algoritmo:mce2}, an algorithm for MCE, which backtracks to find an optimal solution taking into account every possibility in the CLS of every ellipse. This way, we obtain a $\bigO(mn^{2m+1})$ algorithm for MCE.

\begin{algoritmo}
	\caption{Algorithm for MCE}\label{algoritmo:mce2}

	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}

		\Ensure{An optimal solution for MCE.}

		\item[]
		\Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
		\State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
		\EndProcedure
		\State
		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
		\If{$j = m+1$}
		\State \Return $0$
		\EndIf

		\State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$

		\State $S_j \gets \textnormal{CLS-MCE}(Z, a_j, b_j)$
		\For{$q_j \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j)$
		\State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$

		\If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
		\State $(q_j^*, \dots, q_m^*) \gets(q_j, \dots, q_m)$
		\EndIf
		\EndFor

		\State \Return $(q_j^*, \dots, q_m^*)$
		\EndProcedure
	\end{algorithmic}
\end{algoritmo}

### 2020-03-04 defesa/tex/chapter/future.tex
wip

@@
 
-An exact algorithm was also developed for the other problem studied in this work, which the ellipse could not be rotated.
+An exact algorithm was also developed for the other problem studied in this work, in which the ellipse could not be rotated.
 We created an algorithm for it in \autoref{chapter:mce} based on an algorithm for maximum covering using disks, which we introduced in \autoref{chapter:pmclp}.
@@
 We first used instances found in the literature, and then proposed new instances to further analyze the performance of our algorithms.
-Even though the exponential nature of both algorithms proposed by us, 
+Even though both algorithms proposed by us are exponential in nature, 
 in \autoref{chapter:numerical}, we gave several improvements suggestions, which allowed our implementations to obtain optimal solutions for every previously published instance, including instances that no optimal solutions were obtained before, plus some fairly large new ones.

### 2020-03-04 defesa/tex/chapter/introducao.tex
wip

@@
-The Minimum Cover Problem --also known as just the Set Cover Problem--, and the Maximal Covering Problem are the two main types of optimal covering problems found in the literature \cite{karatas}.
+The Minimum Covering Problem -- also known as just the Set Cover Problem --, and the Maximal Covering Problem are the two main types of optimal covering problems found in the literature \cite{karatas}.
 
-One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic.
+One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Covering Problem is very well explored and considered to be a classic.
 Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets needed to cover the whole demand set.
@@
 
-Just like the Minimum Cover problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming, and heuristic methods have been proposed to solve it.
+Just like the Minimum Covering Problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming, and heuristic methods have been proposed to solve it.
 A very complete survey of developments in this area can be found in \citeonline{mclp_review}.
@@
 
-PMCLP under Euclidean distance is also found in the literature as the \sigla{MCD}{Maximum Covering by Disks} problem.
+PMCLP under Euclidean distance is also found in the literature as \sigla{MCD}{Maximum Covering by Disks}.
 Early works only tackled the one-disk version of it.
@@
 In the first version, introduced in \citeonline{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \citeonline{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
-The first version will be referred to as \sigla{MCE}{Maximum Cover by Ellipses} and the second one as  \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.
+The first version will be referred to as \sigla{MCEP}{Maximum Cover by Ellipses Problem} and the second one as  \sigla{MCERP}{Maximum Covering by Ellipses with Rotation Problem}.
 
@@
 The problem was further explored in \citeonline{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \citeonline{canbolat} could not.
-The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though, returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.
+The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.
 
-The main results of this work are presented in \autoref{chapter:e3p} and  \autoref{chapter:mcer}. 
-In \autoref{chapter:e3p}, we introduce a new geometry problem and propose an algorithm for it.
-In \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to proposed a new algorithm for MCER.
-This new algorithm is proved to have a runtime complexity of $\bigO(mn^{3m+1})$, and in \autoref{chapter:numerical}, we analyze several numerical experiments to show its effectiveness and compare it to methods of previous works.
-The rest of our work is structured in the following way: In \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.
+Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented; in \autoref{chapter:e3p}, we introduce a new geometry problem and propose an algorithm for it;
+in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCERP; 
+in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.

### 2020-03-04 defesa/tex/chapter/mcd.tex
wip

@@
 
-\section{Related Work}
+\section{Related work}
 In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.

### 2020-03-04 defesa/tex/chapter/mcd2.tex
wip

@@
 \begin{definicao}
-	Let $D_i(p_i)$ and $D_j(p_j)$ be two unit disk in a strictly convex normed space, and $\{\alpha_{ij}^+, \alpha_{ij}^-\}=\partial D_i(p_i) \cap \partial D_j(p_j)$, we denote by $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ the minimal counter-clockwise arc of $D_i(p_i)$ starting in $\alpha_{ij}^+$ and ending in $\alpha_{ij}^-$.
+	Let $D_i(p_i)$ and $D_j(p_j)$ be two unit disk in a strictly convex normed space, and $\{\alpha_{ij}^+, \alpha_{ij}^-\} \subset \partial D_i(p_i) \cap \partial D_j(p_j)$,
+	 we denote by $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ the minimal counter-clockwise arc of $D_i(p_i)$ starting in $\alpha_{ij}^+$ and ending in $\alpha_{ij}^-$.
 We also refer to $\alpha_{ij}^+$ as an opening intersection point, and to $\alpha_{ij}^-$ as a closing intersection point.
@@
 
+In \autoref{fig:array_disks2}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection points.
+The intersection list $B_1$ is also displayed in \autoref{fig:array_disks2} along with the size of the set of active disks $Q$ after processing a point in $B_1$.
+It is possible to see that the optimal clique highlighted in \autoref{fig:array_disks2} is enclosed by the arcs defined by $\alpha_{14}^+$ and $\alpha_{14}^-$, and can also be identified by following $B_1$ while keeping track of $Q$.
+The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks2}.
+Its usage is very convenient as with $\alpha_{11}^+$ and $\alpha_{11}^-$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point, and removes $D_1$ only after every point has been processed.
+
+\begin{figure}[!htb]
+	\centering
+
+	\caption{The intersection list of a disk with three other disks.}
+	%\input{tex/figures/array_disks.tex}
+	\includegraphics[scale=.3]{tex/figures/3_disks_intersect_.pdf}
+	\fautor
+	\label{fig:array_disks2}
+\end{figure}
+
+%\begin{algoritmo}[!htb]
+%	\caption{Algorithm for MWC.}\label{algoritmo:mwc}
+%	\begin{algorithmic}[1]
+%		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and a set of weights $\Ww=\{w_1, \dots, w_n\}$.}
+%		\Ensure{A point that is inside the maximum weight clique of unit disks.}
+
+%		\item[]
+
+%		\Procedure{$MWC$}{$\Pp, \Ww$}
+%		\State Let $\D=\{D_1, \dots, D_n\}$ be a set of unit disks, with centers in $\Pp$ and weights in $\Ww$
+
+%		\State $Q_{best} \gets \{\}$
+%		\State $q^* \gets$ $p_1$
+%		\ForAll{$D_i \in \D$}
+%		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}
+
+%		\State $Q \gets \{\}$ \Comment{The set of active disks.}
+%		\For{$\alpha \in B_i$}\Comment{Assuming $B_i$ is sorted.}
+%		\State Let $D_j$ be the disk, such that $\theta \in D_j\cap D_i$
+%		\If{$\theta$ is a opening angle}
+%		\State $Q \gets Q \cup \{D_j\}$
+%		\Else
+%		\State $Q \gets Q \setminus \{D_j\}$
+%		\EndIf
+%		\If{$w(Q_{best}) < w(Q)$} 
+%		\State $Q_{best} \gets Q$
+%		\State $q^* \gets$ point corresponding to the intersection angle $\theta$
+%		\EndIf
+%		
+%		\EndFor
+%		\EndFor
+
+%		\State \Return $q^*$
+%		\EndProcedure
+%	\end{algorithmic}
+%\end{algoritmo}
+
 \section{From MWC to MCE}
@@
 
-		First case, the $|\Pp \cap E_j(q_j^*)|=1$ covers only one point. This case is included in $S_j$ as it contains the possible solutions where the center of the ellipse is the actual points in $\Pp$.
+		First case: $|\Pp \cap E_j(q_j^*)|=1$. This case is included in $S_j$ as it contains the possible solutions where the center of the ellipse is the actual points in $\Pp$.
 
-		Second case, $|\Pp \cap E_j(q_j^*)| > 1$.
+		Second case: $|\Pp \cap E_j(q_j^*)| > 1$.
 Let $X = \{i \colon p_i \in \Pp \cap E_j(q_j^*)$.
@@
 
+\section{Determining $\alpha_{ij}^+$ and $\alpha_{ij}^-$}\label{section:ellipses_intersection2}
+
+Let $E_1(q_1)$, and $E_2(q_2)$ be two coverage region of ellipses centered at $q_1, q_2\in\R^2$ respectively, with shape parameters $(a, b)\in\R^2_{>0}$.
+After changing the coordinates to make the center of the first ellipse be at the origin, the intersection points between the two ellipses are defined by
+
+\begin{align}
+	\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1 && (E_1) \label{eq:ell_inter_1}\\
+	\frac{(x-h)^2}{a^2} + \frac{(y-k)^2}{b^2} = 1 && (E_2), \nonumber
+\end{align}
+where $(h,k)\in\R^2$ is the center of the second ellipse after the coordinates were translated by $-q_1$. As both equations are equal to $1$, we have
+\begin{align}
+	b^2x^2 + a^2y^2 &= b^2(x-h)^2 + a^2(y-k)^2 \nonumber\\
+	x &= y\frac{-2ka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2} \nonumber\\
+	x &= y\alpha + \beta.\label{eq:ell_inter_2}
+\end{align}
+Replacing \autoref{eq:ell_inter_2} into \autoref{eq:ell_inter_1}, we get
+\begin{align}\label{eq:ell_inter_3}
+	y^2(b^2\alpha^2 + a^2) + y(2\beta\alpha b^2) + b^2\beta^2 -a^2b^2 = 0,
+\end{align}
+which is a second degree polynomial.
+Then, $\partial E_1(q_1) \cap \partial E_2(q_2) \neq \{\}$ if, and only if the roots of \autoref{eq:ell_inter_3} are real.
+The intersection points itself can be obtained by solving the polynomial for $y$ and plugging its value back into the $x=y\alpha + \beta$ equation.
+
+Suppose that $\partial E_1(q_1) \cap \partial E_2(q_2) = \{p_1, p_2\}$, with $p_1 \neq p_2$.
+To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the intersection angles corresponding to $p_1$ and $p_2$ on $E_1(q_1)$.
+
+Let $\gamma_1$ and $\gamma_2$ be two curves defined as \autoref{eq:parametric_ellipse} for $E_1(q_1)$ and $E_2(q_2)$ respectively. 
+The intersection angle of $p_i$ in $E_j(q_j)$ is defined as $t_i^{(j)} \in [0, 2\pi)$, such that $\gamma_j(t_i^{(j)}) = p_i$, for $i, j \in \{1, 2\}$.
+Obtaining $t_i^{(j)}$ can be done analytically solving the equation
+
+\begin{equation}\label{eq:angle_inter}
+	\dfrac{a}{b}\dfrac{p_{iy}-q_{jy}}{p_{ix}-q_{jx}} = \tan{(t_i^{(j)})}.
+\end{equation}
+
+Determining which one of the points is $\alpha_{ij}^+$, we just need to use the assumption that $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ is minimal.
+This can be done using the angle of the intersection points obtained from \autoref{eq:angle_inter}.
+
 \begin{algoritmo}

### 2020-03-04 defesa/tex/chapter/numerical.tex
wip

@@
 The goal of this chapter is to show the results of the algorithms for MCE-$k$ and MCER-$k$ proposed by us for instances proposed by other works as well as instances created by us. 
-We also give implementation details and suggestions to improve performance, which we adopted in our implementations.
-
-\section{Implementation}
-
-All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3. All the experiments were run in a computer with the following specification:
+We also give implementation details and suggestions to improve performance, which we adopted in our implementations. All the experiments were run in a computer with the following specification:
 \begin{itemize}
@@
 
+\section{Implementation}
+
+In this section, we give more details about the implementation of the algorithms developed in our work.
+
+All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3.
+The actual code is available in \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
+
 \subsection{Determining the eigenvalues of a matrix}
 
-In \autoref{algoritmo:e3p}, we assumed that a procedure which returns every eigenvalue of a given square matrix was available.
+In \autoref{algoritmo:e3p} for E3P, we assumed that a procedure which returns every eigenvalue of a given square matrix was available.
 In practice, we used the very famous linear algebra package LAPACK (see \citeonline{lapack} for more details).
@@
 It can also convert expressions into polynomials in the power format, and output them directly into C code.
-Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++ implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.
+Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++ implementation of E3P's algorithm by printing the polynomial's list of coefficients as C code.
 The actual coefficients of that polynomial are presented in \autoref{chapter:poly} in terms of a generic E3P's instance.
@@
 
-To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} and \autoref{algoritmo:mcer} had to be done.
+To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} for MCE and \autoref{algoritmo:mcer} for MCER had to be done.
 Just translating those algorithms into a programming language is not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
@@
 
-Calling \autoref{algoritmo:e3p} for E3P for every triplet of points in an instance of MCER can be expensive.
-To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.
+Calling E3P's algorithm for every triplet of points in an instance of MCER can be expensive.
+To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling E3P's algorithm if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.
 
@@
 We are adopting them in our implementation because they showed good results in practice.
-For example, without taking the suggestion given by \autoref{eq:upper-bound}, \autoref{algoritmo:mcer-k} takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions.
-In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
+For example, without taking the suggestion given by \autoref{eq:upper-bound}, 
+MCER-$k$'s algorithm takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions.
+In \autoref{tab:mcer-results-ab1}, we show the results of MCER-$k$'s algorithm implemented with all the improvement suggestions given here; for instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
 
@@
 
-In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
+In this section, we present the results of \autoref{algoritmo:mce-k} for MCE-$k$ and \autoref{algoritmo:mcer-k} for MCER-$k$ for instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
 
@@
 
-The numerical results obtained by our implementation of \autoref{algoritmo:mcer-k} are shown in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for instances AB001-AB120.
+The numerical results obtained by our implementation of \autoref{algoritmo:mcer-k} for MCER-$k$ are shown in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for instances AB001-AB120.
 An optimal solution was obtained for every instance, and overall, at most six seconds of CPU time was taken.
@@
 In general, our algorithm took much lower CPU time compared to the methods developed in \citeonline{andreta}.
-For example, for instance CM9, their heuristic method took more than six hours to return a solution, our implementation of \autoref{algoritmo:mcer-k}, on the other hand, obtained an optimal solution in less than five seconds.
+For example, for instance CM9, their heuristic method took more than six hours to return a solution, our implementation of MCER-$k$'s algorithm, on the other hand, obtained an optimal solution in less than five seconds.
 
@@
 It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
-The optimal solution of MCER-$k$ returned by \autoref{algoritmo:mcer-k} for the instance with $n=500$ and $k=5$ is shown in \autoref{fig:TA037}.
+The optimal solution returned by MCER-$k$'s algorithm for the instance with $n=500$ and $k=5$ is shown in \autoref{fig:TA037}.
 

### 2020-03-04 defesa/tex/chapter/tables.tex
wip

@@
 		}
-		\caption{Solutions of MCE-$k$ for instances CM1-CM9.}
+		\caption{Solutions of MCE-$k$ for instances CM1-CM9 obtained by \autoref{algoritmo:mce-k}.}
 		\label{tab:mce-results-cm}
@@
 		}
-		\caption{Solutions of MCER-$k$ for instances CM1-CM9.}
+		\caption{Solutions of MCER-$k$ for instances CM1-CM9 obtained by \autoref{algoritmo:mcer-k}.}
 		\label{tab:mcer-results-cm}
@@
 		}
-		\caption{Solutions of MCE-$k$ for instances AB001-AB060.}
+		\caption{Solutions of MCE-$k$ for instances AB001-AB060 obtained by \autoref{algoritmo:mce-k}.}
 		\label{tab:mce-results-ab1}
@@
 		}
-		\caption{Solutions of MCE-$k$ for instances AB061-AB120.}
+		\caption{Solutions of MCE-$k$ for instances AB061-AB120 obtained by \autoref{algoritmo:mce-k}.}
 		\label{tab:mce-results-ab2}
@@
 		}
-		\caption{Solutions of MCER-$k$ for instances AB001-AB060.}
+		\caption{Solutions of MCER-$k$ for instances AB001-AB060 obtained by \autoref{algoritmo:mcer-k}.}
 		\label{tab:mcer-results-ab1}
@@
 		}
-		\caption{Solutions of MCER-$k$ for instances AB061-AB120.}
+		\caption{Solutions of MCER-$k$ for instances AB061-AB120 obtained by \autoref{algoritmo:mcer-k}.}
 		\label{tab:mcer-results-ab2}
@@
 		}
-		\caption{Solutions of MCE-$k$ for instances TA001-TA007.}
+		\caption{Solutions of MCE-$k$ for instances TA001-TA007 obtained by \autoref{algoritmo:mce-k}.}
 		\label{tab:mce-results-ta1}
@@
 		}
-		\caption{Solutions of MCER-$k$ for instances TA001-TA007.}
+		\caption{Solutions of MCER-$k$ for instances TA001-TA007 obtained by \autoref{algoritmo:mcer-k}.}
 		\label{tab:mcer-results-ta1}
@@
 		}
-		\caption{Solutions of MCE-$k$ for instances TA008-TA022.}
+		\caption{Solutions of MCE-$k$ for instances TA008-TA022 obtained by \autoref{algoritmo:mce-k}.}
 
@@
 		}
-		\caption{Solutions of MCER-$k$ for instances TA008-TA022.}
+		\caption{Solutions of MCER-$k$ for instances TA008-TA022 obtained by \autoref{algoritmo:mcer-k}.}
 

### 2020-03-05 defesa/tex/chapter/mcd2.tex
wip

@@
-In this section, we consider the problem which we refer to as \sigla{MCE}{Maximum Covering by Ellipses}.
-We introduce an algorithm for it, which in fact, works not only for ellipses, but for any disk in a strictly convex normed plane.
-
+In this chapter, we consider the problem, which we refer to as \sigla{MCE}{Maximum Covering by Ellipses}.
+We introduce an algorithm for it, which in fact, works not only for ellipses but for any disk in a strictly convex normed plane.
 \section{Definition}
@@
 A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse.
-Let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem
-
+Let $w: 2^{\Pp} \mapsto \R_{\ge0}$ be a function, which takes a subset of $\Pp$ and returns the sum of the weights of every point in it, defined as
+\begin{equation*}
+w(A) = \sum_{j : p_j \in A} w_j,
+\end{equation*}
+then an optimal solution of MCE is given by the optimization problem
 \begin{equation*}
@@
 \end{equation*}
-
-From now on, since ellipses are just unit circles in a strictly convex normed space $(\R^2, ||.||_Q)$, with $||.||_{a, b}$ being an elliptical norm whose unit disk is an ellipse with shape parameters $(a, b)$, we will develop this work for any set of strictly convex unit disks.
-The following notation is adopted: $D(x)$ represents a unit disk centered at $x\in \R^2$, which is the set of points $\{y \in \R^2 \colon ||y-x|| \le 1 \}$, for any strictly convex plane $(\R^2, ||.||)$, and we denote by $\partial D(x)$, the circle correspondent to that disk.
 
@@
 
+\section{Strictly Convex Normed Plane}
+
+Based on the results of \citeonline{bi}, instead of developing an algorithm for MCE, we are going to consider a more general case and develop an algorithm that works for any set of facilities with a strictly convex coverage region.
+
+A strictly convex normed space is defined in \citeonline{wada} as a space whose every chord of its unit sphere has its midpoint in the interior of its unit ball.
+Thus, $(\R^2, ||\cdot||)$ is a strictly convex normed plane if the unit disk defined by $||\cdot||$ is a strictly convex body.
+For more details about convexity and strictly convexity see \citeonline{conv}.
+
+For example, the norms $||\cdot||_p$, $p\in \mathbb{N}, p>1$, define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
+Ellipses are also strictly convex bodies, given an axis-parallel ellipse with shape parameters $(a, b)$, a norm $||\cdot||_{a,b}$ can be defined, such that its unit disk is the coverage region of that ellipse.
+
+From now on, since ellipses are just unit circles in a strictly convex normed space $(\R^2, ||\cdot||_{a,b})$, with $||\cdot||_{a, b}$ being an elliptical norm whose unit disk is an ellipse with shape parameters $(a, b)$, we will develop this work for any set of strictly convex unit disks.
+
+%The following notation is adopted: $D(x)$ represents a unit disk centered at $x\in \R^2$, which is the set of points $\{y \in \R^2 \colon ||y-x|| \le 1 \}$, for any strictly convex plane $(\R^2, ||.||)$, and we denote by $\partial D(x)$, the circle correspondent to that disk, that is, the boundary of $D(x)$.
+
 \section{Maximum Weight Clique}
@@
 An instance of the \sigla{MWC}{Maximum Weight Clique} is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$; 
-a set of unit disks $\D:=\{D_1(p_1), \dots, D_n(p_n)\}$, with $D_i(p_i)$ being a unit disk in any strictly convex plane; and a set of weights \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$ being the weight of the $i$-th unit disk.
-We omit the center of a unit disk whenever we are referring to an instance of MWC, that is, $D_i:=D_i(p_i)$.
+a norm $||\cdot||$, such that $(\R^2, ||\cdot||)$ is a strictly convex normed plane; and a set of weights \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$. 
+Then, we define a set of unit disks $\D:=\{D_1, \dots, D_n\}$, with $D_i:=\{x \in \R^2 \colon ||x-p_i|| \le 1\}$ being a unit disk centered at $p_i$; we also denote by $\partial D_i$ as the circle correspondent to the $i$-th unit disk, and that $w_i$ is the weight of $D_i$.
+Having said all that, we define an instance of MWC as a tuple $(\Pp, \Ww, ||\cdot||)$.
 
-A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
-Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$, which is inside any of the given disks in $\D$.
+A clique, in this context, is a non-empty intersection region of one or more disks. The weight of a clique is the sum of every disk's weight in it.
+Following this, we define a solution for MWC as just a point $q\in\cup_{j=1}^n D_j$, which is inside any of the given disks in $\D$.
 From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$ as follows
@@
 \end{equation*}
-Therefore, an optimal solution of MWC is defined by	$\max_{q} \sum_{D_k \cap q \neq \emptyset} w_k$.
+Therefore, an optimal solution of MWC is defined as	$\max_{q} \sum_{D_k \cap q \neq \emptyset} w_k$.
 
-Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with only one facility, and $(\Pp, \D, \Ww)$ an instance of MWC, with $\D$ being a set of unit disks in the strictly convex normed space $(\R^2, ||.||_{a,b})$.
-If $q_1$ be a solution for the MCE's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have non-empty intersection.
+Let $D$ be a unit disk in a strictly convex normed plane $(\R^2, ||\cdot||)$, and $p, q \in \partial D$.
+Then we denote by $\widehat{p, q}$ as the counter-clockwise arc of $D$ starting at $p$ and ending at $q$.
+This is represented in \autoref{fig:disk_arc} where the arc $\widehat{p,q}$ is shown with a solid line, and the arc $\widehat{q, p}$ is shown by a dashed line.
+
+\begin{figure}[!htb]
+	\centering
+
+	\caption{The definition of arcs of a circle.}
+	%\input{tex/figures/array_disks.tex}
+	\includegraphics[scale=.3]{tex/figures/disk_arc.pdf}
+	\fautor
+	\label{fig:disk_arc}
+\end{figure}
+
+Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with only one facility, and $(\Pp, \Ww, ||\cdot||_{a,b})$ an instance of MWC, with the unit circle defined by $||\cdot||_{a,b}$ being an axis-parallel ellipse with shape parameters $(a,b)$.
+If $q_1$ be a solution for the MCE's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have a non-empty intersection.
 Also, suppose that $q$ is a solution of MWC. Then, the ellipse with shape parameters $(a, b)$ centered at $q$ covers the points, which are the centers of disks, such that $q \in D_j$.
@@
 
-Let us consider the intersection set of $k$ unit disks $\cap_{j=1}^k D_j(x_j)$, for any strictly convex normed space, with $x_j \in \R^2$ being all distinct.
-Then, in \citeonline{bi}, two results are stated about that set: its boundary is formed by arcs of unit circles whose centers are in $\{x_1, \dots, x_k\}$, its vertices are in the set $\partial D_i(x_i) \cap \partial D_j(x_j)$, for any $i \neq j$; and $|\partial D_i(x_i) \cap \partial D_j(x_j)| \le 2$, for any $i\neq j$.
+Let us consider the intersection set of $k$ unit disks $\cap_{j=1}^k D_j(x_j)$, for any strictly convex normed space, with $x_j \in \R^2$, $j\in \{1, \dots, k\}$ being all distinct.
+Then, in \citeonline{bi}, the following results are stated about that set: its boundary is formed by arcs of unit circles whose centers are in $\{x_1, \dots, x_k\}$, its vertices are in the set $\partial D_i(x_i) \cap \partial D_j(x_j)$, for any $i \neq j$; and $|\partial D_i(x_i) \cap \partial D_j(x_j)| \le 2$, for any $i\neq j$.
 Based on that, we introduce the next definition.
@@
 \begin{definicao}
-	Let $D_i(p_i)$ and $D_j(p_j)$ be two unit disk in a strictly convex normed space, and $\{\alpha_{ij}^+, \alpha_{ij}^-\} \subset \partial D_i(p_i) \cap \partial D_j(p_j)$,
-	 we denote by $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ the minimal counter-clockwise arc of $D_i(p_i)$ starting in $\alpha_{ij}^+$ and ending in $\alpha_{ij}^-$.
+	Let $D_i$ and $D_j$ be two unit disk in a strictly convex normed space, and\\ \mbox{$\{\alpha_{ij}^+, \alpha_{ij}^-\} = \partial D_i(p_i) \cap \partial D_j(p_j)$},
+	 we denote by $\widehat{\alpha_{ij}^+, \alpha_{ij}^-}$ the minimal counter-clockwise arc of $\partial D_i$ starting in $\alpha_{ij}^+$ and ending in $\alpha_{ij}^-$.
 We also refer to $\alpha_{ij}^+$ as an opening intersection point, and to $\alpha_{ij}^-$ as a closing intersection point.
+	 If $\partial D_i$ and $\partial D_j$ intersect at exactly one point, we define $\alpha_{ij}^+ = \alpha_{ij}^- = \partial D_i \cap \partial D_j$.
 \end{definicao}
@@
 That is, only the minimal arc is contained in the interior of $D_j$.
+In \autoref{fig:disk_arc_inter}, the minimal arcs are highlighted with a solid border, and it is possible to see that they are the only ones that are in the intersection's interior.
 
-Based on that, we are going to develop an algorithm that finds the best clique that $\partial D_i$ is part of, for each $i=1, \dots, n$.
-Let \mbox{$q_i \in \partial D_i$} be an optimal solution of $\max_{q_i} \sum_{D_k \cap q_i} w_k$.
-Then, an optimal solution of MWC is just
-$\max_{i=1}^n \max_{q_i} \sum_{D_k \cap q_i} w_k$. Notice that this is enough by the results in \citeonline{bi}.
+\begin{figure}[!htb]
+	\centering
 
-\begin{lema}
-	Let $(\Pp, \D, \Ww)$ be an instance of MWC. For each $i\in \{1, \dots, n\}$,
-	if there is \mbox{$j \in \{1, \dots, n\}$}, $j\neq i$, such that $D_i \cap D_j \neq \emptyset$, then, for any solution $q_i \in \partial D_i$, let $J=\{j \colon q_i \in D_j\}$,
-	$q_i \in \cap_{j \in J, j\neq i}\{\widehat{\alpha_{ij}^+, \alpha_{ij}^-}\}$.
+	\caption{The intersection between two circles, and the arcs .}
+	%\input{tex/figures/array_disks.tex}
+	\includegraphics[scale=.3]{tex/figures/disk_arc_inter.pdf}
+	\fautor
+	\label{fig:disk_arc_inter}
+\end{figure}
+
+Based on that, we are going to develop an algorithm that finds the best clique that $\partial D_i$ is part of, for each $i=1, \dots, n$, and then combine the solutions to get an overall optimal one.
+Notice that this is enough because, by \citeonline{bi}, the arcs of the circles in $\partial \D$ form the boundary of any clique.
+For each $i\in \{1, \dots, m\}$, let $q_i$ be an optimal solution of MWC with an additional constraint that $q_i \in \partial D_i$.
+Then, an optimal solution of MWC can be obtained by just taking a solution of
+$\max_{i=1}^n \max_{q \in \partial D_i} \sum_{D_k \cap q} w_k$.
+
+\begin{lema}\label{lema:mwc}
+	Let $(\Pp, \Ww, ||\cdot||)$ be an instance of MWC. For each $i\in \{1, \dots, n\}$,
+	let $q_i$ be any solution, such that $q_i \in \partial D_i$; and $J=\{j \colon q_i \in D_j\}$.
+If there is \mbox{$j \in \{1, \dots, n\}$}, $j\neq i$, such that $D_i \cap D_j \neq \emptyset$, then $q_i \in \cap_{j \in J, j\neq i}\{\widehat{\alpha_{ij}^+, \alpha_{ij}^-}\}$.
 \end{lema}
@@
 
-For the algorithm, for each $i$, instead of looking for $q_i$, we are going to construct the best subset $J \in \{1, \dots, n\}$.
-This idea is based on the algorithms proposed in \citeonline{drezner} and \citeonline{cabello:2006}.
-Let us consider the following circular list
+Given the set of indexes $J=\{j \colon q_i \in D_j\}$ of disks that contain a solution $q_i\in\partial D_i$, we have that there exists $l, k \in J\setminus \{i\}$, such that  $\cap_{j \in J, j\neq i}\{\widehat{\alpha_{ij}^+, \alpha_{ij}^-}\} = \widehat{\alpha_{il}^+, \alpha_{ik}^-}$.
+Therefore, by \autoref{lema:mwc}, we can just look for an index $l \in \{1, \dots, n\} \setminus \{i\}$, such that it is the solution of $$\max_{l \neq i} \sum_{D_k \cap \alpha_{il}^+} w_k.$$
+Then an optimal solution $q_i \in \partial D_i$ can be obtained by just setting $q_i = \alpha_{il}^+$.
+From that, a $\bigO(n^3)$ algorithm for MWC can be developed by just evaluating, for every pair $i, j \in \{1, \dots, n\}$, the solution defined by $\alpha_{ij}^+$.
+Based on the algorithms for MCD proposed by \citeonline{drezner} and \citeonline{cabello:2006} though, we can develop a $\bigO(n^2\lg{n})$ algorithm for MWC.
+Let $A_i$ be a circular defined as 
 \begin{equation*}
-	A_i = \{\alpha_{ij}^+ \colon j\neq i, D_i \cap D_j \neq \emptyset\} \cup \{\alpha_{ij}^- \colon j\neq i, D_i \cap D_j \neq \emptyset \}.
+	A_i = \{\alpha_{ij}^+ \colon j\neq i, D_i \cap D_j \neq \emptyset\} \cup \{\alpha_{ij}^- \colon j\neq i, D_i \cap D_j \neq \emptyset \},
 \end{equation*}
-Suppose that $A_i$ is sorted by the angles of $D_i$ in $[0, 2\pi)$ corresponding to each intersection point, breaking ties by prioritizing opening ones.
+which contains all the intersection points of $\partial D_i$ with all the other disks.
+Assume that this list is sorted by the angles on $D_i$ in the interval $[0, 2\pi)$ corresponding to the intersection points, breaking ties prioritizing opening intersection points.
 Finding the best solution which $D_i$ is part of can be done by traversing $A_i$ while keeping a set of active disks.
@@
 In practice, traversing a circular list can be emulated by traversing a regular list that has a copy of the original circular list added to its end. 
-Therefore, the list $B_i$ is defined here as a list that contains the elements of $A_i$ and a copy of it shifted to the interval $[2\pi, 4\pi]$. It is defined as
+Therefore, the list $B_i$ is defined here as a list that contains the elements of $A_i$, and a copy of it shifted to the interval $[2\pi, 4\pi]$. It is defined as
 \begin{equation}\label{eq:bi2}
@@
 That is, the algorithm encounters an opening intersection point before reaching a closing one for any circle.
+
+If it is possible to find the intersection between two unit disks (it will be shown that it is possible for the case where the unit disk is an axis-parallel ellipse), for each disk, the runtime complexity of processing every intersection point and sorting the list $B_i$ is $\bigO(n\lg{n})$.
+Therefore, the overall runtime complexity of this algorithm for MWC is $\bigO(n^2\lg{n})$.
 
@@
 
-Now we are going to modify the algorithm for MWC to work as a basis for the algorithm for multiple disks.
-Suppose that an instance $(\Pp, \Ww, \Rr)$ of MCE is given.
-For each ellipse with shape parameters $(a_j, b_j)$, we have the instance $(\Pp, \D, \Ww)$ of MWC, with $\D$ being a set of unit disks from a strictly convex normed space where the unit disk is an axis-parallel ellipse with shape parameters $(a_j, b_j)$.
+Based on the ideas developed for MWC, we are going to propose an algorithm for MCE in this section.
+Suppose that an instance $(\Pp, \Ww, \Rr)$ of MCE is given. For each ellipse with shape parameters $(a_j, b_j)$, we have the equivalent instance $(\Pp, \Ww, ||\cdot||_{a_j,b_j})$ of MWC.
 
@@
 	Let $(\Pp, \Ww, \Rr)$ be an instance of MCE.
-For each $j \in \{1, \dots, m\}$, let $(\Pp, \D, \Ww)$ be the equivalent instance of MWC using the $j$-th ellipse as their unit disk, we define as the \sigla{CLS}{Candidate List Set} $S_j$ for $j$-th ellipse as
+For each $j \in \{1, \dots, m\}$, let \mbox{$(\Pp,  \Ww, ||\cdot||_{a_j,b_j})$} be the equivalent instance of MWC using the $j$-th ellipse as their unit disk, we define as the \sigla{CLS}{Candidate List Set} $S_j$ for $j$-th ellipse as
 	\begin{equation*}
@@
 		Notice that $\Omega(\Pp, \Ww, \Rr)$ is defined as the combination of every possible solution from each CLS. 
-To prove that it contains an optimal solution $Q^*$, it is enough to prove that for all $j\in\{1, \dots, m\}$, there exists $q_j\in S_j$, such that $\Pp \cap E_j(q_j^*) \subset \Pp \cap E_j(q_j)$.
+		To prove that $\Omega(\Pp, \Ww, \Rr)$ contains an optimal solution, we just need to show that for any optimal solution $Q'$, for every $j \in \{1, \dots, m\}$, there exists $q_j \in S_j$, such that $\Pp \cap E_j(q_j') \subset \Pp \cap E_j(q_j)$.
 		That is, we only need to show that the CLS of every ellipse contains a center that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
@@
 
-		First case: $|\Pp \cap E_j(q_j^*)|=1$. This case is included in $S_j$ as it contains the possible solutions where the center of the ellipse is the actual points in $\Pp$.
+		First case: $|\Pp \cap E_j(q_j')|=1$. This case is included in $S_j$ as it contains the possible solutions where the center of the ellipse is the actual points in $\Pp$.
 
-		Second case: $|\Pp \cap E_j(q_j^*)| > 1$.
-Let $X = \{i \colon p_i \in \Pp \cap E_j(q_j^*)$.
-In the equivalent instance of MWC, we have that $\cap_{i\in X} D_i \neq \emptyset$ is a region bounded by arcs of circles with centers in $\Pp \cap E_j(q_j^*)$ with vertices being pairwise intersections of $\partial \D$, with at least one of them being an opening intersection point.
+		Second case: $|\Pp \cap E_j(q_j')| > 1$.
+Let $X = \{i \colon p_i \in \Pp \cap E_j(q_j')\}$.
+In the equivalent instance of MWC, we have that $\cap_{i\in X} D_i \neq \emptyset$ is a region bounded by arcs of circles with centers in $\Pp \cap E_j(q_j')$ with vertices being pairwise intersections of $\partial \D$.
+By \autoref{lema:mwc}, we have that at least one of the vertices of $\cap_{i\in X} D_i$ is an opening intersection point.
 
@@
 
-\section{An algorithm for MCE}
-
-First, we describe, based on \autoref{th:mce2}, an algorithm to return the CLS for every ellipse.
-This algorithm runs in $\bigO(n)$, and is based on the idea used on the development of the algorithm for MWC.
+Based on \autoref{th:mce2}, \autoref{algoritmo:mce_cls} describes a simple $\bigO(n^2)$ algorithm that returns a CLS for an ellipse given a set of points and the ellipse's shape parameters. 
+Then we define \autoref{algoritmo:mce2}, which backtracks the CLS returned by \autoref{algoritmo:mce_cls} of every ellipse to find an optimal solution given an instance of MCE.
+This algorithm can be implemented to have a $\bigO(mn^{2m+1})$ runtime complexity if the CLSs are constructed beforehand in a preprocessing phase.
+\autoref{algoritmo:mce2} can go through every solution in $\Omega(\Pp, \Ww, \Rr)$, and taking $\bigO(mn)$ operations to evaluate each solution hence its runtime complexity.
+Next we give details on how to determine the intersection points between two ellipses.
 
@@
 
-Then, we define in \autoref{algoritmo:mce2}, an algorithm for MCE, which backtracks to find an optimal solution taking into account every possibility in the CLS of every ellipse.
-This way, we obtain a $\bigO(mn^{2m+1})$ algorithm for MCE.
-
-\section{Determining $\alpha_{ij}^+$ and $\alpha_{ij}^-$}\label{section:ellipses_intersection2}
+\section{Determining $\alpha_{ij}^+$ and $\alpha_{ij}^-$ for axis-parallel ellipses}\label{section:ellipses_intersection2}
 

### 2020-03-05 defesa/tex/chapter/mcd2.tex
wip

@@
 
-For example, the norms $||\cdot||_p$, $p\in \mathbb{N}, p>1$, define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
-Ellipses are also strictly convex bodies, given an axis-parallel ellipse with shape parameters $(a, b)$, a norm $||\cdot||_{a,b}$ can be defined, such that its unit disk is the coverage region of that ellipse.
+For example, the norms $||\cdot||_p$, $p\in \mathbb{N}, p>1$ define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
+Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a norm $||\cdot||_{a,b}$, such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.
 
-From now on, since ellipses are just unit circles in a strictly convex normed space $(\R^2, ||\cdot||_{a,b})$, with $||\cdot||_{a, b}$ being an elliptical norm whose unit disk is an ellipse with shape parameters $(a, b)$, we will develop this work for any set of strictly convex unit disks.
+%In the next section we introduce a problem equivalent to MCE with only one facility.
+
+%This way, from now on we will consider a more general version of MCE whose instance is composed by a set of strictly convex norms $\F:=\{f_1, \dots, f_m\}$, instead of the list of shape parameters $\Rr$, and the list $\E:=\{E_1, \dots, E_m\}$ having $ .
 

### 2020-03-06 defesa/tex/chapter/future.tex
wip

@@
 An exact algorithm was also developed for the other problem studied in this work, in which the ellipse could not be rotated.
-We created an algorithm for it in \autoref{chapter:mce} based on an algorithm for maximum covering using disks, which we introduced in \autoref{chapter:pmclp}.
+We created an algorithm for it in \autoref{chapter:mcd2} based on an algorithm proposed by us for a more general problem, which had any strictly convex disk as facilities instead of just ellipses.
 

### 2020-03-06 defesa/tex/chapter/introducao.tex
wip

@@
 From the CLS, a network was built on which MCLP could be applied.
-Generating the CLS specifically for the case of Euclidean distance will be described here on \autoref{chapter:pmclp}.
 
@@
 In the first version, introduced in \citeonline{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \citeonline{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
-The first version will be referred to as \sigla{MCEP}{Maximum Cover by Ellipses Problem} and the second one as  \sigla{MCERP}{Maximum Covering by Ellipses with Rotation Problem}.
+The first version will be referred to as \sigla{MCE}{Planar Maximum Covering Location by Ellipses Problem} and the second one as  \sigla{MCER}{Planar Maximum Covering Location by Ellipses with Rotation Problem}.
 
@@
 
-Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented; in \autoref{chapter:e3p}, we introduce a new geometry problem and propose an algorithm for it;
-in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCERP; 
+Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:mcd2}, we proposed an algorithm for MCE based on developments we made for a more general version of that problem that considers not only ellipses but any strictly convex disk as facilities;
+in \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented; in \autoref{chapter:e3p}, we introduce a new geometry problem, which surged as a subproblem of MCER, and propose an algorithm for it;
+in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCER; 
 in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.

### 2020-03-06 defesa/tex/chapter/mcd2.tex
wip

--- 2020-03-05 defesa/tex/chapter/mcd2.tex
@@
 
+\subsection{Maximum cover by disks}
+In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm.
+Firstly, they solve a sub-problem for two disks in $\bigO(n^3\log{n})$.
+Then, for the rest of the points that are not in that solution, it uses the algorithm developed in \citeonline{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.
+
+Also, in \citeonline{zhou} an heuristic method for large-scale $MCD$ is proposed.
+It uses a probabilistic algorithm called mean-shift which is a gradient ascent method proven to converge to a local density maxima of any probability distribution.
+The mean-shift is utilized to find good candidates of centers for the unit disks, then the method backtracks to find the best assignment.
+The results showed that the greedy algorithm achieves an optimal coverage in some instances, but for some other ones it has a 15 percent worse coverage ratio.
+
+Two exact methods for the case of MCD with only one disk have been found in the literature.
+A $\bigO(n^2)$ algorithm is proposed by \citeonline{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \citeonline{drezner}.
+As it has been mentioned, MCD for one disk is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding three real numbers that sum to zero, given $n$ real numbers).
+Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for MCD for one disk, which meant that no better time-complexity could be achieved.
+Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.
+
+In \citeonline{drezner}, the main idea used to develop the $\bigO(n^2\log{n})$ algorithm is that, even though there are infinitely many points where the disk could be placed, only a few of them, a finite amount of $\bigO(n^2)$, needs to be considered for the method to find an optimal solution.
+The algorithm, for every point, sorts the other points with respect to the angle they form with the first one.
+After that, the first point is placed on the border of the disk and, going through the sorted list, the algorithm inserts and removes points from the disk coverage.
+Also, when inserting and removing a point from the coverage, it only checks the disk centers that make the entering/leaving point to be on the border.
+Because the algorithm only checks the centers that make the disk have two points on its border, the number of centers it goes through is bounded by the number of pairs of points, which is $\binom{n}{2} = \bigO(n^2)$.
+
 \section{Strictly Convex Normed Plane}
 
-Based on the results of \citeonline{bi}, instead of developing an algorithm for MCE, we are going to consider a more general case and develop an algorithm that works for any set of facilities with a strictly convex coverage region.
+In this section, we give a brief introduction to the notion of strictly convex normed planes, which is utilized in the rest of the chapter.
 
-A strictly convex normed space is defined in \citeonline{wada} as a space whose every chord of its unit sphere has its midpoint in the interior of its unit ball.
-Thus, $(\R^2, ||\cdot||)$ is a strictly convex normed plane if the unit disk defined by $||\cdot||$ is a strictly convex body.
+Given a vector space $\mathscr{V}$, and a norm function $||\cdot|| \colon \mathscr{V} \to \R_{\ge0}$ for that vector space, we denote by $(\mathscr{V}, ||\cdot||)$ the normed vector space with respect to $\mathscr{V}$ and $||\cdot||$.
+A strictly convex normed space is defined in \citeonline{wada} as a normed vector space whose every chord of its unit sphere has its midpoint in the interior of its unit ball.
+In other words, in a strictly convex normed space, no line intersects a unit sphere more than twice.
+We also refer to norms that induce strictly convex normed spaces as strictly convex norms.
+Restricting this definition to $\R^2$, we get a strictly convex normed plane, and we refer to its ball as disk, and to its sphere as circle.
 For more details about convexity and strictly convexity see \citeonline{conv}.
 
-For example, the norms $||\cdot||_p$, $p\in \mathbb{N}, p>1$, define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
-Ellipses are also strictly convex bodies, given an axis-parallel ellipse with shape parameters $(a, b)$, a norm $||\cdot||_{a,b}$ can be defined, such that its unit disk is the coverage region of that ellipse.
+For example, the norms $||x||_p=(\sum_{i} |x_i|^p)^{\frac{1}{p}}$, $p\in \mathbb{N}, p>1$ define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
+Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a strictly convex normed space $(\R^2,||\cdot||_{a,b})$, such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.
 
-From now on, since ellipses are just unit circles in a strictly convex normed space $(\R^2, ||\cdot||_{a,b})$, with $||\cdot||_{a, b}$ being an elliptical norm whose unit disk is an ellipse with shape parameters $(a, b)$, we will develop this work for any set of strictly convex unit disks.
-
-%The following notation is adopted: $D(x)$ represents a unit disk centered at $x\in \R^2$, which is the set of points $\{y \in \R^2 \colon ||y-x|| \le 1 \}$, for any strictly convex plane $(\R^2, ||.||)$, and we denote by $\partial D(x)$, the circle correspondent to that disk, that is, the boundary of $D(x)$.
+Instead of developing an algorithm for ellipses only, based on the results of \citeonline{bi}, we describe a more general method that only assumes that the facilities have a strictly convex coverage area, and it is possible to determine the intersection between the boundaries of two of them.
+We refer to this more general version of MCE as \sigla{MCSCD}{Planar Maximum Covering Location by Strictly Convex Disks}, and instead of having a list of shape parameters, a list of strictly convex norm functions $\F=\{f_1, \dots, f_m\}$ is given, and an instance of MCSCD is defined as the tuple $(\Pp, \Ww, \F)$.
+Also, we define for MCSCD the set $\E=\{E_1, \dots, E_m\}$, with $E_j\colon \R^2 \to \R^2$ being a function that takes a center where the $j$-th disk is located and returns the unit disk corresponding to the the norm $f_i$.
 
@@
 
-We introduce in this section a problem equivalent to MCE with only one facility.
+We introduce in this section a problem which is equivalent to the version of MCSCD with only one facility.
 We refer to this equivalent problem as \sigla{MWC}{Maximum Weight Clique}.
 This equivalence is also used in the works for MCD in \citeonline{chazelle:1986} and \citeonline{cabello:2006}.
+Later we use the developments for this problem to construct a CLS for each disk in an instance of MCSCD.
 
@@
 Then, we define a set of unit disks $\D:=\{D_1, \dots, D_n\}$, with $D_i:=\{x \in \R^2 \colon ||x-p_i|| \le 1\}$ being a unit disk centered at $p_i$; we also denote by $\partial D_i$ as the circle correspondent to the $i$-th unit disk, and that $w_i$ is the weight of $D_i$.
-Having said all that, we define an instance of MWC as a tuple $(\Pp, \Ww, ||\cdot||)$.
+All that being said, we define an instance of MWC as a tuple $(\Pp, \Ww, ||\cdot||)$.
 
-A clique, in this context, is a non-empty intersection region of one or more disks. The weight of a clique is the sum of every disk's weight in it.
+In this context, a clique is a non-empty intersection region of one or more disks. The weight of a clique is the sum of every disk's weight in it.
 Following this, we define a solution for MWC as just a point $q\in\cup_{j=1}^n D_j$, which is inside any of the given disks in $\D$.
@@
 
-Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with only one facility, and $(\Pp, \Ww, ||\cdot||_{a,b})$ an instance of MWC, with the unit circle defined by $||\cdot||_{a,b}$ being an axis-parallel ellipse with shape parameters $(a,b)$.
-If $q_1$ be a solution for the MCE's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have a non-empty intersection.
+Let $(\Pp, \Ww, \{||\cdot||\})$ be an instance of MCSCD with only one facility, and $(\Pp, \Ww, ||\cdot||)$ an instance of MWC.
+If $q_1$ be a solution for the MCSCD's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have a non-empty intersection.
 Also, suppose that $q$ is a solution of MWC. Then, the ellipse with shape parameters $(a, b)$ centered at $q$ covers the points, which are the centers of disks, such that $q \in D_j$.
-Therefore, both problems are equivalent.
+Therefore, MCSCD and MWC for both problems are equivalent.
 
@@
 
-\section{From MWC to MCE}
+\section{From MWC to MCSCD}
 
-Based on the ideas developed for MWC, we are going to propose an algorithm for MCE in this section.
-Suppose that an instance $(\Pp, \Ww, \Rr)$ of MCE is given. For each ellipse with shape parameters $(a_j, b_j)$, we have the equivalent instance $(\Pp, \Ww, ||\cdot||_{a_j,b_j})$ of MWC.
+Based on the ideas developed for MWC, we are going to propose an algorithm for MCSCD in this section assuming that for each $f_i \in \F$, it is possible to determine the intersection between two translated unit disks determined by $f_i$.
+Then later, we give details of how to determine the intersection between two ellipses, and develop an algorithm for MCE.
+
+Suppose that an instance $(\Pp, \Ww, \F)$ of MCSCD is given.
+For each $f_i \in \F$, we have the equivalent instance $(\Pp, \Ww, f_i)$ of MWC.
+Next, we introduce a definition for the CLS of each facility.
 
 \begin{definicao}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCE.
-For each $j \in \{1, \dots, m\}$, let \mbox{$(\Pp,  \Ww, ||\cdot||_{a_j,b_j})$} be the equivalent instance of MWC using the $j$-th ellipse as their unit disk, we define as the \sigla{CLS}{Candidate List Set} $S_j$ for $j$-th ellipse as
+	Let $(\Pp, \Ww, \F)$ be an instance of MCSCD.
+For each $j \in \{1, \dots, m\}$, let \mbox{$(\Pp,  \Ww, f_j)$} be the equivalent instance of MWC, we define as the \sigla{CLS}{Candidate List Set} $S_j$ for $j$-th facility as
 	\begin{equation*}
@@
 
-Based on this, we introduce a theorem that allows us to develop an algorithm for MCE based on the developments we made for MWC.
+For each $f_j \in \F$, we consider every pairwise opening -- we could have chose the closing ones -- intersection between the circles induced by $f_j$ centered at every point in $\Pp$.
+Based on this, we introduce a theorem that allows us to develop an algorithm for MCSCD based on the developments we made for MWC.
 
 \begin{theorem}\label{th:mce2}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined as 
+	Let $(\Pp, \Ww, \F)$ be an instance of MCSCD, and $\Omega(\Pp, \Ww, \F)$ be a set of solutions defined as 
 	\begin{equation*}\label{eq:omega2}
-		\Omega(\Pp, \Ww, \Rr) = \{Q\in \R^{2m} \colon q_j \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
+		\Omega(\Pp, \Ww, \F) = \{Q\in \R^{2m} \colon q_j \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
 	\end{equation*}
-	Then there exists an optimal solution $Q^*\in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|\le n^{2m}$.
+	Then there exists an optimal solution $Q^*\in \Omega(\Pp, \Ww, \F)$, and $|\Omega(\Pp, \Ww, \F)|\le n^{2m}$.
 \end{theorem}
 \begin{proof}
-		Notice that $\Omega(\Pp, \Ww, \Rr)$ is defined as the combination of every possible solution from each CLS. 
-		To prove that $\Omega(\Pp, \Ww, \Rr)$ contains an optimal solution, we just need to show that for any optimal solution $Q'$, for every $j \in \{1, \dots, m\}$, there exists $q_j \in S_j$, such that $\Pp \cap E_j(q_j') \subset \Pp \cap E_j(q_j)$.
+		Notice that $\Omega(\Pp, \Ww, \F)$ is defined as the combination of every possible solution from each CLS. 
+		To prove that $\Omega(\Pp, \Ww, \F)$ contains an optimal solution, we just need to show that for any optimal solution $Q'$, for every $j \in \{1, \dots, m\}$, there exists $q_j \in S_j$, such that $\Pp \cap E_j(q_j') \subset \Pp \cap E_j(q_j)$.
 		That is, we only need to show that the CLS of every ellipse contains a center that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
@@
 		Lastly, we have that $|S_j| \le \binom{n}{2} + n = \frac{n(n+1)}{2} \le n^2$. Therefore,
-		$|\Omega(\Pp, \Ww, \Rr)| \le |S_1|\times \dots \times |S_m| \le n^{2m}$.
+		$|\Omega(\Pp, \Ww, \F)| \le |S_1|\times \dots \times |S_m| \le n^{2m}$.
 \end{proof}
+%%%%
 
-Based on \autoref{th:mce2}, \autoref{algoritmo:mce_cls} describes a simple $\bigO(n^2)$ algorithm that returns a CLS for an ellipse given a set of points and the ellipse's shape parameters. 
-Then we define \autoref{algoritmo:mce2}, which backtracks the CLS returned by \autoref{algoritmo:mce_cls} of every ellipse to find an optimal solution given an instance of MCE.
+Based on \autoref{th:mce2}, we can define an algorithm to enumerate every solution in $\Omega(\Pp, \Ww, \F)$.
+If determining $\alpha_{ij}^+$ is possible for every $i, j \in \{1, \dots, n\}$, this algorithm can be implemented to have a $\bigO(mn^{2m+1})$ runtime complexity, if $\bigO(nm)$ operations is taken to evaluate each solution.
+In the next section, we describe an algorithm for MCE, giving the details on how to determine the intersection between two ellipses.
+
+\section{An algorithm for MCE}
+
+Based on \autoref{th:mce2}, in \autoref{algoritmo:mce_cls} we define a simple $\bigO(n^2)$ procedure called CLS-MCE that returns a CLS given a set of points and an ellipse's shape parameters.
+Then in \autoref{algoritmo:mce2}, we define another procedure which backtracks the CLS returned by \autoref{algoritmo:mce_cls} of every ellipse to find an optimal solution given an instance of MCE.
 This algorithm can be implemented to have a $\bigO(mn^{2m+1})$ runtime complexity if the CLSs are constructed beforehand in a preprocessing phase.
-\autoref{algoritmo:mce2} can go through every solution in $\Omega(\Pp, \Ww, \Rr)$, and taking $\bigO(mn)$ operations to evaluate each solution hence its runtime complexity.
-Next we give details on how to determine the intersection points between two ellipses.
+
+%%%%%
 
 \begin{algoritmo}
-	\caption{Algorithm that returns a CLS for a disk.}\label{algoritmo:mce_cls}
+	\caption{Algorithm that returns a CLS for an ellipse.}\label{algoritmo:mce_cls}
 	\begin{algorithmic}[1]
-		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$, and the shape parameters $(a, b)\in\R_{>0}^2$.}
-		\Ensure{A CLS for the axis-parallel ellipse.}
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$, and an ellipse's shape parameters $(a, b)$.}
+		\Ensure{A CLS for the given ellipse.}
 
@@
 
-		\Procedure{CLS-MCE}{$\Pp, \Ww, (a,b)$}
-		\State Let $\D$ be a set of unit disks on the strictly convex normed space $(\R^2, ||.||_{a,b})$.
+		\Procedure{CLS-MCE}{$\Pp, \Ww, (a, b)$}
+		\State Let $\D$ be a set of unit disks on the strictly convex normed space $(\R^2, ||.||_{a, b})$.
 		\State $S \gets \{\}$
@@
 
-\section{Determining $\alpha_{ij}^+$ and $\alpha_{ij}^-$ for axis-parallel ellipses}\label{section:ellipses_intersection2}
+\subsection{Determining $\alpha_{ij}^+$ and $\alpha_{ij}^-$ for axis-parallel ellipses}\label{section:ellipses_intersection2}
 
@@
 Suppose that $\partial E_1(q_1) \cap \partial E_2(q_2) = \{p_1, p_2\}$, with $p_1 \neq p_2$.
-To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the intersection angles corresponding to $p_1$ and $p_2$ on $E_1(q_1)$.
+To determine $\alpha_{12}^+$ and $\alpha_{12}^-$, we need to first determine the intersection angles corresponding to $p_1$ and $p_2$ on $E_1(q_1)$.
 
@@
 \end{algoritmo}
+
+\section{Adding facility cost}
+
+Additionally, in \citeonline{andreta} and \citeonline{canbolat}, two other parameters are present in the definition of the problem.
+This extension is the result of having costs associated with every facility.
+In MCE, though, the total cost, which is the sum of costs of every used facility, is constant; hence, to create a decision about which ones are utilized, a new parameter $k\in\mathbb{N}$ is given, along with a constraint on the number of used ellipses.
+
+We refer to this version of the problem as  \sigla{MCE-$k$}{Planar Maximum Covering Location by Ellipses with a $k$-constraint}.
+An instance of it is given by the same parameters as MCE, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost, and $k\in\mathbb{N}$, $k\le m$.
+
+A solution for MCE-$k$, however,  when compared to MCE's, has a bit more cluttered description.
+We define it as a set $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$, such that $|I|=k$; and a tuple $Q:=(q_1, \dots, q_k)$, with $q_j\in\R^2$ being the center of the $j$-th ellipse in $I$.
+An optimal solution of MCE-$k$ is given by the optimization problem
+
+\begin{equation*}
+	\max_{I, Q} w\left(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j)\right).
+\end{equation*}
+
+Finally, \autoref{algoritmo:mce2} can serve as basis for MCE-$k$'s \autoref{algoritmo:mce-k}. 
+Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
+After that, by keeping track of the utilized ellipses' costs for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
+This simple adjustment achieves a run-time complexity of $\bigO(k\binom{m}{k} \times n^{2k}) = \bigO(m2^mn^{2m+1})$.
+Later in \autoref{chapter:numerical}, we run numerical experiments for MCE-$k$, and compare the obtained results with the results of other works.
+
+\begin{algoritmo}
+	\caption{Algorithm for MCE-$k$}\label{algoritmo:mce-k}
+
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, a list of costs $\Cc=\{c_1, \dots, c_m\}$, and $k\in \mathbb{N}$.}
+		\Ensure{An optimal solution for MCE-$k$.}
+
+		\item[]
+
+		\Procedure{MCE-$k$}{$\Pp, \Ww, \Rr, \Cc, k$}
+		\State $I^* = \{i_1^*, \dots, i_k^*\}\gets \{1, \dots, k\}$
+		\State $Q^* = (q_1^*, \dots, q_k^*) \gets (0, \dots, 0)$
+
+		\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$}
+
+		\State $\Rr' \gets \{(a_j, b_j) \in \Rr: j \in I\}$
+		\State $(q_1, \dots, q_k) \gets MCE(\Pp, \Ww, \Rr')$
+
+		\If{$w(\bigcup_{j=1}^k \Pp \cap E_{i_j}(q_j)) - \sum_{j\in I} c_j > w(\bigcup_{j=1}^k \Pp \cap E_{i_j^*}(q_j^*)) - \sum_{j\in I^*}c_{j}$}
+		\State $Q^* \gets (q_1, \dots, q_k)$
+		\State $I^* \gets I$
+		\EndIf
+		\EndFor
+
+		\State \Return $I^*, Q^*$
+		\EndProcedure
+	\end{algorithmic}
+\end{algoritmo}

### 2020-03-06 defesa/tex/chapter/mcer.tex
wip

@@
 This chapter introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated.
-We refer to this problem as \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.
+We refer to this problem as \sigla{MCER}{Planar Maximum Covering Location by Ellipses with Rotation Problem}.
 In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem.
@@
 
-	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound
+	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound for its size:
 	\begin{eqnarray*}

### 2020-03-10 defesa/article/article.tex
wip

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[a4]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% The graphicx package provides the includegraphics command.
\usepackage{graphicx}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%\usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}

\begin{document}

	\begin{frontmatter}

		%% Title, authors and addresses

		\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
		\tnotetext[t1]{This paper is the results of the research
			project funded by CAPES.}

		%% use the tnoteref command within \title for footnotes;
		%% use the tnotetext command for the associated footnote;
		%% use the fnref command within \author or \address for footnotes;
		%% use the fntext command for the associated footnote;
		%% use the corref command within \author for corresponding author footnotes;
		%% use the cortext command for the associated footnote;
		%% use the ead command for the email address,
		%% and the form \ead[url] for the home page:
		%%
		%% \title{Title\tnoteref{label1}}
		%% \tnotetext[label1]{}
		%% \author{Name\corref{cor1}\fnref{label2}}
		%% \ead{email address}
		%% \ead[url]{home page}
		%% \fntext[label2]{}
		%% \cortext[cor1]{}
		%% \address{Address\fnref{label3}}
		%% \fntext[label3]{}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{<author name>}
		%% \address[label1]{<address>}
		%% \address[label2]{<address>}

		\author[1]{Danilo Tedeschi}
		\ead{danilo.tedeschi@usp.br}

		\author[2]{Marina Andretta}
		\ead{andretta@gmail.com}

		\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
		%\author{John Smith}

		%address{California, United States}

		\begin{abstract}
			%% Text of abstract
			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
			maximizing a function depending on the value of covered points.
			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances having with up to seven hundred demand points and five ellipses.
		\end{abstract}

		\begin{keyword}
			Optimization \sep Covering \sep Combinatorial Optimization
			%% keywords here, in the form: keyword \sep keyword

			%% MSC codes here, in the form: \MSC code \sep code
			%% or \MSC[2008] code \sep code (2000 is the default)

		\end{keyword}

	\end{frontmatter}

	%%
	%% Start line numbering here if you want
	%%
	%\linenumbers

	%% main text
	\section{Introduction}

	The Planar Maximum Covering Location Problem (PMCLP) was first introduced in \cite{church:1984}, and can be seen as a category of problems where the coverage of a demand set, a collection of subsets of $\R^2$, is to be maximized by determining the location of facilities in $\R^2$, with coverage being determined by a distance function.
	In \cite{church:1984}, methods for Euclidean and Rectilinear distances versions of the problem were proposed.
	In \cite{drezner, chazelle:1986}, exact algorithms for the Euclidean PMCLP with only one facility are proposed; and in \cite{cabello:2006} an approximation algorithm is proposed for the version with multiple unit disks as facilities.
	A property of the Euclidean PMCLP, which is utilized in the algorithms developed in \cite{drezner, chazelle:1986, cabello:2006}, and in the method proposed in \cite{church:1984}, is that there is an optimal solution which every facility is located in the demand points, or in the intersection of two circles centered at two demand points; we will prove a similar property for ellipses in our work.

	It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it. In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem. For some instances, the method took too long and did not find an optimal solution. Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
	The problem was further explored in \cite{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
	The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.

	We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
	In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
	The first version will be referred to as Planar Maximum Covering Location by Ellipses Problem (MCE) and the second one as  Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER).

	\section{Problem Definition}

	An instance of MCE and MCER is given by $n$ demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R$, $w_j>0$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j$. We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility. For MCE $E_j\colon\R^2\to\R^2$ is defined as
	\begin{equation}
	E_j(q) = \{p \in \R^2 \colon (p_x-q_x)^2/a_j^2 + (p_y-q_y)^2/b_j^2 \le 1\}.
	\end{equation}
	For MCER, we define $E_j \colon \R^2 \to \R^2 \times [0, \pi)$ as
	\begin{equation}
		E_j(q, \theta) = \left\{p \in \R^2 \colon 
		\left|\left|
		\left(
		\begin{array}{rr}
		\cos{\theta}/a_j & \sin{\theta}/a_j\\
		\sin{\theta}/b_j & -\cos{\theta}/b_j
		\end{array}
		\right)
		\left(
		\begin{array}{c}
		p_x-q_x\\
		p_y-q_y
		\end{array}
		\right)
		\right|\right|_2
		\le 1
		\right\}.
	\end{equation}

Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE as the optimization problem 
\begin{equation}
\max_{q_1, \dots, q_m} \sum_{j=1}^m w(\Pp \cap E_j(q_j)),
\end{equation}
and similarly MCER as
\begin{equation}
\max_{(q_1, \theta_1), \dots, (q_m, \theta_m)} \sum_{j=1}^m w(\Pp \cap E_j(q_j, \theta_j)).
\end{equation}

To make the notation more clear, we denote an instance of MCE or MCER as the tuple $(\Pp, \Ww, \Rr)$, and a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$.

\section{An algorithm for MCE}

We will develop a method which is similar to the one developed in \cite{drezner} for only one euclidean disk, and the exact algorithm developed for multiple Euclidean disks in \cite{cabello:2006}. 
We first describe a Candidate List set (CLS) for each facility, which is finite set of possible locations for each ellipse, which we use to converting MCE into a discrete optimization problem. We, then prove that using the possible solutions obtained from the combination of every ellipse's CLS an optimal solution can be obtained.

%\subsection{An equivalent problem}

Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, then for each $j=1\dots m$, consider $n$ ellipses with shape parameters $(a_j, b_j)$ centered at each one of the points in $\Pp$. Then, if we have $q_j\in\R^2$ and $X \subset \{1, \dots, n\}$, such that $q_j \in \cap_{i\in X}E_j(p_i)$. That is $q_j$ lies in the intersection of a subset of the ellipses centered at $\Pp$. Then $\Pp \cap E_j(q_j) = \{p_i \colon i \in X\}$, that is, if we place an ellipse at $q_j$, it will cover the points which are centers of the ellipses centered at $\Pp$ that contain $q_j$.
From that observation, we can constrain each $q_j$ to be in $\cap_{i\in X} E_j(p_i)$, for some $X \subset \{1, \dots,n\}$, $X \neq \emptyset$.

Let $(\R^2, ||\cdot||)$ be a strictly convex normed plane, and $\D=\{D_1(p_1), \dots, D_n(p_n)\}$ be a set of $n$ unit disks in that space, with the condition that  $\cap_{D\in\D} D \neq \emptyset$. In \cite{bi}, we have the following results about $\cap_{D \in \D} D$:
\begin{itemize}
	\item The $\partial \cap_{D \in \D} D$ is formed by arcs of $D_1(p_1), \dots, D_n(p_n)$.
	\item The vertices of $\partial \cap_{D \in \D} D$ is contained in the set of pairwise-intersection of the circles $\partial D_1(p_1), \dots, \partial D_n(p_n)$.
\end{itemize}

\section{References}
	%% New version of the num-names style
	\bibliographystyle{elsarticle-num-names}
	\bibliography{../references.bib}

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2020-03-10 defesa/presentation/slides.tex
wip

--- 2019-10-23 ONPCE/slides.tex
@@
 \newcommand{\E}{\mathscr{E}}
+\newcommand{\F}{\mathscr{F}}
+\newcommand{\Ww}{\mathscr{W}}
+\newcommand{\Rr}{\mathscr{R}}
 \newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
@@
 \author{Danilo Tedeschi\\Dra. Marina Andretta}
-\title{Fixed-Shape Ellipse by Three Points}
+\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems}
 \institute{Universidade de São Paulo}
@@
 \begin{frame}{Introduction}
+
+	Two versions: 
+	\begin{itemize}
+		\item Planar Maximum Covering Location by Ellipses Problem (MCE) \cite{canbolat};
+		\item Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER) \cite{andreta}.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Introduction}{Ellipse}
 	The shape of an ellipse is given by its major-axis and minor-axis, $(a, b) \in \mathbb{R}^2$, with $a > b > 0$.
@@
 		%\caption{The ellipse as a parametric curve.}
-			\input{ellipse_figure.tex}
+		\includegraphics[scale=.3]{../tex/figures/rotated_ellipse.pdf}
 		\label{fig:ellipse_params}
@@
 
-\begin{frame}{Introduction}
-	Here, the shape will be fixed and the center and angle of rotation are free.
-
-	\begin{figure}
-	\centering
-
-	%\caption{The ellipse as a parametric curve.}
-	\includegraphics[scale=.5]{3ellipses.pdf}
-	\label{fig:ell}
-	\caption{A fix-shape ellipse at different centers and with different angles of rotation.}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Introduction}{Problem definition}
-Given three points $u, v, w \in \R^2$, and the shape $(a,b) \in \R^2$ of an ellipse:
-	\begin{figure}
-	\centering
-
-	%\caption{The ellipse as a parametric curve.}
-	\includegraphics[scale=.5]{e3psol1.pdf}
-	\label{fig:e3psol1}
-	\caption{An instance of the problem.}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Introduction}{Problem definition}
-	A solution is given by the ellipse's center $q \in \R^2$ and the angle of rotation $\theta \in [0, \pi)$, such that $u, v, w$ lie on its border. \textbf{We want to find every solution!}
-	\begin{figure}
-		\centering
-
-		%\caption{The ellipse as a parametric curve.}
-		\includegraphics[scale=.5]{e3psol2.pdf}
-		\label{fig:e3psol2}
-		\caption{Every solution for the instance shown previously.}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Introduction}
-	The equation of an ellipse is given by:
-
-	\begin{equation*}
-	\frac{\left(\left[\begin{array}{c}
-	x-q_x\\
-	y-q_y
-		\end{array}\right]^T
-		\left[\begin{array}{c}
-		\cos\theta\\
-		\sin\theta
-		\end{array}\right]
-		\right)^2}{a^2}+\frac{\left(\left[\begin{array}{c}
-		x-q_x\\
-		q_y-y
-		\end{array}\right]^T
-		\left[\begin{array}{c}
-		\sin\theta\\
-		\cos\theta
-		\end{array}\right]
-		\right)^2}{b^2} = 1.
-	\end{equation*}
-
-	\begin{itemize}
-		\item Fixing the points $u, v, w$, we get $3$ equations and $3$ unknowns $(q_x, q_y, \theta)$.
-		\item Finding every solution is difficult.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-	Let's make the problem simpler by transforming it into a circle problem.
-
-	An ellipse with shape $(a, b)$ can be transformed into a circle of radius $b$ through scaling the $x$-axis by $\frac{b}{a}$:
-	\begin{figure}
-		\centering
-
-		%\caption{The ellipse as a parametric curve.}
-		\includegraphics[scale=.5]{el1.pdf}
-		\label{fig:el1}
-		\caption{Turning an ellipse with shape $(a, b)$ into a circle of radius $b$.}
-	\end{figure}
-
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-
-	Let's rotate the points instead of rotating the ellipse:
-
-	\begin{figure}
-		\centering
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.5]{sol1}
-		\caption{Three points at their initial location.}
-		\label{fig:sol1}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-
-	Firstly, we rotate leaving one point fixed at $(0, 0)$:
-
-	\begin{figure}
-		\centering
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.5]{sol2}
-		\caption{After rotation.}
-		\label{fig:sol2}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-
-	Then, we scale by $\frac{b}{a}$ and check the radius of the circle:
-
-	\begin{figure}
-		\centering
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.5]{sol3}
-		\caption{After scaling.}
-		\label{fig:sol33}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-
-	If the radius is $b$, the angle of rotation is a solution:
-
-	\begin{figure}
-		\centering
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.5]{sol4}
-		\caption{One solution for this instance.}
-		\label{fig:sol4}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Transforming the problem}
-	Formally, we can transform the problem by:
-
-	\begin{itemize}
-		\item Translate the points so $u=(0, 0)$.
-		\item Rotate by $\theta$ and scale the $x$-axis by $\frac{b}{a}$.
-		\item Find the $\theta$'s which produce a circle with radius $b$.
-	\end{itemize}
-
-	This transformation is expressed by:
-
-	\begin{equation*}\label{eq:trpnts}
-	\varphi(p, \theta)=\left[\begin{array}{cc}
-	\frac{b}{a}&0\\
-	0&1
-	\end{array}\right]
-	\left[\begin{array}{cc}
-	\cos{\theta}&\sin{\theta}\\
-	-\sin{\theta}&\cos{\theta}
-	\end{array}\right]\left[\begin{array}{c}
-	p_x\\
-	p_y
-	\end{array}\right],
-	\end{equation*}
-	for $p=u, v, w$.
-
-	\textbf{This is an one variable problem on a closed interval!}
-
-\end{frame}
-
-\begin{frame}{Fixed-shape ellipse by three points}
-	There is a known formula for the radius of a circumscribed circle \cite[p.~189]{johnson1960}:
-
-	\begin{equation*}
-	R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)}
-	\end{equation*}
-
-	\begin{itemize}
-		\item $R$ is the radius.
-		\item $A(\theta)$ is the area of the triangle defined by the points $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
-	\end{itemize}
-	\vspace{\baselineskip}
-
-\end{frame}
-
-\begin{frame}{Fixed-shape ellipse by three points}
-We define the function $\xi : [0, \pi) \mapsto \R$:
-
-	\begin{equation*}
-	\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2
-	\end{equation*}
-
-The roots of $\xi$ are solutions of our problem.
-	\begin{figure}
-	\centering
-
-	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics[scale=.5]{036}
-	\caption{An example of $\xi$.}
-%	\label{fig:circumscribed-circle}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Fixed-shape ellipse by three points}
-	There is no clear pattern in $\xi$.
-	\begin{itemize}
-		\item It can be written as 
-		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
-		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
-	\end{itemize}
-\begin{figure}
-	\centering
-
-	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics[scale=.4]{012}
-	\caption{Another example of $\xi$.}
-	%	\label{fig:circumscribed-circle}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Fixed-shape ellipse by three points}
-	An example with two roots.
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.5]{g4sol}
-		\caption{An example of $\xi$ with $4$ roots.}
-		%	\label{fig:circumscribed-circle}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Polynomial Interpolation}
-	It is a way to approximate a function by a simpler one (a polynomial).
-
-	\begin{itemize}
-		\item A degree $n$ of the interpolation is determined.
-		\item $n+1$ points are chosen, such that the polynomial has to pass through.
-		\item Can be calculated using Lagrange's formula.
-
-		\item We can find every root of a polynomial by determining the eigenvalues of a matrix called The Companion Matrix \cite[p.~195]{horn}.
-
-		\item Depending on the points, the interpolation can be a bad approximation. It can get worse even if $n$ is increased (Runge's Phenomenon) \cite[p.~37]{powell}.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}
-
-	\begin{block}{Chebyshev Polynomial}
-		$T_n: [-1, 1] \mapsto [-1, 1]$ is the $n$-degree Chebyshev polynomial \cite{chebbook}:
-		\begin{equation*}
-		T_n(\cos t) = \cos(nt)
-		\end{equation*}
+\begin{frame}{MCE}
+	\begin{block}{Definition}
+		Demand set $\Pp=\{p_1, \dots, p_n\}$;\\
+		Weights $\Ww = \{w_1, \dots, w_n\}$;\\
+		Shape parameters $\Rr = \{(a_1, b_1), \dots, (a_m, b_m)\}$, $a_j > b_j > 0$.\\
+		Set of functions $\E = \{E_1, \dots, E_m\}$, $E_j(q_j)$ is the $j$-th ellipse's coverage region.
 	\end{block}
-	Also, it can be defined recursively:	
-	\begin{align*}
-	&T_0(x) = 1\\
-	&T_1(x) = x\\
-	&T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x)
-	\end{align*}
-
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}
-\begin{figure}
-	\centering
-
-	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-	\includegraphics[scale=.6]{chebpoly}
-	\caption{Chebyshev Polynomials of degree $1, 2, 3, 4$.}
-	%	\label{fig:circumscribed-circle}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}
-	Interpolation on the roots of $T_n$, also known as Chebyshev Nodes:
-
-	\begin{equation*}
-		x_k = \cos\left(\pi\frac{2k - 1}{2n}\right)
-	\end{equation*}
-
-	The interpolation of a function $f : [-1, 1] \mapsto \R$ can be written directly using Chebyshev polynomial as basis:
-
-	\begin{equation*}
-	f(x) \approx \sum_{k=0}^{n} a_k T_k(x)
-	\end{equation*}
-
-	\begin{itemize}
-		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
-		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}
-		Why is it good?
-
-	\begin{itemize}
-		\item Numerically stable! Way better then polynomials in the power format \cite{gautschi:1979}.
-
-		\item No Runge's Phenomenon, the interpolation converges to $f$.
-		\begin{itemize}
-			\item $\bigO(n^{-m})$ if $f$ is $m$ times differentiable \cite[p.~28]{gottlieb}.
-			\item $\bigO(C^n)$, for $C<1$, if $f$ is analytical in a neighborhood of $[-1, 1]$ \cite{battles:2004}.
-		\end{itemize}
-
-		\item Very used in practice: 
-		\begin{itemize}
-			\item Present in external libraries like NumPy for Python.
-			\item Matlab tool Chebfun: allows functions to be treated as vectors.
-		\end{itemize}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Example}
-	$\xi$ and its approximation of degree $8$.
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{inexn8}
-		\caption{An example of degree $8$ approximation.}
-		%	\label{fig:circumscribed-circle}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Example}
-	$\xi$ and its approximation of degree $10$.
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{inexn10}
-		\caption{An example of degree $10$ approximation.}
-
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Example}
-	$\xi$ and its approximation of degree $12$.
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{inexn12}
-		\caption{An example of degree $12$ approximation.}
-
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}
-	Choosing the degree of the interpolation:
-
-	\begin{itemize}
-		\item There is no guaranteed way to choose it.
-		\item A good rule is to examine the last coefficient (the last coefficient rule-of-thumb \cite[p~.50]{boyd:2001}).
-		\item For a predefined $\epsilon$, choose $n$, such that:
-
-		\begin{equation*}
-		|a_n| \le \epsilon
-		\end{equation*}
-
-		\item There are other ways like checking the error on a Lobatto grid \cite{boyd:2007}.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}
-	For $n=32$, a precision of $10^{-10}$ is expected.
-
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{error_coef}
-		\caption{$|a_n|$ for the interpolation of $\xi$ for an instance.}
-		%	\label{fig:circumscribed-circle}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}{Roots}
-	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$ we have:
-
-	\begin{equation*}
-	\left[\begin{array}{cccccc}
-	0&1&0&0&0\\
-	\frac{1}{2} & 0 & \frac{1}{2} & 0 & 0\\
-	0 & \frac{1}{2} & 0 & \frac{1}{2} & 0\\
-	0 & 0 & \frac{1}{2} & 0 & \frac{1}{2}\\
-	-\frac{a_0}{2a_5} & -\frac{a_1}{2a_5} &-\frac{a_2}{2a_5} &-\frac{a_3}{2a_5} &-\frac{a_4}{2a_5}\\
-	\end{array}\right]
-	\end{equation*}
-
-	\begin{itemize}
-		\item This matrix is a Hessenberg matrix.
-		\item Its eigenvalues can be found by a QR decomposition in $\bigO(n^3)$.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}{Roots}
-	The largest error on roots that were found for $n=32$ is around $10^{-14}$ for an instance:
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{error_roots}
-		\caption{$|\xi(\hat{\theta})|$, where $\hat{\theta}$ is a root of $f_n$.}
-		%	\label{fig:circumscribed-circle}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Chebyshev Interpolation}{Roots}
-	The experiments were made using Python with the NumPy library. The running time is really low, even for $n=64$.
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{running_time}
-		\caption{The running time to find the roots of $f_n$.}
-		%	\label{fig:circumscribed-circle}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Example}
-	An example with $4$ solutions.
-	\begin{figure}
-		\centering
-
-		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
-		\includegraphics[scale=.6]{e3psol012}
-		\caption{An example with $4$ solutions.}
-		%	\label{fig:circumscribed-circle}
-	\end{figure}
 \end{frame}
@@
 	\bibliographystyle{amsalpha}
-	\bibliography{references}
+	\bibliography{../references.bib}
 \end{frame}

### 2020-03-10 defesa/tex/chapter/introducao.tex
wip

@@
 
-PMCLP under Euclidean distance is also found in the literature as \sigla{MCD}{Maximum Covering by Disks}.
+PMCLP under Euclidean distance is also found in the literature as \sigla{MCD}{Maximum Covering by Disks Problem}.
 Early works only tackled the one-disk version of it.
@@
 
-Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:mcd2}, we proposed an algorithm for MCE based on developments we made for a more general version of that problem that considers not only ellipses but any strictly convex disk as facilities;
-in \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented; in \autoref{chapter:e3p}, we introduce a new geometry problem, which surged as a subproblem of MCER, and propose an algorithm for it;
-in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCER; 
-in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.
+Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:mcd2}, we proposed an algorithm for MCE based on developments we made for a more general version of that problem that considers not only ellipses but any strictly convex disk as facilities.
+In \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented: in \autoref{chapter:e3p}, we introduce a new geometry problem, which surged as a subproblem of MCER, and propose an algorithm for it;
+in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCER.
+In \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.

### 2020-03-10 defesa/tex/chapter/mcd2.tex
wip

@@
 
-For example, the norms $||x||_p=(\sum_{i} |x_i|^p)^{\frac{1}{p}}$, $p\in \mathbb{N}, p>1$ define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
-Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a strictly convex normed space $(\R^2,||\cdot||_{a,b})$, such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.
+For example, the norms $||x||_p=(\sum_{i} |x_i|^p)^{\frac{1}{p}}$, $p\in \mathbb{N}, p>1$, define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
+Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a strictly convex normed space $(\R^2,||\cdot||_{a,b})$ such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.
 
 Instead of developing an algorithm for ellipses only, based on the results of \citeonline{bi}, we describe a more general method that only assumes that the facilities have a strictly convex coverage area, and it is possible to determine the intersection between the boundaries of two of them.
-We refer to this more general version of MCE as \sigla{MCSCD}{Planar Maximum Covering Location by Strictly Convex Disks}, and instead of having a list of shape parameters, a list of strictly convex norm functions $\F=\{f_1, \dots, f_m\}$ is given, and an instance of MCSCD is defined as the tuple $(\Pp, \Ww, \F)$.
+We refer to this more general version of MCE as \sigla{MCSCD}{Planar Maximum Covering Location by Strictly Convex Disks Problem}, and instead of having a list of shape parameters, a list of strictly convex norm functions $\F=\{f_1, \dots, f_m\}$ is given, and an instance of MCSCD is defined as the tuple $(\Pp, \Ww, \F)$.
 Also, we define for MCSCD the set $\E=\{E_1, \dots, E_m\}$, with $E_j\colon \R^2 \to \R^2$ being a function that takes a center where the $j$-th disk is located and returns the unit disk corresponding to the the norm $f_i$.
@@
 
-An instance of the \sigla{MWC}{Maximum Weight Clique} is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$; 
+An instance of the MWC is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$; 
 a norm $||\cdot||$, such that $(\R^2, ||\cdot||)$ is a strictly convex normed plane; and a set of weights \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$. 

### 2020-03-10 defesa/tex/chapter/mcer.tex
wip

@@
 
-	As it was shown on \autoref{chapter:mce}, $X$ is a region that is limited by arcs of ellipses.
+	As it was shown in \autoref{chapter:mcd2}, $X$ is a region that is limited by arcs of ellipses.
 As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point, creating a vertex.
@@
 	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
-	Moreover, in Section~\ref{section:ellipses_intersection}, we discuss the problem of determining the intersections between two ellipses.
+	Moreover, in Section~\ref{section:ellipses_intersection2}, we discuss the problem of determining the intersections between two ellipses.
 This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
@@
 That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse.
-This can be done using the results of Section~\ref{section:ellipses_intersection}.
+This can be done using the results of Section~\ref{section:ellipses_intersection2}.
 

### 2020-03-11 defesa/article/article.tex
wip

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
 %% The amssymb package provides various useful mathematical symbols
@@
 
+\usepackage[utf8]{inputenc}
+
 \usepackage[mathscr]{eucal}
@@
 \newcommand{\bigO}{\mathscr{O}}
+\usepackage{amsmath}
+
+\newtheorem{thm}{Theorem}
+\newtheorem{lem}[thm]{Lemma}
+\newdefinition{rmk}{Remark}
+\newdefinition{definition}{Definition}
+\newproof{pf}{Proof}
+
+\RequirePackage{algorithm, algpseudocode}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 
-		\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
+		%\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
 		%\author{John Smith}
@@
 To make the notation more clear, we denote an instance of MCE or MCER as the tuple $(\Pp, \Ww, \Rr)$, and a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$.
+We also use $\partial$ as the boundary operator, for example, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$ given an instance of MCE.
 
@@
 Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, then for each $j=1\dots m$, consider $n$ ellipses with shape parameters $(a_j, b_j)$ centered at each one of the points in $\Pp$.
-Then, if we have $q_j\in\R^2$ and $X \subset \{1, \dots, n\}$, such that $q_j \in \cap_{i\in X}E_j(p_i)$.
-That is $q_j$ lies in the intersection of a subset of the ellipses centered at $\Pp$.
-Then $\Pp \cap E_j(q_j) = \{p_i \colon i \in X\}$, that is, if we place an ellipse at $q_j$, it will cover the points which are centers of the ellipses centered at $\Pp$ that contain $q_j$.
+If we have $q_j\in\R^2$ in a subset of the coverage areas of those ellipses, then $q_j$ is a solution of MCE covering the centers of those ellipses.
+In other words, if $q_j \in \R^2$, and $X \subset \{1, \dots, n\}$, $X \neq \emptyset$, such that $q_j \in \cap_{i\in X}E_j(p_i)$, then $\Pp \cap E_j(q_j) = \{p_i \colon i \in X\}$.
 From that observation, we can constrain each $q_j$ to be in $\cap_{i\in X} E_j(p_i)$, for some $X \subset \{1, \dots,n\}$, $X \neq \emptyset$.
 
-Let $(\R^2, ||\cdot||)$ be a strictly convex normed plane, and $\D=\{D_1(p_1), \dots, D_n(p_n)\}$ be a set of $n$ unit disks in that space, with the condition that  $\cap_{D\in\D} D \neq \emptyset$.
-In \cite{bi}, we have the following results about $\cap_{D \in \D} D$:
+In \cite{bi}, an algorithm is proposed for the problem of determining the intersection of disks of fixed radii from a strictly convex normed plane. 
+We say that $(\R^2, ||\cdot||)$ is a strictly convex normed plane if the unit disk given by the norm $||\cdot||$ is strictly convex.
+Note that for any ellipse, there is a strictly convex normed plane whose unit circle is that ellipse.
+For that reason, we state some results from \cite{bi} here, which we use on the development of an algorithm for MCE.
+
+Let $(\R^2, ||\cdot||)$ be a strictly convex normed plane, and $\D=\{D_1, \dots, D_n\}$ be a set of $n$ unit disks in that space centered at different points, with the condition that  $\cap_{i=1}^n D_i \neq \emptyset$.
+In \cite{bi}, an algorithm was developed to construct this intersection in $\bigO(n\lg{n})$, some of its preliminary results are:
 \begin{itemize}
-	\item The $\partial \cap_{D \in \D} D$ is formed by arcs of $D_1(p_1), \dots, D_n(p_n)$.
-	\item The vertices of $\partial \cap_{D \in \D} D$ is contained in the set of pairwise-intersection of the circles $\partial D_1(p_1), \dots, \partial D_n(p_n)$.
+	\item $\partial \cap_{i=1}^n D_i$ is formed by arcs of $\partial D_1, \dots, \partial D_n$.
+	\item The vertices of $\partial \cap_{i=1}^n D_i$ is contained in the set of pairwise-intersection of the circles $\partial D_1, \dots, \partial D_n$.
+	\item $|\partial D_i \cap \partial D_j| \le 2$.
 \end{itemize}
+
+Based on those, we introduce the next definition for the $k$-th ellipse's CLS, which we refer to as $S_k$.
+
+\begin{definition}\label{def:cls_mce}
+	Given an instance of MCE, for any $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
+	\begin{equation}
+	S_k = \bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \bigcup \Pp.
+	\end{equation}
+\end{definition}
+
+The set of solutions $S_k$, can be computed in $\bigO(n^2)$ as determining the intersections between two axis-parallel ellipses can be done analytically.
+
+\begin{lem}
+	Given an instance of MCE, and $S_1, \dots, S_m$ as defined by \autoref{def:cls_mce}, then the set $\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$.
+\end{lem}
+\begin{pf}
+	Let $Q^*$ be an optimal solution of MCE for the given instance. Then, we are going to prove that there exists $Q' \in \Omega$, which is also optimal.
+
+	For each $k=1, \dots, m$, let $X_k = \{p_i \in \Pp\colon p_i \in E_k(q_k^*)\}$.
+
+	If $|X_k| = 0$, then any $q_k \in S_k$ makes $X_k \subset \Pp \cap E_k(q_k)$.
+
+	if $|X_k| = 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.
+
+	if $|X_k| > 1$, then let $Y_k = \cap_{p \in X_k}E_k(p)$, by the results of \cite{bi}, we have that the boundary of $Y_k$ has vertices in the pairwise intersections of $\{\partial E_k(p) \colon p \in X_k\}$.
+Therefore, at least one vertex of $Y_k$ is in $S_k$, and any of those vertices produce a solution that covers at least the same points covered by $Q^*$.
+
+	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$ hence $|\Omega| \le n^{2m}$.
+\end{pf}
+
+With all this in hand, we can go ahead and define an algorithm for MCE.
+
+\begin{algorithm}
+	\caption{Algorithm for MCE}\label{algoritmo:mce}
+
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}
+
+		\Ensure{An optimal solution for MCE.}
+
+		\item[]
+		\Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
+		\State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
+		\EndProcedure
+		\State
+		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
+		\If{$j = m+1$}
+		\State \Return $0$
+		\EndIf
+
+		\State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$
+		\State Let $S_j$ be the CLS for the $j$-th ellipse as defined by \autoref{def:cls_mce}.
+		%\State $S_j \gets \textnormal{CLS-MCE}(Z, a_j, b_j)$
+		\For{$q_j \in S_j$}
+		\State $Cov \gets \Pp \cap E_j(q_j)$
+		\State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$
+
+		\If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
+		\State $(q_j^*, \dots, q_m^*) \gets(q_j, \dots, q_m)$
+		\EndIf
+		\EndFor
+
+		\State \Return $(q_j^*, \dots, q_m^*)$
+		\EndProcedure
+	\end{algorithmic}
+\end{algorithm}
+
+\autoref{algoritmo:mce} can be proved to have a runtime complexity of $\bigO(mn^{2m+1})$.
+
+\section{Determining every location of an ellipse given its shape and three points}
+
+\input{e3p.tex}
+
+\section{An Algorithm for MCER}\label{section:mcer}
 
@@
 	\bibliographystyle{elsarticle-num-names}
-	\bibliography{../references.bib}
+	\bibliography{../references}
 

### 2020-03-11 defesa/article/e3p.tex
wip

In this section, we introduce the problem of determining every location, here defined as the center and angle of rotation, of an ellipse with fixed shape parameters, such that it contains three given points.
This problem comes up in the development of an algorithm for MCER in the next section. 
It is important to point out that no prior studies were found on it, or even on related problems.
We propose an algorithm for it that involves determining the eigenvalues of a $6\times6$ complex matrix. We also analyze its efficiency in terms of numerical accuracy and display some solutions that it was able to obtain.

\subsection{Problem definition}

Given the shape parameters of an ellipse $(a, b)$, $a > b >0$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.

\subsection{Transforming E3P into a circle problem}

Initially, E3P is a problem with three unknown variables: $(q_x, q_y)$, and $\theta$. However, we can reduce this number to only one, as it will be shown, it is possible to obtain $q$ from $\theta$.
Let us assume that point $u$ is at the origin. If it is not, a simple translation by $-u$ applied to the three points can be made to put $u$ at the origin.
Assume as well that $(q, \theta)$ is a solution of E3P.

Applying a rotation of $-\theta$ to the coordinate system makes the ellipse in the original solution become axis-parallel.
Then, that ellipse can be transformed into a circle of radius $b$ by squeezing the $x$-axis by $b/a$. This two-step transformation can be written as a function $\varphi\colon \R^2 \to \R^2$ defined as

\begin{equation}\label{eq:trpnts}
\varphi(p, \theta)=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
-\sin{\theta}&\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right].
\end{equation}

An example of this transformation can be seen in \autoref{fig:circumscribed-circle}. As $\varphi^{-1}$ is well-defined, instead of solving E3P, we can work with the univariate problem of determining an angle of rotation $\theta \in [0, \pi)$ that makes the triangle with vertices $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ be circumscribed in a circle of radius $b$. To make the notation less cluttered, we denote by $\Lambda(\theta)$ the triangle with vertices $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.

Let $A(\theta)$ denote the area of the triangle $\Lambda(\theta)$. Using the formula given in \cite[p.~189]{johnson1960} for the radius of the circumscribed circle of a triangle, we can obtain a function $\xi \colon [0, \pi) \to \R$ given by
\begin{equation}\label{eq:circumscribed_circle_b}
\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
\end{equation}
whose roots determine solutions of E3P.

\begin{figure}
	\centering

	\includegraphics[scale=.3]{../tex/figures/circumscribed-circle}
	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
	\label{fig:circumscribed-circle}
\end{figure}

\begin{lem}
	E3P has at most six solutions.
\end{lem}

\begin{pf}
	The first thing to notice is that $\xi$ is a real trigonometric polynomial of degree $6$. 
	Its term of highest degree is the multiplication of the norms $\norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2$. In \cite[p.~150]{powell}, where a definition of real trigonometric polynomial is also given, it is stated that a $n$-degree real trigonometric polynomial can have up to $2n$ roots in $[0, 2\pi)$. Therefore, E3P has at most $12$ solutions in $[0, 2\pi]$.
	Half of these solutions, though, are duplicated as ellipses are symmetric to their axis.
\end{pf}

\subsection{Converting $\xi$ into a polynomial}

In \cite[p.~195]{horn}, a theorem is presented stating that for every univariate polynomial of degree $n$, there exists a companion matrix which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial. Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \cite{watkins:2008}). Therefore, finding the roots of a univariate polynomial of degree $n$ can be done in $\bigO(n^3)$. Because of that, we use an approach published in  \cite{boyd:2006} to convert real trigonometric polynomials into complex polynomials to convert $\xi$ into a complex polynomial of degree $12$.

Replacing $\cos{\theta}$ and $\sin{\theta}$ by their identities defined as follows
\begin{align}\label{eq:complex_trig_cos}
\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2},\\
\label{eq:complex_trig_sin}
\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i}.
\end{align}

It is possible to show that with that substitution, plus changing the variable to $z=e^{i\theta}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$, with $\mathbb{S}$ being the unit complex circle ($\mathbb{S} = \{z \in \mathbb{C} : |z|=1\}$, and $g(z) = \sum_{k=0}^{12} c_k z^{k-6}$. Multiplying $g$ by $z^6$, and extending the domain to $\mathbb{C}$, we obtain the degree-$12$ complex polynomial $h(z) = z^6g(z)$.

We can cut in half the degree of the complex polynomial by observing that $angle(-z) = \pi + angle(z)$, which implies, because of the symmetry of ellipses, that $g(z) = g(-z)$. Therefore, every odd degree coefficient of $h$ is zero. Using the substitution $y = z^2$, we obtain a degree-$6$ complex polynomial $f(y) = \sum_{k=0}^{6} c_{2k} y^{k}$. Then, from the roots of $f$ we obtain the set of solutions of E3P:
$\{(u + \varphi^{-1}(\hat{q}, angle(\hat{y})/2), angle(\hat{y})/2) \colon f(\hat{y})=0\}$.

### 2020-03-11 defesa/article/e3p.tex
wip

@@
 
-\begin{lem}
+\begin{lem}\label{lema:e3p}
 	E3P has at most six solutions.
@@
 
-In \cite[p.~195]{horn}, a theorem is presented stating that for every univariate polynomial of degree $n$, there exists a companion matrix which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial.
+In \cite[p.~195]{horn}, a theorem is presented stating that for every univariate polynomial of degree $n$, there exists a companion matrix, which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial.
 Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \cite{watkins:2008}).
-Therefore, finding the roots of a univariate polynomial of degree $n$ can be done in $\bigO(n^3)$.
-Because of that, we use an approach published in  \cite{boyd:2006} to convert real trigonometric polynomials into complex polynomials to convert $\xi$ into a complex polynomial of degree $12$.
+For example, for a degree-$4$ polynomial $\sum_{k=0}^4 a_k x^4$, a possible companion matrix is given by
 
-Replacing $\cos{\theta}$ and $\sin{\theta}$ by their identities defined as follows
-\begin{align}\label{eq:complex_trig_cos}
-\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2},\\
-\label{eq:complex_trig_sin}
-\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i}.
-\end{align}
+ \begin{equation*}
+\left[\begin{array}{ccccc}
+0 & 1 & 0 & 0\\
+0 & 0 & 1 & 0\\
+0 & 0 & 0 & 1\\
+-\dfrac{a_0}{a_4} & -\dfrac{a_1}{a_4} & -\dfrac{a_2}{a_4} & -\dfrac{a_3}{a_4}
+\end{array}\right].
+\end{equation*}
+In practice, we can use the very well-known LAPACK software library to obtain the eigenvalues of a matrix; for more information about LAPACK see \cite{lapack}.
+This approach works for both real or complex polynomials, because of that, based on \cite{weidner}, we describe a way of converting $\xi$ into a complex polynomial.
 
-It is possible to show that with that substitution, plus changing the variable to $z=e^{i\theta}$, we obtain the following function $g : \mathbb{S} \mapsto \mathbb{C}$, with $\mathbb{S}$ being the unit complex circle ($\mathbb{S} = \{z \in \mathbb{C} : |z|=1\}$, and $g(z) = \sum_{k=0}^{12} c_k z^{k-6}$.
-Multiplying $g$ by $z^6$, and extending the domain to $\mathbb{C}$, we obtain the degree-$12$ complex polynomial $h(z) = z^6g(z)$.
+By using the two identities $\cos{\theta} = (e^{i\theta} + e^{-i\theta})/2$, and $\sin{\theta} = (e^{i\theta} - e^{-i\theta})/(2i)$, which relate trigonometric functions with complex numbers in the unit circle $\mathbb{S}=\{z\in \mathbb{C}\colon |z|=1\}$, we can rewrite $\xi$ as a function of the new variable $z=e^{i\theta}\in\mathbb{S}$.
+In \cite{weidner}, it is stated that this substitution when utilized for the task of determining the roots of a real trigonometric polynomial does not yield loss of accuracy.
 
-We can cut in half the degree of the complex polynomial by observing that $angle(-z) = \pi + angle(z)$, which implies, because of the symmetry of ellipses, that $g(z) = g(-z)$.
-Therefore, every odd degree coefficient of $h$ is zero.
-Using the substitution $y = z^2$, we obtain a degree-$6$ complex polynomial $f(y) = \sum_{k=0}^{6} c_{2k} y^{k}$.
-Then, from the roots of $f$ we obtain the set of solutions of E3P:
-$\{(u + \varphi^{-1}(\hat{q}, angle(\hat{y})/2), angle(\hat{y})/2) \colon f(\hat{y})=0\}$.
+As $\xi$ is a real trigonometric polynomial of degree $6$, $z$ appears with exponents from $-6$ up to $6$.
+Multiplying $\xi$ by $z^6$ and extending the domain of $z$ to $\mathbb{C}$, we obtain a complex polynomial $g(z)=\sum_{k=0}^{12} c_k z^k$, for some $c_0, \dots, c_{12} \in \mathbb{C}$.
+In practice, symbolic computation can be used to obtain the actual coefficients of $g$ in terms of an instance of E3P.
+
+Let $angle \colon \mathbb{C} \colon [0, 2\pi)$ be a function that returns the angle of a complex number, then given a root $\hat{z}$ of $g$, if $|\hat{z}|=1$ and $angle(\hat{z}) \in [0, \pi)$, then $\hat{\theta} = angle(\hat{z})$ is a root of $\xi$.
+Observing that for any $z\in \mathbb{C}$, $angle(-z)=\pi+angle(z)$, which is the same symmetry ellipses have, we conclude that $g(-z)=g(z)$, implying that all the odd-degree coefficients of $g$ are zero.
+Using the substitution $y=z^2$, we can obtain a degree-$6$ polynomial $f(y)=\sum_{k=1}^6 c_{2k} y^k$.
+Then, from a root $\hat{y}$ of $f$, we obtain a root $\hat{\theta} = angle(\hat{y})/2$ of $\xi$.
+Lastly, let $C(\theta)\in \R^2$ be the center of the circumcircle of $\Lambda(\theta)$, then from a root $\hat{\theta}$ of $\xi$, we obtain the solution $(\varphi^{-1}(C(\hat{\theta})) + u, \hat{\theta})$ of E3P.
+
+It worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe it can be used for further improvements.
+Analyzing the polynomials produced for several instances, we observed that $c_k = \overline{c_{6-k}}$, for all $k=0\dots 6$.
+
+\subsection{Choosing a precision constant}
+
+We developed an experiment to choose a precision constant for comparing if a root of $f$ is in the unit circle.
+The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of the polynomial $f$, more information about the implementation is given in \autoref{section:implementation}.
+For the experiment, we defined $K\in\R$, $K>0$, and consider instances with ellipse's shape parameters $(K, \frac{K}{2})$, for $K\in\{10^j\colon j=0,\dots,10\}$.
+
+The experiment considers instances of E3P where the three points are the vertices of an ellipse rotated by $\theta\in[0, \pi)$.
+Such instances only have one solution, and therefore, roots with multiplicity greater than one are expected, which can be seen as a special case.
+For each value of $K$, we ran the algorithm for $100$ instances generated randomly by sampling $\theta$ according to a uniform distribution.
+For each instance, we took the root $\hat{z}$ which produced the closest solution to the priorly known one.
+Then, for each $K$, as it can be seen in \autoref{fig:e3p_known_sols2}, we considered the maximum and the average distance to the unit circle $|1-|\hat{z}||$; and, as it can be seen in \autoref{fig:e3p_known_sols1}, the maximum and average error $|f(\hat{z})|$.
+
+From this experiment, we decided to adopt a precision constant of $10^{-6}$ to consider a root of $f$ to be in the unit circle, and as an additional check, we adopted a precision constant of $10^{-9}$ to consider a root to be a solution of E3P.
+
+\begin{figure}
+
+	\begin{subfigure}{.5\textwidth}
+		\centering
+
+		\includegraphics[scale=.5]{../tex/figures/e3p_known_sols2}
+		\caption{}
+		\label{fig:e3p_known_sols2}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+	\centering
+
+	\includegraphics[scale=.5]{../tex/figures/e3p_known_sols1}
+	\caption{}
+	\label{fig:e3p_known_sols1}
+	\end{subfigure}
+\caption{(a) shows the maximum and average distance to the unit circle $|1-|\hat{z}||$.
+(b) shows the maximum and average error $|f(\hat{z})|$, where $\hat{z}$ is a root of $f$ returned by our algorithm.}
+\end{figure}
+
+\subsection{Instances with four and six solutions}
+
+Any instance of E3P, as stated by \autoref{lema:e3p} can have up to six solutions.
+At first, though, this bound seemed to be loose as for randomly generated instances, we were not able to obtain instances with more than two solutions.
+
+After some investigation, though, we were able to construct some four-solution instances (an example is displayed in \autoref{fig:e3p_4sols}).
+An interesting property of those solutions is that every one of them has their three points form an isosceles triangle.
+
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.28]{../tex/figures/e3p_4sols}
+		\caption{An instance of E3P with four solutions.}
+		\label{fig:e3p_4sols}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.28]{../tex/figures/e3p_6sols}
+		\caption{An instance of E3P with six solutions.}
+		\label{fig:e3p_6sols}
+	\end{subfigure}
+\end{figure}
+
+Obtaining six-solution instances, on the other hand, was done by taking a particular case of the isosceles-triangle approach.
+As it can be seen in \autoref{fig:e3p_6sols}, the three points on every one of the six ellipses' border form an equilateral triangle.
+
+It should be pointed out that neither non-isosceles instances with four solutions nor non-equilateral instances with six solutions could be found.
+Further investigating these possible properties of E3P is left as future work.

### 2020-03-12 defesa/article/e3p.tex
wip

@@
 
-Initially, E3P is a problem with three unknown variables: $(q_x, q_y)$, and $\theta$. However, we can reduce this number to only one, as it will be shown, it is possible to obtain $q$ from $\theta$.
+Initially, E3P is a problem of determining the values of three unknown continuous variables $(q_x, q_y)$, and $\theta$.
+However, as it will be shown, we can reduce this number to only one, as it is possible to obtain $q$ uniquely from $\theta$.
 Let us assume that point $u$ is at the origin. If it is not, a simple translation by $-u$ applied to the three points can be made to put $u$ at the origin.

### 2020-03-12 defesa/article/article.tex
wip

--- 2020-03-10 defesa/article/article.tex
@@
-%% This is file `elsarticle-template-1-num.tex',
-%%
-%% Copyright 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%%
-%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
-%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
-%%
-\documentclass[a4]{elsarticle}
+\documentclass[3p, 11pt]{elsarticle}
 
@@
 %% The graphicx package provides the includegraphics command.
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
-%% The amssymb package provides various useful mathematical symbols
+\usepackage{hyperref}
 \usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%\usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-% \biboptions{}
-
+\usepackage{amsmath}
+\usepackage{subcaption}
 \journal{EJOR}
@@
 \newcommand{\bigO}{\mathscr{O}}
+\newtheorem{thm}{Theorem}
+\newtheorem{lem}[thm]{Lemma}
+\newdefinition{rmk}{Remark}
+\newdefinition{definition}{Definition}
+\newproof{pf}{Proof}
+
+\RequirePackage{algorithm, algpseudocode}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+\newcommand{\algorithmautorefname}{Algorithm}
+\newcommand{\definitionautorefname}{Definition}
+\newcommand{\thmautorefname}{Theorem}
 
@@
 
-	%%
-	%% Start line numbering here if you want
-	%%
-	%\linenumbers
+\section{Introduction}\label{section:introduction}
 
-	%% main text
-	\section{Introduction}
+\input{introduction.tex}
 
-	The Planar Maximum Covering Location Problem (PMCLP) was first introduced in \cite{church:1984}, and can be seen as a category of problems where the coverage of a demand set, a collection of subsets of $\R^2$, is to be maximized by determining the location of facilities in $\R^2$, with coverage being determined by a distance function.
-	In \cite{church:1984}, methods for Euclidean and Rectilinear distances versions of the problem were proposed.
-	In \cite{drezner, chazelle:1986}, exact algorithms for the Euclidean PMCLP with only one facility are proposed; and in \cite{cabello:2006} an approximation algorithm is proposed for the version with multiple unit disks as facilities.
-	A property of the Euclidean PMCLP, which is utilized in the algorithms developed in \cite{drezner, chazelle:1986, cabello:2006}, and in the method proposed in \cite{church:1984}, is that there is an optimal solution which every facility is located in the demand points, or in the intersection of two circles centered at two demand points; we will prove a similar property for ellipses in our work.
+\section{An algorithm for MCE}\label{section:mce}
 
-	It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
-In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
-For some instances, the method took too long and did not find an optimal solution.
-Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
-	The problem was further explored in \cite{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
-	The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.
+\input{mce.tex}
 
-	We study two versions of PMCLP with elliptical coverage facilities in this work.
-For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
-	In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
-	The first version will be referred to as Planar Maximum Covering Location by Ellipses Problem (MCE) and the second one as  Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER).
+\section{Determining every location of an ellipse given its shape and three points}\label{section:e3p}
 
-	\section{Problem Definition}
+\input{e3p.tex}
 
-	An instance of MCE and MCER is given by $n$ demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R$, $w_j>0$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j$.
-We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility.
-For MCE $E_j\colon\R^2\to\R^2$ is defined as
-	\begin{equation}
-	E_j(q) = \{p \in \R^2 \colon (p_x-q_x)^2/a_j^2 + (p_y-q_y)^2/b_j^2 \le 1\}.
-	\end{equation}
-	For MCER, we define $E_j \colon \R^2 \to \R^2 \times [0, \pi)$ as
-	\begin{equation}
-		E_j(q, \theta) = \left\{p \in \R^2 \colon 
-		\left|\left|
-		\left(
-		\begin{array}{rr}
-		\cos{\theta}/a_j & \sin{\theta}/a_j\\
-		\sin{\theta}/b_j & -\cos{\theta}/b_j
-		\end{array}
-		\right)
-		\left(
-		\begin{array}{c}
-		p_x-q_x\\
-		p_y-q_y
-		\end{array}
-		\right)
-		\right|\right|_2
-		\le 1
-		\right\}.
-	\end{equation}
+\section{An Algorithm for MCER}\label{section:mcer}
 
-Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE as the optimization problem 
-\begin{equation}
-\max_{q_1, \dots, q_m} \sum_{j=1}^m w(\Pp \cap E_j(q_j)),
-\end{equation}
-and similarly MCER as
-\begin{equation}
-\max_{(q_1, \theta_1), \dots, (q_m, \theta_m)} \sum_{j=1}^m w(\Pp \cap E_j(q_j, \theta_j)).
-\end{equation}
+\input{mcer.tex}
 
-To make the notation more clear, we denote an instance of MCE or MCER as the tuple $(\Pp, \Ww, \Rr)$, and a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$.
+\section{Implementation Details}\label{section:implementation}
 
-\section{An algorithm for MCE}
+\section{Numerical Experiments}\label{section:numerical}
 
-We will develop a method which is similar to the one developed in \cite{drezner} for only one euclidean disk, and the exact algorithm developed for multiple Euclidean disks in \cite{cabello:2006}. 
-We first describe a Candidate List set (CLS) for each facility, which is finite set of possible locations for each ellipse, which we use to converting MCE into a discrete optimization problem.
-We, then prove that using the possible solutions obtained from the combination of every ellipse's CLS an optimal solution can be obtained.
-
-%\subsection{An equivalent problem}
-
-Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, then for each $j=1\dots m$, consider $n$ ellipses with shape parameters $(a_j, b_j)$ centered at each one of the points in $\Pp$.
-Then, if we have $q_j\in\R^2$ and $X \subset \{1, \dots, n\}$, such that $q_j \in \cap_{i\in X}E_j(p_i)$.
-That is $q_j$ lies in the intersection of a subset of the ellipses centered at $\Pp$.
-Then $\Pp \cap E_j(q_j) = \{p_i \colon i \in X\}$, that is, if we place an ellipse at $q_j$, it will cover the points which are centers of the ellipses centered at $\Pp$ that contain $q_j$.
-From that observation, we can constrain each $q_j$ to be in $\cap_{i\in X} E_j(p_i)$, for some $X \subset \{1, \dots,n\}$, $X \neq \emptyset$.
-
-Let $(\R^2, ||\cdot||)$ be a strictly convex normed plane, and $\D=\{D_1(p_1), \dots, D_n(p_n)\}$ be a set of $n$ unit disks in that space, with the condition that  $\cap_{D\in\D} D \neq \emptyset$.
-In \cite{bi}, we have the following results about $\cap_{D \in \D} D$:
-\begin{itemize}
-	\item The $\partial \cap_{D \in \D} D$ is formed by arcs of $D_1(p_1), \dots, D_n(p_n)$.
-	\item The vertices of $\partial \cap_{D \in \D} D$ is contained in the set of pairwise-intersection of the circles $\partial D_1(p_1), \dots, \partial D_n(p_n)$.
-\end{itemize}
-
-\section{References}
+\section*{References}
 	%% New version of the num-names style
-	\bibliographystyle{elsarticle-num-names}
-	\bibliography{../references.bib}
+	\bibliographystyle{elsarticle-num}
+	\bibliography{../references}
 

### 2020-03-12 defesa/article/e3p.tex
wip

@@
 
-Let $A(\theta)$ denote the area of the triangle $\Lambda(\theta)$.
-Using the formula given in \cite[p.~189]{johnson1960} for the radius of the circumscribed circle of a triangle, we can obtain a function $\xi \colon [0, \pi) \to \R$ given by
-\begin{equation}\label{eq:circumscribed_circle_b}
-\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
-\end{equation}
-whose roots determine solutions of E3P.
-
-\begin{figure}
+\begin{figure}[!htb]
 	\centering
 
-	\includegraphics[scale=.3]{../tex/figures/circumscribed-circle}
-	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
+	\includegraphics[scale=.8]{figures/circumscribed-circle}
+	\caption{Transforming a solution of E3P into a solution of the circumcircle problem.}
 	\label{fig:circumscribed-circle}
 \end{figure}
+
+As circles are uniquely defined by three non-collinear points, the circumcircle of $\Lambda(\theta)$ is unique, and its radius and center can be determined analytically \cite{weisstein}.
+Let $|\Lambda(\theta)|$ denote the area of $\Lambda(\theta)$, using the formula from \cite[p.~189]{johnson1960} for the radius of a circumcircle of a triangle, and imposing that radius to be equal $b$, we define a function $\xi \colon [0, \pi) \to \R$ as
+\begin{equation}\label{eq:circumscribed_circle_b}
+\xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
+\end{equation}
+whose roots are angles of rotation which determine solutions of E3P through the inverse transformation $\varphi^{-1}$.
+From a root $\hat{\theta}$ of $\xi$, let $\hat{q}$ be the center of the circumcircle of $\Lambda(\hat{\theta})$, the solution $(\varphi^{-1}(\hat{q}), \hat{\theta})$ of E3P is obtained.
+
+The algorithm for MCER described in the next section, of which E3P is a subproblem, goes through every solution of several instances of E3P.
+This is only possible if the number of solutions of E3P is finite, and it is only viable if that number is small.
+Next we introduce a lemma regarding that matter.
 
@@
 
-By using the two identities $\cos{\theta} = (e^{i\theta} + e^{-i\theta})/2$, and $\sin{\theta} = (e^{i\theta} - e^{-i\theta})/(2i)$, which relate trigonometric functions with complex numbers in the unit circle $\mathbb{S}=\{z\in \mathbb{C}\colon |z|=1\}$, we can rewrite $\xi$ as a function of the new variable $z=e^{i\theta}\in\mathbb{S}$.
+By using the two identities $\cos{\theta} = (e^{i\theta} + e^{-i\theta})/2$, and $\sin{\theta} = (e^{i\theta} - e^{-i\theta})/(2i)$, which relate trigonometric functions with complex numbers in the unit circle $\mathbb{S}=\{z\in \mathbb{C}\colon |z|=1\}$, we can rewrite $\xi$ as a function of the variable $z=e^{i\theta}\in\mathbb{S}$.
 In \cite{weidner}, it is stated that this substitution when utilized for the task of determining the roots of a real trigonometric polynomial does not yield loss of accuracy.
@@
 Multiplying $\xi$ by $z^6$ and extending the domain of $z$ to $\mathbb{C}$, we obtain a complex polynomial $g(z)=\sum_{k=0}^{12} c_k z^k$, for some $c_0, \dots, c_{12} \in \mathbb{C}$.
-In practice, symbolic computation can be used to obtain the actual coefficients of $g$ in terms of an instance of E3P.
+In practice, we utilize symbolic computation to obtain the actual coefficients of $g$ in terms of an instance of E3P.
 
-Let $angle \colon \mathbb{C} \colon [0, 2\pi)$ be a function that returns the angle of a complex number, then given a root $\hat{z}$ of $g$, if $|\hat{z}|=1$ and $angle(\hat{z}) \in [0, \pi)$, then $\hat{\theta} = angle(\hat{z})$ is a root of $\xi$.
-Observing that for any $z\in \mathbb{C}$, $angle(-z)=\pi+angle(z)$, which is the same symmetry ellipses have, we conclude that $g(-z)=g(z)$, implying that all the odd-degree coefficients of $g$ are zero.
-Using the substitution $y=z^2$, we can obtain a degree-$6$ polynomial $f(y)=\sum_{k=1}^6 c_{2k} y^k$.
-Then, from a root $\hat{y}$ of $f$, we obtain a root $\hat{\theta} = angle(\hat{y})/2$ of $\xi$.
-Lastly, let $C(\theta)\in \R^2$ be the center of the circumcircle of $\Lambda(\theta)$, then from a root $\hat{\theta}$ of $\xi$, we obtain the solution $(\varphi^{-1}(C(\hat{\theta})) + u, \hat{\theta})$ of E3P.
+Let $angle \colon \mathbb{C} \colon [0, 2\pi)$ be a function that takes a complex number and returns its angle, then given a root $\hat{z}$ of $g$, if $|\hat{z}|=1$ and $angle(\hat{z}) \in [0, \pi)$, then $\hat{\theta} = angle(\hat{z})$ is a root of $\xi$.
 
-It worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe it can be used for further improvements.
+Observing that for any $z\in \mathbb{C}$, $angle(-z)=\pi+angle(z)$, and that for any ellipse the angles of rotation $\theta$ and $\theta + \pi$ are equivalent, we conclude that $g(-z)=g(z)$.
+This implies that all the odd-degree coefficients of $g$ are zero.
+Therefore, we can use the substitution $y=z^2$ to obtain a degree-$6$ polynomial $f(y)=\sum_{k=1}^6 c_{2k} y^k$ whose roots can be used to determine the roots of $\xi$: from a root $\hat{y}$ of $f$, $\hat{y}\in\mathbb{S}$, we have that $\hat{\theta}=angle(\hat{y})/2$ is a root of $\xi$.
+
+Therefore, using the QR algorithm to obtain the eigenvalues of a companion matrix of the polynomial $f$, we can conclude that an algorithm to obtain every solution of E3P can be implemented, and that such algorithm takes a constant number of operations to do so.
+
+%Lastly, It worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe it can be used for further improvements.
 Analyzing the polynomials produced for several instances, we observed that $c_k = \overline{c_{6-k}}$, for all $k=0\dots 6$.
@@
 
-We developed an experiment to choose a precision constant for comparing if a root of $f$ is in the unit circle.
-The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of the polynomial $f$, more information about the implementation is given in \autoref{section:implementation}.
-For the experiment, we defined $K\in\R$, $K>0$, and consider instances with ellipse's shape parameters $(K, \frac{K}{2})$, for $K\in\{10^j\colon j=0,\dots,10\}$.
+In this section, we describe an experiment we made to choose a precision constant for comparing if a root of $f$ returned as an eigenvalue of its companion matrix is in the unit circle.
+The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of $f$, more information about the implementation is given in \autoref{section:implementation}.
+For the experiment, we defined $K\in\R$, $K>0$, and considered instances with the ellipse's shape parameters $(K, \frac{K}{2})$, for $K\in\{10^j\colon j=0,\dots,10\}$.
 
-The experiment considers instances of E3P where the three points are the vertices of an ellipse rotated by $\theta\in[0, \pi)$.
-Such instances only have one solution, and therefore, roots with multiplicity greater than one are expected, which can be seen as a special case.
+The experiment considered instances of E3P where the three points are the vertices of an ellipse rotated by $\theta\in[0, \pi)$.
+Such instances only have one solution, and therefore, roots with multiplicity greater than one are expected.
 For each value of $K$, we ran the algorithm for $100$ instances generated randomly by sampling $\theta$ according to a uniform distribution.
-For each instance, we took the root $\hat{z}$ which produced the closest solution to the priorly known one.
-Then, for each $K$, as it can be seen in \autoref{fig:e3p_known_sols2}, we considered the maximum and the average distance to the unit circle $|1-|\hat{z}||$; and, as it can be seen in \autoref{fig:e3p_known_sols1}, the maximum and average error $|f(\hat{z})|$.
+For each instance, we took the root $\hat{z}$ which produced the closest solution to the known one.
+Then, for each $K$, as it can be seen in \autoref{fig:e3p_known_sols2}, we considered the maximum and the average distance to the unit circle $|1-|\hat{z}||$; and, as it presented in \autoref{fig:e3p_known_sols1}, the maximum and average error $|f(\hat{z})|$.
 
@@
 
-\begin{figure}
+\begin{figure}[!htb]
 
@@
 
-		\includegraphics[scale=.5]{../tex/figures/e3p_known_sols2}
+		\includegraphics[scale=.8]{figures/e3p_known_sols2}
 		\caption{}
@@
 
-	\includegraphics[scale=.5]{../tex/figures/e3p_known_sols1}
+	\includegraphics[scale=.8]{figures/e3p_known_sols1}
 	\caption{}
@@
 	\end{subfigure}
-\caption{(a) shows the maximum and average distance to the unit circle $|1-|\hat{z}||$.
-(b) shows the maximum and average error $|f(\hat{z})|$, where $\hat{z}$ is a root of $f$ returned by our algorithm.}
+\caption{(a) shows the maximum and average distance to the unit circle $|1-|\hat{z}||$. (b) shows the maximum and average error $|f(\hat{z})|$.}
 \end{figure}
@@
 
-After some investigation, though, we were able to construct some four-solution instances (an example is displayed in \autoref{fig:e3p_4sols}).
-An interesting property of those solutions is that every one of them has their three points form an isosceles triangle.
+After some investigation, we were able to construct some four-solution instances (an example is displayed in \autoref{fig:e3p_4sols}).
+An interesting property of those solutions is their three points form an isosceles triangle.
 
-\begin{figure}
+\begin{figure}[!htb]
 	\begin{subfigure}{.5\textwidth}
@@
 		\includegraphics[scale=.28]{../tex/figures/e3p_4sols}
-		\caption{An instance of E3P with four solutions.}
+		\caption{}
 		\label{fig:e3p_4sols}
@@
 		\includegraphics[scale=.28]{../tex/figures/e3p_6sols}
-		\caption{An instance of E3P with six solutions.}
+		\caption{}
 		\label{fig:e3p_6sols}
 	\end{subfigure}
+\caption{(a) The four solutions for an instance of E3P where the three points form an isosceles triangle.
+(b) The six solutions for an instance of E3P where the three points form an equilateral triangle.}
 \end{figure}
 
-Obtaining six-solution instances, on the other hand, was done by taking a particular case of the isosceles-triangle approach.
-As it can be seen in \autoref{fig:e3p_6sols}, the three points on every one of the six ellipses' border form an equilateral triangle.
+Six-solution instances were found by taking a particular case of the four-solution instances, we took the three points as the vertices of a equilateral triangle.
+An example of that is shown in \autoref{fig:e3p_6sols}.
 

### 2020-03-12 defesa/article/introduction.tex
wip

	
	The Planar Maximum Covering Location Problem (PMCLP) was first introduced in \cite{church:1984}, and can be seen as a category of problems where the coverage of a demand set, a collection of subsets of $\R^2$, is to be maximized by determining the location of facilities in $\R^2$, with coverage being determined by a distance function.
	In \cite{church:1984}, methods for Euclidean and Rectilinear distances versions of the problem were proposed.
	In \cite{drezner, chazelle:1986}, exact algorithms for the Euclidean PMCLP with only one facility are proposed; and in \cite{cabello:2006} an approximation algorithm is proposed for the version with multiple unit disks as facilities.
	A property of the Euclidean PMCLP, which is utilized in the algorithms developed in \cite{drezner, chazelle:1986, cabello:2006}, and in the method proposed in \cite{church:1984}, is that there is an optimal solution which every facility is located in the demand points, or in the intersection of two circles centered at two demand points; we will prove a similar property for ellipses in our work.

	It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it. In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem. For some instances, the method took too long and did not find an optimal solution. Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
	The problem was further explored in \cite{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
	The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.

	We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
	In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
	The first version will be referred to as Planar Maximum Covering Location by Ellipses Problem (MCE) and the second one as  Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER).

	\section{Problem Definition}

	An instance of MCE and MCER is given by $n$ demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R$, $w_j>0$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j$. We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility. For MCE $E_j\colon\R^2\to\R^2$ is defined as
	\begin{equation}
	E_j(q) = \{p \in \R^2 \colon (p_x-q_x)^2/a_j^2 + (p_y-q_y)^2/b_j^2 \le 1\}.
	\end{equation}
	For MCER, we define $E_j \colon \R^2 \to \R^2 \times [0, \pi)$ as
	\begin{equation}
		E_j(q, \theta) = \left\{p \in \R^2 \colon 
		\left|\left|
		\left(
		\begin{array}{rr}
		\cos{\theta}/a_j & \sin{\theta}/a_j\\
		\sin{\theta}/b_j & -\cos{\theta}/b_j
		\end{array}
		\right)
		\left(
		\begin{array}{c}
		p_x-q_x\\
		p_y-q_y
		\end{array}
		\right)
		\right|\right|_2
		\le 1
		\right\}.
	\end{equation}

Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE as the optimization problem 
\begin{equation}
\max_{q_1, \dots, q_m} \sum_{j=1}^m w(\Pp \cap E_j(q_j)),
\end{equation}
and similarly MCER as
\begin{equation}
\max_{(q_1, \theta_1), \dots, (q_m, \theta_m)} \sum_{j=1}^m w(\Pp \cap E_j(q_j, \theta_j)).
\end{equation}

To make the notation more clear, we denote an instance of MCE or MCER as the tuple $(\Pp, \Ww, \Rr)$, and a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$. We also use $\partial$ as the boundary operator, for example, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$ given an instance of MCE.

### 2020-03-12 defesa/article/mce.tex
wip

We will develop a method which is similar to the one developed in \cite{drezner} for only one euclidean disk, and the exact algorithm developed for multiple Euclidean disks in \cite{cabello:2006}. 
We first describe a Candidate List set (CLS) for each facility, which is finite set of possible locations for each ellipse, which we use to converting MCE into a discrete optimization problem. We, then prove that using the possible solutions obtained from the combination of every ellipse's CLS an optimal solution can be obtained.

%\subsection{An equivalent problem}

Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, then for each $j=1\dots m$, consider $n$ ellipses with shape parameters $(a_j, b_j)$ centered at each one of the points in $\Pp$. If we have $q_j\in\R^2$ in a subset of the coverage areas of those ellipses, then $q_j$ is a solution of MCE covering the centers of those ellipses. In other words, if $q_j \in \R^2$, and $X \subset \{1, \dots, n\}$, $X \neq \emptyset$, such that $q_j \in \cap_{i\in X}E_j(p_i)$, then $\Pp \cap E_j(q_j) = \{p_i \colon i \in X\}$.
From that observation, we can constrain each $q_j$ to be in $\cap_{i\in X} E_j(p_i)$, for some $X \subset \{1, \dots,n\}$, $X \neq \emptyset$.

In \cite{bi}, an algorithm is proposed for the problem of determining the intersection of disks of fixed radii from a strictly convex normed plane. 
We say that $(\R^2, ||\cdot||)$ is a strictly convex normed plane if the unit disk given by the norm $||\cdot||$ is strictly convex. Note that for any ellipse, there is a strictly convex normed plane whose unit circle is that ellipse.
For that reason, we state some results from \cite{bi} here, which we use on the development of an algorithm for MCE.

Let $(\R^2, ||\cdot||)$ be a strictly convex normed plane, and $\D=\{D_1, \dots, D_n\}$ be a set of $n$ unit disks in that space centered at different points, with the condition that  $\cap_{i=1}^n D_i \neq \emptyset$. In \cite{bi}, an algorithm was developed to construct this intersection in $\bigO(n\lg{n})$, some of its preliminary results are:
\begin{itemize}
	\item $\partial \cap_{i=1}^n D_i$ is formed by arcs of $\partial D_1, \dots, \partial D_n$.
	\item The vertices of $\partial \cap_{i=1}^n D_i$ is contained in the set of pairwise-intersection of the circles $\partial D_1, \dots, \partial D_n$.
	\item $|\partial D_i \cap \partial D_j| \le 2$.
\end{itemize}

Based on those, we introduce the next definition for the $k$-th ellipse's CLS, which we refer to as $S_k$.

\begin{definition}\label{def:cls_mce}
	Given an instance of MCE, for any $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
	\begin{equation}
	S_k = \bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \bigcup \Pp.
	\end{equation}
\end{definition}

The set of solutions $S_k$, can be computed in $\bigO(n^2)$ as determining the intersections between two axis-parallel ellipses can be done analytically.

\begin{lem}
	Given an instance of MCE, and $S_1, \dots, S_m$ as defined by \autoref{def:cls_mce}, then the set $\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$. 
\end{lem}
\begin{pf}
	Let $Q^*$ be an optimal solution of MCE for the given instance. Then, we are going to prove that there exists $Q' \in \Omega$, which is also optimal.

	For each $k=1, \dots, m$, let $X_k = \{p_i \in \Pp\colon p_i \in E_k(q_k^*)\}$.

	If $|X_k| = 0$, then any $q_k \in S_k$ makes $X_k \subset \Pp \cap E_k(q_k)$.

	if $|X_k| = 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.

	if $|X_k| > 1$, then let $Y_k = \cap_{p \in X_k}E_k(p)$, by the results of \cite{bi}, we have that the boundary of $Y_k$ has vertices in the pairwise intersections of $\{\partial E_k(p) \colon p \in X_k\}$. Therefore, at least one vertex of $Y_k$ is in $S_k$, and any of those vertices produce a solution that covers at least the same points covered by $Q^*$.

	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$ hence $|\Omega| \le n^{2m}$.
\end{pf}

With all this in hand, we can go ahead and define an algorithm for MCE.

\begin{algorithm}
	\caption{Algorithm for MCE}\label{algoritmo:mce}

	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}

		\Ensure{An optimal solution for MCE.}

		\item[]
		\Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
		\State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
		\EndProcedure
		\State
		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
		\If{$j = m+1$}
		\State \Return $0$
		\EndIf

		\State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$
		\State Let $S_j$ be the CLS for the $j$-th ellipse as defined by \autoref{def:cls_mce}.
		%\State $S_j \gets \textnormal{CLS-MCE}(Z, a_j, b_j)$
		\For{$q_j \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j)$
		\State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$

		\If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
		\State $(q_j^*, \dots, q_m^*) \gets(q_j, \dots, q_m)$
		\EndIf
		\EndFor

		\State \Return $(q_j^*, \dots, q_m^*)$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\autoref{algoritmo:mce} can be proved to have a runtime complexity of $\bigO(mn^{2m+1})$.

### 2020-03-12 defesa/article/mcer.tex
wip

The version of PMCLP where the facilities are ellipses that can be freely rotated was first introduced in \cite{andreta} where an exact and a heuristic method were developed for it. In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem. We propose an algorithm for MCER which is able to obtain optimal solutions for every instance proposed in \cite{andreta} including the ones its exact method could not, and its heuristic obtained non-optimal ones.

### 2020-03-13 defesa/article/mcer.tex
wip

@@
 We propose an algorithm for MCER which is able to obtain optimal solutions for every instance proposed in \cite{andreta} including the ones its exact method could not, and its heuristic obtained non-optimal ones.
+
+\begin{definition}
+	Two solutions $Q$ and $Q'$ of MCER, are said to be equivalent to each other if \mbox{$\cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$}.
+\end{definition}
+
+Next, we introduce a lemma which states that any optimal solution of MCER has an equivalent solution where every ellipse that covers at least two points has two points on its border.
+
+\begin{lem}\label{lema:mce_2b}
+	Let $Q^*$ be an optimal solution of MCER. 
+	Then, there exists an equivalent solution $Q'$ to $Q^*$, such that for any $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, $|\Pp \cap \partial E_j(q_j', \theta_j')|\ge 2$.
+\end{lem}
+
+\begin{pf}
+	First, let $q_j'=q_j^*$ and ignore the angle of rotation as it does not change, and assume that we are dealing with axis-parallel ellipses.
+
+	Let $A=\Pp \cap E_j(q_j^*, \theta_j^*)$ be the set of points covered by the $j$-th ellipse and $X=\cap_{p \in A}E_j(p, \theta_j^*)$ be the region of intersection of ellipses centered at each point in $A$.
+By \cite{bi}, the vertices of $\partial X$ are in the set of pairwise intersections of $\{\partial E_j(p, \theta_j^*)\colon p \in A\}$.
+Setting $q_j'$ as any of these vertices makes $E_j(q_j', \theta_j^*)$ have two points on its border.
+\end{pf}
+
+Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.
+
+\begin{definition}
+	Let $Q^*$ be an optimal solution of MCER.
+We define $\Pi(Q^*)$ as the set of every equivalent solution to $Q^*$, such that for any $Q \in\Pi(Q^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j')| \ge 2$.
+\end{definition}
+
+Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.
+
+\begin{definition}\label{def:feasible_angle}
+	Let $E$ be the coverage region of an ellipse and $u, v \in \R^2$.
+An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
+	In addition to that, given an instance of MCER, the set of $(E_j, u, v)$-feasible angles is referred to as
+
+	\begin{equation}
+	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
+	\end{equation}
+	We also define $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
+Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
+\end{definition}
+
+\begin{lem}\label{lema:3pnts}
+	Let $Q^*$ be an optimal solution of MCER; and $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$.
+	If for all $Q'$ equivalent to $Q^*$, $|\Pp \cap E_j(q_j', \theta_j')| < 3$, then there exists $\{u, v\} \subset \Pp \cap E_j(q_j^*, \theta_j^*)$, such that for all $\theta_j\in \Phi_j(u,v)$ there exists $q_j \in \R^2$, such that $\Pp \cap E_j(q_j, \theta_j) = \Pp \cap E_j(q_j^*, \theta_j^*)$.
+
+	%For any $Q'\in\Pi(Q^*)$ and $\{u, v\} \subset \Pp \cap \partial E_j(q_j', \theta_j')$,
+	%if there exists $\theta_j \in \Phi_j(u,v)$, such that for all $q_j \in\delta_j(u,v)$, $\Pp \cap E_j(q_j, \theta_j) \neq \Pp \cap E_j(q_j^*, \theta_j^*)$, then there exists an equivalent solution $\hat{Q}$ to $Q^*$, such that $|\Pp \cap \partial E_j(\hat{q}_j, \hat{\theta}_j)| \ge 3$.
+
+%	If, for all $\hat{Q}$ equivalent to $Q^*$, $|\Pp\cap \partial E_j(\hat{q}_j, \hat{\theta}_j)| < 3$, then for all $\theta\in\Phi_j(u,v)$, there exists $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
+
+\end{lem}
+
+\begin{pf}
+	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E_j(q^*_j, \theta^*_j)$, such that an equivalent optimal solution $(Q', \Theta')$ exists with $u$ and $v$ on the border of $E_j(q_j', \theta_j^*)$.
+Therefore, $\theta_j^*\in\Phi_j(u,v)$.
+
+	Now suppose that $u$ and $v$ have the same $y$-coordinate, if they do not, a rotation can be applied to make them have the same $y$-coordinate.
+Then, the first thing we are proving is that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that any instance can be transformed into using translation and rotation on every element of $\Pp$.
+
+	In \autoref{chapter:definitions}, a function $L\colon \R \to \R_{\ge0}$ was defined in \autoref{eq:function-l}.
+This function takes the angular coefficient $m\in\R$ and, considering the family of lines parallel to the one described by $y=mx$, returns the maximum squared distance between two intersection points of a line in that family and an axis-parallel ellipse centered at the origin.
+
+	To use those results here, we need to consider the ellipse to be fixed at the origin and axis-parallel, and consider the problem of rotating and translating the points in $\Pp$ instead.
+
+	Let $\theta \in [0, \pi]\setminus\{\pi/2\}$, and $u', v'$ be the points $u, v$ after a rotation by $\theta$.
+Then, if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to apply a translation to $u',v'$, such that they end up on the fixed ellipse.
+This means that it is possible to find an angle of rotation and a center to place $E_j$, such that it has $u, v$ on its border.
+
+	Now we use some properties of function $L$ whose details are given in \autoref{chapter:definitions}.
+	Defining $l(\theta)=L(\tan{\theta})$, with $l:[0, \pi]\setminus\{\pi/2\}$, we can say that
+
+	\begin{itemize}
+		\item $l$ is decreasing in $[0, \pi/2)$ because $L$ is decreasing in $[0, \infty)$.
+Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\alpha, \pi/2)$.
+That implies $[0, \alpha] \subset \Phi_j(u,v)$.
+		\item $l(\theta) = l(\pi-\theta)$ because $L$ is an even function.
+Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\pi/2,\pi-\alpha)$.
+That implies $[\pi-\alpha, \pi] \subset \Phi_j(u,v)$.
+	\end{itemize}
+	We then conclude that $\Phi_j(u, v) = [0, \alpha]\cup [\pi-\alpha, \pi]$, and, of course, in the case that there is no $\alpha\in[0, \pi/2)$, such that $l(\alpha)=||v-u||_2^2$, we have $\Phi_j(u,v)=[0, \pi]$.
+	From that, if we rotate every point in $\Pp$ by $\pi-\alpha$, we obtain $\Phi_j(u,v)=[0, 2\alpha]$.
+
+	With this result in hand, we can use a continuity argument to complete our proof as follows.
+	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
+Notice that, in general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, imposing $\delta(\theta_j') = q_j'$ makes $\delta$ be a well-defined function.
+This is shown in \autoref{fig:lema-3-points} where $\delta$ is plotted for the whole interval $\Phi_j(u,v)$.
+
+	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-hand-side of \autoref{eq:rotated_ellipse}.
+Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$ as they are covered by the $j$-th ellipse.
+
+	Then, to evaluate $f_w$ for every center and feasible angle that maintains $u$ and $v$ on $E_j$'s border, we introduce a new function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$, which is defined as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
+	As $f_w$ and $\delta$ are both continuous functions, $g_w$ is also continuous.
+
+	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>0$.
+Then, by continuity, another angle $\bar{\theta} \in \Phi_j(u,v)$ must exist, such that $g_w(\bar{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
+The same can be said about the case where there exists an angle $\theta \in \Phi_j(u,v)$, such that a point $w \in \Pp \setminus E_j(q_j^*, \theta_j^*)$ enters the coverage of $E_j(\delta(\theta), \theta)$.
+\end{pf}

### 2020-03-13 defesa/article/introduction.tex
wip

@@
 	An instance of MCE and MCER is given by $n$ demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R$, $w_j>0$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j$.
-We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility.
-For MCE $E_j\colon\R^2\to\R^2$ is defined as
+We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$.
+Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R$ denote the elliptical norm given by
 	\begin{equation}
-	E_j(q) = \{p \in \R^2 \colon (p_x-q_x)^2/a_j^2 + (p_y-q_y)^2/b_j^2 \le 1\}.
-	\end{equation}
-	For MCER, we define $E_j \colon \R^2 \to \R^2 \times [0, \pi)$ as
-	\begin{equation}
-		E_j(q, \theta) = \left\{p \in \R^2 \colon 
-		\left|\left|
-		\left(
-		\begin{array}{rr}
-		\cos{\theta}/a_j & \sin{\theta}/a_j\\
-		\sin{\theta}/b_j & -\cos{\theta}/b_j
+	||x||_{a,b, \theta}=\left|\left|
+	\left(\begin{array}{rr}
+	\cos{\theta} & \sin{\theta}\\
+	\sin{\theta} & -\cos{\theta}
 	\end{array}
 	\right)
-		\left(
-		\begin{array}{c}
-		p_x-q_x\\
-		p_y-q_y
-		\end{array}
-		\right)
-		\right|\right|_2
-		\le 1
-		\right\}.
+	\left(\begin{array}{cc}
+	a_j & 0\\
+	0 & b_j
+	\end{array}\right) x \right|\right|_2,
 	\end{equation}
+	then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.
 
@@
 To make the notation more clear, we denote an instance of MCE or MCER as the tuple $(\Pp, \Ww, \Rr)$, and a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$.
-We also use $\partial$ as the boundary operator, for example, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$ given an instance of MCE.
+Additionally, whenever we have an instance with only one ellipse, we omit the index referring to the facility, and define a solution of MCE as $q\in\R^2$, and of MCER as $(q, \theta) \in \R^2\times [0, \pi)$.
+We also use $\partial$ as the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$.

### 2020-03-13 defesa/article/mcer.tex
wip

--- 2020-03-12 defesa/article/mcer.tex
@@
 The version of PMCLP where the facilities are ellipses that can be freely rotated was first introduced in \cite{andreta} where an exact and a heuristic method were developed for it.
-In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem.
+In comparison with MCE, this problem introduces a new variable that is responsible for determining the angle of rotation of every ellipse, making MCER a more challenging problem.
 We propose an algorithm for MCER which is able to obtain optimal solutions for every instance proposed in \cite{andreta} including the ones its exact method could not, and its heuristic obtained non-optimal ones.
+
+\begin{definition}
+	Two solutions $Q$ and $Q'$ of MCER, are said to be equivalent to each other if \mbox{$\cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$}.
+Also, if $\cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) \subset \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$, then we say that $Q' \succ Q$.
+\end{definition}
+
+%\begin{definition}
+%	Let $x \in \R^2$, we define $\angle x$ as the angle between the vector $(1, 0)$ and $x$.
+%\end{definition}
+
+Next, we introduce a lemma which states that any optimal solution of MCER has an equivalent solution where every ellipse that covers at least two points has two points on its border.
+
+\begin{lem}\label{lema:mce_2b}
+	Let $Q^*$ be a solution of MCER for an instance $(\Pp, \Ww, \{(a,b)\})$.
+	If $|\Pp \cap E(q^*, \theta^*)| \ge 2$, then there exists a solution $Q$ for the same instance, such that $Q \succ Q^*$, and $|\Pp \cap \partial E(q, \theta)|\ge 2$.
+\end{lem}
+
+\begin{proof}
+	First, let $\theta=\theta^*$ and ignore the angle of rotation as it does not change, and assume that we are dealing with an axis-parallel ellipse.
+
+	Let $A=\Pp \cap E(q^*, \theta^*)$ and $X=\cap_{p \in A}E(p, \theta^*)$ be the region of intersection of ellipses centered at each point in $A$.
+By \cite{bi}, the vertices of $\partial X$ are in the set of pairwise intersections of $\{\partial E(p, \theta^*)\colon p \in A\}$.
+Setting $q$ as any of these vertices makes $E(q, \theta)$ have two points on its border.
+\end{proof}
+
+%Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.
+
+%\begin{definition}
+%	Let $Q^*$ be an optimal solution of MCER.
+We define $\Pi(Q^*)$ as the set of every equivalent solution to $Q^*$, such that for any $Q \in\Pi(Q^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j')| \ge 2$.
+%\end{definition}
+
+Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.
+
+\begin{definition}\label{def:feasible_angle}
+	Let $E$ be the coverage region of an ellipse and $u, v \in \R^2$.
+An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
+	In addition to that, the set of $(E, u, v)$-feasible angles is referred to as
+
+	\begin{equation}
+	\Phi(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E,u,v)\textnormal{-feasible angle}\}.
+	\end{equation}
+	%We also define $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
+Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
+\end{definition}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=.22]{figures/feasible-angle2}
+	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
+	\label{fig:feasible-angle}
+\end{figure}
+
+Next we open a parenthesis to discuss the problem of deciding when it is possible to fit two points on an ellipse.
+
+\begin{lem}\label{lema:l-function}
+	Given an instance $(\Pp, \Ww, \{(a, b)\})$ of MCER, if $u, v \in \Pp$ have the same $y$-coordinate and $||u-v||_2 \le 2a$, then $\Phi(u,v) = [0, \alpha] \cup [\pi - \alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
+\end{lem}
+
+\begin{proof}
+
+	Consider an axis-parallel ellipse with shape parameters $(a, b)\in\R^2_{>0}$, centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
+Suppose that this line intersects the ellipse at least at one point.
+By plugging the line's equation into $x^2/a^2+y^2/b^2=1$, it is possible to obtain the distance between the intersection points.
+The final expression is given by
+	\begin{equation*}\label{eq:dist_line_ellipse}
+	D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
+	\end{equation*}
+	with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$.
+	If $D(m, c) = ||u-v||_2$, then there exists $q_1, q_2 \in \R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$ and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
+It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$.
+	Following that, we define a function $L:\R\mapsto\R$ as
+
+	\begin{equation}\label{eq:function-l}
+	L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
+	\end{equation}
+	which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.
+From that, if $L(m) \ge ||v-u||_2^2$, then there exists $q_1, q_2\in\R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$, and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
+
+	It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
+Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
+	%In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.
+
+	If $\inf{L} \ge ||u-v||_2^2$, then $\Phi(u,v) = [0, \pi)$.
+	Otherwise, let $\beta \in \R$, $\beta \ge 0$, such that $L(\beta) = ||u-v||_2^2$, then as $m>\beta$, we have $L(m) < ||u-v||_2^2$, which means that it is impossible to make the ellipse contain $u$, and $v$.
+	As $L$ is an even function, the same can be said for $m < \beta$. Therefore, we conclude that $\Phi(u,v)=[0, \tan(\beta)] \cup [\pi-\tan(\beta), \pi)$.
+\end{proof}
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[scale=.4]{../tex/figures/L-function-plot}
+%	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
+%	\label{fig:L-function-plot}
+%\end{figure}
+
+%%% Fim L function
+
+\begin{lem}\label{lema:3pnts}
+	Let $Q^*$ be a solution of MCER for the instance $(\Pp, \Ww, \{(a, b)\})$, such that $|\Pp \cap E(q^*, \theta^*)|\ge2$.
+	If for all $\bar{Q} \succ Q^*$, $|\Pp \cap \partial E(\bar{q}, \bar{\theta})| < 3$, then there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that for all $\theta\in \Phi(u,v)$ there exists $q \in \R^2$, such that $(q, \theta)$ is equivalent to $Q^*$.
+\end{lem}
+
+\begin{proof}
+	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that $Q' \succ Q^*$ exists, and $\{u, v\} \subset \partial E(q', \theta^*)$.
+Therefore, $\theta^*\in\Phi(u,v)$.
+
+	Suppose that $u$ and $v$ have the same $y$-coordinate, if they do not, a rotation can be applied to make them do.
+Then, by \autoref{lema:l-function}, $\Phi(u,v)=[0, \alpha] \cup [\pi-\alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
+Then, if we rotate the coordinate system by $\pi-\alpha$, we obtain $\Phi(u,v)=[0, 2\alpha]$.
+
+	With this result in hand, we can use a continuity argument to complete our proof as follows.
+	Let $\delta : \Phi(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E(\delta(\theta), \theta)$, and, from solution $Q'$, $\delta(\theta') = q'$.
+Notice that, in general, for any angle in $\Phi(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, imposing $\delta(\theta') = q'$ makes $\delta$ be a well-defined continuous function.
+This is shown in \autoref{fig:lema-3-points} where $\delta$ is plotted for the whole interval $\Phi(u,v)$.
+
+	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes an angle of rotation $\theta$ and returns the elliptical distance $||\cdot||_{a,b,\theta}$ to the center $\delta(\theta)$; that is $f_w(\theta)=||w-\delta(\theta)||_{a,b,\theta}$.
+	We have that if $w \in \Pp \cap E(q^*, \theta^*)$, then $f_w(\theta^*) \le 1$; and if $w \not\in \Pp \cap E(q^*, \theta^*)$, then $f_w(\theta^*) > 1$.
+
+	Therefore, if there exists $\theta\in\Phi(u,v)$, such that for all $q\in\R^2$, $(q, \theta)$ is not equivalent to $Q^*$, then there exists either $w \in \Pp \cap E(q^*, \theta^*)$, with $f_w(\theta)>1$, or $w \not\in \Pp \cap E(q^*, \theta^*)$, with $f_w(\theta)\le 1$.
+Because $f_w$ is continuous, there exists $\bar{\theta}\in\Phi(u,v)$, such that $f_w(\theta)=1$, implying that $|\Pp \cap \partial E(\delta(\bar{\theta}), \bar{\theta})| \ge 3$.
+\end{proof}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=.7]{figures/lema-3-points}
+	\caption{A visualization of \autoref{lema:3pnts}.}
+	\label{fig:lema-3-points}
+\end{figure}

### 2020-03-15 defesa/article/introduction.tex
wip

@@
 
-	An instance of MCE and MCER is given by $n$ demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R$, $w_j>0$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j$.
+	An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j > 0$.
 We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$.
-Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R$ denote the elliptical norm given by
+Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
 	\begin{equation}
@@
 	\end{equation}
-	then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.
+	then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j,0} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.
 
@@
 We also use $\partial$ as the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$.
+
+\subsection{Facility Cost}
+
+Additionally, in \cite{canbolat, andreta}, two other parameters are present in the definition of the problem.
+This extension is the result of having costs associated with every facility hence, to create a decision about which ones are utilized, a new parameter $k\in\mathbb{N}$ is given limiting the number of utilized ellipses to be exactly $k$.
+
+We refer to this version of the problem as  MCE-$k$, and MCER-$k$.
+An instance of it is given by the same parameters as MCE and MCER, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost, and $k\in\mathbb{N}$, $k\le m$.
+A solution needs another set $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$ to express the indexes of the utilized ellipses.
+
+Solving MCE-$k$ (MCER-$k$) can be done by considering the $\binom{m}{k}$ instances of MCE (MCER-$k$), and then taking the best one as the optimal solution, taking into account the cost of each utilized ellipse.
+As this step can be seen as trivial, we propose algorithms for MCE and MCER, and then in \autoref{section:numerical}, as we use the instances from \cite{canbolat, andreta} in the numerical experiments, we analyze the results obtained by our implementations of the algorithms proposed in this work for MCE-$k$ and MCER-$k$.

### 2020-03-15 defesa/article/mce.tex
wip

@@
-We will develop a method which is similar to the one developed in \cite{drezner} for only one euclidean disk, and the exact algorithm developed for multiple Euclidean disks in \cite{cabello:2006}. 
-We first describe a Candidate List set (CLS) for each facility, which is finite set of possible locations for each ellipse, which we use to converting MCE into a discrete optimization problem.
-We, then prove that using the possible solutions obtained from the combination of every ellipse's CLS an optimal solution can be obtained.
+Similarly to the method developed in \cite{church:1984} for the Euclidean PMCLP, we will describe a Candidate List Set (CLS) of possible locations for each ellipse and then propose an algorithm that constructs solutions combining the possible locations in each ellipse's CLS.
+Based on the approach of \cite{chazelle:1986,cabello:2006}, we will construct the CLS for each ellipse by working with a problem equivalent to MCE for only one facility.
 
-%\subsection{An equivalent problem}
+Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, then consider the problem where $n$ ellipses\\ $E(p_1), \dots, E(p_n)$ are given, and a solution is defined as a point $q\in\R^2$, with an optimal one maximizing
+$w(\{p_i\in\Pp \colon q\in E(p_i)\})$.
+These two problems are equivalent as, let $q\in\R^2$, and $A\subset\Pp$; then $q\in\cap_{p\in A}E(p)$ if, and only if $\Pp \cap E(q) = A$.
 
-Let $(\Pp, \Ww, \Rr)$ be an instance of MCE, then for each $j=1\dots m$, consider $n$ ellipses with shape parameters $(a_j, b_j)$ centered at each one of the points in $\Pp$.
-If we have $q_j\in\R^2$ in a subset of the coverage areas of those ellipses, then $q_j$ is a solution of MCE covering the centers of those ellipses.
-In other words, if $q_j \in \R^2$, and $X \subset \{1, \dots, n\}$, $X \neq \emptyset$, such that $q_j \in \cap_{i\in X}E_j(p_i)$, then $\Pp \cap E_j(q_j) = \{p_i \colon i \in X\}$.
-From that observation, we can constrain each $q_j$ to be in $\cap_{i\in X} E_j(p_i)$, for some $X \subset \{1, \dots,n\}$, $X \neq \emptyset$.
-
-In \cite{bi}, an algorithm is proposed for the problem of determining the intersection of disks of fixed radii from a strictly convex normed plane. 
-We say that $(\R^2, ||\cdot||)$ is a strictly convex normed plane if the unit disk given by the norm $||\cdot||$ is strictly convex.
-Note that for any ellipse, there is a strictly convex normed plane whose unit circle is that ellipse.
-For that reason, we state some results from \cite{bi} here, which we use on the development of an algorithm for MCE.
-
-Let $(\R^2, ||\cdot||)$ be a strictly convex normed plane, and $\D=\{D_1, \dots, D_n\}$ be a set of $n$ unit disks in that space centered at different points, with the condition that  $\cap_{i=1}^n D_i \neq \emptyset$.
-In \cite{bi}, an algorithm was developed to construct this intersection in $\bigO(n\lg{n})$, some of its preliminary results are:
-\begin{itemize}
-	\item $\partial \cap_{i=1}^n D_i$ is formed by arcs of $\partial D_1, \dots, \partial D_n$.
-	\item The vertices of $\partial \cap_{i=1}^n D_i$ is contained in the set of pairwise-intersection of the circles $\partial D_1, \dots, \partial D_n$.
-	\item $|\partial D_i \cap \partial D_j| \le 2$.
-\end{itemize}
-
-Based on those, we introduce the next definition for the $k$-th ellipse's CLS, which we refer to as $S_k$.
+To construct the CLS for each ellipse, let us consider the intersection region $\cap_{p\in A} E(p)$, for some $A\subset \Pp$, $|A|>1$. In \cite{church:1984}, this region 
+is said to have vertices that are in the set of pairwise intersections of the circles with centers in $A$.
+Using the results of \cite{bi}, which develops an algorithm to determine the intersection region of $n$ fixed-radii disks in an strictly convex normed space, it is possible to prove that this is also true for ellipses.
+Based on that, given an instance of MCE, we define the CLS for each ellipse considering also the case where an ellipse could cover only one point in an optimal solution.
 
@@
 
-The set of solutions $S_k$, can be computed in $\bigO(n^2)$ as determining the intersections between two axis-parallel ellipses can be done analytically.
+The CLS for each ellipse can be computed in $\bigO(n^2)$ as two axis-parallel ellipses centered at distinct points intersect at most on two points, and those intersections can be determined analytically.
+Next, we establish a lemma stating that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.
 
-\begin{lem}
+\begin{thm}
 	Given an instance of MCE, and $S_1, \dots, S_m$ as defined by \autoref{def:cls_mce}, then the set $\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$.
-\end{lem}
-\begin{pf}
+\end{thm}
+\begin{proof}
 	Let $Q^*$ be an optimal solution of MCE for the given instance. Then, we are going to prove that there exists $Q' \in \Omega$, which is also optimal.
@@
 	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$ hence $|\Omega| \le n^{2m}$.
-\end{pf}
+\end{proof}
 
-With all this in hand, we can go ahead and define an algorithm for MCE.
+With all this in hand, we define \autoref{algoritmo:mce}, which goes through every possible combination in the CLS of each ellipse.
+As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has a $\bigO(mn^{2m+1})$ runtime complexity.
+In \autoref{section:implementation}, we give more details about the implementation of \autoref{algoritmo:mce}, along with some improvements that can be made.
+In \autoref{section:numerical}, we analyze some numerical experiments for instances proposed in \cite{canbolat, andreta}, and for some new ones.
 
@@
 \end{algorithm}
-
-\autoref{algoritmo:mce} can be proved to have a runtime complexity of $\bigO(mn^{2m+1})$.

### 2020-03-15 defesa/article/mcer.tex
wip

@@
 \end{definition}
-
-%\begin{definition}
-%	Let $x \in \R^2$, we define $\angle x$ as the angle between the vector $(1, 0)$ and $x$.
-%\end{definition}
 
@@
 \end{figure}
+Let $x\in\R^2$, and $\angle x$ be the angle between $x$ and the vector $(1,0)$.
+Then we have that if $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as it is the angle that makes the ellipse's major-axis be parallel to the line that passes through $u$ and $v$.
 
-Next we open a parenthesis to discuss the problem of deciding when it is possible to fit two points on an ellipse.
+Next we open a parenthesis to discuss the problem of deciding for what angles of rotation it is possible to find a center for an ellipse, so it contains two given points.
+We give the result for two points that have the same $y$-coordinate, but this can be generalized.
 
@@
 
-	Consider an axis-parallel ellipse with shape parameters $(a, b)\in\R^2_{>0}$, centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
+	Consider an axis-parallel ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$.
 Suppose that this line intersects the ellipse at least at one point.
@@
 
+Following that, we introduce a lemma that is responsible for connecting the developments of this chapter with the results of \autoref{section:e3p}.
+This lemma makes it possible to describe a type of solution which, for sure, is part of the equivalence class of any optimal solution.
+It states that, for any ellipse that covers more than two points in a given optimal solution, an equivalent solution exists with at least one of the two properties:
+\begin{itemize}
+	\item The ellipse contains at least three points.
+	\item The ellipse contains two points for any feasible angle.
+\end{itemize}
+
 \begin{lem}\label{lema:3pnts}
@@
 
+In \autoref{fig:lema-3-points}, a visualization of \autoref{lema:3pnts} is presented.
+An initial solution is given by the dashed-border ellipse and its center, represented by a star point.
+From it, the continuous function $\delta$ is defined by moving the ellipse through the rotation angles in $\Phi(u,v)$ while maintaining $u, v$ on it.
+Six angles were chosen from $\Phi(u,v)$ to be shown in \autoref{fig:lema-3-points}, among those were $0$ and $\max\{\Phi(u,v)\}$; their corresponding ellipses are displayed with solid-line borders.
+Consistently with \autoref{lema:3pnts}, the points in $\Pp \setminus \{u, v, w\}$ stay within the ellipse's cover for any angle of rotation, and, for point $w$, there exists an angle, such that it is on the ellipse, which is a solution of E3P.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+\begin{definition}\label{def:Sj}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. Then, for all $k\in\{1, \dots, m\}$, we define the CLS of the $k$-th ellipse as $S_k = S_k^{(1)} \cup S_k^{(2)} \cup S_k^{(3)}$ with
+	\begin{align}
+	S_k^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
+	S_k^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \angle(u-v))\in \R^2\times[0, \pi): \{u,v\} \subset \partial E_j(q, \angle(u-v))\}\\
+	S_k^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times[0, \pi): \{u, v, w\} \subset \partial E_j(q, \theta)\}.
+	\end{align}
+\end{definition}
+
+This definition breaks the construction of the CLS $S_j$ into three separated cases.
+The first one, $S_j^{(1)}$, represents solutions where the $j$-th ellipse covers only one point.
+The second one, $S_j^{(2)}$, takes into account solutions where the $j$-th ellipse covers at least two points, and no equivalent solution with three points on the ellipse exists.
+The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse.
+Following this, we move forward and introduce the main result of this section.
+
+\begin{thm}\label{th:mcer}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega$ be a set of solutions defined as 
+	\begin{equation*}\label{eq:omega}
+	\Omega = \{Q \in (\R^2\times[0, \pi))^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
+	\end{equation*}
+	Then there exists an optimal solution $Q^* \in \Omega$, and $|\Omega|\le n^{3m}$.
+\end{thm}
+\begin{proof}
+	The first thing to notice is that $\Omega$ is defined as the combination of every possible solution from each CLS.
+To prove that it contains an optimal solution $Q^*$, we only need to prove that for all $j\in\{1, \dots, m\}$, there exists $(q_j, \theta_j)\in S_j$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) \subset \Pp \cap E_j(q_j, \theta_j)$.
+That is, we only need to show that the CLS of every ellipse contains a center and angle of rotation that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
+To do that, we use \autoref{lema:3pnts} and break the possible optimal solutions into three cases.
+
+	In the first case, we consider solutions where the $j$-th ellipse covers less than one point, that is, $|\Pp \cap E_j(q_j^*, \theta_j^*)|\le1$.
+It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega$ every solution that has an ellipse centered at a point from $\Pp$.
+From that, we can also conclude that $|S_j^{(1)}| \le n$.
+
+	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on it.
+This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $Q^*$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
+	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
+	Moreover, in Section~\ref{section:mce}, we discuss the problem of determining the intersections between two ellipses.
+This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
+In \autoref{section:mce}, it is shown that this problem has at most two solutions.
+Therefore, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
+
+	For the last case, we are left with solutions where the $j$-th ellipse covers more than two points, and there exists an equivalent solution with three points on it. 
+	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega$.
+Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse contain three given points is at most six.
+Therefore, we have that $|S_j^{(3)}| \le 6\binom{n}{3}$.
+
+	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound for its size:
+	\begin{eqnarray*}
+		|S_j| &\le 6\binom{n}{3} + 2\binom{n}{2} + n &= n(n-1)(n-2) + n(n-1) + n\\
+		|S_j| &\le 6\binom{n}{3} + 2\binom{n}{2} + n &= n((n-1)^2+1) \le n^3.
+	\end{eqnarray*}	
+	Therefore, we conclude that  $|\Omega| \le |S_1|\times \dots \times |S_m| \le n^{3m}$.
+\end{proof}

### 2020-03-16 defesa/article/e3p.tex
wip

@@
 
-\begin{equation}\label{eq:trpnts}
+\begin{equation*}%\label{eq:trpnts}
 \varphi(p, \theta)=\left[\begin{array}{cc}
@@
 \end{array}\right].
-\end{equation}
+\end{equation*}
 
@@
 Let $|\Lambda(\theta)|$ denote the area of $\Lambda(\theta)$, using the formula from \cite[p.~189]{johnson1960} for the radius of a circumcircle of a triangle, and imposing that radius to be equal $b$, we define a function $\xi \colon [0, \pi) \to \R$ as
-\begin{equation}\label{eq:circumscribed_circle_b}
+\begin{equation*}
 \xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
-\end{equation}
+\end{equation*}
 whose roots are angles of rotation which determine solutions of E3P through the inverse transformation $\varphi^{-1}$.
@@
 
-\begin{pf}
+\begin{proof}
 	The first thing to notice is that $\xi$ is a real trigonometric polynomial of degree $6$. 
@@
 	Half of these solutions, though, are duplicated as ellipses are symmetric to their axis.
-\end{pf}
+\end{proof}
 
@@
 		\centering
-		\includegraphics[scale=.28]{../tex/figures/e3p_4sols}
+		\includegraphics[scale=.9]{figures/e3p_4sols}
 		\caption{}
@@
 		\centering
-		\includegraphics[scale=.28]{../tex/figures/e3p_6sols}
+		\includegraphics[scale=.9]{figures/e3p_6sols}
 		\caption{}

### 2020-03-16 defesa/article/implementation.tex
wip

--- 2020-02-29 defesa/tex/chapter/numerical.tex
@@
-The goal of this chapter is to show the results of the algorithms for MCE-$k$ and MCER-$k$ proposed by us for instances proposed by other works as well as instances created by us. 
-We also give implementation details and suggestions to improve performance, which we adopted in our implementations.
-
-\section{Implementation}
-
-All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3. All the experiments were run in a computer with the following specification:
-\begin{itemize}
-	\item CPU Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz;
-	\item 16Gib of RAM memory;
-	\item Linux Operating System: Debian 4.19.5.
-\end{itemize}
-
-\subsection{Determining the eigenvalues of a matrix}
-
-In \autoref{algoritmo:e3p}, we assumed that a procedure which returns every eigenvalue of a given square matrix was available.
-In practice, we used the very famous linear algebra package LAPACK (see \citeonline{lapack} for more details).
-Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
-The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference.
-Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.
-
-LAPACK offers a routine called ZGEEV that computes every eigenvalue of a complex matrix by using an implementation of the QR algorithm. 
-This routine optionally can also be asked to compute the right or left eigenvectors depending on two of its parameters. 
-ZGEEV receives in total $14$ parameters, with $4$ of them being used for output.
-We show a brief description of them in \autoref{tab:zgeev}, along with the specification of the value we set each parameter in our implementation.
-%\renewcommand{\arraystretch}{1.1}
-
-\begin{table}[H]
-	\begin{center}
-				\resizebox{\textwidth}{!}{%
-	\begin{tabular}{|c|m{18em}|m{8em}|}
-
-		\hline
-		\textbf{Parameter} & \multicolumn{1}{c|}{\textbf{Description}} & \multicolumn{1}{c|}{\textbf{Value}}\\
-		\hline
-		JOBVL&  Indicates whether to compute the left eigenvalues&  'N' (no eigenvectors should be computed)\\
-		\hline
-		JOBVR&  Indicates whether to compute the right eigenvalues&  'N' (no eigenvectors should be computed)\\
-		\hline
-		N    &  Order of matrix A &  6\\
-		\hline
-		A    &  The square matrix whose eigenvalues are to be computed & The companion matrix \\
-		\hline
-		LDA  &  Leading dimension of A & 6 \\
-		\hline
-		W    &  The eigenvalues output array &  A complex array of size 6\\
-		\hline
-		VL   &  The left eigenvectors output array & A complex array of size 1 \\
-		\hline
-		LDVL &  Leading dimension of VL&  1\\
-		\hline
-		VR   &  The right eigenvectors output array&  A complex array of size 1\\
-		\hline
-		LDVR &  Leading dimension of VR&  1\\
-		\hline
-		WORK &  A workspace for the procedure to utilize&  A complex array of size 12\\
-		\hline
-		LWORK&  Dimension of WORK &  12\\
-		\hline
-		RWORK&  A real workspace of size 2N &  A double array of size 12\\
-		\hline
-		INFO &  An integer containing $0$ if the algorithm was able to compute every eigenvalue &  A pointer to an integer variable\\
-		\hline
-	\end{tabular}
-}
-	\end{center}
-	\caption{The ZGEEV's parameter list.}
-	\label{tab:zgeev}
-\end{table}
-
-\subsection{Symbolic computation}
-
-Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
-Back in \autoref{chapter:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:circumscribed_circle_b} as a complex polynomial in the power format by replacing the sine and cosine functions with the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
-
-As expected, computing the coefficients of that polynomial in terms of the E3P's instance by hand is very challenging; the expressions get too long, and it becomes humanly impossible not to make any mistake.
-For that reason, we resort to Symbolic computation for this task.
-
-In practice, we utilized an external library for Python called SymPy (see \citeonline{sympy} for more information).
-This tool can create expressions using arithmetic operators on predefined symbols, numbers, and other expressions.
-It can also convert expressions into polynomials in the power format, and output them directly into C code.
-Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++ implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.
-The actual coefficients of that polynomial are presented in \autoref{chapter:poly} in terms of a generic E3P's instance.
-
-%This can be done by creating a composition of an expression for $\xi(\theta)(e^{i\theta})^6$ with the expressions for $\cos(\theta)$ and $\sin(\theta)$ defined by \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
-%After that, running a command, we can ask SymPy to transform that expression into a polynomial informing it that its variable is $z=e^{i\theta}$.
-Finally, very conveniently for us, SymPy has a function that outputs expressions directly as C code, which can be used to import the polynomial into our implementation of \autoref{algoritmo:e3p}.
-
-%\section{A greedy algorithm}
-
-%In \citeonline{church:1974}, a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them. 
-%Here we introduce a very similar algorithm for both MCE and MCER with the intention of using it in the development of a sufficient condition to skip non-optimal solutions.
-
-%Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
-Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
-Considering $Z_j \subset \Pp$ as the set of uncovered points before the $j$-th iteration.
-Then, we set the solution for the $j$-th ellipse, as the solution of an instance of MCE-1 or MCER-1 with demand points $Z_j$.
-%That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
-This algorithm can be implemented, such that it takes $\bigO(n^4m)$ operations to construct a solution.
-
-\section{Some details and improvements}\label{section:improvements}
-
-To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} and \autoref{algoritmo:mcer} had to be done.
-Just translating those algorithms into a programming language is not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
-Therefore, we present here some improvements that can be applied to the implementation of those algorithms, which can result in significant growth of performance, especially in terms of CPU time.
-
-\subsection{CLS construction}
-
-In both algorithms, a subroutine to construct an ellipse's CLS is called inside the backtracking routine. This can potentially make the same combination of points be considered multiple times.
-To avoid this unnecessary computation, we compute the CLS for every ellipse beforehand in a preprocessing phase for the whole demand set.
-Then, in the backtracking, we only consider the options of locations that makes the ellipse cover at least one point that has not been covered before.
-
-Another improvement that can be made in the construction of an ellipse's CLS is the elimination of redundant solutions.
-Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER (the same can be said about MCE).
-If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, then we can for sure dismiss solution $(Q', \Theta')$.
-In our implementation, we use the same tree-like data structure as the one described in \citeonline{andreta} to only keep solutions that are not redundant.
-
-Calling \autoref{algoritmo:e3p} for E3P for every triplet of points in an instance of MCER can be expensive.
-To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.
-
-\subsection{Backtracking}
-
-Without any improvement, backtracking through every possible combination of every ellipse's CLS can take a very long time, possibly going through a lot of non-optimal solutions. 
-For this reason, we introduce a sufficient condition for the MCER's case (the MCE's case is analogous), based on MCER for one ellipse, which can be used to skip solutions that for sure are non-optimal.
-
-Given an instance $(\Pp, \Ww, \Rr)$ of MCER, suppose that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-Let $Z_j$ be the points that are not covered by the first $j$ ellipses, and $OPT_j$ the value of the best solution with the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-
-Then, we can obtain an upper-bound for $OPT_j$ by using, for $k\in\{j+1, \dots, m\}$, the solutions $(q_k', \theta_k')$ of MCER for instances with demand set $Z_j$ and only one ellipse with shape parameters $(a_k, b_k)$.
-As these solutions only consider the best cover individually for each ellipse, we have the following inequality
-\begin{equation}
-OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right).
-\end{equation}
-This upper-bound for $OPT_j$ can then be used in the backtracking process to skip solutions that are not better than any optimal solution.
-Let $OPT_{lo}$ be a lower bound for the optimal solution, we have that if
-\begin{equation}
-\label{eq:upper-bound}
-w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) +w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right) \le OPT_{lo},
-\end{equation}
-then $OPT_j \le OPT_{lo}$, which implies that $OPT_j$ is less than or equal the value of any optimal solution.
-This defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-In practice, we can use the value of the best solution found so far as the lower-bound for the optimal solution.
-
-It is worth pointing out that these improvement suggestions do not have an effect in a possible worst case scenario.
-We are adopting them in our implementation because they showed good results in practice.
-For example, without taking the suggestion given by \autoref{eq:upper-bound}, \autoref{algoritmo:mcer-k} takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions.
-In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
-
-\section{Results for known instances}
-
-In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
-
-For each instance, we display the selected ellipses and the income of the found optimal solution. 
-We also display some performance metrics with the intention of giving an idea of how much computation had to be done for the algorithms to find an optimal solution. These metrics are: 
-the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
-For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
-All the tables containing results referenced in this section are presented in \autoref{chapter:tables}.
-We also made available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/} every instance used here, along with the graphical representation of every obtained solution.
-
-\subsection{MCE-$k$}
-
-In \autoref{tab:mce-results-cm}, the results for instances CM1-CM9 are shown. 
-The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than one second for every one of the instances CM1-CM9.
-Even though the experiments were run in a different environment, we can still say that this is a great improvement compared with the results from \citeonline{andreta}.
-For example, to obtain an optimal solution for the instance CM9, the method proposed by \citeonline{andreta} took more than thirty minutes.
-In \autoref{tab:mce-results-ab1} and \autoref{tab:mce-results-ab2}, we present the results for instances AB001-AB120.
-The only instance that our algorithm took more than one second to return an optimal solution was AB120, which it took 1.08 second.
-
-In practice, at least for these instances, the bound $\bigO(2^mn^{2m})$ for the algorithm for MCE-$k$ seems to be loose.
-In instance CM9, for example, this bound says that the number of leaves corresponding to a solution in the backtracking tree should be close to $2^mn^{2m} = 2^3(10^2)^{2\times 3} = 8\times10^{12}$, which is very far from the actual number of $649$ such leaves obtained in practice.
-This is also the case for the size of the CLSs, which are all very far away from its $\bigO(n^2)$ bound.
-The greatest CLS size observed was $174$ for instance CM9, which is still very far away from $n^2$, which in this case is $10^4$.
-
-\subsection{MCER-$k$}
-
-The numerical results obtained by our implementation of \autoref{algoritmo:mcer-k} are shown in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for instances AB001-AB120.
-An optimal solution was obtained for every instance, and overall, at most six seconds of CPU time was taken.
-
-Looking at the numerical results of the heuristic method proposed in \citeonline{andreta}, the only non-optimal solutions it encountered were for instances AB105-AB108.
-For these instances, our algorithm obtained an optimal solution covering one more point.
-In \autoref{fig:AB108}, the optimal solution for AB108 is displayed.
-In general, our algorithm took much lower CPU time compared to the methods developed in \citeonline{andreta}.
-For example, for instance CM9, their heuristic method took more than six hours to return a solution, our implementation of \autoref{algoritmo:mcer-k}, on the other hand, obtained an optimal solution in less than five seconds.
-
-\begin{figure}[!htb]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance AB108.}
-	\includegraphics[scale=.8]{tex/figures/AB108}
-	\fautor
-	\label{fig:AB108}
-\end{figure}
-
-As it was said for the results of MCE-$k$, in practice, the bounds for the CLS size and the number of operations taken by the algorithm is very loose.
-Notice that, the greatest CLS size was $730$ obtained for the third ellipse in instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
-By \autoref{th:mcer}, for MCER, the bound for the number of computations that \autoref{algoritmo:mcer-k} takes is $\bigO(2^mn^{3m})$.
-In instance AB120, for example, the size of the backtracking tree is only $7102$, which is way lower than $2^5100^{15}$.
-
-\section{New instances}
-
-After examining the results obtained by our algorithms for the formerly known instances, constructing new ones, more challenging for our work, can be taken as essential for further analyzing the algorithms proposed by us.
-Besides increasing the size of the demand set and the number of ellipses, we also designed instances with non-unitary weights, which is something none of the previous instances had. 
-Moreover, to create very distinct instances from the previously introduced ones, we used a different probability distribution, other than the uniform one, to generate the location of points.
-We set a time limit of two hours of running time for solving every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
-In total, we designed 46 new instances, which will be referred to as TA01, \dots, TA46, and are available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
-The numerical results for every one of them are displayed in \autoref{chapter:tables}.
-
-The first set of instances were construct sampling each demand points from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
-This is expected to produce a demand set with most points located near the origin, but with the most valuable points located far away from it.
-We generated a set of $n=100$ points, with $m=7$ ellipses, making the $j$-th ellipse have shape parameters randomly taken from a uniform distribution in $[0.5, 1.5]$, and cost $c_j=10\times a_j \times b_j$.
-From that, we created seven instances taking $k \in \{1, \dots, m\}$.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta1}.
-Because the normal distribution generates most of the points close to each other (see \autoref{fig:TA004} for an example), every ellipse's CLS's size ended up being significantly bigger if compared to previously introduced instances with $100$ points.
-This, and the subtle increase in the number of ellipses, made the algorithms for MCER-$k$ and MCE-$k$ time out for some instances.
-The algorithm for MCER-$k$ did not return an optimal solution within the predefined time limit for the last three instances ($k=5, 6, 7)$, while the algorithm for MCE-$k$ did not finish in time for the last instance ($k=7$).
-The optimal solution for MCER-$k$ for the instance with $k=4$ is displayed in \autoref{fig:TA004}.
-
-\begin{figure}[H]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA04.}
-	\includegraphics[scale=.8]{tex/figures/TA004}
-	\fautor
-	\label{fig:TA004}
-\end{figure}
-
-For the second set of instances, we used the same process used for the first set to generate the demand points and the ellipses.
-We kept the number of ellipses at $3$ and created five demand sets with $n\in\{200, 250, 300, 350, 400\}$.
-In total, we had $15$ instances having $k\in\{1, \dots, m\}$.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta2} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta2}.
-The solution of MCER-$k$ for the instance with $n=400$, and $k=2$ is shown in \autoref{fig:TA021}.
-
-\begin{figure}[H]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA21.}
-	\includegraphics[scale=.8]{tex/figures/TA021}
-	\fautor
-	\label{fig:TA021}
-\end{figure}
-
-The third set of instances were constructed generating the demand set following a uniform distribution in $[0, 10]^2$, with each point having unitary weight; and the ellipses by the same process used for the first two set of instances.
-We created instances with $m=5$, $n\in \{400, 450, 500\}$, and $k\in\{1, \dots, m\}$, with a total of $15$ instances.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta3} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta3}.
-Optimal solutions were obtained for every one of the instances in this set.
-It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
-The optimal solution of MCER-$k$ returned by \autoref{algoritmo:mcer-k} for the instance with $n=500$ and $k=5$ is shown in \autoref{fig:TA037}.
-
-\begin{figure}[!htb]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA37.}
-	\includegraphics[scale=.8]{tex/figures/TA037}
-	\fautor
-	\label{fig:TA037}
-\end{figure}
-
-The last set of instances were constructed using two bivariate normal distributions with unitary variance $\mathcal{N}(\mu^{(1)}, \mathbb{I})$ and $\mathcal{N}(\mu^{(2)}, \mathbb{I})$, $\mu^{(1)}, \mu^{(2)} \in \R^2$.
-Half of the points were generated following $\mathcal{N}(\mu^{(1)}, \mathbb{I})$, and the other half $\mathcal{N}(\mu^{(2)}, \mathbb{I})$; the weight of every point was set as its squared distance to the mean of the distribution from which it was generated.
-The ellipses were also divided into two halves, taking their shape parameters from uniform distributions in the intervals $[0.5, 1.5]$, and $[3, 4]$; setting the $j$-th ellipse's weight as $c_j=a_j \times b_j$.
-The purpose of this last set of instances was to create an example where the chosen ellipses in the solution of an instance of MCER-$k$ is not a subset of the chosen ellipses in an optimal solution of that same instance for MCER-$(k+1)$.
-We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$, and defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such counter-example.
-The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mce-results-ta4} for MCER-$k$.
-In \autoref{fig:TA44-45}, we show the solutions for the instances with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
-
-\begin{figure}[!htb]
-	\caption{Optimal solutions for instances TA44 and TA45.}
-	\begin{subfigure}{.5\textwidth}
-			\centering
-		\caption{TA44}
-		\includegraphics[scale=.6]{tex/figures/TA044}
-
-		%\fautor
-		\label{fig:TA043}
-	\end{subfigure}
-	\begin{subfigure}{.5\textwidth}
-			\centering
-		\caption{TA45}
-		\includegraphics[scale=.6]{tex/figures/TA045}
-		%\fautor
-		\label{fig:TA044}
-	\end{subfigure}
-\label{fig:TA44-45}
-	\fautor
-\end{figure}
+All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3.
+The actual code is available in \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.

### 2020-03-16 defesa/article/improvements.tex
wip

In the CLS construction for MCER, calling the algorithm to determine every solution of E3P for every triplet of points can become expensive. To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling that  algorithm if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.

### 2020-03-16 defesa/article/introduction.tex
wip

@@
 Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
-	\begin{equation}
+	\begin{equation*}
 	||x||_{a,b, \theta}=\left|\left|
@@
 	\end{array}\right) x \right|\right|_2,
-	\end{equation}
+	\end{equation*}
 	then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j,0} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.
@@
 Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE as the optimization problem 
-\begin{equation}
+\begin{equation*}
 \max_{q_1, \dots, q_m} \sum_{j=1}^m w(\Pp \cap E_j(q_j)),
-\end{equation}
+\end{equation*}
 and similarly MCER as
-\begin{equation}
+\begin{equation*}
 \max_{(q_1, \theta_1), \dots, (q_m, \theta_m)} \sum_{j=1}^m w(\Pp \cap E_j(q_j, \theta_j)).
-\end{equation}
+\end{equation*}
 
@@
 
-Solving MCE-$k$ (MCER-$k$) can be done by considering the $\binom{m}{k}$ instances of MCE (MCER-$k$), and then taking the best one as the optimal solution, taking into account the cost of each utilized ellipse.
+Solving MCE-$k$ (MCER-$k$) can be done by considering the $\binom{m}{k}$ instances of MCE (MCER), and then taking the best one as the optimal solution, taking into account the cost of each utilized ellipse.
 As this step can be seen as trivial, we propose algorithms for MCE and MCER, and then in \autoref{section:numerical}, as we use the instances from \cite{canbolat, andreta} in the numerical experiments, we analyze the results obtained by our implementations of the algorithms proposed in this work for MCE-$k$ and MCER-$k$.

### 2020-03-16 defesa/article/mce.tex
wip

@@
 
+\begin{lem}\label{lema:e2p}
+	Let $E$ be the coverage region of an axis-parallel ellipse with shape parameters $(a,b)$; and $v \in \R^2$, $v\neq0$, then $|\partial E(0) \cap \partial E(v)| \le 2$, and $\partial E(0) \cap \partial E(v)$ can be determined analytically.
+\end{lem}
+
+\begin{proof}
+	By \cite{bi}, we have that the number of intersections between two strictly convex circles of fixed radii is at most two.
+To determine the intersection points, consider the equality between the equations of $\partial E(0)$ and $\partial E(v)$:
+	$x^2/a^2 + y^2/b^2 = (x-v_x)^2/a^2 + (y-v_y)^2/b^2.$
+	This expression can be reduced to $y=\alpha x + \beta$, for some $\alpha, \beta$.
+Using $\partial E(0)$'s equation, we obtain at most two values for $x$, which consequently, by $y=\alpha x + \beta$, determine the intersection points between the two ellipses.
+\end{proof}
+
 \begin{definition}\label{def:cls_mce}
@@
 
-The CLS for each ellipse can be computed in $\bigO(n^2)$ as two axis-parallel ellipses centered at distinct points intersect at most on two points, and those intersections can be determined analytically.
+By \autoref{lema:e2p}, the CLS for each ellipse can be computed in $\bigO(n^2)$.
 Next, we establish a lemma stating that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.
@@
 
-	If $|X_k| = 0$, then any $q_k \in S_k$ makes $X_k \subset \Pp \cap E_k(q_k)$.
+	%If $|X_k| = 0$, then any $q_k \in S_k$ makes $X_k \subset \Pp \cap E_k(q_k)$.
 
-	if $|X_k| = 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.
+	if $|X_k| \le 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.
 
@@
 As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has a $\bigO(mn^{2m+1})$ runtime complexity.
-In \autoref{section:implementation}, we give more details about the implementation of \autoref{algoritmo:mce}, along with some improvements that can be made.
-In \autoref{section:numerical}, we analyze some numerical experiments for instances proposed in \cite{canbolat, andreta}, and for some new ones.
+In \autoref{section:numerical}, we give more details about the implementation of \autoref{algoritmo:mce} and analyze some numerical experiments for instances proposed in \cite{canbolat, andreta}, and for some new ones.
 

### 2020-03-16 defesa/article/mcer.tex
wip

@@
 
-	\begin{equation}
+	\begin{equation*}
 	\Phi(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E,u,v)\textnormal{-feasible angle}\}.
-	\end{equation}
+	\end{equation*}
 	%We also define $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
@@
 
-	\begin{equation}\label{eq:function-l}
+	\begin{equation*}
 	L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
-	\end{equation}
+	\end{equation*}
 	which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.
@@
 \begin{definition}\label{def:Sj}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. Then, for all $k\in\{1, \dots, m\}$, we define the CLS of the $k$-th ellipse as $S_k = S_k^{(1)} \cup S_k^{(2)} \cup S_k^{(3)}$ with
-	\begin{align}
-	S_k^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
-	S_k^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \angle(u-v))\in \R^2\times[0, \pi): \{u,v\} \subset \partial E_j(q, \angle(u-v))\}\\
-	S_k^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times[0, \pi): \{u, v, w\} \subset \partial E_j(q, \theta)\}.
-	\end{align}
+	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. Then, for all $j\in\{1, \dots, m\}$, we define the CLS of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
+	\begin{align*}
+	S_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
+	S_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \angle(u-v))\in \R^2\times[0, \pi): \{u,v\} \subset \partial E_j(q, \angle(u-v))\}\\
+	S_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times[0, \pi): \{u, v, w\} \subset \partial E_j(q, \theta)\}.
+	\end{align*}
 \end{definition}
 
-This definition breaks the construction of the CLS $S_j$ into three separated cases.
+This definition breaks the construction of the CLS into three separated cases.
 The first one, $S_j^{(1)}$, represents solutions where the $j$-th ellipse covers only one point.
@@
 The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse.
-Following this, we move forward and introduce the main result of this section.
+
+To compute $S_j^{(2)}$, we can observe that, given two points $u, v$, determining every $q\in\R^2$, such that $\{u,v\}\subset\partial E_j(q, \angle(u-v))$ can be transformed into the problem of determining the set $\partial E_j(u, \angle(u-v)) \cap \partial E_j(v, \angle(u-v))$, which, by \autoref{lema:e2p}, is composed of at most two points, which can be determined analytically.
+Therefore, we have that $S_j^{(2)}$ can be computed in $\bigO(n^2)$ operations.
+
+To compute $S_j^{(3)}$, we have to call the algorithm described in \autoref{section:e3p} to determine every solution of E3P for every triplet of points in $\Pp$.
+Even though that algorithm is $\bigO(1)$, it has a high constant factor, thus skipping it, in practice, is a good suggestion.
+Given three points and an ellipse with shape parameters $(a, b)$, the following two conditions are sufficient for E3P to have no solutions, and therefore, if any of them is true, we can skip calling the algorithm to determine every solution of E3P for that instance:
+\begin{itemize}
+	\item The maximum distance between any of the points is greater than $2a$;
+	\item The triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.
+\end{itemize}
+
+Overall, constructing every ellipse's CLS can be implemented to have a $\bigO(n^3)$ runtime complexity.
+Following this, we introduce a theorem, which connects the results for MCER so far, to prove that the set of solutions constructed using the CLSs described by \autoref{def:Sj} contains an optimal solution.
 
@@
 To prove that it contains an optimal solution $Q^*$, we only need to prove that for all $j\in\{1, \dots, m\}$, there exists $(q_j, \theta_j)\in S_j$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) \subset \Pp \cap E_j(q_j, \theta_j)$.
-That is, we only need to show that the CLS of every ellipse contains a center and angle of rotation that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
 To do that, we use \autoref{lema:3pnts} and break the possible optimal solutions into three cases.
@@
 
-	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on it.
-This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $Q^*$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
-	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
-	Moreover, in Section~\ref{section:mce}, we discuss the problem of determining the intersections between two ellipses.
-This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
-In \autoref{section:mce}, it is shown that this problem has at most two solutions.
-Therefore, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
+	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and there is no $Q' \succ Q^*$, such that $|\Pp \cap \partial E_j(q_j', \theta_j')| \ge 3$.
+	This case is addressed by \autoref{lema:3pnts}, which states that there are equivalent solutions to $Q^*$ with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the $j$-th ellipse for every $(E_j, u, v)$-feasible angle.
+	As $\angle(u-v)$ is a $(E_j, u, v)$-feasible angle, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j, \theta_j) = \Pp \cap E_j(q_j^*, \theta_j^*)$.
+	Also, by \autoref{lema:e2p}, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
+
+%	Moreover, as determining every $q\in\R^2$, such that $\{u,v\}\subset \partial E_j(q, \angle(u-v))$ can be transformed into the problem of determining the set $\partial E_j(u, \angle(u-v)) \cap \partial E_j(v, \angle(u-v))$, which, as discussed in \autoref{section:mce}, contains at most two points, we can conclude that $|S_j^{(2)}| \le 2 \binom{n}{2}$.
 
@@
 	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega$.
-Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse contain three given points is at most six.
-Therefore, we have that $|S_j^{(3)}| \le 6\binom{n}{3}$.
+Also, by \autoref{lema:e3p} we can conclude that $|S_j^{(3)}| \le 6\binom{n}{3}$.
 
-	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound for its size:
+	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound for $|S_j|$:
 	\begin{eqnarray*}
@@
 \end{proof}
+
+Finally, we define \autoref{algoritmo:mcer}, which backtracks every possible combination of solutions considering the CLS of every ellipse.
+As evaluating each solution can be implemented to take $\bigO(nm)$ operations, we have that \autoref{algoritmo:mcer} has a $\bigO(mn^{3m+1})$ runtime complexity.
+In the next section, we describe some implementation details and improvements that, in practice, can lower the size of $S_j$ significantly, and also can make the backtracking process described in \autoref{algoritmo:mcer} skip many non-optimal solutions.
+
+\begin{algorithm}
+	\caption{Algorithm for MCER}\label{algoritmo:mcer}
+	\begin{algorithmic}[1]
+		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}
+
+		\Ensure{An optimal solution for the given instance of MCER.}
+
+		\item[]
+		\Procedure{$MCER$}{$\Pp, \Ww, \Rr$}
+		\State \Return $MCER_{bt}(\Pp, \Ww, \Rr, 1)$
+		\EndProcedure
+
+		\item[]
+
+		\Procedure{$MCER_{bt}$}{$Z, \Ww, \Rr, j$}
+		%\If{$j = m+1$}
+		%\State \Return $0$
+		%\EndIf
+
+		%\State $ans \gets 0$
+		\State $(q_{j}^*,\theta_j*); \dots; (q_m^*, \theta_m^*) \gets (0,0); \dots; (0, 0)$ \Comment{Setting to $0$ as a default value.}
+
+		%\State $S_j \gets \textnormal{CLS-MCER}(Z, a_j, b_j)$
+		\State Let $S_j$ be the CLS for the $j$-th ellipse as defined in \autoref{def:Sj}
+
+		\ForAll{$(q_j, \theta_j) \in S_j$}
+		%\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
+
+		\If{$j < m$}
+		\State $(q_{j+1},\theta_{j+1}); \dots; (q_m,\theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$
+		\EndIf
+
+		%\State $Cov \gets \bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)$
+		\If {$w(\bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)) > w(\bigcup_{k=j}^m \Pp \cap E_k(q_k^*, \theta_k^*))$}
+		%\State $ans \gets w(Cov)$
+		%\State $((q_{j}^*,\theta_{j}^*); \dots; (q_m^*, \theta_m^*)) \gets ((q_{j},\theta_{j}); \dots; (q_m, \theta_m))$
+
+		\State $(q_{j}^*,\theta_j*); \dots; (q_m^*, \theta_m^*) \gets  (q_{j},\theta_{j}); \dots; (q_m,\theta_m) $
+		\EndIf
+		\EndFor
+
+		\State \Return $(q_{j}^*,\theta_j*); \dots; (q_m^*, \theta_m^*)$
+		\EndProcedure
+	\end{algorithmic}
+\end{algorithm}

### 2020-03-16 defesa/article/prunning.tex
wip

--- 2020-02-29 defesa/tex/chapter/numerical.tex
@@
-The goal of this chapter is to show the results of the algorithms for MCE-$k$ and MCER-$k$ proposed by us for instances proposed by other works as well as instances created by us. 
-We also give implementation details and suggestions to improve performance, which we adopted in our implementations.
-
-\section{Implementation}
-
-All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3. All the experiments were run in a computer with the following specification:
-\begin{itemize}
-	\item CPU Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz;
-	\item 16Gib of RAM memory;
-	\item Linux Operating System: Debian 4.19.5.
-\end{itemize}
-
-\subsection{Determining the eigenvalues of a matrix}
-
-In \autoref{algoritmo:e3p}, we assumed that a procedure which returns every eigenvalue of a given square matrix was available.
-In practice, we used the very famous linear algebra package LAPACK (see \citeonline{lapack} for more details).
-Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
-The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference.
-Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.
-
-LAPACK offers a routine called ZGEEV that computes every eigenvalue of a complex matrix by using an implementation of the QR algorithm. 
-This routine optionally can also be asked to compute the right or left eigenvectors depending on two of its parameters. 
-ZGEEV receives in total $14$ parameters, with $4$ of them being used for output.
-We show a brief description of them in \autoref{tab:zgeev}, along with the specification of the value we set each parameter in our implementation.
-%\renewcommand{\arraystretch}{1.1}
-
-\begin{table}[H]
-	\begin{center}
-				\resizebox{\textwidth}{!}{%
-	\begin{tabular}{|c|m{18em}|m{8em}|}
-
-		\hline
-		\textbf{Parameter} & \multicolumn{1}{c|}{\textbf{Description}} & \multicolumn{1}{c|}{\textbf{Value}}\\
-		\hline
-		JOBVL&  Indicates whether to compute the left eigenvalues&  'N' (no eigenvectors should be computed)\\
-		\hline
-		JOBVR&  Indicates whether to compute the right eigenvalues&  'N' (no eigenvectors should be computed)\\
-		\hline
-		N    &  Order of matrix A &  6\\
-		\hline
-		A    &  The square matrix whose eigenvalues are to be computed & The companion matrix \\
-		\hline
-		LDA  &  Leading dimension of A & 6 \\
-		\hline
-		W    &  The eigenvalues output array &  A complex array of size 6\\
-		\hline
-		VL   &  The left eigenvectors output array & A complex array of size 1 \\
-		\hline
-		LDVL &  Leading dimension of VL&  1\\
-		\hline
-		VR   &  The right eigenvectors output array&  A complex array of size 1\\
-		\hline
-		LDVR &  Leading dimension of VR&  1\\
-		\hline
-		WORK &  A workspace for the procedure to utilize&  A complex array of size 12\\
-		\hline
-		LWORK&  Dimension of WORK &  12\\
-		\hline
-		RWORK&  A real workspace of size 2N &  A double array of size 12\\
-		\hline
-		INFO &  An integer containing $0$ if the algorithm was able to compute every eigenvalue &  A pointer to an integer variable\\
-		\hline
-	\end{tabular}
-}
-	\end{center}
-	\caption{The ZGEEV's parameter list.}
-	\label{tab:zgeev}
-\end{table}
-
-\subsection{Symbolic computation}
-
-Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
-Back in \autoref{chapter:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:circumscribed_circle_b} as a complex polynomial in the power format by replacing the sine and cosine functions with the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
-
-As expected, computing the coefficients of that polynomial in terms of the E3P's instance by hand is very challenging; the expressions get too long, and it becomes humanly impossible not to make any mistake.
-For that reason, we resort to Symbolic computation for this task.
-
-In practice, we utilized an external library for Python called SymPy (see \citeonline{sympy} for more information).
-This tool can create expressions using arithmetic operators on predefined symbols, numbers, and other expressions.
-It can also convert expressions into polynomials in the power format, and output them directly into C code.
-Using these features, we can write $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions with expressions for the identities given by  \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}, and then import it into our C++ implementation of \autoref{algoritmo:e3p} by printing the polynomial's list of coefficients as C code.
-The actual coefficients of that polynomial are presented in \autoref{chapter:poly} in terms of a generic E3P's instance.
-
-%This can be done by creating a composition of an expression for $\xi(\theta)(e^{i\theta})^6$ with the expressions for $\cos(\theta)$ and $\sin(\theta)$ defined by \autoref{eq:complex_trig_cos} and \autoref{eq:complex_trig_sin}.
-%After that, running a command, we can ask SymPy to transform that expression into a polynomial informing it that its variable is $z=e^{i\theta}$.
-Finally, very conveniently for us, SymPy has a function that outputs expressions directly as C code, which can be used to import the polynomial into our implementation of \autoref{algoritmo:e3p}.
-
-%\section{A greedy algorithm}
-
-%In \citeonline{church:1974}, a simple greedy algorithm was introduced to compare the results obtained by the other algorithms developed by them. 
-%Here we introduce a very similar algorithm for both MCE and MCER with the intention of using it in the development of a sufficient condition to skip non-optimal solutions.
-
-%Let $(\Pp, \Ww, \Rr)$ be an instance of MCE or MCER.
-Then, at the $j$-th iteration of the algorithm we choose the solution for the first ellipse.
-Considering $Z_j \subset \Pp$ as the set of uncovered points before the $j$-th iteration.
-Then, we set the solution for the $j$-th ellipse, as the solution of an instance of MCE-1 or MCER-1 with demand points $Z_j$.
-%That is the same as choosing, among all the possibilities in the $j$-th ellipse's CLS, the solution which maximizes the weight of covered points in $Z_j$.
-This algorithm can be implemented, such that it takes $\bigO(n^4m)$ operations to construct a solution.
-
-\section{Some details and improvements}\label{section:improvements}
-
-To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} and \autoref{algoritmo:mcer} had to be done.
-Just translating those algorithms into a programming language is not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
-Therefore, we present here some improvements that can be applied to the implementation of those algorithms, which can result in significant growth of performance, especially in terms of CPU time.
-
-\subsection{CLS construction}
-
-In both algorithms, a subroutine to construct an ellipse's CLS is called inside the backtracking routine. This can potentially make the same combination of points be considered multiple times.
-To avoid this unnecessary computation, we compute the CLS for every ellipse beforehand in a preprocessing phase for the whole demand set.
-Then, in the backtracking, we only consider the options of locations that makes the ellipse cover at least one point that has not been covered before.
-
-Another improvement that can be made in the construction of an ellipse's CLS is the elimination of redundant solutions.
-Let $(Q, \Theta)$ and $(Q', \Theta')$ be two solutions of MCER (the same can be said about MCE).
-If, for any $j \in \{1, \dots, m\}$, we have $\Pp \cap E_j(q_j', \theta_j') \subset \Pp \cap E(q_j, \theta_j)$, then we can for sure dismiss solution $(Q', \Theta')$.
-In our implementation, we use the same tree-like data structure as the one described in \citeonline{andreta} to only keep solutions that are not redundant.
-
-Calling \autoref{algoritmo:e3p} for E3P for every triplet of points in an instance of MCER can be expensive.
-To avoid that, given three points and an ellipse with shape parameters $(a, b)$, we can skip calling \autoref{algoritmo:e3p} if the maximum distance between any of the points is greater than $2a$, or if the triangle's area with vertices on these three points have area greater than $\frac{3\sqrt{3}}{4}\pi ab$, which can be proved to be the greatest area of an inscribed triangle in an ellipse with shape parameters $(a, b)$.
-
-\subsection{Backtracking}
-
 Without any improvement, backtracking through every possible combination of every ellipse's CLS can take a very long time, possibly going through a lot of non-optimal solutions. 
@@
 
-Given an instance $(\Pp, \Ww, \Rr)$ of MCER, suppose that the first $j$ ellipses are fixed at the locations $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-Let $Z_j$ be the points that are not covered by the first $j$ ellipses, and $OPT_j$ the value of the best solution with the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
+\begin{definition}
+	Given an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We define $OPT_j$ as the value of the best solution with the first $j$ ellipses fixed at locations $(q_1, \theta_1); \dots; (q_j, \theta_j)$, and $Z_j=\Pp \setminus \cup_{k=1}^j E_k(q_k, \theta_k)$.
+\end{definition}
 
-Then, we can obtain an upper-bound for $OPT_j$ by using, for $k\in\{j+1, \dots, m\}$, the solutions $(q_k', \theta_k')$ of MCER for instances with demand set $Z_j$ and only one ellipse with shape parameters $(a_k, b_k)$.
+Then, we can obtain an upper-bound for $OPT_j$ by using, for each $k\in\{j+1, \dots, m\}$, the solution $(q_k', \theta_k')$ of MCER for instance $(Z_k, \{w_i\colon p_i \in Z_k\}, \{(a_k, b_k)\})$.
 As these solutions only consider the best cover individually for each ellipse, we have the following inequality
-\begin{equation}
+\begin{equation*}
 OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right).
-\end{equation}
+\end{equation*}
 This upper-bound for $OPT_j$ can then be used in the backtracking process to skip solutions that are not better than any optimal solution.
 Let $OPT_{lo}$ be a lower bound for the optimal solution, we have that if
-\begin{equation}
-\label{eq:upper-bound}
+\begin{equation}\label{eq:upper-bound}
 w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) +w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right) \le OPT_{lo},
@@
 We are adopting them in our implementation because they showed good results in practice.
-For example, without taking the suggestion given by \autoref{eq:upper-bound}, \autoref{algoritmo:mcer-k} takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions.
-In \autoref{tab:mcer-results-ab1}, we show the results of \autoref{algoritmo:mcer-k} implemented with all the improvement suggestions given here; for instance AB060, the algorithm takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions.
-
-\section{Results for known instances}
-
-In this section, we present the results of \autoref{algoritmo:mce-k} and \autoref{algoritmo:mcer-k} for instances CM1,CM2, CM4, CM5, CM7, CM8 proposed by \citeonline{canbolat}, and for instances CM3,CM6,CM9 and AB001-AB120 proposed by \citeonline{andreta}.
-
-For each instance, we display the selected ellipses and the income of the found optimal solution. 
-We also display some performance metrics with the intention of giving an idea of how much computation had to be done for the algorithms to find an optimal solution. These metrics are: 
-the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
-For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which are dismissed by the improvements suggestions given in \autoref{section:improvements}.
-All the tables containing results referenced in this section are presented in \autoref{chapter:tables}.
-We also made available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/} every instance used here, along with the graphical representation of every obtained solution.
-
-\subsection{MCE-$k$}
-
-In \autoref{tab:mce-results-cm}, the results for instances CM1-CM9 are shown. 
-The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than one second for every one of the instances CM1-CM9.
-Even though the experiments were run in a different environment, we can still say that this is a great improvement compared with the results from \citeonline{andreta}.
-For example, to obtain an optimal solution for the instance CM9, the method proposed by \citeonline{andreta} took more than thirty minutes.
-In \autoref{tab:mce-results-ab1} and \autoref{tab:mce-results-ab2}, we present the results for instances AB001-AB120.
-The only instance that our algorithm took more than one second to return an optimal solution was AB120, which it took 1.08 second.
-
-In practice, at least for these instances, the bound $\bigO(2^mn^{2m})$ for the algorithm for MCE-$k$ seems to be loose.
-In instance CM9, for example, this bound says that the number of leaves corresponding to a solution in the backtracking tree should be close to $2^mn^{2m} = 2^3(10^2)^{2\times 3} = 8\times10^{12}$, which is very far from the actual number of $649$ such leaves obtained in practice.
-This is also the case for the size of the CLSs, which are all very far away from its $\bigO(n^2)$ bound.
-The greatest CLS size observed was $174$ for instance CM9, which is still very far away from $n^2$, which in this case is $10^4$.
-
-\subsection{MCER-$k$}
-
-The numerical results obtained by our implementation of \autoref{algoritmo:mcer-k} are shown in \autoref{tab:mcer-results-cm} for instances CM1-CM9, and in \autoref{tab:mcer-results-ab1} and \autoref{tab:mcer-results-ab2} for instances AB001-AB120.
-An optimal solution was obtained for every instance, and overall, at most six seconds of CPU time was taken.
-
-Looking at the numerical results of the heuristic method proposed in \citeonline{andreta}, the only non-optimal solutions it encountered were for instances AB105-AB108.
-For these instances, our algorithm obtained an optimal solution covering one more point.
-In \autoref{fig:AB108}, the optimal solution for AB108 is displayed.
-In general, our algorithm took much lower CPU time compared to the methods developed in \citeonline{andreta}.
-For example, for instance CM9, their heuristic method took more than six hours to return a solution, our implementation of \autoref{algoritmo:mcer-k}, on the other hand, obtained an optimal solution in less than five seconds.
-
-\begin{figure}[!htb]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance AB108.}
-	\includegraphics[scale=.8]{tex/figures/AB108}
-	\fautor
-	\label{fig:AB108}
-\end{figure}
-
-As it was said for the results of MCE-$k$, in practice, the bounds for the CLS size and the number of operations taken by the algorithm is very loose.
-Notice that, the greatest CLS size was $730$ obtained for the third ellipse in instances CM7-CM9, which is very far away from its bound $\bigO(n^3)$, which in this case is $10^6$.
-By \autoref{th:mcer}, for MCER, the bound for the number of computations that \autoref{algoritmo:mcer-k} takes is $\bigO(2^mn^{3m})$.
-In instance AB120, for example, the size of the backtracking tree is only $7102$, which is way lower than $2^5100^{15}$.
-
-\section{New instances}
-
-After examining the results obtained by our algorithms for the formerly known instances, constructing new ones, more challenging for our work, can be taken as essential for further analyzing the algorithms proposed by us.
-Besides increasing the size of the demand set and the number of ellipses, we also designed instances with non-unitary weights, which is something none of the previous instances had. 
-Moreover, to create very distinct instances from the previously introduced ones, we used a different probability distribution, other than the uniform one, to generate the location of points.
-We set a time limit of two hours of running time for solving every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
-In total, we designed 46 new instances, which will be referred to as TA01, \dots, TA46, and are available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
-The numerical results for every one of them are displayed in \autoref{chapter:tables}.
-
-The first set of instances were construct sampling each demand points from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
-This is expected to produce a demand set with most points located near the origin, but with the most valuable points located far away from it.
-We generated a set of $n=100$ points, with $m=7$ ellipses, making the $j$-th ellipse have shape parameters randomly taken from a uniform distribution in $[0.5, 1.5]$, and cost $c_j=10\times a_j \times b_j$.
-From that, we created seven instances taking $k \in \{1, \dots, m\}$.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta1}.
-Because the normal distribution generates most of the points close to each other (see \autoref{fig:TA004} for an example), every ellipse's CLS's size ended up being significantly bigger if compared to previously introduced instances with $100$ points.
-This, and the subtle increase in the number of ellipses, made the algorithms for MCER-$k$ and MCE-$k$ time out for some instances.
-The algorithm for MCER-$k$ did not return an optimal solution within the predefined time limit for the last three instances ($k=5, 6, 7)$, while the algorithm for MCE-$k$ did not finish in time for the last instance ($k=7$).
-The optimal solution for MCER-$k$ for the instance with $k=4$ is displayed in \autoref{fig:TA004}.
-
-\begin{figure}[H]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA04.}
-	\includegraphics[scale=.8]{tex/figures/TA004}
-	\fautor
-	\label{fig:TA004}
-\end{figure}
-
-For the second set of instances, we used the same process used for the first set to generate the demand points and the ellipses.
-We kept the number of ellipses at $3$ and created five demand sets with $n\in\{200, 250, 300, 350, 400\}$.
-In total, we had $15$ instances having $k\in\{1, \dots, m\}$.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta2} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta2}.
-The solution of MCER-$k$ for the instance with $n=400$, and $k=2$ is shown in \autoref{fig:TA021}.
-
-\begin{figure}[H]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA21.}
-	\includegraphics[scale=.8]{tex/figures/TA021}
-	\fautor
-	\label{fig:TA021}
-\end{figure}
-
-The third set of instances were constructed generating the demand set following a uniform distribution in $[0, 10]^2$, with each point having unitary weight; and the ellipses by the same process used for the first two set of instances.
-We created instances with $m=5$, $n\in \{400, 450, 500\}$, and $k\in\{1, \dots, m\}$, with a total of $15$ instances.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta3} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta3}.
-Optimal solutions were obtained for every one of the instances in this set.
-It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
-The optimal solution of MCER-$k$ returned by \autoref{algoritmo:mcer-k} for the instance with $n=500$ and $k=5$ is shown in \autoref{fig:TA037}.
-
-\begin{figure}[!htb]
-	\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA37.}
-	\includegraphics[scale=.8]{tex/figures/TA037}
-	\fautor
-	\label{fig:TA037}
-\end{figure}
-
-The last set of instances were constructed using two bivariate normal distributions with unitary variance $\mathcal{N}(\mu^{(1)}, \mathbb{I})$ and $\mathcal{N}(\mu^{(2)}, \mathbb{I})$, $\mu^{(1)}, \mu^{(2)} \in \R^2$.
-Half of the points were generated following $\mathcal{N}(\mu^{(1)}, \mathbb{I})$, and the other half $\mathcal{N}(\mu^{(2)}, \mathbb{I})$; the weight of every point was set as its squared distance to the mean of the distribution from which it was generated.
-The ellipses were also divided into two halves, taking their shape parameters from uniform distributions in the intervals $[0.5, 1.5]$, and $[3, 4]$; setting the $j$-th ellipse's weight as $c_j=a_j \times b_j$.
-The purpose of this last set of instances was to create an example where the chosen ellipses in the solution of an instance of MCER-$k$ is not a subset of the chosen ellipses in an optimal solution of that same instance for MCER-$(k+1)$.
-We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$, and defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such counter-example.
-The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mce-results-ta4} for MCER-$k$.
-In \autoref{fig:TA44-45}, we show the solutions for the instances with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
-
-\begin{figure}[!htb]
-	\caption{Optimal solutions for instances TA44 and TA45.}
-	\begin{subfigure}{.5\textwidth}
-			\centering
-		\caption{TA44}
-		\includegraphics[scale=.6]{tex/figures/TA044}
-
-		%\fautor
-		\label{fig:TA043}
-	\end{subfigure}
-	\begin{subfigure}{.5\textwidth}
-			\centering
-		\caption{TA45}
-		\includegraphics[scale=.6]{tex/figures/TA045}
-		%\fautor
-		\label{fig:TA044}
-	\end{subfigure}
-\label{fig:TA44-45}
-	\fautor
-\end{figure}
+For example, without taking the suggestion given by \autoref{eq:upper-bound}, 
+MCER-$k$'s algorithm takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions, while the implementation using \autoref{eq:upper-bound} to prune the backtracking tree for the same instance takes less than one second, and evaluates only \num{1809} solutions in total.

### 2020-03-16 defesa/article/reducing_cls.tex
wip

As for the algorithms for both MCE and MCER, the number of solutions they go through is directly proportional to the size of each ellipse's CLS, reducing their size can significantly improve the performance of both algorithms.

For MCE (the MCER's case is analogous), let $q, q' \in S_j$ be two possible locations in the CLS for the $j$-th ellipse. If $\Pp \cap E_j(q') \subset \Pp \cap E_j(q)$, then $q'$ is redundant and we can remove it from $S_j$, as it produces a solution which is either non-optimal or equivalent to an optimal one.

To remove redundant elements from a CLS, we use the same tree-like data structure described in \cite{andreta}, which keeps every maximal subset of covered points by an ellipse, and supports a query operation to verify if a subset is maximal or not.
First, we sort the elements in $S_j$ by the number of covered demand points, non-decreasingly. Then, we iterate over it, removing elements which make the ellipse cover non-maximal subsets of demand points, when compared to the elements of $S_j$ that have already been processed.

### 2020-03-17 defesa/article/mcer.tex
wip

@@
 \end{figure}
-Let $x\in\R^2$, and $\angle x$ be the angle between $x$ and the vector $(1,0)$.
-Then we have that if $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as it is the angle that makes the ellipse's major-axis be parallel to the line that passes through $u$ and $v$.
+
+For any $x\in\R^2$, we denote by $\angle x\in [0, \pi)$ the minimal angle between $x$ and the vector $(1, 0)$.
+Then, if $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as it is the angle that makes the ellipse's major-axis be parallel to the line that passes through $u$ and $v$.
 

### 2020-03-17 defesa/article/implementation.tex
wip

@@
+In this section, we give more details about the implementation of the algorithms developed in our work.
+
 All the algorithms were implemented using the C++ language, compiled with g++ (G++ 6.3.0) with the optimization flag -O3.
 The actual code is available in \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
+
+\subsection{Determining the eigenvalues of a matrix}
+
+In the algorithm to obtain every solution of E3P described in \autoref{section:e3p}, we assumed that a procedure which returns every eigenvalue of a given complex matrix was available.
+In practice, we used the famous linear algebra package LAPACK (see \cite{lapack} for more details).
+Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
+The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference.
+Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.
+
+To compute every eigenvalue of a complex matrix, LAPACK offers a routine called ZGEEV, which is an implementation of the QR algorithm.
+This routine optionally can also be asked to compute the right or left eigenvectors depending on two of its parameters.
+
+% ZGEEV receives in total $14$ parameters, with $4$ of them being used for output.
+
+\subsection{Symbolic computation}
+
+Back in \autoref{section:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:xi} as a complex polynomial in the new variable $z=e^{i\theta}$.
+We suggested that symbolic computation should be used for this task, as the expressions for that polynomial's coefficients become very long, and doing that by hand is, to say the least, a very tedious work.
+Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
+In practice, we utilized an external library for Python called SymPy (see \cite{sympy} for more information).
+This tool can create expressions using arithmetic operators on predefined symbols, numbers, and other expressions.
+It can also convert expressions into polynomials in the power format, and output them directly into C code.
+Using these features, we wrote $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions by the identities $\cos\theta=(z+z^{-1})/2$ and $\sin\theta=(z+z^{-1})/(2i)$.
+
+The actual coefficients of that polynomial would take more than ten pages if they were to be presented here, because of that, we made them available elsewhere in \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.

### 2020-03-17 defesa/article/mce.tex
wip

@@
 
-\begin{thm}
+\begin{thm}\label{thm:mce}
 	Given an instance of MCE, and $S_1, \dots, S_m$ as defined by \autoref{def:cls_mce}, then the set $\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$.

### 2020-03-17 defesa/article/numerical.tex
wip

The goal of this chapter is to show the results of the algorithms for MCE-$k$ and MCER-$k$ proposed by us for instances proposed by other works as well as instances created by us. All the experiments were run in a computer with the following specification:
\begin{itemize}
	\item CPU Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz;
	\item 16Gib of RAM memory;
	\item Linux Operating System: Debian 4.19.5.
\end{itemize}

\subsection{Numerical Results for known instances}

In this section, we present the results of our algorithms for MCE-$k$ and MCER-$k$ 
for some instances proposed by \cite{canbolat, andreta}. 
We present here the numerical results for the instances CM6-CM9, and AB097-AB120. 
For each instance, we display the selected ellipses and the income, which is the weight of every covered point minus the cost of the selected ellipses, of the found optimal solution. 
We also display some performance metrics with the intention of giving an idea of how much computation had to be done for the algorithms to find an optimal solution. These metrics are: 
the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which were skipped.
We made available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/} every instance used here, along with the graphical representation of every obtained solution.

In \autoref{tab:mce-results-cm}, the results for instances CM7-CM9 are shown for MCE-$k$. 
The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than one second for every one of the instances CM7-CM9.
Even though the experiments were run in a different environment, we can still say that this is a great improvement compared with the results from \cite{andreta}. For example, to obtain an optimal solution for the instance CM9, the method proposed by \cite{andreta} took more than thirty minutes.
In \autoref{tab:mce-results-ab}, we present the results for instances AB097-AB120.
We can also observe here, that in practice, the bound for the CLS size of $n^2$ given by \autoref{thm:mce} seems to be very loose. The closest we got to this number was in instances CM7-CM9 where $|S_3|=174$, which is still very far from $n^2=100^2=\num{10000}$.

For MCER-$k$, the numerical results obtained by our implementation are shown in \autoref{tab:mcer-results-cm} for instances CM7-CM9, and in \autoref{tab:mcer-results-ab} for instances AB097-AB120. 
An optimal solution was obtained for every instance, and overall, at most six seconds of CPU time was taken.

Looking at the numerical results of the heuristic method proposed in \cite{andreta}, the only non-optimal solutions it encountered were for instances AB105-AB108. For these instances, our algorithm obtained an optimal solution covering one more point. In \autoref{fig:AB108}, the optimal solution for AB108 is displayed.
In general, our algorithm took much lower CPU time compared to the methods developed in \cite{andreta}. For example, for instance CM9, their heuristic method took more than six hours to return a solution, and their deterministic one exceeded the predefined time limit of twelve hours, while our implementation of the MCER-$k$'s algorithm took less than five seconds of CPU time.

\begin{figure}[!htb]

\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=.85]{figures/AB108}
	\caption{}
	\label{fig:AB108}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=.85]{figures/AB120}
	\caption{}
	\label{fig:AB120}
\end{subfigure}
	\caption{An optimal solution of MCER-$k$ for the instance AB108 (a), and for the instance AB120 (b).}
\end{figure}

\subsection{New instances}

After examining the results obtained for the formerly known instances, we decided to construct new ones to analyze the algorithms proposed by our work more thoroughly.

Besides increasing the size of the demand set and the number of ellipses, we also designed instances with non-unitary weights, which is something none of the previous instances had. 
Moreover, for some instances, we used a different probability distribution, other than the uniform distribution, to generate the location of the points.
We set a time limit of two hours of CPU time for every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
In total, we designed 46 new instances, which will be referred to as TA01, \dots, TA46, we made all of them available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.

The first set of instances were constructed sampling each demand point from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin. This is expected to produce a demand set with most points located near the origin, with the most valuable ones located far away from it.

We generated a set of $n=100$ points, with $m=7$ ellipses, making the $j$-th ellipse have shape parameters randomly taken from a uniform distribution in $[0.5, 1.5]$, and cost $c_j=10\times a_j \times b_j$. From that, we created seven instances for MCE-$k$ and MCER-$k$ taking $k \in \{1, \dots, m\}$. The results for MCE-$k$ are presented in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are displayed in \autoref{tab:mcer-results-ta1}.

The optimal solution for the instance TA04 for MCE-$k$ and MCER-$k$ is displayed in \autoref{fig:TA04}. There it is possible to see that because of the normal distribution, most of the points are located close to each other, near the origin, making every ellipse's CLS end up being bigger compared to the previously introduced instances with the same number of demand points. 
This, and the increase in the number of ellipses, made the algorithms for MCER-$k$ and MCE-$k$ time out for some instances. The algorithm for MCER-$k$ did not return an optimal solution within two hours for the instances TA05-TA07, while the algorithm for MCE-$k$ did not finish in time only for the instance TA07.

\begin{figure}[H]
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=.9]{figures/MCE_TA04}
	\caption{}
	\label{fig:MCE_TA04}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=.9]{figures/MCER_TA04}
	\caption{}
	\label{fig:MCER_TA04}
\end{subfigure}
	\caption{Two optimal solutions for the instance TA04: (a) for MCE-$k$, and (b) for MCER-$k$.}
	\label{fig:TA04}
\end{figure}

%%%% TABLE CM

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
				\hline
				\input{tables/table_mcek_cm.tex}
				\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances CM7-CM9.}
		\label{tab:mce-results-cm}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%
				%%%

				\hline
				\input{tables/table_mcerk_cm.tex}
				\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCER-$k$ for instances CM7-CM9.}
		\label{tab:mcer-results-cm}
	\end{center}
\end{table}

%%% FIM TABLE CM

%%% TABLE AB
\begin{table}[!htb]
	\begin{center}
		\resizebox{0.85\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header
				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol. leaves & CLS-MCE & Total\\
				\hline
				\input{tables/table_mcek_ab.tex}
				\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances AB097-AB120.}
		\label{tab:mce-results-ab}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tables/table_mcerk_ab.tex}
				\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCER-$k$ for instances AB097-AB120.}
		\label{tab:mcer-results-ab}
	\end{center}
\end{table}

%%% FIM TABLE AB
%%%% NEW INSTANCES

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tables/table_mcek_ta_1.tex}
				\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances TA001-TA007.}
		\label{tab:mce-results-ta1}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tables/table_mcerk_ta_1.tex}
				\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCER-$k$ for instances TA001-TA007.}
		\label{tab:mcer-results-ta1}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				%%%%
				%%%%

				\hline
				\input{tables/table_mcek_ta_2.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances TA008-TA022.}

		\label{tab:mce-results-ta2}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tables/table_mcerk_ta_2.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCER-$k$ for instances TA008-TA022.}

		\label{tab:mcer-results-ta2}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				%%%%
				%%%%

				\hline
				\input{tables/table_mcek_ta_4.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances TA023-TA042.}
		\label{tab:mce-results-ta3}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tables/table_mcerk_ta_4.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCER-$k$ for instances TA023-TA042.}
		\label{tab:mcer-results-ta3}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|crrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				%%%%
				%%%%

				\hline
				\input{tables/table_mcek_ta_5.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances TA043-TA047.}

		\label{tab:mce-results-ta4}
	\end{center}
\end{table}

\begin{table}[!htb]
	\begin{center}
		\resizebox{\textwidth}{!}{%

			\begin{tabular}{|cccc|cr|ccrrrr|}
				\hline
				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
				\hline

				%%% Second line of header

				\multirow{2}{*}{Name} & 
				\multirow{2}{*}{$n$} & 
				\multirow{2}{*}{$m$} & 
				\multirow{2}{*}{$k$} & 
				Selected & 
				\multirow{2}{*}{Income} & 
				CLS size&
				\# E3P&
				\multicolumn{2}{c}{Backtracking Tree} & 
				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\

				%%%%
				%%%%

				\hline
				\input{tables/table_mcerk_ta_5.tex}
				\hline
				%\input{tex/tables/table_mcerk_ta_3.tex}
				%\hline

			\end{tabular}
		}
		\caption{Numerical Results of MCE-$k$ for instances TA043-TA047.}

		\label{tab:mcer-results-ta4}
	\end{center}
\end{table}

### 2020-03-17 defesa/article/prunning.tex
wip

@@
-Without any improvement, backtracking through every possible combination of every ellipse's CLS can take a very long time, possibly going through a lot of non-optimal solutions. 
-For this reason, we introduce a sufficient condition for the MCER's case (the MCE's case is analogous), based on MCER for one ellipse, which can be used to skip solutions that for sure are non-optimal.
+In this section, we introduce a condition for skipping solutions in the backtracking process in the algorithms for MCE and MCER.
+The idea is to prune the backtracking tree by observing that any solution constructed going down the current branch will have a value less than or equal to the current best solution.
+As this condition can be applied for both problems, and their notation differs very little, we describe it only for MCE.
 
-\begin{definition}
-	Given an instance $(\Pp, \Ww, \Rr)$ of MCER.
-We define $OPT_j$ as the value of the best solution with the first $j$ ellipses fixed at locations $(q_1, \theta_1); \dots; (q_j, \theta_j)$, and $Z_j=\Pp \setminus \cup_{k=1}^j E_k(q_k, \theta_k)$.
-\end{definition}
+Given an instance $(\Pp, \Ww, \Rr)$ of MCE, an upper-bound for the value of an optimal solution is the sum of the optimal solutions for each ellipse individually:
+\begin{equation}\label{eq:upper-1}
+\max_{Q} w\left(\bigcup_{j=1}^m \Pp \cap E_j(q_j)\right) \le \sum_{j=1}^m \max_{q_j} w(\Pp \cap E_j(q_j)).
+\end{equation}
 
-Then, we can obtain an upper-bound for $OPT_j$ by using, for each $k\in\{j+1, \dots, m\}$, the solution $(q_k', \theta_k')$ of MCER for instance $(Z_k, \{w_i\colon p_i \in Z_k\}, \{(a_k, b_k)\})$.
-As these solutions only consider the best cover individually for each ellipse, we have the following inequality
-\begin{equation*}
-OPT_j \le w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) + w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right).
-\end{equation*}
-This upper-bound for $OPT_j$ can then be used in the backtracking process to skip solutions that are not better than any optimal solution.
-Let $OPT_{lo}$ be a lower bound for the optimal solution, we have that if
-\begin{equation}\label{eq:upper-bound}
-w\left(\bigcup_{k=1}^{j} \Pp \cap E_k(q_k, \theta_k)\right) +w\left(\bigcup_{k=j+1}^{m} \Pp \cap E_k(q_k', \theta_k')\right) \le OPT_{lo},
+Suppose that the first $k$ ellipses are fixed at locations $(q_1,\dots, q_k)$, and that we have an lower-bound $L$ for the value of an optimal solution.
+Let $Z_k=\Pp\setminus \cup_{j=1}^k E_j(q_j)$ be the points not covered by the first $k$ ellipses, then we can use \autoref{eq:upper-1} to verify if we can skip every solution where the first $k$ ellipses are fixed at  $(q_1,\dots, q_k)$ or not.
+If
+\begin{equation}\label{eq:upper}
+w\left(\bigcup_{j=1}^{k} \Pp \cap E_j(q_j)\right)+
+\sum_{j=k+1}^m \max_{q_j} w(Z_j \cap E_j(q_j)) \le L,
 \end{equation}
-then $OPT_j \le OPT_{lo}$, which implies that $OPT_j$ is less than or equal the value of any optimal solution.
-This defines a sufficient condition for us to dismiss every solution which have the location of the first $j$ ellipses fixed at $(q_1, \theta_1); \dots; (q_j, \theta_j)$.
-In practice, we can use the value of the best solution found so far as the lower-bound for the optimal solution.
+then, any solution with the first $k$ ellipses fixed at $(q_1,\dots, q_k)$ will have value less than or equal to the value of an optimal solution, therefore, we can cut the backtracking tree there.
+In practice, we can use the value of the best solution found at the moment as the lower-bound $L$.
 
-It is worth pointing out that these improvement suggestions do not have an effect in a possible worst case scenario.
-We are adopting them in our implementation because they showed good results in practice.
-For example, without taking the suggestion given by \autoref{eq:upper-bound}, 
-MCER-$k$'s algorithm takes nine seconds to obtain an optimal solution for instance AB060, going through \num{336494451} solutions, while the implementation using \autoref{eq:upper-bound} to prune the backtracking tree for the same instance takes less than one second, and evaluates only \num{1809} solutions in total.
+It is worth mentioning that this improvement do not have an effect in a possible worst case scenario. We decided to adopt it in our implementation because it showed good results in practice.
+For example, without it, 
+MCER-$k$'s algorithm takes nine seconds to obtain an optimal solution for instance AB060 developed by \cite{andreta}, going through \num{336494451} solutions, while the implementation using \autoref{eq:upper} to prune the backtracking tree for the same instance takes less than one second to return an optimal solution, and evaluates only \num{1809} solutions in total.

### 2020-03-18 defesa/article/numerical.tex
wip

@@
 	\centering
-	\includegraphics[scale=.85]{figures/AB108}
+	\includegraphics[scale=.9]{figures/MCER_AB108}
 	\caption{}
@@
 	\centering
-	\includegraphics[scale=.85]{figures/AB120}
+	\includegraphics[scale=.9]{figures/MCER_AB120}
 	\caption{}
@@
 We set a time limit of two hours of CPU time for every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
-In total, we designed 46 new instances, which will be referred to as TA01, \dots, TA46, we made all of them available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
+In total, we designed 47 new instances, which will be referred to as TA01, \dots, TA47, we made all of them available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
 
-The first set of instances were constructed sampling each demand point from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
+The first set of instances, TA01-TA07, were constructed sampling each demand point from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
 This is expected to produce a demand set with most points located near the origin, with the most valuable ones located far away from it.
-
 We generated a set of $n=100$ points, with $m=7$ ellipses, making the $j$-th ellipse have shape parameters randomly taken from a uniform distribution in $[0.5, 1.5]$, and cost $c_j=10\times a_j \times b_j$.
@@
 The results for MCE-$k$ are presented in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are displayed in \autoref{tab:mcer-results-ta1}.
-
-The optimal solution for the instance TA04 for MCE-$k$ and MCER-$k$ is displayed in \autoref{fig:TA04}.
+The optimal solutions for the instance TA04 for MCE-$k$ and MCER-$k$ are displayed in \autoref{fig:TA04}.
 There it is possible to see that because of the normal distribution, most of the points are located close to each other, near the origin, making every ellipse's CLS end up being bigger compared to the previously introduced instances with the same number of demand points.
@@
 
-\begin{figure}[H]
+For the second set of instances, TA08-TA22, we generated the demand set following the same process as for instances TA01-TA07.
+We kept the number of facilities at $3$ and created five demand sets with $n\in\{200, 250, 300, 350, 400\}$.
+In total, we had $15$ instances with $k\in\{1, \dots, m\}$.
+The results for MCE-$k$ are displayed in \autoref{tab:mce-results-ta2} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta2}.
+Our implementation of the algorithm for MCER-$k$ was not able to obtain a solution for the last instance TA22.
+Apart from instance TA13 for MCER-$k$, and instance TA22 for both algorithms, most of the CPU time was spent in constructing the CLSs.
+The graphical representation of solutions for the instance TA21 for MCE-$k$ and MCER-$k$ are shown in \autoref{fig:TA21}.
+
+The third set of instances, TA23-TA42, was constructed generating each demand point following a uniform distribution in $[0, 10]^2$, with each point having unitary weight; and the ellipses by the same process used for instances TA01-TA23.
+We created instances with $m=5$, $n\in \{400, 500, 600, 700\}$, and $k\in\{1, \dots, m\}$, with a total of $20$ instances.
+The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta3} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta3}.
+Optimal solutions were obtained for every one of the instances in this set.
+It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
+The optimal solution returned by MCER-$k$'s algorithm for the instance TA37 with $n=500$ and $k=5$ is shown in \autoref{fig:TA37}.
+
+The last set of instances, TA43-TA47, were constructed using two bivariate normal distributions with distinct means $\mathcal{N}(\mu^{(1)}, \mathbb{I})$ and $\mathcal{N}(\mu^{(2)}, \mathbb{I})$, $\mu^{(1)}, \mu^{(2)} \in \R^2$.
+Half of the points were generated following $\mathcal{N}(\mu^{(1)}, \mathbb{I})$, and the other half $\mathcal{N}(\mu^{(2)}, \mathbb{I})$; the weight of every point was set as its squared distance to the mean of the distribution from which it was generated.
+The ellipses were also divided into two halves, taking their shape parameters from uniform distributions in the intervals $[0.5, 1.5]$, and $[3, 4]$; setting the $j$-th ellipse's weight as $c_j=a_j \times b_j$.
+The purpose of this last set of instances was to create an example where the chosen ellipses in the solution of an instance of MCER-$k$ is not a subset of the chosen ellipses in an optimal solution of that same instance for MCER-$(k+1)$.
+We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$.
+We defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such a counter-example.
+The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mce-results-ta4} for MCER-$k$.
+In \autoref{fig:TA44-45}, we show the solutions for the instances TA44-TA45 with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
+
+\begin{figure}
 \begin{subfigure}{.5\textwidth}
@@
 
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{figures/MCE_TA21}
+		\caption{}
+		\label{fig:MCE_TA21}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{figures/MCER_TA21}
+		\caption{}
+		\label{fig:MCER_TA21}
+	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA21 with $400$ points: (a) for MCE-$k$, and (b) for MCER-$k$.}
+	\label{fig:TA21}
+\end{figure}
+
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{figures/MCE_TA37}
+		\caption{}
+		\label{fig:MCE_TA37}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{figures/MCER_TA37}
+		\caption{}
+		\label{fig:MCER_TA37}
+	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA37: (a) for MCE-$k$, and (b) for MCER-$k$.}
+	\label{fig:TA37}
+\end{figure}
+
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{figures/MCER_TA44}
+		\caption{}
+		\label{fig:MCER_TA44}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{figures/MCER_TA45}
+		\caption{}
+		\label{fig:MCER_TA45}
+	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA44: (a) for MCE-$k$, and (b) for MCER-$k$.}
+	\label{fig:TA44-45}
+\end{figure}
+
 %%%% TABLE CM
 
-\begin{table}[!htb]
+\begin{table}
 	\begin{center}
@@
 
-\begin{table}[!htb]
+\begin{table}
 	\begin{center}
@@
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \#sol leaves & CLS-MCER & Total\\
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \# sol leaves & CLS-MCER & Total\\
 
@@
 %%% TABLE AB
-\begin{table}[!htb]
+\begin{table}
 	\begin{center}
@@
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol. leaves & CLS-MCE & Total\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
 				\hline
@@
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \#sol leaves & CLS-MCER & Total\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol leaves & CLS-MCER & Total\\
 

### 2020-03-18 defesa/article/reducing_cls.tex
wip

@@
 
+In \cite{church:1984}, for the Euclidean PMCLP, this reduction to the CLSs is also employed, and after analyzing some experiments, they concluded that after the removal of redundant locations, the CLSs gets much smaller, and although the reduction step can be quite costly, in the end, it is worth it.
+
 To remove redundant elements from a CLS, we use the same tree-like data structure described in \cite{andreta}, which keeps every maximal subset of covered points by an ellipse, and supports a query operation to verify if a subset is maximal or not.

### 2020-03-18 defesa/tex/chapter/numerical.tex
wip

@@
 
-To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce} for MCE and \autoref{algoritmo:mcer} for MCER had to be done.
+To achieve the results that are shown later in this chapter, an efficient implementation of \autoref{algoritmo:mce2} for MCE and \autoref{algoritmo:mcer} for MCER had to be done.
 Just translating those algorithms into a programming language is not enough to obtain solutions for every instance previously published in \citeonline{andreta}.
@@
 
-Back in \autoref{chapter:mce}, it was shown that the size of a CLS in an instance of MCE is less than or equal $n^2$.
+Back in \autoref{chapter:mcd2}, it was shown that the size of a CLS in an instance of MCE is less than or equal $n^2$.
 This bound, at least for these instances, seems to be very loose.
@@
 
-After examining the results obtained by our algorithms for the formerly known instances, constructing new ones, more challenging for our work, can be taken as essential for further analyzing the algorithms proposed by us.
+After examining the results obtained for the formerly known instances, we decided to construct new ones to analyze the algorithms proposed by our work more thoroughly.
 Besides increasing the size of the demand set and the number of ellipses, we also designed instances with non-unitary weights, which is something none of the previous instances had. 
-Moreover, to create very distinct instances from the previously introduced ones, we used a different probability distribution, other than the uniform one, to generate the location of points.
-We set a time limit of two hours of running time for solving every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
-In total, we designed 46 new instances, which will be referred to as TA01, \dots, TA46, and are available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
-The numerical results for every one of them are displayed in \autoref{chapter:tables}.
+Moreover, for some instances, we used a different probability distribution, other than the uniform distribution, to generate the location of the points.
+We set a time limit of two hours of CPU time for every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
+In total, we designed 47 new instances, which will be referred to as TA01, \dots, TA47, we made all of them available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
 
-The first set of instances were construct sampling each demand points from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
-This is expected to produce a demand set with most points located near the origin, but with the most valuable points located far away from it.
+The first set of instances, TA01-TA07, were constructed sampling each demand point from a bivariate normal distribution $\mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$ being the identity matrix; and setting each point's weight as its squared distance to the origin.
+This is expected to produce a demand set with most points located near the origin, with the most valuable ones located far away from it.
 We generated a set of $n=100$ points, with $m=7$ ellipses, making the $j$-th ellipse have shape parameters randomly taken from a uniform distribution in $[0.5, 1.5]$, and cost $c_j=10\times a_j \times b_j$.
-From that, we created seven instances taking $k \in \{1, \dots, m\}$.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta1}.
-Because the normal distribution generates most of the points close to each other (see \autoref{fig:TA004} for an example), every ellipse's CLS's size ended up being significantly bigger if compared to previously introduced instances with $100$ points.
-This, and the subtle increase in the number of ellipses, made the algorithms for MCER-$k$ and MCE-$k$ time out for some instances.
-The algorithm for MCER-$k$ did not return an optimal solution within the predefined time limit for the last three instances ($k=5, 6, 7)$, while the algorithm for MCE-$k$ did not finish in time for the last instance ($k=7$).
-The optimal solution for MCER-$k$ for the instance with $k=4$ is displayed in \autoref{fig:TA004}.
+From that, we created seven instances for MCE-$k$ and MCER-$k$ taking $k \in \{1, \dots, m\}$.
+The results for MCE-$k$ are presented in \autoref{tab:mce-results-ta1} and the results for MCER-$k$ are displayed in \autoref{tab:mcer-results-ta1}.
+The optimal solutions for the instance TA04 for MCE-$k$ and MCER-$k$ are displayed in \autoref{fig:TA04}.
+There it is possible to see that because of the normal distribution, most of the points are located close to each other, near the origin, making every ellipse's CLS end up being bigger compared to the previously introduced instances with the same number of demand points.
+This, and the increase in the number of ellipses, made the algorithms for MCER-$k$ and MCE-$k$ time out for some instances.
+The algorithm for MCER-$k$ did not return an optimal solution within two hours for the instances TA05-TA07, while the algorithm for MCE-$k$ did not finish in time only for the instance TA07.
 
-\begin{figure}[H]
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
 		\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA04.}
-	\includegraphics[scale=.8]{tex/figures/TA004}
-	\fautor
-	\label{fig:TA004}
+		\includegraphics[scale=.9]{tex/figures/MCE_TA04}
+		\caption{}
+		\label{fig:MCE_TA04}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{tex/figures/MCER_TA04}
+		\caption{}
+		\label{fig:MCER_TA04}
+	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA04: (a) for MCE-$k$, and (b) for MCER-$k$.}
+	\label{fig:TA04}
 \end{figure}
 
-For the second set of instances, we used the same process used for the first set to generate the demand points and the ellipses.
-We kept the number of ellipses at $3$ and created five demand sets with $n\in\{200, 250, 300, 350, 400\}$.
-In total, we had $15$ instances having $k\in\{1, \dots, m\}$.
-The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta2} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta2}.
-The solution of MCER-$k$ for the instance with $n=400$, and $k=2$ is shown in \autoref{fig:TA021}.
+For the second set of instances, TA08-TA22, we generated the demand set following the same process as for instances TA01-TA07.
+We kept the number of facilities at $3$ and created five demand sets with $n\in\{200, 250, 300, 350, 400\}$.
+In total, we had $15$ instances with $k\in\{1, \dots, m\}$.
+The results for MCE-$k$ are displayed in \autoref{tab:mce-results-ta2} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta2}.
+Our implementation of the algorithm for MCER-$k$ was not able to obtain a solution for the last instance TA22.
+Apart from instance TA13 for MCER-$k$, and instance TA22 for both algorithms, most of the CPU time was spent in constructing the CLSs.
+The graphical representation of solutions for the instance TA21 for MCE-$k$ and MCER-$k$ are shown in \autoref{fig:TA21}.
 
-\begin{figure}[H]
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
 		\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA21.}
-	\includegraphics[scale=.8]{tex/figures/TA021}
-	\fautor
-	\label{fig:TA021}
+		\includegraphics[scale=.9]{tex/figures/MCE_TA21}
+		\caption{}
+		\label{fig:MCE_TA21}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{tex/figures/MCER_TA21}
+		\caption{}
+		\label{fig:MCER_TA21}
+	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA21 with $400$ points: (a) for MCE-$k$, and (b) for MCER-$k$.}
+	\label{fig:TA21}
 \end{figure}
 
-The third set of instances were constructed generating the demand set following a uniform distribution in $[0, 10]^2$, with each point having unitary weight; and the ellipses by the same process used for the first two set of instances.
-We created instances with $m=5$, $n\in \{400, 450, 500\}$, and $k\in\{1, \dots, m\}$, with a total of $15$ instances.
+The third set of instances, TA23-TA42, was constructed generating each demand point following a uniform distribution in $[0, 10]^2$, with each point having unitary weight; and the ellipses by the same process used for instances TA01-TA23.
+We created instances with $m=5$, $n\in \{400, 500, 600, 700\}$, and $k\in\{1, \dots, m\}$, with a total of $20$ instances.
 The results for MCE-$k$ can be seen in \autoref{tab:mce-results-ta3} and the results for MCER-$k$ are presented in \autoref{tab:mcer-results-ta3}.
@@
 It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
-The optimal solution returned by MCER-$k$'s algorithm for the instance with $n=500$ and $k=5$ is shown in \autoref{fig:TA037}.
+The optimal solution returned by MCER-$k$'s algorithm for the instance TA37 with $n=500$ and $k=5$ is shown in \autoref{fig:TA37}.
 
-\begin{figure}[!htb]
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
 		\centering
-	\caption{An optimal solution of MCER-$k$ for the instance TA37.}
-	\includegraphics[scale=.8]{tex/figures/TA037}
-	\fautor
-	\label{fig:TA037}
+		\includegraphics[scale=.9]{tex/figures/MCE_TA37}
+		\caption{}
+		\label{fig:MCE_TA37}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[scale=.9]{tex/figures/MCER_TA37}
+		\caption{}
+		\label{fig:MCER_TA37}
+	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA37: (a) for MCE-$k$, and (b) for MCER-$k$.}
+	\label{fig:TA37}
 \end{figure}
 
-The last set of instances were constructed using two bivariate normal distributions with unitary variance $\mathcal{N}(\mu^{(1)}, \mathbb{I})$ and $\mathcal{N}(\mu^{(2)}, \mathbb{I})$, $\mu^{(1)}, \mu^{(2)} \in \R^2$.
+The last set of instances, TA43-TA47, were constructed using two bivariate normal distributions with distinct means $\mathcal{N}(\mu^{(1)}, \mathbb{I})$ and $\mathcal{N}(\mu^{(2)}, \mathbb{I})$, $\mu^{(1)}, \mu^{(2)} \in \R^2$.
 Half of the points were generated following $\mathcal{N}(\mu^{(1)}, \mathbb{I})$, and the other half $\mathcal{N}(\mu^{(2)}, \mathbb{I})$; the weight of every point was set as its squared distance to the mean of the distribution from which it was generated.
@@
 The purpose of this last set of instances was to create an example where the chosen ellipses in the solution of an instance of MCER-$k$ is not a subset of the chosen ellipses in an optimal solution of that same instance for MCER-$(k+1)$.
-We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$, and defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such counter-example.
+We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$.
+We defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such a counter-example.
 The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mce-results-ta4} for MCER-$k$.
-In \autoref{fig:TA44-45}, we show the solutions for the instances with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
+In \autoref{fig:TA44-45}, we show the solutions for the instances TA44-TA45 with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
 
-\begin{figure}[!htb]
-	\caption{Optimal solutions for instances TA44 and TA45.}
+\begin{figure}
 	\begin{subfigure}{.5\textwidth}
 		\centering
-		\caption{TA44}
-		\includegraphics[scale=.8]{tex/figures/TA044}
-
-		%\fautor
-		\label{fig:TA043}
+		\includegraphics[scale=.9]{tex/figures/MCER_TA44}
+		\caption{}
+		\label{fig:MCER_TA44}
 	\end{subfigure}
@@
 		\centering
-		\caption{TA45}
-		\includegraphics[scale=.8]{tex/figures/TA045}
-		%\fautor
-		\label{fig:TA044}
+		\includegraphics[scale=.9]{tex/figures/MCER_TA45}
+		\caption{}
+		\label{fig:MCER_TA45}
 	\end{subfigure}
+	\caption{Two optimal solutions for the instance TA44: (a) for MCE-$k$, and (b) for MCER-$k$.}
 	\label{fig:TA44-45}
-	\fautor
 \end{figure}

### 2020-03-18 defesa/article/e3p.tex
wip

@@
 Let $|\Lambda(\theta)|$ denote the area of $\Lambda(\theta)$, using the formula from \cite[p.~189]{johnson1960} for the radius of a circumcircle of a triangle, and imposing that radius to be equal $b$, we define a function $\xi \colon [0, \pi) \to \R$ as
-\begin{equation*}
+\begin{equation}\label{eq:xi}
 \xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
-\end{equation*}
+\end{equation}
 whose roots are angles of rotation which determine solutions of E3P through the inverse transformation $\varphi^{-1}$.
@@
 \end{equation*}
-In practice, we can use the very well-known LAPACK software library to obtain the eigenvalues of a matrix; for more information about LAPACK see \cite{lapack}.
-This approach works for both real or complex polynomials, because of that, based on \cite{weidner}, we describe a way of converting $\xi$ into a complex polynomial.
+In practice, we can use the very well-known LAPACK software library to obtain the eigenvalues of a matrix\cite{lapack}.
+This approach works for both real or complex polynomials, and, because of that, based on \cite{weidner}, we describe a way of converting $\xi$ into a complex polynomial.
 
-By using the two identities $\cos{\theta} = (e^{i\theta} + e^{-i\theta})/2$, and $\sin{\theta} = (e^{i\theta} - e^{-i\theta})/(2i)$, which relate trigonometric functions with complex numbers in the unit circle $\mathbb{S}=\{z\in \mathbb{C}\colon |z|=1\}$, we can rewrite $\xi$ as a function of the variable $z=e^{i\theta}\in\mathbb{S}$.
+By using the identities $\cos{\theta} = (e^{i\theta} + e^{-i\theta})/2$, and $\sin{\theta} = (e^{i\theta} - e^{-i\theta})/(2i)$, which relate trigonometric functions with complex numbers in the unit circle $\mathbb{S}=\{z\in \mathbb{C}\colon |z|=1\}$, we can rewrite $\xi$ as a function of the variable $z=e^{i\theta}\in\mathbb{S}$.
 In \cite{weidner}, it is stated that this substitution when utilized for the task of determining the roots of a real trigonometric polynomial does not yield loss of accuracy.
@@
 
-Let $angle \colon \mathbb{C} \colon [0, 2\pi)$ be a function that takes a complex number and returns its angle, then given a root $\hat{z}$ of $g$, if $|\hat{z}|=1$ and $angle(\hat{z}) \in [0, \pi)$, then $\hat{\theta} = angle(\hat{z})$ is a root of $\xi$.
+Let $angle \colon \mathbb{C} \to [0, 2\pi)$ be a function that takes a complex number and returns its angle, then given a root $\hat{z}$ of $g$, if $|\hat{z}|=1$ and $angle(\hat{z}) \in [0, \pi)$, then $\hat{\theta} = angle(\hat{z})$ is a root of $\xi$.
 
@@
 In this section, we describe an experiment we made to choose a precision constant for comparing if a root of $f$ returned as an eigenvalue of its companion matrix is in the unit circle.
-The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of $f$, more information about the implementation is given in \autoref{section:implementation}.
+The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of $f$ (more information about the implementation is given in \autoref{section:implementation}).
 For the experiment, we defined $K\in\R$, $K>0$, and considered instances with the ellipse's shape parameters $(K, \frac{K}{2})$, for $K\in\{10^j\colon j=0,\dots,10\}$.
@@
 	\end{subfigure}
-\caption{(a) shows the maximum and average distance to the unit circle $|1-|\hat{z}||$. (b) shows the maximum and average error $|f(\hat{z})|$.}
+\caption{(a) Shows the maximum and average distance to the unit circle $|1-|\hat{z}||$. (b) Shows the maximum and average error $|f(\hat{z})|$.}
 \end{figure}
@@
 
-Any instance of E3P, as stated by \autoref{lema:e3p} can have up to six solutions.
+Any instance of E3P, as stated by \autoref{lema:e3p}, can have up to six solutions.
 At first, though, this bound seemed to be loose as for randomly generated instances, we were not able to obtain instances with more than two solutions.
@@
 After some investigation, we were able to construct some four-solution instances (an example is displayed in \autoref{fig:e3p_4sols}).
-An interesting property of those solutions is their three points form an isosceles triangle.
+An interesting property of those solutions is that their three points form an isosceles triangle.
 

### 2020-03-18 defesa/article/introduction.tex
wip

@@
 
-	An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j > 0$.
+	An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor axis of the $j$-th ellipse, with $a_j > b_j > 0$.
 We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$.

### 2020-03-18 defesa/article/mce.tex
wip

@@
 \begin{lem}\label{lema:e2p}
-	Let $E$ be the coverage region of an axis-parallel ellipse with shape parameters $(a,b)$; and $v \in \R^2$, $v\neq0$, then $|\partial E(0) \cap \partial E(v)| \le 2$, and $\partial E(0) \cap \partial E(v)$ can be determined analytically.
+	Let $E$ be the coverage region of an axis-parallel ellipse with shape parameters $(a,b)$; and $v \in \R^2$, $v\neq0$.
+Then $|\partial E(0) \cap \partial E(v)| \le 2$, and $\partial E(0) \cap \partial E(v)$ can be determined analytically.
 \end{lem}
@@
 	\begin{equation}
-	S_k = \bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \bigcup \Pp.
+	S_k = \Pp \cup \left(\bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \right).
 	\end{equation}
@@
 
-	if $|X_k| \le 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.
+	If $|X_k| \le 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.
 
-	if $|X_k| > 1$, then let $Y_k = \cap_{p \in X_k}E_k(p)$, by the results of \cite{bi}, we have that the boundary of $Y_k$ has vertices in the pairwise intersections of $\{\partial E_k(p) \colon p \in X_k\}$.
+	If $|X_k| > 1$, then let $Y_k = \cap_{p \in X_k}E_k(p)$.
+By the results of \cite{bi}, we have that the boundary of $Y_k$ has vertices in the pairwise intersections of $\{\partial E_k(p) \colon p \in X_k\}$.
 Therefore, at least one vertex of $Y_k$ is in $S_k$, and any of those vertices produce a solution that covers at least the same points covered by $Q^*$.
 
-	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$ hence $|\Omega| \le n^{2m}$.
+	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$. Hence, $|\Omega| \le n^{2m}$.
 \end{proof}
@@
 With all this in hand, we define \autoref{algoritmo:mce}, which goes through every possible combination in the CLS of each ellipse.
-As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has a $\bigO(mn^{2m+1})$ runtime complexity.
+As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has $\bigO(mn^{2m+1})$ runtime complexity.
 In \autoref{section:numerical}, we give more details about the implementation of \autoref{algoritmo:mce} and analyze some numerical experiments for instances proposed in \cite{canbolat, andreta}, and for some new ones.
@@
 		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
-		\If{$j = m+1$}
+		\If{$j = |\Rr|+1$}
 		\State \Return $0$

### 2020-03-18 defesa/article/mcer.tex
wip

@@
 \begin{definition}
-	Two solutions $Q$ and $Q'$ of MCER, are said to be equivalent to each other if \mbox{$\cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$}.
-Also, if $\cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) \subset \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$, then we say that $Q' \succ Q$.
+	Two solutions $Q$ and $Q'$ of MCER, are said to be equivalent to each other if \mbox{$\Pp \cap \cup_{j=1}^m E_j(q_j, \theta_j) = \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$}.
+Also, if $\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$, then we say that $Q' \succ Q$.
 \end{definition}
@@
 
-	Suppose that $u$ and $v$ have the same $y$-coordinate, if they do not, a rotation can be applied to make them do.
+	Suppose that $u$ and $v$ have the same $y$-coordinate (if they do not, a rotation can be applied to make them do).
 Then, by \autoref{lema:l-function}, $\Phi(u,v)=[0, \alpha] \cup [\pi-\alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.

### 2020-03-20 defesa/article/definition.tex
wip

%Given $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with weights $\Ww:=\{w_1, \dots, w_n\}$, $w_i\in\R_{\ge0}$; and $m$ shape parameters $\Rr:=\{(a_1, b_1); \dots; (a_m, b_m)\}$, with $(a_j, b_j) \in \R_{>0}^2$ being the semi-major and semi-minor axis of the $j$-th ellipse.

%For MCE, $\Rr$ describes the shape parameters of $m$ axis-parallel ellipses, and we want to determine a center $q_j\in\R^2$ for each one of them to maximize the weight of the covered points. For MCER, $\Rr$ describes the shape parameters of ellipses that not necessarily are axis-parallel, and we want to determine a center $q_j \in \R^2$, and an angle of rotation $\theta_j\in[0, \pi)$ for each ellipse to maximize the weight of the covered points.

An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{\ge0}^2$ being the semi-major and semi-minor axis of the $j$-th ellipse, with $a_j > b_j > 0$.

For MCE, the shape parameters describe axis-parallel ellipses, and the problem is to determine a center for each ellipse to maximize the weight of covered demand points. For MCER, besides the center, because the ellipses are not necessarily axis-parallel, for each facility, an angle of rotation is also part of the solution, and the problem is to maximize the weight of covered demand points as well.

Let $\E=\{E_1, \dots, E_m\}$ be a list of functions representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$. Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
\begin{equation*}
||x||_{a,b, \theta}=\left|\left|
\left(\begin{array}{rr}
\cos{\theta} & \sin{\theta}\\
\sin{\theta} & -\cos{\theta}
\end{array}
\right)
\left(\begin{array}{cc}
a_j & 0\\
0 & b_j
\end{array}\right) x \right|\right|_2,
\end{equation*}
then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j,0} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.

To make the notation more clear, we define a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$. 
Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE  as the optimization problem 
\begin{equation*}
\max_{Q}  w\left(\cup_{j=1}^m\Pp \cap E_j(q_j)\right),
\end{equation*}
and similarly MCER as
\begin{equation*}
\max_{Q} w\left(\cup_{j=1}^m\Pp \cap E_j(q_j, \theta_j)\right).
\end{equation*}

Additionally, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one ellipse, we omit the index referring to the facility, and we use $\partial$ as the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$.

\subsection{Facility Cost}

In \cite{canbolat, andreta}, as a result of having costs assigned to each facility, two other parameters are present in the definition of the problem.
These new parameters are: the list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost; 
and an integer $k\in\mathbb{N}$, $k\le m$, which introduces a constraint requiring that exactly $k$ facilities have to be utilized.
Because of that, a solution also needs an additional parameter $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$ to express the indexes of the utilized ellipses. We refer to this version of the problem as  MCE-$k$ and MCER-$k$.

From an algorithm for MCE (MCER), we can propose an algorithm for MCE-$k$ (MCER-$k$), which just takes the best overall solution among the $\binom{m}{k}$ instances $(\Pp, \Ww, \Rr')$, such that $\Rr' \subset \Rr$ and $|\Rr'| = k$. 
Therefore, in our work, we focus on developing algorithms for MCE and MCER, and whenever we refer to an algorithm for MCE-$k$ (MCER-$k$), we mean an algorithm as described here, which considers all the $\binom{m}{k}$ instances of MCE (MCER).

%Therefore, as this step can be seen as trivial, we focus on proposing algorithms for MCE and MCER, and in the section where we analyze the numerical experiments, as we use instances from \cite{andreta}, whenever we refer to an algorithm of MCE-$k$ (MCER-$k$), see it as an algorithm based on the approach described here, which uses $\binom{m}{k}$ instances of MCE (MCER) to obtain an optimal solution.

### 2020-03-20 defesa/article/introduction.tex
wip

--- 2020-03-15 defesa/article/introduction.tex
@@
-	
 The Planar Maximum Covering Location Problem (PMCLP) was first introduced in \cite{church:1984}, and can be seen as a category of problems where the coverage of a demand set, a collection of subsets of $\R^2$, is to be maximized by determining the location of facilities in $\R^2$, with coverage being determined by a distance function.
@@
 The first version will be referred to as Planar Maximum Covering Location by Ellipses Problem (MCE) and the second one as  Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER).
-
-	\section{Problem Definition}
-
-	An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)$ being the semi-major and semi-minor of the $j$-th ellipse, with $a_j > b_j > 0$.
-We define a list of functions $\E=\{E_1, \dots, E_m\}$ representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$.
-Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
-	\begin{equation}
-	||x||_{a,b, \theta}=\left|\left|
-	\left(\begin{array}{rr}
-	\cos{\theta} & \sin{\theta}\\
-	\sin{\theta} & -\cos{\theta}
-	\end{array}
-	\right)
-	\left(\begin{array}{cc}
-	a_j & 0\\
-	0 & b_j
-	\end{array}\right) x \right|\right|_2,
-	\end{equation}
-	then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j,0} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.
-
-Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE as the optimization problem 
-\begin{equation}
-\max_{q_1, \dots, q_m} \sum_{j=1}^m w(\Pp \cap E_j(q_j)),
-\end{equation}
-and similarly MCER as
-\begin{equation}
-\max_{(q_1, \theta_1), \dots, (q_m, \theta_m)} \sum_{j=1}^m w(\Pp \cap E_j(q_j, \theta_j)).
-\end{equation}
-
-To make the notation more clear, we denote an instance of MCE or MCER as the tuple $(\Pp, \Ww, \Rr)$, and a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$.
-Additionally, whenever we have an instance with only one ellipse, we omit the index referring to the facility, and define a solution of MCE as $q\in\R^2$, and of MCER as $(q, \theta) \in \R^2\times [0, \pi)$.
-We also use $\partial$ as the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$.
-
-\subsection{Facility Cost}
-
-Additionally, in \cite{canbolat, andreta}, two other parameters are present in the definition of the problem.
-This extension is the result of having costs associated with every facility hence, to create a decision about which ones are utilized, a new parameter $k\in\mathbb{N}$ is given limiting the number of utilized ellipses to be exactly $k$.
-
-We refer to this version of the problem as  MCE-$k$, and MCER-$k$.
-An instance of it is given by the same parameters as MCE and MCER, plus a list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost, and $k\in\mathbb{N}$, $k\le m$.
-A solution needs another set $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$ to express the indexes of the utilized ellipses.
-
-Solving MCE-$k$ (MCER-$k$) can be done by considering the $\binom{m}{k}$ instances of MCE (MCER-$k$), and then taking the best one as the optimal solution, taking into account the cost of each utilized ellipse.
-As this step can be seen as trivial, we propose algorithms for MCE and MCER, and then in \autoref{section:numerical}, as we use the instances from \cite{canbolat, andreta} in the numerical experiments, we analyze the results obtained by our implementations of the algorithms proposed in this work for MCE-$k$ and MCER-$k$.

### 2020-03-20 defesa/article/mce.tex
wip

@@
 
-Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, then consider the problem where $n$ ellipses\\ $E(p_1), \dots, E(p_n)$ are given, and a solution is defined as a point $q\in\R^2$, with an optimal one maximizing
-$w(\{p_i\in\Pp \colon q\in E(p_i)\})$.
-These two problems are equivalent as, let $q\in\R^2$, and $A\subset\Pp$; then $q\in\cap_{p\in A}E(p)$ if, and only if $\Pp \cap E(q) = A$.
+To define this equivalent problem, we need to first state an ellipse's property.
+Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with one facility, and  $p, q \in \R^2$, we have that
+\begin{equation}\label{eq:mce-mwc}
+p \in E(q) \Leftrightarrow ||p-q||_{a, b, 0} \le 1 \Leftrightarrow q \in E(p).
+\end{equation}
+The equivalent problem is given by $n$ ellipses with shape parameters $(a, b)$ centered at $\Pp$.
+Let $q\in\R^2$ be a solution of MCE for one facility, by applying \autoref{eq:mce-mwc} to every point covered by $E(q)$, we obtain that
+\begin{equation}
+\Pp \cap E(q) = \{p_i\in\Pp \colon q\in E(p_i)\},
+\end{equation}
+which implies that the problem of determining $q\in\R^2$ to maximize $w(\{p_i\in\Pp \colon q\in E(p_i)\})$, is equivalent to MCE for one facility.
+This changes the problem from determining a location for an ellipse given $n$ points to the problem of finding a point given $n$ ellipses with fixed locations.
 
@@
 Based on that, given an instance of MCE, we define the CLS for each ellipse considering also the case where an ellipse could cover only one point in an optimal solution.
+
+\begin{figure}[!htb]
+
+	\centering
+
+	\includegraphics[scale=.3]{figures/MCE-vertices2}
+	\caption{Transforming a solution of E3P into a solution of the circumcircle problem.}
+	\label{fig:MCE-vertices}
+\end{figure}
 
@@
 \begin{definition}\label{def:cls_mce}
-	Given an instance of MCE, for any $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
+	Given an instance of MCE, for all $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
 	\begin{equation}
@@
 
-By \autoref{lema:e2p}, the CLS for each ellipse can be computed in $\bigO(n^2)$.
+By \autoref{lema:e2p}, the CLS for each ellipse can be computed in $\bigO(n^2)$, and $|S_k| \le n + 2\binom{n}{2}$.
 Next, we establish a lemma stating that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.

### 2020-03-20 defesa/article/mce.tex
wip

--- 2020-03-18 defesa/article/mce.tex
@@
 Similarly to the method developed in \cite{church:1984} for the Euclidean PMCLP, we will describe a Candidate List Set (CLS) of possible locations for each ellipse and then propose an algorithm that constructs solutions combining the possible locations in each ellipse's CLS.
-Based on the approach of \cite{chazelle:1986,cabello:2006}, we will construct the CLS for each ellipse by working with a problem equivalent to MCE for only one facility.
+Also, based on the approach of \cite{church:1984} for the Euclidean PMCLP, and in \cite{chazelle:1986} for the problem of covering points by one unit disk, we will construct the CLS for each ellipse by using a property of the one-facility MCE.
+Although, it is intuitive that it is possible to adapt the ideas used for solving the problems involving Euclidean disks for axis-parallel ellipses, using the results of \cite{bi}, which studies the problem of determining the intersection of $n$ strictly convex disks with fixed radius, we will prove that for MCE, we have all the necessary geometric properties to develop an algorithm following those approaches.
 
-Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, then consider the problem where $n$ ellipses\\ $E(p_1), \dots, E(p_n)$ are given, and a solution is defined as a point $q\in\R^2$, with an optimal one maximizing
-$w(\{p_i\in\Pp \colon q\in E(p_i)\})$.
-These two problems are equivalent as, let $q\in\R^2$, and $A\subset\Pp$; then $q\in\cap_{p\in A}E(p)$ if, and only if $\Pp \cap E(q) = A$.
+We start by introducing a lemma stating that any solution of the one-facility MCE can be related to the intersection of coverage regions of ellipses centered at the points covered in that solution.
 
-To construct the CLS for each ellipse, let us consider the intersection region $\cap_{p\in A} E(p)$, for some $A\subset \Pp$, $|A|>1$. In \cite{church:1984}, this region 
-is said to have vertices that are in the set of pairwise intersections of the circles with centers in $A$.
-Using the results of \cite{bi}, which develops an algorithm to determine the intersection region of $n$ fixed-radii disks in an strictly convex normed space, it is possible to prove that this is also true for ellipses.
-Based on that, given an instance of MCE, we define the CLS for each ellipse considering also the case where an ellipse could cover only one point in an optimal solution.
+\begin{lem}\label{lema:mce-mwc}
+	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$.
+\end{lem}
+\begin{proof}
+	Let $u, v \in \R^2$, then we have that $u \in E(v)$ if, and only if $v \in E(u)$, which is proved simply by observing that:
+	\begin{equation}\label{eq:peq}
+	u \in E(v) \Leftrightarrow ||u-v||_{a, b, 0} \le 1 \Leftrightarrow v \in E(u).
+	\end{equation}
+	As $\Pp \cap E(q) = A$ can be written as: for all $p \in A$, $p \in E(q)$. Then, using \autoref{eq:peq}, we get that for all $p \in A$, $q \in E(p)$, which implies that $q \in \cap_{p\in A} E(p)$.
+\end{proof}
+
+%To define this equivalent problem, we need to first state an ellipse's property.
+%Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with one facility, and  $p, q \in \R^2$, we have that
+
+%The equivalent problem is given by $n$ ellipses with shape parameters $(a, b)$ centered at $\Pp$.
+Let $q\in\R^2$ be a solution of MCE for one facility, by applying \autoref{eq:peq} to every point covered by $E(q)$, we obtain that
+%\begin{equation}\label{eq:mce-mwc}
+%\Pp \cap E(q) = \{p_i\in\Pp \colon q\in E(p_i)\},
+%\end{equation}
+%which implies that the problem of determining $q\in\R^2$ to maximize $w(\{p_i\in\Pp \colon q\in E(p_i)\})$, is equivalent to MCE for one facility.
+This changes the problem from determining a location for an ellipse given $n$ points to the problem of finding a point given $n$ ellipses with fixed locations.
+
+%Let $A\subset \Pp$, from \autoref{eq:mce-mwc}, we have that if $\Pp \cap E(q) = A$ then $q \in \cap_{p\in A} E(p)$.
+
+From , if we could identify every
+
+Let $A \subset \Pp$, $|A|>1$, let us consider the intersection region $\cap_{p\in A} E(p) \neq \emptyset$.
+From \autoref{lema:mce-mwc}, we can also conclude that if $q \in \cap_{p\in A} E(p)$, then $A \subset \Pp \cap E(q)$.
+
+In \cite{church:1984}, for the Euclidean PMCLP, it was proved that the border of this region contains at least one point that is an intersection between two fixed-radius circles with centers in $A$.
+This, as it turns out, is also true for ellipses, and a proof can be obtained from \cite{bi} where the problem of determining the intersection region of $n$ fixed-radius disks in a strictly convex normed plane is studied.
+From that, we can conclude that there exists $u, v \in A$ and $q \in \partial E(u) \cap \partial E(v)$, such that $q \in \cap_{p\in A} E(p)$.
+Before defining the CLS for each ellipse, we introduce a lemma stating two basic, and yet important properties about the intersection between two axis-parallel ellipses that have the same shape and distinct locations.
 
@@
 \begin{proof}
-	By \cite{bi}, we have that the number of intersections between two strictly convex circles of fixed radii is at most two.
 	To determine the intersection points, consider the equality between the equations of $\partial E(0)$ and $\partial E(v)$:
 	$x^2/a^2 + y^2/b^2 = (x-v_x)^2/a^2 + (y-v_y)^2/b^2.$
-	This expression can be reduced to $y=\alpha x + \beta$, for some $\alpha, \beta$.
-Using $\partial E(0)$'s equation, we obtain at most two values for $x$, which consequently, by $y=\alpha x + \beta$, determine the intersection points between the two ellipses.
+	This expression can be reduced to $y=\alpha x + \beta$, for some $\alpha, \beta$, which can then be plugged into $\partial E(0)$'s equation obtaining $x^2/a^2 + (\alpha x + \beta)^2/b^2 = 1$.
+	We obtain the intersection points by solving this quadratic equation for $x$, and then, for each value of $x$,  determining $y$ from $y=\alpha x + \beta$.
 \end{proof}
-
+Next, we define the CLS of each ellipse, considering also the case where, in an optimal solution, an ellipse covers only one point.
 \begin{definition}\label{def:cls_mce}
-	Given an instance of MCE, for any $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
+	Given an instance of MCE, for all $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
 	\begin{equation}

### 2020-03-21 defesa/article/article.tex
wip

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{subcaption}
+\usepackage{siunitx}
+\sisetup{group-separator = {,}}
+
+\usepackage{multirow}
+
 \journal{EJOR}
@@
 \newtheorem{thm}{Theorem}
-\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prp}{Proposition}
+\newtheorem{lem}{Lemma}
 \newdefinition{rmk}{Remark}
 \newdefinition{definition}{Definition}
-\newproof{pf}{Proof}
+%\newproof{pf}{Proof}
+%\renewcommand\qedsymbol{$\blacksquare$}
 
@@
 \newcommand{\thmautorefname}{Theorem}
+\newcommand{\prpautorefname}{Proposition}
+\newcommand{\lemmaautorefname}{Lemma}
+\newcommand{\lemautorefname}{Lemma}
 
@@
 			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
-			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances having with up to seven hundred demand points and five ellipses.
+			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances with up to seven hundred demand points and five ellipses.
 		\end{abstract}
@@
 
+\section{Definition}\label{section:definition}
+\input{definition.tex}
+
 \section{An algorithm for MCE}\label{section:mce}
@@
 
-\section{Determining every location of an ellipse given its shape and three points}\label{section:e3p}
+\section{Determining every center and angle of rotation of an ellipse given its shape and three points that it must contain}\label{section:e3p}
 
@@
 
+\section{Improvements}\label{section:improvements}
+\input{improvements.tex}
+
+%\section{Reducing the CLS size}\label{section:reducing_cls}
+%\input{reducing_cls.tex}
+
+%\section{Prunning the Backtracking Tree}\label{section:prunning}
+%\input{prunning.tex}
+
 \section{Implementation Details}\label{section:implementation}
+\input{implementation.tex}
 
 \section{Numerical Experiments}\label{section:numerical}
+\input{numerical.tex}
 
+\section{Conclusion}\label{section:conclusion}
+\input{conclusion.tex}
+
+\clearpage
 \section*{References}

### 2020-03-21 defesa/article/conclusion.tex
wip

In this work, we studied two problems of maximum planar covering using ellipses, with most of the substantial results being for the less previously-studied problem where the ellipses can be freely rotated, which we referred to as MCER. 
We devoted most of our work for the development of an exact algorithm for this problem, which depended on the development of an algorithm for a never-studied-before geometric subproblem, which we referred to as E3P. The algorithm proposed for this last problem involves determining the eigenvalues of a six by six complex matrix to obtain the roots of a degree-six polynomial. We believe that further properties can be discovered which would allow the development of a simpler method to obtain the roots of the polynomial whose roots are solutions of E3P.

An exact algorithm was also developed for the other problem where the ellipses had to be axis-parallel. We took a different approach compared to the methods proposed by \cite{canbolat, andreta}, and based our algorithm entirely on the model proposed for the Euclidean PMCLP in \cite{church:1984}.

After giving improvement suggestions for the implementation of both algorithms, we analyzed several numerical experiments that were made using instances from \cite{canbolat, andreta}, and some new ones. Both algorithms performed really well, obtaining optimal solutions for every previously known instance, and only timing out for the really challenging ones from the set of newly constructed ones.

### 2020-03-21 defesa/article/definition.tex
wip

@@
 
-Additionally, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one ellipse, we omit the index referring to the facility, and we use $\partial$ as the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$.
+We define an equivalence and a partial order relation between solutions of both MCE and MCER as follows.
+Two solutions $Q$ and $Q'$ of MCE (MCER), are said to be equivalent to each other if
+they both cover the same set of demand points.
+% $\cup_{j=1}^m \Pp \cap E_j(q_j) = \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($ \cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$).
+That is, two solutions are equivalent if they cover the same set of points.
+We also define a partial order: $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.
+
+%if, and only if $\cup_{j=1}^m \Pp \cap E_j(q_j) \subset \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$).
+That is, $Q' \succ Q$ if, and only if the set of points covered in solution $Q$ is a subset of the points covered in solution $Q'$.
+
+%%% esse paragrafo ainda ta estranho.
+Additionally, we denote by $\partial$ the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ represents the set of points $\{p \in \R^2\colon ||p-q_1||_{a_1,b_1,0} = 1\}$.
+Also, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one facility, we omit the index referring to the ellipse.
 

### 2020-03-21 defesa/article/mce.tex
wip

@@
 Similarly to the method developed in \cite{church:1984} for the Euclidean PMCLP, we will describe a Candidate List Set (CLS) of possible locations for each ellipse and then propose an algorithm that constructs solutions combining the possible locations in each ellipse's CLS.
-Also, based on the approach of \cite{church:1984} for the Euclidean PMCLP, and in \cite{chazelle:1986} for the problem of covering points by one unit disk, we will construct the CLS for each ellipse by using a property of the one-facility MCE.
-Although, it is intuitive that it is possible to adapt the ideas used for solving the problems involving Euclidean disks for axis-parallel ellipses, using the results of \cite{bi}, which studies the problem of determining the intersection of $n$ strictly convex disks with fixed radius, we will prove that for MCE, we have all the necessary geometric properties to develop an algorithm following those approaches.
 
-We start by introducing a lemma stating that any solution of the one-facility MCE can be related to the intersection of coverage regions of ellipses centered at the points covered in that solution.
+To construct a CLS for each ellipse, based on the approach of \cite{church:1984} for the Euclidean PMCLP, and on \cite{chazelle:1986} for the problem of maximizing the coverage of points by a unit disk, we will describe some properties of the one-facility MCE, which will reduce our task to determining the pairwise intersection between ellipses centered at $\Pp$.
 
-\begin{lem}\label{lema:mce-mwc}
-	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$.
-\end{lem}
+%Although, it is intuitive that it is possible to adapt the ideas used for solving the problems involving Euclidean disks for axis-parallel ellipses, using the results of \cite{bi}, which studies the problem of determining the intersection of $n$ strictly convex disks with fixed radius, we will prove that for MCE, we have all the necessary geometric properties to develop an algorithm following those approaches.
+
+We start by introducing a proposition stating that any solution of the one-facility MCE can be related to the intersection of coverage regions of ellipses centered at the points covered in that solution.
+
+\begin{prp}\label{lema:mce-mwc}
+	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
+\end{prp}
 \begin{proof}
@@
 	\end{equation}
-	As $\Pp \cap E(q) = A$ can be written as: for all $p \in A$, $p \in E(q)$. Then, using \autoref{eq:peq}, we get that for all $p \in A$, $q \in E(p)$, which implies that $q \in \cap_{p\in A} E(p)$.
+	Therefore, if $p\in A$, then by \autoref{eq:peq}, $q \in E(p)$, which implies $q \in \cap_{p\in A} E(p)$.
+	The second part of the lemma also follows from \autoref{eq:peq} as if $q' \in \cap_{p\in A} E(p)$, then $||q' - p||_{a,b,0} \le 1$ for all $p \in A$.
 \end{proof}
 
-%To define this equivalent problem, we need to first state an ellipse's property.
-%Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with one facility, and  $p, q \in \R^2$, we have that
+By \autoref{lema:mce-mwc}, we can ignore solutions that are not in $\cap_{p\in A} E(p)$, for some $A \subset \Pp$.
+Because ellipses can be described by strictly convex norms, we will show that the set $\cap_{p\in A} E(p)$ has some convenient properties, which can be used to narrow down the solutions' search space even more.
 
-%The equivalent problem is given by $n$ ellipses with shape parameters $(a, b)$ centered at $\Pp$.
-Let $q\in\R^2$ be a solution of MCE for one facility, by applying \autoref{eq:peq} to every point covered by $E(q)$, we obtain that
-%\begin{equation}\label{eq:mce-mwc}
-%\Pp \cap E(q) = \{p_i\in\Pp \colon q\in E(p_i)\},
-%\end{equation}
-%which implies that the problem of determining $q\in\R^2$ to maximize $w(\{p_i\in\Pp \colon q\in E(p_i)\})$, is equivalent to MCE for one facility.
-This changes the problem from determining a location for an ellipse given $n$ points to the problem of finding a point given $n$ ellipses with fixed locations.
+Let us assume that $|A|>1$ and consider the intersection region $\cap_{p\in A} E(p)$. 
+In \cite{church:1984}, for the Euclidean PMCLP, it was proved that the border of this region contains at least one point that is an intersection between two fixed-radius circles with centers in $A$.
+For ellipses, this means that $ \cap_{p\in A} E(p)$ contains at least one element from the set $\cup_{u, v \in A}\partial E(u) \cap \partial E(v)$.
 
-%Let $A\subset \Pp$, from \autoref{eq:mce-mwc}, we have that if $\Pp \cap E(q) = A$ then $q \in \cap_{p\in A} E(p)$.
+To prove that this is true, we resort to the results of \cite{bi}, which develops an algorithm to determine the intersection region of $n$ strictly convex disks of fixed radius.
+There, it is stated that this intersection region is bounded by the arcs of some of the disks that are part of the intersection, and also that the vertices of this region form a subset of the set of pairwise intersections of the $n$ given circles.
+Following this result, we define the next lemma.
 
-From , if we could identify every
+\begin{lem}\label{lema:mce}
+	Let $q\in \R^2$ be a solution of MCE for the instance $(\Pp, \Ww, \{(a, b)\})$.
+	If $|\Pp \cap E(q)|\ge 2$, then there exists $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, such that $q' \succ q$.
+\end{lem}
+\begin{proof}
+	By \autoref{lema:e2p}, let $A=\Pp \cap E(q)$, we have that for any $q' \in \cap_{p\in A} E(p)$, $q' \succ q$. 
+	Furthermore, by the results of \cite{bi}, we have that there exists $q' \in \cup_{u, v \in A}\partial E(u) \cap \partial E(v)$, such that $q' \in \cup_{p\in A} E(p)$. 
+	Therefore, $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, and $q' \succ q$.
+\end{proof}
 
-Let $A \subset \Pp$, $|A|>1$, let us consider the intersection region $\cap_{p\in A} E(p) \neq \emptyset$.
-From \autoref{lema:mce-mwc}, we can also conclude that if $q \in \cap_{p\in A} E(p)$, then $A \subset \Pp \cap E(q)$.
+Before defining the CLS for each ellipse, we introduce a proposition indicating how to compute the intersection between two axis-parallel ellipses.
 
-In \cite{church:1984}, for the Euclidean PMCLP, it was proved that the border of this region contains at least one point that is an intersection between two fixed-radius circles with centers in $A$.
-This, as it turns out, is also true for ellipses, and a proof can be obtained from \cite{bi} where the problem of determining the intersection region of $n$ fixed-radius disks in a strictly convex normed plane is studied.
-From that, we can conclude that there exists $u, v \in A$ and $q \in \partial E(u) \cap \partial E(v)$, such that $q \in \cap_{p\in A} E(p)$.
-Before defining the CLS for each ellipse, we introduce a lemma stating two basic, and yet important properties about the intersection between two axis-parallel ellipses that have the same shape and distinct locations.
-
-\begin{lem}\label{lema:e2p}
+\begin{prp}\label{lema:e2p}
 	Let $E$ be the coverage region of an axis-parallel ellipse with shape parameters $(a,b)$; and $v \in \R^2$, $v\neq0$.
 Then $|\partial E(0) \cap \partial E(v)| \le 2$, and $\partial E(0) \cap \partial E(v)$ can be determined analytically.
-\end{lem}
+\end{prp}
 
@@
 \end{proof}
-Next, we define the CLS of each ellipse, considering also the case where, in an optimal solution, an ellipse covers only one point.
+Next, we define the CLS for each facility, taking into account solutions where the two points are contained on the ellipse as given by \autoref{lema:mce}, and also, solutions where the ellipse covers only one demand point.
+
 \begin{definition}\label{def:cls_mce}
@@
 By \autoref{lema:e2p}, the CLS for each ellipse can be computed in $\bigO(n^2)$, and $|S_k| \le n + 2\binom{n}{2}$.
-Next, we establish a lemma stating that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.
+Next, we establish the main result of this section, which states that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.
 
@@
 \begin{proof}
-	Let $Q^*$ be an optimal solution of MCE for the given instance. Then, we are going to prove that there exists $Q' \in \Omega$, which is also optimal.
+	Let $Q^*$ be a solution of MCE. Then, we are going to prove that there exists $Q' \in \Omega$, such that $Q'\succ Q^*$.
 
-	For each $k=1, \dots, m$, let $X_k = \{p_i \in \Pp\colon p_i \in E_k(q_k^*)\}$.
+	For each $k\in \{1, \dots, m\}$, let $X_k = \{p_i \in \Pp\colon p_i \in E_k(q_k^*)\}$.
 
@@
 
-	If $|X_k| \le 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.
+	If $|X_k| \le 1$, then there is at least one element $q_k'\in S_k$ that makes $X_k \subset E_k(q_k')$.
 
-	If $|X_k| > 1$, then let $Y_k = \cap_{p \in X_k}E_k(p)$.
-By the results of \cite{bi}, we have that the boundary of $Y_k$ has vertices in the pairwise intersections of $\{\partial E_k(p) \colon p \in X_k\}$.
-Therefore, at least one vertex of $Y_k$ is in $S_k$, and any of those vertices produce a solution that covers at least the same points covered by $Q^*$.
+	If $|X_k| > 1$, by \autoref{lema:mce}, we have that there exists $q_k' \in S_k$, such that $X_k \subset E_k(q_k')$.
 
-	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$. Hence, $|\Omega| \le n^{2m}$.
+	Lastly, by \autoref{lema:e2p}, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$. Hence, $|\Omega| \le n^{2m}$.
 \end{proof}
@@
 As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has $\bigO(mn^{2m+1})$ runtime complexity.
-In \autoref{section:numerical}, we give more details about the implementation of \autoref{algoritmo:mce} and analyze some numerical experiments for instances proposed in \cite{canbolat, andreta}, and for some new ones.
+In \autoref{section:improvements}, we give some suggestions of improvements that can be applied to the implementation of \autoref{algoritmo:mce}, and in \autoref{section:numerical}, we analyze the results obtained by \autoref{algoritmo:mce} for some numerical experiments.
 
@@
 		\EndProcedure
-		\State
+
+		\item[]
+
 		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
-		\If{$j = |\Rr|+1$}
-		\State \Return $0$
-		\EndIf
-
 		\State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$
@@
 			\State $Cov \gets \Pp \cap E_j(q_j)$
+			\If{$j < |\Rr|$}
 				\State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$
+			\EndIf
 

### 2020-03-21 defesa/article/mcer.tex
wip

@@
 
-\begin{definition}
-	Two solutions $Q$ and $Q'$ of MCER, are said to be equivalent to each other if \mbox{$\Pp \cap \cup_{j=1}^m E_j(q_j, \theta_j) = \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$}.
-Also, if $\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$, then we say that $Q' \succ Q$.
-\end{definition}
+%To make the text more clear, we introduce an equivalence relation for the set of solutions of MCER, and also a order relation making the set of solutions partially ordered.
 
-Next, we introduce a lemma which states that any optimal solution of MCER has an equivalent solution where every ellipse that covers at least two points has two points on its border.
+Let $(\Pp, \Ww, \{(a,b)\})$ be an instance of MCER, then given a solution $Q$ for it, with $|\Pp \cap E(q, \theta)| \ge 2$, if we rotate the coordinate system by $-\theta$, and use the result given by \autoref{lema:mce} for an axis-parallel ellipse, we can conclude that another solution $Q'$ exists, such that $Q' \succ Q$ and $|\Pp \cap \partial E(q', \theta)| \ge 2$.
+That is, given a solution for the one-facility MCER, we can obtain another one that covers the same points (possibly more) and the ellipse contains two demand points.
 
-\begin{lem}\label{lema:mce_2b}
-	Let $Q^*$ be a solution of MCER for an instance $(\Pp, \Ww, \{(a,b)\})$.
-	If $|\Pp \cap E(q^*, \theta^*)| \ge 2$, then there exists a solution $Q$ for the same instance, such that $Q \succ Q^*$, and $|\Pp \cap \partial E(q, \theta)|\ge 2$.
-\end{lem}
-
-\begin{proof}
-	First, let $\theta=\theta^*$ and ignore the angle of rotation as it does not change, and assume that we are dealing with an axis-parallel ellipse.
-
-	Let $A=\Pp \cap E(q^*, \theta^*)$ and $X=\cap_{p \in A}E(p, \theta^*)$ be the region of intersection of ellipses centered at each point in $A$.
-By \cite{bi}, the vertices of $\partial X$ are in the set of pairwise intersections of $\{\partial E(p, \theta^*)\colon p \in A\}$.
-Setting $q$ as any of these vertices makes $E(q, \theta)$ have two points on its border.
-\end{proof}
-
-%Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.
-
-%\begin{definition}
-%	Let $Q^*$ be an optimal solution of MCER.
-We define $\Pi(Q^*)$ as the set of every equivalent solution to $Q^*$, such that for any $Q \in\Pi(Q^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j')| \ge 2$.
-%\end{definition}
-
-Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.
+Next, we define a new notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.
 
@@
 
+%%%%% TODO: TERMINEI DE REVISAR AKI.
+
 \begin{figure}[H]
@@
 	\includegraphics[scale=.22]{figures/feasible-angle2}
-	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
+	\caption{The solid border ellipses are rotated by a $(E, u,v)$-feasible angle, while the ellipse with a dashed border is rotated by a not $(E, u, v)$-feasible angle.}
 	\label{fig:feasible-angle}
@@
 For any $x\in\R^2$, we denote by $\angle x\in [0, \pi)$ the minimal angle between $x$ and the vector $(1, 0)$.
-Then, if $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as it is the angle that makes the ellipse's major-axis be parallel to the line that passes through $u$ and $v$.
+If $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as $\angle(u-v)$ is the angle that makes the ellipse's major-axis, the longest segment crossing an ellipse, be parallel to the line that passes through $u$ and $v$.
 
@@
 \begin{proof}
-	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that $Q' \succ Q^*$ exists, and $\{u, v\} \subset \partial E(q', \theta^*)$.
+	According to \autoref{lema:mce}, there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that $Q' \succ Q^*$ exists, and $\{u, v\} \subset \partial E(q', \theta^*)$.
 Therefore, $\theta^*\in\Phi(u,v)$.
@@
 		\ForAll{$(q_j, \theta_j) \in S_j$}
-		%\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
+		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
 
-		\If{$j < m$}
+		\If{$j < |\Rr|$}
 		\State $(q_{j+1},\theta_{j+1}); \dots; (q_m,\theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$

### 2020-03-22 defesa/article/conclusion.tex
wip

@@
-In this work, we studied two problems of maximum planar covering using ellipses, with most of the substantial results being for the less previously-studied problem where the ellipses can be freely rotated, which we referred to as MCER.
-We devoted most of our work for the development of an exact algorithm for this problem, which depended on the development of an algorithm for a never-studied-before geometric subproblem, which we referred to as E3P.
-The algorithm proposed for this last problem involves determining the eigenvalues of a six by six complex matrix to obtain the roots of a degree-six polynomial.
-We believe that further properties can be discovered which would allow the development of a simpler method to obtain the roots of the polynomial whose roots are solutions of E3P.
+In this work, we developed new algorithms for two planar maximum covering by ellipses problems.
+After some improvements suggestions were given, numerical experiments were conducted showing the efficiency of both algorithms for instances from previous works and for new ones with larger demand and facility sets.
 
-An exact algorithm was also developed for the other problem where the ellipses had to be axis-parallel.
-We took a different approach compared to the methods proposed by \cite{canbolat, andreta}, and based our algorithm entirely on the model proposed for the Euclidean PMCLP in \cite{church:1984}.
+We devoted most of our work to the development of an exact algorithm for the version of the problem where the ellipses can be freely rotated.
+In the midst of that, a never-studied-before subproblem came up, for which we also proposed an algorithm involving determining the roots of a complex polynomial.
+Our algorithm for this version of the problem was able to obtain optimal solutions for instances which the heuristic method developed in \cite{andreta} returned non-optimal ones, and the deterministic method timed out.
 
-After giving improvement suggestions for the implementation of both algorithms, we analyzed several numerical experiments that were made using instances from \cite{canbolat, andreta}, and some new ones.
-Both algorithms performed really well, obtaining optimal solutions for every previously known instance, and only timing out for the really challenging ones from the set of newly constructed ones.
+We believe that the never-studied-before subproblem, which was the subject of \autoref{section:e3p}, has some properties that we were not able to explore, which could be the subject of future work. 
+We observed that the solutions, except for one case, always come in pairs; and that the generated complex polynomial whose roots provide solutions for the problem appears to be a self-inverse polynomial.

### 2020-03-22 defesa/article/implementation.tex
wip

@@
 In practice, we used the famous linear algebra package LAPACK (see \cite{lapack} for more details).
-Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the -llapack linking flag to the compilation.
+Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the \textit{-llapack} linking flag to the compilation.
 The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference.
@@
 
-The actual coefficients of that polynomial would take more than ten pages if they were to be presented here, because of that, we made them available elsewhere in \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
+%The actual coefficients of that polynomial would take more than ten pages if they were to be presented here, because of that, we made them available elsewhere in \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.

### 2020-03-22 defesa/article/introduction.tex
wip

@@
 It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
-In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
-For some instances, the method took too long and did not find an optimal solution.
+In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem, and, because it took too long and did not find an optimal solution for some of the proposed instances, a heuristic method was developed using a technique called Simulated Annealing.
+%For some instances, the method took too long and did not find an optimal solution.
 Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
-The problem was further explored in \cite{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
+
+Initially, in the version of the problem defined in \cite{canbolat}, the ellipses could not be rotated. In \cite{andreta} though, the problem where the ellipses can be freely rotated was introduced.
+
+which introduced the version where the ellipses can be freely rotated.
+
+to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
 The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.

### 2020-03-22 defesa/article/mce.tex
wip

@@
 \begin{proof}
-	Let $u, v \in \R^2$, then we have that $u \in E(v)$ if, and only if $v \in E(u)$, which is proved simply by observing that:
+	Let $u, v \in \R^2$, then we have the following equivalence:
 	\begin{equation}\label{eq:peq}
@@
 	\end{equation}
-	Therefore, if $p\in A$, then by \autoref{eq:peq}, $q \in E(p)$, which implies $q \in \cap_{p\in A} E(p)$.
-	The second part of the lemma also follows from \autoref{eq:peq} as if $q' \in \cap_{p\in A} E(p)$, then $||q' - p||_{a,b,0} \le 1$ for all $p \in A$.
+	Therefore, if $p\in A$, by \autoref{eq:peq}, then $q \in E(p)$, which implies $q \in \cap_{p\in A} E(p)$.
+	The second part of the lemma also follows from \autoref{eq:peq}. If $q' \in \cap_{p\in A} E(p)$, then $||q' - p||_{a,b,0} \le 1$ for all $p \in A$.
 \end{proof}
 
-By \autoref{lema:mce-mwc}, we can ignore solutions that are not in $\cap_{p\in A} E(p)$, for some $A \subset \Pp$.
-Because ellipses can be described by strictly convex norms, we will show that the set $\cap_{p\in A} E(p)$ has some convenient properties, which can be used to narrow down the solutions' search space even more.
+By \autoref{lema:mce-mwc}, given a solution $q\in\R^2$, such that for all $A \subset \Pp$, $|A|\neq \emptyset$, $q \not \in \cap_{p\in A} E(p)$, then $\Pp \cap E(q) = \emptyset$.
+Therefore, we can focus on studying the intersection set $\cap_{p\in A} E(p)$, as solutions that are not in one do not cover any demand points.
 
@@
 
-To prove that this is true, we resort to the results of \cite{bi}, which develops an algorithm to determine the intersection region of $n$ strictly convex disks of fixed radius.
+To prove that this is true for ellipses, we resort to the results of \cite{bi}, which develops an algorithm to determine the intersection region of $n$ strictly convex disks of fixed radius.
 There, it is stated that this intersection region is bounded by the arcs of some of the disks that are part of the intersection, and also that the vertices of this region form a subset of the set of pairwise intersections of the $n$ given circles.

### 2020-03-23 defesa/article/definition.tex
wip

@@
 
-An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{\ge0}^2$ being the semi-major and semi-minor axis of the $j$-th ellipse, with $a_j > b_j > 0$.
+An instance of MCE and MCER is given by $n$ distinct demand points $\Pp=\{p_1, \dots, p_n\}$, $p_j\in\R^2$; $n$ weights $\Ww=\{w_1, \dots, w_n\}$, with $w_j\in\R_{>0}$ being the weight of the $j$-th point; and $m$ shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$, with $(a_j, b_j)\in\R_{\ge0}^2$ being the semi-major and semi-minor axis of the $j$-th ellipse, with $a_j > b_j$.
 

### 2020-03-25 defesa/article/article.tex
wip

@@
 \newcommand{\lemautorefname}{Lemma}
+\newcommand{\sigla}[2]{#2 (#1)}
+\newcommand{\citeonline}[1]{\cite{#1}}
 
@@
 
-		\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
+		\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
 		\tnotetext[t1]{This paper is the results of the research
-			project funded by CAPES.}
+			project funded by CAPES and FAPESP.}
 
@@
 
-		%\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
+		\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
 		%\author{John Smith}
@@
 		\begin{keyword}
-			Optimization \sep Covering \sep Combinatorial Optimization
+			Combinatorial optimization \sep planar maximal covering location problem \sep planar covering by ellipses \sep exact algorithms.
 			%% keywords here, in the form: keyword \sep keyword
@@
 
-\section{An algorithm for MCE}\label{section:mce}
+\section{An Algorithm for MCE}\label{section:mce}
 
@@
 
-\section{Determining every center and angle of rotation of an ellipse given its shape and three points that it must contain}\label{section:e3p}
+\section{Determining Every Center and Angle of Rotation of An Ellipse Given Its Shape and Three Points that It Must Contain}\label{section:e3p}
 

### 2020-03-25 defesa/article/conclusion.tex
wip

@@
 In this work, we developed new algorithms for two planar maximum covering by ellipses problems.
-After some improvements suggestions were given, numerical experiments were conducted showing the efficiency of both algorithms for instances from previous works and for new ones with larger demand and facility sets.
+After giving improvements suggestions, and implementation details, we analyzed numerical experiments showing the efficiency of both algorithms for the instances of previous works, and for new ones with larger demand and facility sets.
 
-We devoted most of our work to the development of an exact algorithm for the version of the problem where the ellipses can be freely rotated.
-In the midst of that, a never-studied-before subproblem came up, for which we also proposed an algorithm involving determining the roots of a complex polynomial.
-Our algorithm for this version of the problem was able to obtain optimal solutions for instances which the heuristic method developed in \cite{andreta} returned non-optimal ones, and the deterministic method timed out.
-
-We believe that the never-studied-before subproblem, which was the subject of \autoref{section:e3p}, has some properties that we were not able to explore, which could be the subject of future work. 
-We observed that the solutions, except for one case, always come in pairs; and that the generated complex polynomial whose roots provide solutions for the problem appears to be a self-inverse polynomial.
+We devoted most of our work to the development of an exact algorithm for MCER.
+In the midst of that, a never-studied-before subproblem came up, for which we also proposed an algorithm, which involved determining the roots of a complex polynomial of degree six.
+We believe that further exploring this new problem could be the subject of future work as we observed that its solutions, except for one case, always come in pairs; and that this property seems to be directly connected with the complex polynomial, as its roots seem to come in conjugate pairs.
+These properties, if proved to be true, might be used in the development of a more efficient algorithm.

### 2020-03-25 defesa/article/cover.tex
wip

--- 2020-03-12 defesa/article/article.tex
@@
-\documentclass[3p, 11pt]{elsarticle}
+\documentclass{article}
 
@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{subcaption}
-\journal{EJOR}
+\usepackage{siunitx}
+\sisetup{group-separator = {,}}
+
+\usepackage{multirow}
+
+%\journal{EJOR}
 
@@
 \newtheorem{thm}{Theorem}
-\newtheorem{lem}[thm]{Lemma}
-\newdefinition{rmk}{Remark}
-\newdefinition{definition}{Definition}
-\newproof{pf}{Proof}
+\newtheorem{prp}{Proposition}
+\newtheorem{lem}{Lemma}
+%\newdefinition{rmk}{Remark}
+%\newdefinition{definition}{Definition}
+%\newproof{pf}{Proof}
+%\renewcommand\qedsymbol{$\blacksquare$}
 
@@
 \newcommand{\thmautorefname}{Theorem}
+\newcommand{\prpautorefname}{Proposition}
+\newcommand{\lemmaautorefname}{Lemma}
+\newcommand{\lemautorefname}{Lemma}
+\newcommand{\sigla}[2]{#2 (#1)}
+\newcommand{\citeonline}[1]{\cite{#1}}
 
 \begin{document}
+		\title{Cover Letter}
+		\maketitle
 
-	\begin{frontmatter}
+		Dear Editor, we herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.
 
-		%% Title, authors and addresses
+		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.
 
-		\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
-		\tnotetext[t1]{This paper is the results of the research
-			project funded by CAPES.}
+		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.
 
-		%% use the tnoteref command within \title for footnotes;
-		%% use the tnotetext command for the associated footnote;
-		%% use the fnref command within \author or \address for footnotes;
-		%% use the fntext command for the associated footnote;
-		%% use the corref command within \author for corresponding author footnotes;
-		%% use the cortext command for the associated footnote;
-		%% use the ead command for the email address,
-		%% and the form \ead[url] for the home page:
-		%%
-		%% \title{Title\tnoteref{label1}}
-		%% \tnotetext[label1]{}
-		%% \author{Name\corref{cor1}\fnref{label2}}
-		%% \ead{email address}
-		%% \ead[url]{home page}
-		%% \fntext[label2]{}
-		%% \cortext[cor1]{}
-		%% \address{Address\fnref{label3}}
-		%% \fntext[label3]{}
-
-		%% use optional labels to link authors explicitly to addresses:
-		%% \author[label1,label2]{<author name>}
-		%% \address[label1]{<address>}
-		%% \address[label2]{<address>}
-
-		\author[1]{Danilo Tedeschi}
-		\ead{danilo.tedeschi@usp.br}
-
-		\author[2]{Marina Andretta}
-		\ead{andretta@gmail.com}
-
-		%\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
-		%\author{John Smith}
-
-		%address{California, United States}
-
-		\begin{abstract}
-			%% Text of abstract
-			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
-			maximizing a function depending on the value of covered points.
-			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
-			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances having with up to seven hundred demand points and five ellipses.
-		\end{abstract}
-
-		\begin{keyword}
-			Optimization \sep Covering \sep Combinatorial Optimization
-			%% keywords here, in the form: keyword \sep keyword
-
-			%% MSC codes here, in the form: \MSC code \sep code
-			%% or \MSC[2008] code \sep code (2000 is the default)
-
-		\end{keyword}
-
-	\end{frontmatter}
-
-\section{Introduction}\label{section:introduction}
-
-\input{introduction.tex}
-
-\section{An algorithm for MCE}\label{section:mce}
-
-\input{mce.tex}
-
-\section{Determining every location of an ellipse given its shape and three points}\label{section:e3p}
-
-\input{e3p.tex}
-
-\section{An Algorithm for MCER}\label{section:mcer}
-
-\input{mcer.tex}
-
-\section{Implementation Details}\label{section:implementation}
-
-\section{Numerical Experiments}\label{section:numerical}
-
-\section*{References}
+		%\section*{References}
 		%% New version of the num-names style
-	\bibliographystyle{elsarticle-num}
-	\bibliography{../references}
+		%\bibliographystyle{elsarticle-num}
+		%\bibliography{../references}
 
 \end{document}
-
-%%
-%% End of file `elsarticle-template-1-num.tex'.

### 2020-03-25 defesa/article/definition.tex
wip

@@
 \begin{equation*}
-\max_{Q}  w\left(\cup_{j=1}^m\Pp \cap E_j(q_j)\right),
+\max_{Q}  w\left(\bigcup_{j=1}^m\Pp \cap E_j(q_j)\right),
 \end{equation*}
@@
 \begin{equation*}
-\max_{Q} w\left(\cup_{j=1}^m\Pp \cap E_j(q_j, \theta_j)\right).
+\max_{Q} w\left(\bigcup_{j=1}^m\Pp \cap E_j(q_j, \theta_j)\right).
 \end{equation*}
-
-We define an equivalence and a partial order relation between solutions of both MCE and MCER as follows.
-Two solutions $Q$ and $Q'$ of MCE (MCER), are said to be equivalent to each other if
-they both cover the same set of demand points.
-% $\cup_{j=1}^m \Pp \cap E_j(q_j) = \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($ \cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$).
-That is, two solutions are equivalent if they cover the same set of points.
-We also define a partial order: $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.
-
-%if, and only if $\cup_{j=1}^m \Pp \cap E_j(q_j) \subset \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$).
-That is, $Q' \succ Q$ if, and only if the set of points covered in solution $Q$ is a subset of the points covered in solution $Q'$.
-
-%%% esse paragrafo ainda ta estranho.
-Additionally, we denote by $\partial$ the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ represents the set of points $\{p \in \R^2\colon ||p-q_1||_{a_1,b_1,0} = 1\}$.
-Also, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one facility, we omit the index referring to the ellipse.
 
@@
 In \cite{canbolat, andreta}, as a result of having costs assigned to each facility, two other parameters are present in the definition of the problem.
-These new parameters are: the list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost; 
+These new parameters are: the list of costs $\Cc:=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost; 
 and an integer $k\in\mathbb{N}$, $k\le m$, which introduces a constraint requiring that exactly $k$ facilities have to be utilized.
@@
 
+\subsection{Additional Notation}
+
+%Let $Q$ and $Q'$ be two solutions of MCE or MCER, we define two relations between solutions:
+%\begin{itemize}
+	%\item $Q$ is equivalent to $Q'$ if, and only if the set of covered demand points in both solutions is the same.
+	%\item $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.
+%\end{itemize}
+
+We define an instance of the one-facility MCE or MCER as $(\Pp, \Ww, \{(a,b)\})$ omitting the facility index in every notation. For example, a solution of MCER is denoted as $Q := (q, \theta)$.
+
+Two solutions $Q$ and $Q'$ of MCE or MCER are said to be equivalent to each other if
+the set of covered demand points in both solutions is the same.
+We also define a partial order: $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.
+
+%%% esse paragrafo ainda ta estranho.
+We use the notation $\partial$ to denote the boundary operator.
+For example, let $E \colon \R^2\to\R^2$ be the coverage region of an axis-parallel ellipse, then let $q\in\R^2$, $\partial E(q)$ describes an axis-parallel ellipse centered at $q$.
+If $E$ has shape parameters $(a, b)$, then $\partial E(q) = \{p \in \R^2\colon ||p-q||_{a,b,0} = 1\}$.
+
+%Also, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one facility, we omit the index referring to the ellipse. 
 %Therefore, as this step can be seen as trivial, we focus on proposing algorithms for MCE and MCER, and in the section where we analyze the numerical experiments, as we use instances from \cite{andreta}, whenever we refer to an algorithm of MCE-$k$ (MCER-$k$), see it as an algorithm based on the approach described here, which uses $\binom{m}{k}$ instances of MCE (MCER) to obtain an optimal solution.

### 2020-03-25 defesa/article/e3p.tex
wip

@@
 
-Given the shape parameters of an ellipse $(a, b)$, $a > b >0$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
+Given the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, $a > b$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
 Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.

### 2020-03-25 defesa/article/introduction.tex
wip

--- 2020-03-20 defesa/article/introduction.tex
@@
-The Planar Maximum Covering Location Problem (PMCLP) was first introduced in \cite{church:1984}, and can be seen as a category of problems where the coverage of a demand set, a collection of subsets of $\R^2$, is to be maximized by determining the location of facilities in $\R^2$, with coverage being determined by a distance function.
-In \cite{church:1984}, methods for Euclidean and Rectilinear distances versions of the problem were proposed.
-In \cite{drezner, chazelle:1986}, exact algorithms for the Euclidean PMCLP with only one facility are proposed; and in \cite{cabello:2006} an approximation algorithm is proposed for the version with multiple unit disks as facilities.
-A property of the Euclidean PMCLP, which is utilized in the algorithms developed in \cite{drezner, chazelle:1986, cabello:2006}, and in the method proposed in \cite{church:1984}, is that there is an optimal solution which every facility is located in the demand points, or in the intersection of two circles centered at two demand points; we will prove a similar property for ellipses in our work.
+\sigla{MCLP}{The Maximum Covering Location Problem}, introduced in \cite{church:1974}, is 
+a problem defined on graphs where the objective is to maximize the coverage of a demand set, a subset of the graph's vertices, by choosing the location of a fixed number of facilities, with each facility covering every demand node located within a predefined radius from it.
+MCLP was introduced motivated by the practical observation that covering one hundred percent of a population, which was the subject of most of the covering location problems at that time, can take much more resources than covering ninety percent of it.
 
-It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
-In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem.
-For some instances, the method took too long and did not find an optimal solution.
-Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
-The problem was further explored in \cite{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
-The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.
+A continuous extension of MCLP, where the facility and demand sets are located on the plane and coverage is determined by a norm function, was introduced in \cite{church:1984} and named \sigla{PMCLP}{Planar Maximal Covering Location Problem} following the advances on covering location problems on the plane that were being made at the time.
+
+PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in \cite{bansal}, for example, they are defined as rectangles.
+In \cite{church:1984}, a method was proposed for the version of PMCLP, where the facilities have Euclidean norm coverage.
+This method consisted of obtaining a discrete set of solutions for each facility, which was proved to contain at least one optimal solution, and then using the model developed for MCLP in \cite{church:1974} to determine an optimal solution.
+
+The Euclidean PMCLP is also found in the literature in an algorithmic context as the \sigla{MCD}{Maximum Covering by Disks Problem}.
+In \citeonline{chazelle:1986}, a $\bigO(n^2)$ algorithm for the one-disk version of MCD was proposed, beating the prior $\bigO(n^2\log{n})$ algorithm created in \citeonline{drezner} for the same problem.
+A version with multiple unit disks was studied in \citeonline{cabello:2006}, which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$.
+To achieve its main goal, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
+Additionally, in \citeonline{aronov:2008}, one-disk MCD is proven to be 3SUM-HARD.
+This means that maximizing the number of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.
 
@@
 In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
-The first version will be referred to as Planar Maximum Covering Location by Ellipses Problem (MCE) and the second one as  Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER).
+The first version will be referred to as \sigla{MCE}{Planar Maximum Covering Location by Ellipses Problem} and the second one as  \sigla{MCER}{Planar Maximum Covering Location by Ellipses with Rotation Problem}.
+
+It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
+In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to MCE.
+For some instances, the method took too long and did not find an optimal solution.
+Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
+
+The problem was further explored in \citeonline{andreta}, where exact methods were developed for both MCE and MCER, and a heuristic method was developed for MCER.
+All the methods proposed in \cite{andreta} were based on the enumerative approach of solving optimization subproblems to determine whether an ellipse could cover a subset of demand points or not.
+To avoid having to solve subproblems for every subset of demand points, a tree-like data structure was designed to skip non-maximal sets of demand points.
+The only difference in their methods for MCE and MCER was the subproblem.
+As the subproblem for MCE was a convenient convex optimization model, the method for it performed well and  was able to obtain optimal solutions for instances the method from \cite{canbolat} could not.
+The subproblem for MCER, on the other hand, was more challenging, and ended up making the method time out for large instances.
+For this reason, a heuristic method was developed treating the optimization subproblem as a convex problem.
+The method was able to obtain solutions for every instance, and for the ones the exact method did not time out, it could be verified that the heuristic method returned optimal solution as well.
+
+Based on the developments of \cite{church:1984} for the Euclidean PMCLP, we define a finite set of solutions for each one of the problems, MCE and MCER, which we prove to contain at least one optimal solution, and that, if the number of facilities is assumed to be constant, its size is bounded by a polynomial.
+We propose algorithms for both problems based on the computation of this set of solutions to determine an optimal one.
+For MCER, computing this set of solutions involves solving a subproblem, on which we could not find any prior study, thus, a whole section is devoted to the development of an algorithm for it.
+Besides all that, we give implementation details for both algorithms, and also improvement suggestions which, in practice, can significantly lower the number of solutions evaluated to return an optimal one.
+In the end, we analyze numerical experiments for instances proposed in \cite{canbolat, andreta} and compare the results with the results obtained by the methods proposed in \cite{andreta}.
+Also, to further analyze our algorithms, we also analyzed numerical experiments for new instances with larger demand and facility sets.

### 2020-03-25 defesa/article/mce.tex
wip

@@
 
+%\begin{prp}\label{lema:mce-mwc}
+%	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
+%\end{prp}
+
 \begin{prp}\label{lema:mce-mwc}
-	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
+	Let $q\in \R^2$ be a solution of the one-facility MCE. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
 \end{prp}
@@
 \begin{lem}\label{lema:mce}
-	Let $q\in \R^2$ be a solution of MCE for the instance $(\Pp, \Ww, \{(a, b)\})$.
+	Let $q\in \R^2$ be a solution of the one-facility MCE.
 	If $|\Pp \cap E(q)|\ge 2$, then there exists $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, such that $q' \succ q$.

### 2020-03-25 defesa/article/mcer.tex
wip

@@
 
-Let $(\Pp, \Ww, \{(a,b)\})$ be an instance of MCER, then given a solution $Q$ for it, with $|\Pp \cap E(q, \theta)| \ge 2$, if we rotate the coordinate system by $-\theta$, and use the result given by \autoref{lema:mce} for an axis-parallel ellipse, we can conclude that another solution $Q'$ exists, such that $Q' \succ Q$ and $|\Pp \cap \partial E(q', \theta)| \ge 2$.
+Given an instance of the one-facility MCER, then given a solution $Q$ for it, with $|\Pp \cap E(q, \theta)| \ge 2$, if we rotate the coordinate system by $-\theta$, and use the result given by \autoref{lema:mce} for an axis-parallel ellipse, we can conclude that another solution $Q'$ exists, such that $Q' \succ Q$ and $|\Pp \cap \partial E(q', \theta)| \ge 2$.
 That is, given a solution for the one-facility MCER, we can obtain another one that covers the same points (possibly more) and the ellipse contains two demand points.
@@
 \begin{lem}\label{lema:l-function}
-	Given an instance $(\Pp, \Ww, \{(a, b)\})$ of MCER, if $u, v \in \Pp$ have the same $y$-coordinate and $||u-v||_2 \le 2a$, then $\Phi(u,v) = [0, \alpha] \cup [\pi - \alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
+	Given an instance of the one-facility MCER, if $u, v \in \Pp$ have the same $y$-coordinate and $||u-v||_2 \le 2a$, then $\Phi(u,v) = [0, \alpha] \cup [\pi - \alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
 \end{lem}
@@
 \begin{lem}\label{lema:3pnts}
-	Let $Q^*$ be a solution of MCER for the instance $(\Pp, \Ww, \{(a, b)\})$, such that $|\Pp \cap E(q^*, \theta^*)|\ge2$.
+	Let $Q^*$ be a solution of the one-facility MCER, such that $|\Pp \cap E(q^*, \theta^*)|\ge2$.
 	If for all $\bar{Q} \succ Q^*$, $|\Pp \cap \partial E(\bar{q}, \bar{\theta})| < 3$, then there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that for all $\theta\in \Phi(u,v)$ there exists $q \in \R^2$, such that $(q, \theta)$ is equivalent to $Q^*$.
@@
 \begin{definition}\label{def:Sj}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. Then, for all $j\in\{1, \dots, m\}$, we define the CLS of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
+	Given an instance of MCER. Then, for all $j\in\{1, \dots, m\}$, we define the CLS of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
 	\begin{align*}
@@
 \begin{thm}\label{th:mcer}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega$ be a set of solutions defined as 
+	Given an instance of MCER, let $\Omega$ be a set of solutions defined as 
 	\begin{equation*}\label{eq:omega}

### 2020-03-25 defesa/article/numerical.tex
wip

@@
 In this section, we present the results of our algorithms for MCE-$k$ and MCER-$k$ 
-for some instances proposed by \cite{canbolat, andreta}. 
-We present here the numerical results for the instances CM6-CM9, and AB097-AB120. 
+for the instances with more than $80$ demand points proposed in \cite{canbolat, andreta}. These instances are named CM6-CM9, and AB097-AB120.
+
 For each instance, we display the selected ellipses and the income, which is the weight of every covered point minus the cost of the selected ellipses, of the found optimal solution.
 We also display some performance metrics with the intention of giving an idea of how much computation had to be done for the algorithms to find an optimal solution. These metrics are: 
-the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time spent on constructing the CLSs, and the total CPU time.
+the CLS size of every ellipse, the number of nodes in the backtracking tree, the number of leaves corresponding to a solution in the backtracking tree, the CPU time in seconds spent on constructing the CLSs, and the total CPU time in seconds.
 For the algorithms for MCER, we also have a column for the number of E3P subproblems that were solved, not counting the triplet of points which were skipped.
@@
 
-In \autoref{tab:mce-results-cm}, the results for instances CM7-CM9 are shown for MCE-$k$. 
-The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than one second for every one of the instances CM7-CM9.
+The results of MCE-$k$ are shown in \autoref{tab:mce-results-cm} and  \autoref{tab:mce-results-ab} for instances CM7-CM9 and AB097-AB120 respectively.
+
+The algorithm proposed here showed great results as it was able to obtain optimal solutions in less than one second for every instance.
 Even though the experiments were run in a different environment, we can still say that this is a great improvement compared with the results from \cite{andreta}.
 For example, to obtain an optimal solution for the instance CM9, the method proposed by \cite{andreta} took more than thirty minutes.
-In \autoref{tab:mce-results-ab}, we present the results for instances AB097-AB120.
 We can also observe here, that in practice, the bound for the CLS size of $n^2$ given by \autoref{thm:mce} seems to be very loose.
@@
 An optimal solution was obtained for every instance, and overall, at most six seconds of CPU time was taken.
-
-Looking at the numerical results of the heuristic method proposed in \cite{andreta}, the only non-optimal solutions it encountered were for instances AB105-AB108.
+Looking at the numerical results of the heuristic method proposed in \cite{andreta} for MCER-$k$, the only non-optimal solutions it encountered were for instances AB105-AB108.
 For these instances, our algorithm obtained an optimal solution covering one more point.
-In \autoref{fig:AB108}, the optimal solution for AB108 is displayed.
+In \autoref{fig:AB108-AB120}, the optimal solution for AB108 and AB120 are displayed.
 In general, our algorithm took much lower CPU time compared to the methods developed in \cite{andreta}.
@@
 	\caption{An optimal solution of MCER-$k$ for the instance AB108 (a), and for the instance AB120 (b).}
+	\label{fig:AB108-AB120}
 \end{figure}
@@
 Besides increasing the size of the demand set and the number of ellipses, we also designed instances with non-unitary weights, which is something none of the previous instances had. 
-Moreover, for some instances, we used a different probability distribution, other than the uniform distribution, to generate the location of the points.
-We set a time limit of two hours of CPU time for every instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
-In total, we designed 47 new instances, which will be referred to as TA01, \dots, TA47, we made all of them available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
+Moreover, for some instances, we used a different probability distribution, other than the uniform one, to generate the points.
+We set a time limit of two hours of CPU time for solving each instance, meaning that if an algorithm did not stop in two hours, we report that it was not able to determine an optimal solution. 
+In total, we designed 47 new instances, which will be referred to as TA01, \dots, TA47, and made all of them available at \url{https://sites.icmc.usp.br/andretta/tedeschi-2020/}.
 
@@
 Optimal solutions were obtained for every one of the instances in this set.
-It is possible to see that, compared with the first two sets of instances, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
+It is possible to see that, compared with the first two sets of instances, TA01-TA42, the CLS sizes are smaller, mostly because of the size of the ellipses and the uniform distribution used to generate the points.
 The optimal solution returned by MCER-$k$'s algorithm for the instance TA37 with $n=500$ and $k=5$ is shown in \autoref{fig:TA37}.
@@
 We created seven instances with $n=80$, $m=6$ and $k\in\{1, \dots, m\}$.
-We defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ specifically to create such a counter-example.
-The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mce-results-ta4} for MCER-$k$.
+We defined the values of $\mu^{(1)}$ and $\mu^{(2)}$ as $(-3, -3)$ and $(-3, -3)$ respectively to create such a counter-example.
+The results are shown in \autoref{tab:mce-results-ta4} for MCE-$k$ and in \autoref{tab:mcer-results-ta4} for MCER-$k$.
 In \autoref{fig:TA44-45}, we show the solutions for the instances TA44-TA45 with $k=2$, where two of the bigger-sized ellipses are used, and $k=3$, where one of the bigger-sized ellipses is replaced by two small ones.
@@
 		}
-		\caption{Numerical Results of MCE-$k$ for instances CM7-CM9.}
+		\caption{Numerical results of MCE-$k$ for instances CM7-CM9.}
 		\label{tab:mce-results-cm}
+	\end{center}
+\end{table}
+%%% TABLE AB
+\begin{table}
+	\begin{center}
+		\resizebox{0.85\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|crrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
+				\hline
+				\input{tables/table_mcek_ab.tex}
+				\hline
+
+			\end{tabular}
+		}
+		\caption{Numerical results of MCE-$k$ for instances AB097-AB120.}
+		\label{tab:mce-results-ab}
 	\end{center}
@@
 		}
-		\caption{Numerical Results of MCER-$k$ for instances CM7-CM9.}
+		\caption{Numerical results of MCER-$k$ for instances CM7-CM9.}
 		\label{tab:mcer-results-cm}
@@
 %%% FIM TABLE CM
-
-%%% TABLE AB
-\begin{table}
-	\begin{center}
-		\resizebox{0.85\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|crrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol. leaves & CLS-MCE & Total\\
-				\hline
-				\input{tables/table_mcek_ab.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Numerical Results of MCE-$k$ for instances AB097-AB120.}
-		\label{tab:mce-results-ab}
-	\end{center}
-\end{table}
 
@@
 		}
-		\caption{Numerical Results of MCER-$k$ for instances AB097-AB120.}
+		\caption{Numerical results of MCER-$k$ for instances AB097-AB120.}
 		\label{tab:mcer-results-ab}
@@
 		}
-		\caption{Numerical Results of MCE-$k$ for instances TA001-TA007.}
+		\caption{Numerical results of MCE-$k$ for instances TA001-TA007.}
 		\label{tab:mce-results-ta1}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|ccrrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\# E3P&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \# sol leaves & CLS-MCER & Total\\
-
-				%%%%
-				%%%%
-
-				\hline
-				\input{tables/table_mcerk_ta_1.tex}
-				\hline
-
-			\end{tabular}
-		}
-		\caption{Numerical Results of MCER-$k$ for instances TA001-TA007.}
-		\label{tab:mcer-results-ta1}
 	\end{center}
@@
 		}
-		\caption{Numerical Results of MCE-$k$ for instances TA008-TA022.}
+		\caption{Numerical results of MCE-$k$ for instances TA008-TA022.}
 
 		\label{tab:mce-results-ta2}
-	\end{center}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\resizebox{\textwidth}{!}{%
-
-			\begin{tabular}{|cccc|cr|ccrrrr|}
-				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
-				\hline
-
-				%%% Second line of header
-
-				\multirow{2}{*}{Name} & 
-				\multirow{2}{*}{$n$} & 
-				\multirow{2}{*}{$m$} & 
-				\multirow{2}{*}{$k$} & 
-				Selected & 
-				\multirow{2}{*}{Income} & 
-				CLS size&
-				\# E3P&
-				\multicolumn{2}{c}{Backtracking Tree} & 
-				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \# sol leaves & CLS-MCER & Total\\
-
-				%%%%
-				%%%%
-
-				\hline
-				\input{tables/table_mcerk_ta_2.tex}
-				\hline
-				%\input{tex/tables/table_mcerk_ta_3.tex}
-				%\hline
-
-			\end{tabular}
-		}
-		\caption{Numerical Results of MCER-$k$ for instances TA008-TA022.}
-
-		\label{tab:mcer-results-ta2}
 	\end{center}
@@
 		}
-		\caption{Numerical Results of MCE-$k$ for instances TA023-TA042.}
+		\caption{Numerical results of MCE-$k$ for instances TA023-TA042.}
 		\label{tab:mce-results-ta3}
+	\end{center}
+\end{table}
+
+\begin{table}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|crrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol leaves & CLS-MCER & Total\\
+
+				\hline
+				\input{tables/table_mcek_ta_5.tex}
+				\hline
+				%\input{tex/tables/table_mcerk_ta_3.tex}
+				%\hline
+
+			\end{tabular}
+		}
+		\caption{Numerical results of MCE-$k$ for instances TA043-TA047.}
+
+		\label{tab:mce-results-ta4}
 	\end{center}
@@
 
-				%%%%
-				%%%%
-
 				\hline
-				\input{tables/table_mcerk_ta_4.tex}
+				\input{tables/table_mcerk_ta_1.tex}
 				\hline
-				%\input{tex/tables/table_mcerk_ta_3.tex}
-				%\hline
 
@@
 		}
-		\caption{Numerical Results of MCER-$k$ for instances TA023-TA042.}
-		\label{tab:mcer-results-ta3}
+		\caption{Numerical results of MCER-$k$ for instances TA001-TA007.}
+		\label{tab:mcer-results-ta1}
 	\end{center}
@@
 
-			\begin{tabular}{|cccc|cr|crrrr|}
+			\begin{tabular}{|cccc|cr|ccrrrr|}
 				\hline
-				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{5}{c|}{Performance metrics}\\
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
 				\hline
@@
 				CLS size&
+				\# E3P&
 				\multicolumn{2}{c}{Backtracking Tree} & 
 				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
-				& & & & \centering Ellipses & & $|S_k|$ & \# nodes & \# sol leaves & CLS-MCER & Total\\
-
-				%%%%
-				%%%%
-
-				%%%%
-				%%%%
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \# sol leaves & CLS-MCER & Total\\
 
 				\hline
-				\input{tables/table_mcek_ta_5.tex}
+				\input{tables/table_mcerk_ta_2.tex}
 				\hline
@@
 		}
-		\caption{Numerical Results of MCE-$k$ for instances TA043-TA047.}
+		\caption{Numerical results of MCER-$k$ for instances TA008-TA022.}
 
-		\label{tab:mce-results-ta4}
+		\label{tab:mcer-results-ta2}
+	\end{center}
+\end{table}
+
+\begin{table}
+	\begin{center}
+		\resizebox{\textwidth}{!}{%
+
+			\begin{tabular}{|cccc|cr|ccrrrr|}
+				\hline
+				\multicolumn{4}{|c|}{Instance} & \multicolumn{2}{c|}{Optimal Solution} & \multicolumn{6}{c|}{Performance metrics}\\
+				\hline
+
+				%%% Second line of header
+
+				\multirow{2}{*}{Name} & 
+				\multirow{2}{*}{$n$} & 
+				\multirow{2}{*}{$m$} & 
+				\multirow{2}{*}{$k$} & 
+				Selected & 
+				\multirow{2}{*}{Income} & 
+				CLS size&
+				\# E3P&
+				\multicolumn{2}{c}{Backtracking Tree} & 
+				\multicolumn{2}{c|}{\centering CPU Time (s)}\\
+				& & & & \centering Ellipses & & $|S_k|$ & subproblems & \# nodes & \# sol leaves & CLS-MCER & Total\\
+
+				\hline
+				\input{tables/table_mcerk_ta_4.tex}
+				\hline
+				%\input{tex/tables/table_mcerk_ta_3.tex}
+				%\hline
+
+			\end{tabular}
+		}
+		\caption{Numerical results of MCER-$k$ for instances TA023-TA042.}
+		\label{tab:mcer-results-ta3}
 	\end{center}
@@
 				\hline
-				%\input{tex/tables/table_mcerk_ta_3.tex}
-				%\hline
 
@@
 		}
-		\caption{Numerical Results of MCE-$k$ for instances TA043-TA047.}
-
+		\caption{Numerical results of MCER-$k$ for instances TA043-TA047.}
 		\label{tab:mcer-results-ta4}

### 2020-03-26 defesa/article/definition.tex
dissertacao depositada

@@
 
-We define an instance of the one-facility MCE or MCER as $(\Pp, \Ww, \{(a,b)\})$ omitting the facility index in every notation. For example, a solution of MCER is denoted as $Q := (q, \theta)$.
+In some cases, it will be more convenient to work with the one-facility version of MCE or MCER.
+When that is the case, we use an adapted notation removing all the unnecessary indexes, sequences and sets used to specify multiple facilities.
+For example, a solution of the one-facility MCER is denoted by $Q:=(q,\theta)$.
 

### 2020-03-26 defesa/tex/chapter/definicoes.tex
wip
dissertacao depositada

@@
 A circle (or circumference) is a set of points in $\R^2$ that have the same Euclidean distance, also known as radius, to another point, also referred to as the center of the circle.
-A unit circle is a circle with radius equal to $1$.
+A unit circle is a circle with radius equal to one.
 
@@
 Suppose that this line intersects the ellipse at least at one point.
-Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points.
-The final expression is given by
-\begin{equation*}\label{eq:dist_line_ellipse}
-D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
+Plugging the line's equation into \autoref{equation:pellipse}, we get
+\begin{align}
+\frac{x^2}{a^2}+\frac{(mx + c)^2}{b^2} -1 &= 0 \nonumber\\
+x^2\left(\frac{1}{a^2} + \frac{m^2}{b^2}\right) + \frac{2mxc}{b^2} + \frac{c^2}{b^2} - 1 &= 0\nonumber.
+\end{align}
+Let $(x_1, y_1)$, and $(x_2, y_2)$ be the ellipse-line intersection points. Then, we have that
+\begin{align}
+(x_1-x_2)^2 &= \frac{\frac{4m^2c^2}{b^4} - 4\left(\frac{1}{a^2} + \frac{m^2}{b^2}\right)\left(\frac{c^2}{b^2}-1\right)}{\left(\frac{1}{a^2} + \frac{m^2}{b^2}\right)^2}\nonumber\\
+(x_1-x_2)^2 &= \frac{4m^2c^2a^4}{(b^2+a^2m^2)^2} - \frac{4(c^2-b^2)a^2}{b^2+a^2m^2}\nonumber\\
+(x_1-x_2)^2 &= 4\frac{m^2c^2a^4 - (b^2+a^2m^2)(c^2-b^2)a^2}{(b^2+a^2m^2)^2}\nonumber\\
+(x_1-x_2)^2 &= 4\frac{a^2b^2(a^2m^2 + b^2 -c^2)}{(b^2+a^2m^2)^2}\nonumber.
+\end{align}
+Then, as $(y_1-y_2)^2 = (mx_1 - mx_2)^2 = m^2(x_1-x_2)^2$, we get the final expression for the distance between two ellipse-line intersection points
+\begin{equation*}
+\sqrt{(x_1-x_2)^2+(y_1-y_2)^2}=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)}.
 \end{equation*}
-with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$.
-It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$.
-From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$.
-Following that, we define a function $L:\R\mapsto\R_{>0}$ as
 
-\begin{equation}\label{eq:function-l}
-L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
-\end{equation}
-which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.
+%\begin{figure}[H]
+%	\centering
 
-It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
-Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
-In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.
-
-\begin{figure}[H]
-	\centering
-
-	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
-	\includegraphics[scale=.4]{tex/figures/L-function-plot}
-	\fautor
-	\label{fig:L-function-plot}
-\end{figure}
+%	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
+%	\includegraphics[scale=.4]{tex/figures/L-function-plot}
+%	\fautor
+%	\label{fig:L-function-plot}
+%\end{figure}
 
@@
 \begin{equation}\label{eq:rotated_ellipse}
-\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
+\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}-1=0.
 \end{equation}

### 2020-03-26 defesa/tex/chapter/mcd2.tex
dissertacao depositada

@@
 
-Let $(\Pp, \Ww, \{||\cdot||\})$ be an instance of MCSCD with only one facility, and $(\Pp, \Ww, ||\cdot||)$ an instance of MWC.
+Let $(\Pp, \Ww, ||\cdot||)$ be an instance of MCSCD with only one facility, and $(\Pp, \Ww, ||\cdot||)$ an instance of MWC.
 If $q_1$ be a solution for the MCSCD's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have a non-empty intersection.
-Also, suppose that $q$ is a solution of MWC. Then, the ellipse with shape parameters $(a, b)$ centered at $q$ covers the points, which are the centers of disks, such that $q \in D_j$.
+Also, suppose that $q$ is a solution of MWC. 
+Then, the $D(q)$ covers the points, which are the centers of disks, such that $q \in D_j$.
 Therefore, MCSCD and MWC for both problems are equivalent.

### 2020-03-26 defesa/tex/chapter/mcer.tex
wip
dissertacao depositada

@@
 
-Given an instance of $MCER$, we define $Q:=(q_1, \dots, q_m) \in \R^{2m}$ as the centers of each ellipse, and $\Theta:=(\theta_1, \dots, \theta_m) \in [0, \pi)^m$ as the angles of rotation of each ellipse.
-Then, we define MCER as the problem of determining $Q$ and $\Theta$ (placing and rotating each ellipse) to maximize the weight of the points covered by the $m$ ellipses given by
+Given an instance of $MCER$, we define $Q:=((q_1,\theta_1); \dots; (q_m, \theta_m)) \in (\R^{2}\times[0, \pi))^m$, $(q_j, \theta_j)$ being $j$-th ellipse's the center and the angle of rotation.
+Then, we define MCER as the problem of determining $Q$ (placing and rotating each ellipse) to maximize the weight of the points covered by the $m$ ellipses given by
 \begin{equation}\label{eq:optMCEn}
-\max_{Q, \Theta}{w\left(\bigcup_{i=1}^{m} \Pp \cap E_i(q_i, \theta_i)\right)}.
+\max_{Q}{w\left(\bigcup_{i=1}^{m} \Pp \cap E_i(q_i, \theta_i)\right)}.
 \end{equation}
@@
 We say that two solutions are equivalent if the set of points covered by them is the same.
-That is, two solutions of MCER $(Q, \Theta)$ and $(Q', \Theta')$ are said to be equivalent if, and only if
+That is, two solutions of MCER $Q$ and $Q'$ are said to be equivalent if, and only if
 $$\bigcup_{j=1}^m\Pp \cap E_j(q_j', \theta_j') = \bigcup_{j=1}^m\Pp \cap E_j(q_j, \theta_j).$$
+
+We also define a partial order relation between two solutions. Let $Q$ and $Q'$ be two solutions of MCER, then $Q \succ Q'$ if, and only if
+
+$$\bigcup_{j=1}^m\Pp \cap E_j(q_j', \theta_j') \subset \bigcup_{j=1}^m\Pp \cap E_j(q_j, \theta_j).$$
+
+In some cases, it will be more convenient to work with the one-facility version of MCER.
+When that is the case, we use an adapted notation removing all the unnecessary indexes, sequences and sets used to specify multiple facilities.
+For example, a solution of the one-facility MCER is defined as $Q := (q, \theta)$.
 
@@
 \begin{lema}\label{lema:mce_2b}
-	Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. 
-	Then, for any $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, 
-	an equivalent solution $(Q', \Theta^*)$ exists, such that $|\Pp \cap \partial E_j(q_j', \theta_j^*)|\ge 2$.
+	Let $Q$ be a solution for the one-facility MCER, such that $|\Pp \cap E(q, \theta)| \ge 2$.
+	There exists a solution $Q'$, such that $Q' \succ Q$ and $|\Pp \cap \partial E(q', \theta')|\ge 2$.
 \end{lema}
@@
 \begin{proof}
-	First, the angle of rotation can be ignored as it does not change.
-
-	Let $A=\Pp \cap E_j(q_j^*, \theta_j)$ be the set of points covered by the $j$-th ellipse and $X=\cap_{p \in A}E_j(p, \theta_j)$ be the region of intersection of ellipses centered at each point in $A$.
+	If we rotate the coordinate system by $-\theta$, we get a solution where the ellipse is axis-parallel.
 
@@
 As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point, creating a vertex.
-Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
+Selecting any of these vertices as $q'$ and $\theta'=\theta$ will make $|\Pp \cap \partial E(q', \theta')| \ge 2$.
 
@@
 
-Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.
+%Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.
 
-\begin{definicao}
-	Let $(Q^*, \Theta^*)$ be an optimal solution for an instance $(\Pp, \Ww, \Rr)$ of MCER.
+%\begin{definicao}
+%	Let $(Q^*, \Theta^*)$ be an optimal solution for an instance $(\Pp, \Ww, \Rr)$ of MCER.
 We define $\Pi(Q^*, \Theta^*)$ as the set of every equivalent solution of $(Q^*, \Theta^*)$, such that for any $(Q, \Theta)\in\Pi(Q^*, \Theta^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.
-\end{definicao}
+%\end{definicao}
 
@@
 An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
-	In addition to that, given an instance  $(\Pp, \Ww, \Rr)$ of MCER, the set of $(E_j, u, v)$-feasible angles is referred to as
+	In addition to that, the set of $(E, u, v)$-feasible angles is referred to as
 
 	\begin{equation}
-	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
+	\Phi(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
 	\end{equation}
-	We also define $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
-Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
 \end{definicao}
+
+For any $x\in\R^2$, we denote by $\angle x\in [0, \pi)$ the minimal angle between $x$ and the vector $(1, 0)$.
+If $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as $\angle(u-v)$ is the angle that makes the ellipse's major-axis, the longest segment crossing an ellipse, be parallel to the line that passes through $u$ and $v$.
 
@@
 
+Next we open a parenthesis to discuss the problem of deciding for what angles of rotation it is possible to find a center for an ellipse, so it contains two given points.
+We give the result for two points that have the same $y$-coordinate, but this can be generalized.
+
+\begin{lema}\label{lema:l-function}
+	Given an instance of the one-facility MCER, if $u, v \in \Pp$ have the same $y$-coordinate and $||u-v||_2 \le 2a$, then $\Phi(u,v) = [0, \alpha] \cup [\pi - \alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
+\end{lema}
+
+\begin{proof}
+
+	In \autoref{chapter:definitions}, we determined the following formula for the distance between the intersection points of an axis-parallel ellipse centered at the origin, with shape parameters $(a,b)$, and a line represented by the equation $y=mx+c$, with $m, c\in \R$:
+
+	\begin{equation*}\label{eq:dist_line_ellipse}
+	D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
+	\end{equation*}
+	with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$.
+	If $D(m, c) = ||u-v||_2$, then there exists $q_1, q_2 \in \R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$ and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
+It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$.
+	Following that, we define a function $L:\R\mapsto\R$ as
+
+	\begin{equation*}
+	L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
+	\end{equation*}
+	which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient. 
+	An example of that function is shown in \autoref{fig:L-function-plot}.	
+	From that, if $L(m) \ge ||v-u||_2^2$, then there exists $q_1, q_2\in\R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$, and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
+
+	It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
+Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
+	%In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.
+
+	If $\inf{L} \ge ||u-v||_2^2$, then $\Phi(u,v) = [0, \pi)$.
+	Otherwise, let $\beta \in \R$, $\beta \ge 0$, such that $L(\beta) = ||u-v||_2^2$, then as $m>\beta$, we have $L(m) < ||u-v||_2^2$, which means that it is impossible to make the ellipse contain $u$, and $v$.
+	As $L$ is an even function, the same can be said for $m < \beta$. Therefore, we conclude that $\Phi(u,v)=[0, \tan(\beta)] \cup [\pi-\tan(\beta), \pi)$.
+\end{proof}
+
+\begin{figure}[H]
+	\centering
+
+	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
+	\includegraphics[scale=.4]{tex/figures/L-function-plot}
+	\fautor
+	\label{fig:L-function-plot}
+\end{figure}
+
 Following that, we introduce a lemma that is responsible for connecting the developments of this chapter with the results of \autoref{chapter:e3p}.
@@
 \begin{lema}\label{lema:3pnts}
-Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; \\$j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.\\
-If, for all $(\hat{Q}, \hat{\theta})$ equivalent solution of $(Q^*, \Theta^*)$, $|\Pp\cap \partial E_j(\hat{q}_j, \hat{\theta}_j)| < 3$, then for all $\theta\in\Phi_j(u,v)$, there exists $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.
+Let $Q^*$ be a solution of the one-facility MCER, such that $|\Pp \cap E(q^*, \theta^*)|\ge2$.
+If for all $\bar{Q} \succ Q^*$, $|\Pp \cap \partial E(\bar{q}, \bar{\theta})| < 3$, then there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that for all $\theta\in \Phi(u,v)$ there exists $q \in \R^2$, such that $(q, \theta)$ is equivalent to $Q^*$.
 
@@
 \begin{proof}
-	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E_j(q^*_j, \theta^*_j)$, such that an equivalent optimal solution $(Q', \Theta')$ exists with $u$ and $v$ on the border of $E_j(q_j', \theta_j^*)$.
-Therefore, $\theta_j^*\in\Phi_j(u,v)$.
+	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that $Q' \succ Q^*$ exists, and $\{u, v\} \subset \partial E(q', \theta^*)$.
+Therefore, $\theta^*\in\Phi(u,v)$.
 
-	Now suppose that $u$ and $v$ have the same $y$-coordinate, that is, the angle between them is $0$.
-If they do not, a rotation can be applied to make them have the same $y$-coordinate.
-Then, the first thing we are proving is that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that any instance can be transformed into using translation and rotation on every element of $\Pp$.
-
-	In \autoref{chapter:definitions}, a function $L\colon \R \to \R_{\ge0}$ was defined in \autoref{eq:function-l}.
-This function takes the angular coefficient $m\in\R$ and, considering the family of lines parallel to the one described by $y=mx$, returns the maximum squared distance between two intersection points of a line in that family and an axis-parallel ellipse centered at the origin.
-
-	To use those results here, we need to consider the ellipse to be fixed at the origin and axis-parallel, and consider the problem of rotating and translating the points in $\Pp$ instead.
-
-	Let $\theta \in [0, \pi]\setminus\{\pi/2\}$, and $u', v'$ be the points $u, v$ after a rotation by $\theta$.
-Then, if $L(\tan{\theta}) \ge ||v-u||_2^2$, it is possible to apply a translation to $u',v'$, such that they end up on the fixed ellipse.
-This means that it is possible to find an angle of rotation and a center to place $E_j$, such that it has $u, v$ on its border.
-
-	Now we use some properties of function $L$ whose details are given in \autoref{chapter:definitions}.
-	Defining $l(\theta)=L(\tan{\theta})$, with $l:[0, \pi]\setminus\{\pi/2\}$, we can say that
-
-	\begin{itemize}
-		\item $l$ is decreasing in $[0, \pi/2)$ because $L$ is decreasing in $[0, \infty)$.
-Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\alpha, \pi/2)$.
-That implies $[0, \alpha] \subset \Phi_j(u,v)$.
-		\item $l(\theta) = l(\pi-\theta)$ because $L$ is an even function.
-Therefore, if there is $\alpha\in[0, \pi/2)$, such that $l(\alpha) = ||v-u||_2^2$, then $l(\theta)>||v-u||_2^2$, for $\theta\in(\pi/2,\pi-\alpha)$.
-That implies $[\pi-\alpha, \pi] \subset \Phi_j(u,v)$.
-	\end{itemize}
-	We then conclude that $\Phi_j(u, v) = [0, \alpha]\cup [\pi-\alpha, \pi]$, and, of course, in the case that there is no $\alpha\in[0, \pi/2)$, such that $l(\alpha)=||v-u||_2^2$, we have $\Phi_j(u,v)=[0, \pi]$.
-	From that, if we rotate every point in $\Pp$ by $\pi-\alpha$, we obtain $\Phi_j(u,v)=[0, 2\alpha]$.
+	Suppose that $u$ and $v$ have the same $y$-coordinate (if they do not, a rotation can be applied to make them do).
+Then, by \autoref{lema:l-function}, $\Phi(u,v)=[0, \alpha] \cup [\pi-\alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
+Then, if we rotate the coordinate system by $\pi-\alpha$, we obtain $\Phi(u,v)=[0, 2\alpha]$.
 
 	With this result in hand, we can use a continuity argument to complete our proof as follows.
-	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
-Notice that, in general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, imposing $\delta(\theta_j') = q_j'$ makes $\delta$ be a well-defined function.
-This is shown in \autoref{fig:lema-3-points} where $\delta$ is plotted for the whole interval $\Phi_j(u,v)$.
+	Let $\delta : \Phi(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E(\delta(\theta), \theta)$, and, from solution $Q'$, $\delta(\theta') = q'$.
+Notice that, in general, for any angle in $\Phi(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, imposing $\delta(\theta') = q'$ makes $\delta$ be a well-defined continuous function.
+This is shown in \autoref{fig:lema-3-points} where $\delta$ is plotted for the whole interval $\Phi(u,v)$.
 
-	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-hand-side of \autoref{eq:rotated_ellipse}.
-Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$ as they are covered by the $j$-th ellipse.
+	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes an angle of rotation $\theta$ and returns the elliptical distance $||\cdot||_{a,b,\theta}$ to the center $\delta(\theta)$; that is $f_w(\theta)=||w-\delta(\theta)||_{a,b,\theta}$.
+	We have that if $w \in \Pp \cap E(q^*, \theta^*)$, then $f_w(\theta^*) \le 1$; and if $w \not\in \Pp \cap E(q^*, \theta^*)$, then $f_w(\theta^*) > 1$.
 
-	Then, to evaluate $f_w$ for every center and feasible angle that maintains $u$ and $v$ on $E_j$'s border, we introduce a new function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$, which is defined as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
-	As $f_w$ and $\delta$ are both continuous functions, $g_w$ is also continuous.
-
-	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>0$.
-Then, by continuity, another angle $\bar{\theta} \in \Phi_j(u,v)$ must exist, such that $g_w(\bar{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis.
-The same can be said about the case where there exists an angle $\theta \in \Phi_j(u,v)$, such that a point $w \in \Pp \setminus E_j(q_j^*, \theta_j^*)$ enters the coverage of $E_j(\delta(\theta), \theta)$.
+	Therefore, if there exists $\theta\in\Phi(u,v)$, such that for all $q\in\R^2$, $(q, \theta)$ is not equivalent to $Q^*$, then there exists either $w \in \Pp \cap E(q^*, \theta^*)$, with $f_w(\theta)>1$, or $w \not\in \Pp \cap E(q^*, \theta^*)$, with $f_w(\theta)\le 1$.
+Because $f_w$ is continuous, there exists $\bar{\theta}\in\Phi(u,v)$, such that $f_w(\theta)=1$, implying that $|\Pp \cap \partial E(\delta(\bar{\theta}), \bar{\theta})| \ge 3$.
 \end{proof}
@@
 
-Let $(Q^*, \Theta^*)$ be any optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
-We will define a set of solutions $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$.
-This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ for sure contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
-Before that, we introduce a definition for the CLS of every ellipse, which is then used to construct the set of solutions $\Omega(\Pp, \Ww, \Rr)$.
+Let $Q^*$ be any optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER.
+We will define a set of solutions $\Omega$ and show that there exists an equivalent solution $Q'$ to  $Q^*$, such that $Q' \in \Omega$.
+This is the same thing as showing that $\Omega$ for sure contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
+Before that, we introduce a definition for the CLS of every ellipse, which is then used to construct the set of solutions $\Omega$.
 
 \begin{definicao}\label{def:Sj}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER.
-Then, for all $j\in\{1, \dots, m\}$, we define the \sigla{CLS}{Candidate Locations Set} of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
-	\begin{align}
+	Given an instance of MCER. Then, for all $j\in\{1, \dots, m\}$, we define the CLS of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
+\begin{align*}
 S_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
-		S_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \tilde{\Phi}_j(u,v))\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \tilde{\Phi}_j(u,v))\}\\
-		S_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v, w\} \subset \partial E_j(q, \theta)\}.
-	\end{align}
+S_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \angle(u-v))\in \R^2\times[0, \pi): \{u,v\} \subset \partial E_j(q, \angle(u-v))\}\\
+S_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times[0, \pi): \{u, v, w\} \subset \partial E_j(q, \theta)\}.
+\end{align*}
 \end{definicao}
 
-This definition breaks the construction of the CLS $S_j$ into three separated cases.
+This definition breaks the construction of the CLS into three separated cases.
 The first one, $S_j^{(1)}$, represents solutions where the $j$-th ellipse covers only one point.
@@
 The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse.
-Following this, we move forward and introduce the main result of this section.
+
+To compute $S_j^{(2)}$, we can observe that, given two points $u, v$, determining every $q\in\R^2$, such that $\{u,v\}\subset\partial E_j(q, \angle(u-v))$ can be transformed into the problem of determining the set $\partial E_j(u, \angle(u-v)) \cap \partial E_j(v, \angle(u-v))$, which, by \autoref{lema:mce_2b}, is composed of at most two points, which can be determined analytically.
+Therefore, we have that $S_j^{(2)}$ can be computed in $\bigO(n^2)$ operations.
+
+To compute $S_j^{(3)}$, we have to call \autoref{algoritmo:e3p}, which by \autoref{th:e3p} is $\bigO(1)$.
+
+Overall, constructing every ellipse's CLS can be implemented to have a $\bigO(n^3)$ runtime complexity.
+Following this, we introduce a theorem, which connects the results for MCER so far, to prove that the set of solutions constructed using the CLSs described by \autoref{def:Sj} contains an optimal solution.
 
 \begin{theorem}\label{th:mcer}
-	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined as 
+	Given an instance of MCER, let $\Omega$ be a set of solutions defined as 
 \begin{equation*}\label{eq:omega}
-	\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
+\Omega = \{Q \in (\R^2\times[0, \pi))^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
 \end{equation*}
-Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|\le n^{3m}$.
+Then there exists an optimal solution $Q^* \in \Omega$, and $|\Omega|\le n^{3m}$.
 \end{theorem}
 \begin{proof}
-	The first thing to notice is that $\Omega(\Pp, \Ww, \Rr)$ is defined as the combination of every possible solution from each CLS.
-To prove that it contains an optimal solution $(Q^*, \Theta^*)$, we only need to prove that for all $j\in\{1, \dots, m\}$, there exists $(q_j, \theta_j)\in S_j$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) \subset \Pp \cap E_j(q_j, \theta_j)$.
-That is, we only need to show that the CLS of every ellipse contains a center and angle of rotation that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution.
+		The first thing to notice is that $\Omega$ is defined as the combination of every possible solution from each CLS.
+To prove that it contains an optimal solution $Q^*$, we only need to prove that for all $j\in\{1, \dots, m\}$, there exists $(q_j, \theta_j)\in S_j$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) \subset \Pp \cap E_j(q_j, \theta_j)$.
 To do that, we use \autoref{lema:3pnts} and break the possible optimal solutions into three cases.
@@
 	In the first case, we consider solutions where the $j$-th ellipse covers less than one point, that is, $|\Pp \cap E_j(q_j^*, \theta_j^*)|\le1$.
-It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega(\Pp, \Ww, \Rr)$ every solution that has an ellipse centered at a point from $\Pp$.
+It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega$ every solution that has an ellipse centered at a point from $\Pp$.
 From that, we can also conclude that $|S_j^{(1)}| \le n$.
 
-	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on it.
-This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
-	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
-	Moreover, in Section~\ref{section:ellipses_intersection2}, we discuss the problem of determining the intersections between two ellipses.
-This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points.
-In \autoref{section:ellipses_intersection}, it is shown that this problem has at most two solutions.
-Therefore, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
+	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and there is no $Q' \succ Q^*$, such that $|\Pp \cap \partial E_j(q_j', \theta_j')| \ge 3$.
+	This case is addressed by \autoref{lema:3pnts}, which states that there are equivalent solutions to $Q^*$ with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the $j$-th ellipse for every $(E_j, u, v)$-feasible angle.
+	As $\angle(u-v)$ is a $(E_j, u, v)$-feasible angle, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j, \theta_j) = \Pp \cap E_j(q_j^*, \theta_j^*)$.
+	Also, by \autoref{lema:mce_2b}, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
+
+	%	Moreover, as determining every $q\in\R^2$, such that $\{u,v\}\subset \partial E_j(q, \angle(u-v))$ can be transformed into the problem of determining the set $\partial E_j(u, \angle(u-v)) \cap \partial E_j(v, \angle(u-v))$, which, as discussed in \autoref{section:mce}, contains at most two points, we can conclude that $|S_j^{(2)}| \le 2 \binom{n}{2}$.
 
 	For the last case, we are left with solutions where the $j$-th ellipse covers more than two points, and there exists an equivalent solution with three points on it. 
-	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega(\Pp, \Ww, \Rr)$.
-Also, in \autoref{lema:3pnts} it is stated that the number of centers and angles of rotation that make an ellipse contain three given points is at most six.
-Therefore, we have that $|S_j^{(3)}| \le 6\binom{n}{3}$.
+	As $S_j^{(3)}$ contains every center and angle of rotation that puts three points on the $j$-th ellipse, an equivalent solution for this case is present in the set of solutions $\Omega$.
+Also, by \autoref{lema:e3p} we can conclude that $|S_j^{(3)}| \le 6\binom{n}{3}$.
 
-	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound for its size:
+	Combining the three cases, as $S_j=S_j^{(1)}\cup S_j^{(2)} \cup S_j^{(3)}$, we get the following bound for $|S_j|$:
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}	
-	Therefore, we conclude that  $|\Omega(\Pp, \Ww, \Rr)| \le |S_1|\times \dots \times |S_m| \le n^{3m}$.
+	Therefore, we conclude that  $|\Omega| \le |S_1|\times \dots \times |S_m| \le n^{3m}$.
 \end{proof}
@@
 Let $E$ be the coverage region of an ellipse with shape parameters $(a, b)$.
-We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \tilde{\Phi}_j(u,v)) \in \R^2\times[0, \pi)$, such that, $\{u, v\}\subset \partial E(q, \tilde{\Phi}_j(u,v))$.
-That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse.
+We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \angle(u-v) \in \R^2\times[0, \pi)$, such that, $\{u, v\}\subset \partial E(q, \angle(u-v))$.
+That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\angle(u-v)$, and the points $u$, $v$ are on the ellipse.
 This can be done using the results of Section~\ref{section:ellipses_intersection2}.
@@
 	For every $j\in\{1, \dots, m\}$, unless $Z=\{\}$, when choosing the center and angle of rotation for the $j$-th ellipse, \autoref{algoritmo:mcer} does not consider any $(q_j, \theta_j) \in \R^2 \times \R$, such that $Z \cap E_j(q_j, \theta_j) = \{\}$.
-Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
+Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega$.
 As evaluating each solution can be done in $\bigO(nm)$, we get the overall runtime complexity of $\bigO(mn^{3m+1})$.
@@
 
-Then, in the same way that it is done in \autoref{chapter:mce}, we introduce \autoref{algoritmo:mcer-k} for MCER-$k$ that uses \autoref{algoritmo:mcer} for every $I:=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$.
+Then, in the same way that it is done in \autoref{chapter:mcd2}, we introduce \autoref{algoritmo:mcer-k} for MCER-$k$ that uses \autoref{algoritmo:mcer} for every $I:=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$.
 Therefore, \autoref{algoritmo:mcer-k} returns an optimal solution for MCER-$k$ in $\bigO(k\binom{m}{k}n^{3k+1}) = \bigO(m2^mn^{3m+1})$ time.

### 2020-03-28 defesa/article/article.tex
wip

@@
 
-		\author[1]{Danilo Tedeschi}
+		\author[add1]{Danilo Tedeschi}
 		\ead{danilo.tedeschi@usp.br}
 
-		\author[2]{Marina Andretta}
-		\ead{andretta@gmail.com}
+		\author[add1]{Marina Andretta}
+		\ead{andretta@icmc.usp.br}
 
-		\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
-		%\author{John Smith}
+		\address[add1]{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
+\end{frontmatter}
+\clearpage
+%\begin{frontmatter}
+%		\begin{abstract}
 
-		%address{California, United States}
-
-		\begin{abstract}
+\section*{Abstract}
 			%% Text of abstract
@@
 			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances 	with up to seven hundred demand points and five ellipses.
-		\end{abstract}
-
-		\begin{keyword}
-			Combinatorial optimization \sep planar maximal covering location problem \sep planar covering by ellipses \sep exact algorithms.
+\subsection*{Keywords}
+			Combinatorial optimization, planar maximal covering location problem, planar covering by ellipses, exact algorithms.
 			%% keywords here, in the form: keyword \sep keyword
@@
 
-		\end{keyword}
+%		\end{keyword}
 
-	\end{frontmatter}
+%	\end{frontmatter}
 
@@
 	%% New version of the num-names style
-	\bibliographystyle{elsarticle-num}
+	\bibliographystyle{apa}
 	\bibliography{../references}

### 2020-03-28 defesa/article/e3p.tex
wip

@@
 In this section, we describe an experiment we made to choose a precision constant for comparing if a root of $f$ returned as an eigenvalue of its companion matrix is in the unit circle.
-The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of $f$ (more information about the implementation is given in \autoref{section:implementation}).
+The implementation was coded in C++, and LAPACK's ZGEEV was utilized to obtain the eigenvalues of the companion matrix of $f$ (more information about the implementation is given in Section~\ref{section:implementation}).
 For the experiment, we defined $K\in\R$, $K>0$, and considered instances with the ellipse's shape parameters $(K, \frac{K}{2})$, for $K\in\{10^j\colon j=0,\dots,10\}$.

### 2020-03-28 defesa/article/mce.tex
wip

@@
 As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has $\bigO(mn^{2m+1})$ runtime complexity.
-In \autoref{section:improvements}, we give some suggestions of improvements that can be applied to the implementation of \autoref{algoritmo:mce}, and in \autoref{section:numerical}, we analyze the results obtained by \autoref{algoritmo:mce} for some numerical experiments.
+In Section~\ref{section:improvements}, we give some suggestions of improvements that can be applied to the implementation of \autoref{algoritmo:mce}, and in Section~\ref{section:numerical}, we analyze the results obtained by Section~\ref{algoritmo:mce} for some numerical experiments.
 

### 2020-03-28 defesa/article/mcer.tex
wip

@@
 
-Following that, we introduce a lemma that is responsible for connecting the developments of this chapter with the results of \autoref{section:e3p}.
+Following that, we introduce a lemma that is responsible for connecting the developments of this chapter with the results of Section~\ref{section:e3p}.
 This lemma makes it possible to describe a type of solution which, for sure, is part of the equivalence class of any optimal solution.
@@
 
-To compute $S_j^{(3)}$, we have to call the algorithm described in \autoref{section:e3p} to determine every solution of E3P for every triplet of points in $\Pp$.
+To compute $S_j^{(3)}$, we have to call the algorithm described in Section~\ref{section:e3p} to determine every solution of E3P for every triplet of points in $\Pp$.
 Even though that algorithm is $\bigO(1)$, it has a high constant factor, thus skipping it, in practice, is a good suggestion.

### 2020-03-30 defesa/article/mce.tex
wip

--- 2020-03-25 defesa/article/mce.tex
@@
 As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has $\bigO(mn^{2m+1})$ runtime complexity.
-In \autoref{section:improvements}, we give some suggestions of improvements that can be applied to the implementation of \autoref{algoritmo:mce}, and in \autoref{section:numerical}, we analyze the results obtained by \autoref{algoritmo:mce} for some numerical experiments.
+In Section~\ref{section:improvements}, we give some suggestions of improvements that can be applied to its implementation, and in Section~\ref{section:numerical}, we analyze the results obtained for some numerical experiments.
 

### 2020-04-05 defesa/presentation/slides.tex
wip

@@
 \documentclass{beamer}
+\usefonttheme{serif}
+\usetheme{boadilla}
 
@@
 \usepackage{tikz}
+\usepackage{subcaption}
+\usepackage{graphicx}
+\usepackage{hyperref}
 \usetikzlibrary{quotes, angles, intersections}
@@
 \newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
+\newcommand{\sigla}[2]{#2 (#1)}
+\newcommand{\citeonline}[1]{\cite{#1}}
 
-\author{Danilo Tedeschi\\Dra. Marina Andretta}
-\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems}
+\newtheorem{thm}{Theorem}
+\newtheorem{prp}{Proposition}
+\newtheorem{lem}{Lemma}
+\theoremstyle{definition}
+%\newtheorem{definition}{Definition}[section]
+
+\author{Danilo Tedeschi}
+\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems}
 \institute{Universidade de São Paulo}
@@
 		\footnotesize This research has been funded by Cordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES).
-This is part of a Master's research project on the problem: \textit{Planar Maximal Covering by Ellipses with Rotation}.
+	\end{frame}
+
+	\begin{frame}{Introduction}{Related problems}
+
+		\sigla{MCLP}{The Maximum Covering Location Problem} 
+		\begin{itemize}
+			\item Introduced in \cite{church:1974},
+			\item Maximize the coverage demand vertices on a graph,
+			\item Choose the location (vertex) of a fixed number of facilities,
+			\item A demand vertex is considered covered if a facility is located within its coverage radius.
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Introduction}{Related problems}
+
+	\sigla{PMCLP}{The Planar Maximum Covering Location Problem} 
+	\begin{itemize}
+		\item Introduced in \cite{church:1984},
+		\item Maximize the coverage demand vertices in $\R^2$,
+		\item Choose the location (could be anywhere in $\R^2$) of a fixed number of facilities,
+		\item A demand vertex is considered covered if a facility is located within its coverage radius,
+		\item Several distance functions were studied. We are particularly interested in the Euclidean PMCLP.
+	\end{itemize}
 	\end{frame}
@@
 
-	Two versions: 
+	We propose algorithms for two versions of PMCLP.
+
+\end{frame}
+
+\begin{frame}{Introduction}{MCE}
+	Planar Maximum Covering Location by Ellipses Problem (MCE):
 	\begin{itemize}
-		\item Planar Maximum Covering Location by Ellipses Problem (MCE) \cite{canbolat};
-		\item Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER) \cite{andreta}.
+		\item Introduced in \cite{canbolat}, 
+		\item Mixed Non-linear optimization and a heuristic method in \cite{canbolat},
+		\item Exact method, solving convex sub-problems in \cite{andreta}.
 	\end{itemize}
+
+	\begin{block}{Our algorithm}		
+		Based on the approach used for the Euclidean PMCLP in \cite{church:1984}.
+		Transform MCE into a combinatorial optimization problem.
+	\end{block}
+\end{frame}
+
+\begin{frame}{Introduction}{MCER}
+	Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER):
+	\begin{itemize}
+		\item Introduced in \cite{andreta}, 
+		\item Exact method, solving many optimization sub-problems in \cite{canbolat},
+		\item Heuristic method in \cite{andreta}.
+		\item Much more challenging than MCE.
+	\end{itemize}
+
+	\begin{block}{Our algorithm}		
+		Transforms MCER into a combinatorial optimization problem.
+	\end{block}
 \end{frame}
@@
 \begin{frame}{Introduction}{Ellipse}
-	The shape of an ellipse is given by its major-axis and minor-axis, $(a, b) \in \mathbb{R}^2$, with $a > b > 0$.
+	The shape of an ellipse is given by its major-axis and minor-axis, $(a, b) \in \mathbb{R}^2_{>0}$, $a > b$.
 
@@
 
+\begin{frame}{Introduction}{Ellipse}
+	An ellipse can be defined using a norm function $||\cdot||_{a,b,\theta}$ given by
+	\begin{equation*}
+		||x||_{a,b, \theta}=\left|\left|
+		\left(\begin{array}{rr}
+		\cos{\theta} & \sin{\theta}\\
+		\sin{\theta} & -\cos{\theta}
+		\end{array}
+		\right)
+		\left(\begin{array}{cc}
+		1/a & 0\\
+		0 & 1/b
+		\end{array}\right) x \right|\right|_2.
+	\end{equation*}
+\end{frame}
+
+\begin{frame}{Problem definition}
+	%\begin{block}{Definition}
+	An instance of both MCE and MCER is given by
+	\begin{itemize}
+		\item A demand set $\Pp:=\{p_1, \dots, p_n\}$, $p_j \in \R^2$;
+		\item Each point has a weight $\Ww := \{w_1, \dots, w_n\}$, $w_j \in \R_{\ge0}$;
+		\item A list of shape parameters $\Rr := \{(a_1, b_1); \dots; (a_m, b_m)\}$, $(a_j, b_j) \in \R^2_{>0}$, with $a_j > b_j$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Problem definition}
+	\begin{figure}
+		\begin{subfigure}{.4\textwidth}
+			\centering
+			\includegraphics[scale=.55]{../article/figures/MCE_TA04}
+			\caption{}
+			\label{fig:MCE_TA04}
+		\end{subfigure}
+		\begin{subfigure}{.4\textwidth}
+			\centering
+			\includegraphics[scale=.55]{../article/figures/MCER_TA04}
+			\caption{}
+			\label{fig:MCER_TA04}
+		\end{subfigure}
+		\caption{Solutions for the same instance of (a) MCE, and (b) MCER.}
+		\label{fig:TA04}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Problem definition}{More notation}
+
+	\begin{block}{Weight function}
+	Let $w\colon 2^\Pp \to \R$ be a function defined as
+
+	\begin{equation*}
+	w(A) = \sum_{j \colon p_j \in A} w_j.
+	\end{equation*}
+
+%	which takes a subset of $\Pp$ and returns the sum of the weights of the points in that subset.
+	\end{block}
+
+\begin{block}{MCE's solution}
+	$Q:=(q_1, \dots, q_m) \in \R^{2m}$.
+\end{block}
+
+\begin{block}{MCER's solution}
+	%$Q:=(q_1, \dots, q_m)$.\\
+	$Q:=((q_1, \theta_1); \dots; (q_m, \theta_m)) \in (\R^2\times [0, \pi))^m$.
+\end{block}
+
+	%(Only used to make the text more clear)
+\end{frame}
+
+\begin{frame}{Problem definition}{MCE}
+	Let $E_j \colon \R^2 \to \R^2$ be the coverage region of the $j$-th ellipse defined as
+	\begin{equation*}
+	E_j(q) = \{x \in \R^2\colon ||x-q||_{a,b,0} \le 1\}.
+	\end{equation*}
+	Then, MCE is defined as the optimization problem:
+	\begin{equation*}
+	\max_{Q}  w\left(\bigcup_{j=1}^m\Pp \cap E_j(q_j)\right).
+	\end{equation*}
+\end{frame}
+
+\begin{frame}{Problem definition}{MCER}
+	Let $E_j \colon \R^2\times[0, \pi) \to \R^2$ be the coverage region of the $j$-th ellipse defined as
+	\begin{equation*}
+	E_j(q,\theta) = \{x \in \R^2\colon ||x-q||_{a,b,\theta} \le 1\}.
+	\end{equation*}
+	Then, MCER is defined as the optimization problem:
+	\begin{equation*}
+	\max_{Q}  w\left(\bigcup_{j=1}^m\Pp \cap E_j(q_j,\theta_j)\right).
+	\end{equation*}
+
+	\begin{block}{Remark}
+		For the one-facility MCE and MCER, we omit the index referring to the ellipse.
+	\end{block}
+\end{frame}
+
 \begin{frame}{MCE}
-	\begin{block}{Definition}
-		Demand set $\Pp=\{p_1, \dots, p_n\}$;\\
-		Weights $\Ww = \{w_1, \dots, w_n\}$;\\
-		Shape parameters $\Rr = \{(a_1, b_1), \dots, (a_m, b_m)\}$, $a_j > b_j > 0$.\\
-		Set of functions $\E = \{E_1, \dots, E_m\}$, $E_j(q_j)$ is the $j$-th ellipse's coverage region.
+	$\{p_1, p_2, p_3\} \subset E(q)$
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.55]{figures/mce-mwc0}
+		\caption{A solution for the one-facility MCE.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCE}
+	$\{p_1, p_2, p_3\} \subset E(q) \implies q \in E(p_1) \cap E(p_2) \cap E(p_3)$.
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.55]{figures/mce-mwc}
+		\caption{A solution for the one-facility MCE.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCE}
+	In general we have
+	\begin{equation*}
+	A = \Pp \cap E(q) \implies 	q \in \cap_{p \in A} E(p),
+	\end{equation*}
+and
+	\begin{equation*}
+	q' \in \cap_{p \in A} E(p) \implies	A \subset E(q').
+	\end{equation*}
+
+	\begin{block}{Intersection region of ellipses}
+		By \cite{bi}, we have that if $|A|>1$, there is at least one intersection between two ellipses in the border of $\cap_{p\in A} E(p)$.
 	\end{block}
+\end{frame}
+
+\begin{frame}{MCE}
+	$\{q_1, q_2, q_3\} \subset \bigcup_{1 \le i < j \le 3} \partial E(p_i) \cap \partial E(p_j)$.
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.55]{figures/mce-mwc1}
+		\caption{A solution for the one-facility MCE.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCE}
+	In general, we have
+	\begin{equation*}
+	|\partial E(u) \cap \partial E(v)| \le 2, 
+	\end{equation*}
+	and that $\partial E(u) \cap \partial E(v)$ can be determined analytically.
+\end{frame}
+
+\begin{frame}{MCE}{Candidate List Set}
+
+	Based on \cite{church:1984}, we define a Candidate List Set (CLS) for each facility as follows.
+
+	\begin{definition}\label{def:cls_mce}
+		Given an instance of MCE, for all $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
+		\begin{equation*}
+		S_k = \Pp \cup \left(\bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \right).
+		\end{equation*}
+	\end{definition}
+\end{frame}
+
+\begin{frame}{MCE}{Main result}
+	\begin{thm}\label{thm:mce}
+		Given an instance of MCE, and $S_1, \dots, S_m$ as defined previously, then the set $$\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$.
+	\end{thm}
+
+\begin{itemize}
+	\item Notice that $|S_k| \le n(n+1)/2 \le n^2$.
+	\item An algorithm with $\bigO(mn^{2m+1})$ runtime complexity can be implemented.
+\end{itemize}
+
+\end{frame}
+
+%%% E3P
+
+\begin{frame}{Determining Every Center and Angle of Rotation of An Ellipse Given Its Shape and Three Points that It Must Contain}
+	Given
+	\begin{itemize}
+		\item The coverage region function of an ellipse $E \colon \R^2 \times [0, \pi) \to \R^2$.
+		\item Three points $u, v, w \in \R^2$.
+	\end{itemize}
+Let us call E3P the problem whose solution is given by $(q, \theta) \in \R^2 \times [0, \pi)$, such that
+
+$$\{u, v, w\} \subset \partial E(q, \theta).$$
+
+We want to compute every solution of E3P.
+
+We did not find any work on E3P in the literature.
+\end{frame}
+
+\begin{frame}{E3P}
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.4]{../tex/figures/e3p_4sols}
+		\caption{Example of every solution for an instance of E3P.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{E3P}{Transforming the problem}
+	Let us define a function $\varphi \colon \R^2 \times [0, \pi) \to \R^2$ that transforms the problem as follows.
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.7]{../article/figures/circumscribed-circle}
+		\caption{Transforming a solution of E3P into a solution of the circumcircle problem.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{E3P}{Transforming the problem}
+	If $u$ is at the origin, this function can be described as
+	\begin{equation*}%\label{eq:trpnts}
+	\varphi(p, \theta)=\left[\begin{array}{cc}
+	\frac{b}{a}&0\\
+	0&1
+	\end{array}\right]
+	\left[\begin{array}{cc}
+	\cos{\theta}&\sin{\theta}\\
+	-\sin{\theta}&\cos{\theta}
+	\end{array}\right]\left[\begin{array}{c}
+	p_x\\
+	p_y
+	\end{array}\right].
+	\end{equation*}
+
+	\begin{itemize}
+		\item For a fixed angle, $\varphi$ is bijective, we refer to $\varphi^{-1}$ as its inverse.
+		\item Let us denote by $\Lambda(\theta)$ as the triangle with vertices $\varphi(u), \varphi(v), \varphi(w)$.
+		%\item if $\theta$ The circumscribed circle of $\Lambda(\theta)$ has radius $b$.
+		\item E3P is equivalent to determining $\theta$, such that the circumscribed circle of $\Lambda(\theta)$ has radius $b$.
+	\end{itemize}	
+\end{frame}
+
+\begin{frame}{E3P}{Transforming the problem}
+	A circle is uniquely defined by $\Lambda(\theta)$, and its radius and center can be determined analytically \cite{weisstein}.
+
+	Let $|\Lambda(\theta)|$ be the area of $\Lambda(\theta)$, and imposing that the radius of that circle is equal to $b$, we define a function $\xi \colon [0, \pi) \to \R$ whose roots determine solutions of E3P.
+
+	\begin{equation*}\label{eq:xi}
+	\xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2.
+	\end{equation*}
+\end{frame}
+
+\begin{frame}{E3P}
+	\begin{lem}\label{lema:e3p}
+		E3P has at most six solutions.
+	\end{lem}
+\begin{itemize}
+	\item $\xi$ can be written as $\sum_{0 \le j+k \le 6} c_{j,k} \cos^j\theta \sin^k\theta$,
+	\item It is a real trigonometric polynomial, 
+	\item By \cite[p.~150]{powell}, it has at most $12$ roots in $[0, 2\pi)$,
+	\item As ellipses are symmetrical, we can dismiss half of the roots.
+\end{itemize}
 \end{frame}
@@
 	\frametitle{References}
-	\bibliographystyle{amsalpha}
-	\bibliography{../references.bib}
+	\bibliographystyle{acm}
+	\bibliography{../references}
 \end{frame}

### 2020-04-06 defesa/presentation/slides.tex
wip

@@
 
+\begin{frame}{E3P}{Transforming the problem}
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.7]{figures/inexn16}
+		\caption{A plot of $\xi$ in $[0, \pi)$ for an instance of E3P.}
+	\end{figure}
+\end{frame}
+
 \begin{frame}{E3P}
@@
 	\item $\xi$ can be written as $\sum_{0 \le j+k \le 6} c_{j,k} \cos^j\theta \sin^k\theta$,
-	\item It is a real trigonometric polynomial, 
-	\item By \cite[p.~150]{powell}, it has at most $12$ roots in $[0, 2\pi)$,
+	\item It is a real trigonometric polynomial of degree $6$, can be written as
+	\begin{equation*}
+		\sum_{k=0}^6 a_k \cos{k\theta} + \sum_{k=1}^6 b_k \sin{k\theta}
+	\end{equation*} 
+	\item A $n$-degree real trig. poly. can have up to $2n$ roots in $[0, 2\pi)$ \cite[p.~150]{powell},
 	\item As ellipses are symmetrical, we can dismiss half of the roots.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{E3P}{Finding the roots of $\xi$}
+	We will convert $\xi$ into a complex polynomial on $z=e^{i\theta}$ using the identities
+	\begin{eqnarray*}
+	\cos{\theta} = \frac{e^{i\theta} + e^{-i\theta}}{2},\\
+	\sin{\theta} = \frac{e^{i\theta} - e^{-i\theta}}{2i}.
+	\end{eqnarray*}
+\end{frame}
+
+\begin{frame}{E3P}{Finding the roots of $\xi$}
+	We define a function $g \colon \mathbb{S} \to \mathbb{C}$ given by
+
+	\begin{equation*}
+	g(z=e^{i\theta}) = \xi(\theta).
+	\end{equation*}
+
+	Extending the domain to $\mathbb{C}$ we define a polynomial 
+	$$f(z) = z^6 g(z).$$
+	\begin{itemize}
+		\item The exponents of $g$ go from $-6$ to $6$,
+		\item The roots of $f$ that are in $\mathbb{S}$ are roots of $g$.
+		\item In practice, we used symbolic computation for this task,
+		\item No loss of accuracy \cite{weidner}.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{E3P}{Finding the roots of $\xi$}
+	We can cut in half the degree of $f$ by observing that
+	\begin{equation*}
+	angle(-z)=\pi+angle(z).
+	\end{equation*}
+
+	As an ellipse rotated by $\theta$ is identical to an ellipse rotated by $\pi + \theta$, we get that
+
+	$$f(-z) = f(z).$$
+
+	Therefore, every odd coefficient of $f$ is zero, and we can use another substitution $y=z^2$ to obtain a $6$-degree polynomial.
+\end{frame}
+
+\begin{frame}{E3P}{Determining the roots of a polynomial}
+	For every univariate polynomial of degree $n$, there exists a companion matrix, which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial \cite[p.~195]{horn}.
+
+\end{frame}
+
+\begin{frame}{E3P}{Determining the roots of a polynomial}
+	For a degree-$4$ polynomial $\sum_{k=0}^4 a_k x^k$, a companion matrix is given by
+
+	\begin{equation*}
+	\left[\begin{array}{ccccc}
+	0 & 1 & 0 & 0\\
+	0 & 0 & 1 & 0\\
+	0 & 0 & 0 & 1\\
+	-\dfrac{a_0}{a_4} & -\dfrac{a_1}{a_4} & -\dfrac{a_2}{a_4} & -\dfrac{a_3}{a_4}
+	\end{array}\right].
+	\end{equation*}
+
+	\begin{itemize}
+		\item QR algorithm can determine the eigenvalues in $\bigO(n^3)$ \cite{watkins:2008}.
+		\item In practice, we use LAPACK's ZGEEV routine.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{E3P}{Choosing a precision constant}
+	We need to choose a precision constant to check if a root is in $\mathbb{S}$.
+
+	In practice, every eigenvalue $\hat{z}$ returned by the QR algorithm, we consider it to be in $\mathbb{S}$ if
+
+	\begin{equation*}
+	|1 - \hat{z}| < \epsilon.
+	\end{equation*}
+
+	\begin{itemize}
+		\item Experiments with three points $(a, 0); (-a, 0); (a, b)$ rotated by a random angle.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{E3P}{Choosing a precision constant}
+	\begin{figure}[!htb]
+
+		\begin{subfigure}{.44\textwidth}
+			\centering
+
+			\includegraphics[scale=.53]{../article/figures/e3p_known_sols2}
+			\caption{}
+			\label{fig:e3p_known_sols2}
+		\end{subfigure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+
+			\includegraphics[scale=.53]{../article/figures/e3p_known_sols1}
+			\caption{}
+			\label{fig:e3p_known_sols1}
+		\end{subfigure}
+		\caption{(a) $|1-\hat{z}|$. (b) $|f(\hat{z})|$.}
+	\end{figure}
+
+\begin{itemize}
+	\item We define $\epsilon = 10^{-6}$.
+	\item We further check if $|f(\hat{z})| < 10^{-9}$ to consider $\hat{z}$ to be a root of $f$.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{E3P}
+	These possible properties were observed in practice, and could be used in future work:
+	\begin{itemize}
+		\item Instances with $6$ solutions seem to always come from an equilateral triangle's vertices.
+		\item Instances with $4$ solutions seem to always come from an isosceles triangle's vertices.
+		\item The coefficients of $f$ seem to have the following symmetry property:
+		\begin{equation*}
+		c_k = \overline{c_{6-k}}.
+		\end{equation*}
 	\end{itemize}

### 2020-04-07 defesa/presentation/slides.tex
wip

@@
 
+\begin{frame}{MCER}
+	The algorithm for MCE is based on the fact that there is at most $2$ centers for an ellipse to contain two points.
+	\\~\
+
+	For MCER, we will use a similar idea based on the results for E3P.
+
+	\begin{itemize}
+		\item We will prove that any solution $(q,\theta)$ for the one-facility MCER can always be classified as one out of three possible types.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{MCER}
+	It covers at most one point.
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.6]{figures/mcer3}
+		\caption{Example of solution for the one-facility MCER.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCER}
+	It covers at least three points, and there exists $\{u,v,w\}\subset E(q,\theta)$, such that their E3P's instance has at least one solution.
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.6]{figures/mcer2}
+		\caption{Example of solution for the one-facility MCER.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCER}
+	It covers at least two points, and there is no $\{u,v,w\}\subset E(q,\theta)$, such that their E3P's instance has at least one solution.
+	\begin{figure}
+		\centering
+		\includegraphics[scale=.6]{figures/mcer1}
+		\caption{Example of solution for the one-facility MCER.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCER}
+Let $Q$ and $Q'$ be two solutions of MCER, then we say that $Q \succ Q'$ if, and only if
+
+\begin{equation*}
+\bigcup_{j=1}^m \Pp \cap E_j(q_j', \theta_j') \subset \bigcup_{j=1}^m \Pp \cap E_j(q_j, \theta_j).
+\end{equation*}
+
+\begin{lem}\label{lema:mce_2b}
+	Let $Q$ be a solution for the one-facility MCER, such that $|\Pp \cap E(q, \theta)| \ge 2$.
+	There exists a solution $Q'$, such that $Q' \succ Q$ and $|\Pp \cap \partial E(q', \theta')|\ge 2$.
+\end{lem}
+\end{frame}
+
+\begin{frame}{MCER}{Feasible angle}
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=.22]{../article/figures/feasible-angle2}
+	\caption{The solid border ellipses are rotated by a $(E, u,v)$-feasible angle, while the ellipse with a dashed border is rotated by a not $(E, u, v)$-feasible angle.}
+	\label{fig:feasible-angle}
+\end{figure}
+\end{frame}
+
+\begin{frame}{MCER}{Feasible angle}
+	\begin{definition}\label{def:feasible_angle}
+		Let $E$ be the coverage region of an ellipse and $u, v \in \R^2$.
+An angle $\theta \in [0, \pi)$ is said to be $(E, u, v)$-feasible if there is $q \in \R^2$ such that $\{u, v\} \subset \partial E(q, \theta)$.
+		In addition to that, the set of $(E, u, v)$-feasible angles is referred to as
+
+		\begin{equation*}
+		\Phi(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E,u,v)\textnormal{-feasible angle}\}.
+		\end{equation*}
+		%We also define $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$.
+Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
+	\end{definition}
+
+\end{frame}
+
+\begin{frame}{MCER}{Feasible angle}
+	\begin{lem}\label{lema:l-function}
+		Given an instance of the one-facility MCER, if $u, v \in \Pp$ have the same $y$-coordinate and $||u-v||_2 \le 2a$, then $\Phi(u,v) = [0, \alpha] \cup [\pi - \alpha, \pi)$, for some $\alpha \in [0, \pi/2]$.
+	\end{lem}
+\end{frame}
+
+\begin{frame}{MCER}{Feasible angle}
+	$L(m)$ is the maximum distance between the intersection of a line from the set $\{y=mx + c \colon c \in \R\}$ and an ellipse $\partial E(0, 0)$.
+	\begin{figure}[H]
+	\centering
+		\includegraphics[scale=.26]{../tex/figures/L-function-plot}
+		\caption{Plot of function $L$ in the interval $[-7, 7]$.}
+		\label{fig:L-function-plot}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCER}
+	The only problem now is with respect to solutions which we can find another solution covering the same points with three points on the ellipse.
+	\\~\
+
+	Next, we prove that in this case, for any feasible angle of rotation, a solution exists covering the same set of points.
+\end{frame}
+
+\begin{frame}{MCER}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=.7]{../article/figures/lema-3-points}
+%		\caption{}
+		\label{fig:lema-3-points}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{MCER}
+	Let $Q$ and $Q'$ be two solutions of MCER, we say that they are equivalent if, and only if
+	\begin{equation*}
+	\bigcup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = 	\bigcup_{j=1}^m \Pp \cap E_j(q_j', \theta_j').
+	\end{equation*}
+\begin{lem}\label{lema:3pnts}
+	Let $Q^*$ be a solution of the one-facility MCER, such that $|\Pp \cap E(q^*, \theta^*)|\ge2$.
+	If for all $\bar{Q} \succ Q^*$, $|\Pp \cap \partial E(\bar{q}, \bar{\theta})| < 3$, then there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that for all $\theta\in \Phi(u,v)$ there exists $q \in \R^2$, such that $(q, \theta)$ is equivalent to $Q^*$.
+\end{lem}
+\end{frame}
+
+\begin{frame}{MCER}{Proof}
+	\begin{itemize}
+		\item Take $u, v \in E(q^*, \theta^*)$, such that there exists $Q'\succ Q$ with $\{u,v\} \subset \partial E(q', \theta')$.
+
+		\item We can rotate the coordinate system to make $\Phi(u,v) = [0, 2\alpha]$.
+
+		\item Define $\delta \colon \Phi(u,v) \to \R^2$, such that 
+		\begin{eqnarray*}
+		\textnormal{ for all }\theta \in \Phi(u,v)\implies \{u,v\} \subset \partial E(\delta(\theta), \theta)\\
+		\delta(\theta')=q'
+		\end{eqnarray*}
+
+		\item That is, $\delta(\theta)$ returns the center to make the ellipse contain the two points $u$ and $v$.
+
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{MCER}{Proof}
+	\begin{itemize}
+		\item For any $w$ covered, by continuity, we have that
+		\begin{eqnarray*}
+		\exists \theta \in \Phi(u,v)\colon||w-\delta(\theta)||_{a,b,\theta} > 1\\ 
+		\Leftrightarrow\\
+		\exists \bar{\theta} \in \Phi(u,v) \colon |w-\delta(\bar{\theta})||_{a,b,\bar{\theta}}=1.
+		\end{eqnarray*}
+
+		\item That is, if for any feasible angle $w$ becomes uncovered, there must be another angle that puts it on the ellipse.
+
+		\item The same argument can be used for a point that is initially uncovered.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{MCE}
+	With this lemma, we can choose any feasible angle for a pair of points or three points to put on the ellipse.
+	\\~\
+
+	Let $u \in \R^2$, we define $\angle u$ denotes the minimal angle between the vector $u$ and the $x$-axis.
+
+	\begin{itemize}
+		\item If $\Phi(u,v) \neq \emptyset$, then $\angle (u-v) \in \Phi(u,v)$.
+		\item The longest segment that intersects an ellipse is its major-axis.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{MCER}{CLS}
+	Following this, we define the CLS for each ellipse.
+
+	\begin{definition}\label{def:Sj}
+		Given an instance of MCER. Then, for all $j\in\{1, \dots, m\}$, we define the CLS of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
+		\begin{align*}
+		S_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
+		S_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \angle(u-v))\in \R^2\times[0, \pi): \{u,v\} \subset \partial E_j(q, \angle(u-v))\}\\
+		S_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times[0, \pi): \{u, v, w\} \subset \partial E_j(q, \theta)\}.
+		\end{align*}
+	\end{definition}
+\end{frame}
+
+\begin{frame}{MCER}
+	Finally, we can construct a finite set which contains an optimal solution.
+
+	\begin{thm}\label{th:mcer}
+		Given an instance of MCER, let $\Omega$ be a set of solutions defined as 
+		\begin{equation*}\label{eq:omega}
+		\Omega = \{Q \in (\R^2\times[0, \pi))^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
+		\end{equation*}
+		Then there exists an optimal solution $Q^* \in \Omega$, and $|\Omega|\le n^{3m}$.
+	\end{thm}
+\end{frame}
+
+\begin{frame}{MCER}{proof}
+$$|S_j^{(2)}| \le 2 \binom{n}{2} = \frac{n(n+1)}{2} \le n^2,$$
+
+$$|S_j^{(3)}| \le 6 \binom{n}{3} = n((n-1)^2+1) \le n^3.$$
+
+\begin{itemize}
+	\item For an ellipse, if an equivalent solution is not in $S_j^{(2)}$, we can apply the previous lemma, which implies that an equivalent solution is in $S_j^{(3)}$.
+
+	\item An $\bigO(mn^{3m+1})$ runtime algorithm can be implemented.
+\end{itemize}
+\end{frame}
+
 \begin{frame}[allowframebreaks]

### 2020-04-08 defesa/presentation/slides.tex
wip

@@
 
+\begin{frame}{Numerical Experiments}{Facility Cost}
+	We ran experiments for the version where each facility has a cost associated with it.
+	\begin{itemize}
+		\item MCE-$k$ (MCER-$k$) is the problem where exactly $k$ facilities have to be utilized.
+		\item We solve MCE-$k$ (MCER-$k$) by solving the $\binom{m}{k}$ instances of MCE (MCER). 
+	\end{itemize} 
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{Known Instances}
+	First we consider the instances that were also analyzed in \cite{andreta}.
+
+	\begin{itemize}
+		\item At most $100$ points and $5$ ellipses,
+		\item The demand points are uniformly distributed,
+		\item Points have unit weights.
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{MCE-$k$}
+	\begin{itemize}
+		\item Our algorithm took at most $0.1$s of CPU time for each instance.
+		\item The method developed in \cite{andreta} took more than $45$ minutes for some instances.
+		\item In practice, the amount of computation was much lower than the asymptotic bound.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{MCER-$k$}
+	\begin{itemize}
+	\item Our algorithm took at most $6$s of CPU time for each instance.
+	\item The deterministic method developed in \cite{andreta} timed out for some instances.
+	\item The heuristic method took more than $7$ hours of CPU time.
+	\item The heuristic method did not obtain an optimal solution for four instances.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{MCER-$k$}
+	\begin{figure}[!htb]
+
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_AB108}
+			\caption{}
+			\label{fig:AB108}
+		\end{subfigure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_AB120}
+			\caption{}
+			\label{fig:AB120}
+		\end{subfigure}
+		\caption{An optimal solution of MCER-$k$ for the instance AB108 (a), and for the instance AB120 (b).}
+		\label{fig:AB108-AB120}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	To further analyze we decided to create new instances.
+	\begin{itemize}
+		\item Normally distributed demand points,
+		\item Non-unitary weights,
+		\item Up to $700$ points,
+		\item Up to $7$ ellipses.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	First set of instances TA01-TA07.
+	\begin{itemize}
+		\item $p_j \sim \mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$.
+		\item $w_j = ||p_j||_2^2$.
+		\item $a_j, b_j \sim U(0.5, 1.5)$.
+		\item The cost of the $j$-th ellipse is $c_j = 10 \times a_j \times b_j$.
+		\item Seven instances $n=100$ points, with $m=7$ ellipses and $k \in \{1,\dots, m\}$.
+		\item MCE: timed out (2h) for instance with $k=7$,
+		\item MCER: Timed out (2h) for isntance with $k=5,6,7$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	\begin{figure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCE_TA04}
+			\caption{}
+			\label{fig:MCE_TA04}
+		\end{subfigure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_TA04}
+			\caption{}
+			\label{fig:MCER_TA04}
+		\end{subfigure}
+		\caption{Two optimal solutions for the instance TA04: (a) for MCE-$k$, and (b) for MCER-$k$.}
+		\label{fig:TA04}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	Second set of instances TA08-TA22.
+	\begin{itemize}
+		\item $p_j \sim \mathcal{N}([0, 0]^T, \mathbb{I})$, with $\mathbb{I} \in \R^{2\times 2}$.
+		\item $w_j = ||p_j||_2^2$.
+		\item $a_j, b_j \sim U(0.5, 1.5)$.
+		\item The cost of the $j$-th ellipse is $c_j = 10 \times a_j \times b_j$.
+		\item Instances  $n\in\{200, 250, 300, 350, 400\}$ points, with $m=3$ ellipses and $k \in \{1,\dots, m\}$.
+		\item MCE: Obtained optimal solutions for every instance,
+		\item MCER: Timed out (2h) for the instance with $n=400$ and $k=3$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+
+	\begin{figure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCE_TA21}
+			\caption{}
+			\label{fig:MCE_TA21}
+		\end{subfigure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_TA21}
+			\caption{}
+			\label{fig:MCER_TA21}
+		\end{subfigure}
+		\caption{Two optimal solutions for the instance TA21 with $400$ points: (a) for MCE-$k$, and (b) for MCER-$k$.}
+		\label{fig:TA21}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	Third set of instances TA23-TA42.
+	\begin{itemize}
+		\item $p_j \sim U[0, 10]^2$.
+		\item $w_j = 1$.
+		\item $a_j, b_j \sim U(0.5, 1.5)$.
+		\item The cost of the $j$-th ellipse is $c_j = 10 \times a_j \times b_j$.
+		\item Instances  $n\in\{400, 500, 600, 700\}$ points, with $m=5$ ellipses and $k \in \{1,\dots, m\}$.
+		\item We Obtained optimal solutions for every instance,
+		\item The CLSs are much smaller compared to the previous set of instances.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	\begin{figure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCE_TA37}
+			\caption{}
+			\label{fig:MCE_TA37}
+		\end{subfigure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_TA37}
+			\caption{}
+			\label{fig:MCER_TA37}
+		\end{subfigure}
+		\caption{Two optimal solutions for the instance TA37: (a) for MCE-$k$, and (b) for MCER-$k$.}
+		\label{fig:TA37}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	Last set of instances TA43-TA47.
+	\begin{itemize}
+		\item Half of the points follow $\mathcal{N}(\mu^{(1)}, \mathbb{I})$, and the other half follow $\mathcal{N}(\mu^{(2)}, \mathbb{I})$.
+		\item $\mu^{(1)} = (-3, -3)$ and $\mu^{(2)} = (-3, -3)$,
+		\item $w_j$ is set to its distance to the mean that from the distribution it was generated from.
+		\item For the one half: $a_j, b_j \sim U(0.5, 1.5)$; for the other half $a_j, b_j \sim U(3, 4)$.
+		\item The cost of the $j$-th ellipse is $c_j = a_j \times b_j$.
+		%\item Create an example where the chosen ellipses in the solution of an instance of MCER-$k$ is not a subset of the chosen ellipses in an optimal solution of that same instance for MCER-$(k+1)$.
+		\item Instances  $n=80$ points, with $m=5$ ellipses and $k \in \{1,\dots, m\}$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Numerical Experiments}{New instances}
+	\begin{figure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_TA44}
+			\caption{}
+			\label{fig:MCER_TA44}
+		\end{subfigure}
+		\begin{subfigure}{.44\textwidth}
+			\centering
+			\includegraphics[scale=.6]{../article/figures/MCER_TA45}
+			\caption{}
+			\label{fig:MCER_TA45}
+		\end{subfigure}
+		\caption{Two optimal solutions for the instance TA44: (a) for MCE-$k$, and (b) for MCER-$k$.}
+		\label{fig:TA44-45}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Conclusion}
+	We conclude by leaving some directions for future works.
+	\begin{itemize}
+		\item There is a lot of room to further study E3P.
+		\begin{itemize}
+			\item We showed some possible properties.
+			\item Perhaps, these properties can be used to decrease the degree of the complex polynomial.
+		\end{itemize}
+		\item Use a Integer Linear Programming Model instead of backtracking the solution.
+		\item Adapt the approximation scheme developed in \cite{cabello:2006} for MCE and MCER.
+	\end{itemize}
+\end{frame}
+
 \begin{frame}[allowframebreaks]

### 2020-07-08 defesa/article/introduction.tex
Add article changes

@@
 
+%New paragraph
+{\color{Green}
+	In the real world, this problem comes up when a telecommunications company has to buy and place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming profit maximization.
+	More details about the applications of PMCLP can be found in \cite{canbolat}, which also ponders about the practical importance of considering the PMCLP with elliptical coverage.
+
+	As a first approach to solving MCE, a mixed-integer non-linear programming method was proposed in \cite{canbolat}. 
+	Its performance was measured using a constructed set of instances. The results were considered unsatisfactory, as, for some instances, the method could not find an optimal solution within an hour. 
+	For this reason, a second method using a heuristic technique called Simulated Annealing was developed.
+For the same set of instances, the heuristic was able to obtain solutions within the predefined time limit, and for some of them, it was even able to find optimal solutions.
+}
+
+{\color{Red}
 It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
@@
 Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
+}
 
@@
 For this reason, a heuristic method was developed treating the optimization subproblem as a convex problem.
-The method was able to obtain solutions for every instance, and for the ones the exact method did not time out, it could be verified that the heuristic method returned optimal solution as well.
+The method was able to obtain solutions for every instance, and for the ones the exact method did not time out, it could be verified that the heuristic method returned optimal {\color{blue}solutions} as well.
 

### 2020-07-19 article/conclusion.tex
move article directory up

--- 2020-03-25 defesa/article/conclusion.tex
@@
 These properties, if proved to be true, might be used in the development of a more efficient algorithm.
+
+{\color{Green}
+	Finally, we leave some additional suggestions for future works on this subject.
+We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though, extensive work would be necessary to adapt, somehow, the theory developed for this version, especially, of MCER.
+We also believe that investigating coverage of points by ellipsoids in higher dimensions can be a great subject of future studies taking this work as the starting point; 
+coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective.
+}

### 2020-07-19 article/introduction.tex
move article directory up

--- 2020-07-08 defesa/article/introduction.tex
@@
 
-{\color{Red}
-It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.
-In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to MCE.
-For some instances, the method took too long and did not find an optimal solution.
-Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
-}
-
 The problem was further explored in \citeonline{andreta}, where exact methods were developed for both MCE and MCER, and a heuristic method was developed for MCER.
@@
 In the end, we analyze numerical experiments for instances proposed in \cite{canbolat, andreta} and compare the results with the results obtained by the methods proposed in \cite{andreta}.
-Also, to further analyze our algorithms, we also analyzed numerical experiments for new instances with larger demand and facility sets.
+Also, to further {\color{blue}evaluate} our algorithms, we analyzed numerical experiments for new instances with larger demand and facility sets.
+
+{\color{Red}
+This paper is organized as follows.
+Section~\ref{section:definition} presents the definitions of both problems as well as introduces some notations used throughout the rest of the work.
+The algorithm for MCE is developed in Section~\ref{section:mce}, and the algorithm for MCER in Section~\ref{section:mcer} with the observation that its development depends on a subproblem whose algorithm is developed in Section~\ref{section:e3p}.
+Improvements suggestions to the implementations are given in Section~\ref{section:improvements} while the implementation details are given in Section~\ref{section:implementation}.
+Numerical results are presented and analyzed in Section~\ref{section:numerical}.
+Finally, a conclusion is given in Section~\ref{section:conclusion}.
+}

### 2020-07-19 article/mcer.tex
move article directory up

--- 2020-03-28 defesa/article/mcer.tex
@@
 	with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$.
-	If $D(m, c) = ||u-v||_2$, then there exists $q_1, q_2 \in \R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$ and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
+	If $D(m, c) = ||u-v||_2$, then there exist $q_1, q_2 \in \R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$ and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
 It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$.
@@
 	which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.
-From that, if $L(m) \ge ||v-u||_2^2$, then there exists $q_1, q_2\in\R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$, and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
+From that, if $L(m) \ge ||v-u||_2^2$, then there exist $q_1, q_2\in\R^2$, such that $\{u, v\} \subset \partial E(q_1, \tan{m})$, and $\{u, v\} \subset \partial E(q_2, \pi-\tan{m})$.
 
-	It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty, 0]$, and attains every value in the interval $(4b^2, 4a^2]$.
+	It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $(-\infty, 0]$, is decreasing in $[0, \infty)$, and attains every value in the interval $(4b^2, 4a^2]$.
 Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
@@
 	Therefore, if there exists $\theta\in\Phi(u,v)$, such that for all $q\in\R^2$, $(q, \theta)$ is not equivalent to $Q^*$, then there exists either $w \in \Pp \cap E(q^*, \theta^*)$, with $f_w(\theta)>1$, or $w \not\in \Pp \cap E(q^*, \theta^*)$, with $f_w(\theta)\le 1$.
-Because $f_w$ is continuous, there exists $\bar{\theta}\in\Phi(u,v)$, such that $f_w(\theta)=1$, implying that $|\Pp \cap \partial E(\delta(\bar{\theta}), \bar{\theta})| \ge 3$.
+Because $f_w$ is continuous, there exists $\bar{\theta}\in\Phi(u,v)$, such that $f_w(\bar{\theta})=1$, implying that $|\Pp \cap \partial E(\delta(\bar{\theta}), \bar{\theta})| \ge 3$.
 \end{proof}
@@
 	\begin{equation*}\label{eq:omega}
-	\Omega = \{Q \in (\R^2\times[0, \pi))^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
+	\Omega = \{Q \in (\R^2\times[0, \pi))^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
 	\end{equation*}
@@
 
-	In the first case, we consider solutions where the $j$-th ellipse covers less than one point, that is, $|\Pp \cap E_j(q_j^*, \theta_j^*)|\le1$.
+	In the first case, we consider solutions where the $j$-th ellipse covers at most one point, that is, $|\Pp \cap E_j(q_j^*, \theta_j^*)|\le1$.
 It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega$ every solution that has an ellipse centered at a point from $\Pp$.
-From that, we can also conclude that $|S_j^{(1)}| \le n$.
+From that, we can also conclude that $|S_j^{(1)}| = n$.
 
@@
 	As $\angle(u-v)$ is a $(E_j, u, v)$-feasible angle, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j, \theta_j) = \Pp \cap E_j(q_j^*, \theta_j^*)$.
-	Also, by \autoref{lema:e2p}, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.
+	{\color{blue}Also from \autoref{lema:e2p}, we can arrive at the conclusion that $|S_j^{(2)}| \le 2\binom{n}{2}$.}
 

### 2020-07-19 paper/article.tex
finsh some corrections

--- 2020-03-28 defesa/article/article.tex
@@
 %% The graphicx package provides the includegraphics command.
+
+%\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{graphicx}
+%\usepackage{graphicx}
 \usepackage{hyperref}
@@
 \usepackage{multirow}
+\usepackage{cancel}
 
 \journal{EJOR}
+
+%\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 
@@
 %\renewcommand\qedsymbol{$\blacksquare$}
+
+\bibliographystyle{plainnat}
 
@@
 
-		%% use the tnoteref command within \title for footnotes;
-		%% use the tnotetext command for the associated footnote;
-		%% use the fnref command within \author or \address for footnotes;
-		%% use the fntext command for the associated footnote;
-		%% use the corref command within \author for corresponding author footnotes;
-		%% use the cortext command for the associated footnote;
-		%% use the ead command for the email address,
-		%% and the form \ead[url] for the home page:
-		%%
-		%% \title{Title\tnoteref{label1}}
-		%% \tnotetext[label1]{}
-		%% \author{Name\corref{cor1}\fnref{label2}}
-		%% \ead{email address}
-		%% \ead[url]{home page}
-		%% \fntext[label2]{}
-		%% \cortext[cor1]{}
-		%% \address{Address\fnref{label3}}
-		%% \fntext[label3]{}
-
-		%% use optional labels to link authors explicitly to addresses:
-		%% \author[label1,label2]{<author name>}
-		%% \address[label1]{<address>}
-		%% \address[label2]{<address>}
-
-		\author[add1]{Danilo Tedeschi}
+		\author[add1]{Danilo Tedeschi\corref{cor1}}
 		\ead{danilo.tedeschi@usp.br}
@@
 		\address[add1]{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
+
+		\cortext[cor1]{Corresponding author.}
 \end{frontmatter}
@@
 			%% Text of abstract
-			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
-			maximizing a function depending on the value of covered points.
-			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
+
+			{\color{Red}
+		Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to choose the location of ellipses given their major and minor axis to cover demand points, maximizing a function depending on the value of covered points.
+		}We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
 			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances 	with up to seven hundred demand points and five ellipses.
@@
 \input{improvements.tex}
-
 %\section{Reducing the CLS size}\label{section:reducing_cls}
@@
 \clearpage
-\section*{References}
+%\section*{References}
 	%% New version of the num-names style
-	\bibliographystyle{apa}
-	\bibliography{../references}
+	%\bibliographystyle{natdin}
+	\bibliography{../defesa/references}
 
 \end{document}
-
-%%
-%% End of file `elsarticle-template-1-num.tex'.

### 2020-07-19 paper/conclusion.tex
finsh some corrections

--- 2020-07-19 article/conclusion.tex
@@
 coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective.
+{\color{Red}Lastly, as it has been pointed out, the critical parameter of both algorithms developed in this paper is the number of ellipses, we think that trading-off being able to run with large demand sets can be the basis for future work on an alternative algorithm that can obtain optimal solutions for instances with larger sets of ellipses.}
 }

### 2020-07-19 paper/cover.tex
finsh some corrections

--- 2020-03-25 defesa/article/cover.tex
@@
-\documentclass{article}
+\documentclass[letterpaper]{letter}
 
@@
 \newcommand{\citeonline}[1]{\cite{#1}}
+\signature{Danilo Tedeschi}
 
 \begin{document}
-		\title{Cover Letter}
-		\maketitle
 
-		Dear Editor, we herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.
+		%\title{Cover Letter}
+		%\maketitle
+
+		\begin{letter}{}
+
+			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
+
+		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.
 
@@
 
+		\closing{On behalf of the authors and with our best regards,}
+			\end{letter}
 		%\section*{References}

### 2020-07-19 paper/definition.tex
finsh some corrections

--- 2020-03-26 defesa/article/definition.tex
@@
 
-Let $\E=\{E_1, \dots, E_m\}$ be a list of functions representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$.
+Let $\E=\{E_1, \dots, E_m\}$ be a list of functions representing the coverage area of each facility, with $E_j \colon \R^2 \to {\color{blue}\mathcal{P}(\R^2)}$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to {\color{blue}\mathcal{P}(\R^2)}$.
 Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
@@
 \left(\begin{array}{cc}
-a_j & 0\\
-0 & b_j
+1/a & 0\\
+0 & 1/b
 \end{array}\right) x \right|\right|_2,
@@
 We use the notation $\partial$ to denote the boundary operator.
-For example, let $E \colon \R^2\to\R^2$ be the coverage region of an axis-parallel ellipse, then let $q\in\R^2$, $\partial E(q)$ describes an axis-parallel ellipse centered at $q$.
+For example, let $E \colon \R^2\to{\color{blue} \mathcal{P}(\R^2)}$ be the coverage region of an axis-parallel ellipse, then let $q\in\R^2$, $\partial E(q)$ describes an axis-parallel ellipse centered at $q$.
 If $E$ has shape parameters $(a, b)$, then $\partial E(q) = \{p \in \R^2\colon ||p-q||_{a,b,0} = 1\}$.

### 2020-07-19 paper/e3p.tex
finsh some corrections

--- 2020-03-28 defesa/article/e3p.tex
@@
 
-Given the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, $a > b$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
+Given the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, $a > b$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to{\color{blue}\mathcal{P}(\R^2)}$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
 Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.
@@
 Applying a rotation of $-\theta$ to the coordinate system makes the ellipse in the original solution become axis-parallel.
-Then, that ellipse can be transformed into a circle of radius $b$ by squeezing the $x$-axis by $b/a$. This two-step transformation can be written as a function $\varphi\colon \R^2 \to \R^2$ defined as
+Then, that ellipse can be transformed into a circle of radius $b$ by squeezing the $x$-axis by $b/a$.
+This two-step transformation can be written as a function ${\color{blue}\varphi_\theta\colon \R^2 \to \R^2}$ defined as
 
+\color{blue}
 \begin{equation*}%\label{eq:trpnts}
-\varphi(p, \theta)=\left[\begin{array}{cc}
+\varphi_\theta(p)=\left[\begin{array}{cc}
 \frac{b}{a}&0\\
@@
 \end{equation*}
+\color{black}
 
 An example of this transformation can be seen in \autoref{fig:circumscribed-circle}.
-As $\varphi^{-1}$ is well-defined, instead of solving E3P, we can work with the univariate problem of determining an angle of rotation $\theta \in [0, \pi)$ that makes the triangle with vertices $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ be circumscribed in a circle of radius $b$.
-To make the notation less cluttered, we denote by $\Lambda(\theta)$ the triangle with vertices $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
+As {\color{blue} $\varphi_\theta^{-1}$} is well-defined, instead of solving E3P, we can work with the univariate problem of determining an angle of rotation $\theta \in [0, \pi)$ that makes the triangle with vertices {\color{blue}$\varphi_\theta(u), \varphi_\theta(v), \varphi_\theta(w)$} be circumscribed in a circle of radius $b$.
+To make the notation less cluttered, we denote by $\Lambda(\theta)$ the triangle with vertices {\color{blue}$\varphi_\theta(u), \varphi_\theta(v), \varphi_\theta(w)$}.
 
@@
 \begin{equation}\label{eq:xi}
-\xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
+\xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{{\color{blue}\varphi_\theta(v)}}^2\norm{{\color{blue}\varphi_\theta(w)}}^2\norm{{\color{blue}\varphi_\theta(v)}-{\color{blue}\varphi_\theta(w)}}^2,
 \end{equation}
-whose roots are angles of rotation which determine solutions of E3P through the inverse transformation $\varphi^{-1}$.
-From a root $\hat{\theta}$ of $\xi$, let $\hat{q}$ be the center of the circumcircle of $\Lambda(\hat{\theta})$, the solution $(\varphi^{-1}(\hat{q}), \hat{\theta})$ of E3P is obtained.
+whose roots are angles of rotation which determine solutions of E3P through the inverse transformation {\color{blue}$\varphi_\theta^{-1}$}.
+From a root $\hat{\theta}$ of $\xi$, let $\hat{q}$ be the center of the circumcircle of $\Lambda(\hat{\theta})$, the solution $({\color{blue}\varphi_{\hat{\theta}}^{-1}}(\hat{q}), \hat{\theta})$ of E3P is obtained.
 
@@
 	The first thing to notice is that $\xi$ is a real trigonometric polynomial of degree $6$. 
-	Its term of highest degree is the multiplication of the norms $\norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2$.
+	Its term of highest degree is the multiplication of the norms $\norm{{\color{blue}\varphi_\theta(v)}}^2\norm{{\color{blue}\varphi_\theta(w)}}^2\norm{{\color{blue}\varphi_\theta(v)}-{\color{blue}\varphi_\theta(w)}}^2$.
 In \cite[p.~150]{powell}, where a definition of real trigonometric polynomial is also given, it is stated that a $n$-degree real trigonometric polynomial can have up to $2n$ roots in $[0, 2\pi)$.
@@
 Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \cite{watkins:2008}).
-For example, for a degree-$4$ polynomial $\sum_{k=0}^4 a_k x^4$, a possible companion matrix is given by
+For example, for a {\color{blue} $4$-degree} polynomial $\sum_{k=0}^4 a_k x^4$, a possible companion matrix is given by
 
@@
 
-The experiment considered instances of E3P where the three points are the vertices of an ellipse rotated by $\theta\in[0, \pi)$.
+The experiment considered instances of E3P where the three points are vertices of an ellipse rotated by $\theta\in[0, \pi)$.
 Such instances only have one solution, and therefore, roots with multiplicity greater than one are expected.

### 2020-07-19 paper/implementation.tex
finsh some corrections

--- 2020-03-22 defesa/article/implementation.tex
@@
 
-In the algorithm to obtain every solution of E3P described in \autoref{section:e3p}, we assumed that a procedure which returns every eigenvalue of a given complex matrix was available.
+In the algorithm to obtain every solution of E3P described in Section~\ref{section:e3p}, we assumed that a procedure which returns every eigenvalue of a given complex matrix was available.
 In practice, we used the famous linear algebra package LAPACK (see \cite{lapack} for more details).
@@
 
-Back in \autoref{section:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:xi} as a complex polynomial in the new variable $z=e^{i\theta}$.
+Back in Section~\ref{section:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:xi} as a complex polynomial in the new variable $z=e^{i\theta}$.
 We suggested that symbolic computation should be used for this task, as the expressions for that polynomial's coefficients become very long, and doing that by hand is, to say the least, a very tedious work.

### 2020-07-19 paper/introduction.tex
finsh some corrections

--- 2020-07-19 article/introduction.tex
@@
 
-PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in \cite{bansal}, for example, they are defined as rectangles.
-In \cite{church:1984}, a method was proposed for the version of PMCLP, where the facilities have Euclidean norm coverage.
-This method consisted of obtaining a discrete set of solutions for each facility, which was proved to contain at least one optimal solution, and then using the model developed for MCLP in \cite{church:1974} to determine an optimal solution.
+{\color{Red}PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in \cite{bansal}, for example, the demand set is defined as a set of rectangles; and in \cite{younies}, a version of PMCLP where coverage is determined using block norms is studied.
+For a more comprehensive review on PMCLP and MCLP, please see \cite{murray}.}
+
+{\color{Red}In our work, because of the similarities with the problems studied by us, we are particularly interested in the Euclidean PMCLP defined with coverage being determined by the Euclidean norm.
+In \cite{church:1984}, a method for this version of PMCLP was developed following the demonstration of a theorem, which showed that a finite set of locations could be constructed to contain at least one optimal solution transforming PMCLP into a combinatorial optimization problem.}
 
@@
 We study two versions of PMCLP with elliptical coverage facilities in this work.
-For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
+For both of them, each ellipse is defined to have {\color{Red}fixed major and minor axis} and an undefined location, which is part of the solution.
 In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.

### 2020-07-19 paper/prunning.tex
finsh some corrections

--- 2020-03-17 defesa/article/prunning.tex
@@
 
-Suppose that the first $k$ ellipses are fixed at locations $(q_1,\dots, q_k)$, and that we have an lower-bound $L$ for the value of an optimal solution.
+Suppose that the first $k$ ellipses are fixed at locations $(q_1,\dots, q_k)$, and that we have a lower-bound $L$ for the value of an optimal solution.
 Let $Z_k=\Pp\setminus \cup_{j=1}^k E_j(q_j)$ be the points not covered by the first $k$ ellipses, then we can use \autoref{eq:upper-1} to verify if we can skip every solution where the first $k$ ellipses are fixed at  $(q_1,\dots, q_k)$ or not.

### 2020-07-26 paper/answer_rev_1.tex
wip

--- 2020-07-19 paper/cover.tex
@@
 %\renewcommand\qedsymbol{$\blacksquare$}
+\usepackage[dvipsnames]{xcolor}
 
@@
 
-		%\title{Cover Letter}
+		%\title{Answer to Reviewer #1}
 		%\maketitle
@@
 
-			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
+		\opening{Answer to Reviewer \#1}
+		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
 
-		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.
+		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.
 
-		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.
+		The changes we have made to the text are highlighted by different colors. 
+		\begin{itemize}
+			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper derived.
 
-		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.
+			\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.
+
+			\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.
+		\end{itemize}
+
+		Following we provide answers to each one of your comments:
+
+		\textbf{Comment \#1:} ``(...) In particular, addressing under which real-world conditions the elliptical shape is the ideal shape to model coverage (...)".
+
+		We address this issued by re-writing a piece of our introduction.
+The changes are in the ``Introduction" section (page 3).
+We decided to make a brief comment about the real-world applications of the problem and cite another work that explores this with greater detail.
+Also, because of the changes made to fit this comment, we ended up rewriting the next paragraph.
+
+		\textbf{Comment \#2:} ``(...) Given fixed coverage areas, is it possible to allow minor and major axes to be decision variables to determine with shapes cover a particular space better?
+The aspect ratio and how elongated or circular the ellipses are at the final solution given different space densities might be an interesting issue to explore, rather than fixing the shape of the ellipses from the onset."
+
+		We thought about this extension for a while, but it does not seem to be trivial to adapt the current method to make it work for this version of the problem, at least we could not figure out a way to do it.
+Also, we did not find any evidence that this particular extension has a real-world motivation behind it, so we decided not to further explore it in the main text, and just added a paragraph to the ``Conclusion" section (page 29) elaborating on some possible extensions (including this one) that could be the theme of future research.
 

### 2020-07-26 paper/answer_rev_2.tex
wip

--- 2020-07-26 paper/answer_rev_1.tex
@@
 
-		\opening{Answer to Reviewer \#1}
+		\opening{Answer to Reviewer \#2}
 		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
@@
 		\begin{itemize}
-			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper derived.
+			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper originated.
 
-			\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.
+			\item The {\color{Red} red} highlights are corrections concerning the points made by reviewer \#1.
 
-			\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.
+			\item The {\color{Green} green} highlights are corrections concerning the points made by reviewer \#2.
+
+			\item The {\color{Orange} orange} highlights are corrections concerning points made by both reviewers.
 		\end{itemize}
@@
 
-		\textbf{Comment \#1:} ``(...) In particular, addressing under which real-world conditions the elliptical shape is the ideal shape to model coverage (...)".
+		\textbf{Comment \#1:} `` The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."
 
+		We address this issued by adding a paragraph to the end of our introduction, please see page 3 and 4.
+
+		\textbf{Comment \#2:} ``In my opinion "fixed shape" ellipses should be replaced by "fixed shape parameters" ellipses, or ellipses with the given semi-major and semi-minor axes.
+Alternately the term "fixed shape" ellipses should be explained."
+
+		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote some pieces of text were this was being used:
+		\begin{itemize}
+			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.
+
+			\item In the ``Introduction" section (page 3), we changed the description of our problem to: ``(...) each ellipse is defined to have fixed major and minor axis and an undefined location (...)."
+
+			\item Section 4 had in its title (page 7) ``(...) of An Ellipse Given Its Shape and (...)", we replaced it by ``(...) of An Ellipse Given Its Shape Parameters and (...)."
+		\end{itemize}
+
+		\textbf{Comment \#3:} ``Please, extend the description of practical applications."
 		We address this issued by re-writing a piece of our introduction.
@@
 
-		\textbf{Comment \#2:} ``(...) Given fixed coverage areas, is it possible to allow minor and major axes to be decision variables to determine with shapes cover a particular space better?
-The aspect ratio and how elongated or circular the ellipses are at the final solution given different space densities might be an interesting issue to explore, rather than fixing the shape of the ellipses from the onset."
+		\textbf{Comment \#4:} ``The literature review in Introduction is a bit limited and should to be extended analyzing more approaches and references on the subject.
+It can be expected that beginning from the first publication [8] in 1984 a reasonable number of references on the subject have been published.
+See, e.g.
+papers: (...)"
 
-		We thought about this extension for a while, but it does not seem to be trivial to adapt the current method to make it work for this version of the problem, at least we could not figure out a way to do it.
-Also, we did not find any evidence that this particular extension has a real-world motivation behind it, so we decided not to further explore it in the main text, and just added a paragraph to the ``Conclusion" section (page 29) elaborating on some possible extensions (including this one) that could be the theme of future research.
+		This issued is addressed in the ``Introduction" section on page 2. We agree with you that the literature review needed improvement, this is the sum-up of the changes we made:
+
+		\begin{itemize}
+			\item We add a citation to ``H Younies and G O Wesolowsky.
+Planar maximal covering location problem under block norm distance measure".
+This shows another example of versions of PMCLP other than the classical one using Euclidean norm.
+			\item We add a citation to the survey paper: ``Alan T.
+Murray.
+Maximal coverage location problem: Impacts, significance, and evolution.".
+Instead of giving an extensive review, we use a common practice of citing a survey paper.
+		\end{itemize}
+
+		Also, regarding the possible works that we could cite in our paper suggested by you, besides the PHD thesis of Daoqin Tong, who has some of his works cited in the above survey, we think that the other suggested papers seem not to be that closely related to our problem.
+
+		\textbf{Comment \#5:} ``Please, clarify what is the critical parameter for your algorithm: the number of ellipses or the number of demand points?"
+
+		We addressed this issue in section 8.2 ``New instances" (page 19). Now, we hope it is clear that the critical parameter is the number of ellipses.
+
+		\textbf{Comment \#6:} ``In the paper overlapping of covering ellipses is allowed, i.e.
+a demand point can be covered by more than one ellipse.
+However, it seems natural that the weight of the demand point covered by various ellipses can differ from the weight of the same point covered by only one ellipse."
+
+		We are using the same definition of PMCLP used in the several works we cited, maybe you could elaborate more why this seems natural?
+
+		\textbf{Comment \#7:} ``What happens if no overlapping between covering ellipses is allowed. Please, comment on this."
+
+		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.
+		\href{http://www.sharelatex.com}{Something Linky}
 

### 2020-07-26 paper/article.tex
wip

@@
 
-\section{Determining Every Center and Angle of Rotation of An Ellipse Given Its Shape and Three Points that It Must Contain}\label{section:e3p}
+\section{Determining Every Center and Angle of Rotation of An Ellipse Given {\color{Red} Its Shape Parameters} and Three Points that It Must Contain}\label{section:e3p}
 

### 2020-07-26 paper/conclusion.tex
wip

--- 2020-07-19 article/conclusion.tex
@@
 	Finally, we leave some additional suggestions for future works on this subject.
-We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though, extensive work would be necessary to adapt, somehow, the theory developed for this version, especially, of MCER.
+We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though extensive work would be necessary to adapt, somehow, the theory developed for this version, especially of MCER.
 We also believe that investigating coverage of points by ellipsoids in higher dimensions can be a great subject of future studies taking this work as the starting point; 
 coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective.
-}
+%{\color{Red}
+%	The last suggestion we give is that 
+%	Lastly, as it has been pointed out, the critical parameter of both algorithms developed in this paper is the number of ellipses.
+We think that trading-off being able to run with large demand sets can be the basis for future work on an alternative algorithm that can obtain optimal solutions for instances with larger sets of ellipses.}
+%}

### 2020-07-26 paper/introduction.tex
wip

@@
 %New paragraph
-{\color{Green}
+{\color{Orange}
 	In the real world, this problem comes up when a telecommunications company has to buy and place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming profit maximization.
@@
 This paper is organized as follows.
-Section~\ref{section:definition} presents the definitions of both problems as well as introduces some notations used throughout the rest of the work.
-The algorithm for MCE is developed in Section~\ref{section:mce}, and the algorithm for MCER in Section~\ref{section:mcer} with the observation that its development depends on a subproblem whose algorithm is developed in Section~\ref{section:e3p}.
+Section~\ref{section:definition} presents the definitions of both problems and introduces some notations used throughout the rest of the work.
+An algorithm for MCE is developed in Section~\ref{section:mce}, and an algorithm for MCER in Section~\ref{section:mcer} with the observation that its development depends on a subproblem whose algorithm is developed in Section~\ref{section:e3p}.
 Improvements suggestions to the implementations are given in Section~\ref{section:improvements} while the implementation details are given in Section~\ref{section:implementation}.

### 2020-07-26 paper/answer_rev_2.tex
wip

@@
 		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.
-		\href{http://www.sharelatex.com}{Something Linky}
+
+		Please see: \href{"https://github.com/danft/masters-thesis/raw/master/paper/figures/answer_to_reviewer_2.pdf"}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer_to_reviewer_2.pdf} for a counter-example of how our algorithm fails for this constraint.
+That is, there is a non-overlapping solution, however, none of them is in the set of solutions we look for.
 

### 2020-07-26 paper/answer_rev_2.tex
wip

--- 2020-07-26 paper/answer_rev_2.tex
@@
 		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.
-		\href{http://www.sharelatex.com}{Something Linky}
+
+		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint.
+That is, there is a non-overlapping solution, however, none of them is in the set of solutions we look for.
 

### 2020-07-31 paper/comments_to_reviewers.tex
wip

--- 2020-07-19 paper/cover.tex
@@
 \begin{document}
+\begin{letter}{Comments to reviewers}
+			\opening{Dear Steffen Rebennack\\Editor of EJOR}
 
-		%\title{Cover Letter}
-		%\maketitle
+			Thanks for the great opportunity of having our work reviewed by EJOR's editorial board, which provided great comments and suggestions that surely enhanced the quality of our work.
 
-		\begin{letter}{}
+			Besides the modifications in the text to address the issues raised by the reviewers, we have also made some small corrections and changes of notation on our own.
+These modifications were mostly suggestions given by the board that reviewed the dissertation from which this paper derived.
+In the text, we annoted these changes with the color {\color{blue}blue}.
 
-			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
+			The other modifications were made to address the issues raised by the reviewers, and we highlighted them as follows:
 
-		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.
+			\begin{itemize}
+				\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.
 
-		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.
+				\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.
 
-		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.
+				\item The {\color{Orange} orange} highlights are corrections concerning points made by both reviewers.
+			\end{itemize}
+
+			Please see in the next pages the answers to both reviewers.
 
@@
 \end{letter}
-		%\section*{References}
-		%% New version of the num-names style
-		%\bibliographystyle{elsarticle-num}
-		%\bibliography{../references}
+	\input{answer_rev_1.tex}
+	\input{answer_rev_2.tex}
 

### 2020-07-31 paper/answer_rev_2.tex
wip

@@
-\documentclass[letterpaper]{letter}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% The graphicx package provides the includegraphics command.
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{subcaption}
-\usepackage{siunitx}
-\sisetup{group-separator = {,}}
-
-\usepackage{multirow}
-
-%\journal{EJOR}
-
-\usepackage[mathscr]{eucal}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\Co}{\mathbb{Co}}
-\newcommand{\D}{\mathscr{D}}
-\newcommand{\Pp}{\mathscr{P}}
-\newcommand{\Cc}{\mathscr{C}}
-\newcommand{\E}{\mathscr{E}}
-\newcommand{\F}{\mathscr{F}}
-\newcommand{\Ww}{\mathscr{W}}
-\newcommand{\Rr}{\mathscr{R}}
-\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
-\newcommand{\bigO}{\mathscr{O}}
-\newtheorem{thm}{Theorem}
-\newtheorem{prp}{Proposition}
-\newtheorem{lem}{Lemma}
-%\newdefinition{rmk}{Remark}
-%\newdefinition{definition}{Definition}
-%\newproof{pf}{Proof}
-%\renewcommand\qedsymbol{$\blacksquare$}
-\usepackage[dvipsnames]{xcolor}
-
-\RequirePackage{algorithm, algpseudocode}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-\newcommand{\algorithmautorefname}{Algorithm}
-\newcommand{\definitionautorefname}{Definition}
-\newcommand{\thmautorefname}{Theorem}
-\newcommand{\prpautorefname}{Proposition}
-\newcommand{\lemmaautorefname}{Lemma}
-\newcommand{\lemautorefname}{Lemma}
-\newcommand{\sigla}[2]{#2 (#1)}
-\newcommand{\citeonline}[1]{\cite{#1}}
-\signature{Danilo Tedeschi}
-
-\begin{document}
-
 		%\title{Answer to Reviewer #1}
@@
 		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint.
-That is, there is a non-overlapping solution, however, none of them is in the set of solutions we look for.
+That is, there are non-overlapping solutions, however, it is possible to see that our algorithm would fail to find any -- try it yourself, notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
 
@@
 			\end{letter}
-		%\section*{References}
-		%% New version of the num-names style
-		%\bibliographystyle{elsarticle-num}
-		%\bibliography{../references}
-
-\end{document}

### 2020-08-09 paper/answer_rev_1.tex
wip

--- 2020-03-25 defesa/article/cover.tex
@@
-\documentclass{article}
+		%\title{Answer to Reviewer #1}
+		%\maketitle
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[preprint,review,12pt]{elsarticle}
+\section*{Answer to reviewer \# 1}
+		%\opening{Answer to Reviewer \#1}
 
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
 
-%% The graphicx package provides the includegraphics command.
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{subcaption}
-\usepackage{siunitx}
-\sisetup{group-separator = {,}}
+		First, thanks for dedicating your time to revise our work, it is a great honor for us to continue to improve our work with your help.
 
-\usepackage{multirow}
+		Following we provide answers to each one of the comments you have given us:
 
-%\journal{EJOR}
+		\textbf{Comment \#1:} ``The authors indicate that `it is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.' I would like the authors to expand on this.
+In particular, addressing under which real-world conditions the elliptical shape is the ideal shape to model coverage.
+The paper is technically correct, and it was interesting to follow the development of the model; however, the authors did not really intent to connect to a real-world application where elliptical coverage is needed or desired.
+Maybe there's little research because there's no interest on the particular problem?
+In the absence of a practical application motivating the extension to ellipses, this paper has limited interest."
 
-\usepackage[mathscr]{eucal}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\Co}{\mathbb{Co}}
-\newcommand{\D}{\mathscr{D}}
-\newcommand{\Pp}{\mathscr{P}}
-\newcommand{\Cc}{\mathscr{C}}
-\newcommand{\E}{\mathscr{E}}
-\newcommand{\F}{\mathscr{F}}
-\newcommand{\Ww}{\mathscr{W}}
-\newcommand{\Rr}{\mathscr{R}}
-\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
-\newcommand{\bigO}{\mathscr{O}}
-\newtheorem{thm}{Theorem}
-\newtheorem{prp}{Proposition}
-\newtheorem{lem}{Lemma}
-%\newdefinition{rmk}{Remark}
-%\newdefinition{definition}{Definition}
-%\newproof{pf}{Proof}
-%\renewcommand\qedsymbol{$\blacksquare$}
+		We agree with that a real-world application connection was missing in our work.
+We believe that after the changes we made to address this issue, it is clear that the problems explored in our paper is not of limited interested.
 
-\RequirePackage{algorithm, algpseudocode}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-\newcommand{\algorithmautorefname}{Algorithm}
-\newcommand{\definitionautorefname}{Definition}
-\newcommand{\thmautorefname}{Theorem}
-\newcommand{\prpautorefname}{Proposition}
-\newcommand{\lemmaautorefname}{Lemma}
-\newcommand{\lemautorefname}{Lemma}
-\newcommand{\sigla}[2]{#2 (#1)}
-\newcommand{\citeonline}[1]{\cite{#1}}
+		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S.
+Canbolat and Michael von Massow.
+Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:
 
-\begin{document}
-		\title{Cover Letter}
-		\maketitle
+		``In the real world, this problem comes up when a telecommunications company has to buy and
+		place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming
+		profit maximization. More details about the applications of PMCLP can be found in [5], which also
+		ponders about the practical importance of considering the PMCLP with elliptical coverage."
 
-		Dear Editor, we herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.
+		This change can be found in page 3 of the manuscript.
+Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.
 
-		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.
+		\textbf{Comment \#2:} ``I also would like the authors to discuss potential extensions, specially if there's evidence that the elliptical shape is indeed useful to model facility coverage.
+Given fixed coverage areas, is it possible to allow minor and major axes to be decision variables to determine with shapes cover a particular space better?
+The aspect ratio and how elongated or circular the ellipses are at the final solution given different space densities might be an interesting issue to explore, rather than fixing the shape of the ellipses from the onset."
 
-		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.
+		Thanks for this idea of extension to our problem, we think it is very interesting, and we did devote some time to think about it.
+		We believe that there is not a trivial adaptation to any of methods that would make it possible to work for this variation of the problem; at least for us it seems like it would require extensive work.
+		We added a paragraph to the conclusion to pass this idea on, giving it as a suggestion for future works on the subject:
 
-		%\section*{References}
-		%% New version of the num-names style
-		%\bibliographystyle{elsarticle-num}
-		%\bibliography{../references}
+		``We believe
+		that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of
+		MCE and MCER; having only one additional decision variable –the major or minor axis– might
+		still allow a similar model to be employed, even though extensive work would be necessary to
+		adapt, somehow, the theory developed for this version, especially of MCER."
 
-\end{document}
+	%	\closing{On behalf of the authors and with our best regards,}
+			%\end{letter}

### 2020-08-09 paper/answer_rev_2.tex
wip

@@
 
-		\begin{letter}{}
-
-		\opening{Answer to Reviewer \#2}
+%		\begin{letter}{}
+%
+%		\opening{Answer to Reviewer \#2}
 		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}
 
+		\section*{Answer to reviewer \# 2}
 		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.
 
-		The changes we have made to the text are highlighted by different colors. 
-		\begin{itemize}
-			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper originated.
-
-			\item The {\color{Red} red} highlights are corrections concerning the points made by reviewer \#1.
-
-			\item The {\color{Green} green} highlights are corrections concerning the points made by reviewer \#2.
-
-			\item The {\color{Orange} orange} highlights are corrections concerning points made by both reviewers.
-		\end{itemize}
-
-		Following we provide answers to each one of your comments:
+		Following we provide answers to each one of the comments you have given us:
 
@@
 
-		We address this issued by adding a paragraph to the end of our introduction, please see page 3 and 4.
+		We address this issued by adding a paragraph to the end of our Introduction:
 
-		\textbf{Comment \#2:} ``In my opinion "fixed shape" ellipses should be replaced by "fixed shape parameters" ellipses, or ellipses with the given semi-major and semi-minor axes.
-Alternately the term "fixed shape" ellipses should be explained."
+		``This paper is organized as follows. Section 2 presents the definitions of both problems and
+		3introduces some notations used throughout the rest of the work. An algorithm for MCE is developed
+		in Section 3, and an algorithm for MCER in Section 5 with the observation that its development
+		depends on a subproblem whose algorithm is developed in Section 4. Improvements suggestions to
+		the implementations are given in Section 6 while the implementation details are given in Section 7.
+		Numerical results are presented and analyzed in Section 8. Finally, a conclusion is given in Section 9."
 
-		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote some pieces of text were this was being used:
+		This paragraph can be found in the manuscript in pages 3 and 4.
+
+		\textbf{Comment \#2:} ``In my opinion `fixed shape' ellipses should be replaced by `fixed shape parameters' ellipses, or ellipses with the given semi-major and semi-minor axes.
+Alternately the term `fixed shape' ellipses should be explained."
+
+		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote the pieces of text where this was being used:
 		\begin{itemize}
@@
 
-			\item In the ``Introduction" section (page 3), we changed the description of our problem to: ``(...) each ellipse is defined to have fixed major and minor axis and an undefined location (...)."
+			\item In the Introduction section (page 3), we changed the description of our problem to: ``(...) each ellipse is defined to have fixed major and minor axis and an undefined location (...)."
 
@@
 		\textbf{Comment \#3:} ``Please, extend the description of practical applications."
-		We address this issued by re-writing a piece of our introduction.
-The changes are in the ``Introduction" section (page 3).
-We decided to make a brief comment about the real-world applications of the problem and cite another work that explores this with greater detail.
-Also, because of the changes made to fit this comment, we ended up rewriting the next paragraph.
+
+		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S.
+Canbolat and Michael von Massow.
+Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:
+
+		``In the real world, this problem comes up when a telecommunications company has to buy and
+		place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming
+		profit maximization. More details about the applications of PMCLP can be found in [5], which also
+		ponders about the practical importance of considering the PMCLP with elliptical coverage."
+
+		This change can be found in page 3 of the manuscript.
+Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.
 
@@
 See, e.g.
-papers: (...)"
+papers:
 
-		This issued is addressed in the ``Introduction" section on page 2. We agree with you that the literature review needed improvement, this is the sum-up of the changes we made:
+		'A Combinatorial Maximum Cover Approach to 2D Translational Geometric Covering' by K. Daniels A. Mathur R. Grinde
+
+		'Covering a polygonal region by rectangles' by G. Scheithauer, Y. Stoyan, T. Romanova, A. Krivulya
+
+		'Translational polygon containment and minimal enclosure' using mathematical programming
+		by V.J. Milenkovic , K. Daniels
+
+		and references in 2007 PhD thesis of Daoqin Tong from the Ohio State University."
+
+		This issued is addressed in the Introduction section on page 2.
+We agree with you that the literature review needed improvement, and we believe that we were able to improve on that regard with the following changes:
 
 		\begin{itemize}
-			\item We add a citation to ``H Younies and G O Wesolowsky.
+			\item We added a citation to ``H Younies and G O Wesolowsky.
 Planar maximal covering location problem under block norm distance measure".
 This shows another example of versions of PMCLP other than the classical one using Euclidean norm.
-			\item We add a citation to the survey paper: ``Alan T.
+			\item We added a citation to the survey paper: ``Alan T.
 Murray.
@@
 
-		Also, regarding the possible works that we could cite in our paper suggested by you, besides the PHD thesis of Daoqin Tong, who has some of his works cited in the above survey, we think that the other suggested papers seem not to be that closely related to our problem.
+	Now, after these additions, the piece of our Introduction doing literature review of PMCLP is as follows:
+
+	``A continuous extension of MCLP, where the facility and demand sets are located on the plane and coverage is determined by a norm function, was introduced in [8] and named Planar Maximal	Covering Location Problem (PMCLP) following the advances on covering location problems on the	plane that were being made at the time.
+
+	PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage
+	defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in [4], for example, the demand set is defined as a set of rectangles; and in [20], a version of PMCLP where coverage is determined using block norms is studied.
+For a more comprehensive review on PMCLP and MCLP, please see [15].
+
+	In our work, because of the similarities with the problems studied by us, we are particularly interested in the Euclidean PMCLP defined with coverage being determined by the Euclidean norm.	In [8], a method for this version of PMCLP was developed following the demonstration of a theorem,	which showed that a finite set of locations could be constructed to contain at least one optimal	solution transforming PMCLP into a combinatorial optimization problem."
+
+	We did consider the list of suggested works we could look at to improve our literature review you have given us, however, even though we think they are great suggestions, we decided to cite two works we were more familiar with, also with the intention of not extending this part of the Introduction too much.
+	It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.
 
@@
 
-		We addressed this issue in section 8.2 ``New instances" (page 19). Now, we hope it is clear that the critical parameter is the number of ellipses.
+		We addressed this issue in section 8.2 ``New instances" (page 19):
+
+		``We were able to run experiments with up to 700 demand points; however, it is clear that the number of ellipses is the critical parameter of both algorithms, as even for small demand sets, we could not go over 7 ellipses."
 
@@
 
-		We are using the same definition of PMCLP used in the several works we cited, maybe you could elaborate more why this seems natural?
+		Thanks for this comment, we, too, think that depending on the viewpoint, considering the weight of each point to be a function which depends on the set of ellipses covering is more natural.
+We believe that our methods could be trivially adapted to work with this different definition, however, we also think that we have to ponder about doing this change because this is not the traditional definition of any other PMCLP we have based our developments on; meaning that we would have to have a strong motive for this not to look like an arbitrary change.
 
@@
 
-		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.
+		Thanks for the great question, we thought a lot about this, and we came up with some arguments to show you what happens if we add this constraint to our problem.
 
-		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint.
-That is, there are non-overlapping solutions, however, it is possible to see that our algorithm would fail to find any -- try it yourself, notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
+		First, for an example of covering without overlapping, please see the paper ``Covering point sets with two disjoint disks or squares" by Cabello, S., Díaz Báñez, J.M., Seara, C., Sellarès, J.A., Urrutia, J., Ventura, I.
 
-		\closing{On behalf of the authors and with our best regards,}
-			\end{letter}
+		This work deals with the problem of covering points using two Euclidean disks with the constraint of no overlapping being allowed.
+This article is cited by a work we are citing in our Introduction: ``Covering many or few points with unit disks." by Mark de Berg, Sergio Cabello, and Sariel Har-Peled.
+		This work develops an algorithm for the overlap-allowed covering of points by multiple Euclidean disks.
+In its Introduction, the authors cite the previous work that does not allow overlap saying: ``This condition changes the problem significantly, because now issues related to packing problems arise".
+		Based on this, we are safe to say that we should expect that adding a no-overlap constraint would change our problem significantly too.
+
+		The way our methods work is to look for solutions with points on the ellipses, this type of solution is not favorable when we have this constraint as, for example, see the counter-example in this figure:
+
+		\includegraphics[scale=.6]{figures/answer-to-reviewer-2}
+
+		It is possible to see that there are non-overlapping solutions, however, our algorithm would fail to find any.
+Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
+
+		We believe methods for the problems with this additional constraint would have to come from a different base idea than ours do.
+
+	%	\closing{On behalf of the authors and with our best regards,}
+	%		\end{letter}

### 2020-08-09 paper/comments_to_reviewers.tex
wip

@@
-\documentclass[letterpaper]{letter}
+\documentclass{report}
 
+%\usepackage{scrletter}
 %% Use the option review to obtain double line spacing
@@
 \newcommand{\citeonline}[1]{\cite{#1}}
-\signature{Danilo Tedeschi}
+%\signature{Danilo Tedeschi}
 
 \begin{document}
-\begin{letter}{Comments to reviewers}
-			\opening{Dear Steffen Rebennack\\Editor of EJOR}
+
+%\begin{letter}{Comments to reviewers}
+%			\opening{Dear Steffen Rebennack\\Editor of EJOR}
+%			\date{}
+
+			\noindent Dear Steffen Rebennack,\\ Editor of EJOR
+			\\
+			\\
 
@@
 
-			Besides the modifications in the text to address the issues raised by the reviewers, we have also made some small corrections and changes of notation on our own.
-These modifications were mostly suggestions given by the board that reviewed the dissertation from which this paper derived.
-In the text, we annoted these changes with the color {\color{blue}blue}.
+			Besides the modifications in the text to address the issues raised by the reviewers, we have also made some small corrections and changes of notation on our own in the hopes of improving the manuscript.
+In the text, we annotated these changes with the color {\color{blue}blue}.
 
@@
 			Please see in the next pages the answers to both reviewers.
+			\\
+			\\
+			\\
+			On behalf of the authors and with our best regards,\\
+			Danilo Tedeschi.
+%\end{letter}
+\clearpage
+	\input{answer_rev_1.tex}
 
-			\closing{On behalf of the authors and with our best regards,}
-\end{letter}
-	\input{answer_rev_1.tex}
+	\clearpage
 	\input{answer_rev_2.tex}

### 2020-08-10 paper/answer_rev_1.tex
wip

@@
 		First, thanks for dedicating your time to revise our work, it is a great honor for us to continue to improve our work with your help.
-
-		Following we provide answers to each one of the comments you have given us:
+We have split your review into two sections, which we called ``comments", one regarding the lack of a real-world application connection, and the other regarding potential extensions to the problems studied by us.
+Please find below our responses to them.
+		\\
 
@@
 
-		We agree with that a real-world application connection was missing in our work.
-We believe that after the changes we made to address this issue, it is clear that the problems explored in our paper is not of limited interested.
-
-		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S.
+		Thanks a lot for this great detailed feedback. 
+		Upon receiving your input, we did question ourselves about the interest there is on our work, and we ended up coming to an agreement that a real-world connection is fundamental to making a case this problem is worth being published.
+		We addressed this issue by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S.
 Canbolat and Michael von Massow.
@@
 Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.
+		\\
 
@@
 
-		Thanks for this idea of extension to our problem, we think it is very interesting, and we did devote some time to think about it.
-		We believe that there is not a trivial adaptation to any of methods that would make it possible to work for this variation of the problem; at least for us it seems like it would require extensive work.
-		We added a paragraph to the conclusion to pass this idea on, giving it as a suggestion for future works on the subject:
+		Thanks for this idea of an extension to our problem, we think it is very interesting, and we did devote some time to think about it.
+		We believe that there is not a trivial adaptation to any of our methods that would make it possible to work for this variation of the problem; at least for us, it seems like it would require extensive work.
+		We hypothesized that with this addition of a new variable (the ellipse's semi-major or semi-minor), we could have a similar result for MCER: there is a constant number of let's call locations (center, angle of rotation, and the new parameter), which makes four points be on the ellipse with a fixed area.
+Although, We could not prove it nor disprove it.
+		We also thought about the possibility of having an optimization method on top of our current algorithm to decide the new parameter, but we could not think of a way we could make a model like that work.
+		Even though we could not make too much out of the suggestion, we still believe that it could be a good idea for future works on the subject.
+Therefore, we added a paragraph to the conclusion to pass this idea on:
 

### 2020-08-11 paper/answer_rev_2.tex
wip

@@
 		\section*{Answer to reviewer \# 2}
-		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.
+		Thanks a lot for dedicating your time to revise our work.
+We found every one of your comments very helpful and insightful, and we believe that after taking them into account our work has much improved.
 
-		Following we provide answers to each one of the comments you have given us:
+		Following we provide replies to each one of the comments you have given us:
 
-		\textbf{Comment \#1:} `` The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."
+		\textbf{Comment \#1:} ``The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."
 
-		We address this issued by adding a paragraph to the end of our Introduction:
+		We addressed this issued by adding a paragraph to the end of our Introduction:
 
@@
 		This paragraph can be found in the manuscript in pages 3 and 4.
+		\\
 
@@
 
-		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote the pieces of text where this was being used:
+		Thanks for the great observation; we agree that it is not very clear what the term 'fixed shape' ellipses means, and decided to rewrite the text everywhere it appeared.
+Please find below the changes we have made:
 		\begin{itemize}
@@
 
-		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S.
+		Thanks for the comment, we addressed this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S.
 Canbolat and Michael von Massow.
@@
 
-		This issued is addressed in the Introduction section on page 2.
-We agree with you that the literature review needed improvement, and we believe that we were able to improve on that regard with the following changes:
+		Thanks for all the great suggestions, after pondering about it, we agree that our literature review needed work, thanks for pointing it out.
+		We spent some time on trying to improve it, in summary, those are the changes we have made to our introduction:
 
@@
 
-	Now, after these additions, the piece of our Introduction doing literature review of PMCLP is as follows:
+	After these additions, the piece of our Introduction doing literature review of PMCLP is as follows:
 
@@
 
-	We did consider the list of suggested works we could look at to improve our literature review you have given us, however, even though we think they are great suggestions, we decided to cite two works we were more familiar with, also with the intention of not extending this part of the Introduction too much.
+	We did consider the list of works you gave us as suggestions, however, even though we think they are great papers, we decided to cite two works we were more familiar with.
 It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.
+\\
 
@@
 		``We were able to run experiments with up to 700 demand points; however, it is clear that the number of ellipses is the critical parameter of both algorithms, as even for small demand sets, we could not go over 7 ellipses."
+		\\
 
@@
 
-		Thanks for this comment, we, too, think that depending on the viewpoint, considering the weight of each point to be a function which depends on the set of ellipses covering is more natural.
+		Thanks for this comment, we, too, think that depending on the viewpoint, considering the weight of each point to be a function which depends on the set of ellipses covering it is more natural.
 We believe that our methods could be trivially adapted to work with this different definition, however, we also think that we have to ponder about doing this change because this is not the traditional definition of any other PMCLP we have based our developments on; meaning that we would have to have a strong motive for this not to look like an arbitrary change.
+		\\
 
@@
 
-		The way our methods work is to look for solutions with points on the ellipses, this type of solution is not favorable when we have this constraint as, for example, see the counter-example in this figure:
+		We also produced an example to show you what would happen if we simply added this constraint without changing anything to our method. 
+		The way our algorithms work is that it looks for solutions with points on the ellipses.
+This type of solution is not favorable when we have this constraint as, for example, see the counter-example in this figure:
 
@@
 
-		It is possible to see that there are non-overlapping solutions, however, our algorithm would fail to find any.
+		The solution shown is non-overlapping -- actually there are an infinite number of non-overlapping equivalent solutions --, however, our algorithm would fail to find any equivalent solution.
 Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
-
-		We believe methods for the problems with this additional constraint would have to come from a different base idea than ours do.
+		We believe methods for the problems with this additional constraint would have to come from a different basis.
 

### 2020-08-15 paper/answer_rev_2.tex
wip

@@
 		\textbf{Comment \#1:} ``The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."
+		\\
 
@@
 
-		``This paper is organized as follows. Section 2 presents the definitions of both problems and
-		3introduces some notations used throughout the rest of the work. An algorithm for MCE is developed
+		``This paper is organized as follows. Section 2 presents the definitions of both problems and introduces some notations used throughout the rest of the work. An algorithm for MCE is developed
 		in Section 3, and an algorithm for MCER in Section 5 with the observation that its development
@@
 Alternately the term `fixed shape' ellipses should be explained."
+		\\
 
-		Thanks for the great observation; we agree that it is not very clear what the term 'fixed shape' ellipses means, and decided to rewrite the text everywhere it appeared.
+		Thanks for the great observation; we agree that it is not very clear what the term `fixed shape' ellipses means, and decided to rewrite the text everywhere it appeared.
 Please find below the changes we have made:
@@
 Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:
+		\\
 
@@
 
-		'A Combinatorial Maximum Cover Approach to 2D Translational Geometric Covering' by K. Daniels A. Mathur R. Grinde
+		`A Combinatorial Maximum Cover Approach to 2D Translational Geometric Covering' by K. Daniels A. Mathur R. Grinde
 
-		'Covering a polygonal region by rectangles' by G. Scheithauer, Y. Stoyan, T. Romanova, A. Krivulya
+		`Covering a polygonal region by rectangles' by G. Scheithauer, Y. Stoyan, T. Romanova, A. Krivulya
 
-		'Translational polygon containment and minimal enclosure' using mathematical programming
+		`Translational polygon containment and minimal enclosure' using mathematical programming
 		by V.J. Milenkovic , K. Daniels
@@
 		and references in 2007 PhD thesis of Daoqin Tong from the Ohio State University."
+		\\
 
-		Thanks for all the great suggestions, after pondering about it, we agree that our literature review needed work, thanks for pointing it out.
-		We spent some time on trying to improve it, in summary, those are the changes we have made to our introduction:
+		Thanks for all the great suggestions, after pondering about it, we agree that our literature review needed work, it is great that you pointed it out.
+		We spent some time on trying to improve it, and in summary, those are the changes we have made to our Introduction:
 
@@
 
-	We did consider the list of works you gave us as suggestions, however, even though we think they are great papers, we decided to cite two works we were more familiar with.
+	We did consider the list of works you gave us as suggestions, however, even though we think they are great papers, we decided to cite works that we judged to be closer to the problems we are studying.
+We also had the goal to not extend the literature review too much, as the field of geometric covering is too vast, we tried to keep it concise by only citing works that study very specific problems, and a survey paper.
 	It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.
+If after reading this, you still feel like our literature review is not satisfactory, we can change it to include your suggestions.
 \\
@@
 		\textbf{Comment \#5:} ``Please, clarify what is the critical parameter for your algorithm: the number of ellipses or the number of demand points?"
+		\\
 
-		We addressed this issue in section 8.2 ``New instances" (page 19):
+		We addressed this issue in Section 8.2 ``New instances" (page 19):
 
@@
 However, it seems natural that the weight of the demand point covered by various ellipses can differ from the weight of the same point covered by only one ellipse."
+		\\
 
@@
 		\textbf{Comment \#7:} ``What happens if no overlapping between covering ellipses is allowed. Please, comment on this."
+		\\
 
@@
 
-		The solution shown is non-overlapping -- actually there are an infinite number of non-overlapping equivalent solutions --, however, our algorithm would fail to find any equivalent solution.
+		The solution shown is non-overlapping -- actually there are an infinite number of non-overlapping equivalent solutions --.
+However, our algorithm would fail to find any equivalent solution.
 Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.

### 2020-08-15 paper/comments_to_reviewers.tex
wip

@@
 			\begin{itemize}
-				\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.
+				\item The {\color{Red} red} highlights are corrections concerning the points made by reviewer \#1.
 
-				\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.
+				\item The {\color{Green} green} highlights are corrections concerning the points made by reviewer \#2.
 

### 2020-08-16 paper/acknowledgments.tex
wip

%We are very grateful for the editorial process conducted by this journal, every comment, and suggestion sent to us by the reviewers were very insightful and detailed; without them, we could not have improved our work the way we did, reaching the quality it is now.

We are very grateful for the editorial process conducted by this journal, every comment. The reviewers sent us very detailed and insightful comments and suggestions; without them, we could not have improved our work the way we did, reaching the quality it is now.

We would also like to express our gratitude to the funding institutions Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES), and Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP)\footnote{Processes 2013/07375-0 and 2016/01860-1.} that made this research possible.

### 2020-08-17 paper/acknowledgments.tex
wip

@@
 
-We are very grateful for the editorial process conducted by this journal, every comment.
-The reviewers sent us very detailed and insightful comments and suggestions; without them, we could not have improved our work the way we did, reaching the quality it is now.
-
-We would also like to express our gratitude to the funding institutions Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES), and Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP)\footnote{Processes 2013/07375-0 and 2016/01860-1.} that made this research possible.
+We would like to thank the reviewers for their useful suggestions, that greatly improved this work.
+We would also like to express our gratitude to the funding institutions Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES), and Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) (processes 2013/07375-0 and 2016/01860-1) that made this research possible.

### 2020-08-18 paper/article.tex
wip

@@
 
-\bibliographystyle{plainnat}
+\bibliographystyle{elsarticle-template/model2-names}
+%\biboptions{longnamesfirst,angle,semicolon}
 
@@
 		\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
-		\tnotetext[t1]{This paper is the results of the research
-			project funded by CAPES and FAPESP.}
+	%	\tnotetext[t1]{This paper is the results of the research
+	%		project funded by CAPES and FAPESP.}
 
 		\author[add1]{Danilo Tedeschi\corref{cor1}}
-		\ead{danilo.tedeschi@usp.br}
+		\ead{danilof.t2@gmail.com}
 
@@
 
-		\address[add1]{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
+		\address[add1]{Departamento de Matemática Aplicada e Estatística, Instituto de Ciências Matemáticas e de Computação, Universidade de São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
 
@@
 \input{conclusion.tex}
+{\color{Brown}
+\section{Acknowledgments}\label{section:acknowledgements}
+\input{acknowledgments.tex}
+}
 
